% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[margin=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[1pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Experienced Software Engineer with 3+ years in full stack development, skilled in Java, Python, and cloud technologies. Proven track record delivering scalable web apps, optimizing database performance, and leading cross-functional teams. Strong knowledge in Agile methodologies and DevOps practices drives efficient product delivery and continuous integration. Passionate about leveraging innovative solutions for impactful business results.

\vspace{3pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, TypeScript, Java, SQL, HTML/CSS, Bash

\textbf{Frameworks \& Libraries:} React, Node.js, Express.js, Django, Bootstrap, jQuery

\textbf{Database \& Data Management:} MySQL, PostgreSQL, MongoDB, DynamoDB

\textbf{Cloud \& DevOps:} AWS (EC2, S3, Lambda), Docker, Kubernetes, CI/CD, GitLab, GitHub Actions

\textbf{Software Development Practices:} Agile methodology, Scrum, Test Driven Development, pair programming, SDLC, debugging

\textbf{Computer Science Fundamentals:} Object Oriented Programming, Data Structures, Algorithms, Design Patterns

\textbf{Systems \& Networking:} RESTful APIs, microservices architecture, Unix/Linux environments, security best practices

\textbf{Soft Skills:} Team collaboration, mentoring, problem solving, communication, continuous learning

\vspace{6pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer – KILATECH (Pvt) Ltd, Sri Lanka (Apr 2020 – Dec 2022) -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{1pt}

Worked as a full stack developer, primarily developing Shopify applications and managing custom web application projects from development through deployment, RESTful APIs, cloud services, CI/CD pipelines, security best practices, and comprehensive testing.

\begin{itemize}
\item Developed scalable full stack web and Shopify apps leveraging JavaScript, React, and Node.js to enhance e-commerce platforms.
\item Implemented RESTful APIs, integrated payment systems, and optimized database queries for performance and reliability.
\item Deployed and maintained cloud based applications using AWS, Docker, and CI/CD pipelines ensuring 99\% uptime.
\item Collaborated in Agile teams through pair programming and code reviews, contributing to continuous improvement culture.
\item Applied TDD and secure coding standards throughout the SDLC, improving maintainability and reducing defects.
\end{itemize}

\textbf{Software Engineer – KILATECH (Pvt) Ltd, Sri Lanka (Apr 2020 – Dec 2022) -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{1pt}

Supported the development of enterprise applications by contributing to both frontend and backend tasks across multiple projects.

\begin{itemize}
\item Assisted in the development of enterprise level web and mobile applications, contributing across both frontend and backend.
\item Participated in the design and implementation of a Proposal Management System and Mailroom Tracking System.
\item Collaborated with cross functional teams to gather requirements, perform testing, and ensure successful deployments.
\item Gained experience in full stack development, software testing, and secure coding within a collaborative Agile environment.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Inventory Management System --- \textit{Personal Project}

\vspace{1pt}

Developed a web-based inventory system to streamline stock tracking and reporting.

\begin{itemize}
\item Built responsive UI with React and integrated backend REST APIs using Spring Boot.
\item Implemented real-time stock updates reducing discrepancies by 25\%.
\item Optimized database schema in MySQL, enhancing query response times by 20\%.
\item Deployed the system on AWS for improved scalability and availability.
\end{itemize}

\textbf{Customer Support Chatbot} --- \textit{Group Capstone Project, Seneca Polytechnic}

\vspace{1pt}

Created an AI-powered chatbot to automate customer query handling and improve support.

\begin{itemize}
\item Developed chatbot backend with Python Flask and integrated NLP capabilities.
\item Designed conversational flows to handle 80\% of common inquiries without human aid.
\item Used MongoDB for dynamic data storage and fast retrieval.
\item Implemented CI/CD pipelines for seamless deployment and updates.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}
