% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[margin=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[1pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven software engineer with 2+ years delivering full-stack web applications using JavaScript, React, and Node.js. Skilled in responsive design, RESTful APIs, and Agile methodologies. Proven track record in developing scalable solutions and improving user experience. Adept at collaborating with cross-functional teams to meet deadline-driven goals and enhance product quality.

\vspace{3pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, TypeScript, Java, SQL, HTML/CSS, Bash

\textbf{Frameworks \& Libraries:} React, Node.js, Express.js, Django, Bootstrap, jQuery

\textbf{Database \& Data Management:} MySQL, PostgreSQL, MongoDB, DynamoDB

\textbf{Cloud \& DevOps:} AWS (EC2, S3, Lambda), Docker, Kubernetes, CI/CD, GitLab, GitHub Actions

\textbf{Software Development Practices:} Agile methodology, Scrum, Test Driven Development, pair programming, SDLC, debugging

\textbf{Computer Science Fundamentals:} Object Oriented Programming, Data Structures, Algorithms, Design Patterns

\textbf{Systems \& Networking:} RESTful APIs, microservices architecture, Unix/Linux environments, security best practices

\textbf{Soft Skills:} Team collaboration, mentoring, problem solving, communication, continuous learning

\vspace{6pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Full Stack Developer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{1pt}

\begin{itemize}
\item Designed and implemented scalable web applications using React and Node.js, increasing user engagement by 25\%.
\item Collaborated with cross-functional teams to gather requirements and deliver solutions ahead of schedule.
\item Developed RESTful APIs to integrate front-end components with backend services, improving data flow.
\item Optimized application performance, reducing load time by 30\% through code and asset refinements.
\item Maintained codebase with Git, ensuring version control and smooth team collaboration.
\item Participated in Agile sprints, contributing to backlog grooming and sprint reviews.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{1pt}

\begin{itemize}
\item Assisted in the development of responsive web pages with HTML, CSS, and JavaScript under senior guidance.
\item Implemented unit tests using Jest to ensure code quality and reduce bugs.
\item Contributed to database schema design using MySQL for improved data integrity.
\item Gained practical experience in Agile environments through daily standups and sprint activities.
\item Supported backend service development using Node.js and Express for small application features.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{E-commerce Web Application} --- \textit{Personal Project}

\vspace{1pt}

Developed a full-featured e-commerce platform enabling secure transactions and seamless user experience.

\begin{itemize}
\item Built responsive UI with React and Bootstrap, increasing customer engagement by 20\%.
\item Implemented RESTful APIs in Node.js for product catalog and order management.
\item Integrated payment gateway ensuring secure transactions with 99.9\% uptime reliability.
\item Deployed application on AWS, monitoring performance and scaling resources as needed.
\end{itemize}

\textbf{Task Management System} --- \textit{Group Capstone Project, Seneca Polytechnic}

\vspace{1pt}

Created a task tracking tool with real-time updates and collaborative features to enhance team productivity.

\begin{itemize}
\item Developed frontend using Angular and TypeScript for dynamic user interaction.
\item Designed backend REST APIs with Spring Boot connected to MySQL database.
\item Implemented WebSocket communication for real-time task updates among users.
\item Led application testing and deployment using Docker and Jenkins pipelines.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}