% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[margin=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[1pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Detail-oriented Software Engineer with over 2 years experience delivering scalable web applications using JavaScript, React, and Node.js. Proven ability to enhance user experience and optimize system performance, contributing to project success in agile environments. Skilled in cross-functional collaboration, problem-solving, and end-to-end product development aligned with business goals.

\vspace{3pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, TypeScript, Java, SQL, HTML/CSS, Bash

\textbf{Frameworks \& Libraries:} React, Node.js, Express.js, Django, Bootstrap, jQuery

\textbf{Database \& Data Management:} MySQL, PostgreSQL, MongoDB, DynamoDB

\textbf{Cloud \& DevOps:} AWS (EC2, S3, Lambda), Docker, Kubernetes, CI/CD, GitLab, GitHub Actions

\textbf{Software Development Practices:} Agile methodology, Scrum, Test Driven Development, pair programming, SDLC, debugging

\textbf{Computer Science Fundamentals:} Object Oriented Programming, Data Structures, Algorithms, Design Patterns

\textbf{Systems \& Networking:} RESTful APIs, microservices architecture, Unix/Linux environments, security best practices

\textbf{Soft Skills:} Team collaboration, mentoring, problem solving, communication, continuous learning

\vspace{6pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer – KILATECH (Pvt) Ltd, Sri Lanka (Apr 2020 – Dec 2022) -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{1pt}

Worked as a full stack developer, primarily developing Shopify applications and managing custom web application projects from development through deployment, RESTful APIs, cloud services, CI/CD pipelines, security best practices, and comprehensive testing.

\begin{itemize}
\item Developed scalable full stack web and Shopify apps leveraging JavaScript, React, and Node.js to enhance e-commerce platforms.
\item Implemented RESTful APIs, integrated payment systems, and optimized database queries for performance and reliability.
\item Deployed and maintained cloud based applications using AWS, Docker, and CI/CD pipelines ensuring 99\% uptime.
\item Collaborated in Agile teams through pair programming and code reviews, contributing to continuous improvement culture.
\item Applied TDD and secure coding standards throughout the SDLC, improving maintainability and reducing defects.
\end{itemize}

\textbf{Software Engineer – KILATECH (Pvt) Ltd, Sri Lanka (Apr 2020 – Dec 2022) -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{1pt}

Supported the development of enterprise applications by contributing to both frontend and backend tasks across multiple projects.

\begin{itemize}
\item Assisted in the development of enterprise level web and mobile applications, contributing across both frontend and backend.
\item Participated in the design and implementation of a Proposal Management System and Mailroom Tracking System.
\item Collaborated with cross functional teams to gather requirements, perform testing, and ensure successful deployments.
\item Gained experience in full stack development, software testing, and secure coding within a collaborative Agile environment.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Customer Feedback Portal --- \textit{Personal Project}

\vspace{1pt}

Developed a React-based feedback system to collect and analyze customer inputs.

\begin{itemize}
\textbackslash\{\}item Designed front-end components enabling seamless user input and real-time validation.
\textbackslash\{\}item Implemented Node.js API linked to MongoDB for data storage and retrieval.
\textbackslash\{\}item Integrated sentiment analysis feature to classify feedback, improving insights by 20\textbackslash\{\}\%.
\textbackslash\{\}item Deployed application using Docker containers ensuring scalable and consistent environment.
\end{itemize}

\textbf{Inventory Management System} --- \textit{Group Capstone Project, Seneca Polytechnic}

\vspace{1pt}

Built a full-stack inventory management app for real-time stock tracking and reporting.

\begin{itemize}
\textbackslash\{\}item Created RESTful APIs using Express.js for secure and efficient data transactions.
\textbackslash\{\}item Developed React dashboard to visualize inventory levels and generate dynamic reports.
\textbackslash\{\}item Established database schema in MySQL supporting complex queries with optimized performance.
\textbackslash\{\}item Implemented user authentication with JWT, enhancing system security and access control.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}