% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[margin=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[1pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with over 3 years of experience in developing robust web applications, specializing in both frontend and backend technologies. Proven track record in agile environments delivering scalable solutions using JavaScript frameworks, REST APIs, and database management. Adept at improving application performance and collaborating cross-functionally to meet business goals.

\vspace{3pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, TypeScript, Java, SQL, HTML/CSS, Bash

\textbf{Frameworks \& Libraries:} React, Node.js, Express.js, Django, Bootstrap, jQuery

\textbf{Database \& Data Management:} MySQL, PostgreSQL, MongoDB, DynamoDB

\textbf{Cloud \& DevOps:} AWS (EC2, S3, Lambda), Docker, Kubernetes, CI/CD, GitLab, GitHub Actions

\textbf{Software Development Practices:} Agile methodology, Scrum, Test Driven Development, pair programming, SDLC, debugging

\textbf{Computer Science Fundamentals:} Object Oriented Programming, Data Structures, Algorithms, Design Patterns

\textbf{Systems \& Networking:} RESTful APIs, microservices architecture, Unix/Linux environments, security best practices

\textbf{Soft Skills:} Team collaboration, mentoring, problem solving, communication, continuous learning

\vspace{6pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer – KILATECH (Pvt) Ltd, Sri Lanka (Apr 2020 – Dec 2022) -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{1pt}

Worked as a full stack developer, primarily developing Shopify applications and managing custom web application projects from development through deployment, RESTful APIs, cloud services, CI/CD pipelines, security best practices, and comprehensive testing.

\begin{itemize}
\item Developed scalable full stack web and Shopify apps leveraging JavaScript, React, and Node.js to enhance e-commerce platforms.
\item Implemented RESTful APIs, integrated payment systems, and optimized database queries for performance and reliability.
\item Deployed and maintained cloud based applications using AWS, Docker, and CI/CD pipelines ensuring 99\% uptime.
\item Collaborated in Agile teams through pair programming and code reviews, contributing to continuous improvement culture.
\item Applied TDD and secure coding standards throughout the SDLC, improving maintainability and reducing defects.
\end{itemize}

\textbf{Software Engineer Trainee – FMI (Pvt) Ltd, Sri Lanka (Apr 2019 – Dec 2019) -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{1pt}

Supported the development of enterprise applications by contributing to both frontend and backend tasks across multiple projects.

\begin{itemize}
\item Assisted in the development of enterprise level web and mobile applications, contributing across both frontend and backend.
\item Participated in the design and implementation of a Proposal Management System and Mailroom Tracking System.
\item Collaborated with cross functional teams to gather requirements, perform testing, and ensure successful deployments.
\item Gained experience in full stack development, software testing, and secure coding within a collaborative Agile environment.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{E-Commerce Platform Development} --- \textit{Personal Project}

\vspace{1pt}

Led full-stack development of scalable e-commerce web app using React and Node.js.

\begin{itemize}
\item Designed responsive UI components with React and Bootstrap for seamless user experience.
\item Built secure REST APIs with Node.js to handle product and user management.
\item Integrated payment gateway and enhanced security protocols to protect transactions.
\item Optimized MongoDB queries reducing database response times by 25\%.
\end{itemize}

\textbf{Inventory Management System} --- \textit{Group Capstone Project, Seneca Polytechnic}

\vspace{1pt}

Developed backend inventory system featuring Spring Boot and MySQL database integration.

\begin{itemize}
\textbackslash\{\}item Implemented RESTful services enabling real-time stock updates and reporting.
\textbackslash\{\}item Engineered database schemas for efficient data storage and retrieval in MySQL.
\textbackslash\{\}item Collaborated with frontend developers to synchronize API endpoints with UI needs.
\textbackslash\{\}item Deployed the solution on AWS improving system availability and scalability.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}