% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[margin=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[1pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with 3+ years in full-stack development, specializing in .NET, React.js, and SQL Server. Proven record optimizing applications for performance and scalability. Skilled in Agile methodologies and cross-functional collaboration. Adept at delivering measurable business value through innovative solutions and strong problem-solving skills.

\vspace{3pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, TypeScript, Java, SQL, HTML/CSS, Bash

\textbf{Frameworks \& Libraries:} React, Node.js, Express.js, Django, Bootstrap, jQuery

\textbf{Database \& Data Management:} MySQL, PostgreSQL, MongoDB, DynamoDB

\textbf{Cloud \& DevOps:} AWS (EC2, S3, Lambda), Docker, Kubernetes, CI/CD, GitLab, GitHub Actions

\textbf{Software Development Practices:} Agile methodology, Scrum, Test Driven Development, pair programming, SDLC, debugging

\textbf{Computer Science Fundamentals:} Object Oriented Programming, Data Structures, Algorithms, Design Patterns

\textbf{Systems \& Networking:} RESTful APIs, microservices architecture, Unix/Linux environments, security best practices

\textbf{Soft Skills:} Team collaboration, mentoring, problem solving, communication, continuous learning

\vspace{6pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Full Stack Developer – KILATECH (Pvt) Ltd, Sri Lanka (Apr 2020 – Dec 2022) -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{1pt}

Worked as a full stack developer, primarily developing Shopify applications and managing custom web application projects from development through deployment, RESTful APIs, cloud services, CI/CD pipelines, security best practices, and comprehensive testing.

\begin{itemize}
\item Developed scalable full stack web and Shopify apps leveraging JavaScript, React, and Node.js to enhance e-commerce platforms.
\item Implemented RESTful APIs, integrated payment systems, and optimized database queries for performance and reliability.
\item Deployed and maintained cloud based applications using AWS, Docker, and CI/CD pipelines ensuring 99\% uptime.
\item Collaborated in Agile teams through pair programming and code reviews, contributing to continuous improvement culture.
\item Applied TDD and secure coding standards throughout the SDLC, improving maintainability and reducing defects.
\end{itemize}

\textbf{Full Stack Developer – KILATECH (Pvt) Ltd, Sri Lanka (Apr 2020 – Dec 2022) -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{1pt}

Supported the development of enterprise applications by contributing to both frontend and backend tasks across multiple projects.

\begin{itemize}
\item Assisted in the development of enterprise level web and mobile applications, contributing across both frontend and backend.
\item Participated in the design and implementation of a Proposal Management System and Mailroom Tracking System.
\item Collaborated with cross functional teams to gather requirements, perform testing, and ensure successful deployments.
\item Gained experience in full stack development, software testing, and secure coding within a collaborative Agile environment.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{E-Commerce Web Application Development --- \textit{Personal Project}

\vspace{1pt}

Built scalable e-commerce platform using React.js frontend and .NET Core backend for seamless user experience.

\begin{itemize}
\textbackslash\{\}item Designed RESTful APIs to handle product catalog and order processing efficiently.
\textbackslash\{\}item Optimized frontend performance reducing page load time by 20\textbackslash\{\}\%.
\textbackslash\{\}item Implemented secure user authentication with JWT tokens ensuring data privacy.
\textbackslash\{\}item Integrated SQL Server for robust data management and reporting.
\end{itemize}

\textbf{Inventory Management System} --- \textit{Group Capstone Project, Seneca Polytechnic}

\vspace{1pt}

Developed inventory system using ASP.NET MVC and SQL Server, improving stock tracking accuracy.

\begin{itemize}
\textbackslash\{\}item Automated stock update processes reducing manual errors by 35\textbackslash\{\}\%.
\textbackslash\{\}item Created interactive dashboards for real-time inventory monitoring.
\textbackslash\{\}item Improved database query efficiency enhancing report generation speed.
\textbackslash\{\}item Collaborated with stakeholders to adapt features per evolving business requirements.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}