% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[margin=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[1pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with 3+ years’ expertise in full-stack development and delivering scalable web applications. Skilled in JavaScript, React, Node.js, and Python with a strong focus on clean code and agile methodologies. Proven ability to optimize performance, collaborate cross-functionally, and contribute to product innovation aligned with business goals.

\vspace{3pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, TypeScript, Java, SQL, HTML/CSS, Bash

\textbf{Frameworks \& Libraries:} React, Node.js, Express.js, Django, Bootstrap, jQuery

\textbf{Database \& Data Management:} MySQL, PostgreSQL, MongoDB, DynamoDB

\textbf{Cloud \& DevOps:} AWS (EC2, S3, Lambda), Docker, Kubernetes, CI/CD, GitLab, GitHub Actions

\textbf{Software Development Practices:} Agile methodology, Scrum, Test Driven Development, pair programming, SDLC, debugging

\textbf{Computer Science Fundamentals:} Object Oriented Programming, Data Structures, Algorithms, Design Patterns

\textbf{Systems \& Networking:} RESTful APIs, microservices architecture, Unix/Linux environments, security best practices

\textbf{Soft Skills:} Team collaboration, mentoring, problem solving, communication, continuous learning

\vspace{6pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Full Stack Developer – KILATECH (Pvt) Ltd, Sri Lanka (Apr 2020 – Dec 2022) -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{1pt}

Worked as a full stack developer, primarily developing Shopify applications and managing custom web application projects from development through deployment, RESTful APIs, cloud services, CI/CD pipelines, security best practices, and comprehensive testing.

\begin{itemize}
\item Developed scalable full stack web and Shopify apps leveraging JavaScript, React, and Node.js to enhance e-commerce platforms.
\item Implemented RESTful APIs, integrated payment systems, and optimized database queries for performance and reliability.
\item Deployed and maintained cloud based applications using AWS, Docker, and CI/CD pipelines ensuring 99\% uptime.
\item Collaborated in Agile teams through pair programming and code reviews, contributing to continuous improvement culture.
\item Applied TDD and secure coding standards throughout the SDLC, improving maintainability and reducing defects.
\end{itemize}

\textbf{Full Stack Developer – KILATECH (Pvt) Ltd, Sri Lanka (Apr 2020 – Dec 2022) -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{1pt}

Supported the development of enterprise applications by contributing to both frontend and backend tasks across multiple projects.

\begin{itemize}
\item Assisted in the development of enterprise level web and mobile applications, contributing across both frontend and backend.
\item Participated in the design and implementation of a Proposal Management System and Mailroom Tracking System.
\item Collaborated with cross functional teams to gather requirements, perform testing, and ensure successful deployments.
\item Gained experience in full stack development, software testing, and secure coding within a collaborative Agile environment.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{E-Commerce Web Application --- \textit{Personal Project}

\vspace{1pt}

Built a scalable e-commerce platform with React front-end and Node.js back-end.

\begin{itemize}
\textbackslash\{\}item Developed user-friendly UI components with React for seamless shopping experiences.
\textbackslash\{\}item Implemented RESTful APIs for product and order management with Node.js.
\textbackslash\{\}item Optimized database queries in MongoDB, reducing load time by 40\textbackslash\{\}\%.
\textbackslash\{\}item Deployed application on AWS using Docker containers ensuring high availability.
\end{itemize}

\textbf{Real-Time Chat Application} --- \textit{Group Capstone Project, Seneca Polytechnic}

\vspace{1pt}

Designed and deployed a real-time chat app leveraging WebSocket and Node.js.

\begin{itemize}
\textbackslash\{\}item Created interactive chat UI with React for real-time messaging capabilities.
\textbackslash\{\}item Built scalable server using Node.js and WebSocket for instant data exchange.
\textbackslash\{\}item Integrated MongoDB for message storage with optimized query performance.
\textbackslash\{\}item Implemented user authentication and secure data transmission protocols.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}