% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Developer with extensive backend and DevOps expertise in building scalable applications and automated CI/CD pipelines. Proficient in Python, JavaScript, and cloud platforms including AWS and GCP with hands-on experience implementing secure delivery workflows using GitHub Actions, Docker, and Kubernetes. Skilled in integrating security checks, quality automation, and Infrastructure as Code to support governed application delivery and cross-functional collaboration.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, PHP, SQL, Bash, PowerShell

\textbf{Backend \& API Development:} Node.js, Django, Flask, REST API, GraphQL, Microservices

\textbf{Cloud Platforms \& Infrastructure:} AWS, GCP, AWS Lambda, AWS EC2, AWS S3, CloudFormation

\textbf{DevOps \& CI/CD:} GitHub Actions, Jenkins, Docker, Kubernetes, Terraform, GitLab CI/CD

\textbf{Database \& Data Systems:} PostgreSQL, MySQL, MongoDB, Redis, DynamoDB, ETL Pipelines

\textbf{Security \& Compliance:} OAuth, JWT, API Security, OWASP, IAM, Encryption

\textbf{Development Practices:} Agile, Scrum, Code Reviews, Unit Testing, TDD, Technical Documentation

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Problem Solving, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js to enhance e-commerce functionality.
\item Built and maintained CI/CD pipelines using GitHub Actions and AWS ensuring consistent uptime and automated delivery workflows.
\item Implemented RESTful APIs, optimized database queries, and integrated secure authentication with OAuth and JWT standards.
\item Collaborated within Agile teams through code reviews, sprint planning, and cross-functional collaboration to ensure quality.
\item Integrated security checks and automated testing into deployment pipelines improving code reliability and reducing issues.
\item Led backend development for multiple applications while mentoring junior developers on DevOps and secure coding practices.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications with backend services and automated deployment environment configurations.
\item Contributed to design and implementation of scalable service scaffolding for management and tracking systems.
\item Worked closely with cross-functional teams to gather requirements, perform testing, and support deployment validation.
\item Gained hands-on experience in full stack development, CI/CD workflows, and secure coding within Agile environments.
\item Collaborated in project reviews to identify improvements in performance, scalability, and pipeline delivery practices.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Automated vulnerability scanning and patching to strengthen enterprise security and reduce manual intervention effort.
\vspace{-1pt}
\begin{itemize}
\item Developed automated CI/CD workflows using Python and Jenkins for vulnerability scanning and patch deployment pipelines.
\item Integrated Nessus API for real-time vulnerability reporting, compliance tracking, and risk prioritization dashboards.
\item Created alert systems and monitoring dashboards to track security compliance and remediation progress across environments.
\item Reduced manual intervention by 60\% and accelerated patch cycles through fully automated delivery and validation workflows.
\end{itemize}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with notes, videos, and quizzes using cloud infrastructure.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL to support online education at scale.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time progress monitoring dashboards.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent usage.
\item Deployed the platform on AWS with Docker containers, CDN caching, and SSL encryption ensuring reliable student access.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}