% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

DevOps-focused Software Engineer with 2+ years of experience building scalable applications and automating infrastructure using Python, JavaScript, and TypeScript. Proficient in Docker, Kubernetes, and CI/CD pipelines with GitHub Actions and Jenkins. Experienced in cloud technologies including AWS and GCP, with a strong engineering mindset and hands-on SDLC delivery. Collaborative team player skilled in Agile and Scrum methodologies, driving automation and developer efficiency in production environments.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, TypeScript, PHP, SQL, Bash

\textbf{Frameworks \& Libraries:} React, Django, Node.js, Flask, FastAPI, Express.js

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, Redis, DynamoDB

\textbf{Cloud \& DevOps:} AWS, GCP, Docker, Kubernetes, Jenkins, GitHub Actions

\textbf{DevOps \& Automation:} CI/CD Pipelines, Infrastructure as Code, Terraform, Ansible, Automation, Release Management

\textbf{Software Development Practices:} Agile, Scrum, SDLC, System Design, Microservices

\textbf{Computer Science Fundamentals:} Data Structures, Algorithms, Design Patterns, OOP

\textbf{Systems \& Networking:} Cloud Computing, Networking, Linux, Security, Monitoring

\textbf{Soft Skills:} Ownership, Communication, Analytical Thinking, Collaboration, Adaptability, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable applications using JavaScript, Python, and TypeScript with React and Node.js to enhance system functionality.
\item Built and maintained CI/CD pipelines using GitHub Actions and Jenkins ensuring consistent deployment and infrastructure reliability.
\item Deployed cloud applications on AWS and GCP using Docker and Kubernetes for high availability and automated scaling capabilities.
\item Collaborated within Agile and Scrum teams to deliver production-class features through code reviews and sprint planning sessions.
\item Applied design patterns and SDLC best practices to improve system performance, maintainability, and deployment automation.
\item Led backend development initiatives while mentoring team members on DevOps tooling and distributed application support.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in building enterprise applications across frontend and backend using Python, JavaScript, and various frameworks.
\item Contributed to system design and implementation of management platforms following Agile methodologies and SDLC processes.
\item Worked with cross-functional teams to gather requirements, perform testing, and support production deployment phases.
\item Gained hands-on experience in application development, DevOps tooling, and automation within collaborative Agile workflows.
\item Participated in project reviews to identify improvements in scalability, performance optimization, and code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Automated vulnerability scanning and patching workflows to strengthen enterprise security and reduce manual operational effort.
\vspace{-1pt}
\begin{itemize}
\item Developed automated DevOps workflows using Python and Jenkins for continuous vulnerability scanning and patch deployment cycles.
\item Integrated Nessus API for real-time vulnerability reporting, risk prioritization, and compliance tracking across environments.
\item Created monitoring dashboards and alert systems to track security compliance, remediation progress, and patching efficiency.
\item Reduced manual intervention by 60\% and accelerated patch cycles through full CI/CD pipeline automation and orchestration.
\end{itemize}

\textbf{Automated Cryptocurrency Trading Bot} -- \emph{Personal Project}

\vspace{-1pt}

Built a Python trading bot using Binance API and WebSocket to automate trade execution with risk control and live monitoring.
\vspace{-1pt}
\begin{itemize}
\item Developed a fully automated trading bot in Python using Binance API and WebSocket for real-time data streaming and execution.
\item Implemented dynamic trading strategies, stop-loss mechanisms, and order execution algorithms with automated risk management.
\item Integrated Pandas and NumPy for market analysis and backtesting to improve trading accuracy and decision-making processes.
\item Deployed using Docker on AWS EC2 for 24/7 uptime, reliability, and continuous monitoring with detailed operational logging.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}