% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Developer with proven expertise in building AI-powered web applications using React, Python, and modern cloud infrastructure. Experienced in developing scalable solutions with RESTful APIs, database optimization, and deploying production-ready systems on AWS. Adept at integrating OpenAI APIs, implementing secure authentication, and collaborating across cross-functional teams in Agile environments. Passionate about leveraging AI technologies to create innovative solutions that drive business transformation.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, SQL, HTML5, CSS3

\textbf{Frontend \& UI Frameworks:} React, Redux, Tailwind CSS, Bootstrap, Material UI, Next.js

\textbf{Backend \& Database:} Node.js, Django, Flask, FastAPI, PostgreSQL, Supabase

\textbf{Cloud \& DevOps:} AWS, Docker, Vercel, GitHub Actions, CI/CD, Serverless

\textbf{AI \& Automation:} OpenAI APIs, LLM Integration, Prompt Engineering, Workflow Automation, AI Agents

\textbf{Development Tools:} Git, GitHub, VS Code, Postman, REST API, GraphQL

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Problem Solving, Initiative, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Built full stack AI-powered web applications using React, JavaScript, Python, and Node.js to deliver innovative e-commerce solutions.
\item Developed and integrated RESTful APIs with secure authentication, optimized database queries, and payment systems for reliability.
\item Deployed scalable cloud applications on AWS using Docker and CI/CD pipelines ensuring consistent uptime and high performance.
\item Collaborated with cross-functional teams in Agile environments through code reviews and sprint planning to ship quality features.
\item Applied test-driven development and secure coding practices throughout SDLC improving maintainability and reducing production issues.
\item Mentored junior developers on coding best practices, API design, and deployment strategies while leading backend development efforts.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to developing enterprise web applications with React frontend and Python backend integrating modern frameworks and APIs.
\item Designed and implemented Proposal Management and Mailroom Tracking Systems collaborating with product and technical stakeholders.
\item Worked closely with cross-functional teams to gather requirements, conduct testing, and support seamless deployment to production.
\item Gained hands-on experience building full stack features, debugging applications, and following secure coding standards in Agile teams.
\item Participated in project reviews to identify performance improvements, troubleshoot issues, and enhance code quality and scalability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable full stack LMS with React and Python enabling real-time learning for over 6,000 students during the pandemic.
\vspace{-1pt}
\begin{itemize}
\item Developed full stack LMS using React, Node.js, and PostgreSQL supporting lesson uploads, quizzes, and performance tracking features.
\item Integrated real-time progress dashboards for teachers and students with secure authentication and role-based access control mechanisms.
\item Optimized database queries and implemented caching strategies to handle high concurrent usage with reliable performance and uptime.
\item Deployed on AWS with Docker, CDN caching, and SSL encryption ensuring scalable and secure access for thousands of concurrent users.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Created an AI-powered chat app using React and Node.js with text-to-speech and voice-to-text for inclusive accessibility.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application with React, Node.js, and WebSockets integrating accessibility-focused UI following WCAG standards.
\item Integrated AWS Polly and Azure AI APIs to enable text-to-speech and voice-to-text communication for users with reading challenges.
\item Tested application with assistive technologies ensuring compliance with accessibility guidelines and delivering inclusive user experience.
\item Deployed on AWS with Docker containers and serverless patterns ensuring low-latency, scalable real-time communication for all users.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}