% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with hands-on expertise in Python, JavaScript, and TypeScript, specializing in building scalable DevOps solutions and CI/CD automation. Proven experience with Docker, Kubernetes, GitHub Actions, Jenkins, and cloud platforms including AWS and GCP. Strong engineering mindset with production-class delivery across Agile and Scrum methodologies. Adept at system design, automation, and optimizing developer workflows in fast-paced enterprise environments.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, TypeScript, Bash, PowerShell, SQL

\textbf{DevOps \& CI/CD:} Docker, Kubernetes, GitHub Actions, Jenkins, GitLab CI/CD, Terraform

\textbf{Cloud Platforms:} AWS, Google Cloud Platform, Azure, AWS Lambda, AWS EC2, CloudFormation

\textbf{Frameworks \& Libraries:} React, Node.js, Django, Flask, FastAPI, Express.js

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, Redis, DynamoDB, SQLite

\textbf{Development Practices:} Agile, Scrum, SDLC, Microservices, REST API, System Design

\textbf{Systems \& Networking:} Linux, Nginx, Load Balancing, VPC, Monitoring, Security Best Practices

\textbf{Soft Skills:} Ownership, Communication, Analytical Thinking, Collaboration, Adaptability, Problem Solving

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using JavaScript, React, and Node.js enhancing system functionality and performance.
\item Built and maintained CI/CD pipelines using Docker, GitHub Actions, and AWS for automated deployments and consistent uptime.
\item Optimized RESTful APIs, integrated secure payment systems, and improved database performance through query optimization.
\item Collaborated in Agile Scrum teams on sprint planning, code reviews, and pair programming to deliver high-quality solutions.
\item Applied test-driven development and secure coding best practices across SDLC improving maintainability and reducing defects.
\item Mentored junior developers on DevOps automation, deployment strategies, and coding standards driving team efficiency.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in building enterprise web and mobile applications across frontend and backend using modern development frameworks.
\item Contributed to design and implementation of Proposal Management and Mailroom Tracking Systems with modular architecture.
\item Collaborated with cross-functional teams on requirements gathering, system testing, and deployment ensuring quality delivery.
\item Gained hands-on experience in full stack development, automation testing, and secure coding within Agile Scrum workflows.
\item Participated in project reviews identifying improvements in performance, scalability, and maintainability of codebases.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic }

\vspace{-1pt}

Automated vulnerability scanning and patching workflows using Python, Jenkins, and Nessus API to strengthen enterprise security.
\vspace{-1pt}
\begin{itemize}
\item Developed automated CI/CD workflows using Python and Jenkins for vulnerability scanning and patch deployment across systems.
\item Integrated Nessus API for real-time vulnerability reporting, risk prioritization, and compliance tracking across infrastructure.
\item Built dashboards and alert systems to monitor security compliance, remediation progress, and automated patching workflows.
\item Reduced manual intervention by 60\% and accelerated patch cycles through full automation improving enterprise security posture.
\end{itemize}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS using React, Node.js, and MySQL deployed on AWS to support 6K+ students with lessons and quizzes.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed full-stack LMS using React, Node.js, and MySQL supporting online education during the pandemic.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards for educators.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent usage.
\item Deployed on AWS with Docker, CDN caching, and SSL encryption ensuring reliable access for over 6,000 students globally.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}