% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with hands-on experience building AI-powered workflows, automation tools, and scalable full stack applications using TypeScript, Python, React, and Node.js. Proven track record developing internal tools, integrating APIs, and rapidly prototyping solutions that multiply team output. Skilled in cloud infrastructure, CI/CD automation, and LLM integration with a passion for tinkering and solving complex problems through resourceful experimentation.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} TypeScript, JavaScript, Python, SQL, HTML5, CSS3, Bash

\textbf{AI \& Automation:} LLM API, ChatGPT API, Prompt Engineering, n8n, Workflow Automation, AI Integration

\textbf{Frameworks \& Libraries:} React, Node.js, Express.js, Django, Flask, FastAPI

\textbf{Database \& APIs:} PostgreSQL, MongoDB, REST API, GraphQL, WebSockets

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, GitHub Actions, CI/CD, Serverless

\textbf{Development Practices:} Agile, Rapid Prototyping, System Design, Testing, Code Reviews

\textbf{Soft Skills:} Resourcefulness, Ownership, Adaptability, Collaboration, Continuous Learning, Communication

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using TypeScript, React, and Node.js to enhance e-commerce functionality.
\item Implemented RESTful APIs, optimized database queries, and integrated secure payment systems improving reliability and performance.
\item Deployed cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and fast iteration cycles.
\item Collaborated within Agile teams through code reviews, sprint planning, and rapid prototyping to deliver high-quality solutions.
\item Applied test-driven development and automation throughout SDLC reducing production issues and accelerating release velocity.
\item Led backend development while mentoring junior developers on best practices for API design, automation, and deployment workflows.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications across frontend and backend components using modern JavaScript frameworks.
\item Contributed to design and implementation of Proposal Management and Mailroom Tracking Systems with API integrations.
\item Worked with cross functional teams to gather requirements, perform testing, and support deployment phases in Agile workflows.
\item Gained hands-on experience in full stack development, automation tooling, and secure coding within fast-paced environments.
\item Collaborated in project reviews to identify improvements in performance, scalability, and code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Automated Cryptocurrency Trading Bot} -- \emph{Personal Project}

\vspace{-1pt}

Created a Python trading bot using Binance API and WebSocket to automate trade execution with risk control and live monitoring.
\vspace{-1pt}
\begin{itemize}
\item Developed a fully automated trading bot in Python using Binance API and WebSocket for real-time data streaming and execution.
\item Implemented dynamic trading strategies, stop-loss mechanisms, and order execution algorithms to optimize trade performance.
\item Integrated Pandas and NumPy for market analysis and backtesting to improve trading accuracy and decision-making logic.
\item Deployed using Docker on AWS EC2 for 24/7 uptime, reliability, and monitoring with detailed logging and alerting systems.
\end{itemize}

\textbf{Custom Business Web Solutions} -- \emph{Personal Project}

\vspace{-1pt}

Built POS, e-commerce sites, landing pages, and inventory systems with secure, responsive design, improving workflow efficiency.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed multiple custom web solutions using React, Next.js, and Express.js for diverse client business needs.
\item Implemented secure authentication, inventory tracking, and payment processing with Stripe API integration for seamless UX.
\item Collaborated with clients to gather requirements and translate business needs into scalable applications with rapid turnaround.
\item Optimized UI performance, responsiveness, and SEO across all client projects to enhance user engagement and conversion rates.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}