% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with expertise in Python, AI integration, and full stack development. Proven experience building scalable applications, implementing RESTful APIs, and automating workflows across cloud platforms. Skilled in prompt engineering, machine learning APIs, and collaborating with cross-functional teams in Agile environments. Strong communicator with a high ownership mindset, committed to delivering maintainable, data-driven solutions that solve real-world problems.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, SQL, Bash, HTML, CSS

\textbf{AI \& Machine Learning:} Prompt Engineering, LLM API, ChatGPT API, Machine Learning APIs, AI Integration

\textbf{Frameworks \& Libraries:} React, Django, Flask, FastAPI, Node.js

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, ETL Pipelines, Data Warehousing

\textbf{Cloud \& DevOps:} AWS, GCP, Docker, CI/CD, GitHub Actions

\textbf{API Development \& Integration:} REST API, GraphQL, WebSockets, API Gateway, OpenAPI

\textbf{Software Development Practices:} Agile, Scrum, Technical Documentation, System Design, Testing

\textbf{Soft Skills:} Collaboration, Communication, Ownership, Adaptability, Continuous Learning, Curiosity

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using Python, JavaScript, and React to enhance system functionality and performance.
\item Implemented and optimized RESTful APIs with secure authentication and data handling to improve reliability and system integrity.
\item Deployed and maintained cloud-based applications on AWS using Docker and CI/CD pipelines ensuring consistent uptime and availability.
\item Collaborated within Agile teams through code reviews, sprint planning, and cross-functional collaboration to deliver quality outcomes.
\item Applied test-driven development and documented architecture decisions throughout SDLC improving maintainability and reducing issues.
\item Led backend development for multiple applications while mentoring junior developers on best practices and secure coding standards.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level web applications across both frontend and backend components using modern frameworks.
\item Contributed to the design and implementation of scalable systems including Proposal Management and Mailroom Tracking platforms.
\item Worked closely with cross-functional teams to gather requirements, perform testing, and support deployment phases collaboratively.
\item Gained hands-on experience building APIs, working with structured data, and applying secure coding practices in Agile workflows.
\item Collaborated in project reviews to identify improvements in performance, scalability, and code maintainability across deliverables.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with notes, videos, quizzes, and real-time performance tracking dashboards.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL to support structured online education during the pandemic.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards for teachers and administrators.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent usage and reliability.
\item Deployed the platform on AWS with CDN caching and SSL encryption, ensuring reliable access and performance for over 6,000 students.
\end{itemize}

\textbf{Automated Cryptocurrency Trading Bot} -- \emph{Personal Project}

\vspace{-1pt}

Created a Python trading bot using Binance API and WebSocket to automate trade execution with risk control and live monitoring.
\vspace{-1pt}
\begin{itemize}
\item Developed a fully automated trading bot in Python using Binance API and WebSocket for real-time data streaming and trade execution.
\item Implemented dynamic trading strategies, stop-loss mechanisms, and order execution algorithms to manage risk and optimize performance.
\item Integrated Pandas and NumPy for market data analysis and backtesting to improve trading accuracy and validate strategy effectiveness.
\item Deployed using Docker on AWS EC2 for 24/7 uptime and reliability, with detailed logging for monitoring and performance evaluation.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}