% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with expertise in Python, AI/ML integration, and scalable cloud-based systems. Proven experience building intelligent solutions using LLM APIs, prompt engineering, and automation workflows. Skilled in designing full stack applications with Django, Flask, and FastAPI alongside AWS and GCP cloud platforms. Strong background in Agile methodologies, CI/CD pipelines, and cross-functional collaboration to deliver production-ready AI-driven applications.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, SQL, HTML5, CSS3, Bash

\textbf{AI \& Machine Learning:} LLM API, ChatGPT API, Prompt Engineering, AI Integration, Machine Learning APIs, Automation

\textbf{Frameworks \& Libraries:} Django, Flask, FastAPI, React, Node.js, Bootstrap

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQLite, Redis, DynamoDB

\textbf{Cloud \& DevOps:} AWS, Google Cloud Platform, Microsoft Azure, Docker, Kubernetes, CI/CD

\textbf{Development Practices:} Agile, Scrum, REST API, Microservices, TDD, Code Reviews

\textbf{Soft Skills:} Problem Solving, Communication, Collaboration, Adaptability, Continuous Learning, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using Python, React, and Node.js, integrating AI capabilities and automation workflows.
\item Built and deployed RESTful APIs with Django and FastAPI, optimizing performance and ensuring secure integration with external systems.
\item Deployed cloud-based solutions on AWS and GCP using Docker, Kubernetes, and CI/CD pipelines for high availability and reliability.
\item Collaborated in Agile teams through sprint planning, code reviews, and pair programming to deliver intelligent, production-ready solutions.
\item Applied test-driven development and secure coding practices throughout SDLC, improving maintainability and reducing production defects.
\item Led backend development for multiple applications while mentoring junior developers on best practices in AI integration and deployment.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web and mobile applications, contributing to both frontend and backend components using Python and JavaScript.
\item Contributed to design and implementation of scalable systems including Proposal Management and Mailroom Tracking solutions.
\item Worked closely with cross-functional teams to gather requirements, perform testing, and support deployment phases in Agile workflows.
\item Gained hands-on experience in full stack development, automation, API integration, and secure coding practices.
\item Collaborated in project reviews to identify improvements in performance, scalability, and maintainability of intelligent applications.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to access lessons, quizzes, and tracking dashboards during the pandemic using Python and React.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack LMS using React, Node.js, and MySQL with integrated lesson uploads, quizzes, and real-time performance tracking.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent user sessions.
\item Deployed platform on AWS with CDN caching, SSL encryption, and autoscaling to ensure reliable access for over 6,000 students.
\item Integrated dashboards for educators to monitor progress, leveraging data visualization tools and optimized backend API responses.
\end{itemize}

\textbf{Automated Cryptocurrency Trading Bot} -- \emph{Personal Project}

\vspace{-1pt}

Created a Python trading bot using Binance API and WebSocket to automate execution with risk control and live monitoring capabilities.
\vspace{-1pt}
\begin{itemize}
\item Developed automated trading bot in Python using Binance API and WebSocket for real-time data streaming and intelligent order execution.
\item Implemented dynamic trading strategies, stop-loss mechanisms, and risk management algorithms with automated decision-making logic.
\item Integrated Pandas and NumPy for market analysis and backtesting to improve trading accuracy and optimize strategy performance.
\item Deployed using Docker on AWS EC2 for 24/7 uptime, reliability, and monitoring with detailed logging and alert systems.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}