% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with proven expertise in full stack development, cloud infrastructure, and secure application design. Skilled in Python, JavaScript, React, Node.js, and AWS with hands-on experience in Agile environments, cross-functional collaboration, and delivering scalable enterprise solutions. Strong analytical mindset with demonstrated ability in requirements analysis, system design, risk management, and operational workflows. Proficient in Microsoft Office, Jira, and reporting dashboards, committed to driving initiatives aligned with security, compliance, and governance standards.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, SQL, Bash, PowerShell, PHP

\textbf{Frameworks \& Libraries:} React, Django, Node.js, Bootstrap, Flask

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQL Server, pandas

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, CI/CD, GitHub Actions

\textbf{Security \& Compliance:} OWASP, Threat Intelligence, Incident Response, IAM, Risk Assessments, Vulnerability Management

\textbf{Tools \& Reporting:} Jira, Microsoft Office, Power BI, Excel, Confluence

\textbf{Soft Skills:} Communication, Collaboration, Analytical Thinking, Ownership, Adaptability, Mentorship

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using JavaScript, React, and Node.js aligned with enterprise security standards.
\item Implemented RESTful APIs, optimized SQL queries, and integrated secure authentication improving reliability and compliance.
\item Deployed cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring uptime and adherence to operational SLAs.
\item Collaborated in Agile teams through code reviews, sprint planning, and documentation supporting cross-functional coordination.
\item Applied secure coding standards and testing throughout SDLC reducing production issues and ensuring governance alignment.
\item Led backend development initiatives while mentoring junior developers fostering knowledge transfer and team capability growth.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level applications across frontend and backend components supporting business operations.
\item Contributed to design and implementation of the Proposal Management and Mailroom Tracking Systems aligned with requirements.
\item Worked closely with cross-functional teams to gather requirements, perform testing, and support deployment ensuring quality.
\item Gained hands-on experience in full stack development, software testing, and secure coding within Agile workflows and standards.
\item Collaborated in project reviews identifying improvements in performance, scalability, and operational efficiency across initiatives.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to access notes, videos, and quizzes with performance tracking and secure authentication.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed full-stack LMS using React, Node.js, and MySQL to support online education with scalable architecture.
\item Integrated modules for lesson uploads, quizzes, and real-time performance dashboards enabling teachers to track student progress.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent usage and compliance.
\item Deployed platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 students with minimal downtime.
\end{itemize}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Automated vulnerability scanning and patching to strengthen enterprise security and reduce manual effort through CI/CD workflows.
\vspace{-1pt}
\begin{itemize}
\item Developed automated workflows using Python and Jenkins for vulnerability scanning and patch deployment reducing remediation time.
\item Integrated Nessus API for real-time vulnerability reporting and risk prioritization aligned with enterprise security frameworks.
\item Created dashboards and alert systems to track security compliance and remediation progress ensuring transparency and accountability.
\item Reduced manual intervention by 60\% and accelerated patch cycles through full CI/CD automation improving operational efficiency.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}