% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Developer with hands-on experience in building scalable web applications, RESTful APIs, and cloud-based solutions using Python, JavaScript, SQL, and modern frameworks. Proficient in data analytics, business intelligence tools, and automation with strong SQL capabilities for deriving actionable insights. Proven track record in optimizing workflows, designing dashboards, and collaborating with cross-functional teams in Agile environments to deliver measurable business impact and operational excellence.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming \& Scripting:} Python, SQL, JavaScript, PHP, Bash, PowerShell

\textbf{Data \& Business Intelligence:} SQL, Power BI, Data Visualization, ETL Pipelines, BigQuery, pandas

\textbf{Database Management:} PostgreSQL, MySQL, MongoDB, SQL Server, Database Design

\textbf{Frameworks \& Tools:} React, Django, Node.js, Flask, FastAPI, REST API

\textbf{Cloud \& DevOps:} AWS, GCP, Docker, Kubernetes, CI/CD, GitHub Actions

\textbf{Development Practices:} Agile, Scrum, SDLC, Testing, Technical Documentation, Code Reviews

\textbf{Analytics \& Reporting:} Data Analysis, MIS Reporting, Automation, Chart.js, Performance Optimization

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Ownership, Innovation

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using JavaScript, React, Node.js, and SQL enhancing functionality and user experience.
\item Designed RESTful APIs, optimized SQL queries, and integrated secure payment systems improving system reliability and performance.
\item Deployed cloud-based solutions using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and operational excellence.
\item Collaborated in Agile teams through code reviews, sprint planning, and pair programming delivering high-quality, impactful results.
\item Applied test-driven development and secure coding standards throughout SDLC reducing production issues and enhancing maintainability.
\item Led backend development for multiple applications while mentoring junior developers on coding best practices and deployment strategies.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web and mobile applications across frontend and backend components using modern frameworks.
\item Contributed to design and implementation of Proposal Management and Mailroom Tracking Systems improving operational workflows.
\item Worked with cross-functional teams gathering requirements, performing testing, and supporting deployment phases in Agile sprints.
\item Gained hands-on experience in full stack development, software testing, and secure coding practices within collaborative environments.
\item Participated in project reviews identifying improvements in performance, scalability, and code quality to drive business impact.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built scalable LMS enabling 6K+ students to learn with notes, videos, and interactive quizzes using cloud-based infrastructure.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack LMS using React, Node.js, and MySQL enabling online education for over 6,000 students during the pandemic.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards providing actionable insights.
\item Implemented secure authentication, role-based access, and optimized SQL queries supporting high concurrent usage and scalability.
\item Deployed on AWS with CDN caching and SSL encryption ensuring reliable access, high availability, and data security at scale.
\end{itemize}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic }

\vspace{-1pt}

Automated vulnerability scanning and patching workflows to strengthen enterprise security reducing manual effort by 60 percent.
\vspace{-1pt}
\begin{itemize}
\item Developed automated workflows using Python and Jenkins for vulnerability scanning and patch deployment reducing manual intervention.
\item Integrated Nessus API for real-time vulnerability reporting, risk prioritization, and actionable insights for security compliance.
\item Created dashboards and alert systems tracking security metrics, remediation progress, and operational risks in real time effectively.
\item Accelerated patch cycles through CI/CD automation achieving 60\% reduction in manual effort and improving enterprise security posture.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}