% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with hands-on experience in application support, troubleshooting, and full stack development using JavaScript, TypeScript, React, Node.js, PHP, and MySQL. Skilled in debugging production systems, maintaining REST APIs, and supporting cloud infrastructure on AWS and Azure. Proficient in Agile workflows, Jira ticketing, Docker, and CI/CD pipelines with a strong foundation in problem-solving and technical documentation.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, PHP, Python, SQL, HTML5, CSS3, Bash

\textbf{Frameworks \& Libraries:} React, Node.js, NestJS, Next.js, Django, Bootstrap

\textbf{Database \& Data Management:} MySQL, PostgreSQL, MongoDB, REST API, Prisma

\textbf{Cloud \& DevOps:} Microsoft Azure, AWS, Docker, GitHub Actions, CI/CD, Monitoring

\textbf{Development Practices:} Agile, Scrum, Debugging, Unit Testing, Code Reviews, Technical Documentation

\textbf{Security \& Integration:} OAuth, JWT, API Security, Microservices, Legacy System Integration

\textbf{Soft Skills:} Problem Solving, Communication, Collaboration, Adaptability, Analytical Thinking, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed and maintained full stack web applications using JavaScript, React, and Node.js to enhance platform functionality.
\item Debugged production issues, performed root-cause analysis using logs and monitoring tools to ensure system reliability.
\item Implemented and maintained RESTful APIs, optimized SQL queries, and integrated secure authentication flows with OAuth and JWT.
\item Deployed and maintained cloud-based applications on AWS and Azure using Docker and CI/CD pipelines for consistent uptime.
\item Collaborated within Agile teams using Jira for ticketing, sprint planning, and code reviews to ensure quality deliverables.
\item Created and maintained technical documentation to support ongoing development, troubleshooting, and knowledge transfer.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in troubleshooting and resolving production issues across enterprise-level web and mobile applications.
\item Contributed to the development and maintenance of backend services and database integrations using Node.js and MySQL.
\item Collaborated with cross-functional teams to gather requirements, perform testing, and support deployment phases.
\item Gained hands-on experience in full stack development, debugging, and secure coding within Agile workflows.
\item Participated in code reviews and project retrospectives to improve system performance, scalability, and maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS using React, Node.js, and MySQL supporting 6K+ students with secure authentication and real-time tracking.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL to support online education during the pandemic.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time progress dashboards for teachers.
\item Implemented secure authentication, role-based access, and optimized database queries for high concurrent usage and reliability.
\item Deployed the platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive real-time chat app using React, Node.js, and Socket.io with text-to-speech and voice-to-text features.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and Socket.io with accessibility-focused UI design and responsive layout.
\item Integrated Azure Speech Services to enable text-to-speech and voice-to-text communication for low-vision users.
\item Followed WCAG accessibility standards and tested with assistive technologies to ensure inclusive and barrier-free usability.
\item Deployed on AWS using Docker containers for scalable, low-latency communication with monitoring and logging enabled.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}