% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Software Engineer with proven expertise in Angular, React, JavaScript, TypeScript, and responsive UI development. Experienced in building modular, testable web applications with RESTful APIs and modern frontend frameworks. Strong foundation in Agile methodologies, version control using Git, and cloud-based deployments on AWS. Demonstrated ability to troubleshoot, collaborate with cross-functional teams, and deliver high-quality solutions aligned with accessibility and testing best practices.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Frontend Development:} Angular, React, JavaScript, TypeScript, HTML5, CSS3

\textbf{Frameworks \& Libraries:} RxJS, NgRx, Redux, Bootstrap, Material UI, jQuery

\textbf{Testing \& Quality Assurance:} Karma, Jasmine, Unit Testing, TDD, Integration Testing, Postman

\textbf{Backend \& APIs:} Node.js, REST API, Express.js, Django, Flask, FastAPI

\textbf{Cloud \& DevOps:} AWS, Azure, Docker, CI/CD, Jenkins, GitHub Actions

\textbf{Tools \& Collaboration:} Git, GitHub, JIRA, Confluence, Visual Studio Code, Maven

\textbf{Security \& Best Practices:} OWASP, Web Accessibility, OAuth, JWT, API Security, TLS

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Problem Solving, Ownership, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed modular and testable web applications using JavaScript, React, and TypeScript with RESTful API integration.
\item Implemented responsive UI components and optimized frontend performance following modern development best practices.
\item Debugged and resolved application issues using browser dev tools ensuring seamless functionality and user experience.
\item Collaborated within Agile teams through code reviews, sprint planning, and version control using Git and GitHub.
\item Applied test-driven development methodologies utilizing unit and integration testing frameworks to maintain code quality.
\item Deployed cloud-based applications using AWS and CI/CD pipelines ensuring high availability and scalability.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications using frontend and backend technologies within Agile workflows.
\item Contributed to UI implementation and testing ensuring responsive design principles and cross-browser compatibility.
\item Worked closely with senior developers and cross-functional teams to gather requirements and resolve technical issues.
\item Gained hands-on experience in version control tools, debugging techniques, and secure coding practices.
\item Collaborated in project reviews to identify improvements in performance, scalability, and code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS with Angular-compatible features supporting 6K+ students with interactive lessons, quizzes, and dashboards.
\vspace{-1pt}
\begin{itemize}
\item Developed a full-stack LMS using React and Node.js with modular components ensuring reusability and testability.
\item Integrated RESTful APIs for lesson uploads, quizzes, and performance tracking with real-time progress monitoring.
\item Implemented secure authentication, role-based access control, and optimized database queries for concurrent users.
\item Deployed on AWS with CI/CD pipelines, SSL encryption, and CDN caching ensuring reliable access for 6,000+ students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive real-time chat app for low-vision users with accessibility features following WCAG standards.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and WebSockets with modular and responsive UI design.
\item Integrated AWS Polly and Azure Speech Services to enable text-to-speech and voice-to-text communication features.
\item Followed WCAG accessibility standards and tested with assistive technologies to ensure inclusive usability.
\item Deployed on AWS using Docker containers for scalable, low-latency communication with high availability.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}