% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Developer with proven experience building scalable web applications using JavaScript, React, Node.js, and backend technologies. Strong foundation in HTML, CSS, SASS, and responsive UI development with a passion for learning modern frameworks and accessibility standards. Experienced in Agile workflows, cloud deployment, and collaborative development. Eager to grow technical expertise in AEM, component-based architecture, and enterprise content management while contributing to inclusive, high-performance digital experiences.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, HTML5, CSS3, SASS, Python, SQL, Bash

\textbf{Frontend Frameworks \& Libraries:} React, Redux, Bootstrap, jQuery, Material UI

\textbf{Backend \& API Development:} Node.js, Express.js, REST API, Django, Flask

\textbf{Database \& Data Management:} MySQL, PostgreSQL, MongoDB, SQLite

\textbf{Cloud \& DevOps:} AWS, Docker, CI/CD, GitHub Actions, Git

\textbf{Development Practices:} Agile, Scrum, Code Reviews, SDLC, Testing

\textbf{Accessibility \& Design:} WCAG Standards, UI/UX Principles, Responsive Design

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js to enhance user experiences and functionality.
\item Implemented RESTful APIs, optimized SQL queries, and integrated secure systems to improve reliability and backend performance.
\item Deployed cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring uptime, stability, and efficient delivery.
\item Collaborated in Agile teams through code reviews, sprint planning, and pair programming to consistently deliver quality solutions.
\item Applied test-driven development and secure coding standards throughout SDLC improving maintainability and reducing production issues.
\item Led backend development for multiple applications while mentoring team members on best coding practices and deployment workflows.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level web and mobile applications across both frontend and backend components using modern tools.
\item Contributed to design and implementation of business applications collaborating closely with cross functional development teams.
\item Worked with teams to gather requirements, perform comprehensive testing, and support smooth deployment phases for key projects.
\item Gained hands-on experience in full stack development, software testing, and secure coding within Agile workflows and sprint cycles.
\item Participated in project reviews to identify improvements in performance, scalability, and code maintainability across applications.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL to support online education during the pandemic.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time progress dashboards for teachers.
\item Implemented secure authentication, role-based access, and optimized database queries for high concurrent usage and stability.
\item Deployed the platform on AWS with CDN caching and SSL encryption, ensuring reliable access for over 6,000 students daily.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users and individuals with reading challenges, integrating accessibility features.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and Socket.io with accessibility-focused UI design and WCAG compliance.
\item Integrated AWS Polly and Azure Speech Services to enable text-to-speech and voice-to-text communication for inclusive usability.
\item Followed WCAG accessibility standards and tested with assistive technologies to ensure an inclusive experience for diverse users.
\item Deployed on AWS App Runner with Docker containers for scalable, low-latency communication and consistent uptime under high load.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}