% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with expertise in building scalable full stack web applications using JavaScript, React, Next.js, Python, and Django. Experienced in developing customer-facing solutions, collaborating with cross-functional teams, and delivering high-quality products using Agile methodologies. Strong technical foundation in PostgreSQL, AWS, and CI/CD pipelines with a proven ability to translate requirements into intuitive user experiences and data-driven product decisions.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, SQL, HTML5, CSS3

\textbf{Frontend Development:} React, Redux, Next.js, Bootstrap, Material UI, Responsive Design

\textbf{Backend Development:} Django, Node.js, PostgreSQL, REST API, GraphQL, MySQL

\textbf{Cloud \& DevOps:} AWS, Docker, CI/CD, GitHub Actions, Infrastructure as Code

\textbf{Product \& Development Practices:} Agile, Scrum, System Design, A/B Testing, Technical Documentation

\textbf{Soft Skills:} Communication, Collaboration, Ownership, Adaptability, Attention to Detail, Customer Focus

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js collaborating with cross-functional teams.
\item Implemented RESTful APIs and optimized PostgreSQL queries improving system performance and delivering user-centric features.
\item Deployed cloud applications using AWS and CI/CD pipelines ensuring consistent uptime and high-quality product releases.
\item Engaged with stakeholders to gather requirements and translate business needs into technical specifications and features.
\item Applied data-driven decisions through A/B testing and analytics improving user engagement and conversion metrics.
\item Conducted code reviews and mentored developers on best practices fostering quality and ownership across the team.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to developing enterprise web applications across frontend and backend collaborating with product and design teams.
\item Assisted in building the Proposal Management System translating user requirements into technical implementations.
\item Worked closely with cross-functional teams to gather feedback, perform testing, and support deployment phases.
\item Gained experience in Agile workflows participating in sprint planning, stand-ups, and retrospectives to ensure delivery.
\item Supported performance analysis and scalability improvements identifying opportunities to enhance product quality.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with interactive quizzes, videos, and real-time progress tracking.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and PostgreSQL supporting online education for students.
\item Integrated modules for quizzes and performance tracking with dashboards providing real-time insights for educators.
\item Implemented secure authentication and role-based access optimizing database queries for high concurrent usage.
\item Deployed the platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 users.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive real-time chat app integrating text-to-speech and voice-to-text for accessibility-focused users.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and WebSockets with accessibility-first UI design principles.
\item Integrated AWS Polly and speech services enabling text-to-speech and voice-to-text communication for low-vision users.
\item Followed WCAG accessibility standards and tested with assistive technologies ensuring inclusive and usable experiences.
\item Deployed on AWS using Docker containers for scalable, low-latency communication with high availability and reliability.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}