% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with strong full stack development experience using React, Node.js, and Python. Skilled in building scalable cloud-based applications on AWS with Docker and CI/CD pipelines. Proven ability to develop RESTful APIs, optimize databases including PostgreSQL and DynamoDB, and deliver high-quality software in Agile environments. Eager to contribute to innovative AI-powered solutions while continuously learning modern technologies and best practices.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, SQL, HTML5, CSS3

\textbf{Frontend Development:} React, Redux, Bootstrap, Material UI, React Query

\textbf{Backend Development:} Node.js, Express.js, Django, Flask, FastAPI, REST API

\textbf{Database \& Caching:} PostgreSQL, MySQL, MongoDB, DynamoDB, Redis

\textbf{Cloud \& DevOps:} AWS, Docker, CI/CD, GitHub Actions, Kubernetes

\textbf{Development Practices:} Agile, Scrum, Unit Testing, Code Reviews, Technical Documentation

\textbf{Soft Skills:} Communication, Team Collaboration, Problem Solving, Adaptability, Continuous Learning, Curiosity

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using React, Node.js, and JavaScript to enhance e-commerce functionality and performance.
\item Implemented RESTful APIs with secure authentication, optimized SQL queries, and integrated payment systems improving reliability.
\item Deployed and maintained cloud applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and availability.
\item Collaborated within Agile teams through code reviews, sprint planning, and pair programming to deliver high-quality software.
\item Applied test-driven development and secure coding standards throughout SDLC reducing production issues and improving maintainability.
\item Led backend development for multiple applications while mentoring junior developers on coding best practices and deployment strategies.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing web and mobile applications across frontend and backend components using modern technology stacks.
\item Contributed to design and implementation of Proposal Management and Mailroom Tracking Systems with cross functional teams.
\item Worked closely with teams to gather requirements, perform testing, and support deployment phases in Agile workflows.
\item Gained hands-on experience in full stack development, software testing, and secure coding practices within production environments.
\item Collaborated in project reviews to identify improvements in performance, scalability, and code maintainability across applications.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with notes, videos, and interactive quizzes using React and Node.js on AWS.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL to support online education for thousands of students.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards for teachers and administrators.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent user access.
\item Deployed the platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 active students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive real-time chat app for low-vision users integrating accessibility features with React, Node.js, and AWS.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and WebSockets with accessibility-focused UI design and user testing.
\item Integrated AWS services to enable text-to-speech and voice-to-text communication for users with reading challenges.
\item Followed WCAG accessibility standards and tested with assistive technologies to ensure inclusive usability and compliance.
\item Deployed on AWS using Docker containers for scalable, low-latency communication with continuous integration and delivery.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}