% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with strong foundations in data engineering, ETL pipeline development, and cloud-based solutions. Proven experience building scalable systems using Python, SQL, and modern cloud platforms including AWS and GCP. Skilled in designing robust data workflows, implementing CI/CD automation, and collaborating across cross-functional teams to deliver reliable, secure, and performance-optimized solutions that drive business outcomes.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming \& Scripting:} Python, SQL, Bash, PowerShell, JavaScript

\textbf{Data Engineering \& ETL:} ETL Pipelines, Data Warehousing, pandas, SQL Server, PostgreSQL, MySQL

\textbf{Cloud Platforms \& Services:} AWS, GCP, Microsoft Azure, AWS Lambda, AWS S3, BigQuery

\textbf{DevOps \& Orchestration:} Docker, Kubernetes, CI/CD, GitHub Actions, GitLab CI/CD, Jenkins

\textbf{Data Visualization \& BI Tools:} Power BI, Data Visualization, Chart.js, Google Data Studio

\textbf{Development Practices:} Agile, Scrum, Git, Technical Documentation, Code Reviews, Version Control

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Continuous Learning, Analytical Thinking

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using Python, JavaScript, and SQL, optimizing database queries and API performance.
\item Built and maintained automated ETL pipelines using Python and cloud services to support analytics and reporting requirements.
\item Deployed cloud-based solutions on AWS with Docker and CI/CD pipelines, ensuring high availability and consistent system uptime.
\item Collaborated within Agile teams through code reviews, sprint planning, and cross-functional communication for quality delivery.
\item Applied best practices in data validation, security, and governance throughout SDLC to improve reliability and maintainability.
\item Mentored junior developers on coding standards, deployment automation, and troubleshooting data-related production issues.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise applications with focus on backend data integration and frontend user interface components.
\item Contributed to design and implementation of data-driven systems including tracking and management workflow applications.
\item Worked closely with cross-functional teams to gather requirements, perform testing, and support deployment phases effectively.
\item Gained hands-on experience in full stack development, software testing, and secure coding practices within Agile workflows.
\item Collaborated in project reviews to identify improvements in performance, scalability, data quality, and code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS with data-driven dashboards enabling 6K+ students to learn with notes, videos, and interactive quizzes.
\vspace{-1pt}
\begin{itemize}
\item Designed full-stack LMS using Python, React, and MySQL with optimized database schemas for high concurrent user performance.
\item Integrated data modules for lesson tracking, quiz analytics, and real-time performance dashboards for instructors and learners.
\item Implemented secure authentication, role-based access controls, and optimized SQL queries to support thousands of active users.
\item Deployed platform on AWS with CDN caching, SSL encryption, and monitoring to ensure reliable access for over 6,000 students.
\end{itemize}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Automated vulnerability scanning and patching workflows to strengthen enterprise security and reduce manual operational effort.
\vspace{-1pt}
\begin{itemize}
\item Developed automated workflows using Python and Jenkins for vulnerability scanning, patch deployment, and compliance tracking.
\item Integrated Nessus API for real-time vulnerability reporting, data analysis, and risk prioritization across enterprise systems.
\item Created monitoring dashboards and alert systems to track security compliance metrics and remediation progress continuously.
\item Reduced manual intervention by 60\% and accelerated patch cycles through full CI/CD automation and data-driven decision-making.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}