% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Software Engineer with hands-on experience in developing scalable full stack web applications using JavaScript, React, and Node.js. Skilled in Angular, TypeScript, HTML5, CSS3, and consuming RESTful APIs to build responsive, accessible, and modular frontend solutions. Proven ability to collaborate in Agile environments, troubleshoot complex applications, and apply test-driven development practices. Experienced in cloud deployment with AWS, CI/CD pipelines, and version control using Git and GitHub. Committed to writing clean, reusable code while continuously learning new technologies and frameworks.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Frontend Development:} JavaScript, TypeScript, Angular, React, HTML5, CSS3

\textbf{Frameworks \& Libraries:} Node.js, Bootstrap, Material UI, Redux, React Query, RxJS

\textbf{Backend \& API Development:} RESTful APIs, Express.js, Django, Flask, GraphQL, WebSockets

\textbf{Database \& Data Management:} MySQL, PostgreSQL, MongoDB, SQLite, Firebase, DynamoDB

\textbf{Cloud \& DevOps:} AWS, Azure, Docker, CI/CD, Jenkins, GitHub Actions

\textbf{Testing \& Version Control:} Unit Testing, Karma, Jasmine, Git, GitHub, TDD

\textbf{Software Development Practices:} Agile, Scrum, Code Reviews, SDLC, Design Patterns, OOP

\textbf{Security \& Accessibility:} WCAG Standards, OWASP, OAuth, JWT, API Security, Encryption

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Problem Solving, Critical Thinking, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js to deliver responsive and accessible user experiences.
\item Built and consumed RESTful APIs, optimized SQL queries, and integrated secure payment systems to enhance system reliability and performance.
\item Deployed and maintained cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring high availability and consistent uptime.
\item Collaborated within Agile teams through code reviews, sprint planning, and pair programming to ensure timely delivery of high-quality features.
\item Applied test-driven development and secure coding standards throughout SDLC improving code maintainability and reducing production issues.
\item Led backend development for multiple applications while mentoring junior developers on best practices for coding, testing, and deployment.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level web applications across both frontend and backend using modern JavaScript frameworks and libraries.
\item Contributed to the design and implementation of the Proposal Management System and Mailroom Tracking System with clean, modular code.
\item Worked closely with cross functional teams to gather requirements, perform thorough testing, and support deployment phases successfully.
\item Gained hands-on experience in full stack development, troubleshooting, and secure coding within Agile workflows and Scrum methodologies.
\item Collaborated in project reviews to identify improvements in performance, scalability, and code maintainability across multiple applications.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes using modern web tech.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full-stack LMS using React, Node.js, and MySQL with responsive design to support online education during the pandemic.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time progress dashboards using RESTful APIs and WebSockets.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent usage and data integrity.
\item Deployed the platform on AWS with CDN caching, SSL encryption, and CI/CD pipelines ensuring reliable access for over 6,000 active students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users with WCAG accessibility standards, text-to-speech, and voice-to-text integration.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and Socket.io with accessibility-focused UI design adhering to WCAG 2.1 guidelines.
\item Integrated AWS Polly and Azure Speech Services to enable text-to-speech and voice-to-text communication for users with reading challenges.
\item Followed WCAG accessibility standards and tested with assistive technologies including screen readers to ensure inclusive usability for all users.
\item Deployed on AWS App Runner with Docker containers and CI/CD pipelines for scalable, low-latency communication with high availability uptime.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}