% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Engineer with proven experience in designing, developing, and deploying scalable web applications across the entire software stack. Proficient in React, Node.js, Python, and modern frameworks including Bootstrap, Material UI, and Redux. Strong backend expertise with Django, Flask, and RESTful APIs, combined with database management experience in MySQL, PostgreSQL, and MongoDB. Skilled in cloud platforms (AWS, GCP), CI/CD pipelines, Docker, and implementing OWASP security best practices.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Frontend Technologies:} React, Redux, HTML5, CSS3, JavaScript, Bootstrap, Material UI, Vite

\textbf{Backend Technologies:} Node.js, Python, Django, Flask, FastAPI, Express.js, REST API

\textbf{Database Systems:} MySQL, PostgreSQL, MongoDB, SQLite, Firebase, Database Design

\textbf{Cloud \& DevOps:} AWS, GCP, Azure, Docker, CI/CD, Git, GitHub, Terraform

\textbf{Security \& Best Practices:} OWASP, OAuth, JWT, API Security, Encryption, TLS, IAM

\textbf{Development Practices:} Agile, Scrum, Design Patterns, Unit Testing, Code Reviews, Documentation

\textbf{Collaboration Tools:} Jira, Microsoft Teams, Git, Slack, VS Code, Technical Documentation

\textbf{Soft Skills:} Communication, Team Collaboration, Problem Solving, Adaptability, Ownership, Time Management

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using React, Node.js, and Material UI to enhance functionality and user experience.
\item Designed and implemented RESTful APIs with secure authentication, optimizing database queries in MySQL and PostgreSQL.
\item Deployed cloud-based applications on AWS leveraging Docker containers and CI/CD pipelines for consistent uptime and availability.
\item Collaborated within Agile teams through code reviews, sprint planning, and documentation to ensure high-quality deliverables.
\item Applied OWASP security standards and best practices throughout the SDLC improving maintainability and reducing production issues.
\item Led backend development for multiple applications while mentoring junior developers on coding standards and deployment practices.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Participated in full stack development of enterprise web applications using React, Python, and Bootstrap across frontend and backend.
\item Contributed to design and implementation of scalable systems integrating third-party APIs and database management solutions.
\item Collaborated with cross-functional teams and product owners to gather requirements, perform testing, and support deployment phases.
\item Gained hands-on experience in debugging, troubleshooting, and implementing testable code within Agile workflows and sprints.
\item Participated in code reviews to ensure adherence to coding standards, performance optimization, and scalability improvements.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes online.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, MySQL, and Bootstrap to support online education during the pandemic.
\item Integrated modules for lesson uploads, quizzes, and real-time progress tracking dashboards optimized for maximum responsiveness.
\item Implemented secure authentication, role-based access control, and optimized SQL queries for high concurrent usage and scalability.
\item Deployed the platform on AWS with CDN caching and TLS encryption, ensuring reliable and secure access for over 6,000 students.
\end{itemize}

\textbf{PROSPR " Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive real-time chat app for low-vision users integrating accessibility features and assistive technologies.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, WebSockets, and Material UI with accessibility-focused UI design principles.
\item Integrated AWS cloud services and third-party APIs to enable text-to-speech and voice-to-text communication for enhanced accessibility.
\item Followed WCAG standards and tested with assistive technologies ensuring inclusive usability and adherence to design best practices.
\item Deployed on AWS using Docker containers for scalable, low-latency communication with monitoring and logging for reliability.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}