% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Full Stack Web Developer with strong foundation in JavaScript, React, and Node.js, transitioning into frontend-focused Angular development. Experienced in building scalable web applications, implementing RESTful APIs, and working within Agile teams. Skilled in HTML5, CSS3, responsive design, and version control using Git. Adept at collaborating with cross-functional teams, following guidance from senior developers, and contributing to code reviews. Committed to writing clean, maintainable code while continuously learning modern frontend technologies.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Frontend Technologies:} HTML5, CSS3, JavaScript, TypeScript, React, Angular

\textbf{UI Frameworks \& Design:} Bootstrap, Material UI, SASS, Responsive Design, UI/UX

\textbf{Backend \& APIs:} Node.js, Express.js, REST API, Python, Django

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQL

\textbf{DevOps \& Tools:} Git, GitHub, CI/CD, Docker, AWS

\textbf{Testing \& Development Practices:} Unit Testing, Debugging, Agile, Scrum, Code Reviews

\textbf{Soft Skills:} Communication, Team Collaboration, Adaptability, Problem Solving, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js enhancing frontend functionality and user experience.
\item Implemented RESTful APIs and integrated secure systems while writing clean, modular, maintainable code following best practices.
\item Deployed and maintained cloud applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and smooth deployments.
\item Collaborated within Agile teams through code reviews, sprint planning, and cross-functional coordination to deliver high-quality solutions.
\item Applied responsive design principles and debugging techniques using browser dev tools to optimize performance and user interface.
\item Contributed to unit testing, troubleshooting, and defect triage throughout SDLC improving maintainability and reducing production issues.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications across frontend and backend components following guidance from senior developers.
\item Contributed to design and implementation of scalable systems while adhering to coding standards and version control best practices.
\item Worked closely with cross-functional teams including designers and product managers to gather requirements and support testing phases.
\item Gained hands-on experience in full stack development, debugging, and implementing responsive designs within Agile workflows.
\item Collaborated in project reviews to identify improvements in performance, code quality, and maintainability across multiple projects.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built scalable LMS enabling 6K+ students to learn with notes, videos, and interactive quizzes using modern web technologies.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed full-stack LMS using React, Node.js, and MySQL implementing modular, maintainable frontend components.
\item Integrated modules for lesson uploads, quizzes, and real-time progress dashboards following responsive design principles with Material UI.
\item Implemented secure authentication, role-based access, and optimized database queries ensuring optimal performance for concurrent users.
\item Deployed platform on AWS with CI/CD pipelines, SSL encryption, and version control ensuring reliable access for over 6,000 students.
\end{itemize}

\textbf{PROSPR " Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed inclusive chat app for low-vision users integrating accessibility features following WCAG guidelines and modern standards.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Node.js, and Socket.io implementing accessibility-focused UI design with WCAG compliance.
\item Integrated AWS services to enable text-to-speech and voice-to-text communication ensuring inclusive user experience and navigation.
\item Followed web accessibility standards and tested with assistive technologies collaborating with cross-functional team members throughout.
\item Deployed on AWS with Docker containers implementing responsive design and debugging using browser dev tools for optimal performance.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}