% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Backend Developer with strong expertise in Python, Django, Flask, and FastAPI for building scalable APIs and robust backend systems. Experienced in designing RESTful architectures, optimizing database performance with PostgreSQL and MySQL, and deploying cloud-based solutions on AWS and GCP using Docker and CI/CD pipelines. Proven ability to collaborate in Agile environments, deliver secure integrations, and enhance system reliability through test-driven development and performance optimization.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, PHP, SQL, Bash

\textbf{Backend Frameworks \& Libraries:} Django, Flask, FastAPI, Node.js, Express.js

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQLite, Redis

\textbf{Cloud \& DevOps:} AWS, GCP, Docker, Kubernetes, CI/CD, GitHub Actions

\textbf{APIs \& Integration:} REST API, GraphQL, WebSockets, Microservices, API Gateway

\textbf{Software Development Practices:} Agile, Scrum, TDD, Unit Testing, Code Reviews

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable backend APIs using Python, Django, and Flask integrated with React frontends to enhance application functionality.
\item Implemented RESTful and GraphQL APIs with optimized PostgreSQL queries and secure authentication to improve reliability and performance.
\item Deployed cloud-based backend systems using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and seamless scalability.
\item Collaborated within Agile teams through sprint planning, code reviews, and pair programming to ensure high-quality backend deliverables.
\item Applied test-driven development and secure coding standards throughout SDLC improving backend maintainability and reducing bugs.
\item Led backend architecture design for microservices while mentoring junior developers on best practices for API development and deployment.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise backend services and APIs to support web and mobile application components.
\item Contributed to the backend design and implementation of the Proposal Management and Mailroom Tracking Systems.
\item Worked closely with cross functional teams to gather backend requirements, perform integration testing, and support deployment phases.
\item Gained hands-on experience in backend development, database design, API testing, and secure coding within Agile workflows.
\item Collaborated in project reviews to identify improvements in backend performance, scalability, and database query optimization.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS backend using Python, Node.js, and MySQL enabling 6K+ students to access lessons, quizzes, and progress tracking.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed backend APIs using Node.js and Express.js with MySQL to support online education during the pandemic.
\item Integrated modules for lesson uploads, quizzes, and real-time progress tracking with secure authentication and role-based access.
\item Implemented optimized database queries and caching mechanisms to handle high concurrent usage and improve backend performance.
\item Deployed the backend on AWS with Docker, CDN caching, and SSL encryption ensuring reliable access for over 6,000 students.
\end{itemize}

\textbf{Automated Cryptocurrency Trading Bot} -- \emph{Personal Project}

\vspace{-1pt}

Created a Python trading bot using Binance API and WebSocket for automated trade execution with risk control and live monitoring.
\vspace{-1pt}
\begin{itemize}
\item Developed a fully automated backend trading bot in Python using Binance API and WebSocket for real-time data streaming.
\item Implemented dynamic trading strategies, stop-loss mechanisms, and order execution algorithms with secure API integrations.
\item Integrated Pandas and NumPy for market analysis and backtesting to improve trading accuracy and backend processing efficiency.
\item Deployed using Docker on AWS EC2 for 24/7 backend uptime, reliability, and monitoring with detailed logging and error handling.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}