% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Backend Developer with hands-on experience building scalable server-side applications and RESTful APIs using Python, Django, Flask, and Node.js. Proficient in database management with PostgreSQL, MySQL, and MongoDB, and skilled in deploying secure cloud infrastructure on AWS and GCP. Experienced in implementing CI/CD pipelines, optimizing backend performance, and collaborating with cross-functional teams in Agile environments to deliver robust, testable, and efficient code.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, SQL, PHP, Bash, PowerShell

\textbf{Backend Frameworks:} Django, Flask, FastAPI, Node.js, Express.js

\textbf{Database Management:} PostgreSQL, MySQL, MongoDB, SQLite, Redis

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, CI/CD, GitHub Actions, Terraform

\textbf{API \& Architecture:} REST API, GraphQL, Microservices, Clean Architecture, MVC

\textbf{Security \& Testing:} OAuth, JWT, OWASP, Unit Testing, Integration Testing, API Security

\textbf{Development Practices:} Agile, Scrum, Code Reviews, Git, Version Control, Technical Documentation

\textbf{Soft Skills:} Problem Solving, Communication, Collaboration, Attention to Detail, Adaptability, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable backend systems and RESTful APIs using Node.js and Django to enhance application functionality and performance.
\item Optimized database queries and designed schemas in PostgreSQL and MySQL to improve data retrieval speed and system reliability.
\item Implemented secure authentication mechanisms and data protection measures adhering to OWASP security standards and best practices.
\item Deployed and maintained cloud infrastructure on AWS using Docker and CI/CD pipelines ensuring high availability and consistent uptime.
\item Collaborated with frontend developers in Agile teams through code reviews and sprint planning to deliver integrated solutions on time.
\item Applied test-driven development and wrote reusable, efficient code reducing production issues and improving long-term maintainability.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in backend development for enterprise applications including API design, database integration, and server-side logic implementation.
\item Contributed to building the Proposal Management and Mailroom Tracking Systems with secure data handling and optimized performance.
\item Worked with cross-functional teams to gather requirements, conduct testing, and support deployment of backend services and databases.
\item Gained experience in Python backend frameworks, SQL database management, and version control using Git in Agile development workflows.
\item Participated in code reviews and collaborated on identifying improvements in backend scalability, security, and code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable backend LMS using Node.js, MySQL, and AWS supporting 6K+ students with secure authentication and real-time data access.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed RESTful APIs using Node.js and Express.js to handle lesson uploads, quizzes, and performance tracking endpoints.
\item Implemented secure user authentication with JWT, role-based access control, and optimized SQL queries for high concurrent user sessions.
\item Integrated real-time data dashboards for teachers using WebSockets and optimized database indexing for fast query performance.
\item Deployed the backend on AWS with SSL encryption, CDN caching, and scalable infrastructure ensuring reliable access for over 6,000 users.
\end{itemize}

\textbf{Automated Cryptocurrency Trading Bot} -- \emph{Personal Project}

\vspace{-1pt}

Created a Python trading bot using Binance API and WebSocket for automated trade execution with real-time data streaming and risk control.
\vspace{-1pt}
\begin{itemize}
\item Developed a fully automated trading bot in Python leveraging Binance API and WebSocket for real-time cryptocurrency market data streaming.
\item Implemented dynamic trading algorithms, stop-loss mechanisms, and order execution logic with Pandas and NumPy for market analysis.
\item Integrated secure API authentication, error handling, and logging to ensure reliable and safe execution of automated trading strategies.
\item Deployed the bot on AWS EC2 using Docker for 24/7 uptime, continuous monitoring, and detailed logging of all trading activity.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}