% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Backend Developer with hands-on experience building scalable server-side applications and APIs using Python, JavaScript, and Node.js. Proven ability to design and implement RESTful APIs, optimize database performance, and deploy secure cloud-based systems on AWS. Skilled in working with SQL and NoSQL databases, CI/CD pipelines, and collaborating with cross-functional teams in Agile environments. Strong foundation in computer science, security best practices, and problem-solving with a focus on performance and scalability.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, PHP, SQL, Bash, PowerShell

\textbf{Backend Frameworks:} Node.js, Django, Flask, FastAPI, Express.js

\textbf{Database Management:} PostgreSQL, MySQL, MongoDB, SQLite, Redis

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, CI/CD, GitHub Actions, GitLab

\textbf{API \& Security:} RESTful APIs, GraphQL, JWT, OAuth, API Security, Encryption

\textbf{Software Development:} Agile, Scrum, Git, Code Reviews, TDD, Unit Testing

\textbf{Soft Skills:} Problem Solving, Collaboration, Communication, Adaptability, Attention to Detail, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable backend services using Node.js and Python to enhance e-commerce functionality and system reliability.
\item Designed and implemented RESTful APIs, optimized SQL queries, and integrated secure payment systems for improved performance.
\item Deployed cloud-based applications on AWS using Docker and CI/CD pipelines ensuring consistent uptime and high availability.
\item Collaborated in Agile teams through code reviews, sprint planning, and pair programming to deliver high-quality solutions.
\item Applied test-driven development, secure coding standards, and data protection measures to reduce production issues.
\item Led backend development for multiple applications while mentoring junior developers on best practices and deployment.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications focusing on backend logic, database integration, and API design.
\item Contributed to the design and implementation of Proposal Management and Mailroom Tracking Systems with secure backends.
\item Worked with cross-functional teams to gather requirements, perform testing, and support deployment phases effectively.
\item Gained experience in server-side development, database management, and secure coding practices within Agile workflows.
\item Collaborated in project reviews to identify improvements in backend performance, scalability, and code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS backend using Node.js and MySQL to support 6K+ students with secure authentication and real-time tracking.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed backend APIs using Node.js and MySQL to support lesson uploads, quizzes, and performance tracking.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent usage.
\item Integrated real-time progress dashboards for teachers with efficient server-side logic and data processing capabilities.
\item Deployed the platform on AWS with SSL encryption and CDN caching ensuring reliable access for over 6,000 students.
\end{itemize}

\textbf{Automated Cryptocurrency Trading Bot} -- \emph{Personal Project}

\vspace{-1pt}

Created a Python trading bot using Binance API and WebSocket for automated trade execution with risk control and live monitoring.
\vspace{-1pt}
\begin{itemize}
\item Developed a fully automated trading bot in Python using Binance API and WebSocket for real-time data streaming and processing.
\item Implemented dynamic trading strategies, stop-loss mechanisms, and order execution algorithms for efficient trade automation.
\item Integrated Pandas and NumPy for market analysis and backtesting to improve trading accuracy and decision-making logic.
\item Deployed using Docker on AWS EC2 for 24/7 uptime, reliability, and monitoring with detailed logging and error handling.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}