% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with 3+ years of backend development experience specializing in API design, database management, and cloud infrastructure. Proficient in Python, Java, SQL, and SpringBoot with proven expertise in deploying scalable applications using Docker, Kubernetes, and CI/CD pipelines. Strong background in Agile methodologies, troubleshooting production systems, and collaborating with cross-functional teams to deliver secure, high-performance solutions aligned with business objectives.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, Java, JavaScript, SQL, PHP, Bash, PowerShell, HTML5, CSS3

\textbf{Backend Frameworks \& Tools:} SpringBoot, Django, Flask, Node.js, Express.js, FastAPI, RESTful Web Services, JSON

\textbf{Database \& Batch Processing:} Oracle, PostgreSQL, MySQL, MongoDB, SQL Server, Redis, Database Management, ETL Pipelines

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, GitHub Actions, Jenkins, CI/CD, Terraform, CloudFormation

\textbf{Software Development \& Testing:} Object-Oriented Design, Unit Testing, UI Automation, TDD, SDLC, Agile, Scrum, Code Reviews

\textbf{Systems \& Integration:} Microservices, API Gateway, Event-Driven Architecture, Integration Testing, Debugging, Troubleshooting

\textbf{Tools \& Collaboration:} Jira, Confluence, Git, GitLab, Postman, FastLane, Technical Documentation, Monitoring

\textbf{Soft Skills:} Relationship Management, Team Collaboration, Problem Solving, Communication, Analytical Thinking, Adaptability

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable backend applications using Python, Node.js, and RESTful APIs to support e-commerce and enterprise solutions.
\item Optimized SQL queries and integrated secure payment systems improving database performance and system reliability by 30 percent.
\item Deployed cloud-based applications using AWS, Docker, Kubernetes, and CI/CD pipelines ensuring high availability and uptime.
\item Collaborated with cross-functional teams through Agile sprints, code reviews, and pair programming to deliver quality software.
\item Implemented unit testing, UI automation, and secure coding practices throughout SDLC reducing production defects significantly.
\item Provided technical guidance and mentored junior developers on backend development, troubleshooting, and deployment best practices.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web and mobile applications with focus on backend integration and database management tasks.
\item Contributed to design and implementation of Proposal Management and Mailroom Tracking Systems using Agile methodologies.
\item Worked with technology and business partners to gather requirements, perform testing, and support deployment activities.
\item Gained hands-on experience in batch processing, debugging, and troubleshooting within production support environments.
\item Participated in project reviews identifying performance improvements, scalability enhancements, and code quality optimizations.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS supporting 6K+ students with secure authentication, real-time dashboards, and optimized database queries.
\vspace{-1pt}
\begin{itemize}
\item Designed full-stack LMS using React, Node.js, and MySQL with RESTful APIs supporting lesson uploads and performance tracking.
\item Implemented secure authentication, role-based access control, and optimized SQL queries for high concurrent user traffic.
\item Integrated real-time dashboards for teachers enabling progress monitoring and automated quiz scoring with JSON data exchange.
\item Deployed on AWS with Docker, CDN caching, and SSL encryption ensuring reliable access and disaster recovery for 6K students.
\end{itemize}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Automated vulnerability scanning and patch deployment reducing manual effort by 60 percent and accelerating remediation cycles.
\vspace{-1pt}
\begin{itemize}
\item Developed automated workflows using Python, Jenkins, and CI/CD pipelines for vulnerability scanning and patch management.
\item Integrated Nessus API for real-time vulnerability reporting, risk prioritization, and compliance tracking with JSON outputs.
\item Created monitoring dashboards and alert systems tracking security compliance and remediation progress across systems.
\item Reduced manual intervention by 60 percent accelerating patch cycles through full automation and adherence to security policies.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}