% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Back End Developer with strong expertise in Python, JavaScript, and SQL. Experienced in designing scalable APIs, optimizing database queries, and solving complex algorithmic challenges. Proven ability to evaluate code quality, debug workflows, and improve system performance through structured problem-solving. Skilled in data structures, algorithms, and technical documentation with a track record of delivering high-quality solutions in fast-paced environments.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, SQL, HTML, CSS, PHP

\textbf{Frameworks \& Libraries:} Django, Flask, Node.js, React, Express.js, FastAPI

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQLite, Redis

\textbf{Cloud \& DevOps:} AWS, Docker, CI/CD, GitHub Actions, AWS Lambda

\textbf{Computer Science Fundamentals:} Data Structures, Algorithms, Object-Oriented Programming, Design Patterns, Debugging

\textbf{Software Development Practices:} Agile, Code Reviews, Testing, Technical Documentation, Performance Optimization

\textbf{Soft Skills:} Problem Solving, Communication, Collaboration, Adaptability, Detail-Oriented, Analytical Thinking

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Built scalable backend systems using Python, JavaScript, and SQL solving complex algorithmic challenges and optimizing performance.
\item Developed RESTful APIs with secure authentication improving system reliability while maintaining clean, debuggable code architecture.
\item Optimized database queries and data structures across PostgreSQL and MySQL reducing latency and enhancing application responsiveness.
\item Deployed cloud applications using AWS and Docker with CI/CD pipelines ensuring consistent uptime and automated delivery workflows.
\item Collaborated in Agile teams conducting code reviews and evaluating solution correctness to maintain high-quality deliverables.
\item Mentored team members on debugging workflows, algorithmic problem solving, and best practices for backend development excellence.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to backend development of enterprise applications solving coding challenges and implementing efficient algorithms.
\item Assisted in designing data structures and SQL queries for Proposal Management and Mailroom Tracking Systems improving performance.
\item Worked with cross-functional teams to evaluate code quality, perform testing, and support deployment phases in Agile workflows.
\item Gained hands-on experience debugging complex workflows and applying best practices in software testing and secure coding standards.
\item Participated in project reviews identifying improvements in code correctness, scalability, and overall system maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS using Python, JavaScript, and SQL supporting 6K+ students with real-time quizzes and progress tracking.
\vspace{-1pt}
\begin{itemize}
\item Designed backend architecture using Node.js and MySQL solving complex data structure challenges for concurrent user management.
\item Implemented secure authentication and role-based access with JWT optimizing database queries for high-performance data retrieval.
\item Integrated real-time progress tracking and quiz evaluation modules applying algorithmic logic for accurate scoring and feedback.
\item Deployed on AWS with CDN caching and SSL encryption ensuring scalable, reliable access for over 6,000 concurrent students.
\end{itemize}

\textbf{Automated Cryptocurrency Trading Bot} -- \emph{Personal Project}

\vspace{-1pt}

Developed a Python trading bot using Binance API and WebSocket for automated trade execution with real-time market analysis.
\vspace{-1pt}
\begin{itemize}
\item Built automated trading algorithms in Python using Binance API solving complex market analysis challenges with data structures.
\item Implemented dynamic trading strategies with stop-loss mechanisms applying algorithmic logic for risk control and order execution.
\item Integrated Pandas and NumPy for backtesting and market analysis optimizing trading accuracy through structured problem solving.
\item Deployed using Docker on AWS EC2 ensuring 24/7 uptime with detailed logging and monitoring for performance evaluation.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}