% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Detail-oriented Software Engineer with expertise in Python, JavaScript, and backend development. Proficient in designing scalable systems, debugging complex workflows, and implementing algorithms using data structures. Experienced in evaluating code quality, optimizing performance, and collaborating across teams. Skilled in RESTful APIs, cloud platforms, and Agile methodologies with strong problem-solving abilities and a commitment to continuous learning.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, SQL, HTML, CSS, PHP

\textbf{Frameworks \& Libraries:} React, Django, Flask, Node.js, Bootstrap

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQLite

\textbf{Cloud \& DevOps:} AWS, Docker, CI/CD, GitHub Actions, Jenkins

\textbf{Software Development Practices:} Agile, Scrum, Testing, Debugging, Code Reviews

\textbf{Computer Science Fundamentals:} Data Structures, Algorithms, OOP, Design Patterns

\textbf{Soft Skills:} Problem Solving, Communication, Collaboration, Adaptability, Detail-Oriented

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable backend systems using Python and JavaScript to support enterprise applications and e-commerce platforms.
\item Implemented RESTful APIs with optimized database queries enhancing system reliability and performance across production environments.
\item Debugged complex workflows and resolved technical issues using systematic problem-solving and data structure knowledge.
\item Collaborated within Agile teams through code reviews and sprint planning ensuring high-quality, maintainable code deliverables.
\item Applied testing methodologies and secure coding standards throughout SDLC improving overall system correctness and stability.
\item Mentored team members on backend best practices, algorithms, and coding challenges to elevate technical quality across projects.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing backend components for enterprise applications using Python and JavaScript ensuring functional correctness.
\item Evaluated code quality and performed debugging workflows to identify performance bottlenecks and optimize system behavior.
\item Collaborated with cross-functional teams to gather requirements, conduct testing, and support seamless deployment processes.
\item Gained hands-on experience in algorithms, data structures, and backend logic while adhering to Agile development practices.
\item Participated in code reviews to improve performance, scalability, and maintainability across multiple software projects.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS using Python and JavaScript enabling 6K+ students to learn with notes, videos, and interactive quizzes.
\vspace{-1pt}
\begin{itemize}
\item Designed backend architecture using Python and JavaScript with MySQL for lesson uploads, quizzes, and performance tracking.
\item Implemented secure authentication and optimized database queries to handle high concurrent usage and ensure data correctness.
\item Debugged complex workflows and tested platform functionality to guarantee reliable performance under heavy student load.
\item Deployed on AWS with SSL encryption ensuring scalable, secure access for over 6,000 students with minimal downtime.
\end{itemize}

\textbf{Automated Cryptocurrency Trading Bot} -- \emph{Personal Project}

\vspace{-1pt}

Created a Python trading bot using Binance API to automate trade execution with algorithms for risk control and monitoring.
\vspace{-1pt}
\begin{itemize}
\item Developed automated trading logic in Python implementing algorithms and data structures for order execution and risk management.
\item Integrated Binance API for real-time data processing and evaluated system correctness through backtesting and performance analysis.
\item Debugged trading workflows and optimized code performance to ensure accurate execution under varying market conditions.
\item Deployed on AWS EC2 using Docker for 24/7 uptime with detailed logging to monitor system health and trading accuracy.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}