% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Backend Software Engineer with expertise in designing and implementing scalable server-side systems and RESTful APIs using Python, JavaScript, PHP, and Node.js. Experienced in database management with PostgreSQL, MySQL, and MongoDB, ensuring data integrity, security, and high performance. Skilled in cloud deployment with AWS and GCP, implementing CI/CD pipelines, and optimizing backend architectures for reliability and maintainability.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, PHP, SQL, Bash, PowerShell

\textbf{Backend Frameworks \& APIs:} Node.js, Django, Flask, FastAPI, Express.js, RESTful API

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQL optimization, NoSQL, Data modeling

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, CI/CD pipelines, GitHub Actions, Infrastructure as Code

\textbf{Software Development Practices:} Agile, Scrum, Unit Testing, TDD, Code Reviews, Technical Documentation

\textbf{Computer Science Fundamentals:} Object-Oriented Programming, Design Patterns, Data Structures, Algorithms, System Design

\textbf{Systems \& Security:} Linux, Git, Version Control, API Security, OAuth, JWT

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Ownership, Technical Documentation

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable backend APIs using Node.js and Python with RESTful design patterns to enhance system functionality.
\item Optimized PostgreSQL and MySQL queries, implemented database indexing strategies improving response times and data integrity.
\item Deployed cloud-based applications on AWS using Docker and CI/CD pipelines ensuring high availability and consistent uptime.
\item Collaborated with cross-functional teams through Agile sprints, code reviews, and technical planning to deliver solutions.
\item Applied secure coding practices and implemented authentication mechanisms throughout SDLC reducing security vulnerabilities.
\item Mentored junior developers on backend architecture best practices, Git workflows, and deployment automation techniques.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing backend components for enterprise web applications using Python and JavaScript frameworks.
\item Contributed to database design and implementation for Proposal Management and Mailroom Tracking Systems with SQL.
\item Worked with cross-functional teams to gather requirements, perform testing, and support deployment phases effectively.
\item Gained hands-on experience in server-side logic, API development, and database management within Agile workflows.
\item Participated in code reviews and technical discussions to identify improvements in performance and maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable backend LMS using Node.js and MySQL enabling 6K+ students to access educational content with secure APIs.
\vspace{-1pt}
\begin{itemize}
\item Designed and implemented RESTful APIs using Node.js and Express.js with MySQL database for lesson and quiz management.
\item Developed server-side authentication, role-based access control, and optimized database queries for concurrent usage.
\item Integrated real-time performance tracking dashboards with WebSocket connections for teachers and administrators.
\item Deployed backend infrastructure on AWS with load balancing and SSL encryption ensuring reliable access for 6,000+ users.
\end{itemize}

\textbf{Automated Cryptocurrency Trading Bot} -- \emph{Personal Project}

\vspace{-1pt}

Created a Python-based trading bot with Binance API and WebSocket for automated trade execution and real-time monitoring.
\vspace{-1pt}
\begin{itemize}
\item Developed backend trading algorithms in Python using Binance API and WebSocket for real-time market data processing.
\item Implemented order execution logic, stop-loss mechanisms, and risk management strategies with object-oriented design.
\item Integrated Pandas and NumPy for data analysis, backtesting strategies, and performance optimization of trading models.
\item Deployed on AWS EC2 with Docker for continuous operation, implemented logging and monitoring for system reliability.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}