% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Backend Engineer with 4+ years of experience building scalable, high-performance systems using Node.js, TypeScript, and JavaScript. Proven expertise in designing RESTful APIs, optimizing PostgreSQL databases, and deploying cloud-based solutions on AWS with Docker and CI/CD pipelines. Strong foundation in object-oriented programming, design patterns, and serverless architecture. Skilled in cross-functional collaboration within Agile teams, delivering customer-centric solutions that drive business value and operational efficiency.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Backend Development:} Node.js, TypeScript, JavaScript, Express.js, Python, PHP

\textbf{Database \& Query Optimization:} PostgreSQL, MySQL, MongoDB, SQL, Database Modeling, Data Migrations

\textbf{API Development \& Security:} REST API, GraphQL, JWT, OAuth, Input Validation, API Security

\textbf{Cloud \& DevOps:} AWS, AWS Lambda, Docker, Kubernetes, CI/CD, Serverless Architecture

\textbf{Software Engineering Practices:} OOP, Design Patterns, Microservices, TDD, Agile, Scrum

\textbf{Performance \& Scalability:} Load Balancing, Caching, Autoscaling, Performance Optimization, High Availability

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Ownership, Remote Work

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable backend services using Node.js and JavaScript with RESTful APIs ensuring high availability and reliability.
\item Optimized PostgreSQL queries and database models to improve performance, manage migrations, and support growing transaction volumes.
\item Built secure APIs with JWT authentication, input validation, and queue-based processing to handle concurrency and idempotency.
\item Deployed cloud-based applications on AWS using Docker, serverless architecture, and CI/CD pipelines ensuring consistent uptime.
\item Collaborated with cross-functional teams in Agile sprints through code reviews and pair programming to deliver customer-focused features.
\item Mentored junior developers on backend best practices, design patterns, and scalable system architecture to drive team growth.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to backend development of enterprise applications, building APIs and integrating database layers with business logic.
\item Assisted in designing and implementing the Proposal Management System with focus on scalability and maintainable code architecture.
\item Worked closely with product teams to gather requirements, perform integration testing, and support deployment phases effectively.
\item Gained hands-on experience in full stack development, SQL optimization, and secure coding practices within Agile workflows.
\item Participated in code reviews and team retrospectives to identify performance improvements and enhance system reliability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable backend for an LMS using Node.js and PostgreSQL, supporting 6K+ students with real-time progress tracking.
\vspace{-1pt}
\begin{itemize}
\item Designed backend architecture using Node.js and Express.js with RESTful APIs to handle lesson uploads, quizzes, and analytics.
\item Optimized PostgreSQL database schema and queries to efficiently manage high concurrent usage and real-time data synchronization.
\item Implemented secure authentication with JWT, role-based access control, and input validation ensuring data integrity and security.
\item Deployed on AWS with serverless functions, Docker containers, and SSL encryption ensuring reliable access for over 6,000 students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed backend for a real-time chat app using Node.js and Socket.io with AWS Polly integration for accessibility features.
\vspace{-1pt}
\begin{itemize}
\item Built scalable backend with Node.js and Socket.io to manage real-time WebSocket connections and message broadcasting efficiently.
\item Integrated AWS Polly API for text-to-speech and designed RESTful endpoints to support accessibility features and voice interactions.
\item Implemented concurrency handling, message queuing, and database persistence using PostgreSQL to ensure reliable message delivery.
\item Deployed on AWS App Runner with Docker containers optimizing for low-latency communication and horizontal autoscaling capabilities.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}