% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Backend Software Developer with expertise in building scalable data pipelines, RESTful APIs, and cloud-based systems using Python, SQL, and modern DevOps tools. Proven ability to design and optimize relational databases, implement ELT workflows, and deploy containerized applications on AWS and GCP. Experienced in Agile development with strong collaboration skills across cross-functional teams to deliver high-performance backend solutions.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, SQL, JavaScript, Bash, PowerShell, PHP

\textbf{Backend \& API Development:} RESTful APIs, Django, Flask, FastAPI, Node.js, Express.js

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, Data Warehousing, ETL Pipelines, BigQuery

\textbf{Cloud \& DevOps:} AWS, Google Cloud Platform, Docker, Kubernetes, CI/CD, Infrastructure as Code

\textbf{Software Development Practices:} Agile, Scrum, Unit Testing, Integration Testing, Git, Technical Documentation

\textbf{Systems \& Architecture:} Microservices, Serverless, Performance Optimization, Scalability, Monitoring, Automation

\textbf{Soft Skills:} Collaboration, Communication, Problem Solving, Adaptability, Ownership, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable backend systems and RESTful APIs using Python, Node.js, and SQL to enhance application performance and reliability.
\item Designed and optimized relational database schemas and complex SQL queries to support efficient data manipulation and reporting workflows.
\item Built and maintained automated ELT data pipelines integrating multiple data sources into cloud-based warehouses with AWS services.
\item Deployed containerized applications using Docker and Kubernetes with CI/CD pipelines ensuring consistent uptime and rapid deployments.
\item Collaborated with cross-functional teams in Agile sprints through code reviews and pair programming to deliver high-quality solutions.
\item Monitored and optimized API performance, database indexing, and query execution plans to achieve maximum efficiency and scalability.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level backend systems and APIs for Proposal Management and Mailroom Tracking Systems applications.
\item Contributed to database design, SQL query optimization, and data integration tasks across multiple internal business platforms.
\item Worked closely with cross-functional teams to gather backend requirements, perform testing, and support deployment phases successfully.
\item Gained hands-on experience in backend development, API testing, and secure coding practices within Agile and Scrum workflows.
\item Participated in project reviews to identify improvements in performance, scalability, and code maintainability across backend services.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS backend with RESTful APIs and MySQL database supporting 6K+ students with lessons, quizzes, and tracking.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full-stack LMS backend using Node.js, RESTful APIs, and MySQL to support online education at scale.
\item Implemented secure authentication, role-based access control, and optimized SQL queries for high concurrent user performance.
\item Built automated data pipelines for lesson uploads, quiz grading, and performance tracking with real-time progress dashboards.
\item Deployed the platform on AWS with Docker containers, CDN caching, and SSL encryption ensuring reliable access for 6,000+ students.
\end{itemize}

\textbf{Automated Cryptocurrency Trading Bot} -- \emph{Personal Project}

\vspace{-1pt}

Created a Python trading bot using Binance API and WebSocket to automate trade execution with risk control and live monitoring.
\vspace{-1pt}
\begin{itemize}
\item Developed a fully automated trading bot in Python using Binance API and WebSocket for real-time market data streaming and execution.
\item Implemented dynamic trading algorithms, stop-loss mechanisms, and order execution logic with efficient data processing workflows.
\item Integrated Pandas for market analysis and backtesting to improve trading accuracy and optimize strategy performance continuously.
\item Deployed using Docker on AWS EC2 for 24/7 uptime with automated monitoring, logging, and error handling for reliable operations.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}