% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Detail-oriented software professional transitioning into Business Analysis with strong technical foundation and proven ability to bridge business and technology. Experienced in requirements gathering, process documentation, and cross-functional collaboration through Agile workflows. Skilled in translating stakeholder needs into technical specifications while supporting testing, deployment, and continuous improvement initiatives. Proficient in data analysis, documentation tools, and SDLC with hands-on exposure to AI integration and system design.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Business Analysis \& Documentation:} Requirements Analysis, Process Mapping, User Stories, UAT Coordination, Technical Documentation

\textbf{Data \& Reporting Tools:} Excel, SQL, Data Visualization, Power BI, Microsoft Office Suite

\textbf{Project \& Collaboration Tools:} Jira, Agile, Scrum, Slack, Version Control

\textbf{Technical Skills:} APIs, Database Design, SDLC, Testing, AI Integration

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Attention to Detail, Stakeholder Management

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Collaborated with stakeholders to gather and document requirements ensuring alignment between business needs and technical solutions.
\item Analyzed business processes and translated functional requirements into user stories and acceptance criteria for development teams.
\item Coordinated testing activities including UAT support, issue tracking, and defect resolution to ensure quality deliverables.
\item Facilitated Agile ceremonies and maintained project documentation including meeting notes, status updates, and process diagrams.
\item Worked closely with cross-functional teams to clarify scope changes and support continuous improvement initiatives.
\item Supported data analysis and reporting using SQL queries to provide insights for business decision-making and performance tracking.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in gathering and documenting business requirements for enterprise applications supporting proposal and tracking systems.
\item Supported process mapping efforts to identify as-is workflows and recommend improvements for operational efficiency.
\item Coordinated with cross-functional teams to clarify requirements, perform testing, and track issues through resolution.
\item Contributed to project documentation including workflow diagrams, test cases, and deployment support materials.
\item Participated in Agile workflows and sprint reviews to identify opportunities for performance and scalability improvements.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Gathered requirements and documented business processes for a scalable LMS supporting 6K+ students with tracking and analytics.
\vspace{-1pt}
\begin{itemize}
\item Analyzed user needs and documented functional requirements for lesson management, quizzes, and performance tracking features.
\item Created process flow diagrams and user stories to support development of real-time dashboards for teachers and administrators.
\item Coordinated testing activities including test case creation and UAT support ensuring system reliability for concurrent users.
\item Collaborated with stakeholders to refine scope and optimize database design for high-volume educational data management.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Documented requirements and supported testing for an inclusive chat application integrating AI speech services and accessibility features.
\vspace{-1pt}
\begin{itemize}
\item Gathered and documented accessibility requirements working closely with stakeholders to define user stories and acceptance criteria.
\item Supported integration of AI-powered speech services by documenting API specifications and coordinating testing with assistive tools.
\item Created workflow diagrams and process documentation to map user journeys and ensure compliance with WCAG accessibility standards.
\item Assisted with UAT coordination and issue tracking ensuring seamless deployment of real-time communication features on cloud infrastructure.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}