% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with 2+ years of progressive IT and business experience in full stack development, data management, and cross-functional collaboration. Proficient in SQL, Python, JavaScript, and requirements gathering with a strong foundation in Agile methodologies, testing, and system implementation. Experienced in delivering scalable web applications, API integration, and cloud deployment while working closely with business and technical teams to translate requirements into efficient solutions.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming \& Scripting:} Python, JavaScript, SQL, PHP, Bash, PowerShell

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, Database Design, Query Optimization

\textbf{Development Frameworks \& Tools:} React, Django, Node.js, Flask, FastAPI, Bootstrap

\textbf{Cloud \& DevOps:} AWS, GCP, Docker, CI/CD, GitHub Actions, GitLab

\textbf{Testing \& Quality Assurance:} Unit Testing, Integration Testing, Automation Testing, Debugging, QA Validation

\textbf{Software Development Practices:} Agile, Scrum, SDLC, Requirements Analysis, System Design, Documentation

\textbf{Collaboration \& Project Tools:} Jira, Confluence, Git, Technical Documentation, Code Reviews

\textbf{Soft Skills:} Communication, Collaboration, Analytical Thinking, Adaptability, Problem Solving, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed full stack web applications using JavaScript, React, and Node.js to enhance functionality and user experience.
\item Implemented RESTful APIs and optimized SQL queries to improve data retrieval performance and system reliability.
\item Deployed cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring high availability and consistent uptime.
\item Collaborated within Agile teams through code reviews, sprint planning, and testing to deliver high-quality solutions on schedule.
\item Gathered business requirements and translated them into technical specifications aligned with development and QA standards.
\item Applied secure coding practices and test-driven development throughout SDLC reducing production defects and improving maintainability.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web and mobile applications across frontend and backend components within Agile workflows.
\item Contributed to the design, testing, and implementation of Proposal Management and Mailroom Tracking Systems.
\item Worked closely with cross-functional teams to gather requirements, perform QA validation, and support deployment phases.
\item Gained hands-on experience in full stack development, software testing, and secure coding ensuring quality deliverables.
\item Collaborated in project reviews to identify improvements in performance, scalability, and code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to access notes, videos, quizzes, and performance tracking during the pandemic.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL to support online education during the pandemic.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards for teachers and students.
\item Implemented secure authentication, role-based access control, and optimized SQL queries for high concurrent user sessions.
\item Deployed the platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 students.
\end{itemize}

\textbf{Custom Business Web Solutions} -- \emph{Personal Project}

\vspace{-1pt}

Built POS systems, e-commerce sites, landing pages, and inventory solutions with secure design improving workflow efficiency.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed multiple custom web solutions using React, Next.js, and Express.js tailored to client business needs.
\item Implemented secure authentication, inventory tracking, and integrated Stripe API for payment processing and data security.
\item Collaborated with clients to gather requirements, translate business needs, and deliver scalable, responsive applications.
\item Optimized UI performance, responsiveness, and SEO across all client projects enhancing user engagement and conversion rates.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}