% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with expertise in cloud computing, microservices, and full stack development. Proven experience translating technical requirements into scalable solutions across AWS, GCP, Docker, and Kubernetes. Skilled in system development lifecycle, integration testing, and release management with strong proficiency in Python, JavaScript, and SQL. Adept at troubleshooting complex systems, implementing secure coding standards, and collaborating across functional teams to deliver high-quality software solutions.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, PHP, SQL, Bash, PowerShell

\textbf{Cloud \& DevOps:} AWS, GCP, Docker, Kubernetes, CI/CD, Infrastructure as Code

\textbf{Frameworks \& Integration:} React, Node.js, Django, RESTful APIs, Microservices

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQL optimization

\textbf{Development Practices:} Agile, Scrum, SDLC, TDD, Code Reviews, Version Control

\textbf{Security \& Testing:} OWASP, OAuth, Encryption, Unit Testing, Integration Testing

\textbf{System Design \& Architecture:} Design Patterns, OOP, Troubleshooting, Performance Optimization

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Problem Solving, Learning Agility, Analytical Thinking

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable web applications using JavaScript, React, and Node.js translating user requirements into functional features.
\item Implemented RESTful APIs and optimized SQL queries adhering to security, logging, and performance standards across system components.
\item Deployed cloud-based solutions using AWS, Docker, and CI/CD pipelines following release management processes and version controls.
\item Conducted integration testing, troubleshooting, and preventative maintenance ensuring code quality and system reliability.
\item Collaborated within Agile teams through code reviews and sprint planning to deliver high-quality software meeting business requirements.
\item Evaluated emerging technologies for fit with existing systems analyzing upstream and downstream impacts on processes and architecture.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise applications following SDLC phases from requirements analysis through deployment and maintenance.
\item Contributed to system design and integration of Proposal Management and Mailroom Tracking Systems across functional teams.
\item Worked with cross functional stakeholders to gather requirements, perform testing, and document software development processes.
\item Gained experience in troubleshooting, debugging, and implementing secure coding practices within Agile development workflows.
\item Collaborated in project reviews identifying opportunities for performance improvements, scalability enhancements, and code quality.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack LMS using React, Node.js, and MySQL translating educational requirements into technical specifications.
\item Integrated lesson uploads, quizzes, and performance tracking modules ensuring system adherence to security and testing standards.
\item Implemented secure authentication and role-based access with optimized database queries for high concurrent user performance.
\item Deployed platform on AWS with CDN caching and SSL encryption following release management processes ensuring reliable uptime.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users and individuals with reading challenges, integrating accessibility features.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Node.js, and Socket.io analyzing user requirements for accessibility compliance.
\item Integrated AWS Polly and Azure cloud services enabling text-to-speech and voice-to-text communication across platforms.
\item Followed WCAG standards and conducted testing with assistive technologies ensuring system met non-functional requirements.
\item Deployed on AWS App Runner using Docker containers implementing microservices architecture for scalable low-latency performance.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}