% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with expertise in cloud infrastructure, AI integration, and full stack development across AWS, GCP, and Microsoft Azure. Proven ability to design scalable solutions, automate workflows, and drive cloud migration projects. Skilled in Python, JavaScript, and REST API development with hands-on experience in DevOps, CI/CD pipelines, and cloud governance. Strong communicator with a self-starter mentality, focused on continuous learning and delivering innovative solutions.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Platforms \& Infrastructure:} AWS, Microsoft Azure, Google Cloud Platform, Docker, Kubernetes, Terraform

\textbf{Programming \& Scripting:} Python, JavaScript, TypeScript, Bash, PowerShell, SQL

\textbf{AI \& Machine Learning:} AI Integration, LLM API, ChatGPT API, Prompt Engineering, Machine Learning APIs

\textbf{DevOps \& Automation:} CI/CD, GitHub Actions, Jenkins, Infrastructure as Code, Workflow Automation

\textbf{Cloud Services \& APIs:} REST API, AWS Lambda, AWS S3, Azure Active Directory, Microsoft 365, IAM

\textbf{Security \& Governance:} Cloud Security, IAM Policies, Encryption, OWASP, Threat Intelligence

\textbf{Databases \& Data Management:} PostgreSQL, MySQL, MongoDB, BigQuery, ETL Pipelines, Data Warehousing

\textbf{Monitoring \& Optimization:} CloudWatch, Logging, Performance Optimization, Autoscaling, Load Balancing

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Continuous Learning, Adaptability, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using JavaScript, React, and Node.js while integrating REST APIs across cloud platforms.
\item Deployed and maintained cloud infrastructure on AWS utilizing Docker, Kubernetes, and CI/CD pipelines ensuring high availability.
\item Optimized SQL queries and database performance while implementing secure authentication and API integrations for reliability.
\item Collaborated within Agile teams through sprint planning, code reviews, and technical documentation to deliver quality solutions.
\item Applied secure coding standards and automation throughout SDLC reducing production issues and improving system maintainability.
\item Led backend development initiatives while mentoring team members on best practices for cloud deployment and architecture design.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications while contributing to both frontend and backend system components.
\item Contributed to cloud migration planning and implementation of scalable systems aligned with business requirements.
\item Worked with cross functional teams to gather requirements, perform integration testing, and support deployment activities.
\item Gained hands-on experience in full stack development, automation, and secure coding practices within Agile environments.
\item Collaborated in project reviews identifying opportunities for performance improvements and system optimization strategies.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to access lessons, quizzes, and performance tracking with cloud deployment on AWS.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack LMS using React, Node.js, and MySQL with real-time dashboards for tracking student progress and engagement.
\item Integrated secure authentication, role-based access controls, and optimized database queries for high concurrent user volumes.
\item Deployed platform on AWS with CDN caching, SSL encryption, and autoscaling ensuring reliable access for over 6,000 students.
\item Implemented lesson uploads, interactive quizzes, and performance analytics modules enhancing online education accessibility.
\end{itemize}

\textbf{PROSPR " Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed inclusive chat application for low-vision users integrating AI-powered text-to-speech and voice-to-text features.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Node.js, and Socket.io with accessibility-focused UI following WCAG standards.
\item Integrated AWS Polly and Azure Speech Services enabling text-to-speech and voice-to-text for inclusive communication.
\item Deployed on AWS App Runner with Docker containers ensuring scalable, low-latency performance and high availability.
\item Tested with assistive technologies validating compliance with accessibility requirements and ensuring inclusive usability.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}