% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with 2+ years of experience in cloud infrastructure, DevOps automation, and full stack development. Proven expertise in AWS, Docker, Kubernetes, and GitLab CI/CD pipelines with hands-on experience in Infrastructure as Code using Terraform and CloudFormation. Skilled in Python, Bash scripting, and monitoring tools to ensure high availability and system reliability. Strong background in Agile methodologies, cross-functional collaboration, and delivering scalable solutions aligned with business objectives.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud \& Infrastructure:} AWS (EC2, S3, RDS, Lambda), Terraform, CloudFormation, Infrastructure as Code, VPC Configuration

\textbf{DevOps \& Automation:} Docker, Kubernetes, GitLab CI/CD, GitHub Actions, Jenkins, Continuous Deployment

\textbf{Programming \& Scripting:} Python, Bash, PowerShell, JavaScript, SQL

\textbf{Monitoring \& Security:} CloudWatch, OWASP, IAM Policies, Encryption, Security Best Practices

\textbf{Systems \& Databases:} Linux, PostgreSQL, MySQL, MongoDB, Database Administration

\textbf{Development Practices:} Agile, Scrum, Git, Code Reviews, Technical Documentation

\textbf{Soft Skills:} Problem Solving, Cross-Functional Collaboration, Communication, Adaptability, Ownership, Attention to Detail

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Deployed cloud-based applications on AWS using Docker, Kubernetes, and CI/CD pipelines ensuring high availability and 99.9\% uptime.
\item Implemented Infrastructure as Code with Terraform and CloudFormation to automate provisioning and reduce manual deployment time.
\item Monitored system performance using CloudWatch and optimized resource utilization improving application reliability and response times.
\item Collaborated with development teams through Agile sprints and code reviews to deliver scalable infrastructure solutions on schedule.
\item Automated deployment workflows using GitLab CI/CD and GitHub Actions reducing release cycles and improving deployment consistency.
\item Implemented security best practices including IAM policies, encryption, and vulnerability assessments ensuring compliance with standards.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in deploying enterprise applications on cloud infrastructure supporting both development and production environments.
\item Contributed to automation scripts using Python and Bash to streamline deployment processes and reduce manual configuration tasks.
\item Worked with cross-functional teams to gather infrastructure requirements, perform testing, and support production deployments.
\item Gained hands-on experience in cloud services, containerization, and DevOps practices within Agile development workflows.
\item Collaborated in project reviews to identify performance improvements, scalability enhancements, and infrastructure optimization opportunities.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS on AWS using Infrastructure as Code supporting 6K+ students with high availability and automated deployments.
\vspace{-1pt}
\begin{itemize}
\item Designed cloud architecture on AWS using EC2, RDS, and S3 with autoscaling and load balancing for high availability and performance.
\item Automated infrastructure provisioning using Terraform and deployed CI/CD pipelines with GitHub Actions for continuous delivery.
\item Implemented CloudWatch monitoring and alerting to track system health, resource utilization, and application performance metrics.
\item Configured security groups, IAM roles, and SSL encryption ensuring secure access and compliance with security best practices.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Deployed scalable real-time chat infrastructure on AWS using Docker and Kubernetes ensuring low-latency and high availability.
\vspace{-1pt}
\begin{itemize}
\item Deployed containerized application on AWS App Runner using Docker and Kubernetes for scalable, low-latency real-time communication.
\item Automated deployment pipelines using GitLab CI/CD reducing deployment time and ensuring consistent environment configurations.
\item Integrated AWS CloudWatch for monitoring, logging, and alerting to maintain system reliability and quickly resolve infrastructure issues.
\item Configured VPC networking, security groups, and IAM policies ensuring secure and isolated cloud infrastructure for production workloads.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}