% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Cloud Developer with hands-on experience designing, deploying, and maintaining scalable cloud-native applications on AWS, GCP, and Azure. Proficient in building RESTful APIs, microservices, and event-driven architectures using Python, JavaScript, and Node.js. Skilled in Infrastructure as Code (Terraform), containerization (Docker, Kubernetes), and CI/CD automation (GitHub Actions, GitLab CI/CD). Strong foundation in secure coding practices, cloud security, and observability with focus on reliability and performance optimization.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, TypeScript, Node.js, SQL, Bash, PowerShell, PHP

\textbf{Cloud Platforms \& Services:} AWS, Microsoft Azure, Google Cloud Platform, AWS Lambda, AWS S3, CloudWatch, IAM

\textbf{Backend Frameworks \& APIs:} Django, Flask, FastAPI, Express.js, REST API, GraphQL, Microservices, Event-Driven Architecture

\textbf{Databases \& Storage:} PostgreSQL, MySQL, MongoDB, DynamoDB, SQL Server, Redis, Firebase

\textbf{DevOps \& Infrastructure:} Docker, Kubernetes, Terraform, CI/CD, GitHub Actions, Jenkins, Infrastructure as Code

\textbf{Security \& Compliance:} OWASP, OAuth, JWT, Encryption, API Security, IAM Policies, Zero Trust Architecture

\textbf{Monitoring \& Observability:} CloudWatch, Cloud Monitoring, Logging, Performance Optimization, Load Testing, Autoscaling

\textbf{Soft Skills:} Communication, Collaboration, Ownership, Adaptability, Problem Solving, Continuous Improvement

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable cloud-native web applications using JavaScript, React, and Node.js, deployed on AWS with Docker and Kubernetes.
\item Designed and implemented RESTful APIs with secure authentication (OAuth, JWT) and optimized database queries for PostgreSQL and MySQL.
\item Built and maintained CI/CD pipelines using GitHub Actions and GitLab CI/CD, automating build, test, and deployment processes.
\item Integrated cloud-based payment systems with encryption and compliance controls, ensuring secure transaction processing.
\item Implemented observability through logging and monitoring with CloudWatch, improving application performance and uptime.
\item Collaborated with cross-functional teams in Agile sprints, conducting code reviews and mentoring developers on best practices.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to design and development of enterprise web applications using Python, JavaScript, and cloud-based infrastructure.
\item Assisted in building scalable backend services and RESTful APIs integrated with PostgreSQL and MongoDB databases.
\item Worked within Agile teams to gather requirements, perform integration testing, and support deployment activities.
\item Gained hands-on experience with Docker containerization and Infrastructure as Code principles for repeatable deployments.
\item Participated in code reviews and technical documentation efforts to improve maintainability and collaboration.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS on AWS supporting 6K+ students with secure authentication, real-time dashboards, and optimized performance.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a cloud-native LMS using React, Node.js, and MySQL deployed on AWS with autoscaling and load balancing.
\item Implemented secure role-based access control (JWT, OAuth) and encryption to protect user data and ensure compliance.
\item Integrated real-time progress tracking and analytics dashboards, optimizing database queries for high concurrent usage.
\item Deployed infrastructure using Terraform and CI/CD pipelines, achieving 99.9\% uptime with CDN caching and SSL encryption.
\end{itemize}

\textbf{PROSPR " Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive real-time chat application with accessibility features using AWS and Azure cloud services.
\vspace{-1pt}
\begin{itemize}
\item Built a cloud-native real-time chat application using React, Node.js, and Socket.io deployed on AWS App Runner with Docker.
\item Integrated Azure Speech Services and AWS Polly APIs for text-to-speech and voice-to-text accessibility features.
\item Followed WCAG standards and conducted testing with assistive technologies to ensure inclusive and accessible design.
\item Implemented Infrastructure as Code (Terraform) and CI/CD automation for scalable, low-latency deployment across regions.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}