% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Software Engineer with strong foundations in cybersecurity, cloud infrastructure, and systems automation. Experienced in developing secure full stack applications, implementing vulnerability management workflows, and automating security processes using Python, AWS, and CI/CD pipelines. Adept at incident response, threat analysis, and collaborating across teams to deliver scalable solutions. Passionate about applying technical skills to cybersecurity investigations and continuously learning emerging threats and technologies.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming \& Scripting:} Python, JavaScript, Bash, PowerShell, SQL

\textbf{Cybersecurity \& Security Operations:} Incident Response, Threat Intelligence, SIEM, Vulnerability Management, OWASP, Digital Forensics

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, CI/CD, GitHub Actions

\textbf{Networking \& Systems:} TCP/IP, VPN, Active Directory, Linux, Windows Server

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQL Server

\textbf{Frameworks \& Libraries:} React, Django, Node.js, Bootstrap

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Accountability, Customer Service

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed secure full stack web applications using JavaScript, React, and Node.js while implementing OWASP best practices.
\item Integrated authentication systems, secure payment processing, and SQL injection prevention to enhance application security.
\item Deployed cloud applications on AWS with Docker and CI/CD pipelines, ensuring consistent uptime and rapid incident response.
\item Collaborated across Agile teams through code reviews and sprint planning, ensuring secure and high-quality deliverables.
\item Applied secure coding standards and vulnerability assessments throughout SDLC to reduce production security risks.
\item Mentored junior developers on secure deployment practices, threat mitigation, and monitoring for emerging vulnerabilities.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise applications with focus on secure coding, authentication, and access control mechanisms.
\item Contributed to secure design and implementation of Proposal Management and Mailroom Tracking Systems with IAM integration.
\item Collaborated with cross functional teams to gather requirements, perform security testing, and support secure deployments.
\item Gained hands-on experience in vulnerability assessments, secure SDLC practices, and incident documentation within Agile workflows.
\item Participated in project reviews to identify security improvements, performance optimization, and threat mitigation strategies.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic }

\vspace{-1pt}

Automated vulnerability scanning and patching to strengthen enterprise security and reduce manual effort.
\vspace{-1pt}
\begin{itemize}
\item Developed automated workflows using Python and Jenkins for continuous vulnerability scanning and patch deployment cycles.
\item Integrated Nessus API for real-time vulnerability reporting, risk prioritization, and compliance tracking across infrastructure.
\item Created dashboards and alert systems to monitor security compliance, remediation progress, and incident response metrics.
\item Reduced manual intervention by 60\% and accelerated patch cycles through full CI/CD automation and threat intelligence feeds.
\end{itemize}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL with secure authentication and role-based access.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time progress dashboards for teachers.
\item Implemented OAuth, JWT authentication, and optimized database queries to support high concurrent usage and data security.
\item Deployed the platform on AWS with CDN caching, SSL encryption, and monitoring, ensuring reliable access for 6,000+ students.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}