% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Software Engineer with 2+ years of hands-on experience in full stack development, cloud infrastructure, and security-focused system design. Proven ability to analyze technical risks, collaborate with cross-functional teams, and translate complex security concerns into actionable engineering solutions. Skilled in AWS, GCP, Docker, Kubernetes, and CI/CD automation with demonstrated experience in vulnerability assessment, secure coding practices, and implementing security controls across development workflows.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming \& Scripting:} Python, JavaScript, SQL, Bash, PowerShell, HTML/CSS

\textbf{Cloud \& Infrastructure:} AWS, Google Cloud Platform, Docker, Kubernetes, IAM, VPC

\textbf{Security \& Compliance:} Threat Intelligence, Incident Response, Risk Assessments, OWASP, API Security, Encryption

\textbf{DevOps \& Automation:} CI/CD Pipelines, GitHub Actions, GitLab CI/CD, Infrastructure as Code, Automation Testing

\textbf{Data \& Analysis:} PostgreSQL, MongoDB, ETL Pipelines, Data Visualization, BigQuery, Pandas

\textbf{Frameworks \& Tools:} React, Django, Node.js, SIEM, Jira, MITRE ATT\&CK

\textbf{Soft Skills:} Communication, Collaboration, Analytical Thinking, Adaptability, Problem Solving, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed secure full stack applications using React, Node.js, and Python, implementing OAuth, JWT, and encryption best practices.
\item Designed and optimized RESTful APIs and SQL queries while integrating security controls including XSS prevention and input validation.
\item Deployed cloud applications on AWS and GCP using Docker, Kubernetes, and CI/CD pipelines ensuring high availability and uptime.
\item Collaborated with cross-functional teams through Agile workflows, code reviews, and sprint planning to deliver secure, scalable solutions.
\item Applied secure SDLC practices and test-driven development reducing production vulnerabilities and improving overall system reliability.
\item Mentored junior developers on secure coding standards, cloud security configurations, and deployment automation best practices.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise applications with focus on secure authentication, authorization, and data protection mechanisms.
\item Contributed to design and implementation of tracking systems while identifying and documenting security requirements and controls.
\item Worked with teams to gather requirements, perform security testing, and validate control effectiveness throughout deployment phases.
\item Gained experience in full stack development, vulnerability assessment, and implementing security best practices within Agile workflows.
\item Participated in project reviews identifying performance, security, and scalability improvements across application architecture.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic }

\vspace{-1pt}

Automated vulnerability scanning and patching workflows to strengthen enterprise security posture and reduce manual remediation effort.
\vspace{-1pt}
\begin{itemize}
\item Developed automated vulnerability management workflows using Python and Jenkins for continuous scanning and prioritized patch deployment.
\item Integrated Nessus API for real-time vulnerability reporting, risk scoring, and automated remediation tracking across enterprise systems.
\item Created security dashboards and alerting mechanisms to monitor compliance status, track remediation progress, and surface control gaps.
\item Reduced manual security intervention by 60\% and accelerated patch cycles through fully automated CI/CD security integration.
\end{itemize}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a secure, scalable LMS supporting 6,000+ students with role-based access, encrypted data transmission, and cloud deployment.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed full stack LMS using React, Node.js, and MySQL implementing secure authentication and role-based authorization.
\item Integrated lesson management, quiz modules, and real-time progress tracking with encrypted data storage and secure API communication.
\item Implemented security controls including input validation, session management, and SQL injection prevention across all application layers.
\item Deployed on AWS with SSL encryption, CDN caching, and CloudWatch monitoring ensuring reliable, secure access for 6,000+ concurrent users.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}