% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Software Engineer with strong expertise in Python development, cloud infrastructure, and security automation. Skilled in building scalable applications using JavaScript, React, Node.js, and AWS with hands-on experience in secure coding, vulnerability management, and threat intelligence. Proven ability to design automated workflows, integrate APIs, and implement security best practices across enterprise systems. Adept at collaborating with cross-functional teams to deliver high-quality solutions aligned with security frameworks and compliance standards.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, SQL, Bash, PowerShell, PHP

\textbf{AI \& Machine Learning:} Machine Learning APIs, LLM API, ChatGPT API, Prompt Engineering, AI Integration, pandas

\textbf{Security \& Threat Intelligence:} MITRE ATT\&CK, SIEM, Threat Intelligence, Incident Response, Vulnerability management tools, Malware analysis

\textbf{Cloud \& Infrastructure:} AWS, GCP, Microsoft Azure, Docker, Kubernetes, Terraform

\textbf{Automation \& DevOps:} CI/CD, GitHub Actions, Jenkins, Infrastructure as Code, Workflow Automation, Scripting

\textbf{Data \& Analytics:} PostgreSQL, MongoDB, ETL Pipelines, BigQuery, Data Visualization, SQL Server

\textbf{Security Frameworks \& Standards:} Zero Trust Architecture, OWASP, API Security, IAM, Encryption, TLS

\textbf{Soft Skills:} Collaboration, Problem Solving, Adaptability, Communication, Analytical Thinking, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using Python, JavaScript, React, and Node.js with automated testing and secure coding standards.
\item Implemented RESTful APIs and optimized database queries for PostgreSQL and MySQL improving system performance and reliability.
\item Deployed cloud-based applications on AWS using Docker, Kubernetes, and CI/CD pipelines ensuring high availability and uptime.
\item Collaborated with cross-functional teams using Agile methodology and code reviews to deliver secure, high-quality solutions.
\item Applied security best practices including authentication, encryption, and vulnerability assessment throughout the SDLC lifecycle.
\item Mentored junior developers on secure coding, automated workflows, and cloud deployment strategies improving team productivity.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise applications across frontend and backend using secure coding and testing practices.
\item Contributed to the design of systems including Proposal Management and Mailroom Tracking with performance optimization focus.
\item Worked with cross-functional teams to gather requirements, conduct testing, and support secure deployment workflows.
\item Gained hands-on experience in full stack development, cloud infrastructure, and security integration within Agile teams.
\item Collaborated in project reviews to identify improvements in system scalability, performance, and code maintainability standards.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic }

\vspace{-1pt}

Automated vulnerability scanning and patching workflows to strengthen enterprise security and reduce manual remediation effort.
\vspace{-1pt}
\begin{itemize}
\item Developed automated workflows using Python and Jenkins for continuous vulnerability scanning and patch deployment automation.
\item Integrated Nessus API for real-time vulnerability reporting, risk prioritization, and compliance tracking across systems.
\item Created security dashboards and alert systems to monitor compliance status and accelerate remediation progress tracking.
\item Reduced manual security operations by 60\% and accelerated patch cycles through full CI/CD automation implementation.
\end{itemize}

\textbf{Automated Cryptocurrency Trading Bot} -- \emph{Personal Project}

\vspace{-1pt}

Created a Python trading bot with API integration and real-time data streaming for automated trade execution and risk control.
\vspace{-1pt}
\begin{itemize}
\item Developed a fully automated trading bot in Python using Binance API and WebSocket for real-time market data streaming.
\item Implemented dynamic trading strategies, stop-loss mechanisms, and automated order execution algorithms for risk management.
\item Integrated pandas and NumPy for market analysis, backtesting, and improving trading accuracy through data-driven insights.
\item Deployed using Docker on AWS EC2 for 24/7 uptime, reliability, and comprehensive monitoring with detailed logging infrastructure.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}