% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Software Engineer with hands-on experience in full stack development, cloud infrastructure, and cybersecurity automation. Proficient in Python scripting, AWS cloud services, and CI/CD pipelines with a proven track record of implementing secure systems and automating workflows. Experienced in vulnerability management, incident response, and collaborating across teams in Agile environments to protect intellectual property while maintaining operational efficiency.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming \& Scripting:} Python, Bash, PowerShell, JavaScript, SQL

\textbf{Cloud \& Infrastructure:} AWS, Docker, Kubernetes, Infrastructure as Code, Terraform

\textbf{Security \& Compliance:} Vulnerability Management, Incident Response, OWASP, Threat Intelligence, SIEM

\textbf{DevOps \& Automation:} CI/CD, GitHub Actions, Jenkins, Automation Testing, GitLab CI/CD

\textbf{Networking \& Systems:} Linux System Administration, Windows Server, VPN, Networking Principles, Active Directory

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Problem Solving, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed secure full stack applications using JavaScript, React, and Node.js while implementing OWASP security standards throughout SDLC.
\item Deployed and maintained cloud infrastructure on AWS using Docker and CI/CD pipelines ensuring 99.9\% uptime and rapid incident response.
\item Automated patching workflows and security updates using Python scripts reducing manual intervention and accelerating remediation cycles.
\item Collaborated with cross functional teams in Agile sprints to balance security requirements with innovation and development velocity.
\item Conducted code reviews and implemented secure coding practices to protect intellectual property and mitigate vulnerabilities.
\item Monitored application performance and security alerts using CloudWatch and logging tools to ensure proactive threat detection.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise applications while learning security best practices and vulnerability assessment methodologies.
\item Contributed to system design and testing phases ensuring alignment with security policies and operational requirements.
\item Worked closely with cross functional teams to document technical processes and support disaster recovery planning initiatives.
\item Gained hands-on experience in secure SDLC, application security audits, and implementing necessary security controls.
\item Participated in Agile workflows and project reviews to identify performance improvements and security enhancements.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic }

\vspace{-1pt}

Automated vulnerability scanning and patching workflows to strengthen enterprise security posture and reduce manual remediation effort.
\vspace{-1pt}
\begin{itemize}
\item Developed automated vulnerability scanning and patch deployment workflows using Python, Jenkins, and CI/CD pipelines for enterprise systems.
\item Integrated Nessus API for real-time vulnerability reporting, risk prioritization, and detailed incident documentation across all endpoints.
\item Created centralized dashboards and alert systems to track security compliance, patch status, and remediation progress in real time.
\item Reduced manual intervention by 60\% and accelerated patch cycles through full automation without disrupting critical user workflows.
\end{itemize}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable and secure LMS on AWS supporting 6K+ students with encrypted data, role-based access, and high availability infrastructure.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack LMS using React, Node.js, and MySQL with secure authentication, role-based access control, and encrypted data transmission.
\item Deployed on AWS using EC2, S3, and RDS with CDN caching, SSL encryption, and automated backups for disaster recovery and high availability.
\item Implemented monitoring and logging using CloudWatch to track performance, detect anomalies, and ensure rapid incident response capabilities.
\item Optimized database queries and implemented caching strategies to support over 6,000 concurrent users with minimal latency and downtime.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}