% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with proven experience in full stack development, data integration, and cloud infrastructure. Skilled in Python, JavaScript, SQL, and Power BI with hands-on expertise in building scalable applications, automating workflows, and transforming data into actionable insights. Experienced in Agile environments, collaborating with cross-functional teams to deliver high-quality solutions that drive operational efficiency and business outcomes.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, SQL, PHP, HTML, CSS

\textbf{Data \& Analytics:} Power BI, ETL Pipelines, Data Visualization, BigQuery, Data Modeling, DAX

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQLite, Database Design

\textbf{Cloud \& DevOps:} AWS, GCP, Docker, Kubernetes, CI/CD, GitHub Actions

\textbf{Frameworks \& Tools:} React, Node.js, Django, Flask, FastAPI, REST API

\textbf{Software Development Practices:} Agile, Scrum, Testing, Automation, SDLC, Requirements Analysis

\textbf{Soft Skills:} Analytical Thinking, Communication, Team Collaboration, Problem Solving, Adaptability, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js to enhance functionality and user experience.
\item Implemented RESTful APIs, optimized SQL queries, and integrated secure systems to improve reliability and operational performance.
\item Deployed and maintained cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and availability.
\item Collaborated within Agile teams through code reviews, sprint planning, and cross-functional communication to deliver quality outcomes.
\item Applied test-driven development and secure coding standards throughout SDLC improving maintainability and reducing production issues.
\item Led backend development for multiple applications while mentoring junior developers on best coding and deployment best practices.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web and mobile applications across both frontend and backend components using modern frameworks.
\item Contributed to the design and implementation of the Proposal Management and Mailroom Tracking Systems for operational efficiency.
\item Worked closely with cross-functional teams to gather requirements, perform user acceptance testing, and support deployment phases.
\item Gained hands-on experience in full stack development, software testing, and secure coding practices within Agile workflows.
\item Collaborated in project reviews to identify improvements in performance, scalability, and code quality for ongoing initiatives.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with notes, videos, and interactive quizzes using modern web technologies.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full-stack LMS using React, Node.js, and MySQL to support online education with interactive features.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards for educators and students.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent user activity.
\item Deployed the platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 active student users.
\end{itemize}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Automated vulnerability scanning and patching to strengthen enterprise security and reduce manual operational effort significantly.
\vspace{-1pt}
\begin{itemize}
\item Developed automated workflows using Python and Jenkins for vulnerability scanning and patch deployment across infrastructure.
\item Integrated Nessus API for real-time vulnerability reporting and risk prioritization enabling proactive security response measures.
\item Created dashboards and alert systems to track security compliance and remediation progress for stakeholders and security teams.
\item Reduced manual intervention by 60\% and accelerated patch cycles through full CI/CD automation and streamlined deployment pipelines.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}