% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Web Developer with proven expertise in Python, SQL, and data visualization tools including Power BI. Skilled in building scalable web applications, designing analytics dashboards, and automating data workflows using cloud platforms like AWS and GCP. Strong analytical mindset with hands-on experience in database design, API integration, and cross-functional collaboration within Agile teams. Committed to delivering data-driven solutions that support strategic business objectives.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, SQL, PHP, HTML, CSS

\textbf{Data \& Analytics:} Power BI, Excel, Data Visualization, ETL Pipelines, BigQuery, Chart.js

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, Database Design, SQL Queries

\textbf{Frameworks \& Libraries:} React, Django, Node.js, Bootstrap, Flask, FastAPI

\textbf{Cloud \& DevOps:} AWS, GCP, Docker, CI/CD, GitHub Actions, Cloud Monitoring

\textbf{Software Development Practices:} Agile, Scrum, SDLC, Testing, Debugging, Technical Documentation

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Attention to Detail, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js to support business analytics and reporting.
\item Designed and optimized SQL queries and database schemas across PostgreSQL and MySQL to improve data integrity and performance.
\item Built interactive dashboards and data visualizations using Power BI and Chart.js to communicate actionable insights to stakeholders.
\item Deployed cloud-based applications on AWS with Docker and CI/CD pipelines ensuring high availability and consistent uptime.
\item Collaborated within Agile teams through code reviews, sprint planning, and pair programming to deliver high-quality solutions.
\item Led development of data-driven web applications while mentoring junior developers on best practices and technical standards.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level web applications with a focus on data management and reporting functionalities.
\item Contributed to the design and implementation of business intelligence dashboards for operational tracking and insights.
\item Worked closely with cross-functional teams to gather requirements, perform user acceptance testing, and support deployments.
\item Gained hands-on experience in full stack development, SQL database design, and analytics workflows within Agile environments.
\item Collaborated in project reviews to identify improvements in data accuracy, system performance, and reporting capabilities.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS platform enabling 6K+ students to access lessons, quizzes, and performance tracking dashboards online.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL to deliver online education at scale.
\item Integrated real-time performance dashboards and analytics for teachers to monitor student progress and engagement metrics.
\item Implemented secure authentication, role-based access control, and optimized SQL queries for high concurrent user activity.
\item Deployed the platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 active students.
\end{itemize}

\textbf{Custom Business Web Solutions} -- \emph{Personal Project}

\vspace{-1pt}

Built POS systems, e-commerce sites, and inventory management solutions with secure design and workflow automation features.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed custom web solutions using React, Next.js, and Express.js tailored to client business requirements.
\item Implemented secure authentication, inventory tracking dashboards, and payment processing with Stripe API integration.
\item Collaborated with clients to gather requirements and translate business needs into scalable data-driven applications.
\item Optimized UI performance, responsiveness, and data presentation across all projects to enhance user engagement and insights.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}