% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with 4+ years of experience designing and deploying scalable data pipelines, AI-powered solutions, and cloud-based applications. Proficient in Python, SQL, and full stack development with hands-on experience integrating AI/ML technologies, including ChatGPT API and machine learning models. Proven expertise in building automated workflows, optimizing data architectures, and delivering secure, high-performance systems using AWS, Docker, and CI/CD pipelines. Adept at collaborating with cross-functional teams in Agile environments to deliver compliant, data-driven solutions.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming \& Scripting:} Python, SQL, Bash, JavaScript, PowerShell

\textbf{AI \& Machine Learning:} ChatGPT API, LLM Integration, Prompt Engineering, Machine Learning APIs, NLP Models

\textbf{Data Engineering \& Analytics:} ETL Pipelines, Data Warehousing, BigQuery, pandas, Data Visualization

\textbf{Databases \& Query Optimization:} PostgreSQL, MySQL, MongoDB, SQL Server, SQLite

\textbf{Cloud \& Infrastructure:} AWS, Docker, Kubernetes, Terraform, CI/CD Pipelines

\textbf{Development Frameworks:} Django, Flask, FastAPI, React, Node.js

\textbf{Systems \& Environments:} Unix/Linux, Ubuntu, Shell Scripting, Automation, System Design

\textbf{Soft Skills:} Problem Solving, Communication, Collaboration, Adaptability, Continuous Learning, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable data pipelines and AI-powered applications using Python, SQL, and React to enhance system reliability and performance.
\item Integrated ChatGPT API and machine learning models into production workflows to automate data processing and reporting tasks effectively.
\item Optimized SQL queries and database architectures for large datasets, reducing processing time and improving data quality and accuracy.
\item Deployed cloud-based solutions using AWS, Docker, and CI/CD pipelines, ensuring high availability and consistent uptime for critical systems.
\item Collaborated within Agile teams through code reviews, sprint planning, and technical documentation to deliver compliant, scalable solutions.
\item Led backend development initiatives and mentored junior engineers on data engineering best practices, automation, and secure coding standards.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in building enterprise data solutions and web applications across frontend and backend components using Python and JavaScript.
\item Contributed to design and implementation of data-driven systems including Proposal Management and Mailroom Tracking Systems with SQL integration.
\item Worked closely with cross-functional teams to gather requirements, perform testing, and support deployment phases in Agile environments.
\item Gained hands-on experience in full stack development, data analysis, software testing, and secure coding within structured SDLC workflows.
\item Collaborated in project reviews to identify improvements in performance, scalability, data accuracy, and code maintainability across systems.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Automated Cryptocurrency Trading Bot} -- \emph{Personal Project}

\vspace{-1pt}

Created a Python trading bot using Binance API and WebSocket to automate trade execution with risk control and live monitoring.
\vspace{-1pt}
\begin{itemize}
\item Developed a fully automated trading bot in Python using Binance API and WebSocket for real-time data streaming and decision-making.
\item Implemented dynamic trading strategies, stop-loss mechanisms, and order execution algorithms using pandas and NumPy for market analysis.
\item Integrated backtesting workflows to validate trading accuracy and optimize performance before deploying strategies in live environments.
\item Deployed using Docker on AWS EC2 for 24/7 uptime, reliability, and monitoring with detailed logging and automated error handling.
\end{itemize}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Automated vulnerability scanning and patching to strengthen enterprise security and reduce manual effort using Python workflows.
\vspace{-1pt}
\begin{itemize}

\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}