% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with 3+ years of experience building scalable data pipelines, full stack applications, and cloud-based solutions using Python, JavaScript, and SQL. Proven expertise in AWS, Docker, and CI/CD automation with hands-on experience integrating third-party APIs and optimizing database performance. Skilled in collaborating with cross-functional teams to translate complex business requirements into reliable, production-ready systems. Adept at Agile methodologies and passionate about delivering high-quality, maintainable code.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, SQL, Bash, PowerShell, PHP

\textbf{Frameworks \& Libraries:} Django, Flask, FastAPI, React, Node.js, pandas

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQL optimization, ETL pipelines, data quality monitoring

\textbf{Cloud \& DevOps:} AWS, Docker, Jenkins, Git, CI/CD, CloudWatch

\textbf{Software Development Practices:} Agile, Scrum, code reviews, testing, SDLC, version control

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Analytical Thinking, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable data pipelines and APIs using Python, Django, and Node.js to support analytics and business intelligence workflows.
\item Optimized complex SQL queries and database schemas across PostgreSQL and MySQL, improving query performance by reducing execution time.
\item Deployed cloud-based applications on AWS using Docker, Jenkins, and CI/CD pipelines ensuring 99.9\% uptime and automated deployments.
\item Collaborated with business teams and analysts to gather requirements, implement business logic, and deliver insights through dashboards.
\item Integrated third-party APIs including payment gateways and data providers, ensuring secure and reliable data exchange across systems.
\item Applied Agile methodologies, conducted code reviews, and mentored junior developers on best practices for testing and deployment.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in building enterprise web applications using Python, JavaScript, and SQL with a focus on backend data processing and APIs.
\item Contributed to designing and implementing scalable solutions for proposal management and tracking systems supporting business operations.
\item Worked with cross-functional teams to gather requirements, perform testing, troubleshoot data issues, and support production deployments.
\item Gained hands-on experience in Git version control, Docker containerization, and Agile workflows to deliver high-quality software releases.
\item Collaborated in sprint reviews to identify performance bottlenecks and recommend improvements for scalability and code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS using Python and React, enabling 6,000+ students to access lessons, quizzes, and real-time progress tracking.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full-stack LMS using React, Node.js, and MySQL to support online education during the pandemic with 6K+ users.
\item Implemented secure authentication, role-based access control, and optimized SQL queries to handle high concurrent user sessions efficiently.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards for teachers and administrators.
\item Deployed the platform on AWS with Docker, CDN caching, SSL encryption, and CloudWatch monitoring for reliable uptime and performance.
\end{itemize}

\textbf{Automated Cryptocurrency Trading Bot} -- \emph{Personal Project}

\vspace{-1pt}

Created a Python trading bot using Binance API and WebSocket for real-time data streaming, automated execution, and risk management.
\vspace{-1pt}
\begin{itemize}
\item Developed a fully automated trading bot in Python using Binance API, WebSocket, and pandas for real-time market data analysis and execution.
\item Implemented dynamic trading strategies, stop-loss mechanisms, and risk controls to manage order execution and minimize trading losses.
\item Integrated NumPy and pandas for backtesting historical market data, improving accuracy and strategy performance over multiple iterations.
\item Deployed using Docker on AWS EC2 for 24/7 uptime with CloudWatch logging and monitoring to track bot performance and trading activity.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}