% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Data Analyst with strong expertise in Python, SQL, and Power BI, specializing in transforming complex datasets into actionable insights that enhance customer experience and drive business decisions. Proven ability to develop dashboards, analyze customer behavior patterns, and collaborate with cross-functional teams to deliver data-driven solutions. Experienced in leveraging cloud platforms, ETL pipelines, and visualization tools to monitor KPIs and inform strategic improvements across diverse industries.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming \& Scripting:} Python, SQL, JavaScript, PHP, Bash, PowerShell

\textbf{Data Analysis \& Visualization:} Power BI, Chart.js, Data Visualization, Google Data Studio, Statistical Analysis

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, BigQuery, ETL Pipelines, Data Warehousing

\textbf{Cloud \& DevOps:} AWS, GCP, Microsoft Azure, Docker, CI/CD, GitHub Actions

\textbf{Frameworks \& Libraries:} Django, Flask, FastAPI, React, Node.js, Bootstrap

\textbf{AI \& Machine Learning:} Machine Learning APIs, AI Integration, LLM API, ChatGPT API, Prompt Engineering

\textbf{Soft Skills:} Analytical Thinking, Problem Solving, Communication, Team Collaboration, Adaptability

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Analyzed large datasets using Python and SQL to identify customer behavior patterns and pain points driving product improvements.
\item Developed interactive dashboards and reports using Power BI and visualization tools to present insights to stakeholders clearly.
\item Created optimized SQL queries to extract, manipulate, and analyze data from PostgreSQL and MySQL databases for decision support.
\item Collaborated with cross-functional teams through Agile workflows to implement data-driven solutions enhancing customer experience.
\item Monitored key performance indicators and customer experience metrics to inform strategic business and product development decisions.
\item Deployed cloud-based analytics solutions on AWS and GCP using Docker and CI/CD pipelines ensuring scalability and reliability.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in collecting, processing, and analyzing datasets to support enterprise reporting and customer experience improvements.
\item Contributed to dashboard development and data visualization efforts using Python and SQL for stakeholder presentations.
\item Worked closely with cross-functional teams to gather requirements, perform data testing, and support analytics deployment phases.
\item Gained hands-on experience in statistical analysis, hypothesis testing, and data extraction within Agile development workflows.
\item Collaborated in project reviews to identify data quality improvements and optimize performance for scalability and accuracy.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling data-driven insights for 6K+ students through performance tracking and interactive analytics dashboards.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full-stack LMS using React, Node.js, and MySQL to analyze student engagement and learning outcomes data.
\item Integrated real-time dashboards for teachers to track performance metrics, quiz results, and student progress using visualization tools.
\item Implemented secure authentication and optimized SQL queries to handle high concurrent usage and extract meaningful insights efficiently.
\item Deployed on AWS with monitoring and logging to ensure reliable data access and performance tracking for over 6,000 active students.
\end{itemize}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Automated vulnerability scanning and reporting using Python to analyze security data and reduce manual effort by 60 percent.
\vspace{-1pt}
\begin{itemize}
\item Developed automated workflows using Python and Jenkins to extract, process, and analyze vulnerability data from security scans.
\item Integrated Nessus API for real-time data reporting and risk prioritization using statistical analysis and hypothesis testing methods.
\item Created interactive dashboards and alert systems to visualize security compliance metrics and track remediation progress clearly.
\item Reduced manual data processing by 60\% through full CI/CD automation enabling faster security decision-making and patching cycles.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}