% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with expertise in backend development, database management, and automation. Proven ability to design and optimize database environments, implement secure architectures, and automate workflows using Python, SQL, and scripting. Experienced in cloud infrastructure, vulnerability management, and system performance tuning. Adept at collaborating with cross-functional teams to deliver reliable solutions in Agile environments. Strong analytical and problem-solving skills with a commitment to operational excellence.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, SQL, Bash, PowerShell, JavaScript, PHP

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, Database Administration, Database Design, SQL Server

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, CI/CD, Infrastructure as Code, Automation

\textbf{Security \& Compliance:} Vulnerability Management, OWASP, Incident Response, Risk Assessments, Encryption, IAM

\textbf{Systems \& Networking:} Linux, Windows Server Administration, Networking Principles, Monitoring, Logging

\textbf{Software Development Practices:} Agile, Scrum, Testing, Debugging, Technical Documentation, SDLC

\textbf{Soft Skills:} Analytical Thinking, Problem Solving, Communication, Collaboration, Adaptability, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js to enhance system functionality and reliability.
\item Implemented RESTful APIs, optimized SQL queries, and integrated secure payment systems improving database performance and security.
\item Deployed and maintained cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and high availability.
\item Collaborated within Agile teams through code reviews, sprint planning, and pair programming to deliver high-quality technical solutions.
\item Applied secure coding standards and test-driven development throughout SDLC reducing production issues and improving maintainability.
\item Led backend development for multiple applications while mentoring junior developers on coding best practices and deployment strategies.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level web applications with both frontend and backend components supporting business operations.
\item Contributed to the design and implementation of Proposal Management and Mailroom Tracking Systems using structured development processes.
\item Worked closely with cross-functional teams to gather requirements, perform testing, and support deployment phases ensuring project success.
\item Gained hands-on experience in full stack development, software testing, and secure coding within Agile workflows and team environments.
\item Collaborated in project reviews to identify improvements in performance, scalability, and code maintainability across multiple systems.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Automated vulnerability scanning and patching workflows to strengthen enterprise security posture and reduce manual effort significantly.
\vspace{-1pt}
\begin{itemize}
\item Developed automated workflows using Python and Jenkins for vulnerability scanning and patch deployment improving security operations efficiency.
\item Integrated Nessus API for real-time vulnerability reporting and risk prioritization enabling proactive threat mitigation and compliance tracking.
\item Created dashboards and alert systems to track security compliance and remediation progress ensuring timely resolution of identified vulnerabilities.
\item Reduced manual intervention by 60\% and accelerated patch cycles through full CI/CD automation increasing operational reliability and security posture.
\end{itemize}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling over 6,000 students to learn with notes, videos, and interactive quizzes efficiently.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full-stack LMS using React, Node.js, and MySQL to support online education during the pandemic with high availability.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards for teachers improving educational outcomes.
\item Implemented secure authentication, role-based access, and optimized database queries for high concurrent usage ensuring data integrity and performance.
\item Deployed the platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 students with minimal downtime.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}