% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with hands-on experience in data engineering, ETL pipeline development, and cloud-based analytics solutions. Proficient in SQL, Python, and building scalable data workflows using modern tools and frameworks. Skilled in designing data models, optimizing queries, and collaborating with cross-functional teams to deliver high-quality insights. Experienced in AWS, Docker, CI/CD automation, and Agile methodologies with a focus on data integrity and performance optimization.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, SQL, JavaScript, PHP, Bash, PowerShell

\textbf{Data Engineering \& Analytics:} ETL Pipelines, Data Warehousing, Data Visualization, Power BI, BigQuery, Data Modeling

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQLite, Database Design, Query Optimization

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, CI/CD, GitHub Actions, Terraform

\textbf{Frameworks \& Libraries:} Django, Flask, FastAPI, React, Node.js, Pandas, NumPy

\textbf{Software Development Practices:} Agile, Scrum, Requirements Analysis, Testing, SDLC, Technical Documentation

\textbf{Soft Skills:} Collaboration, Communication, Problem Solving, Adaptability, Analytical Thinking, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable data pipelines and analytics solutions using Python, SQL, and cloud technologies to support business insights.
\item Optimized complex SQL queries and database performance improving data retrieval efficiency and supporting real-time reporting needs.
\item Deployed cloud-based applications on AWS using Docker and CI/CD pipelines ensuring high availability and consistent performance.
\item Collaborated with cross-functional teams in Agile workflows through sprint planning and code reviews to deliver quality solutions.
\item Integrated RESTful APIs and built data workflows supporting analytics dashboards and business intelligence tools like Power BI.
\item Applied best practices in data integrity, testing, and documentation throughout the software development lifecycle.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing data-driven applications across frontend and backend components supporting enterprise analytics requirements.
\item Contributed to designing and implementing systems for tracking and reporting using structured data models and SQL databases.
\item Worked with cross-functional teams to gather requirements, perform data validation, and support deployment phases.
\item Gained hands-on experience in ETL processes, data transformation, and analytics workflows within Agile development environments.
\item Collaborated in project reviews identifying improvements in data quality, performance optimization, and system scalability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS with data pipelines for analytics, real-time tracking, and structured reporting for over 6,000 students.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed full-stack LMS using React, Node.js, and MySQL with optimized data models for performance tracking.
\item Integrated data collection modules for quizzes and progress tracking with real-time analytics dashboards for instructors.
\item Implemented secure authentication, role-based access, and optimized SQL queries to handle high concurrent user activity.
\item Deployed platform on AWS with CDN caching and SSL encryption ensuring reliable data access for thousands of active users.
\end{itemize}

\textbf{Automated Cryptocurrency Trading Bot} -- \emph{Personal Project}

\vspace{-1pt}

Created a Python-based trading bot with real-time data ingestion, transformation, and automated analytics using APIs and libraries.
\vspace{-1pt}
\begin{itemize}
\item Developed automated trading bot in Python using Binance API and WebSocket for real-time data streaming and transformation.
\item Implemented dynamic algorithms, data processing workflows, and risk control mechanisms to optimize trade execution accuracy.
\item Integrated Pandas and NumPy for market data analysis, backtesting strategies, and generating actionable trading insights.
\item Deployed using Docker on AWS EC2 for continuous uptime with detailed logging and monitoring for reliability and performance.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}