% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Detail-oriented Software Engineer with strong expertise in full stack development, data architecture, and cloud infrastructure. Skilled in SQL, Python, JavaScript, and analytics workflows using PostgreSQL, MySQL, and AWS. Experienced building scalable systems, integrating APIs, and collaborating cross-functionally to deliver actionable insights and data-driven solutions. Adept at translating complex technical concepts into clear, business-focused narratives for diverse stakeholders.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, SQL, JavaScript, Bash, PowerShell, PHP

\textbf{Frameworks \& Libraries:} React, Django, Node.js, pandas, Flask

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQLite, Data Warehousing, ETL Pipelines

\textbf{Cloud \& DevOps:} AWS, GCP, Docker, Kubernetes, CI/CD, GitLab

\textbf{Data Analytics \& Visualization:} BigQuery, Power BI, Chart.js, Data Visualization, Google Data Studio

\textbf{Development Practices:} Agile, Scrum, Requirements Analysis, Testing, Technical Documentation

\textbf{Systems \& Networking:} Cloud Computing, Linux, Security Best Practices, API Gateway, Networking

\textbf{Soft Skills:} Communication, Problem Solving, Collaboration, Adaptability, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web and e-commerce applications using JavaScript, React, and Node.js to enhance business functionality.
\item Implemented RESTful APIs, optimized SQL queries, and integrated secure payment systems to improve performance and reliability.
\item Deployed cloud applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and streamlined operations.
\item Collaborated within Agile teams through code reviews, sprint planning, and pair programming to deliver high-quality solutions.
\item Applied test-driven development and secure coding standards throughout SDLC improving maintainability and reducing issues.
\item Led backend development for multiple applications while mentoring junior developers on best coding and deployment practices.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level web and mobile applications across both frontend and backend components.
\item Contributed to the design and implementation of Proposal Management and Mailroom Tracking Systems for operational efficiency.
\item Worked closely with cross-functional teams to gather requirements, perform testing, and support deployment phases effectively.
\item Gained hands-on experience in full stack development, software testing, and secure coding within Agile workflows.
\item Collaborated in project reviews to identify improvements in performance, scalability, and code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full-stack LMS using React, Node.js, and MySQL to support online education during the pandemic.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards for teachers.
\item Implemented secure authentication, role-based access, and optimized database queries for high concurrent usage.
\item Deployed the platform on AWS with CDN caching and SSL encryption, ensuring reliable access for over 6,000 students.
\end{itemize}

\textbf{Custom Business Web Solutions} -- \emph{Personal Project}

\vspace{-1pt}

Built POS, e-commerce sites, landing pages, and inventory systems with secure, responsive web design improving workflow efficiency.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed multiple custom web solutions using React, Next.js, and Express.js for diverse business needs.
\item Implemented secure authentication, inventory tracking, and payment processing with Stripe API integration.
\item Collaborated with clients to gather requirements and translate business needs into scalable, data-driven applications.
\item Optimized UI performance, responsiveness, and SEO across all client projects to enhance user engagement and metrics.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}