% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with 3+ years of experience in full stack development, cloud platforms, and data-driven solutions. Proficient in Python, JavaScript, SQL, and modern frameworks with proven expertise in AWS, Azure, and Power BI integration. Demonstrated ability to implement automation, manage databases, and deliver scalable technology systems that enhance operational efficiency and support cross-functional stakeholders.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, SQL, PHP, HTML5, CSS3, Bash, PowerShell

\textbf{Data \& BI Platforms:} Power BI, BigQuery, Data Visualization, ETL Pipelines, Chart.js, Database Administration

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, Database Design, Query Writing, Data Integrity

\textbf{Cloud \& DevOps:} AWS, Microsoft Azure, Docker, Kubernetes, CI/CD, GitHub Actions

\textbf{Automation \& Integration:} Automation, API Integration, Workflow Automation, n8n, REST API, GraphQL

\textbf{Frameworks \& Libraries:} React, Django, Node.js, Flask, FastAPI, Bootstrap

\textbf{Microsoft Technologies:} Office 365, Teams, SharePoint, Azure Integration, Windows Environments, Excel

\textbf{Soft Skills:} Communication, Stakeholder Engagement, Collaboration, Analytical Thinking, Adaptability, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js with cloud-based deployment on AWS infrastructure.
\item Implemented RESTful APIs, optimized SQL queries, and integrated secure systems to improve performance and ensure data integrity.
\item Deployed and maintained cloud applications using AWS, Docker, and CI/CD pipelines ensuring 99.9\% uptime and system availability.
\item Collaborated within Agile teams through code reviews and sprint planning to deliver accurate and timely project deliverables.
\item Applied secure coding standards and automation throughout SDLC improving maintainability and reducing production incidents.
\item Led backend development for multiple applications while mentoring junior developers on integration and deployment practices.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications across both frontend and backend components with database integration.
\item Contributed to design and implementation of Proposal Management and Mailroom Tracking Systems supporting operational workflows.
\item Worked closely with cross-functional teams to gather requirements, perform testing, and support deployment phases.
\item Gained hands-on experience in full stack development, database management, and secure coding within Agile frameworks.
\item Collaborated in project reviews to identify improvements in performance, scalability, and code quality for system efficiency.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full-stack LMS using React, Node.js, and MySQL to support online education during the pandemic.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards for reporting accuracy.
\item Implemented secure authentication, role-based access, and optimized database queries for high concurrent user traffic.
\item Deployed the platform on AWS with CDN caching and SSL encryption, ensuring reliable access for over 6,000 students.
\end{itemize}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Automated vulnerability scanning and patching to strengthen enterprise security and reduce manual operational effort.
\vspace{-1pt}
\begin{itemize}
\item Developed automated workflows using Python and Jenkins for vulnerability scanning and patch deployment across systems.
\item Integrated Nessus API for real-time vulnerability reporting and risk prioritization to ensure technology system stability.
\item Created dashboards and alert systems to track security compliance and monitor remediation progress for stakeholders.
\item Reduced manual intervention by 60\% and accelerated patch cycles through full CI/CD automation and process optimization.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}