% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with expertise in full stack web development, data processing automation, and cloud-based system deployment. Proficient in Python, JavaScript, SQL, and data manipulation frameworks with hands-on experience building scalable applications and optimizing workflows. Skilled in collaborating across cross-functional teams using Agile methodologies to deliver high-quality technical solutions and comprehensive documentation in fast-paced environments.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, SQL, PHP, HTML5, CSS3, Bash, PowerShell

\textbf{Frameworks \& Libraries:} React, Django, Flask, Node.js, Express.js, Bootstrap

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQLite, Database Design, ETL Pipelines

\textbf{Cloud \& DevOps:} AWS, Google Cloud Platform, Docker, Kubernetes, CI/CD, GitHub Actions

\textbf{Data Analysis \& Automation:} Excel, Data Visualization, Power BI, Workflow Automation, Python Scripting

\textbf{Software Development Practices:} Agile, Scrum, SDLC, Testing, Technical Documentation, Code Reviews

\textbf{Soft Skills:} Analytical Thinking, Communication, Collaboration, Problem Solving, Adaptability, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js to enhance system functionality and reliability.
\item Implemented RESTful APIs, optimized SQL queries, and integrated secure data processing systems to improve performance and accuracy.
\item Deployed and maintained cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and scalability.
\item Collaborated within Agile teams through code reviews, sprint planning, and technical documentation to ensure quality deliverables.
\item Applied test-driven development and secure coding standards throughout SDLC improving maintainability and reducing production issues.
\item Led backend development initiatives while mentoring junior developers on best coding practices and deployment automation strategies.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level web applications across both frontend and backend components using modern frameworks.
\item Contributed to design and implementation of data management systems focusing on workflow efficiency and user experience improvements.
\item Worked closely with cross-functional teams to gather requirements, perform testing, and support deployment phases across projects.
\item Gained hands-on experience in full stack development, automated testing, and secure coding within Agile workflows and sprints.
\item Collaborated in project reviews to identify improvements in performance, scalability, data integrity, and code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with notes, videos, quizzes, and automated performance tracking dashboards.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL to support online education during the pandemic period.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards for teachers and administrators.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent usage and reliability.
\item Deployed the platform on AWS with CDN caching and SSL encryption, ensuring reliable access for over 6,000 active student users.
\end{itemize}

\textbf{Automated Cryptocurrency Trading Bot} -- \emph{Personal Project}

\vspace{-1pt}

Created a Python trading bot using Binance API and WebSocket to automate trade execution with risk control and live monitoring.
\vspace{-1pt}
\begin{itemize}
\item Developed a fully automated trading bot in Python using Binance API and WebSocket for real-time data streaming and market analysis.
\item Implemented dynamic trading strategies, stop-loss mechanisms, and order execution algorithms for controlled risk management processes.
\item Integrated Pandas and NumPy for market analysis, backtesting, and data manipulation to improve trading accuracy and decision making.
\item Deployed using Docker on AWS EC2 for 24/7 uptime, reliability, and monitoring with detailed logging and error handling mechanisms.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}