% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with 2+ years of experience in full stack development, data pipeline engineering, and analytics automation. Proficient in Python, SQL, and cloud technologies with hands-on expertise in ETL processes, data visualization using Power BI, and building scalable applications on AWS and GCP. Proven track record collaborating in Agile teams to deliver data-driven solutions and operational analytics tools. Skilled in designing dashboards, optimizing database queries, and supporting AI/ML workflows within regulated environments.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, SQL, JavaScript, Bash, PowerShell

\textbf{Data Engineering \& Analytics:} ETL Pipelines, Data Visualization, Power BI, BigQuery, pandas

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQL Server, Data Warehousing

\textbf{Cloud \& DevOps:} AWS, GCP, Docker, Kubernetes, CI/CD, Infrastructure as Code

\textbf{Machine Learning \& AI:} Machine Learning APIs, AI Integration, Python notebooks, Model experimentation

\textbf{Software Development Practices:} Agile, Scrum, SDLC, Testing, Technical Documentation

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Analytical Thinking, Customer Focus

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using Python, JavaScript, and React while designing RESTful APIs and ETL workflows.
\item Optimized SQL queries and database performance across PostgreSQL and MySQL ensuring efficient data retrieval and analytics readiness.
\item Deployed cloud-based applications on AWS and GCP using Docker, CI/CD pipelines, and infrastructure as code for operational reliability.
\item Collaborated with cross functional Agile teams conducting code reviews, sprint planning, and technical discussions to drive delivery.
\item Applied best practices in secure coding, testing, and documentation throughout SDLC improving system maintainability and compliance.
\item Mentored junior developers on backend architecture, database design, and deployment workflows supporting team capability building.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise applications supporting frontend interfaces, backend APIs, and data integration requirements.
\item Contributed to designing Proposal Management and Mailroom Tracking Systems using Python, SQL, and JavaScript frameworks.
\item Collaborated with cross functional teams gathering business requirements, testing deliverables, and supporting deployment activities.
\item Gained hands-on experience in data transformation, database queries, and system testing within Agile development environments.
\item Participated in project reviews identifying opportunities for performance optimization, scalability enhancements, and code quality.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built scalable LMS enabling 6K+ students to access lessons, quizzes, and performance dashboards with secure authentication.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack LMS using React, Node.js, and MySQL supporting lesson uploads, interactive quizzes, and performance tracking.
\item Implemented secure role-based access controls and optimized database queries to handle high concurrent usage efficiently.
\item Integrated real-time analytics dashboards enabling teachers to monitor student progress and engagement metrics dynamically.
\item Deployed on AWS with CDN caching, SSL encryption, and autoscaling ensuring reliable access for over 6,000 active students.
\end{itemize}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Automated vulnerability scanning and patching workflows reducing manual effort and accelerating enterprise security compliance.
\vspace{-1pt}
\begin{itemize}
\item Developed automated workflows using Python and Jenkins for continuous vulnerability scanning and patch deployment orchestration.
\item Integrated Nessus API for real-time vulnerability reporting, risk prioritization, and compliance tracking across environments.
\item Created operational dashboards and alert systems to monitor security metrics, remediation progress, and patch cycle performance.
\item Reduced manual intervention by 60\% through full CI/CD automation improving patch deployment speed and operational efficiency.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}