% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with expertise in data systems, cloud platforms, and technology integration. Proficient in Python, SQL, AWS, Power BI, and database management with a strong foundation in automation, API integration, and scalable application development. Experienced in delivering technology solutions that enhance operational efficiency and support data-driven decision-making. Skilled at collaborating with cross-functional teams and translating technical requirements into actionable solutions for stakeholders.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming \& Scripting:} Python, JavaScript, SQL, Bash, PowerShell, PHP

\textbf{Data \& Analytics Platforms:} Power BI, BigQuery, ETL Pipelines, Data Visualization, Data Warehousing

\textbf{Cloud Platforms \& Services:} AWS, Microsoft Azure, Google Cloud Platform, Docker, Kubernetes

\textbf{Database Management:} PostgreSQL, MySQL, MongoDB, SQLite, Database Design, Query Optimization

\textbf{Integration \& Automation:} REST API, GraphQL, Workflow Automation, CI/CD Pipelines, n8n, Robotics Deployment

\textbf{Development \& Collaboration Tools:} Git, GitHub Actions, Jira, Microsoft Office 365, SharePoint, Teams

\textbf{Soft Skills:} Analytical Thinking, Communication, Collaboration, Problem Solving, Adaptability, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using JavaScript, React, and Node.js integrating APIs and cloud services for reliability.
\item Optimized SQL queries and database schemas to enhance performance, supporting high-volume data processing and real-time reporting.
\item Deployed applications on AWS using Docker and CI/CD pipelines ensuring consistent uptime and automated patch management processes.
\item Collaborated with cross-functional teams through Agile sprints, code reviews, and stakeholder meetings to deliver quality solutions.
\item Analyzed operational data and created performance dashboards enabling data-driven insights for business decision-making.
\item Implemented secure authentication, role-based access controls, and API integrations adhering to industry security best practices.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing web applications with both frontend and backend components supporting enterprise-level operations.
\item Contributed to Proposal Management and Mailroom Tracking Systems ensuring data accuracy, consistency, and timely reporting.
\item Worked with teams to gather requirements, perform testing, and support deployment phases within Agile development workflows.
\item Gained experience in database management, query writing, and integration of technology platforms to support operational teams.
\item Collaborated in project reviews identifying improvements in performance, scalability, and adherence to technical standards.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS using React, Node.js, and MySQL enabling 6K+ students to learn with notes, videos, and quizzes.
\vspace{-1pt}
\begin{itemize}
\item Designed full-stack LMS with lesson uploads, quizzes, and performance tracking dashboards supporting real-time operational data.
\item Implemented secure authentication and role-based access controls ensuring data integrity and user-specific content delivery.
\item Optimized database queries and indexing strategies to handle high concurrent usage and deliver consistent platform performance.
\item Deployed on AWS with CDN caching, SSL encryption, and monitoring ensuring reliable access for over 6,000 concurrent users.
\end{itemize}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Automated vulnerability scanning and patching using Python and Jenkins reducing manual effort and strengthening security.
\vspace{-1pt}
\begin{itemize}
\item Developed automated workflows using Python and Jenkins for vulnerability scanning, reporting, and patch deployment processes.
\item Integrated Nessus API for real-time vulnerability detection, risk prioritization, and compliance tracking across systems.
\item Created dashboards and alert systems for tracking security remediation progress and reporting to operations and stakeholders.
\item Reduced manual intervention by 60\% and accelerated patch cycles through full CI/CD automation and scheduled task execution.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}