% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

DevOps Engineer with hands-on experience automating infrastructure, building CI/CD pipelines, and managing cloud environments using AWS, Docker, Kubernetes, and Terraform. Proven ability to deploy and monitor scalable applications, implement Infrastructure as Code, and collaborate across Development, QA, and Operations teams. Skilled in scripting with Python, Bash, and PowerShell, as well as optimizing cloud resources for performance, security, and cost efficiency.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Platforms \& Infrastructure:} AWS (EC2, S3, RDS, Lambda, CloudFormation), Google Cloud Platform, Terraform, Ansible, CloudWatch

\textbf{CI/CD \& DevOps Tools:} Jenkins, GitHub Actions, GitLab CI/CD, Docker, Kubernetes, Git

\textbf{Scripting \& Automation:} Python, Bash, PowerShell, Shell Scripting, Workflow Automation

\textbf{Monitoring, Logging \& Security:} CloudWatch, Cloud Logging, OWASP, IAM, SSL/TLS, Encryption

\textbf{Systems \& Networking:} Linux (Ubuntu), Nginx, Load Balancing, VPC, Cloud Networking, DNS

\textbf{Databases \& APIs:} PostgreSQL, MySQL, MongoDB, REST API, GraphQL

\textbf{Development \& Design:} Agile, Scrum, System Design, Performance Optimization, Technical Documentation

\textbf{Soft Skills:} Problem Solving, Collaboration, Adaptability, Communication, Continuous Learning, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Deployed and maintained cloud applications on AWS using Docker containers and CI/CD pipelines ensuring high availability.
\item Built automated deployment workflows with GitHub Actions and GitLab CI/CD reducing deployment time and manual intervention.
\item Implemented Infrastructure as Code with Terraform and CloudFormation to provision and manage scalable cloud environments.
\item Monitored application performance using CloudWatch and logging tools troubleshooting issues to ensure optimal uptime.
\item Collaborated with development, QA, and operations teams in Agile sprints to streamline software delivery and deployments.
\item Optimized cloud resource utilization and implemented autoscaling to improve performance and reduce operational costs.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in provisioning and configuring cloud infrastructure for enterprise applications using AWS and automation scripts.
\item Supported deployment activities and release management working closely with DevOps and QA teams in Agile environments.
\item Contributed to building CI/CD pipelines for automated testing and deployment improving delivery speed and consistency.
\item Participated in monitoring and troubleshooting application and infrastructure performance to ensure system reliability.
\item Gained hands-on experience with Docker, scripting, and cloud security best practices in production environments.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS deployed on AWS with automated infrastructure provisioning supporting 6K+ concurrent users securely.
\vspace{-1pt}
\begin{itemize}
\item Deployed the platform on AWS using EC2, S3, and RDS with automated infrastructure provisioning through CloudFormation.
\item Configured SSL encryption, CDN caching, and load balancing to ensure high availability and low-latency access globally.
\item Implemented monitoring and alerting using CloudWatch to track performance metrics and resolve bottlenecks proactively.
\item Optimized database queries and autoscaling policies to handle traffic spikes and reduce cloud costs by 30\%.
\end{itemize}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Automated vulnerability scanning and patch deployment using Python, Jenkins, and Nessus reducing manual effort by 60%.
\vspace{-1pt}
\begin{itemize}
\item Developed automated CI/CD pipelines using Jenkins and Python for continuous vulnerability scanning and patch deployment.
\item Integrated Nessus API for real-time vulnerability reporting, risk prioritization, and compliance tracking dashboards.
\item Implemented logging, monitoring, and alerting solutions to track security remediation progress and automate notifications.
\item Deployed workflows in Docker containers on AWS ensuring scalable, repeatable, and secure patching processes across environments.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}