% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

DevOps professional with proven experience in cloud infrastructure, CI/CD automation, and application deployment across Azure, AWS, and GCP environments. Skilled in Infrastructure as Code using Terraform, Docker, and Kubernetes orchestration to enable reliable, scalable SaaS platforms. Experienced in managing secure deployment pipelines, implementing monitoring and logging solutions, and supporting production systems with strong focus on operational excellence and cross-functional collaboration.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud \& Infrastructure:} Microsoft Azure, AWS, GCP, Infrastructure as Code, Terraform

\textbf{DevOps \& Automation:} Azure DevOps, CI/CD Pipelines, Docker, Kubernetes, GitHub Actions, Jenkins

\textbf{Scripting \& Automation:} PowerShell, Bash, Python, Shell Scripting, Automation

\textbf{Systems \& Databases:} SQL Server, PostgreSQL, MySQL, Linux, Windows Server, IIS

\textbf{Security \& Compliance:} IAM, OAuth, SSL/TLS, OWASP, Security Best Practices, Encryption

\textbf{Monitoring \& Operations:} CloudWatch, Monitoring, Logging, Incident Response, Load Balancing

\textbf{Soft Skills:} Problem Solving, Communication, Collaboration, Adaptability, Ownership, Documentation

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Deployed and maintained cloud infrastructure using AWS, Docker, and CI/CD pipelines ensuring high availability and reliability.
\item Implemented automated deployment workflows and infrastructure monitoring to reduce manual intervention and minimize downtime.
\item Optimized application performance through load balancing, caching strategies, and database query tuning across production systems.
\item Collaborated with cross-functional teams through Agile ceremonies and code reviews to deliver secure, scalable solutions.
\item Applied security best practices and secure coding standards throughout SDLC reducing vulnerabilities in production environments.
\item Documented deployment processes, configuration changes, and troubleshooting procedures to support operational transparency.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Supported deployment and testing of enterprise applications across development, staging, and production environments.
\item Contributed to environment configuration management ensuring consistency and alignment across multiple application instances.
\item Worked with cross-functional teams to gather requirements, validate builds, and support release coordination activities.
\item Gained hands-on experience with CI/CD pipelines, infrastructure automation, and deployment best practices within Agile teams.
\item Participated in incident troubleshooting and post-deployment support to identify and resolve application stability issues.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built scalable LMS on AWS with automated deployment pipelines supporting 6K+ concurrent users with high availability and security.
\vspace{-1pt}
\begin{itemize}
\item Designed cloud architecture on AWS with autoscaling, load balancing, and CDN caching to support high-volume concurrent usage.
\item Implemented CI/CD pipelines for automated testing, build validation, and deployment to staging and production environments.
\item Configured SSL encryption, IAM policies, and security groups to enforce secure access and protect sensitive educational data.
\item Monitored system performance using CloudWatch and logging tools to ensure platform reliability and rapid incident resolution.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Deployed real-time chat app on AWS using Docker containers with automated build and release pipelines for scalable delivery.
\vspace{-1pt}
\begin{itemize}
\item Containerized application using Docker and deployed on AWS App Runner ensuring scalable, low-latency infrastructure delivery.
\item Automated build and deployment workflows using CI/CD pipelines with version control and environment-specific configurations.
\item Configured cloud networking, load balancing, and SSL termination to support secure real-time communication at scale.
\item Monitored application health, uptime, and performance metrics using AWS monitoring tools and implemented automated alerting.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}