% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

DevOps-focused Software Engineer with 3+ years building scalable cloud infrastructure and automating CI/CD pipelines across AWS environments. Proven expertise in containerization with Docker and Kubernetes, infrastructure as code using Terraform and Ansible, and implementing automated deployment workflows that enhance system reliability. Skilled in Python development, monitoring frameworks, and designing distributed systems with strong focus on performance and availability. Experienced mentor committed to elevating team capabilities through code reviews and knowledge sharing.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{DevOps \& Automation:} Docker, Kubernetes, Terraform, Ansible, Jenkins, GitHub Actions

\textbf{Cloud Platforms \& Services:} AWS, AWS Lambda, AWS EC2, AWS S3, AWS RDS, CloudFormation

\textbf{Programming \& Scripting:} Python, JavaScript, Bash, PowerShell, SQL

\textbf{Monitoring \& Reliability:} CloudWatch, Cloud Logging, High Availability, Performance Optimization, Disaster Recovery

\textbf{CI/CD \& Infrastructure:} CI/CD Pipelines, Infrastructure as Code, Continuous Integration, Continuous Deployment

\textbf{Development Practices:} Agile, Scrum, Code Reviews, Technical Documentation, System Design

\textbf{Soft Skills:} Mentorship, Communication, Collaboration, Problem Solving, Adaptability, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Deployed and maintained cloud infrastructure on AWS using Docker, Kubernetes, and automated CI/CD pipelines ensuring 99.9\% uptime.
\item Implemented infrastructure as code with Terraform to provision scalable environments reducing deployment time by 40\%.
\item Developed Python automation scripts and RESTful APIs optimizing database performance and system reliability across services.
\item Orchestrated container deployments using Docker and Kubernetes improving resource utilization and application scalability.
\item Established DevOps best practices including automated testing, continuous integration, and monitoring frameworks with CloudWatch.
\item Mentored junior engineers on containerization, cloud architecture, and CI/CD workflows elevating team technical capabilities.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to enterprise application development utilizing Agile methodologies and participating in sprint planning sessions.
\item Assisted in designing distributed system architectures with focus on scalability, performance, and fault tolerance.
\item Collaborated with cross functional teams to automate deployment processes and integrate monitoring solutions.
\item Gained hands-on experience with configuration management platforms and container orchestration technologies.
\item Supported continuous integration workflows by writing automated tests and improving build pipeline efficiency.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic }

\vspace{-1pt}

Engineered automated security workflows reducing manual patching effort by 60% through CI/CD integration and real-time monitoring.
\vspace{-1pt}
\begin{itemize}
\item Built automated vulnerability scanning and patch deployment workflows using Python, Jenkins, and infrastructure as code principles.
\item Integrated Nessus API for real-time security reporting enabling proactive risk prioritization and compliance tracking.
\item Designed monitoring dashboards and alert systems tracking remediation progress and ensuring continuous security compliance.
\item Accelerated patch deployment cycles through fully automated CI/CD pipelines reducing manual intervention across environments.
\end{itemize}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Architected scalable LMS on AWS serving 6,000+ concurrent users with high availability and optimized cloud resource utilization.
\vspace{-1pt}
\begin{itemize}
\item Deployed full stack application on AWS leveraging EC2, S3, and RDS with autoscaling to handle 6,000+ concurrent student users.
\item Implemented CDN caching and SSL encryption ensuring reliable performance and secure access across distributed user base.
\item Optimized database queries and configured load balancers improving response times and system availability during peak usage.
\item Established monitoring and logging frameworks using CloudWatch to track application health and proactively address performance issues.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}