% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with expertise in cloud infrastructure, automation, and DevOps practices. Experienced in deploying scalable applications using AWS, Docker, Kubernetes, and CI/CD pipelines. Proficient in infrastructure-as-code tools including Terraform and Ansible, with strong knowledge of Python scripting and Linux environments. Proven ability to design secure, reliable systems and collaborate effectively within Agile teams to deliver impactful solutions for mission-critical applications.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Infrastructure as Code \& Automation:} Terraform, Ansible, CloudFormation, Docker, Kubernetes, Infrastructure Automation

\textbf{Cloud Platforms \& Services:} Microsoft Azure, AWS (EC2, S3, RDS, Lambda), Google Cloud Platform, Azure DevOps, Cloud Networking

\textbf{CI/CD \& DevOps Tools:} GitHub Actions, GitLab CI/CD, Jenkins, CI/CD Pipelines, Release Management, Version Control

\textbf{Operating Systems \& Scripting:} Linux (Ubuntu), Bash Scripting, PowerShell, Shell Scripting, Python Automation, Unix Environments

\textbf{Monitoring \& System Operations:} Cloud Monitoring, Logging, CloudWatch, System Administration, Load Balancing, High Availability

\textbf{Database \& Security:} PostgreSQL, MySQL, MongoDB, SQL Server, IAM Policies, Security Best Practices, Encryption

\textbf{Soft Skills:} Problem Solving, Communication, Collaboration, Adaptability, Ownership, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Deployed and maintained cloud applications using AWS, Docker, and CI/CD pipelines ensuring high availability and uptime.
\item Implemented automated workflows with GitLab CI/CD and GitHub Actions to streamline deployment and reduce manual intervention.
\item Optimized infrastructure configurations and SQL queries to improve system performance and reliability in production environments.
\item Collaborated within Agile teams through sprint planning, code reviews, and pair programming to deliver scalable solutions.
\item Applied infrastructure automation and secure coding standards throughout SDLC to enhance maintainability and reduce issues.
\item Mentored junior developers on DevOps best practices, containerization strategies, and deployment workflows for applications.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in deploying enterprise applications using CI/CD pipelines and containerized environments for reliable delivery.
\item Contributed to infrastructure design and automation efforts for the Proposal Management and Mailroom Tracking Systems.
\item Worked closely with cross functional teams to gather requirements, perform testing, and support deployment and monitoring.
\item Gained hands-on experience in DevOps practices, cloud platforms, scripting, and automation within Agile workflows.
\item Collaborated in project reviews to identify improvements in performance, scalability, infrastructure efficiency, and uptime.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with interactive quizzes, deployed on AWS using automation and monitoring.
\vspace{-1pt}
\begin{itemize}
\item Designed and deployed a full-stack LMS on AWS with automated scaling, load balancing, and CDN caching for high availability.
\item Implemented secure authentication, role-based access, and optimized database queries to handle high concurrent user traffic.
\item Automated deployment using CI/CD pipelines and Docker containers ensuring consistent releases and minimal downtime for users.
\item Monitored platform performance and uptime using CloudWatch and logging tools to ensure reliable access for over 6,000 students.
\end{itemize}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Automated vulnerability scanning and patching using Python, Jenkins, and Nessus API to strengthen enterprise security posture.
\vspace{-1pt}
\begin{itemize}
\item Developed automated workflows using Python and Jenkins for continuous vulnerability scanning and patch deployment across systems.
\item Integrated Nessus API for real-time vulnerability reporting, risk prioritization, and automated remediation tracking dashboards.
\item Created alert systems and compliance dashboards to monitor security posture and accelerate remediation response cycles.
\item Reduced manual intervention by 60\% and accelerated patch deployment through full CI/CD automation and infrastructure scripting.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}