% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

DevOps Engineer with hands-on experience building CI/CD pipelines, automating infrastructure, and managing cloud environments. Skilled in Docker, Kubernetes, AWS, GCP, Terraform, and GitLab CI/CD with a strong foundation in scripting, monitoring, and secure deployment practices. Experienced in full stack development and Agile collaboration, bringing a developer-focused mindset to platform engineering and operational excellence.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud \& Infrastructure:} AWS, Google Cloud Platform, Terraform, Ansible, Infrastructure as Code, CloudFormation

\textbf{DevOps \& CI/CD:} Docker, Kubernetes, GitLab CI/CD, GitHub Actions, Jenkins, Continuous Integration

\textbf{Monitoring \& Observability:} Cloud Monitoring, Cloud Logging, CloudWatch, Logging, Autoscaling, Performance Optimization

\textbf{Scripting \& Automation:} Python, Bash, PowerShell, Shell Scripting, Workflow Automation, Automation Testing

\textbf{Database \& Security:} PostgreSQL, MySQL, MongoDB, IAM, Encryption, OAuth, API Security

\textbf{Programming \& Development:} JavaScript, Node.js, React, Django, REST API, Microservices

\textbf{Systems \& Networking:} Linux, Ubuntu, Nginx, Load Balancing, VPC, Cloud Networking, Networking principles

\textbf{Soft Skills:} Problem Solving, Collaboration, Adaptability, Communication, Ownership, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Built and maintained CI/CD pipelines using GitHub Actions and GitLab to automate deployment workflows and reduce manual effort.
\item Deployed and managed cloud-based applications on AWS using Docker containers ensuring consistent uptime and system reliability.
\item Optimized infrastructure using Infrastructure as Code practices, automating build and deployment processes across environments.
\item Collaborated with Agile teams on sprint planning, code reviews, and release management to deliver high-quality production systems.
\item Implemented secure authentication, IAM policies, and API security standards to meet compliance and governance requirements.
\item Monitored system performance using cloud logging and observability tools to identify bottlenecks and improve operational efficiency.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in automating deployment workflows and build processes for enterprise web applications within Agile environments.
\item Contributed to infrastructure provisioning and configuration management using scripting and version control best practices.
\item Worked with cross-functional teams to gather requirements, perform testing, and support production deployment phases.
\item Gained hands-on experience in containerization, cloud deployment, and monitoring to support scalable system performance.
\item Collaborated in project retrospectives to identify improvements in reliability, automation, and deployment efficiency.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS with automated CI/CD deployment on AWS enabling 6K+ students to access lessons and performance tracking.
\vspace{-1pt}
\begin{itemize}
\item Automated deployment pipelines using GitHub Actions and Docker to streamline continuous integration and continuous deployment.
\item Provisioned AWS infrastructure with CloudFormation and Terraform ensuring scalability and resilience for high concurrent usage.
\item Implemented monitoring and logging using CloudWatch to track system performance and identify optimization opportunities.
\item Configured CDN caching, load balancing, and SSL encryption to ensure high availability and secure access for over 6,000 students.
\end{itemize}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Automated vulnerability scanning and patching workflows using Python and Jenkins to strengthen enterprise security posture.
\vspace{-1pt}
\begin{itemize}
\item Developed CI/CD workflows with Jenkins and Python scripts to automate vulnerability scanning and patch deployment processes.
\item Integrated Nessus API for real-time vulnerability reporting and risk prioritization aligned with compliance requirements.
\item Built observability dashboards and alert systems to track security compliance and remediation progress across environments.
\item Reduced manual intervention by 60\% and accelerated patch cycles through full automation and Infrastructure as Code practices.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}