% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

DevOps Engineer with proven expertise in AWS cloud infrastructure, CI/CD automation, and Infrastructure as Code using Terraform and Jenkins. Skilled in building scalable, secure systems with Docker, Kubernetes, and monitoring tools like CloudWatch. Experienced in deploying production environments with high availability and implementing security best practices. Strong background in automation, system reliability, and cross-functional collaboration within Agile teams.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud \& Infrastructure:} AWS (EC2, S3, RDS, Lambda), Infrastructure as Code (Terraform), CloudFormation, GCP, Autoscaling

\textbf{DevOps \& Automation:} CI/CD Pipelines, Jenkins, GitHub Actions, GitLab CI/CD, Ansible, Bash Scripting

\textbf{Containerization \& Orchestration:} Docker, Kubernetes, Docker Compose, Kubernetes Clusters, Microservices Architecture

\textbf{Monitoring \& Observability:} CloudWatch, Cloud Monitoring, Cloud Logging, System Performance Monitoring, Alerting

\textbf{Security \& Compliance:} IAM Policies, SIEM, OAuth, Encryption (KMS, TLS), API Security, Vulnerability Management

\textbf{Programming \& Scripting:} Python, Bash, PowerShell, SQL, JavaScript, Shell Scripting

\textbf{Networking \& System Administration:} VPC, Load Balancing, Nginx, Route53, Cloud Networking, Linux System Administration

\textbf{Development \& Database:} PostgreSQL, MySQL, MongoDB, REST API, Node.js, Version Control (Git)

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Ownership, Mentorship

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Deployed cloud-based applications on AWS using Docker containers and CI/CD pipelines ensuring 99.9\% uptime and availability.
\item Implemented automated deployment workflows with Jenkins and GitHub Actions reducing release times and manual errors by 40\%.
\item Optimized infrastructure performance through monitoring, alerting, and resource scaling across production environments.
\item Configured IAM policies, secure authentication systems, and encryption protocols to maintain compliance and data security.
\item Collaborated with cross-functional Agile teams to streamline deployments and improve developer experience through code reviews.
\item Applied Infrastructure as Code principles and maintained version-controlled configurations for consistent environment provisioning.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in deploying enterprise applications and configuring cloud infrastructure supporting scalable production systems.
\item Participated in CI/CD pipeline development and automated testing to improve deployment reliability and speed.
\item Collaborated with DevOps teams to implement monitoring solutions and troubleshoot infrastructure issues in real time.
\item Gained hands-on experience with containerization, cloud deployments, and security best practices within Agile workflows.
\item Supported system reliability initiatives by documenting processes and contributing to infrastructure automation projects.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS on AWS supporting 6K+ students with automated deployments, CDN caching, and SSL encryption for secure access.
\vspace{-1pt}
\begin{itemize}
\item Deployed full-stack application on AWS EC2 with autoscaling, load balancing, and CloudWatch monitoring for high availability.
\item Configured S3 buckets for static content delivery with CDN caching reducing latency and improving user experience significantly.
\item Implemented SSL/TLS encryption, IAM policies, and secure authentication to protect student data and ensure compliance standards.
\item Automated database backups and disaster recovery strategies using AWS RDS ensuring data integrity and business continuity.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Deployed scalable real-time chat app on AWS using Docker containers with CI/CD automation for low-latency communication.
\vspace{-1pt}
\begin{itemize}
\item Containerized application using Docker and deployed on AWS App Runner with automated scaling for reliable real-time performance.
\item Built CI/CD pipeline with GitHub Actions automating testing, builds, and deployments to reduce release cycles and manual effort.
\item Configured CloudWatch monitoring, logging, and alerting to track application health and quickly respond to performance issues.
\item Implemented secure networking with VPC, IAM roles, and encrypted data transmission ensuring compliance with security standards.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}