% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with proven expertise in cloud infrastructure, DevOps automation, and full stack development. Experienced in deploying scalable applications on AWS and GCP using Docker, Kubernetes, and CI/CD pipelines with GitHub Actions. Skilled in building secure, high-availability systems with PostgreSQL, monitoring tools, and Infrastructure as Code. Strong collaborator with a track record of optimizing deployments, automating workflows, and supporting distributed systems across international environments.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud \& Infrastructure:} Google Cloud Platform, AWS, Docker, Kubernetes, Terraform, Infrastructure as Code

\textbf{CI/CD \& Automation:} GitHub Actions, GitLab CI/CD, Jenkins, Continuous Integration, Continuous Deployment

\textbf{Programming \& Scripting:} Python, Bash, JavaScript, Node.js, Shell Scripting, PowerShell

\textbf{Database \& Monitoring:} PostgreSQL, MySQL, MongoDB, Cloud Monitoring, Logging, Performance Optimization

\textbf{Security \& Compliance:} IAM, TLS, Encryption, OAuth, OWASP, Vulnerability Management

\textbf{Frameworks \& Tools:} React, Next.js, Django, Flask, Git, Nginx

\textbf{Soft Skills:} Problem Solving, Communication, Collaboration, Adaptability, Continuous Learning, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Deployed and maintained cloud-based applications on AWS using Docker and CI/CD pipelines ensuring 99.9\% uptime and availability.
\item Built and optimized RESTful APIs with Node.js and PostgreSQL improving system performance and reducing query latency by 30\%.
\item Implemented Infrastructure as Code with Terraform and automated deployment workflows reducing manual configuration by 50\%.
\item Collaborated within Agile teams using Git workflows, code reviews, and sprint planning to deliver high-quality infrastructure.
\item Applied security best practices including IAM policies, TLS encryption, and vulnerability scanning throughout the SDLC.
\item Monitored production systems using Cloud Monitoring and logging tools to track uptime, performance metrics, and error rates.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in deploying enterprise web applications on cloud infrastructure supporting both frontend and backend components.
\item Contributed to CI/CD pipeline configuration and testing automation to accelerate safe deployments across environments.
\item Worked with cross functional teams to gather infrastructure requirements, conduct testing, and support production releases.
\item Gained hands-on experience with containerization, orchestration, and monitoring tools in Agile development workflows.
\item Collaborated in post-deployment reviews to identify performance bottlenecks, scalability improvements, and reliability enhancements.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Deployed a scalable LMS on AWS serving 6K+ students with CDN caching, load balancing, and SSL encryption for reliability.
\vspace{-1pt}
\begin{itemize}
\item Architected and deployed full stack LMS on AWS using Docker, EC2, and RDS to support high-availability online education.
\item Configured CloudWatch monitoring, automated backups, and disaster recovery strategies ensuring 99.9\% platform uptime.
\item Implemented load balancing, CDN caching with CloudFront, and SSL/TLS encryption to optimize performance and security.
\item Automated CI/CD pipelines using GitHub Actions to streamline deployments and reduce release cycles for new features.
\end{itemize}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Automated vulnerability scanning and patch deployment using Python, Jenkins, and Nessus API reducing manual effort by 60%.
\vspace{-1pt}
\begin{itemize}
\item Developed automated workflows with Python and Jenkins for vulnerability scanning, patching, and compliance tracking.
\item Integrated Nessus API for real-time security reporting, risk prioritization, and automated remediation alerts.
\item Built monitoring dashboards to track security compliance, patch status, and vulnerability trends across infrastructure.
\item Reduced manual security operations by 60\% and accelerated patch cycles through full CI/CD automation and orchestration.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}