% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven DevOps Engineer with hands-on experience building and maintaining CI/CD pipelines, cloud infrastructure, and automation workflows. Proficient in scripting with Python, Bash, and PowerShell, and skilled in Infrastructure as Code using Terraform, Ansible, and CloudFormation. Experienced in deploying scalable applications on AWS and GCP using Docker and Kubernetes. Adept at implementing monitoring and logging solutions to ensure system reliability and performance.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{CI/CD \& Version Control:} Jenkins, GitHub Actions, GitLab CI/CD, Git, Bitbucket, CI/CD Pipelines

\textbf{Infrastructure as Code:} Terraform, Ansible, CloudFormation, Infrastructure Automation

\textbf{Cloud Platforms \& Services:} AWS, Google Cloud Platform, AWS EC2, AWS S3, AWS Lambda, AWS RDS

\textbf{Containerization \& Orchestration:} Docker, Kubernetes, Docker Compose, Container Orchestration

\textbf{Scripting \& Automation:} Python, Bash, PowerShell, Shell Scripting, Workflow Automation

\textbf{Monitoring \& Observability:} CloudWatch, Cloud Logging, Cloud Monitoring, System Health Tracking

\textbf{Systems \& Networking:} Linux, Ubuntu, Networking Concepts, VPC, Security Best Practices

\textbf{Soft Skills:} Problem Solving, Communication, Collaboration, Adaptability, Ownership, Documentation

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Built and maintained CI/CD pipelines using GitHub Actions and GitLab CI automating deployments and ensuring reliable software builds.
\item Deployed and managed cloud infrastructure on AWS using Terraform and CloudFormation improving scalability and consistency.
\item Automated deployment workflows with Docker and Kubernetes reducing manual intervention and accelerating release cycles significantly.
\item Developed Python and Bash scripts to automate repetitive tasks and optimize system operations improving overall team efficiency.
\item Implemented monitoring and logging solutions using CloudWatch and Cloud Logging to track system health and performance metrics.
\item Collaborated within Agile teams through sprint planning and code reviews ensuring high-quality deliverables and continuous improvement.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in building automated CI/CD pipelines for enterprise applications improving deployment frequency and reducing errors.
\item Contributed to cloud infrastructure provisioning using Infrastructure as Code tools supporting scalable application environments.
\item Gained hands-on experience with version control systems including Git, GitLab, and Bitbucket in collaborative development workflows.
\item Supported deployment and monitoring of containerized applications using Docker ensuring consistent performance across environments.
\item Collaborated with cross-functional teams to gather requirements, perform testing, and support deployment phases within Agile workflows.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Automated vulnerability scanning and patching workflows using Python and Jenkins reducing manual effort by 60 percent.
\vspace{-1pt}
\begin{itemize}
\item Developed automated CI/CD workflows using Python and Jenkins for vulnerability scanning and patch deployment across environments.
\item Integrated Nessus API for real-time vulnerability reporting and risk prioritization improving security compliance and visibility.
\item Created monitoring dashboards and alert systems to track security compliance and remediation progress using logging best practices.
\item Reduced manual intervention by 60 percent and accelerated patch cycles through full CI/CD automation and infrastructure orchestration.
\end{itemize}

\textbf{Automated Cryptocurrency Trading Bot} -- \emph{Personal Project}

\vspace{-1pt}

Created a Python trading bot deployed on AWS EC2 using Docker for 24/7 uptime with automated trade execution and monitoring.
\vspace{-1pt}
\begin{itemize}
\item Developed a fully automated trading bot in Python using Binance API and WebSocket for real-time data streaming and execution.
\item Implemented dynamic trading strategies, stop-loss mechanisms, and order execution algorithms with rigorous backtesting and analysis.
\item Deployed using Docker on AWS EC2 with automated monitoring and logging ensuring 24/7 uptime and reliable performance under load.
\item Configured CloudWatch monitoring and alerting for system health tracking enabling proactive incident response and system optimization.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}