% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven DevOps Engineer with hands-on experience in cloud infrastructure, CI/CD automation, and system reliability. Proven ability to deploy scalable infrastructure using AWS, Docker, Kubernetes, and Infrastructure as Code tools like Terraform and Ansible. Skilled in shell scripting, Python automation, and database management with PostgreSQL and MySQL. Strong Linux administration background with expertise in networking, monitoring, and troubleshooting production environments.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{DevOps \& Infrastructure:} Terraform, Ansible, Docker, Kubernetes, Infrastructure as Code, CI/CD Pipelines

\textbf{Cloud Platforms \& Services:} AWS, AWS EC2, AWS S3, AWS RDS, Google Cloud Platform, CloudFormation

\textbf{Programming \& Scripting:} Python, Bash, Shell Scripting, PowerShell, JavaScript

\textbf{Database \& Data Systems:} PostgreSQL, MySQL, MongoDB, Redis, Database Administration, SQL

\textbf{Version Control \& Automation:} Git, GitHub, GitLab, GitHub Actions, Jenkins, Automation

\textbf{Systems \& Networking:} Linux, Ubuntu, Networking Principles, Load Balancing, VPN, System Administration

\textbf{Monitoring \& Security:} Monitoring, Logging, CloudWatch, Security Best Practices, High Availability

\textbf{Soft Skills:} Collaboration, Problem Solving, Adaptability, Technical Documentation, Communication, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Deployed and maintained cloud infrastructure on AWS using Docker, CI/CD pipelines, and automation ensuring consistent uptime.
\item Provisioned and configured databases including PostgreSQL and MySQL with optimized queries to improve performance and reliability.
\item Implemented Infrastructure as Code practices for environment provisioning, deployment automation, and configuration management.
\item Built and maintained CI/CD pipelines using GitHub Actions and GitLab CI/CD to support continuous integration and deployment workflows.
\item Wrote shell scripts and Python automation tools to streamline deployment validation, monitoring, and troubleshooting processes.
\item Collaborated with cross-functional teams through code reviews, sprint planning, and Agile workflows to ensure quality deliverables.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in deploying enterprise applications across development, staging, and production environments using automation tools.
\item Supported infrastructure provisioning and configuration management tasks for scalable web and mobile application systems.
\item Collaborated with DevOps teams to troubleshoot deployment issues, improve system stability, and optimize performance.
\item Gained hands-on experience with version control systems, CI/CD workflows, and secure deployment practices within Agile teams.
\item Participated in infrastructure reviews to identify improvements in scalability, reliability, and disaster recovery strategies.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Deployed a scalable LMS infrastructure on AWS with high availability, CDN caching, and SSL encryption for 6K+ students.
\vspace{-1pt}
\begin{itemize}
\item Provisioned and deployed AWS infrastructure using EC2, RDS, and S3 with automated deployment scripts for high availability.
\item Configured load balancing, CDN caching, and SSL encryption to ensure reliable, low-latency access for concurrent users.
\item Implemented database replication and automated backup strategies for disaster recovery and data integrity across environments.
\item Monitored system performance using CloudWatch and automated alerts to proactively address infrastructure issues and optimize uptime.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Deployed scalable real-time chat infrastructure on AWS using Docker containers and automated CI/CD pipelines for reliability.
\vspace{-1pt}
\begin{itemize}
\item Containerized application using Docker and deployed on AWS App Runner for scalable, low-latency real-time communication.
\item Built automated CI/CD pipelines using GitHub Actions to streamline testing, deployment, and environment provisioning workflows.
\item Configured networking, load balancing, and monitoring to ensure high availability and performance under concurrent user load.
\item Implemented infrastructure automation scripts for environment setup, deployment validation, and troubleshooting production issues.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}