% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven DevOps Engineer with strong expertise in cloud infrastructure, containerization, and CI/CD automation. Proven experience deploying scalable applications on AWS and GCP using Docker, Kubernetes, and Infrastructure as Code. Skilled in building secure, high-availability systems with monitoring, automation, and compliance best practices. Adept at collaborating with cross-functional teams to optimize deployment pipelines and enhance system reliability in fast-paced environments.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud \& Infrastructure:} Google Cloud Platform, AWS, Infrastructure as Code, Terraform, CloudFormation, Disaster Recovery

\textbf{Containers \& Orchestration:} Kubernetes, Docker, Docker Compose, Autoscaling, Cluster Management, Container Optimization

\textbf{CI/CD \& Automation:} GitHub Actions, GitLab CI/CD, Jenkins, Continuous Integration, Continuous Deployment, GitOps

\textbf{Monitoring \& Observability:} Cloud Monitoring, Cloud Logging, CloudWatch, Performance Metrics, Incident Response, Logging

\textbf{Security \& Compliance:} IAM, Encryption, TLS, OAuth, JWT, Vulnerability Management, API Security

\textbf{Databases \& Backend:} PostgreSQL, MySQL, MongoDB, Backup Strategies, Database Administration, SQL

\textbf{Scripting \& Development:} Python, Bash, Shell Scripting, PowerShell, Node.js, Linux System Administration

\textbf{Networking \& Load Balancing:} VPC, Subnets, Load Balancing, Nginx, Reverse Proxy, Cloud Networking, CDN

\textbf{Soft Skills:} Problem Solving, Communication, Team Collaboration, Continuous Learning, Adaptability, Documentation

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Deployed and maintained cloud-based applications on AWS using Docker, Kubernetes, and CI/CD pipelines for consistent uptime.
\item Implemented Infrastructure as Code with Terraform and CloudFormation to automate provisioning and ensure repeatable deployments.
\item Built and optimized CI/CD pipelines with GitHub Actions and GitLab CI/CD to accelerate release cycles and improve code quality.
\item Monitored system performance and uptime using CloudWatch, logging, and alerting to proactively address incidents and outages.
\item Applied IAM policies, encryption, and secure coding standards to ensure compliance with security best practices across environments.
\item Collaborated with cross-functional Agile teams through code reviews, documentation, and sprint planning to deliver high-quality solutions.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in deploying enterprise applications using Docker containers and cloud infrastructure to support scalable service delivery.
\item Contributed to automated testing, build pipelines, and deployment workflows within Agile development cycles and CI/CD environments.
\item Worked with PostgreSQL and MySQL databases to perform backups, monitoring, and basic administration tasks for production systems.
\item Collaborated with development teams to gather requirements, troubleshoot issues, and support deployment phases across multiple projects.
\item Gained hands-on experience with Linux system administration, shell scripting, and version control using Git and GitHub workflows.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes.
\vspace{-1pt}
\begin{itemize}
\item Deployed the platform on AWS with Docker and Kubernetes for high availability, supporting over 6,000 concurrent student users.
\item Implemented Infrastructure as Code using Terraform to automate provisioning of cloud resources and streamline environment setup.
\item Configured CloudWatch monitoring, logging, and alerting to track system performance, uptime, and error rates across all services.
\item Applied SSL/TLS encryption, IAM roles, and secure authentication to ensure data protection and compliance with security standards.
\end{itemize}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Automated vulnerability scanning and patching to strengthen enterprise security and reduce manual effort.
\vspace{-1pt}
\begin{itemize}
\item Developed automated CI/CD workflows using Python, Jenkins, and shell scripts for vulnerability scanning and patch deployment pipelines.
\item Integrated Nessus API with monitoring dashboards to track security compliance, remediation progress, and incident response metrics.
\item Reduced manual intervention by 60\% through full automation of patch cycles, improving system reliability and security posture.
\item Implemented Infrastructure as Code and version control with Git to ensure repeatable, auditable deployments across environments.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}