% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

DevSecOps-focused Software Engineer with 3+ years of experience building secure, scalable cloud applications and automating security workflows. Proficient in Python scripting, CI/CD pipeline security, and AWS infrastructure with hands-on expertise in vulnerability management, secure coding, and API security. Proven track record implementing shift-left security practices, automating patch workflows, and collaborating with cross-functional teams to deliver enterprise-grade solutions that prioritize security-by-design principles.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Security \& DevSecOps:} OWASP Top 10, API Security, Vulnerability Management, IAM, JWT, OAuth, Encryption

\textbf{Programming \& Scripting:} Python, Bash, PowerShell, JavaScript, SQL, Shell Scripting

\textbf{Cloud \& Infrastructure:} AWS, Docker, Kubernetes, Terraform, CloudFormation, Infrastructure as Code

\textbf{CI/CD \& Automation:} GitLab CI/CD, GitHub Actions, Jenkins, CI/CD Pipelines, Continuous Integration

\textbf{APIs \& Integrations:} REST API, GraphQL, API Gateway, OpenAPI, WebSockets, Serverless

\textbf{Threat \& Incident Response:} Threat Intelligence, Incident Response, MITRE ATT\&CK, SIEM, Risk Assessments

\textbf{Soft Skills:} Communication, Leadership, Mentorship, Collaboration, Adaptability, Problem Solving

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using JavaScript, React, and Node.js with secure coding standards and OWASP best practices.
\item Implemented RESTful APIs with OAuth and JWT authentication while conducting security reviews to mitigate XSS and SQL injection risks.
\item Deployed cloud applications on AWS using Docker, CI/CD pipelines, and infrastructure automation ensuring security compliance and uptime.
\item Collaborated within Agile teams through code reviews, security architecture discussions, and sprint planning for high-quality deliverables.
\item Applied test-driven development and integrated security testing frameworks throughout SDLC reducing vulnerabilities in production.
\item Led backend development initiatives while mentoring junior engineers on secure coding, API security, and DevSecOps automation practices.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web and mobile applications with a focus on secure coding practices and frontend-backend integration.
\item Contributed to design and implementation of Proposal Management and Mailroom Tracking Systems using Agile methodologies and version control.
\item Worked with cross-functional teams to gather security requirements, perform testing, and support secure deployment phases.
\item Gained hands-on experience in full stack development, vulnerability remediation, and secure API design within collaborative workflows.
\item Collaborated in project reviews to identify performance improvements, threat mitigation strategies, and code maintainability enhancements.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Automated vulnerability scanning and patching workflows to strengthen enterprise security posture and reduce manual remediation effort.
\vspace{-1pt}
\begin{itemize}
\item Developed automated workflows using Python and Jenkins for continuous vulnerability scanning, patch deployment, and compliance tracking.
\item Integrated Nessus API for real-time vulnerability reporting, risk prioritization, and remediation status monitoring across infrastructure.
\item Created security dashboards and alert systems to track compliance metrics, remediation progress, and threat exposure in real time.
\item Reduced manual intervention by 60\% and accelerated patch cycles through full CI/CD automation and shift-left security integration.
\end{itemize}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS with secure authentication and role-based access enabling 6K+ students to learn with interactive educational content.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL implementing secure authentication and authorization controls.
\item Integrated lesson uploads, quizzes, and performance tracking with real-time dashboards following API security and data protection principles.
\item Implemented role-based access control, encrypted data storage, and optimized database queries for high concurrent usage and scalability.
\item Deployed the platform on AWS with CDN caching, SSL/TLS encryption, and monitoring ensuring secure access for over 6,000 active students.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}