% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with expertise in DevOps, cloud security, and automation. Proficient in integrating security controls into CI/CD pipelines using GitHub Actions, Jenkins, and GitLab. Experienced with AWS, GCP, Kubernetes, Docker, and Infrastructure as Code tools like Terraform and CloudFormation. Skilled in Python, Bash, and PowerShell scripting for vulnerability management and security automation. Strong understanding of OWASP standards, secure coding practices, and cloud security best practices.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming \& Scripting:} Python, Bash, PowerShell, JavaScript, SQL

\textbf{DevOps \& CI/CD:} GitHub Actions, GitLab CI/CD, Jenkins, Docker, Kubernetes

\textbf{Cloud Platforms \& IaC:} AWS, GCP, Microsoft Azure, Terraform, CloudFormation

\textbf{Security \& Compliance:} OWASP, Vulnerability Management, API Security, Encryption, IAM

\textbf{Monitoring \& Incident Response:} SIEM, Threat Intelligence, Risk Assessments, CloudWatch, Logging

\textbf{Databases \& Architecture:} PostgreSQL, MySQL, MongoDB, Microservices, REST API

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Ownership, Documentation

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Deployed and maintained cloud applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and security posture.
\item Implemented secure RESTful APIs, optimized SQL queries, and integrated payment systems with encryption and authentication controls.
\item Applied secure coding standards and OWASP best practices throughout SDLC reducing vulnerabilities and production issues.
\item Collaborated within Agile teams performing code reviews, sprint planning, and security-focused pair programming sessions.
\item Automated deployment workflows using GitHub Actions and Jenkins improving release consistency and reducing manual effort.
\item Mentored developers on secure coding, cloud security configurations, and DevOps best practices for scalable deployments.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to enterprise application development across frontend and backend components following secure design principles.
\item Assisted in implementing Proposal Management and Mailroom Tracking Systems with security and compliance requirements.
\item Worked with cross functional teams to gather requirements, perform security testing, and support secure deployment phases.
\item Gained hands-on experience in full stack development, vulnerability testing, and secure coding within Agile workflows.
\item Collaborated in project reviews identifying improvements in performance, scalability, security, and code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Automated vulnerability scanning and patching to strengthen enterprise security and reduce manual effort significantly.
\vspace{-1pt}
\begin{itemize}
\item Developed automated security workflows using Python and Jenkins for vulnerability scanning and patch deployment processes.
\item Integrated Nessus API for real-time vulnerability reporting, risk prioritization, and compliance tracking across systems.
\item Created dashboards and alert systems to track security compliance, remediation progress, and policy enforcement metrics.
\item Reduced manual intervention by 60\% and accelerated patch cycles through full CI/CD automation and Infrastructure as Code.
\end{itemize}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn securely with authentication, encryption, and cloud deployment.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL with secure authentication and role-based access.
\item Implemented secure data handling, encrypted communications, and optimized database queries for high concurrent usage scenarios.
\item Deployed the platform on AWS with SSL encryption, CDN caching, and automated monitoring for reliable access and uptime.
\item Integrated performance tracking dashboards and real-time analytics ensuring scalability and compliance with security standards.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}