% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Developer with 5+ years building scalable web applications using React, Next.js, and modern JavaScript frameworks. Proven expertise in ecommerce development, headless CMS integration, cloud architecture on AWS and GCP, and CI/CD automation. Skilled in UI/UX design, graphic design tools, and collaborating within distributed Agile teams using GitHub and Jira. Adept at quickly adapting to evolving requirements and delivering high-quality solutions.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, PHP, SQL, HTML5, CSS3/SCSS

\textbf{Frameworks \& Libraries:} React, Next.js, Redux, Node.js, Express.js, Bootstrap, Material UI

\textbf{CMS \& Ecommerce:} Headless CMS, Contentful, Shopify, REST API, GraphQL, Payment Integration

\textbf{Cloud \& DevOps:} AWS, AWS Lambda, EC2, S3, Netlify, Docker, CI/CD, GitHub Actions

\textbf{Database \& Data Management:} MySQL, PostgreSQL, MongoDB, DynamoDB, Firebase

\textbf{Design \& UI/UX:} UI/UX Design, Graphic Design, Adobe Creative Suite, Responsive Design, Web Design

\textbf{Development Practices:} Agile, Scrum, Git, GitHub, Jira, Code Reviews, TDD, Documentation

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Problem Solving, Self-Starter, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack ecommerce applications using React, Next.js, and Node.js integrated with Shopify APIs.
\item Built headless CMS integrations with secure payment systems optimizing performance and enhancing user experience across platforms.
\item Deployed cloud-based solutions on AWS using Lambda, EC2, and S3 with CI/CD pipelines ensuring high availability and uptime.
\item Collaborated within distributed Agile teams using GitHub and Jira to deliver features through sprint planning and code reviews.
\item Applied UI/UX design principles and responsive layouts using HTML5, CSS3/SCSS, and modern JavaScript frameworks for ATS compliance.
\item Mentored junior developers on architecture design, secure coding practices, and deployment strategies across multiple projects.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to full stack development of enterprise web applications using React, Node.js, and SQL databases for scalability.
\item Assisted in designing and implementing the Proposal Management and Mailroom Tracking Systems with RESTful API integration.
\item Collaborated with cross functional teams using Jira to gather requirements, conduct testing, and support deployment phases.
\item Gained hands-on experience in Agile workflows, secure coding standards, and full SDLC from requirements to production release.
\item Participated in project reviews identifying improvements in performance, scalability, and maintainability for code optimization.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS using React, Next.js, and AWS enabling 6K+ students to access lessons, quizzes, and interactive content.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack LMS with React, Next.js, Node.js, and MySQL supporting lesson uploads, quizzes, and real-time dashboards.
\item Implemented secure authentication, role-based access control, and optimized SQL queries for high concurrent user performance.
\item Deployed on AWS with CDN caching, SSL encryption, and load balancing ensuring reliable access for over 6,000 active students.
\item Integrated UI/UX design principles and responsive layouts using CSS3/SCSS for accessibility and cross-device compatibility.
\end{itemize}

\textbf{Custom Business Web Solutions} -- \emph{Personal Project}

\vspace{-1pt}

Developed ecommerce sites, POS systems, and landing pages using React, Next.js, and headless CMS with Stripe payment integration.
\vspace{-1pt}
\begin{itemize}
\item Built custom ecommerce solutions with Next.js, headless CMS integration, and Shopify APIs for inventory and order management.
\item Implemented secure authentication, payment processing with Stripe API, and responsive UI design using HTML5, CSS3, and SCSS.
\item Collaborated with clients using Jira to gather requirements and translate business needs into scalable, user-friendly applications.
\item Optimized performance, SEO, and UI/UX across projects deployed on AWS and Netlify ensuring fast load times and high engagement.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}