% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven DevOps Engineer with 4+ years building scalable cloud infrastructure and automating CI/CD pipelines using AWS, Azure, Docker, and Kubernetes. Experienced in scripting with Python, Bash, and PowerShell to streamline deployments and infrastructure management. Proven ability to design resilient systems, implement Infrastructure as Code with Terraform, and maintain high-availability environments while collaborating in Agile teams to deliver secure, efficient solutions.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud \& Infrastructure:} Azure, AWS, GCP, IaaS, Virtual Machines, Blob Storage

\textbf{DevOps \& Automation:} CI/CD, Jenkins, GitHub Actions, GitLab CI/CD, Terraform, Ansible

\textbf{Scripting \& Programming:} Python, Bash, PowerShell, Shell Scripting, JavaScript

\textbf{Containerization \& Orchestration:} Docker, Kubernetes, Docker Compose, Container Management

\textbf{Monitoring \& Logging:} CloudWatch, Cloud Monitoring, Logging, Performance Optimization

\textbf{Systems Administration:} Windows Server, Linux, Ubuntu, Active Directory, VPN

\textbf{Database \& Data Technologies:} PostgreSQL, MySQL, MongoDB, SQL Server, Database Administration

\textbf{Security \& Compliance:} IAM, Encryption, OWASP, TLS, Security Best Practices

\textbf{Version Control \& Collaboration:} Git, GitHub, GitLab, Bitbucket, Jira, Confluence

\textbf{Soft Skills:} Communication, Collaboration, Ownership, Adaptability, Problem Solving

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Deployed and maintained cloud infrastructure on AWS using Docker, CI/CD pipelines, and Infrastructure as Code practices.
\item Automated deployment workflows with GitHub Actions and GitLab CI/CD, reducing manual release efforts and improving reliability.
\item Monitored application performance using CloudWatch and logging tools, ensuring consistent uptime and rapid incident response.
\item Implemented secure authentication and IAM policies across cloud environments to meet organizational security standards.
\item Collaborated in Agile teams through sprint planning, code reviews, and technical documentation for seamless knowledge transfer.
\item Optimized infrastructure scalability and resource utilization using Docker containers and Kubernetes orchestration strategies.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in designing and deploying enterprise applications with a focus on infrastructure, testing, and deployment phases.
\item Gained hands-on experience with cloud platforms, scripting, and automation tools in Agile development workflows.
\item Supported system administration tasks including configuration management, backup strategies, and performance tuning.
\item Collaborated with cross functional teams to gather requirements, conduct testing, and document deployment procedures.
\item Contributed to improving system reliability by identifying performance bottlenecks and implementing optimization strategies.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS on AWS with Docker, CDN, and SSL encryption, supporting 6K+ students with high availability.
\vspace{-1pt}
\begin{itemize}
\item Deployed full stack LMS on AWS using EC2, RDS, and S3 with Docker containers for consistent environment provisioning.
\item Automated deployment pipelines using CI/CD tools to enable rapid releases with zero downtime and rollback capabilities.
\item Configured CDN caching, SSL/TLS encryption, and IAM policies to ensure secure and performant access for concurrent users.
\item Monitored application health using CloudWatch and logging services, resolving incidents proactively to maintain uptime.
\end{itemize}

\textbf{PROSPR " Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Deployed real-time chat app on AWS App Runner using Docker containers with automated CI/CD for scalable accessibility.
\vspace{-1pt}
\begin{itemize}
\item Containerized application with Docker and deployed on AWS App Runner for auto-scaling and low-latency communication.
\item Integrated AWS Polly API and Azure Speech Services, managing cross-cloud authentication and secure API configuration.
\item Implemented CI/CD pipelines using GitHub Actions to automate testing, build, and deployment across staging and production.
\item Configured monitoring and alerting to track application performance, latency, and availability with CloudWatch dashboards.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}