% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with hands-on experience in full stack development, cloud infrastructure, and automation. Strong analytical and problem-solving skills with proven ability to deliver scalable, high-performance applications. Proficient in Python, JavaScript, React, and AWS with demonstrated expertise in data analysis, system optimization, and collaborative teamwork. Disciplined approach to executing complex projects under pressure while maintaining strict attention to detail and adherence to best practices.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, SQL, Bash, PowerShell, HTML, CSS

\textbf{Data Analysis \& Automation:} pandas, NumPy, Excel, ETL Pipelines, Workflow Automation, Jenkins

\textbf{Cloud \& Infrastructure:} AWS, Docker, CI/CD, Monitoring, Logging, CloudWatch

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQL Queries, Database Design

\textbf{Financial \& Trading Systems:} API Integration, Real-time Data Processing, Risk Management, Automation

\textbf{Development Practices:} Agile, Scrum, Testing, Documentation, Code Reviews, Performance Optimization

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Discipline, Analytical Thinking

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js to enhance functionality and user experience.
\item Implemented RESTful APIs, optimized SQL queries, and integrated secure payment systems improving reliability and performance.
\item Deployed and maintained cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and availability.
\item Collaborated within Agile teams through code reviews, sprint planning, and pair programming to ensure high-quality deliverables.
\item Applied test-driven development and secure coding standards throughout SDLC improving maintainability and reducing production issues.
\item Led backend development for multiple applications while mentoring junior developers on best coding and deployment practices.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level web and mobile applications across both frontend and backend components.
\item Contributed to the design and implementation of the Proposal Management and Mailroom Tracking Systems for operational efficiency.
\item Worked closely with cross functional teams to gather requirements, perform testing, and support deployment phases successfully.
\item Gained hands-on experience in full stack development, software testing, and secure coding within Agile workflows and sprints.
\item Collaborated in project reviews to identify improvements in performance, scalability, and code maintainability across systems.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Automated Cryptocurrency Trading Bot} -- \emph{Personal Project}

\vspace{-1pt}

Created a Python trading bot using Binance API and WebSocket to automate trade execution with risk control and live monitoring.
\vspace{-1pt}
\begin{itemize}
\item Developed a fully automated trading bot in Python using Binance API and WebSocket for real-time data streaming and execution.
\item Implemented dynamic trading strategies, stop-loss mechanisms, and order execution algorithms to optimize performance under pressure.
\item Integrated pandas and NumPy for market analysis and backtesting to improve trading accuracy and risk management compliance.
\item Deployed using Docker on AWS EC2 for 24/7 uptime, reliability, and monitoring with detailed logging and performance reporting.
\end{itemize}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes efficiently.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL to support online education during the pandemic lockdown.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time progress dashboards for educators and admins.
\item Implemented secure authentication, role-based access, and optimized database queries for high concurrent usage and data integrity.
\item Deployed the platform on AWS with CDN caching and SSL encryption, ensuring reliable access for over 6,000 students concurrently.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}