% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Developer with proven expertise in cloud infrastructure and DevOps automation. Skilled in AWS services including Lambda, EC2, S3, CloudWatch, and IAM with hands-on experience in Infrastructure as Code using CloudFormation and Terraform. Proficient in Python, Bash scripting, and CI/CD pipelines through GitHub Actions and GitLab. Strong background in building scalable applications, implementing security best practices, and collaborating across technical teams to deliver reliable cloud solutions.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud \& AWS Services:} AWS Lambda, EC2, S3, CloudWatch, IAM, KMS, Route53, CloudFormation, VPC

\textbf{DevOps \& Infrastructure:} Docker, Kubernetes, Terraform, CI/CD Pipelines, GitHub Actions, GitLab CI/CD

\textbf{Programming \& Scripting:} Python, Bash, JavaScript, SQL, PowerShell

\textbf{Development \& Frameworks:} Django, Flask, FastAPI, React, Node.js, REST API

\textbf{Database \& Data:} PostgreSQL, MySQL, MongoDB, DynamoDB, ETL Pipelines, Data Warehousing

\textbf{Security \& Networking:} IAM Policies, Encryption, OAuth, JWT, VPN, Cloud Networking, OWASP

\textbf{Methodologies \& Tools:} Agile, Scrum, Git, Jira, Postman, System Design

\textbf{Soft Skills:} Analytical Thinking, Communication, Collaboration, Adaptability, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using JavaScript, React, and Node.js while deploying on AWS infrastructure with Docker.
\item Implemented RESTful APIs with secure authentication, optimized database queries, and integrated payment systems for reliability.
\item Deployed cloud-based solutions using AWS services, Docker containers, and CI/CD pipelines ensuring consistent uptime.
\item Collaborated within Agile teams through code reviews, sprint planning, and cross functional communication to deliver quality.
\item Applied Infrastructure as Code principles and secure coding standards throughout SDLC improving maintainability.
\item Led backend development initiatives while mentoring team members on best practices for deployment and cloud architecture.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise applications across frontend and backend using modern frameworks and cloud technologies.
\item Contributed to design and implementation of management systems with focus on scalability and performance optimization.
\item Worked with cross functional teams to gather requirements, perform testing, and support cloud deployment initiatives.
\item Gained hands-on experience in full stack development, Infrastructure as Code, and secure coding within Agile workflows.
\item Collaborated in project reviews to identify improvements in performance, cloud infrastructure, and code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL deployed on AWS infrastructure for scalability.
\item Integrated secure authentication with IAM policies, role-based access, and optimized database queries for concurrent users.
\item Implemented real-time dashboards for performance tracking with CloudWatch monitoring and automated alerting mechanisms.
\item Deployed platform on AWS using S3, EC2, CloudFormation, and CDN ensuring reliable access for over 6,000 students.
\end{itemize}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Automated vulnerability scanning and patching to strengthen enterprise security and reduce manual effort.
\vspace{-1pt}
\begin{itemize}
\item Developed automated workflows using Python and CI/CD pipelines for vulnerability scanning and patch deployment processes.
\item Integrated security APIs for real-time vulnerability reporting with risk prioritization and compliance tracking dashboards.
\item Created monitoring dashboards and alert systems using CloudWatch to track security compliance and remediation progress.
\item Reduced manual intervention by 60\% and accelerated patch cycles through full CI/CD automation with Infrastructure as Code.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}