% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Software Engineer with 2+ years of experience building business-critical backend systems, APIs, and internal tools using TypeScript, React, and Node.js. Skilled in PostgreSQL database design, AWS cloud infrastructure, and developing reliable platforms for inventory management, operational workflows, and system integrations. Experienced in delivering deterministic, auditable solutions that support real-time data workflows and external customer interactions.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, SQL, HTML5, CSS3, PHP

\textbf{Frameworks \& Libraries:} React, Next.js, Node.js, NestJS, Express.js, Redux

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, Database Design, Query Optimization

\textbf{Cloud \& DevOps:} AWS, AWS EC2, Docker, CI/CD, GitHub Actions, Infrastructure as Code

\textbf{API \& Integration:} REST API, GraphQL, WebSockets, API Gateway, Microservices, OAuth

\textbf{Software Development Practices:} Agile, Scrum, System Design, Testing, Code Reviews, Technical Documentation

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Ownership, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed full stack web applications using JavaScript, TypeScript, React, and Node.js to enhance platform reliability and workflows.
\item Implemented RESTful APIs, optimized PostgreSQL queries, and integrated secure payment systems improving consistency and performance.
\item Deployed and maintained cloud applications using AWS EC2, Docker, and CI/CD pipelines ensuring high availability and uptime.
\item Collaborated within Agile teams through code reviews, sprint planning, and pair programming to deliver business-critical features.
\item Applied test-driven development and secure coding practices throughout SDLC improving maintainability and reducing production issues.
\item Led backend development for multiple applications while mentoring junior developers on best practices and deployment workflows.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications across both frontend and backend components using modern frameworks.
\item Contributed to design and implementation of internal operational systems including inventory and tracking platforms.
\item Worked closely with cross functional teams to gather requirements, perform testing, and support deployment phases.
\item Gained hands-on experience in full stack development, database modeling, and secure coding within Agile workflows.
\item Collaborated in project reviews to identify improvements in performance, scalability, and code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS using React, Node.js, and PostgreSQL enabling 6K+ students to access lessons, quizzes, and progress tracking.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and PostgreSQL to support concurrent user sessions and workflows.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards for administrative users.
\item Implemented secure authentication, role-based access control, and optimized database queries for high-volume operations.
\item Deployed the platform on AWS EC2 with SSL encryption and monitoring ensuring reliable access for over 6,000 active users.
\end{itemize}

\textbf{Custom Business Web Solutions} -- \emph{Personal Project}

\vspace{-1pt}

Built POS systems, e-commerce sites, and inventory management tools using React, Next.js, and Express.js for business workflows.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed custom web solutions using React, Next.js, and Express.js for inventory and operational management.
\item Implemented secure authentication, inventory tracking, and payment processing with Stripe API integration for client systems.
\item Collaborated with clients to gather requirements and translate business needs into scalable, maintainable applications.
\item Optimized UI performance, responsiveness, and data consistency across all projects to enhance reliability and user experience.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}