% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Adaptable Software Engineer with 3+ years delivering full stack web applications using Python, React, and Node.js alongside cloud platforms like AWS and GCP. Skilled in building scalable data pipelines, integrating REST APIs, and deploying automated workflows with Docker and CI/CD. Experienced collaborating with cross functional stakeholders in Agile environments to translate technical solutions into business impact. Passionate about leveraging AI tools and emerging technologies to accelerate development cycles and solve diverse problems.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, SQL, HTML5, CSS3, Bash, PowerShell

\textbf{Frameworks \& Libraries:} React, Django, Flask, FastAPI, Node.js, Bootstrap

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, ETL Pipelines, BigQuery, pandas

\textbf{Cloud \& DevOps:} AWS, GCP, Docker, Kubernetes, CI/CD, GitHub Actions

\textbf{AI \& Automation:} AI Integration, Prompt Engineering, LLM API, Workflow Automation, Machine Learning APIs

\textbf{Software Development:} Agile, Scrum, REST API, System Design, TDD, Code Reviews

\textbf{Soft Skills:} Communication, Adaptability, Problem Solving, Collaboration, Continuous Learning, Empathy

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using Python, React, and Node.js to enhance business workflows and functionality.
\item Designed RESTful APIs, optimized SQL queries, and integrated secure payment systems to improve reliability and performance.
\item Deployed cloud-based applications on AWS with Docker and CI/CD pipelines ensuring consistent uptime and rapid delivery cycles.
\item Collaborated with cross functional teams to gather requirements, deliver solutions quickly, and manage stakeholder expectations.
\item Leveraged Agile methodologies, code reviews, and pair programming to maintain high-quality deliverables and team alignment.
\item Mentored junior developers on backend development best practices, secure coding standards, and deployment automation workflows.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to enterprise web and mobile applications across frontend and backend components in Agile development environments.
\item Assisted in designing and implementing systems for proposal management and tracking workflows to streamline business operations.
\item Collaborated with cross functional teams to gather requirements, perform testing, and support deployment phases for production.
\item Gained hands-on experience in full stack development, software testing, and secure coding practices throughout the SDLC lifecycle.
\item Participated in project reviews to identify improvements in performance, scalability, and maintainability across multiple systems.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to access notes, videos, and quizzes with real-time tracking and secure authentication.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack LMS using React, Node.js, and MySQL to support online education with lesson uploads and performance tracking.
\item Integrated real-time progress dashboards for teachers and students with secure authentication and role-based access controls.
\item Optimized database queries and implemented caching strategies to handle high concurrent usage from over 6,000 active students.
\item Deployed platform on AWS with CDN caching and SSL encryption ensuring reliable access and data security for all users globally.
\end{itemize}

\textbf{Automated Cryptocurrency Trading Bot} -- \emph{Personal Project}

\vspace{-1pt}

Created Python trading bot using Binance API and WebSocket to automate trade execution with risk controls and live monitoring.
\vspace{-1pt}
\begin{itemize}
\item Developed automated trading bot in Python using Binance API and WebSocket for real-time data streaming and order execution.
\item Implemented dynamic trading strategies, stop-loss mechanisms, and risk management algorithms to improve trading performance.
\item Integrated pandas and NumPy for market analysis and backtesting to validate trading accuracy and optimize strategy performance.
\item Deployed using Docker on AWS EC2 for 24/7 uptime with detailed logging and monitoring to ensure reliability and rapid issue response.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}