% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Full Stack Web Developer with proven expertise in React, TypeScript, Python, and AWS, specializing in building scalable web applications from concept to production. Experienced in clean architecture, FastAPI backend development, PostgreSQL databases, and deploying AI-integrated solutions in enterprise environments. Demonstrated ability to ship production-ready features, work cross-functionally with stakeholders, and maintain high-performance systems serving thousands of users with strong product intuition and end-to-end ownership.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, TypeScript, SQL, HTML5, CSS3, Bash

\textbf{Frontend Technologies:} React, Redux, React Query, Bootstrap, Material UI, Responsive Design

\textbf{Backend \& APIs:} FastAPI, Django, Flask, Node.js, REST API, GraphQL

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQLite, Redis

\textbf{Cloud \& Infrastructure:} AWS, Docker, AWS Lambda, AWS EC2, AWS S3, CloudWatch

\textbf{DevOps \& Development Practices:} CI/CD, GitHub Actions, Agile, Code Reviews, Unit Testing

\textbf{AI \& Integration:} AI Integration, LLM API, ChatGPT API, Prompt Engineering, Automation

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Ownership, Problem Solving, Product Sense

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using React, TypeScript, and Node.js to deliver production-grade e-commerce functionality.
\item Architected RESTful APIs with FastAPI and optimized PostgreSQL queries to enhance system performance and reliability for enterprise clients.
\item Deployed cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and seamless feature rollouts.
\item Collaborated within Agile teams through code reviews, sprint planning, and pair programming to ship high-quality customer-facing features.
\item Applied test-driven development and secure coding standards throughout the SDLC improving maintainability and reducing production defects.
\item Led backend development initiatives while mentoring junior developers on architecture design, deployment best practices, and product thinking.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications across frontend and backend components using React, Python, and SQL databases.
\item Contributed to the design and implementation of the Proposal Management System and Mailroom Tracking System for internal stakeholders.
\item Worked closely with cross functional teams to gather requirements, perform integration testing, and support production deployment phases.
\item Gained hands-on experience in full stack development, API security, and Agile workflows within fast-paced collaborative environments.
\item Participated in project reviews to identify performance improvements, scalability enhancements, and code maintainability optimizations.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes using React.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack LMS using React, Node.js, and PostgreSQL to support online education with real-time progress tracking dashboards.
\item Integrated secure authentication, role-based access control, and optimized database queries for high concurrent usage and performance.
\item Implemented modules for lesson uploads, quizzes, and student analytics with intuitive UI/UX for teachers and administrators.
\item Deployed on AWS with CDN caching, SSL encryption, and autoscaling to ensure reliable access for over 6,000 active students daily.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed inclusive real-time chat app for low-vision users integrating accessibility features and AI-powered speech services.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Node.js, and WebSockets with accessibility-focused UI adhering to WCAG standards.
\item Integrated AWS Polly and Azure Speech Services to enable seamless text-to-speech and voice-to-text communication for inclusivity.
\item Tested with assistive technologies and conducted user feedback sessions to ensure usability for individuals with reading challenges.
\item Deployed on AWS using Docker containers for scalable, low-latency communication with monitoring and automated deployment pipelines.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}