% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Detail-oriented Front-End Developer with 3+ years of experience building responsive web applications using JavaScript, React, and modern frontend technologies. Proven ability to deliver high-performance, user-centric interfaces while collaborating with cross-functional teams in Agile environments. Skilled in consuming RESTful APIs, implementing accessible design practices, and optimizing UI performance. Committed to writing clean, maintainable code and continuously learning new technologies to create seamless digital experiences.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Frontend Technologies:} JavaScript (ES6+), HTML5, CSS3, React, Redux, Bootstrap, Material UI

\textbf{Programming \& Scripting:} TypeScript, Python, PHP, SQL, Bash, PowerShell

\textbf{Backend \& APIs:} Node.js, REST API, Django, GraphQL, JSON, WebSockets

\textbf{Development Tools \& Practices:} Git, GitHub, Agile, Scrum, CI/CD, Unit Testing

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, GitHub Actions, GitLab CI/CD

\textbf{Design \& Performance:} Responsive Design, UI/UX, Performance Optimization, Accessibility Standards, Web Design

\textbf{Soft Skills:} Collaboration, Communication, Problem Solving, Adaptability, Attention to Detail, Team Leadership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed responsive web applications using JavaScript, React, and modern frontend frameworks to deliver seamless user experiences.
\item Built and consumed RESTful APIs while optimizing performance and ensuring secure data handling across full stack applications.
\item Collaborated with designers and backend teams in Agile sprints to create accessible, user-centric interfaces for diverse users.
\item Utilized Git version control and CI/CD pipelines to maintain code quality and support continuous integration and deployment.
\item Applied object-oriented and functional programming principles in JavaScript to build scalable, maintainable frontend components.
\item Conducted code reviews and debugging sessions using modern tools to optimize UI performance and resolve cross-browser issues.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in building responsive web interfaces using HTML5, CSS3, and JavaScript for enterprise-level applications.
\item Worked closely with cross-functional teams to gather requirements and implement frontend features aligned with user needs.
\item Contributed to performance tuning and debugging efforts to enhance UI responsiveness and accessibility across platforms.
\item Gained hands-on experience with Agile methodologies including sprint planning, stand-ups, and iterative development cycles.
\item Supported testing and deployment phases ensuring consistent user experience and adherence to inclusive design practices.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a responsive frontend using React with optimized components for lesson uploads, quizzes, and dashboards.
\item Integrated RESTful APIs with Node.js backend to handle real-time data updates and secure user authentication with JWT tokens.
\item Implemented role-based access control and performance optimization techniques ensuring smooth experience for 6,000+ users.
\item Deployed the platform on AWS with CDN caching, SSL encryption, and monitoring to ensure high availability and security.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users and individuals with reading challenges, integrating accessibility features.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat interface using React and Socket.io with accessibility-focused design adhering to WCAG standards.
\item Integrated AWS Polly and Azure Speech Services to enable text-to-speech and voice-to-text for inclusive communication.
\item Conducted extensive testing with assistive technologies to ensure usability for users with visual and reading challenges.
\item Deployed on AWS App Runner with Docker containers optimizing for scalable, low-latency, and high-performance delivery.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}