% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Frontend Developer with 3+ years building scalable, user-centered web applications using React, TypeScript, and modern JavaScript. Experienced in developing intuitive UI components, implementing responsive design, and collaborating with cross-functional teams in Agile environments. Skilled in translating complex technical requirements into elegant, accessible interfaces with strong understanding of UI/UX principles and HCI standards. Proven ability to deliver high-performance solutions integrating secure authentication, real-time features, and cloud infrastructure.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, HTML5, CSS3, SQL

\textbf{Frontend Frameworks \& Libraries:} React, Next.js, Redux, React Query, Bootstrap, Material UI

\textbf{UI/UX \& Design:} UI/UX Design, Responsive Design, HCI Principles, Accessibility (WCAG), Data Visualization

\textbf{Backend \& APIs:} Node.js, Express.js, REST API, GraphQL, WebSockets, Django

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, Firebase, SQLite

\textbf{Cloud \& DevOps:} AWS, Docker, CI/CD, GitHub Actions, GitLab CI/CD, Kubernetes

\textbf{Development Practices:} Agile, Scrum, Code Reviews, Unit Testing, TDD, Performance Optimization

\textbf{Soft Skills:} Collaboration, Problem Solving, Communication, Adaptability, Ownership, Iterative Design

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js with responsive, user-centered UI design.
\item Implemented RESTful APIs, optimized database queries, and integrated secure authentication flows to improve system reliability.
\item Deployed and maintained cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and performance.
\item Collaborated within Agile teams through code reviews, sprint planning, and iterative feedback cycles to deliver high-quality UIs.
\item Applied test-driven development and usability testing throughout SDLC improving maintainability and reducing production issues.
\item Led frontend development for multiple web applications while mentoring junior developers on best practices and modern frameworks.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level web applications with a focus on intuitive frontend components and responsive UI design.
\item Contributed to the design and implementation of the Proposal Management and Mailroom Tracking Systems with interactive interfaces.
\item Worked closely with cross-functional teams to gather requirements, perform usability testing, and support deployment phases.
\item Gained hands-on experience in full stack development, UI refinement, and secure coding within collaborative Agile workflows.
\item Collaborated in project reviews to identify improvements in performance, scalability, user experience, and code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users with accessibility-focused UI design integrating HCI best practices.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and WebSockets with accessibility-focused UI design and HCI principles.
\item Integrated AWS Polly and Azure Speech Services to enable text-to-speech and voice-to-text communication for inclusive usability.
\item Followed WCAG accessibility standards and tested with assistive technologies ensuring intuitive, high-impact user experience.
\item Deployed on AWS App Runner with Docker containers for scalable, low-latency communication and responsive performance.
\end{itemize}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with notes, videos, and interactive quizzes using modern frontend frameworks.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full-stack LMS using React, Node.js, and MySQL with intuitive UI components for online education.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time progress dashboards and data visualization.
\item Implemented secure authentication, role-based access, and optimized database queries for high concurrent usage and responsiveness.
\item Deployed the platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 students globally.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}