% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Frontend Engineer with proven expertise in building scalable, high-performance web applications using React, JavaScript, and modern frontend frameworks. Experienced in developing intuitive user interfaces, integrating responsive design principles, and collaborating with cross-functional teams to deliver seamless user experiences. Skilled in full stack development with proficiency in Node.js, cloud technologies, and Agile methodologies, bringing strong problem-solving abilities and technical communication skills to fast-paced startup environments.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Frontend Technologies:} JavaScript, React, HTML5, CSS3, Tailwind CSS, Bootstrap

\textbf{Programming \& Scripting:} TypeScript, Python, Node.js, SQL, Bash

\textbf{Frameworks \& Libraries:} Redux, React Query, Next.js, Material UI, jQuery

\textbf{Development Tools \& Practices:} Git, GitHub, CI/CD, Agile, Scrum, Code Reviews

\textbf{Backend \& Database:} REST API, PostgreSQL, MySQL, MongoDB, GraphQL

\textbf{Cloud \& DevOps:} AWS, Docker, GitHub Actions, Performance Optimization

\textbf{Design \& UX:} Responsive Design, UI/UX, Web Design, Brand Consistency

\textbf{Soft Skills:} Communication, Team Collaboration, Problem Solving, Adaptability, Attention to Detail

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js to enhance e-commerce functionality.
\item Implemented RESTful APIs, optimized SQL queries, and integrated secure payment systems improving system reliability and performance.
\item Collaborated closely with UX/UI designers translating design concepts into functional, responsive frontend code using modern frameworks.
\item Deployed cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and high availability.
\item Applied test-driven development and secure coding standards throughout SDLC improving maintainability and reducing production issues.
\item Worked within Agile teams through code reviews, sprint planning, and pair programming to ensure high-quality deliverables.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications across frontend and backend components using modern JavaScript frameworks.
\item Contributed to the design and implementation of Proposal Management and Mailroom Tracking Systems ensuring high graphic standards.
\item Worked closely with cross-functional teams to gather requirements, perform testing, and support deployment phases.
\item Gained hands-on experience in full stack development, software testing, and secure coding within Agile workflows.
\item Collaborated in project reviews to identify improvements in performance, scalability, and code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with notes, videos, and interactive quizzes during the pandemic.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL to support online education during the pandemic.
\item Implemented responsive and adaptive design principles ensuring seamless experiences across desktop and mobile devices.
\item Integrated secure authentication, role-based access, and optimized database queries for high concurrent usage and performance.
\item Deployed the platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 students.
\end{itemize}

\textbf{Custom Business Web Solutions} -- \emph{Personal Project}

\vspace{-1pt}

Built POS, e-commerce sites, landing pages, and inventory systems with secure, responsive design improving workflow efficiency.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed multiple custom web solutions using React, Next.js, and Express.js with high-performance frontend code.
\item Implemented secure authentication, inventory tracking, and payment processing with Stripe API integration ensuring reliability.
\item Collaborated with clients to gather requirements and translate business needs into scalable, intuitive user interfaces.
\item Optimized UI performance, responsiveness, and SEO across all client projects enhancing user engagement and brand consistency.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}