% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Frontend Developer with strong expertise in React, JavaScript, and modern web technologies. Proven ability to build responsive, pixel-perfect user interfaces and scalable applications using TypeScript, Next.js, and Tailwind CSS. Experienced in translating Figma designs into production-ready code, collaborating in Agile teams, and taking ownership of projects from concept to deployment. Adept at cloud infrastructure, CI/CD workflows, and delivering high-quality solutions in fast-paced environments.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Frontend Technologies:} React, Next.js, TypeScript, JavaScript, HTML5, CSS3

\textbf{Styling \& UI Frameworks:} Tailwind CSS, Bootstrap, Material UI, SASS, Responsive Design

\textbf{Backend \& APIs:} Node.js, Express.js, REST API, GraphQL, Serverless

\textbf{Database \& Cloud:} PostgreSQL, MySQL, MongoDB, AWS, Docker, Firebase

\textbf{Development Tools:} Git, GitHub, CI/CD, Figma, Jira, Slack

\textbf{Soft Skills:} Ownership, Collaboration, Communication, Adaptability, Problem Solving, Autonomy

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Built responsive full stack web applications using JavaScript, React, and Node.js delivering scalable e-commerce solutions.
\item Translated Figma designs into pixel-perfect, cross-device compatible UIs ensuring consistent user experience and accessibility.
\item Implemented RESTful APIs and optimized database queries improving system performance and reliability across production environments.
\item Deployed cloud-based applications using AWS, Docker, and CI/CD pipelines maintaining high availability and consistent uptime.
\item Collaborated in Agile teams through GitHub workflows, code reviews, and sprint planning ensuring timely, high-quality deliverables.
\item Led backend development for multiple applications while mentoring junior developers on best practices and deployment strategies.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in building enterprise web and mobile applications contributing to both frontend and backend development efforts.
\item Worked with cross functional teams to gather requirements, conduct testing, and support deployment of production-ready systems.
\item Contributed to design and implementation of Proposal Management and Mailroom Tracking Systems using modern development frameworks.
\item Gained hands-on experience in full stack development, secure coding practices, and Agile workflows across multiple project cycles.
\item Participated in project reviews identifying opportunities for performance optimization, scalability improvements, and code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to access notes, videos, and interactive quizzes with real-time progress tracking.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed full stack LMS using React, Node.js, and MySQL supporting real-time student engagement and learning.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with dynamic dashboards for teachers and administrators.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent user loads.
\item Deployed platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 active students daily.
\end{itemize}

\textbf{Custom Business Web Solutions} -- \emph{Personal Project}

\vspace{-1pt}

Built POS systems, e-commerce sites, landing pages, and inventory management tools with secure, responsive web design.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed multiple custom web solutions using React, Next.js, and Express.js tailored to client business needs.
\item Implemented secure authentication, inventory tracking, and payment processing with Stripe API integration for e-commerce platforms.
\item Collaborated with clients to gather requirements and translate business goals into scalable, user-friendly web applications.
\item Optimized UI performance, cross-device responsiveness, and SEO across all projects enhancing user engagement and conversion rates.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}