% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Frontend Developer with proven expertise in building scalable web applications using React, JavaScript, and TypeScript. Skilled in translating design files into responsive, production-ready interfaces while maintaining high code quality and attention to detail. Experienced in implementing RESTful APIs, deploying cloud-based applications on AWS, and working within Agile teams. Adept at leveraging AI tools to accelerate development workflows and troubleshoot complex frontend issues across browsers and devices.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Frontend Technologies:} React, TypeScript, JavaScript, HTML5, CSS3, Redux

\textbf{UI Frameworks \& Styling:} Bootstrap, Material UI, SASS, Responsive Design, Mobile-First Design

\textbf{Development Tools \& Workflow:} Git, GitHub Actions, Docker, CI/CD Pipelines, VS Code

\textbf{Backend \& APIs:} Node.js, REST API, GraphQL, WebSockets, API Integration

\textbf{Cloud \& Deployment:} AWS, AWS S3, AWS EC2, AWS Lambda, CloudWatch

\textbf{Data \& Visualization:} Chart.js, Data Visualization, PostgreSQL, MongoDB, Real-Time Data

\textbf{Testing \& Quality Assurance:} Unit Testing, Integration Testing, Debugging, Code Reviews, Performance Optimization

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Problem Solving, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable web applications using JavaScript, React, and Node.js with responsive design for desktop and mobile interfaces.
\item Translated design requirements into production-ready React components maintaining consistency across frontend codebase.
\item Implemented RESTful APIs connecting frontend interfaces to backend services with dynamic data flows and real-time updates.
\item Deployed cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring reliable performance across browsers.
\item Collaborated within Agile teams through code reviews and sprint planning ensuring high-quality deliverables and standards.
\item Applied secure coding practices and optimized frontend performance improving maintainability and reducing production issues.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing web applications with frontend and backend components using React and Node.js frameworks.
\item Contributed to design implementation of Proposal Management and Mailroom Tracking Systems with responsive layouts.
\item Worked closely with cross-functional teams gathering requirements, performing testing, and supporting deployment phases.
\item Gained hands-on experience debugging frontend issues, optimizing performance, and implementing accessibility standards.
\item Collaborated in project reviews identifying improvements in scalability, code maintainability, and user experience design.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built scalable LMS enabling 6K+ students to learn with interactive dashboards, real-time progress tracking, and responsive design.
\vspace{-1pt}
\begin{itemize}
\item Designed full-stack LMS using React, Node.js, and MySQL supporting lesson uploads, quizzes, and performance tracking dashboards.
\item Implemented responsive frontend interfaces with dynamic data flows ensuring accessibility across desktop and mobile devices.
\item Integrated secure authentication and role-based access with optimized database queries for high concurrent usage scenarios.
\item Deployed platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 concurrent students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed inclusive real-time chat app with accessibility-focused UI using React, Node.js, and AWS speech integration services.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Node.js, and Socket.io with accessibility-focused responsive UI design.
\item Integrated AWS Polly and Azure Speech Services enabling text-to-speech and voice-to-text communication features.
\item Followed WCAG accessibility standards testing with assistive technologies ensuring inclusive usability across devices.
\item Deployed on AWS App Runner with Docker containers for scalable low-latency communication and reliable uptime monitoring.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}