% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Frontend Engineer with hands-on experience building scalable web applications using React, JavaScript, and TypeScript. Proven expertise in developing accessible, high-performance user interfaces and collaborating cross-functionally with Product, Design, and Backend teams. Skilled in modern frontend architecture, state management, and CI/CD pipelines with a strong foundation in cloud deployment and Agile methodologies. Passionate about delivering intuitive user experiences and contributing to collaborative engineering cultures.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, HTML5, CSS3, SQL

\textbf{Frontend Frameworks \& Libraries:} React, Redux, Next.js, Bootstrap, Material UI, Tailwind CSS

\textbf{Backend \& APIs:} Node.js, REST API, GraphQL, Django, Flask, Express.js

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, Firebase, SQLite

\textbf{Cloud \& DevOps:} AWS, Docker, CI/CD, GitHub Actions, Vercel, Kubernetes

\textbf{Testing \& Tools:} Jest, Unit Testing, Git, Postman, Webpack, Figma

\textbf{Development Practices:} Agile, Scrum, Code Reviews, Performance Optimization, Accessibility Standards, Design Patterns

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Ownership, Problem Solving, Team Leadership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full-stack web applications using JavaScript, React, and Node.js to enhance e-commerce functionality and user engagement.
\item Implemented RESTful APIs, optimized SQL queries, and integrated secure payment systems improving reliability and transaction throughput.
\item Deployed and maintained cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and rapid feature delivery.
\item Collaborated within Agile teams through code reviews, sprint planning, and pair programming to maintain high-quality code and best practices.
\item Applied test-driven development and accessibility standards throughout SDLC reducing production issues and improving user experience.
\item Led backend development for multiple applications while mentoring junior developers on secure coding and deployment best practices.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web and mobile applications across frontend and backend components using modern frameworks.
\item Contributed to the design and implementation of Proposal Management and Mailroom Tracking Systems improving operational workflows.
\item Worked closely with cross-functional teams to gather requirements, perform testing, and support deployment phases of key features.
\item Gained hands-on experience in full-stack development, software testing, and secure coding within Agile and Scrum methodologies.
\item Collaborated in project reviews to identify improvements in performance, scalability, accessibility, and overall code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full-stack LMS using React, Node.js, and MySQL to support online education during the pandemic for 6K+ students.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time progress dashboards for teachers and administrators.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent usage and fast load times.
\item Deployed the platform on AWS with CDN caching and SSL encryption ensuring reliable access, performance, and data security for all users.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users and individuals with reading challenges integrating accessibility features.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and Socket.io with accessibility-focused UI design for inclusive communication.
\item Integrated AWS Polly and Azure Speech Services to enable text-to-speech and voice-to-text communication for users with visual impairments.
\item Followed WCAG accessibility standards and tested with assistive technologies to ensure inclusive usability and compliance with a11y guidelines.
\item Deployed on AWS App Runner with Docker containers for scalable, low-latency communication and seamless performance under varying user loads.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}