% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Developer with 2+ years of experience building scalable SaaS web applications using React, Node.js, and TypeScript. Proven track record designing and launching high-performance systems from concept to production while collaborating in Agile teams. Strong computer science fundamentals with expertise in cloud infrastructure, API development, and system architecture. Skilled at owning technical initiatives, solving complex engineering challenges, and delivering impactful solutions in fast-paced environments.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, SQL, HTML5, CSS3, PHP

\textbf{Frontend Frameworks \& Libraries:} React, Redux, Next.js, Bootstrap, Material UI, Tailwind CSS

\textbf{Backend Frameworks \& APIs:} Node.js, Express.js, Django, Flask, REST API, GraphQL

\textbf{Databases \& Data Management:} PostgreSQL, MySQL, MongoDB, Firebase, Redis, SQLite

\textbf{Cloud Infrastructure \& DevOps:} AWS, Docker, Kubernetes, CI/CD, GitHub Actions, Terraform

\textbf{Software Development Practices:} Agile, Scrum, System Design, TDD, Code Reviews, Scalability

\textbf{Computer Science Fundamentals:} Data Structures, Algorithms, OOP, Design Patterns, Performance Optimization

\textbf{Soft Skills:} Critical Thinking, Problem Solving, Communication, Collaboration, Ownership, Adaptability

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Architected and developed scalable full stack web applications using React, Node.js, and TypeScript to deliver high-performance SaaS solutions.
\item Designed and implemented RESTful APIs with optimized database queries across PostgreSQL and MongoDB to improve system reliability.
\item Owned deployment of cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and high availability.
\item Collaborated within Agile teams through code reviews and sprint planning to deliver impactful features aligned with business objectives.
\item Applied test-driven development and secure coding standards throughout SDLC reducing production issues and enhancing maintainability.
\item Led backend development for multiple web applications while mentoring junior developers on system design and engineering best practices.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to developing enterprise-level web applications across frontend and backend using React and Node.js in Agile workflows.
\item Designed and implemented features for Proposal Management and Mailroom Tracking Systems with scalable and maintainable architecture.
\item Collaborated with cross-functional teams to gather requirements, perform integration testing, and support deployment phases effectively.
\item Gained hands-on experience in full stack development, API design, and secure coding practices within professional engineering environments.
\item Participated in project reviews to identify improvements in performance, scalability, and overall code quality across multiple initiatives.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS using React, Node.js, and MySQL enabling 6K+ students to learn with notes, videos, and interactive quizzes.
\vspace{-1pt}
\begin{itemize}
\item Architected and developed a full stack LMS using React, Node.js, and MySQL to support online education during the pandemic lockdown.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards for teachers and administrators.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent user performance.
\item Deployed the platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 students and educators.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive real-time chat app using React, Node.js, and Socket.io with accessibility features for low-vision users.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and Socket.io with an accessibility-focused UI design and responsive layout.
\item Integrated AWS Polly and Azure Speech Services to enable text-to-speech and voice-to-text communication for inclusive user experiences.
\item Followed WCAG accessibility standards and tested with assistive technologies to ensure full usability for users with reading challenges.
\item Deployed on AWS App Runner with Docker containers for scalable, low-latency communication and reliable uptime across all user sessions.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}