% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Frontend Web Developer with 3+ years of experience building responsive, accessible, and high-performance web applications using modern JavaScript frameworks including React, Node.js, and Angular. Proven expertise in translating design mockups into scalable user interfaces, optimizing front-end performance, and collaborating with cross-functional teams in Agile environments. Skilled in implementing WCAG accessibility standards, integrating RESTful APIs, and leveraging CI/CD pipelines to deliver seamless user experiences.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Frontend Technologies:} JavaScript (ES6+), TypeScript, React, HTML5, CSS3, SASS

\textbf{Frameworks \& UI Libraries:} Redux, React Query, Bootstrap, Material UI, Angular, jQuery

\textbf{Backend \& APIs:} Node.js, Express.js, REST API, GraphQL, WebSockets

\textbf{Database \& Cloud:} PostgreSQL, MySQL, MongoDB, AWS, GCP, Firebase

\textbf{DevOps \& Testing:} Git, Docker, CI/CD, GitHub Actions, Unit Testing, Integration Testing

\textbf{Development Practices:} Agile, Scrum, OOP, Functional Programming, Performance Optimization, WCAG 2.1

\textbf{Soft Skills:} Collaboration, Communication, Problem Solving, Adaptability, Attention to Detail, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js to deliver seamless user experiences.
\item Translated design mockups into responsive, accessible interfaces following modern front-end best practices and standards.
\item Implemented RESTful APIs and optimized front-end performance through lazy loading, code splitting, and caching techniques.
\item Collaborated with cross-functional teams in Agile environments through sprint planning, code reviews, and pair programming.
\item Built reusable UI components and contributed to design systems ensuring consistency across multiple applications.
\item Deployed cloud-based applications using AWS, Docker, and CI/CD pipelines while maintaining high availability and performance.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web and mobile applications with focus on frontend components and user interface design.
\item Contributed to the design and implementation of accessible, user-centric applications following WCAG accessibility standards.
\item Worked closely with designers and backend developers to integrate APIs and ensure seamless data flow between systems.
\item Participated in Agile ceremonies including sprint planning, stand-ups, and retrospectives to support team collaboration.
\item Gained hands-on experience in performance optimization, testing, and debugging to ensure code reliability and maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full-stack LMS using React, Node.js, and MySQL to support online education during the pandemic.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time progress dashboards for teachers.
\item Implemented secure authentication, role-based access, and optimized database queries for high concurrent usage and performance.
\item Deployed the platform on AWS with CDN caching and SSL encryption, ensuring reliable access for over 6,000 students globally.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users and individuals with reading challenges, integrating accessibility features.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and Socket.io with accessibility-focused UI design and components.
\item Integrated AWS Polly and Azure Speech Services to enable text-to-speech and voice-to-text communication for inclusivity.
\item Followed WCAG accessibility standards and tested with assistive technologies to ensure usability for low-vision users.
\item Deployed on AWS App Runner with Docker containers for scalable, low-latency communication and high availability.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}