% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Web Developer with proven expertise in building responsive, high-performance web applications using JavaScript, React, Node.js, and modern frontend frameworks. Skilled in HTML5, CSS3, TypeScript, API integration, and performance optimization. Experienced in collaborating with cross-functional teams, implementing accessibility standards, and delivering user-centric interfaces. Adept at version control with Git, CI/CD pipelines, and Agile methodologies to ensure seamless deployment and maintainability.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Frontend Technologies:} HTML5, CSS3, JavaScript, TypeScript, React, Redux

\textbf{Styling \& Frameworks:} SASS, Bootstrap, Material UI, Responsive Design, Flexbox

\textbf{Development Tools:} Git, GitHub, GitLab, NPM, Webpack, CI/CD

\textbf{API \& Backend Integration:} REST API, GraphQL, Node.js, Express.js, PostgreSQL

\textbf{Testing \& Performance:} Unit Testing, Debugging, Performance Optimization, Chrome DevTools

\textbf{Design \& Accessibility:} UI/UX Principles, WCAG Standards, Web Design, Cross-Browser Compatibility

\textbf{Soft Skills:} Communication, Team Collaboration, Problem Solving, Adaptability, Critical Thinking

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js improving user experience and e-commerce functionality.
\item Implemented RESTful APIs and optimized SQL queries to enhance system performance, reliability, and seamless frontend-backend integration.
\item Deployed cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and efficient release management.
\item Collaborated within Agile teams through code reviews, sprint planning, and pair programming to deliver high-quality user-centric interfaces.
\item Applied test-driven development and secure coding standards throughout SDLC improving maintainability and reducing production defects.
\item Mentored junior developers on best coding practices, version control workflows, and deployment strategies to enhance team productivity.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web and mobile applications across frontend and backend components using modern frameworks and tools.
\item Contributed to the design and implementation of the Proposal Management and Mailroom Tracking Systems ensuring functional requirements.
\item Worked closely with cross-functional teams to gather requirements, perform testing, and support deployment phases within Agile workflows.
\item Gained hands-on experience in full stack development, software testing, debugging, and secure coding throughout the software development lifecycle.
\item Collaborated in project reviews to identify improvements in performance, scalability, code maintainability, and user interface responsiveness.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with notes, videos, quizzes, and real-time progress tracking during the pandemic.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full-stack LMS using React, Node.js, and MySQL to support online education with responsive user interfaces.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards for teachers and students.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent usage and performance.
\item Deployed the platform on AWS with CDN caching and SSL encryption, ensuring reliable access for over 6,000 students with minimal downtime.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive real-time chat app for low-vision users integrating accessibility features and assistive technology support.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and Socket.io with accessibility-focused UI design and responsive layouts.
\item Integrated AWS Polly and Azure Speech Services to enable text-to-speech and voice-to-text communication for enhanced accessibility.
\item Followed WCAG accessibility standards and tested with assistive technologies to ensure inclusive usability and cross-browser compatibility.
\item Deployed on AWS App Runner with Docker containers for scalable, low-latency communication and consistent uptime across multiple devices.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}