% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Frontend Developer with hands-on experience building scalable web applications using JavaScript, React, and Node.js. Proficient in HTML5, CSS3, and modern frameworks including Angular and Bootstrap, with strong understanding of REST APIs and Agile methodologies. Skilled in writing clean, maintainable code and collaborating cross-functionally to deliver user-friendly solutions. Passionate about combining design and technology to create pixel-perfect, responsive interfaces.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, HTML5, CSS3, SQL

\textbf{Frameworks \& Libraries:} React, Angular, Node.js, Express.js, Bootstrap, Material UI

\textbf{Database \& Data Management:} MongoDB, PostgreSQL, MySQL, Firebase

\textbf{Cloud \& DevOps:} AWS, Docker, CI/CD, GitHub Actions, Git

\textbf{Software Development Practices:} Agile, Scrum, Unit Testing, Integration Testing, Code Reviews, SDLC

\textbf{Computer Science Fundamentals:} Data Structures, Algorithms, Object-Oriented Programming, Design Patterns

\textbf{Systems \& Networking:} REST API, Security best practices, Cloud computing, Version Control

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Continuous Learning, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack websites using JavaScript, React, Node.js, and HTML/CSS to enhance user experience and platform functionality.
\item Implemented secure RESTful APIs and optimized database queries to improve application performance, security, and maintainability.
\item Deployed and maintained cloud applications with AWS, Docker, and CI/CD pipelines ensuring high availability and consistent uptime.
\item Collaborated within Agile Scrum teams through code reviews, sprint planning, and pair programming to meet shared user story goals.
\item Applied test-driven development, automated testing frameworks, and secure coding practices throughout the software development lifecycle.
\item Led backend development initiatives and mentored junior developers on best practices for coding, testing, and deployment workflows.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications across frontend and backend components using modern JavaScript frameworks and tools.
\item Contributed to design, implementation, and testing of Proposal Management and Mailroom Tracking Systems within Agile workflows.
\item Worked with cross-functional teams to gather requirements, perform unit and integration testing, and support deployment phases.
\item Gained hands-on experience in full stack development, debugging, and secure coding practices aligned with SDLC best practices.
\item Collaborated in project reviews to identify and implement performance, scalability, and code maintainability improvements.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes online.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed full stack LMS using React, Node.js, and MySQL to support online education during the pandemic lockdown.
\item Integrated lesson uploads, interactive quizzes, and performance tracking with real-time dashboards for educators and students.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent user traffic.
\item Deployed platform on AWS with CDN caching and SSL encryption, ensuring reliable access for over 6,000 students and teachers.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users integrating accessibility features and assistive technology support.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Node.js, and Socket.io with accessibility-focused UI design and responsive layout.
\item Integrated AWS Polly and Azure Speech Services to enable text-to-speech and voice-to-text communication for inclusive usability.
\item Followed WCAG accessibility standards and tested with assistive technologies to ensure compliance and enhance user experience.
\item Deployed on AWS App Runner with Docker containers for scalable, low-latency, and reliable real-time communication capabilities.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}