% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Frontend Software Engineer with 5+ years of experience building scalable web applications and enterprise-grade features using React, JavaScript, and modern frontend frameworks. Proven expertise in designing distributed systems, implementing RESTful APIs, and deploying cloud-based solutions on AWS and GCP. Skilled in developing secure, user-centric platforms with role-based access control, authentication systems, and third-party integrations. Strong collaborator across cross-functional teams with deep understanding of Computer Science fundamentals and commitment to delivering high-quality, reliable software.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, HTML5, CSS3, SQL

\textbf{Frontend Frameworks \& Libraries:} React, Redux, Next.js, Angular, Bootstrap, Material UI

\textbf{Backend \& APIs:} Node.js, REST API, GraphQL, Django, Flask, Microservices

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, CI/CD, GitHub Actions, Terraform

\textbf{Database \& Authentication:} PostgreSQL, MongoDB, OAuth, JWT, SSO, IAM

\textbf{Security \& Architecture:} OWASP, API Security, RBAC, System Design, Scalability, TLS

\textbf{Development Practices:} Agile, Scrum, TDD, Code Reviews, Design Patterns, OOP

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Ownership, Problem Solving, Mentorship

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using React, Node.js, and REST APIs to deliver enterprise-grade features for clients.
\item Implemented authentication, role-based access control, and secure payment integrations to ensure system reliability and security.
\item Deployed cloud-based applications on AWS with Docker and CI/CD pipelines maintaining consistent uptime and high availability.
\item Collaborated with cross-functional teams through Agile workflows, code reviews, and sprint planning to deliver quality software.
\item Applied design patterns, test-driven development, and Computer Science fundamentals to improve code maintainability and performance.
\item Led backend architecture for multiple projects while mentoring junior developers on best practices and distributed system design.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to enterprise web application development focusing on frontend components, backend APIs, and database integrations.
\item Assisted in designing and implementing scalable systems including Proposal Management and Mailroom Tracking platforms.
\item Collaborated with product and engineering teams to gather requirements, perform integration testing, and support deployments.
\item Gained hands-on experience in full stack development, secure coding standards, and service-oriented architecture principles.
\item Participated in Agile ceremonies and code reviews to identify improvements in scalability, performance, and system reliability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS supporting 6K+ students with real-time dashboards, secure authentication, and role-based access control.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack LMS using React, Node.js, and MySQL with secure authentication and role-based permissions for educators.
\item Developed real-time performance tracking dashboards and quiz modules enabling teachers to monitor student progress effectively.
\item Implemented optimized database queries and caching strategies to handle high concurrent user traffic with minimal latency.
\item Deployed platform on AWS with SSL encryption, CDN integration, and load balancing ensuring reliable access for 6,000+ users.
\end{itemize}

\textbf{PROSPR " Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed inclusive real-time chat app with text-to-speech, voice-to-text, and WCAG-compliant UI for low-vision users.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Node.js, and WebSockets with accessibility-first UI design and navigation.
\item Integrated AWS Polly and Azure Speech Services APIs to enable seamless text-to-speech and voice-to-text communication features.
\item Applied WCAG accessibility standards and conducted testing with assistive technologies to ensure inclusive user experiences.
\item Deployed on AWS with Docker containers and autoscaling to support low-latency, scalable real-time messaging for diverse users.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}