% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Frontend Developer with 3+ years of experience building scalable, user-friendly web applications using JavaScript, TypeScript, and React. Proven ability to deliver high-quality features from design to deployment while collaborating with cross-functional teams. Skilled in developing complex data visualizations, state management solutions, and accessible user interfaces. Strong foundation in modern frontend architecture, performance optimization, and component-driven development with a focus on code quality and maintainability.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Frontend Technologies:} JavaScript, TypeScript, React, Redux, HTML5, CSS3

\textbf{UI Frameworks \& Libraries:} Material UI, Bootstrap, SASS, React Query, Chart.js

\textbf{Development \& Testing:} Git, GitHub, Unit Testing, Code Reviews, CI/CD, Agile

\textbf{Data \& Visualization:} REST API, GraphQL, Data Visualization, Postman, Performance Optimization

\textbf{Cloud \& Deployment:} AWS, Docker, GitHub Actions, CDN, Cloud Monitoring

\textbf{Backend \& Database:} Node.js, PostgreSQL, MySQL, MongoDB, Python

\textbf{Soft Skills:} Communication, Team Collaboration, Adaptability, Problem Solving, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable frontend features using JavaScript, TypeScript, and React ensuring fast, user-friendly interfaces for enterprise applications.
\item Built complex data visualizations including dashboards and interactive charts improving data-driven decision-making capabilities.
\item Collaborated with product managers, designers, and backend engineers to translate product requirements into functional user interfaces.
\item Implemented state management solutions using Redux and React Query optimizing performance and maintainability across applications.
\item Participated in code reviews and knowledge sharing sessions maintaining high code quality standards and team best practices.
\item Deployed cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and scalable performance.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing frontend components for enterprise web applications using React and modern JavaScript frameworks.
\item Contributed to design system development creating reusable components following accessibility and performance best practices.
\item Worked closely with cross-functional teams gathering requirements, conducting testing, and supporting deployment workflows.
\item Gained hands-on experience in frontend architecture including component design, state management, and performance optimization techniques.
\item Collaborated in Agile sprint planning and code reviews identifying improvements in scalability, accessibility, and code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with notes, videos, and interactive quizzes using React and modern frontend tools.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed frontend interface using React with state management and real-time progress dashboards for teachers and students.
\item Integrated interactive data visualizations for lesson tracking, quiz performance, and student analytics using Chart.js and custom components.
\item Implemented accessible UI components following WCAG standards ensuring inclusive usability for diverse learner populations.
\item Deployed frontend on AWS with CDN caching and performance optimization ensuring fast load times for over 6,000 concurrent users.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users and individuals with reading challenges integrating accessibility features.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat frontend using React and WebSockets with accessibility-focused UI design prioritizing keyboard navigation and screen readers.
\item Integrated AWS Polly and Azure Speech Services enabling text-to-speech and voice-to-text communication for enhanced user accessibility.
\item Followed WCAG accessibility standards and conducted usability testing with assistive technologies ensuring inclusive design compliance.
\item Deployed scalable frontend on AWS using Docker containers optimizing for low-latency real-time communication and high availability.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}