% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Frontend Developer with proven expertise in building scalable, user-friendly web applications using React, JavaScript, and modern frontend technologies. Experienced in developing e-commerce platforms, implementing secure payment integrations, and creating responsive, accessible interfaces that prioritize usability. Skilled in collaborating with cross-functional teams, translating business requirements into intuitive design solutions, and delivering high-quality code in Agile environments.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Frontend Technologies:} JavaScript ES6+, TypeScript, HTML5, CSS3, SASS, Responsive Design

\textbf{Frameworks \& Libraries:} React, Redux, Next.js, Vue.js, Angular, Bootstrap, Material UI

\textbf{Backend \& APIs:} Node.js, Express.js, REST API, GraphQL, Payment Gateway Integration

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, Firebase, SQL

\textbf{Development Tools \& Practices:} Git, GitHub, CI/CD, Docker, Agile, Code Reviews, Testing

\textbf{Design \& UX:} UI/UX Best Practices, Accessibility Standards, Cross-Browser Compatibility, Wireframing

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Self-Motivated, Detail-Oriented

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full-stack web and e-commerce applications using React, JavaScript, and Node.js to enhance user experience.
\item Integrated secure payment systems and optimized frontend performance to improve transaction reliability and customer satisfaction.
\item Built responsive, accessible interfaces following modern UI/UX best practices to ensure usability across all devices and browsers.
\item Collaborated with cross-functional teams through Agile sprints, code reviews, and wireframe discussions to deliver high-quality products.
\item Deployed cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and seamless user accessibility.
\item Mentored junior developers on frontend best practices, code organization, and maintainability to improve overall team productivity.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications with focus on frontend components using modern JavaScript frameworks and libraries.
\item Contributed to UI design and implementation for Proposal Management and Mailroom Tracking Systems with responsive, user-friendly interfaces.
\item Worked closely with cross-functional teams to gather requirements, validate design concepts, and support deployment phases effectively.
\item Gained hands-on experience in version control systems, testing frameworks, and secure coding practices within Agile development workflows.
\item Collaborated in project reviews to identify frontend performance improvements, accessibility enhancements, and code maintainability strategies.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with notes, videos, and interactive quizzes using modern frontend technologies.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full-stack LMS using React, Node.js, and MySQL to support online education with intuitive user interface.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time progress dashboards for educators and students.
\item Implemented secure authentication, role-based access control, and optimized frontend performance for high concurrent user accessibility.
\item Deployed the platform on AWS with responsive design, SSL encryption, and CDN caching ensuring reliable access for over 6,000 users.
\end{itemize}

\textbf{Custom Business Web Solutions} -- \emph{Personal Project}

\vspace{-1pt}

Built e-commerce sites, POS systems, and landing pages with secure, responsive design improving workflow efficiency for small businesses.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed multiple custom e-commerce solutions using React, Next.js, and Express.js with focus on user-friendly interfaces.
\item Implemented secure payment processing with Stripe API integration, inventory tracking, and checkout workflows for streamlined transactions.
\item Collaborated with small business clients to gather requirements and translate business needs into scalable, accessible web applications.
\item Optimized UI performance, mobile responsiveness, cross-browser compatibility, and SEO across all projects to enhance user engagement.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}