% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with hands-on experience developing scalable full stack web applications using JavaScript, React, and Node.js. Skilled in building responsive user interfaces, integrating RESTful APIs, and deploying cloud-based solutions on AWS. Proficient in modern frontend technologies including Vue.js, PHP/Laravel, and templating systems, with a strong focus on accessibility, performance optimization, and collaborative Agile development.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Frontend Development:} JavaScript, HTML5, CSS3, Vue.js, React, Bootstrap, Responsive Design

\textbf{Backend \& Templating:} PHP, Laravel, Node.js, SQL, RESTful APIs, MySQL, PostgreSQL

\textbf{Tools \& DevOps:} Git, GitHub, Docker, AWS, CI/CD Pipelines, Webpack

\textbf{Development Practices:} Agile, Scrum, Code Reviews, Testing, Debugging, Performance Optimization

\textbf{Design \& Accessibility:} UI/UX, WCAG Standards, Figma Implementation, Web Design, Component Consistency

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Attention to Detail, Feedback Reception, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript and React to enhance e-commerce functionality and user experience.
\item Implemented RESTful APIs and integrated secure payment systems improving system reliability and performance for production systems.
\item Deployed and maintained cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring 99.9\% uptime and fast deployment cycles.
\item Collaborated within Agile teams through code reviews, sprint planning, and pair programming to deliver high-quality features on schedule.
\item Applied test-driven development and secure coding standards throughout SDLC reducing production issues and improving code maintainability.
\item Led backend development for multiple applications while mentoring junior developers on best coding and deployment practices regularly.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level web applications across both frontend and backend components using modern JavaScript frameworks.
\item Contributed to the design and implementation of Proposal Management and Mailroom Tracking Systems improving internal workflow efficiency.
\item Worked closely with cross functional teams to gather requirements, perform testing, and support deployment phases successfully.
\item Gained hands-on experience in full stack development, software testing, and secure coding practices within Agile development workflows.
\item Collaborated in project reviews to identify improvements in performance, scalability, and code maintainability across multiple projects.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with notes, videos, and interactive quizzes during the pandemic using React.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full-stack LMS using React, Node.js, and MySQL to support online education for over 6,000 concurrent students.
\item Integrated lesson uploads, quizzes, and performance tracking with real-time dashboards enabling teachers to monitor student progress.
\item Implemented secure authentication, role-based access, and optimized database queries for high concurrent usage and fast page load times.
\item Deployed the platform on AWS with CDN caching and SSL encryption ensuring reliable access and secure data transmission for all users.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users integrating accessibility features and following WCAG standards with React.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and Socket.io with accessibility-focused UI design following WCAG standards.
\item Integrated AWS Polly and Azure Speech Services enabling text-to-speech and voice-to-text communication for inclusive user experience.
\item Followed WCAG accessibility standards and tested with assistive technologies ensuring usability for users with visual and reading challenges.
\item Deployed on AWS App Runner with Docker containers for scalable, low-latency communication supporting real-time messaging capabilities.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}