% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Frontend Developer with expertise in JavaScript, Python, and modern web technologies including React, Node.js, and SQL. Proven ability to evaluate code logic, solve complex algorithmic problems, and improve system performance through detailed analysis and debugging. Experienced in developing scalable applications, writing clean code, and ensuring quality through rigorous testing. Strong communicator skilled at explaining technical solutions clearly and collaborating across teams to deliver high-quality results.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, Python, HTML5, CSS3, SQL, TypeScript

\textbf{Frontend Frameworks \& Libraries:} React, Redux, Bootstrap, Material UI, jQuery

\textbf{Backend \& APIs:} Node.js, Django, Flask, REST API, GraphQL

\textbf{Databases:} MySQL, PostgreSQL, MongoDB, SQLite

\textbf{Computer Science Fundamentals:} Algorithms, Data Structures, Object-Oriented Programming, Design Patterns, Debugging

\textbf{Development Tools \& Practices:} Git, GitHub, Testing, Code Reviews, Agile, Technical Documentation

\textbf{Soft Skills:} Communication, Problem Solving, Detail-Oriented, Adaptability, Team Collaboration

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript and React to enhance functionality and user experience.
\item Implemented RESTful APIs and optimized SQL queries to improve system reliability and performance across applications.
\item Evaluated code logic and debugged complex issues to ensure high-quality deliverables and maintainability.
\item Collaborated within Agile teams through code reviews and sprint planning to ensure consistent quality standards.
\item Applied test-driven development and secure coding standards throughout SDLC reducing production issues significantly.
\item Mentored junior developers on best coding practices and explained technical solutions to improve team knowledge.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications across frontend and backend components using modern technologies.
\item Contributed to design and implementation of systems while evaluating code quality and correctness.
\item Worked closely with cross functional teams to gather requirements, perform testing, and support deployment phases.
\item Gained hands-on experience solving coding challenges and debugging workflows within Agile development environment.
\item Collaborated in project reviews to identify improvements in performance, scalability, and code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with interactive quizzes, videos, and performance tracking dashboards.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL to support online education during the pandemic.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time progress dashboards for teachers.
\item Implemented secure authentication, role-based access, and optimized database queries for high concurrent usage and performance.
\item Deployed the platform on AWS with SSL encryption, ensuring reliable access for over 6,000 students with consistent uptime.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users integrating accessibility features and assistive technologies.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and Socket.io with accessibility-focused UI design and usability.
\item Integrated AWS Polly and Azure Speech Services to enable text-to-speech and voice-to-text communication for users.
\item Followed WCAG accessibility standards and tested with assistive technologies to ensure inclusive usability and compliance.
\item Deployed on AWS App Runner with Docker containers for scalable, low-latency communication and consistent performance.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}