% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Frontend Developer with expertise in building modern, scalable web applications using React, JavaScript, HTML5, and CSS3. Proficient in Redux state management, consuming RESTful APIs, and implementing responsive user interfaces with frameworks like Bootstrap and Material UI. Experienced in Agile development, CI/CD pipelines, and collaborating with cross-functional teams to deliver high-quality solutions. Passionate about learning new technologies and sharing knowledge to drive innovation and excellence.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Frontend Development:} React, JavaScript, HTML5, CSS3, Redux, Bootstrap

\textbf{State Management \& Data Flow:} Redux, React Query, Flux, RESTful APIs, JSON, GraphQL

\textbf{Styling \& UI Frameworks:} SASS, Material UI, Tailwind CSS, Responsive Design, UI/UX

\textbf{Backend \& Database:} Node.js, Express.js, PostgreSQL, MongoDB, MySQL

\textbf{Cloud \& DevOps:} AWS, Docker, CI/CD, GitHub Actions, GitLab CI/CD

\textbf{Development Practices:} Agile, Scrum, Git, Code Reviews, Testing, TDD

\textbf{Soft Skills:} Collaboration, Communication, Adaptability, Problem Solving, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using React, JavaScript, and Node.js with Redux state management patterns.
\item Implemented RESTful APIs consuming JSON data and integrated secure payment systems improving system reliability and performance.
\item Deployed cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and high availability.
\item Collaborated within Agile teams through code reviews, sprint planning, and pair programming to deliver quality solutions.
\item Applied best practices in frontend development including responsive design, component reusability, and performance optimization.
\item Mentored junior developers on React workflows, Redux data patterns, and coding best practices across development lifecycle.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications with focus on frontend components using modern JavaScript frameworks.
\item Contributed to design and implementation of Proposal Management and Mailroom Tracking Systems with intuitive interfaces.
\item Worked closely with cross-functional teams to gather requirements, perform testing, and support deployment cycles.
\item Gained hands-on experience in frontend development, consuming APIs, and implementing state management within Agile workflows.
\item Collaborated in project reviews to identify improvements in UI performance, scalability, and code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic }

\vspace{-1pt}

Developed an inclusive chat app for low-vision users integrating accessibility features with real-time communication capabilities.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Node.js, and Socket.io with accessibility-focused UI design and WCAG compliance.
\item Integrated AWS Polly and Azure Speech Services to enable text-to-speech and voice-to-text communication for inclusive usability.
\item Implemented Redux state management for handling real-time message flow, user sessions, and application state across components.
\item Deployed on AWS App Runner with Docker containers for scalable, low-latency communication supporting diverse accessibility needs.
\end{itemize}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with notes, videos, and interactive quizzes during the pandemic.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed full-stack LMS using React, Node.js, and MySQL with Redux for managing application state and user data.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time progress dashboards consuming RESTful APIs.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent user sessions.
\item Deployed the platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 students worldwide.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}