% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Full Stack Web Developer with 3+ years of experience building scalable web applications using JavaScript, React, Node.js, Python, and Django. Proven expertise in designing and maintaining software platforms, collaborating with product managers, and delivering clean, efficient code. Skilled in database systems including PostgreSQL, MySQL, and MongoDB, with hands-on experience in Agile methodologies, CI/CD pipelines, and cloud deployment on AWS and GCP. Passionate about emerging technologies and best practices.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, PHP, SQL, HTML5, CSS3

\textbf{Frontend Technologies:} React, Redux, Angular, Bootstrap, Material UI, SASS

\textbf{Backend Technologies:} Node.js, Express.js, Django, Flask, FastAPI, REST API

\textbf{Database Systems:} PostgreSQL, MySQL, MongoDB, SQLite, Firebase, DynamoDB

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, CI/CD, GitHub Actions, Terraform

\textbf{Development Practices:} Agile, Scrum, Code Reviews, Unit Testing, TDD, Technical Documentation

\textbf{Soft Skills:} Communication, Team Collaboration, Problem Solving, Adaptability, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js to enhance platform functionality and user experience.
\item Designed and implemented RESTful APIs and optimized SQL queries to improve system performance and ensure data integrity.
\item Deployed and maintained cloud-based applications on AWS using Docker and CI/CD pipelines ensuring reliable uptime and availability.
\item Collaborated with product managers and developers through Agile workflows to define requirements and deliver high-quality features.
\item Participated in code reviews and applied best practices throughout SDLC to maintain clean, efficient, and well-documented code.
\item Mentored junior developers on coding standards, debugging techniques, and deployment best practices to strengthen team capabilities.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications across frontend and backend components using modern development frameworks.
\item Contributed to design and implementation of management systems collaborating with cross-functional teams on feature requirements.
\item Worked closely with senior developers to troubleshoot technical issues and resolve bugs ensuring application stability.
\item Gained hands-on experience in full stack development, database systems, and secure coding practices within Agile environments.
\item Participated in code reviews and testing phases to identify improvements in performance, scalability, and maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to access notes, videos, quizzes, and track performance with real-time dashboards.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL to support online education with interactive features.
\item Integrated lesson uploads, quizzes, and real-time progress dashboards enabling teachers to monitor student performance effectively.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent user activity.
\item Deployed platform on AWS with CDN caching and SSL encryption ensuring reliable access and performance for over 6,000 students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users integrating accessibility features and speech-to-text communication.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and WebSockets with accessibility-focused UI design for inclusive usability.
\item Integrated AWS Polly and Azure Speech Services to enable text-to-speech and voice-to-text communication for enhanced accessibility.
\item Followed WCAG accessibility standards and tested with assistive technologies ensuring compliance and usability for diverse users.
\item Deployed on AWS with Docker containers for scalable, low-latency communication ensuring high availability and performance.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}