% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Developer with 4+ years of experience designing and deploying secure, high-performance browser-based applications and backend APIs. Proficient in JavaScript, TypeScript, Node.js, and modern frameworks including React and Express.js. Expertise in REST API design, CI/CD pipelines, and relational/NoSQL databases such as PostgreSQL, MongoDB, and Redis. Skilled in implementing robust testing strategies with Jest and maintaining production systems with proactive debugging and optimization. Committed to collaboration with cross-functional teams to deliver scalable solutions.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, PHP, SQL, HTML5, CSS3

\textbf{Frameworks \& Libraries:} React, Node.js, Express.js, Redux, Django, Bootstrap

\textbf{Database \& Data Management:} PostgreSQL, MongoDB, MySQL, Redis, SQLite

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, CI/CD Pipelines, GitHub Actions, Jenkins

\textbf{API \& Architecture:} REST API, GraphQL, Microservices, JWT, OAuth, API Security

\textbf{Testing \& Quality:} Unit Testing, Integration Testing, Jest, Postman, TDD

\textbf{Security \& Best Practices:} OWASP, XSS Prevention, SQL Injection, HTTPS, Encryption

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Problem Solving, Ownership, Time Management

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed secure, scalable full stack applications using JavaScript, TypeScript, React, and Node.js to enhance e-commerce functionality.
\item Designed and implemented RESTful APIs with Express.js, optimizing database queries across PostgreSQL and MongoDB for performance.
\item Deployed and maintained cloud applications using AWS, Docker, and CI/CD pipelines ensuring 99.9\% uptime and system reliability.
\item Collaborated with Product and Design teams through Agile workflows, sprint planning, and code reviews to deliver high-quality features.
\item Implemented comprehensive testing strategies using Jest for unit and integration testing, improving code maintainability and reducing bugs.
\item Led backend development initiatives and mentored junior developers on secure coding standards, API design, and deployment best practices.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in building enterprise-level web applications across frontend and backend using JavaScript and modern frameworks.
\item Contributed to the design and implementation of secure APIs and database integrations for Proposal Management and Tracking Systems.
\item Worked closely with cross-functional teams to gather requirements, perform testing, and support production deployments.
\item Gained hands-on experience in full stack development, debugging production issues, and implementing fixes within Agile workflows.
\item Participated in code reviews and testing cycles to identify performance improvements and ensure adherence to development standards.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with secure authentication, real-time dashboards, and interactive content.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full-stack LMS using React, Node.js, Express.js, and MySQL to support online education at scale.
\item Integrated secure authentication with JWT, role-based access control, and optimized SQL queries for high concurrent user traffic.
\item Implemented real-time performance tracking dashboards for teachers, with modules for lesson uploads, quizzes, and progress analytics.
\item Deployed on AWS with Docker, CI/CD automation, SSL encryption, and CDN caching ensuring reliable access for 6,000+ students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic }

\vspace{-1pt}

Developed an inclusive chat app for low-vision users integrating real-time communication and accessibility features.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, Express.js, and Socket.io with WCAG-compliant accessibility-focused UI.
\item Integrated AWS Polly and Azure Speech Services to enable text-to-speech and voice-to-text communication for diverse user needs.
\item Conducted comprehensive testing with assistive technologies and Jest to ensure inclusive usability and feature reliability.
\item Deployed on AWS App Runner with Docker containers and CI/CD pipelines for scalable, low-latency, and secure communication.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}