% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Web Developer with hands-on experience building scalable web applications using JavaScript, React, Node.js, PHP, and MySQL. Proven ability to implement secure RESTful APIs, optimize database schemas, and deploy cloud-based solutions using AWS and Docker. Skilled in applying MVC architecture, Object-Oriented Programming, and Agile methodologies to deliver high-quality software. Strong collaborator with a focus on clean code, secure coding practices, and continuous improvement.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} PHP, JavaScript, Python, SQL, HTML5, CSS3

\textbf{Frameworks \& Libraries:} React, Node.js, jQuery, Bootstrap, Django, Laravel

\textbf{Database \& Data Management:} MySQL, PostgreSQL, MongoDB, Object Relational Mapping, Schema Design

\textbf{Cloud \& DevOps:} AWS, Docker, Git, GitHub Actions, CI/CD Pipelines

\textbf{Software Development Practices:} Agile, Scrum, MVC Architecture, Secure Coding, Code Reviews, Testing

\textbf{Computer Science Fundamentals:} Object-Oriented Programming, Functional Programming, Design Patterns, Data Structures

\textbf{Systems \& Networking:} Linux Command Line, Unix Environments, Security Best Practices, Version Control

\textbf{Soft Skills:} Problem Solving, Communication, Collaboration, Adaptability, Customer Service, Initiative

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js to enhance e-commerce functionality and performance.
\item Implemented RESTful APIs, optimized MySQL queries, and integrated secure payment systems to improve reliability and user experience.
\item Deployed cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and availability for end users.
\item Collaborated within Agile teams through code reviews, sprint planning, and pair programming to deliver high-quality software on schedule.
\item Applied secure coding standards and Object-Oriented Programming principles throughout SDLC reducing production issues significantly.
\item Led backend development initiatives and mentored junior developers on MVC architecture, best practices, and deployment workflows.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications using PHP, JavaScript, and MySQL across frontend and backend components successfully.
\item Contributed to design and implementation of Proposal Management and Mailroom Tracking Systems following MVC architecture principles.
\item Worked closely with cross functional teams to gather requirements, perform testing, and support deployment phases in Agile environment.
\item Gained hands-on experience in full stack development, secure coding practices, and software testing within iterative workflows.
\item Collaborated in project reviews to identify improvements in performance, scalability, and code maintainability across multiple systems.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes successfully.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full-stack LMS using React, Node.js, and MySQL following MVC architecture to support online education needs.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards using AJAX and JSON data exchange.
\item Implemented secure authentication, role-based access, and optimized MySQL database schemas for high concurrent usage and performance.
\item Deployed the platform on AWS with SSL encryption and CDN caching ensuring reliable access for over 6,000 students across regions.
\end{itemize}

\textbf{Custom Business Web Solutions} -- \emph{Personal Project}

\vspace{-1pt}

Built POS, e-commerce sites, landing pages, and inventory systems with secure responsive web design improving workflow efficiency.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed multiple custom web solutions using PHP, JavaScript, React, and MySQL following Object-Oriented Programming.
\item Implemented secure authentication, inventory tracking, payment processing with clean HTML and CSS following secure coding techniques.
\item Collaborated with clients to gather requirements and translate business needs into scalable applications using Agile methodologies.
\item Optimized UI performance, responsiveness, and database queries across all client projects to enhance user engagement and satisfaction.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}