% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Full Stack Developer with strong frontend expertise in building responsive, user-focused web applications using React, JavaScript, and modern UI frameworks. Proven ability to develop scalable solutions integrating RESTful APIs, cloud services, and backend technologies including Node.js and Django. Experienced in translating UI/UX designs into high-quality code while optimizing performance and collaborating with distributed teams in Agile environments to deliver seamless end-to-end functionality.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, HTML5, CSS3, SQL

\textbf{Frontend Frameworks \& Libraries:} React, Redux, Bootstrap, Material UI, SASS, React Query

\textbf{Backend Technologies:} Node.js, Express.js, Django, Flask, RESTful APIs, GraphQL

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQLite, Firebase, DynamoDB

\textbf{Cloud \& DevOps:} AWS, Azure, Docker, Git, GitHub Actions, CI/CD

\textbf{Software Development Practices:} Agile, Scrum, Code Reviews, Unit Testing, Design Patterns, Version Control

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Attention to Detail, Team Leadership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed responsive full stack web applications using React, JavaScript, and Node.js with emphasis on intuitive frontend design.
\item Translated UI/UX wireframes into high-quality, accessible code ensuring cross-browser compatibility and optimal user experience.
\item Integrated RESTful APIs with backend systems optimizing performance, scalability, and seamless end-to-end functionality.
\item Deployed cloud-based applications using AWS and Docker with CI/CD pipelines ensuring maximum uptime and reliability.
\item Participated in code reviews and collaborated within Agile teams to maintain best practices and deliver quality deliverables.
\item Troubleshot technical issues across the stack reducing production bugs and improving application speed and usability.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications focusing on frontend components and responsive user interface implementation.
\item Collaborated with backend developers to integrate APIs and ensure seamless data flow across frontend and backend systems.
\item Contributed to UI/UX design translation into functional code following modern web development and accessibility standards.
\item Worked closely with cross functional teams to gather requirements, perform testing, and support deployment in Agile workflows.
\item Debugged and resolved technical issues improving application performance, scalability, and overall code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS with React and Node.js enabling 6K+ students to access lessons, quizzes, and real-time progress tracking.
\vspace{-1pt}
\begin{itemize}
\item Developed full stack LMS using React, Node.js, and MySQL translating UI/UX designs into responsive, user-friendly interfaces.
\item Integrated RESTful APIs for lesson uploads, quizzes, and real-time dashboards ensuring seamless backend and frontend integration.
\item Implemented secure authentication and role-based access optimizing database queries for high concurrent user performance.
\item Deployed on AWS with CDN caching and SSL encryption ensuring maximum speed, scalability, and reliable access for 6K+ students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed inclusive real-time chat app using React and Node.js integrating accessibility features for low-vision users.
\vspace{-1pt}
\begin{itemize}
\item Built responsive frontend with React and Socket.io for real-time communication following WCAG accessibility standards.
\item Integrated AWS and Azure APIs for text-to-speech and voice-to-text ensuring seamless API collaboration with backend developers.
\item Optimized UI for maximum usability and tested with assistive technologies to ensure inclusive, accessible user experience.
\item Deployed using Docker on AWS with cloud services ensuring scalable, low-latency communication for distributed users.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}