% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Developer with expertise in React, Python, and TypeScript, specializing in building scalable applications and data-intensive systems. Proven ability to design and optimize RESTful APIs, manage PostgreSQL databases, and deploy cloud-native solutions on AWS and Azure. Experienced in CI/CD automation, performance optimization, and delivering high-quality products in Agile environments. Strong ownership mindset with a focus on architectural design, security best practices, and continuous improvement.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, TypeScript, SQL, HTML5, CSS3, Bash, PowerShell

\textbf{Frontend Technologies:} React, Angular, Redux, Bootstrap, Material UI, Next.js

\textbf{Backend Technologies:} Node.js, Django, Flask, FastAPI, Express.js, RESTful APIs

\textbf{Database \& Data Systems:} PostgreSQL, MySQL, MongoDB, SQL, Pandas, Schema Design

\textbf{Cloud \& DevOps:} AWS, Azure, Docker, GitHub Actions, CI/CD, Microservices

\textbf{Software Engineering:} Design Patterns, OOP, Unit Testing, Integration Testing, Performance Optimization

\textbf{Soft Skills:} Analytical Thinking, Problem Solving, Communication, Collaboration, Adaptability, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using React, TypeScript, and Python frameworks optimizing performance for large datasets.
\item Designed and implemented RESTful APIs and microservices ensuring efficient data flow and integration across cloud-native systems.
\item Optimized PostgreSQL schema design and complex SQL queries improving database performance and reducing query execution time.
\item Deployed and maintained cloud-based applications on AWS using Docker and CI/CD pipelines ensuring high availability and reliability.
\item Collaborated within Agile teams through code reviews, sprint planning, and iterative delivery to meet product goals and quality standards.
\item Applied test-driven development and secure coding practices throughout SDLC improving system stability and reducing production issues.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise applications using React and Python frameworks across frontend and backend components.
\item Contributed to designing and implementing data-driven systems including dashboards, filters, and reporting functionalities.
\item Worked closely with cross-functional teams to gather requirements, perform integration testing, and support deployment phases.
\item Gained hands-on experience in full stack development, API design, and performance tuning within Agile workflows.
\item Participated in code reviews and project retrospectives to identify improvements in scalability, code quality, and maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS using React, Node.js, and PostgreSQL enabling 6K+ students to access interactive learning resources.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React and Node.js with PostgreSQL database to support online education at scale.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards for teachers and students.
\item Implemented secure authentication, role-based access control, and optimized SQL queries for high concurrent usage and performance.
\item Deployed the platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 active students.
\end{itemize}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Automated vulnerability scanning and patching workflows using Python, reducing manual effort and strengthening enterprise security.
\vspace{-1pt}
\begin{itemize}
\item Developed automated workflows using Python, FastAPI, and Jenkins for vulnerability scanning and patch deployment across systems.
\item Integrated Nessus API for real-time vulnerability reporting, risk prioritization, and compliance tracking with detailed dashboards.
\item Created monitoring and alert systems to track security compliance, remediation progress, and performance metrics in production.
\item Reduced manual intervention by 60\% and accelerated patch cycles through full CI/CD automation and release process optimization.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}