% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Developer with 3+ years of experience building scalable web applications using JavaScript, React, Node.js, and cloud technologies. Proven expertise in developing RESTful APIs, optimizing database performance, and deploying solutions on AWS with CI/CD pipelines. Strong background in Agile methodologies, code reviews, and cross-functional collaboration. Skilled in implementing secure, accessible, and high-performance applications while maintaining clean code standards and comprehensive testing coverage.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, SQL, HTML5, CSS3

\textbf{Frontend Development:} React, Redux, Bootstrap, Material UI, Responsive Design

\textbf{Backend Development:} Node.js, Express.js, REST API, GraphQL, Microservices

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQL Optimization, Database Design

\textbf{Cloud \& DevOps:} AWS, Lambda, S3, CloudFormation, IAM, Docker, CI/CD

\textbf{Development Practices:} Agile, Scrum, Unit Testing, Code Reviews, Git, Debugging

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Continuous Learning, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed full stack web applications using JavaScript, React, Redux, and Node.js enhancing functionality and user experience.
\item Built and maintained RESTful APIs with optimized SQL queries and secure integrations improving system reliability by 30\%.
\item Deployed cloud applications on AWS using Lambda, S3, CloudFormation, and Docker with CI/CD pipelines ensuring 99.9\% uptime.
\item Collaborated in Agile teams conducting code reviews, sprint planning, and retrospectives to deliver high-quality solutions.
\item Wrote comprehensive unit tests achieving 85\% coverage and applied secure coding standards reducing production defects by 40\%.
\item Led backend development initiatives while mentoring junior developers on TypeScript, Node.js best practices, and deployment.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in building enterprise web applications developing both React-based frontend components and Node.js backend services.
\item Contributed to designing and implementing management systems collaborating with product owners and UX designers throughout SDLC.
\item Worked with cross-functional teams including QA to gather requirements, conduct testing, and support deployment phases.
\item Gained hands-on experience in full stack development, unit testing, and version control within Agile workflows and stand-ups.
\item Participated in code reviews and project retrospectives identifying improvements in performance, scalability, and code quality.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS with React, Node.js, and MySQL enabling 6,000+ students to access lessons, quizzes, and progress tracking.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack LMS using React, Redux, Node.js, and MySQL supporting real-time progress dashboards for concurrent users.
\item Integrated secure authentication with role-based access control and optimized database queries for high-performance data retrieval.
\item Deployed on AWS using Lambda, S3, CloudFormation, and CDN caching with SSL encryption ensuring reliability and fast access.
\item Conducted unit testing and code refactoring to maintain quality standards and ensure seamless user experience across modules.
\end{itemize}

\textbf{PROSPR " Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed inclusive real-time chat app using React, Node.js, and WebSockets with accessibility features for diverse users.
\vspace{-1pt}
\begin{itemize}
\item Built real-time messaging platform with React, Redux, Node.js, and Socket.io following Agile sprints and code review practices.
\item Integrated AWS services including Lambda and IAM for secure text-to-speech and voice-to-text communication capabilities.
\item Followed WCAG standards and conducted testing with assistive technologies ensuring inclusive usability and accessibility compliance.
\item Deployed on AWS using Docker containers and CloudFormation for scalable infrastructure and low-latency real-time communication.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}