% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Engineer with 5+ years of experience designing and deploying scalable web applications using React, TypeScript, Node.js, and Express.js. Proven expertise in RESTful API development, cloud-based architecture, and CI/CD automation across AWS and Microsoft Azure environments. Adept at delivering robust solutions through Agile collaboration, problem-solving, and continuous integration practices that enhance performance and security.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, PHP, SQL, HTML5, CSS3

\textbf{Frontend Frameworks \& Libraries:} React, Next.js, Redux, Bootstrap, Material UI, Tailwind CSS

\textbf{Backend \& API Development:} Node.js, Express.js, Django, Flask, RESTful APIs, GraphQL

\textbf{Databases \& Data Management:} PostgreSQL, MySQL, MongoDB, Azure Cosmos DB, Firebase, DynamoDB

\textbf{Cloud \& DevOps:} Microsoft Azure, AWS, Docker, Kubernetes, CI/CD Pipelines, GitHub Actions

\textbf{Version Control \& Collaboration:} Git, GitHub, GitLab, Bitbucket, Code Reviews, Agile Methodologies

\textbf{Security \& Architecture:} OAuth, JWT, API Security, Microservices, Clean Architecture, IAM

\textbf{Soft Skills:} Problem Solving, Analytical Thinking, Communication, Collaboration, Adaptability, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using React, TypeScript, Node.js, and Express.js improving e-commerce functionality.
\item Implemented RESTful APIs with optimized database queries and secure payment integrations enhancing system reliability and speed.
\item Deployed cloud-based applications on Microsoft Azure and AWS using Docker, Kubernetes, and automated CI/CD pipelines.
\item Collaborated within Agile teams through sprint planning, code reviews, and pair programming to deliver high-quality solutions.
\item Applied secure coding standards and version control with Git throughout SDLC reducing production issues and improving maintainability.
\item Led backend development for multiple applications while mentoring junior developers on best practices and deployment strategies.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web and mobile applications across frontend and backend components using modern frameworks.
\item Contributed to design and implementation of Proposal Management and Mailroom Tracking Systems with RESTful API integration.
\item Worked closely with cross-functional teams to gather requirements, perform testing, and support deployment phases.
\item Gained hands-on experience in full stack development, software testing, and secure coding within Agile workflows.
\item Collaborated in project reviews identifying improvements in performance, scalability, and code maintainability across applications.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS using React, Node.js, and Express.js enabling 6K+ students to learn with notes, videos, and quizzes.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS with React, TypeScript, Express.js, and MySQL supporting online education delivery.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards for teachers and students.
\item Implemented secure authentication, role-based access, and optimized RESTful APIs for high concurrent usage and scalability.
\item Deployed the platform on AWS with CI/CD pipelines, SSL encryption, and CDN caching ensuring reliable access for 6,000+ users.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive real-time chat app with React, Node.js, and Express.js integrating accessibility features for users.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, TypeScript, Node.js, Express.js, and WebSockets with accessible UI design.
\item Integrated Microsoft Azure Speech Services and Azure Entra ID enabling text-to-speech and voice-to-text communication.
\item Followed WCAG accessibility standards and tested with assistive technologies to ensure inclusive usability across platforms.
\item Deployed on cloud infrastructure with Docker containers and CI/CD pipelines for scalable, low-latency real-time communication.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}