% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Developer with expertise in designing and deploying scalable web applications using JavaScript, TypeScript, React, Node.js, and cloud infrastructure. Proven success building RESTful APIs, implementing microservices architecture, and leveraging AWS serverless technologies including Lambda, S3, and DynamoDB. Adept at full stack development spanning frontend interfaces, backend services, and database optimization with PostgreSQL and MongoDB. Strong collaborator experienced in Agile environments, CI/CD automation, and delivering high-quality software solutions.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, PHP, SQL, HTML5, CSS3, Bash

\textbf{Frontend Technologies:} React, Next.js, Redux, Tailwind CSS, Bootstrap, Material UI

\textbf{Backend \& APIs:} Node.js, NestJS, Express.js, RESTful APIs, GraphQL, Microservices

\textbf{Database Management:} PostgreSQL, MySQL, MongoDB, DynamoDB, Redis, SQL Optimization

\textbf{Cloud \& DevOps:} AWS Lambda, S3, EC2, Docker, Kubernetes, CI/CD, GitHub Actions, Terraform

\textbf{Testing \& Quality:} Unit Testing, Integration Testing, Jest, TDD, Postman, Automation Testing

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Ownership, Mentorship, Problem Solving

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, TypeScript, React, and Node.js to enhance functionality and performance.
\item Designed and implemented RESTful APIs with optimized SQL queries and secure authentication improving system reliability and scalability.
\item Deployed cloud-based applications on AWS using Docker, Lambda, and CI/CD pipelines ensuring high availability and consistent uptime.
\item Collaborated within Agile teams conducting code reviews, sprint planning, and mentoring developers on best practices and standards.
\item Integrated unit testing frameworks and TDD methodologies throughout SDLC reducing production issues and improving code maintainability.
\item Led backend microservices development while ensuring seamless integration with frontend components and third-party APIs.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications across frontend and backend using modern frameworks and cloud deployment strategies.
\item Contributed to design and implementation of scalable management systems with focus on performance optimization and user experience.
\item Worked with cross-functional teams to gather requirements, perform integration testing, and support continuous deployment phases.
\item Gained hands-on experience in full stack development, database management, and secure coding within Agile and Scrum workflows.
\item Participated in code reviews and project retrospectives to identify improvements in scalability, maintainability, and architecture.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL supporting online education with interactive dashboards.
\item Integrated modules for lesson uploads, quizzes, and real-time performance tracking with role-based access control and authentication.
\item Optimized database queries and implemented caching strategies to support high concurrent usage and improve application performance.
\item Deployed the platform on AWS with S3 storage, CloudFront CDN, and SSL encryption ensuring reliable access for over 6,000 students.
\end{itemize}

\textbf{PROSPR " Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users and individuals with reading challenges, integrating accessibility features.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and WebSockets with accessibility-focused UI adhering to WCAG standards.
\item Integrated AWS Polly and Azure Speech Services to enable text-to-speech and voice-to-text communication for inclusive usability.
\item Implemented secure authentication, data encryption, and optimized backend services to ensure low-latency real-time messaging.
\item Deployed on AWS using Docker containers and serverless architecture for scalable, cost-effective, and reliable communication.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}