% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Developer with proven expertise in React, Python, and SQL, specializing in building scalable web applications for complex business requirements. Experienced in developing financial and data-driven platforms, implementing RESTful APIs, and optimizing PostgreSQL databases for performance. Strong collaborator who translates stakeholder feedback into robust technical solutions while maintaining high code quality through Agile practices and continuous deployment.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, SQL, HTML5, CSS3, Bash

\textbf{Frontend Technologies:} React, Redux, Bootstrap, Material UI, responsive design

\textbf{Backend \& Databases:} Django, Flask, FastAPI, PostgreSQL, MySQL, REST API

\textbf{Cloud \& DevOps:} AWS, Docker, CI/CD, GitHub Actions, Linux environments

\textbf{Development Practices:} Agile, Scrum, TDD, code reviews, technical documentation

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Ownership, Stakeholder Engagement

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using JavaScript, React, and Python to deliver enhanced business functionality and user experience.
\item Implemented RESTful APIs and optimized SQL queries in PostgreSQL and MySQL improving system performance and data retrieval efficiency.
\item Deployed cloud-based applications using AWS and Docker with CI/CD pipelines ensuring reliable uptime and continuous delivery.
\item Collaborated directly with stakeholders and Agile teams translating business requirements into technical solutions through sprint planning.
\item Applied test-driven development and secure coding practices throughout SDLC reducing production issues and improving maintainability.
\item Led backend development initiatives while mentoring junior developers on best practices for coding standards and deployment strategies.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications across frontend and backend components using modern JavaScript and Python frameworks.
\item Contributed to design and implementation of business management systems incorporating user feedback and requirements analysis.
\item Worked closely with cross functional teams gathering requirements, performing testing, and supporting deployment phases in Agile workflows.
\item Gained hands-on experience in full stack development, database design, and secure coding practices within collaborative team environments.
\item Participated in project reviews identifying improvements in performance, scalability, and code quality to enhance overall system reliability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to access lessons, videos, and quizzes with real-time progress tracking and performance analytics.
\vspace{-1pt}
\begin{itemize}
\item Developed full stack LMS using React and Python with PostgreSQL database supporting concurrent usage by thousands of students and teachers.
\item Integrated modules for lesson uploads, interactive quizzes, and performance tracking with real-time dashboards for educators and administrators.
\item Implemented secure authentication, role-based access control, and optimized database queries ensuring data integrity and fast response times.
\item Deployed platform on AWS with CDN caching and SSL encryption ensuring reliable access, scalability, and security for all system users.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed inclusive real-time chat application for low-vision users integrating text-to-speech and voice-to-text accessibility features.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React and Python with WebSocket integration and accessibility-focused UI following WCAG standards.
\item Integrated AWS Polly and cloud-based speech services enabling text-to-speech and voice-to-text communication for inclusive user experience.
\item Tested application with assistive technologies ensuring compatibility and usability for users with visual impairments and reading challenges.
\item Deployed on AWS using Docker containers for scalable low-latency communication with continuous monitoring and performance optimization.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}