% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Developer with 3+ years of experience building scalable web applications using React, TypeScript, Python, and Node.js. Proven expertise in designing RESTful APIs, integrating third-party services, and deploying cloud-based solutions on AWS. Strong background in Agile methodologies, cross-functional collaboration, and delivering enterprise-grade features that solve real-world problems. Experienced in database systems including PostgreSQL and MongoDB, with a pragmatic approach to shipping clean, maintainable code in fast-paced environments.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, SQL, HTML5, CSS3, PHP, Bash

\textbf{Frontend Technologies:} React, Redux, React Query, Bootstrap, Material UI, Responsive Design

\textbf{Backend \& APIs:} Node.js, Django, Flask, FastAPI, RESTful APIs, GraphQL, Microservices

\textbf{Database Systems:} PostgreSQL, MongoDB, MySQL, SQLite, DynamoDB, Database Design

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, CI/CD, GitHub Actions, Infrastructure as Code

\textbf{Development Practices:} Agile, Scrum, OOP, Design Patterns, TDD, Code Reviews, Documentation

\textbf{Data \& Visualization:} Data Analytics, ETL Pipelines, Chart.js, Power BI, Data Visualization

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Ownership, Continuous Learning, Problem Solving

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using JavaScript, React, TypeScript, and Node.js to deliver custom features for clients.
\item Built and maintained RESTful APIs with third-party integrations, optimizing PostgreSQL queries to improve performance and reliability.
\item Deployed cloud-based solutions on AWS using Docker and CI/CD pipelines, ensuring high availability and consistent uptime for users.
\item Collaborated cross-functionally within Agile teams through sprint planning, code reviews, and backlog prioritization for deliverables.
\item Applied design patterns and secure coding throughout SDLC, reducing production issues and improving long-term code maintainability.
\item Led backend development for enterprise applications while mentoring junior developers on API design and deployment best practices.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in building enterprise web applications across frontend and backend using React, Node.js, and database systems like MongoDB.
\item Contributed to the design and implementation of Proposal Management and Mailroom Tracking Systems with custom workflow configurations.
\item Worked with cross-functional teams to gather requirements, perform integration testing, and support deployment in Agile environments.
\item Gained hands-on experience in full stack development, API integrations, and secure coding practices within rapid development cycles.
\item Participated in project reviews to identify opportunities for performance optimization, scalability improvements, and code quality.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS using React, Node.js, and PostgreSQL enabling 6K+ students to access lessons, quizzes, and progress tracking.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack LMS with React, TypeScript, and Node.js to support online education with custom modules and real-time dashboards.
\item Integrated lesson uploads, interactive quizzes, and performance tracking features with role-based access for teachers and students.
\item Implemented secure authentication, optimized database queries, and ensured data integrity for high concurrent usage across user base.
\item Deployed on AWS with CDN caching, SSL encryption, and autoscaling configurations to reliably serve over 6,000 active students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed inclusive real-time chat application using React, Node.js, and WebSockets with accessibility features for low-vision users.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application with React, TypeScript, Node.js, and Socket.io featuring accessibility-focused UI and WCAG compliance.
\item Integrated AWS Polly and Azure Speech Services APIs to enable text-to-speech and voice-to-text communication for inclusive usability.
\item Collaborated with team members to gather user requirements, perform testing with assistive technologies, and iterate on design feedback.
\item Deployed on AWS App Runner using Docker containers for scalable, low-latency communication with enterprise-grade reliability.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}