% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Full Stack Engineer with expertise in building scalable web applications using TypeScript, React, Next.js, Python, and Django. Proven track record deploying cloud infrastructure on AWS, Azure, and GCP with Docker and Kubernetes orchestration. Experienced in AI integrations, RESTful APIs, and shipping production-ready code in fast-paced Agile environments. Strong foundation in DevOps practices, CI/CD pipelines, and secure system architecture, delivering high-impact solutions across frontend and backend.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} TypeScript, JavaScript, Python, SQL, HTML5, CSS3, Bash

\textbf{Frameworks \& Libraries:} React, Next.js, Django, Node.js, Tailwind CSS, Redux

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, Redis, DynamoDB

\textbf{Cloud \& DevOps:} AWS, Azure, GCP, Docker, Kubernetes, CI/CD Pipelines

\textbf{AI \& Machine Learning:} AI Integration, LLM API, Prompt Engineering, Machine Learning APIs

\textbf{Software Development Practices:} Agile, Scrum, System Design, TDD, Microservices, REST API

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Problem Solving, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using TypeScript, React, and Node.js to deliver high-performance web solutions.
\item Implemented RESTful APIs with Django and optimized database queries to improve system reliability and throughput by 40\%.
\item Deployed cloud infrastructure on AWS and Azure using Docker, Kubernetes, and CI/CD pipelines for consistent uptime.
\item Collaborated with cross-functional teams in Agile sprints, conducting code reviews and shipping production code daily.
\item Applied secure coding practices and test-driven development throughout SDLC reducing production bugs by 35\%.
\item Mentored junior developers on full stack best practices, DevOps workflows, and cloud deployment strategies.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to full stack development of enterprise applications using Python, JavaScript, and cloud-based architectures.
\item Assisted in designing and implementing scalable backend services and frontend components for management systems.
\item Collaborated with cross-functional teams to gather requirements, perform testing, and support deployment workflows.
\item Gained hands-on experience with Agile methodologies, CI/CD pipelines, and DevOps practices in production environments.
\item Participated in code reviews and architecture discussions to improve performance, scalability, and maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS using React, Node.js, and cloud infrastructure supporting 6K+ students with real-time dashboards.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack LMS with TypeScript, React, and Node.js delivering interactive lessons, quizzes, and progress tracking.
\item Implemented secure authentication with JWT, role-based access control, and optimized database queries for scalability.
\item Integrated real-time dashboards using WebSockets enabling teachers to monitor student performance and engagement metrics.
\item Deployed on AWS with Docker containers, CDN caching, and SSL encryption ensuring reliable access for 6,000+ concurrent users.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive real-time chat application integrating AI-powered speech services for accessibility compliance.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat using React, Node.js, and Socket.io with accessible UI adhering to WCAG standards for inclusivity.
\item Integrated AWS and Azure AI services for text-to-speech and voice-to-text enabling seamless communication for low-vision users.
\item Optimized frontend performance with Tailwind CSS and responsive design ensuring cross-device accessibility and usability.
\item Deployed on AWS using Docker containers and orchestrated with CI/CD pipelines achieving low-latency real-time communication.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}