% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Developer with extensive experience in Node.js, TypeScript, and microservices architecture. Proven expertise in backend development, API design, event-driven systems, and Azure cloud solutions. Skilled in architecting scalable applications, conducting code reviews, and collaborating with cross-functional teams within Agile environments. Strong background in SDLC best practices, technical documentation, and mentoring junior developers to deliver high-quality solutions aligned with business objectives.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Backend \& API Development:} Node.js, TypeScript, Express.js, RESTful APIs, GraphQL, Microservices

\textbf{Cloud \& DevOps:} Microsoft Azure, AWS, Docker, Kubernetes, CI/CD, GitHub Actions

\textbf{Architecture \& Messaging:} Event-Driven Architecture, Microservices, API Gateway, System Design, Scalability

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, Redis, SQL Optimization

\textbf{Development Practices:} Agile, Scrum, Code Reviews, SDLC, Technical Documentation, TDD

\textbf{Frontend Technologies:} React, JavaScript, HTML5, CSS3, Bootstrap, Redux

\textbf{Soft Skills:} Communication, Collaboration, Mentorship, Adaptability, Problem Solving, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using JavaScript, React, and Node.js implementing RESTful APIs and microservices architecture.
\item Architected backend systems with TypeScript and Node.js, optimizing event-driven messaging and database queries for high performance.
\item Deployed and maintained cloud solutions using Azure and AWS with Docker, Kubernetes, and CI/CD pipelines ensuring system reliability.
\item Conducted code reviews and mentored junior developers on design patterns, best practices, and technical decision-making processes.
\item Collaborated with product owners and scrum masters in Agile sprints to align technical implementations with business goals.
\item Created comprehensive technical documentation for system architecture, API specifications, and deployment procedures following SDLC standards.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise applications with backend API development using Node.js and TypeScript within Agile workflows.
\item Contributed to system design and technical specifications for Proposal Management and Mailroom Tracking Systems architecture.
\item Worked closely with cross-functional teams to gather requirements, perform integration testing, and support deployment phases.
\item Gained hands-on experience in microservices development, event messaging systems, and secure coding practices during SDLC phases.
\item Collaborated in technical reviews to identify improvements in scalability, performance optimization, and maintainability of backend systems.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Architected a scalable LMS using Node.js and microservices enabling 6K+ students to access real-time lessons and quizzes securely.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack LMS architecture with React frontend and Node.js backend implementing RESTful APIs and event-driven messaging patterns.
\item Built microservices for lesson uploads, quiz modules, and performance tracking with real-time dashboards using TypeScript and Node.js.
\item Implemented secure authentication with JWT, role-based access controls, and optimized database queries for high concurrent user load.
\item Deployed on Azure with Docker containers, CDN caching, SSL encryption, and automated CI/CD pipelines ensuring 99.9\% uptime for 6K+ users.
\end{itemize}

\textbf{PROSPR " Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed inclusive real-time chat application using Node.js and WebSockets integrating Azure Speech Services for accessible communication.
\vspace{-1pt}
\begin{itemize}
\item Built event-driven chat backend using Node.js, TypeScript, and WebSockets implementing microservices architecture for scalable messaging.
\item Integrated Azure Speech Services and AWS Polly APIs for text-to-speech and voice-to-text enabling accessibility-focused communication.
\item Designed RESTful APIs and event messaging system ensuring real-time data synchronization following WCAG accessibility standards.
\item Deployed on Azure App Runner with Docker containers, implementing CI/CD pipelines and monitoring for low-latency, scalable communication.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}