% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Developer with expertise in building scalable, user-friendly web applications using JavaScript, React, and Node.js. Proven ability to deliver intuitive frontend experiences and robust backend integrations while collaborating with cross-functional teams. Experienced in leveraging modern frameworks, cloud technologies, and CI/CD pipelines to create maintainable solutions from concept to production. Strong communicator skilled in translating technical concepts and business requirements into high-quality software.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Frontend Technologies:} JavaScript, TypeScript, HTML5, CSS3, React, Vue.js, TailwindCSS

\textbf{Backend \& Databases:} Node.js, Express.js, Python, SQL, PostgreSQL, MySQL, MongoDB

\textbf{Cloud \& DevOps:} AWS, Docker, CI/CD, GitHub Actions, GitLab CI/CD, Kubernetes

\textbf{Development Practices:} Agile, Scrum, Testing, Code Reviews, Clean Architecture, SDLC

\textbf{Security \& Performance:} OAuth, JWT, OWASP, Performance Optimization, API Security, Encryption

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Ownership, Technical Documentation

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Built complex, maintainable frontends using JavaScript and React while ensuring scalability and user-friendly design for web applications.
\item Designed and integrated RESTful APIs with optimized SQL queries to enhance system reliability, performance, and backend functionality.
\item Deployed cloud-based applications on AWS using Docker and CI/CD pipelines, achieving consistent uptime and reliable production environments.
\item Collaborated with cross-functional Agile teams through code reviews, sprint planning, and pair programming to deliver high-quality solutions.
\item Applied test-driven development and secure coding standards throughout the development lifecycle, reducing production issues significantly.
\item Mentored junior developers on best practices for frontend architecture, backend integration, and deployment while leading key initiatives.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to building enterprise web and mobile applications by developing both frontend components and backend integrations effectively.
\item Participated in design collaboration and architecture discussions for Proposal Management and Mailroom Tracking Systems features.
\item Worked with cross-functional teams to gather requirements, perform comprehensive testing, and support deployment phases successfully.
\item Gained hands-on experience building full stack applications within Agile workflows while following secure coding and testing standards.
\item Engaged in project reviews to identify performance improvements, scalability enhancements, and maintainability optimizations for codebases.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes using modern web tech.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full-stack LMS using React, Node.js, and MySQL supporting scalable online education with modular architecture.
\item Integrated lesson uploads, interactive quizzes, and performance tracking with real-time progress dashboards for educators and students.
\item Implemented secure authentication, role-based access control, and optimized SQL queries to handle high concurrent user volumes efficiently.
\item Deployed the platform on AWS with CDN caching and SSL encryption, ensuring reliable and secure access for over 6,000 active students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive real-time chat app for low-vision users integrating accessibility features and voice communication capabilities.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and Socket.io with accessibility-focused UI design and inclusive user experience.
\item Integrated AWS Polly and Azure Speech Services to enable seamless text-to-speech and voice-to-text communication for diverse user needs.
\item Followed WCAG accessibility standards and tested with assistive technologies ensuring compliance and inclusive usability for all users.
\item Deployed on AWS App Runner with Docker containers for scalable, low-latency communication and reliable performance under varying loads.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}