% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Full Stack Engineer with extensive experience building scalable web applications and payment systems using JavaScript, React, Node.js, Python, and Django. Proven track record deploying cloud-based solutions on AWS and GCP with Docker, Kubernetes, and CI/CD pipelines. Experienced collaborating across cross-functional teams in Agile environments to deliver high-quality products. Strong focus on API development, secure authentication, and performance optimization to support global user bases.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, PHP, SQL, HTML5, CSS3

\textbf{Frontend Technologies:} React, Redux, Next.js, Bootstrap, Material UI, Tailwind CSS

\textbf{Backend \& APIs:} Node.js, Express.js, Django, Flask, REST API, GraphQL

\textbf{Database \& Data:} PostgreSQL, MySQL, MongoDB, Redis, DynamoDB, Firebase

\textbf{Cloud \& Infrastructure:} AWS, GCP, Docker, Kubernetes, Lambda, Terraform, CloudFormation

\textbf{DevOps \& CI/CD:} GitHub Actions, Jenkins, GitLab CI/CD, Monitoring, Logging

\textbf{Architecture, Design \& Delivery:} Microservices, Serverless, Event-Driven, System Design, Scalability, Agile, Scrum, TDD, Code Reviews, Documentation

\textbf{Security \& Authentication:} OAuth, JWT, IAM, Encryption, API Security, OWASP

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Mentorship, Ownership, Problem Solving

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using React, Node.js, and JavaScript to deliver robust e-commerce solutions.
\item Built and maintained RESTful APIs, optimized database queries, and integrated secure payment systems for reliable performance.
\item Deployed cloud-based applications on AWS with Docker and CI/CD pipelines ensuring high availability and consistent uptime.
\item Collaborated with cross-functional teams through Agile practices including code reviews and sprint planning for quality delivery.
\item Applied test-driven development and secure coding standards throughout SDLC reducing production issues and improving stability.
\item Mentored junior engineers on backend development, coding best practices, and deployment workflows to elevate team capabilities.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to developing enterprise web and mobile applications across frontend and backend components within Agile teams.
\item Assisted in designing and implementing Proposal Management and Mailroom Tracking Systems to streamline business workflows.
\item Collaborated with stakeholders to gather requirements, perform testing, and support deployment phases for seamless releases.
\item Gained hands-on experience in full stack development, software testing, and secure coding practices within iterative cycles.
\item Participated in project reviews identifying improvements in performance, scalability, and maintainability of production systems.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL to support online education during the pandemic.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards for teachers and students.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent user access.
\item Deployed the platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 active students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic }

\vspace{-1pt}

Developed an inclusive chat app for low-vision users and individuals with reading challenges, integrating accessibility features.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and Socket.io with accessibility-focused UI following WCAG standards.
\item Integrated AWS Polly and Azure Speech Services enabling text-to-speech and voice-to-text communication for inclusive access.
\item Tested with assistive technologies and conducted user feedback sessions to ensure usability for individuals with disabilities.
\item Deployed on AWS App Runner with Docker containers for scalable, low-latency communication supporting distributed user base.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}
