% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Full Stack Software Engineer with 2+ years building scalable web and mobile applications using JavaScript, TypeScript, React, and Node.js. Experienced in designing end-to-end product features, architecting RESTful APIs, and deploying cloud-based solutions on AWS with Docker and CI/CD pipelines. Skilled in Agile development, code reviews, and delivering user-focused products that drive growth and engagement. Proven ability to work autonomously, rapidly evaluate technologies, and ship features that enhance user experience.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, PHP, SQL, HTML5, CSS3, Bash

\textbf{Frameworks \& Libraries:} React, React Native, Node.js, Express.js, Django, Redux, Bootstrap

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, Redis, ETL Pipelines, Data Warehousing

\textbf{Cloud \& DevOps:} AWS, GCP, Docker, Kubernetes, CI/CD, GitHub Actions

\textbf{Software Development Practices:} Agile, Scrum, TDD, Code Reviews, REST API, System Design

\textbf{Computer Science Fundamentals:} Data Structures, Algorithms, OOP, Design Patterns, Performance Optimization

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Ownership, Problem Solving, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, TypeScript, React, and Node.js to enhance user experience.
\item Designed and implemented RESTful APIs, optimized SQL queries, and integrated secure payment systems improving reliability.
\item Deployed cloud-based applications on AWS using Docker and CI/CD pipelines ensuring consistent uptime and high availability.
\item Collaborated in Agile teams through code reviews, sprint planning, and continuous deployment to deliver high-quality features.
\item Applied test-driven development and typed code standards throughout SDLC reducing production issues and technical debt.
\item Led backend development while mentoring junior engineers on best practices, architecture design, and deployment workflows.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web and mobile applications across frontend and backend components using modern frameworks.
\item Contributed to feature design and implementation for Proposal Management and Mailroom Tracking Systems with cross-functional teams.
\item Worked closely with product and design teams to gather requirements, perform testing, and support deployment phases.
\item Gained hands-on experience in full stack development, unit testing, and secure coding within Agile workflows and sprints.
\item Collaborated in project reviews identifying improvements in performance, scalability, and maintainability across codebases.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS with React, Node.js, and MySQL enabling 6K+ students to learn with notes, videos, and interactive quizzes.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed full stack LMS using React, Node.js, and MySQL supporting online education with real-time dashboards.
\item Integrated modules for lesson uploads, quizzes, and performance tracking enabling teachers to monitor student progress.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent usage.
\item Deployed platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 active students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed inclusive real-time chat app for low-vision users integrating text-to-speech and voice-to-text with accessibility features.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Node.js, and WebSockets with accessibility-focused UI design for inclusivity.
\item Integrated AWS Polly and Azure Speech Services enabling text-to-speech and voice-to-text communication for diverse users.
\item Followed WCAG accessibility standards and tested with assistive technologies ensuring compliance and usability for all users.
\item Deployed on AWS using Docker containers for scalable, low-latency communication with automated CI/CD deployment pipelines.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}