% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Developer with 3+ years of experience building scalable web applications using JavaScript, React, and Node.js. Proven expertise in developing RESTful APIs, implementing secure authentication, and deploying cloud-based solutions on AWS with Docker and CI/CD pipelines. Strong background in Agile development, database management, and cross-functional collaboration. Passionate about creating robust, user-focused applications that solve real-world problems.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, SQL, HTML5, CSS3

\textbf{Frontend Development:} React, Redux, Bootstrap, Material UI, Angular, Responsive Design

\textbf{Backend Development:} Node.js, Express.js, RESTful APIs, Django, Flask, FastAPI

\textbf{Database Management:} PostgreSQL, MySQL, MongoDB, SQLite, DynamoDB, Firebase

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, Jenkins, GitHub Actions, CI/CD

\textbf{Security \& Authentication:} OAuth, JWT, SSO, OWASP, API Security, Encryption

\textbf{Development Practices:} Agile, Scrum, Git, Unit Testing, Technical Documentation

\textbf{Soft Skills:} Communication, Team Collaboration, Adaptability, Problem Solving, Ownership, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js, building RESTful APIs for e-commerce systems.
\item Implemented secure authentication with OAuth and JWT, integrated payment gateways, and optimized database queries for performance.
\item Deployed cloud-based applications on AWS using Docker, Jenkins, and CI/CD pipelines ensuring 99.9\% uptime and fast releases.
\item Collaborated within Agile teams through sprint planning, code reviews, and pair programming to deliver high-quality features.
\item Applied test-driven development, wrote comprehensive unit tests, and followed security best practices throughout the SDLC.
\item Mentored junior developers on development best practices, Git workflows, and deployment strategies while leading backend projects.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to full stack development of enterprise web applications using frontend and backend technologies in Agile environment.
\item Participated in requirements gathering, design sessions, development, testing, and deployment phases for management systems.
\item Collaborated with cross-functional teams including designers and engineers to ensure seamless integration and optimal user experience.
\item Gained hands-on experience building RESTful APIs, implementing authentication, and working with relational and document databases.
\item Supported code reviews and participated in performance optimization efforts to improve application scalability and responsiveness.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS using React, Node.js, and MySQL enabling 6K+ students to access lessons, quizzes, and performance tracking.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed full stack LMS with React frontend and Node.js backend, implementing RESTful APIs for content management.
\item Integrated secure authentication with OAuth, role-based access control, and real-time dashboards for teachers and administrators.
\item Optimized MySQL database queries and implemented caching strategies to support high concurrent usage across 6,000+ active users.
\item Deployed platform on AWS with Docker containers, configured load balancing, SSL encryption, and CDN for reliable global access.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed inclusive real-time chat app using React, Node.js, and WebSockets with accessibility features for low-vision users.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application with React and Node.js using Socket.io for bidirectional communication and instant message delivery.
\item Integrated AWS services for text-to-speech and voice-to-text capabilities, enhancing accessibility for users with visual impairments.
\item Followed WCAG accessibility standards and conducted testing with assistive technologies to ensure inclusive and usable interface design.
\item Deployed on AWS using Docker containers with CI/CD pipeline for automated testing, deployment, and scalable low-latency performance.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}