% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Developer with hands-on experience building scalable web applications using Python, Django, JavaScript, and React. Proven expertise in cloud infrastructure with AWS and GCP, implementing CI/CD pipelines, and integrating AI/ML APIs including LLM-based solutions. Skilled in crafting intuitive user interfaces, optimizing backend systems, and collaborating within Agile teams to deliver impactful features that enhance user experience and drive business value.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, SQL, HTML5, CSS3, PHP

\textbf{Frameworks \& Libraries:} Django, React, Vue.js, Node.js, Bootstrap, Flask

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, ETL Pipelines, BigQuery

\textbf{Cloud \& DevOps:} Google Cloud Platform, AWS, Docker, CI/CD, GitHub Actions, Serverless

\textbf{AI \& Machine Learning:} LLM API, ChatGPT API, OpenAI, Prompt Engineering, AI Integration

\textbf{Development Practices:} Agile, Scrum, REST API, Microservices, Unit Testing, TDD

\textbf{Soft Skills:} Collaboration, Communication, Problem Solving, Adaptability, Continuous Learning, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, Django, and Node.js to enhance functionality and user experience.
\item Implemented RESTful APIs, optimized SQL queries, and integrated secure authentication systems improving reliability and performance.
\item Deployed and maintained cloud applications on AWS and GCP using Docker and CI/CD pipelines ensuring consistent uptime and availability.
\item Collaborated within Agile teams through code reviews, sprint planning, and pair programming to deliver high-quality, user-focused features.
\item Applied test-driven development and secure coding practices throughout SDLC reducing production issues and improving maintainability.
\item Led backend development initiatives while mentoring junior developers on best practices for coding, deployment, and cloud optimization.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level web applications across frontend and backend components using modern frameworks and tools.
\item Contributed to design and implementation of scalable systems including Proposal Management and Mailroom Tracking applications.
\item Worked closely with cross-functional teams to gather requirements, perform testing, and support deployment phases in Agile workflows.
\item Gained hands-on experience in full stack development, software testing, and secure coding practices within collaborative team environments.
\item Participated in project reviews to identify improvements in performance, scalability, and code maintainability across multiple projects.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with notes, videos, quizzes, and real-time performance tracking dashboards.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed full-stack LMS using React, Node.js, and MySQL to support online education for over 6,000 concurrent users.
\item Integrated modules for lesson uploads, interactive quizzes, and performance tracking with real-time dashboards for educators.
\item Implemented secure authentication, role-based access control, and optimized database queries for high-performance concurrent usage.
\item Deployed platform on AWS with CDN caching and SSL encryption ensuring reliable access and enhanced security for all users.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed inclusive chat app for low-vision users integrating text-to-speech, voice-to-text, and WCAG accessibility standards.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Node.js, and Socket.io with accessibility-focused UI design for inclusive communication.
\item Integrated AWS Polly and Azure Speech Services to enable text-to-speech and voice-to-text communication for diverse user needs.
\item Followed WCAG accessibility standards and tested with assistive technologies to ensure usability for low-vision and reading-challenged users.
\item Deployed on AWS App Runner with Docker containers ensuring scalable, low-latency communication with automated deployment pipelines.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}