% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Full Stack Software Engineer with 2+ years of experience delivering scalable web applications using JavaScript, React, Node.js, Python, and Django. Skilled in building REST APIs, optimizing database performance, and deploying cloud infrastructure on AWS and GCP with Docker and CI/CD pipelines. Proven collaborator in Agile teams, contributing to cross-functional product development, code reviews, and technical documentation while ensuring code quality and system reliability.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, PHP, SQL, HTML5, CSS3

\textbf{Frameworks \& Libraries:} React, Redux, Django, Flask, Node.js, Bootstrap

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQLite, Redis

\textbf{Cloud \& DevOps:} AWS, GCP, Docker, Kubernetes, GitHub Actions, CI/CD

\textbf{Software Development Practices:} Agile, Scrum, REST API, TDD, Code Reviews, Debugging

\textbf{Computer Science Fundamentals:} Data Structures, Algorithms, OOP, Design Patterns, MVC

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Problem Solving, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js to enhance e-commerce functionality.
\item Implemented RESTful APIs and optimized SQL queries to improve system performance, maintainability, and reliability.
\item Deployed cloud-based applications on AWS with Docker and CI/CD pipelines ensuring consistent uptime and availability.
\item Collaborated with cross-functional teams through code reviews and sprint planning to deliver high-quality features.
\item Applied test-driven development and secure coding standards throughout SDLC to reduce production issues.
\item Contributed to backend development while mentoring junior engineers on best practices and deployment strategies.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web and mobile applications across frontend and backend components.
\item Contributed to design and implementation of Proposal Management and Mailroom Tracking Systems.
\item Worked with cross-functional teams to gather requirements, perform testing, and support deployment phases.
\item Gained hands-on experience in full stack development, software testing, and secure coding within Agile workflows.
\item Collaborated in project reviews to identify improvements in performance, scalability, and code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL to support online education during the pandemic.
\item Integrated modules for lesson uploads, quizzes, and real-time performance tracking dashboards for teachers.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent usage.
\item Deployed the platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users and individuals with reading challenges, integrating accessibility features.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and Socket.io with accessibility-focused user interface design.
\item Integrated AWS Polly and Azure Speech Services to enable text-to-speech and voice-to-text communication features.
\item Followed WCAG accessibility standards and tested with assistive technologies to ensure inclusive usability.
\item Deployed on AWS App Runner with Docker containers for scalable and low-latency communication.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}