% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Engineer with 3+ years of experience building and maintaining scalable SaaS applications across frontend and backend technologies. Proficient in JavaScript, TypeScript, React, Redux, Python, and Django with strong expertise in cloud platforms including AWS, GCP, and Azure. Demonstrated success in developing performant systems, implementing comprehensive testing strategies, and collaborating with cross-functional teams to deliver user-focused solutions that drive product value and business impact.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, SQL, HTML5, CSS3

\textbf{Frontend Technologies:} React, Redux, Next.js, Bootstrap, Material UI, React Query

\textbf{Backend \& APIs:} Django, Flask, Node.js, REST API, GraphQL, FastAPI

\textbf{Databases:} PostgreSQL, MySQL, MongoDB, SQLite, DynamoDB, BigQuery

\textbf{Cloud \& DevOps:} AWS, Azure, GCP, Docker, Kubernetes, CI/CD, GitHub Actions

\textbf{Testing \& Quality:} Unit Testing, Integration Testing, Jest, Postman, TDD

\textbf{Soft Skills:} Collaboration, Communication, Adaptability, Ownership, Problem Solving

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack SaaS applications using JavaScript, React, Redux, and Node.js to deliver robust user experiences.
\item Built maintainable RESTful APIs with comprehensive unit and integration tests ensuring high code quality and system reliability.
\item Deployed applications on AWS and GCP using Docker containers and CI/CD pipelines maintaining consistent uptime and performance.
\item Monitored application performance through logging and debugging workflows to identify bottlenecks and optimize system efficiency.
\item Collaborated with engineering and product teams in Agile workflows to design features from technical planning through deployment.
\item Owned features end-to-end taking responsibility for code correctness, documentation, and post-release support to ensure stability.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to full stack development of enterprise web applications working across frontend React components and backend APIs.
\item Participated in architectural discussions and feature solutioning to support scalable and effective product design decisions.
\item Executed unit and integration testing strategies using automated frameworks to maintain strong test coverage and code quality.
\item Worked closely with cross-functional teams including UX and product to gather requirements and deliver user-focused solutions.
\item Documented features clearly to support team alignment, knowledge sharing, and future development across distributed engineering teams.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to access lessons, videos, and quizzes with real-time tracking and performance dashboards.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack LMS using React, Node.js, and MySQL with role-based access and secure authentication to support online education.
\item Integrated modules for lesson uploads, interactive quizzes, and performance tracking delivering cohesive user-focused learning experiences.
\item Optimized database queries and implemented caching strategies to handle high concurrent usage ensuring reliable platform performance.
\item Deployed on AWS with SSL encryption and CDN integration maintaining uptime and scalability for over 6,000 active student users.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed inclusive real-time chat application for low-vision users integrating text-to-speech and voice-to-text accessibility features.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat using React, Node.js, and WebSockets with accessibility-focused UI following WCAG standards for inclusive design.
\item Integrated AWS and Azure cloud services for text-to-speech and voice-to-text enabling seamless communication for diverse user needs.
\item Maintained strong test coverage with automated testing frameworks ensuring stable and trustworthy product experience across features.
\item Deployed on AWS with Docker containers for scalable low-latency communication owning features from design through production support.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}