% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Web Developer with 2+ years of professional experience designing, building, and optimizing scalable web applications across frontend and backend environments. Proficient in PHP, JavaScript, MySQL, React, Node.js, and RESTful API integration with strong expertise in secure coding, cloud deployment, and database optimization. Experienced in Agile workflows, cross-functional collaboration, and delivering high-performance solutions that support automation and business growth within dynamic teams.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} PHP, JavaScript, Python, SQL, HTML5, CSS3

\textbf{Frameworks \& Libraries:} React, Node.js, jQuery, Bootstrap, Angular, Django

\textbf{Database \& API Development:} MySQL, PostgreSQL, REST API, JSON, XML, Database Optimization

\textbf{Cloud \& DevOps:} AWS, Docker, Git, CI/CD, GitHub Actions, Linux

\textbf{Security \& Best Practices:} OAuth, JWT, OWASP, Encryption, Secure Coding, Authentication

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Attention to Detail, Problem Solving, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js improving e-commerce functionality and user engagement.
\item Implemented RESTful APIs and optimized MySQL queries enhancing system reliability, performance, and backend data processing efficiency.
\item Deployed and maintained cloud applications on AWS with Docker and CI/CD pipelines ensuring consistent uptime and seamless releases.
\item Collaborated within Agile teams through code reviews and sprint planning delivering high-quality solutions aligned with business objectives.
\item Applied secure coding standards and test-driven development throughout SDLC reducing production issues and improving maintainability.
\item Mentored junior developers on best practices for backend development, deployment workflows, and version control using Git repositories.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications across frontend and backend components supporting business automation and workflows.
\item Contributed to the design and implementation of Proposal Management and Mailroom Tracking Systems integrating APIs and database logic.
\item Worked closely with cross-functional teams to gather requirements, perform testing, and support deployment phases within Agile workflows.
\item Gained hands-on experience in full stack development, secure coding, and troubleshooting technical issues across application layers.
\item Collaborated in project reviews identifying improvements in performance, scalability, and code maintainability for enterprise solutions.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS with React, Node.js, and MySQL enabling 6K+ students to access lessons, quizzes, and progress tracking dashboards.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL supporting online education with real-time progress tracking.
\item Integrated modules for lesson uploads, quizzes, and performance dashboards enabling teachers to monitor student engagement effectively.
\item Implemented secure authentication with role-based access and optimized MySQL queries for high concurrent usage and system performance.
\item Deployed on AWS with CDN caching and SSL encryption ensuring reliable and secure access for over 6,000 students during the pandemic.
\end{itemize}

\textbf{Custom Business Web Solutions} -- \emph{Personal Project}

\vspace{-1pt}

Built POS, e-commerce sites, landing pages, and inventory systems with secure, responsive web design improving workflow efficiency.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed multiple custom web solutions using React, Next.js, and Express.js tailored to client business requirements.
\item Implemented secure authentication, inventory tracking, and payment processing integrating Stripe API for seamless transaction handling.
\item Collaborated with clients to gather requirements and translate business needs into scalable, user-friendly web applications and systems.
\item Optimized UI performance, responsiveness, and SEO across all client projects enhancing user engagement and overall system effectiveness.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}