% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Full Stack Developer with proven expertise in building scalable backend services and user-facing applications using React, Node.js, Python, and modern cloud infrastructure. Strong experience with RESTful APIs, event-driven architectures, and end-to-end feature delivery across frontend and backend systems. Skilled in CI/CD automation, database optimization, and workflow orchestration with a focus on reliability and maintainability. Collaborative team player experienced in Agile environments, committed to delivering intuitive interfaces backed by robust backend logic.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, TypeScript, SQL, PHP, HTML5, CSS3, Bash

\textbf{Frontend Frameworks \& Libraries:} React, Redux, Next.js, Bootstrap, Material UI, Tailwind CSS

\textbf{Backend Frameworks \& APIs:} Node.js, Express.js, Django, Flask, FastAPI, REST API, GraphQL, WebSockets

\textbf{Databases \& Data Management:} PostgreSQL, MySQL, MongoDB, Redis, DynamoDB, SQLite

\textbf{Cloud, DevOps \& Infrastructure:} AWS, Docker, Kubernetes, CI/CD, GitHub Actions, Terraform, CloudFormation

\textbf{Architecture \& Engineering Practices:} Microservices, Event-Driven Architecture, System Design, Unit Testing, Integration Testing

\textbf{Observability, Security \& Performance:} Monitoring, Logging, CloudWatch, OAuth, JWT, Performance Optimization, Load Balancing

\textbf{Soft Skills:} Collaboration, Communication, Problem Solving, Adaptability, Ownership, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using React, Node.js, and Python, delivering end-to-end features across backend services and user-facing UIs.
\item Implemented RESTful APIs and GraphQL endpoints, integrating event-driven systems and workflow orchestration for real-time data synchronization.
\item Optimized SQL queries and database schemas in PostgreSQL and MySQL, improving performance and ensuring correctness in production workflows.
\item Deployed cloud-based applications on AWS with Docker, Kubernetes, and CI/CD pipelines, achieving high availability and observability across environments.
\item Collaborated with product managers, designers, and operations teams in Agile sprints to gather requirements and deliver cohesive user experiences.
\item Established automated testing practices including unit, integration, and end-to-end tests, reducing production issues and accelerating iteration cycles.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in building enterprise web applications with focus on backend logic, API design, and frontend component integration across the stack.
\item Contributed to Proposal Management and Mailroom Tracking Systems, implementing data models and backend services for workflow automation.
\item Worked closely with cross-functional teams to gather requirements, perform integration testing, and support deployment phases in Agile cycles.
\item Gained hands-on experience with full stack development, secure coding practices, and version control using Git and GitLab in collaborative workflows.
\item Participated in code reviews and project retrospectives, identifying improvements in system reliability, scalability, and maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS using React, Node.js, and MySQL enabling 6K+ students to access lessons, quizzes, and performance tracking.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed full stack LMS with React frontend and Node.js backend, implementing RESTful APIs for lesson uploads and quiz management.
\item Integrated real-time progress dashboards and role-based access control, ensuring secure authentication and authorization across user roles.
\item Optimized PostgreSQL database queries and caching strategies to support high concurrent usage and improve response times for 6,000+ active users.
\item Deployed platform on AWS with Docker, SSL encryption, and CDN caching, achieving reliable uptime and seamless scalability during peak traffic.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed inclusive chat app for low-vision users with React, Node.js, and Socket.io, integrating text-to-speech and voice-to-text features.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Node.js, Express.js, and Socket.io with event-driven architecture for instant message delivery.
\item Integrated AWS Polly and Azure Speech Services APIs to enable text-to-speech and voice-to-text communication, enhancing accessibility for users.
\item Followed WCAG accessibility standards and conducted testing with assistive technologies to ensure intuitive and inclusive user experience.
\item Deployed application on AWS App Runner using Docker containers, ensuring scalable infrastructure and low-latency communication across sessions.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}