% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Full Stack Software Engineer with expertise in JavaScript, TypeScript, React, and Node.js specializing in building scalable web and mobile applications. Experienced in cloud infrastructure using AWS, Docker, and CI/CD pipelines with demonstrated success deploying production systems serving thousands of users. Strong product mindset with end-to-end ownership from requirements to deployment, focusing on user-centric design and performance optimization.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, SQL, HTML5, CSS3

\textbf{Frontend Development:} React, Redux, React Query, Bootstrap, Material UI, Responsive Design

\textbf{Backend \& APIs:} Node.js, Express.js, REST API, GraphQL, WebSockets, Microservices

\textbf{Database \& Data:} PostgreSQL, MySQL, MongoDB, Redis, ETL Pipelines, BigQuery

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, CI/CD, GitHub Actions, Infrastructure as Code

\textbf{Testing \& Quality:} Unit Testing, Integration Testing, TDD, Code Reviews, Performance Optimization

\textbf{Development Practices:} Agile, Scrum, System Design, Design Patterns, Technical Documentation

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Ownership, Problem Solving, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed full stack web applications using JavaScript, React, and Node.js delivering scalable e-commerce solutions.
\item Built RESTful APIs and optimized database queries improving system reliability and reducing response times significantly.
\item Deployed cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and availability.
\item Collaborated within Agile teams through code reviews and sprint planning to deliver high-quality products on schedule.
\item Applied test-driven development and secure coding standards throughout SDLC reducing production bugs and improving quality.
\item Led backend development initiatives while mentoring junior developers on best practices for coding and deployment.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Built enterprise web applications developing both frontend and backend components using modern JavaScript frameworks.
\item Contributed to design and implementation of systems handling proposal management and automated tracking workflows.
\item Worked with cross functional teams gathering requirements, performing testing, and supporting deployment processes.
\item Gained experience in full stack development, automated testing, and secure coding practices within Agile environment.
\item Participated in code reviews identifying improvements in performance, scalability, and overall code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack LMS using React, Node.js, and MySQL supporting online education with interactive learning modules.
\item Integrated lesson uploads, quizzes, and performance tracking with real-time dashboards for monitoring student progress.
\item Implemented secure authentication, role-based access control, and optimized queries for handling concurrent users.
\item Deployed on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 students simultaneously.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users and individuals with reading challenges, integrating accessibility features.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Node.js, and Socket.io with accessibility-focused interface design.
\item Integrated AWS Polly and Azure Speech Services enabling text-to-speech and voice-to-text communication features.
\item Followed WCAG accessibility standards testing with assistive technologies to ensure inclusive usability for all users.
\item Deployed on AWS App Runner with Docker containers achieving scalable, low-latency communication infrastructure.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}