% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Web Developer with 3+ years building scalable web applications using JavaScript, React, Node.js, Python, and modern cloud technologies. Proven expertise in designing clean, efficient code, integrating RESTful APIs, and deploying solutions on AWS with CI/CD automation. Experienced collaborating with cross-functional teams in Agile environments to deliver high-quality software products that enhance user experience and system performance.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, Python, SQL, PHP, HTML5, CSS3

\textbf{Frontend Technologies:} React, Redux, Bootstrap, Material UI, SASS

\textbf{Backend Technologies:} Node.js, Django, Flask, FastAPI, Express.js

\textbf{Database Systems:} PostgreSQL, MySQL, MongoDB, SQLite, Firebase

\textbf{Cloud \& DevOps:} AWS, Docker, CI/CD, GitHub Actions, Terraform

\textbf{Development Practices:} Agile, Scrum, Code Reviews, Unit Testing, TDD

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js enhancing platform functionality and user engagement.
\item Designed and implemented RESTful APIs with optimized SQL queries improving system performance and ensuring reliable data processing.
\item Deployed cloud-based applications on AWS using Docker and CI/CD pipelines maintaining consistent uptime and streamlined release cycles.
\item Collaborated with Product Managers and cross-functional teams in Agile sprints to define requirements and deliver quality features.
\item Performed code reviews and applied secure coding standards throughout SDLC reducing production issues and enhancing maintainability.
\item Mentored junior developers on best practices in backend development, testing methodologies, and deployment automation strategies.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications across frontend and backend components using modern development frameworks.
\item Contributed to the design and implementation of internal tracking systems improving workflow efficiency and data accuracy.
\item Worked with cross-functional teams to gather feature requirements, conduct testing, and support successful deployment phases.
\item Gained hands-on experience in full stack development, debugging, and secure coding practices within Agile team environments.
\item Participated in project reviews to identify opportunities for performance optimization, scalability improvements, and code quality.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to access lessons, videos, and quizzes with real-time performance tracking dashboards.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL supporting online education with interactive features.
\item Integrated modules for lesson uploads, quizzes, and performance tracking providing real-time dashboards for instructors.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent user activity.
\item Deployed the platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 active students.
\end{itemize}

\textbf{PROSPR " Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive real-time chat app for low-vision users integrating text-to-speech and voice-to-text accessibility features.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and Socket.io with accessibility-focused UI design and navigation.
\item Integrated AWS Polly and Azure Speech Services enabling seamless text-to-speech and voice-to-text communication features.
\item Followed WCAG accessibility standards and conducted testing with assistive technologies ensuring inclusive usability for all users.
\item Deployed on AWS App Runner with Docker containers for scalable, low-latency communication and continuous availability.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}