% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Full Stack Web Developer with 2+ years of experience building scalable web applications and internal tools using React, JavaScript, TypeScript, Node.js, and RESTful APIs. Proven ability to design and implement end-to-end solutions across frontend and backend systems with strong focus on performance optimization, database management, and cloud deployment. Experienced in Agile environments, collaborating with cross-functional teams to deliver high-quality, user-centric products while maintaining clean, modular, and well-tested code.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Frontend Development:} React, Redux, JavaScript, TypeScript, HTML5, CSS3

\textbf{Backend Development:} Node.js, REST API, GraphQL, Python, Django, Flask

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQL, Database Design

\textbf{Cloud \& DevOps:} AWS, Docker, CI/CD, GitHub Actions, GitLab CI/CD, Kubernetes

\textbf{Development Practices:} Agile, Code Reviews, Testing, System Design, Performance Optimization

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Ownership, Problem Solving

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js to enhance functionality and user experience.
\item Designed and implemented RESTful APIs with optimized SQL queries improving system performance and backend reliability.
\item Deployed cloud applications using AWS, Docker, and CI/CD pipelines ensuring high availability and consistent uptime.
\item Collaborated in Agile teams through code reviews, sprint planning, and pair programming to deliver high-quality features.
\item Applied test-driven development and secure coding practices throughout SDLC reducing production issues and improving maintainability.
\item Led backend development initiatives while mentoring junior engineers on coding standards, architecture, and deployment strategies.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications across frontend and backend components using modern tech stacks.
\item Contributed to design and implementation of Proposal Management and Mailroom Tracking Systems with clean, modular code.
\item Worked closely with cross-functional teams to gather requirements, perform testing, and support deployment phases.
\item Gained hands-on experience in full stack development, software testing, and secure coding within Agile workflows.
\item Collaborated in project reviews to identify improvements in performance, scalability, and overall code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with notes, videos, and interactive quizzes during the pandemic.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack LMS using React, Node.js, and MySQL to support online education with high concurrent user access.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards for educators.
\item Implemented secure authentication, role-based access control, and optimized database queries for improved performance.
\item Deployed platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 active students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed inclusive chat app for low-vision users integrating accessibility features and assistive technologies.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Node.js, and WebSocket with accessibility-focused UI adhering to WCAG standards.
\item Integrated AWS Polly and Azure Speech Services enabling text-to-speech and voice-to-text for inclusive communication.
\item Tested extensively with assistive technologies ensuring usability for individuals with reading challenges and low vision.
\item Deployed on AWS with Docker containers for scalable, low-latency communication accessible to diverse user groups.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}