% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Developer with proven expertise in building scalable web applications using JavaScript, TypeScript, React, Python, and Django. Experienced in delivering end-to-end product features across backend, frontend, and APIs within Agile environments. Strong track record in cloud infrastructure with AWS, CI/CD pipelines, and maintaining production systems with high reliability. Passionate about creating intuitive user experiences and translating customer needs into robust technical solutions.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, PHP, SQL, HTML5, CSS3

\textbf{Frontend Technologies:} React, Redux, React Query, Bootstrap, Material UI, SASS

\textbf{Backend \& APIs:} Django, Node.js, Flask, FastAPI, REST API, GraphQL

\textbf{Databases \& Storage:} PostgreSQL, MySQL, MongoDB, Redis, DynamoDB, Firebase

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, CI/CD, Terraform, GitHub Actions

\textbf{Development Practices:} Agile, Scrum, TDD, Code Reviews, System Design, Technical Documentation

\textbf{Soft Skills:} Ownership, Collaboration, Adaptability, Communication, Problem Solving, Curiosity

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed full stack web applications using JavaScript, React, and Node.js delivering scalable features for e-commerce platforms.
\item Designed and implemented RESTful APIs optimizing database queries and integrating secure payment systems for improved reliability.
\item Deployed cloud-based applications on AWS with Docker and CI/CD pipelines ensuring consistent uptime and rapid feature delivery.
\item Collaborated within Agile teams through code reviews and sprint planning to ship high-quality features aligned with product goals.
\item Applied test-driven development and secure coding practices throughout SDLC reducing production issues and improving maintainability.
\item Led backend development for Shopify applications while mentoring junior developers on best practices and ownership in production.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Built enterprise web applications across frontend and backend components contributing to multiple product feature releases.
\item Contributed to design and implementation of Proposal Management and Mailroom Tracking Systems used by internal teams daily.
\item Worked closely with cross-functional teams to gather requirements, perform testing, and support deployment phases successfully.
\item Gained hands-on experience in full stack development, software testing, and secure coding within collaborative Agile workflows.
\item Participated in project reviews identifying improvements in performance, scalability, and code maintainability for production systems.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes efficiently.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack LMS using React, Node.js, and MySQL supporting online education with lesson uploads and performance tracking.
\item Integrated real-time progress dashboards and quizzes with secure authentication and role-based access for students and teachers.
\item Optimized database queries and implemented caching strategies to handle high concurrent usage during peak learning periods.
\item Deployed platform on AWS with CDN, SSL encryption, and autoscaling ensuring reliable access for over 6,000 active students.
\end{itemize}

\textbf{PROSPR " Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive real-time chat app for low-vision users integrating accessibility features and voice communication tools.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Node.js, and Socket.io with accessibility-focused UI adhering to WCAG standards.
\item Integrated AWS Polly and Azure Speech Services enabling seamless text-to-speech and voice-to-text communication for users.
\item Tested application with assistive technologies ensuring inclusive usability for individuals with reading challenges and low vision.
\item Deployed on AWS App Runner with Docker containers for scalable, low-latency communication supporting concurrent user sessions.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}