% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Developer with 3+ years of experience designing, building, and deploying scalable web applications and microservices using Node.js, JavaScript, React, and Angular. Proven expertise in developing RESTful APIs, implementing CI/CD pipelines, and leveraging containerization with Docker and Kubernetes. Skilled in Agile methodologies, database design with SQL Server and MySQL, and collaborating with cross-functional teams to deliver high-quality solutions that enhance performance and user experience.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, SQL, HTML5, CSS3

\textbf{Frontend Technologies:} React, Angular, Next.js, Vue.js, Bootstrap, Material UI

\textbf{Backend \& APIs:} Node.js, Express.js, REST API, Microservices, GraphQL

\textbf{Databases:} MySQL, MS SQL Server, PostgreSQL, MongoDB

\textbf{Cloud \& DevOps:} Docker, Kubernetes, OpenShift, AWS, CI/CD, GitHub Actions

\textbf{Testing \& Development Practices:} Unit Testing, Integration Testing, Agile, Scrum, Code Reviews, TDD

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Problem Solving, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, Node.js, and Angular to enhance functionality and user experience.
\item Designed and maintained RESTful APIs and microservices optimizing performance, scalability, and responsiveness of applications.
\item Deployed containerized applications using Docker and Kubernetes ensuring consistent uptime, reliability, and efficient cloud services.
\item Collaborated within Agile teams conducting code reviews, sprint planning, and testing to deliver high-quality, maintainable solutions.
\item Implemented CI/CD pipelines and automation testing strategies improving deployment efficiency and reducing production issues.
\item Led backend development for multiple applications while mentoring junior developers on best practices and technical design.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level web applications across frontend and backend using modern frameworks and technologies.
\item Contributed to design and implementation of internal systems collaborating with cross-functional teams throughout the SDLC.
\item Worked closely with development teams to gather requirements, perform thorough testing, and support deployment activities.
\item Gained hands-on experience in full stack development, API integration, and secure coding within Agile workflows and environments.
\item Participated in post-implementation reviews identifying improvements in performance, scalability, and code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS using Node.js and React enabling 6K+ students to learn with notes, videos, quizzes, and tracking features.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL to support online education with interactive modules.
\item Implemented RESTful APIs, real-time progress dashboards, and performance tracking for teachers ensuring responsive user experience.
\item Integrated secure authentication, role-based access control, and optimized SQL queries for high concurrent usage and scalability.
\item Deployed the platform on AWS with containerization and SSL encryption ensuring reliable access for over 6,000 active students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive real-time chat app using Node.js and React integrating accessibility features for low-vision users.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and WebSockets with accessibility-focused UI design and testing.
\item Integrated cloud-based speech services enabling text-to-speech and voice-to-text communication for inclusive user experience.
\item Followed WCAG accessibility standards and tested with assistive technologies ensuring compliance and usability for all users.
\item Deployed on AWS using Docker containers for scalable, low-latency communication with automated CI/CD pipelines and monitoring.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}