% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Full Stack Engineer with 2+ years of experience building scalable web applications using React, Node.js, and cloud technologies. Proficient in developing RESTful APIs, integrating microservices, and deploying applications on AWS and GCP with CI/CD automation. Experienced in Agile environments, collaborating across cross-functional teams to deliver secure, high-quality solutions. Strong foundation in JavaScript, TypeScript, SQL databases, and DevOps practices with a focus on continuous learning and problem-solving.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript (ES6+), TypeScript, Python, SQL, HTML5, CSS3

\textbf{Frontend Technologies:} React.js, Next.js, Redux, Bootstrap, Material UI, Responsive Design

\textbf{Backend \& APIs:} Node.js, Express.js, RESTful APIs, Microservices, Event-Driven Architecture

\textbf{Databases:} PostgreSQL, MySQL, MongoDB, SQL Query Optimization

\textbf{Cloud \& DevOps:} AWS, Google Cloud Platform, Docker, Kubernetes, Jenkins, GitHub Actions

\textbf{Security \& Authentication:} OAuth2, JWT, SSL/TLS, API Security, Secure Coding Practices

\textbf{Development Practices:} Agile, Scrum, CI/CD Pipelines, Code Reviews, Unit Testing, SDLC

\textbf{Soft Skills:} Collaboration, Communication, Problem Solving, Adaptability, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed full stack web applications using JavaScript, React, and Node.js to deliver scalable and maintainable e-commerce solutions.
\item Implemented RESTful APIs and optimized SQL queries for PostgreSQL and MySQL to improve system performance and reliability.
\item Deployed cloud-based applications on AWS using Docker and CI/CD pipelines ensuring consistent uptime and automated deployments.
\item Collaborated within Agile teams through code reviews, sprint planning, and daily standups to deliver high-quality features on schedule.
\item Applied secure coding practices and test-driven development throughout SDLC reducing production issues and enhancing code quality.
\item Mentored junior developers on best practices for backend development, deployment automation, and secure API design principles.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications across frontend and backend components using modern JavaScript frameworks.
\item Contributed to the design and implementation of scalable systems following service-oriented architecture and RESTful API patterns.
\item Worked closely with cross-functional teams to gather requirements, perform integration testing, and support deployment phases.
\item Gained hands-on experience in full stack development, automated testing, and secure coding within Agile and Scrum workflows.
\item Participated in code reviews and project retrospectives to identify improvements in performance, scalability, and maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full-stack LMS using React, Node.js, and MySQL to support online education during the pandemic.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time progress dashboards for teachers.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent usage.
\item Deployed the platform on AWS with CDN caching and SSL/TLS encryption ensuring reliable access for over 6,000 students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users and individuals with reading challenges integrating accessibility features.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and Socket.io with accessibility-focused UI following WCAG standards.
\item Integrated AWS Polly and Azure Speech Services to enable text-to-speech and voice-to-text communication for inclusivity.
\item Tested the application with assistive technologies and gathered user feedback to ensure usability for diverse accessibility needs.
\item Deployed on AWS App Runner with Docker containers for scalable, low-latency communication and automated CI/CD deployments.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}