% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Developer with hands-on expertise in building scalable web applications using React, Node.js, and modern cloud technologies. Proficient in designing RESTful APIs, implementing responsive interfaces, and leveraging AWS, Docker, and CI/CD pipelines for reliable deployments. Experienced in Agile collaboration, code reviews, and secure coding practices with strong knowledge of PostgreSQL, MongoDB, and microservices architecture. Passionate about continuous learning and applying emerging technologies to deliver high-quality, user-centered solutions.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, SQL, HTML5, CSS3, PHP, Bash

\textbf{Frontend Technologies:} React, Redux, Bootstrap, Material UI, SASS, Responsive Design

\textbf{Backend Technologies:} Node.js, Express.js, Django, Flask, RESTful APIs, GraphQL

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, Redis, SQLite, Database Design

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, CI/CD Pipelines, GitHub Actions, Terraform

\textbf{Testing \& Quality:} Unit Testing, Integration Testing, Postman, Jest, TDD, Code Reviews

\textbf{Software Architecture:} Microservices, Design Patterns, Scalability, Clean Architecture, MVC

\textbf{Soft Skills:} Collaboration, Communication, Problem Solving, Adaptability, Ownership, Mentorship

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using React, Node.js, and JavaScript delivering responsive user interfaces and APIs.
\item Built and optimized RESTful APIs with secure authentication and payment integration improving system reliability and performance.
\item Deployed cloud-based solutions using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and automated delivery workflows.
\item Collaborated in Agile teams through code reviews, sprint planning, and pair programming to maintain high-quality code standards.
\item Applied test-driven development and secure coding practices across SDLC improving maintainability and reducing production defects.
\item Mentored junior developers on best practices for backend development, deployment strategies, and modern coding standards.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in building enterprise web applications with both frontend and backend components using modern JavaScript frameworks.
\item Contributed to design and implementation of Proposal Management and Mailroom Tracking Systems with full stack development.
\item Worked with cross functional teams to gather requirements, perform testing, and support deployment phases in Agile workflows.
\item Gained hands-on experience in scalable application development, automated testing, and secure coding within production systems.
\item Participated in project reviews identifying improvements in performance, scalability, and code maintainability for systems.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed full stack LMS using React, Node.js, and MySQL supporting online education for pandemic learning needs.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards for teachers and students.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent user traffic.
\item Deployed platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 active student users.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users and individuals with reading challenges, integrating accessibility features.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Node.js, and Socket.io with accessibility-focused UI following WCAG standards.
\item Integrated AWS Polly and Azure Speech Services enabling text-to-speech and voice-to-text communication for inclusive usability.
\item Tested application with assistive technologies ensuring compliance with accessibility guidelines and inclusive user experiences.
\item Deployed on AWS App Runner with Docker containers for scalable, low-latency communication and reliable real-time messaging.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}