% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Full Stack Software Engineer with 4+ years of experience developing scalable web applications using JavaScript, TypeScript, Node.js, React, and modern cloud infrastructure. Proven ability to deliver high-performance solutions with strong proficiency in AI tooling integration, including ChatGPT and Codex, to accelerate development cycles. Skilled in backend development with Node.js and PHP, frontend frameworks like React and Next.js, and cloud platforms such as AWS. Experienced with CI/CD pipelines, testing best practices, and Agile methodologies.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Node.js, PHP, Python, SQL, HTML5, CSS3

\textbf{Frontend Frameworks \& Libraries:} React, Next.js, Redux, Bootstrap, Material UI, SASS

\textbf{Backend \& API Development:} Node.js, Express.js, REST API, GraphQL, Microservices, Serverless

\textbf{Database \& Caching:} MySQL, PostgreSQL, MongoDB, Redis, DynamoDB, Firebase

\textbf{Cloud Infrastructure \& DevOps:} AWS, Docker, Kubernetes, Terraform, CI/CD, GitHub Actions

\textbf{Testing \& Quality Assurance:} Unit Testing, Integration Testing, TDD, Postman, Automation Testing

\textbf{AI \& Automation Tools:} ChatGPT API, Prompt Engineering, AI Integration, Workflow Automation

\textbf{Software Engineering Practices:} Agile, Scrum, Code Reviews, Design Patterns, Clean Architecture

\textbf{Soft Skills:} Communication, Collaboration, Ownership, Adaptability, Problem Solving, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, TypeScript, React, and Node.js to enhance functionality and user experience.
\item Implemented RESTful APIs, optimized SQL and NoSQL queries, and integrated secure systems to improve reliability and performance.
\item Deployed and maintained cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and high availability.
\item Collaborated within Agile teams through code reviews, sprint planning, and daily standups to deliver high-quality software solutions.
\item Applied testing best practices and secure coding standards throughout SDLC improving maintainability and reducing production issues.
\item Led backend development initiatives while mentoring team members on coding standards, deployment practices, and AI tooling integration.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications across frontend and backend components using modern JavaScript frameworks.
\item Contributed to design and implementation of management systems with focus on scalability, performance, and maintainability.
\item Worked closely with cross functional teams to gather requirements, perform testing, and support deployment phases using Agile methods.
\item Gained hands-on experience in full stack development, software testing, and secure coding within collaborative team environments.
\item Collaborated in project reviews to identify improvements in performance, scalability, and code quality through iterative feedback loops.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with notes, videos, and interactive quizzes using modern web technologies.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL to support online education with high concurrent usage.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time progress dashboards for instructors.
\item Implemented secure authentication, role-based access control, and optimized database queries for scalability and reliability.
\item Deployed the platform on AWS with CDN caching and SSL encryption, ensuring reliable access for over 6,000 active students.
\end{itemize}

\textbf{PROSPR " Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive real-time chat app for low-vision users integrating accessibility features and speech technologies.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and WebSockets with accessibility-focused UI design and WCAG compliance.
\item Integrated AWS Polly and Azure Speech Services to enable seamless text-to-speech and voice-to-text communication for users.
\item Followed accessibility standards and tested with assistive technologies to ensure inclusive usability for diverse user groups.
\item Deployed on AWS using Docker containers for scalable, low-latency communication with monitoring and logging enabled.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}