% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Developer with expertise in backend services, API design, and modern frontend frameworks. Proficient in building scalable systems using Python, JavaScript, React, and Node.js with strong experience in cloud infrastructure, CI/CD pipelines, and event-driven architectures. Proven track record delivering end-to-end solutions across distributed systems, databases, and user-facing applications while collaborating with cross-functional teams in Agile environments.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, TypeScript, SQL, HTML5, CSS3, Bash

\textbf{Frontend Frameworks \& Libraries:} React, Redux, Next.js, Bootstrap, Material UI, Tailwind CSS

\textbf{Backend \& API Development:} Node.js, Django, Flask, FastAPI, Express.js, REST API, GraphQL

\textbf{Database \& Data Systems:} PostgreSQL, MySQL, MongoDB, Redis, SQLite, DynamoDB

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, CI/CD, GitHub Actions, Infrastructure as Code

\textbf{Architecture \& Engineering Practices:} Microservices, Event-Driven Architecture, System Design, Clean Architecture

\textbf{Testing \& Quality Assurance:} Unit Testing, Integration Testing, TDD, Automation Testing, Postman

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Problem Solving, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using JavaScript, React, and Node.js implementing RESTful APIs and backend services.
\item Built event-driven workflows and microservices architecture improving system reliability and real-time data processing capabilities.
\item Optimized PostgreSQL and MySQL database queries and implemented caching strategies enhancing application performance significantly.
\item Deployed cloud-based solutions on AWS using Docker, Kubernetes, and CI/CD pipelines ensuring high availability and observability.
\item Collaborated with product managers and cross-functional teams translating business requirements into intuitive user experiences.
\item Established automated testing practices across backend services and frontend components reducing production issues and deployment time.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise applications across frontend and backend components using modern frameworks and API integration.
\item Contributed to design and implementation of workflow management systems supporting operational efficiency and user engagement.
\item Collaborated with cross-functional teams gathering requirements, performing testing, and supporting deployment phases in Agile sprints.
\item Gained hands-on experience building full stack features, implementing secure authentication, and optimizing database interactions.
\item Participated in code reviews and technical discussions identifying improvements in performance, scalability, and maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with notes, videos, and interactive quizzes during the pandemic outbreak.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed full stack LMS using React, Node.js, and MySQL supporting real-time dashboards and performance tracking.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent user sessions.
\item Integrated backend APIs for lesson uploads, quizzes, and progress tracking ensuring seamless data flow between services and UI.
\item Deployed platform on AWS with Docker, CDN caching, and SSL encryption ensuring reliable access for over 6,000 active students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed inclusive real-time chat application for low-vision users integrating accessibility features and assistive technology.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Node.js, and Socket.io with event-driven architecture for low-latency communication.
\item Integrated AWS Polly and Azure Speech Services APIs enabling text-to-speech and voice-to-text functionality for accessibility.
\item Followed WCAG accessibility standards and tested with assistive technologies ensuring inclusive usability across user groups.
\item Deployed on AWS App Runner using Docker containers with automated CI/CD pipelines ensuring scalability and consistent uptime.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}