% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Developer with expertise in JavaScript, React, Python, and SQL-based systems including PostgreSQL and MySQL. Skilled in building scalable web applications, designing modern user interfaces, and implementing backend financial calculations. Experienced collaborating with cross-functional teams in Agile environments to translate end-user requirements into robust technical solutions. Proven track record deploying cloud-based platforms using AWS, Docker, and CI/CD pipelines with a strong interest in expanding financial domain knowledge.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, SQL, HTML5, CSS3, Bash

\textbf{Frontend Frameworks \& Libraries:} React, Redux, Bootstrap, Material UI, jQuery

\textbf{Backend Frameworks \& APIs:} Django, Flask, Node.js, RESTful APIs, FastAPI

\textbf{Databases \& Data Management:} PostgreSQL, MySQL, MongoDB, SQLite, Database Design

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, CI/CD Pipelines, GitHub Actions

\textbf{Development Practices:} Agile, Scrum, SDLC, Testing, Code Reviews, TDD

\textbf{Systems \& Architecture:} Linux Environments, Microservices, Clean Architecture, Performance Optimization

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js delivering high-performance user experiences.
\item Designed and implemented RESTful APIs with optimized SQL queries in PostgreSQL and MySQL improving system reliability by 35\%.
\item Deployed cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring 99.9\% uptime and consistent availability.
\item Collaborated in Agile teams through daily standups, code reviews, and sprint planning ensuring on-time delivery of features.
\item Applied test-driven development and secure coding standards throughout SDLC reducing production defects significantly.
\item Mentored junior developers on Python backend best practices and modern React development improving team productivity.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in building enterprise web applications with Python and JavaScript across frontend and backend components.
\item Contributed to designing and implementing Proposal Management System using SQL databases and React interfaces.
\item Collaborated with cross-functional teams to gather requirements, perform testing, and support deployment phases.
\item Gained hands-on experience in full stack development, software testing, and secure coding within Agile workflows.
\item Participated in project reviews to identify improvements in performance, scalability, and code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built scalable LMS with React and Python enabling 6K+ students to learn through videos, quizzes, and real-time dashboards.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack LMS using React frontend and Python backend with PostgreSQL database supporting concurrent users efficiently.
\item Integrated lesson uploads, quizzes, and real-time performance tracking dashboards enabling teachers to monitor progress.
\item Implemented secure authentication with role-based access control and optimized SQL queries for high-volume concurrent usage.
\item Deployed platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 active students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed inclusive real-time chat app for low-vision users integrating text-to-speech and voice-to-text accessibility features.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Node.js, and WebSockets with accessibility-focused UI for inclusive user experience.
\item Integrated AWS Polly and Azure Speech Services enabling text-to-speech and voice-to-text communication for diverse users.
\item Followed WCAG accessibility standards and tested with assistive technologies ensuring compliance and inclusive usability.
\item Deployed on AWS using Docker containers for scalable low-latency communication with automated CI/CD deployment pipelines.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}