% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Developer with proven experience building scalable web applications using React, Node.js, and Django. Skilled in both relational and NoSQL databases including PostgreSQL, MySQL, and MongoDB. Adept at collaborating with distributed teams in remote environments and delivering end-to-end features across the stack. Strong communicator with expertise in cloud deployment, CI/CD pipelines, and Agile methodologies, committed to writing clean, maintainable code.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, Python, SQL, HTML5, CSS3, TypeScript

\textbf{Frontend Technologies:} React, Redux, Bootstrap, Material UI, SASS

\textbf{Backend Technologies:} Node.js, Django, Flask, Express.js, REST API

\textbf{Database Systems:} PostgreSQL, MySQL, MongoDB, Firebase, SQLite

\textbf{Cloud \& DevOps:} AWS, Docker, CI/CD, GitHub Actions, Kubernetes

\textbf{Development Practices:} Agile, Scrum, Git, Code Reviews, Testing

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Problem Solving, Time Management

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using React, Node.js, and JavaScript to enhance e-commerce functionality.
\item Built and maintained RESTful APIs with optimized SQL queries and secure payment integrations improving system reliability.
\item Deployed cloud-based applications on AWS using Docker and CI/CD pipelines ensuring consistent uptime and availability.
\item Collaborated with distributed Agile teams through code reviews and sprint planning to deliver high-quality features.
\item Applied test-driven development and secure coding standards across the SDLC reducing production issues significantly.
\item Led backend development initiatives while mentoring junior developers on best practices and deployment strategies.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications across frontend and backend using modern frameworks and databases.
\item Contributed to design and implementation of the Proposal Management and Mailroom Tracking Systems end-to-end.
\item Worked closely with cross-functional teams to gather requirements, perform testing, and support deployment phases.
\item Gained hands-on experience in full stack development and secure coding within Agile workflows and remote collaboration.
\item Collaborated in project reviews to identify performance improvements, scalability enhancements, and code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS using React, Node.js, and MySQL enabling 6K+ students to learn with notes, videos, and interactive quizzes.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed full stack LMS using React, Node.js, and MySQL to support online education during the pandemic.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards for educators.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent usage.
\item Deployed platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed inclusive real-time chat app using React, Node.js, and Socket.io with accessibility features for low-vision users.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Node.js, and Socket.io with accessibility-focused UI design and features.
\item Integrated AWS Polly and Azure Speech Services enabling text-to-speech and voice-to-text communication capabilities.
\item Followed WCAG accessibility standards and tested with assistive technologies to ensure inclusive usability for all users.
\item Deployed on AWS App Runner with Docker containers for scalable, low-latency communication and high availability.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}