% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Developer with 3+ years of experience building scalable web applications using React, Node.js, and MongoDB. Proven ability to debug complex issues across frontend and backend systems while collaborating with cross-functional teams. Strong communicator skilled at explaining technical concepts to both technical and non-technical stakeholders. Experienced in deploying cloud-based solutions using AWS, implementing CI/CD pipelines, and supporting production environments in fast-paced Agile settings.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, SQL, HTML5, CSS3

\textbf{Frontend Technologies:} React, Redux, Bootstrap, Material UI, React Query, Responsive Design

\textbf{Backend Technologies:} Node.js, Express.js, RESTful APIs, Django, Flask, GraphQL

\textbf{Database \& Data Management:} MongoDB, PostgreSQL, MySQL, Redis, Firebase

\textbf{Cloud \& DevOps:} AWS, Docker, CI/CD, GitHub Actions, Kubernetes, Infrastructure as Code

\textbf{Software Development Practices:} Agile, Scrum, System Design, Debugging, Code Reviews, Technical Documentation

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Customer Support, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed full stack web applications using React and Node.js, implementing features to enhance e-commerce functionality and user experience.
\item Built and maintained RESTful APIs with Express.js, optimizing database queries and integrating secure payment systems for reliability.
\item Deployed cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and production system stability.
\item Debugged and resolved complex frontend and backend issues across production systems to minimize downtime and improve system performance.
\item Collaborated within Agile teams through code reviews, sprint planning, and pair programming to deliver high-quality customer-facing products.
\item Mentored junior developers on best practices for coding, testing, debugging, and deployment while leading backend development initiatives.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications across frontend and backend components using React, Node.js, and MongoDB.
\item Contributed to design and implementation of internal tools including Proposal Management and Mailroom Tracking Systems.
\item Worked with cross-functional teams to gather requirements, perform testing, and support deployment phases in Agile environments.
\item Gained hands-on experience in full stack development, debugging production issues, and applying secure coding practices throughout SDLC.
\item Collaborated in project reviews to identify improvements in performance, scalability, and maintainability across customer-facing products.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS using React, Node.js, and MySQL enabling 6,000+ students to access notes, videos, quizzes, and performance tracking.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack LMS using React, Node.js, Express.js, and MySQL to support online education with real-time progress dashboards.
\item Integrated modules for lesson uploads, interactive quizzes, and performance tracking with secure role-based authentication and access control.
\item Optimized database queries and implemented caching strategies to handle high concurrent usage and improve application responsiveness.
\item Deployed platform on AWS with CDN caching, SSL encryption, and autoscaling ensuring reliable access for over 6,000 active students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed inclusive real-time chat application using React, Node.js, and Socket.io with integrated accessibility features for low-vision users.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Node.js, Express.js, and Socket.io with accessibility-focused UI following WCAG standards.
\item Integrated AWS Polly and Azure Speech Services to enable text-to-speech and voice-to-text communication for inclusive user experience.
\item Tested application with assistive technologies to ensure usability for individuals with reading challenges and visual impairments.
\item Deployed on AWS App Runner using Docker containers ensuring scalable, low-latency communication and reliable production system performance.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}