% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Software Developer with 3+ years of experience building scalable web applications and APIs using JavaScript, React, Node.js, Python, and SQL. Proven expertise in developing RESTful APIs, optimizing database queries with PostgreSQL and MySQL, and deploying cloud-based solutions on AWS and GCP using Docker and CI/CD pipelines. Strong background in Agile methodologies, data-driven applications, and cross-functional collaboration to deliver high-quality software solutions.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, SQL, HTML5, CSS3, Bash, PowerShell

\textbf{Frontend Development:} React, Redux, Next.js, Bootstrap, Material UI, Responsive Design

\textbf{Backend Development:} Node.js, Express.js, Django, Flask, FastAPI, RESTful APIs

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQL Optimization, Data Modeling, ETL Pipelines

\textbf{Cloud \& DevOps:} AWS, Google Cloud, Docker, Kubernetes, CI/CD, GitHub Actions

\textbf{Testing \& Quality Assurance:} Unit Testing, Integration Testing, TDD, Postman, Code Reviews

\textbf{Version Control \& Collaboration:} Git, GitHub, GitLab, Bitbucket, Agile, Scrum

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Ownership, Team Leadership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js integrated with RESTful APIs and backend services.
\item Built and maintained RESTful APIs ensuring security, performance, and comprehensive documentation for seamless front-end integration.
\item Optimized SQL queries and database design in PostgreSQL and MySQL improving performance and ensuring data integrity across systems.
\item Deployed and maintained cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring high availability and uptime.
\item Collaborated within Agile teams through code reviews, sprint planning, and iterative development to deliver high-quality software solutions.
\item Applied unit and integration testing with TDD practices throughout SDLC reducing production issues and improving code maintainability.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications using both frontend and backend technologies within Agile development workflows.
\item Contributed to the design and implementation of data-driven applications including Proposal Management and Mailroom Tracking Systems.
\item Worked closely with cross-functional teams including product managers and designers to gather requirements and support deployment.
\item Gained hands-on experience in full stack development, SQL database management, and secure coding practices throughout project lifecycle.
\item Participated in code reviews and testing phases to identify improvements in performance, scalability, and application reliability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes online.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL supporting interactive lessons, quizzes, and performance tracking.
\item Built secure RESTful APIs for user authentication, role-based access, and real-time progress dashboards for teachers and students.
\item Optimized database queries and implemented caching strategies to handle high concurrent usage and improve application performance.
\item Deployed the platform on AWS with Docker, CDN caching, and SSL encryption ensuring reliable access for over 6,000 students daily.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users and individuals with reading challenges integrating accessibility features.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and WebSockets with accessibility-focused UI following WCAG standards.
\item Integrated AWS and Azure cloud services to enable text-to-speech and voice-to-text communication for inclusive user experience.
\item Developed RESTful APIs for user authentication, message handling, and real-time data synchronization across multiple client devices.
\item Deployed on AWS using Docker containers and orchestration tools ensuring scalable, low-latency communication for all users.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}