% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Engineer with 2+ years of experience building high-performance web applications using modern technologies including React, TypeScript, Node.js, and GraphQL. Proven expertise in designing scalable distributed systems, implementing RESTful and GraphQL APIs, and optimizing performance across the full stack. Strong background in cloud infrastructure with AWS, Docker, and CI/CD pipelines. Experienced collaborating with cross-functional teams to deliver end-to-end product experiences from design to production.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, SQL, HTML5, CSS3

\textbf{Frontend Technologies:} React, Redux, GraphQL, Bootstrap, Material UI, Responsive Design

\textbf{Backend \& APIs:} Node.js, Express.js, REST API, GraphQL, Microservices, WebSockets

\textbf{Databases:} PostgreSQL, MySQL, MongoDB, Redis, Database Design, Query Optimization

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, CI/CD, GitHub Actions, Infrastructure as Code

\textbf{Architecture \& Design:} System Design, Scalability, Performance Optimization, Design Patterns, Clean Architecture

\textbf{Development Practices:} Agile, Scrum, TDD, Code Reviews, Technical Documentation

\textbf{Soft Skills:} Collaboration, Communication, Ownership, Adaptability, Problem Solving, Analytical Thinking

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using React, Node.js, and GraphQL to enhance functionality and user engagement.
\item Designed and implemented RESTful and GraphQL APIs with optimized database queries improving system performance and reliability.
\item Deployed cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring high availability and consistent uptime.
\item Collaborated with cross-functional teams through code reviews, sprint planning, and pair programming to deliver quality products.
\item Applied test-driven development and secure coding standards throughout SDLC reducing production issues and enhancing maintainability.
\item Led end-to-end development of multiple applications while mentoring junior developers on architectural best practices and deployment.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to building enterprise-level web applications across frontend and backend using modern frameworks and technologies.
\item Participated in design and implementation of scalable systems including Proposal Management and Mailroom Tracking applications.
\item Collaborated with Product and Design teams to gather requirements, perform testing, and support deployment across all phases.
\item Gained hands-on experience in full stack development, debugging distributed systems, and optimizing performance in Agile workflows.
\item Engaged in technical planning and code reviews to identify improvements in scalability, performance, and overall code quality.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with notes, videos, and interactive quizzes during the pandemic.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL supporting high concurrent usage and real-time updates.
\item Integrated lesson uploads, quizzes, and performance tracking with dashboards for teachers to monitor student progress effectively.
\item Implemented secure authentication, role-based access control, and optimized database queries for scalability and performance.
\item Deployed on AWS with CDN caching and SSL encryption ensuring reliable, secure access for over 6,000 concurrent students.
\end{itemize}

\textbf{PROSPR " Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive real-time chat app for low-vision users integrating text-to-speech and voice-to-text accessibility.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and WebSockets with accessibility-focused UI following WCAG standards.
\item Integrated AWS Polly and Azure Speech Services enabling text-to-speech and voice-to-text communication for inclusive usability.
\item Conducted testing with assistive technologies ensuring seamless experience for users with visual and reading challenges.
\item Deployed on AWS with Docker containers for scalable, low-latency real-time communication and consistent high availability.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}