% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Full Stack Engineer with strong backend experience building scalable, high-performance systems using Python, JavaScript, and cloud infrastructure. Proven expertise in designing event-driven architectures, RESTful APIs, and distributed systems deployed on AWS and GCP. Skilled in PostgreSQL, Docker, Kubernetes, and CI/CD automation with a focus on reliability, observability, and rapid delivery. Experienced in Agile environments, collaborating across teams to translate complex requirements into clean, maintainable code.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, TypeScript, SQL, HTML5, CSS3, Bash, PowerShell

\textbf{Backend \& APIs:} Node.js, Django, Flask, FastAPI, Express.js, REST API, GraphQL, WebSockets

\textbf{Databases \& Data:} PostgreSQL, MySQL, MongoDB, Redis, DynamoDB, ETL Pipelines, Data Modeling

\textbf{Cloud \& Infrastructure:} AWS, GCP, Docker, Kubernetes, Terraform, Lambda, EC2, S3, RDS

\textbf{Architecture \& Systems:} Microservices, Event-Driven Architecture, Distributed Systems, CRUD Systems, API Gateway

\textbf{DevOps \& CI/CD:} GitHub Actions, GitLab CI/CD, Jenkins, Docker Compose, Infrastructure as Code, Monitoring

\textbf{Development Practices:} Agile, Scrum, TDD, Code Reviews, System Design, Performance Optimization, Observability

\textbf{Soft Skills:} High Ownership, Collaboration, Communication, Adaptability, Problem Solving, Pragmatism

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using JavaScript, React, and Node.js with event-driven architecture patterns for reliability.
\item Designed and implemented high-performance RESTful APIs optimizing PostgreSQL queries and secure payment integrations at scale.
\item Deployed and maintained cloud infrastructure on AWS using Docker, Kubernetes, and CI/CD pipelines ensuring high availability.
\item Collaborated in Agile teams through code reviews, sprint planning, and pair programming to deliver high-quality production systems.
\item Applied test-driven development, clean architecture, and observability practices improving system performance and maintainability.
\item Led backend development for multiple applications mentoring junior engineers on distributed systems and deployment best practices.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level web applications across frontend and backend with focus on scalability and performance.
\item Contributed to designing and building distributed systems for Proposal Management and Mailroom Tracking with clean interfaces.
\item Worked closely with cross-functional teams gathering requirements, performing integration testing, and supporting deployments.
\item Gained hands-on experience in full stack development, event-driven systems, and secure coding within Agile development workflows.
\item Collaborated in project reviews identifying improvements in performance, reliability, data integrity, and overall system design.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS supporting 6K+ students with lesson management, quizzes, and real-time dashboards using cloud infrastructure.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and PostgreSQL supporting high-concurrency student and teacher workflows.
\item Implemented secure authentication, role-based access control, and real-time progress tracking with optimized database query performance.
\item Built event-driven modules for lesson uploads, quiz management, and performance dashboards ensuring reliable state management at scale.
\item Deployed on AWS with Docker, CDN caching, SSL encryption, and monitoring ensuring 99.9\% uptime for over 6,000 concurrent students.
\end{itemize}

\textbf{Automated Cryptocurrency Trading Bot} -- \emph{Personal Project}

\vspace{-1pt}

Created a Python trading bot using Binance API and WebSocket for real-time automated trade execution with risk control and logging.
\vspace{-1pt}
\begin{itemize}
\item Developed a fully automated trading bot in Python using Binance API and WebSocket for real-time market data streaming and execution.
\item Implemented dynamic trading strategies, stop-loss mechanisms, and order execution algorithms with deterministic state management.
\item Integrated Pandas and NumPy for market analysis, backtesting, and performance optimization improving trading accuracy and reliability.
\item Deployed using Docker on AWS EC2 with 24/7 uptime, comprehensive logging, and monitoring for high-performance, compute-heavy workloads.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}