% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Developer with expertise in Python, JavaScript, and cloud-native architectures on AWS. Proven experience building scalable web applications, implementing CI/CD pipelines, and deploying containerized solutions using Docker and AWS services. Skilled in React, Node.js, Django, and PostgreSQL with hands-on experience integrating AI APIs and automation workflows. Passionate about leveraging modern frameworks and DevOps practices to deliver high-quality solutions.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, TypeScript, SQL, HTML5, CSS3, Bash

\textbf{Frameworks \& Libraries:} React, Next.js, Node.js, Django, Flask, FastAPI, Redux

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, Redis, AWS RDS, DynamoDB

\textbf{Cloud \& DevOps:} AWS, AWS S3, AWS Lambda, Docker, Kubernetes, GitHub Actions, CI/CD

\textbf{AI Integration \& APIs:} OpenAI SDK, LLM API, ChatGPT API, Prompt Engineering, Machine Learning APIs

\textbf{Software Development:} Agile, Scrum, REST API, Microservices, System Design, TDD

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Ownership, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js to enhance functionality and user experience.
\item Implemented RESTful APIs, optimized PostgreSQL queries, and integrated secure payment systems improving reliability and performance.
\item Deployed and maintained cloud-based applications using AWS, Docker, and GitHub Actions ensuring consistent uptime and availability.
\item Collaborated within Agile teams through code reviews, sprint planning, and pair programming to ensure high-quality deliverables.
\item Applied test-driven development and secure coding standards throughout SDLC improving maintainability and reducing production issues.
\item Led backend development for multiple applications while mentoring junior developers on best coding and deployment practices.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level web and mobile applications across both frontend and backend components using modern frameworks.
\item Contributed to the design and implementation of Proposal Management and Mailroom Tracking Systems with secure authentication layers.
\item Worked closely with cross-functional teams to gather requirements, perform integration testing, and support deployment phases.
\item Gained hands-on experience in full stack development, containerization, and secure coding within Agile workflows and sprint cycles.
\item Collaborated in project reviews to identify improvements in performance, scalability, and code maintainability across deployments.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes online.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full-stack LMS using React, Node.js, and PostgreSQL to support online education during the pandemic.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time progress dashboards for teachers.
\item Implemented secure authentication, role-based access, and optimized database queries for high concurrent usage and scalability.
\item Deployed the platform on AWS with S3 storage and SSL encryption, ensuring reliable access for over 6,000 active students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users integrating AI-powered accessibility features and real-time communication.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and WebSockets with accessibility-focused UI design and navigation.
\item Integrated AWS Polly and Azure Speech Services APIs to enable text-to-speech and voice-to-text communication for inclusivity.
\item Followed WCAG accessibility standards and tested with assistive technologies to ensure inclusive usability for all user groups.
\item Deployed on AWS using Docker containers and ECS for scalable, low-latency communication with automated CI/CD pipelines.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}