% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Software Engineer with proven expertise in designing, developing, and deploying scalable web applications using JavaScript, React, Node.js, Python, and cloud technologies. Experienced in building robust backend services, RESTful APIs, and database-driven solutions with strong emphasis on code quality, testing, and Agile collaboration. Skilled in implementing CI/CD pipelines, containerization, and cloud infrastructure to ensure reliability and performance at scale.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, PHP, SQL, HTML5, CSS3

\textbf{Frontend Technologies:} React, Redux, Bootstrap, Material UI, SASS, Responsive Design

\textbf{Backend \& APIs:} Node.js, Express.js, Django, Flask, REST API, GraphQL

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, Database Design, Query Optimization

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, CI/CD, GitHub Actions, Infrastructure as Code

\textbf{Development Practices:} Agile, Scrum, Code Reviews, Unit Testing, TDD, Technical Documentation

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Ownership, Mentorship

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js to enhance functionality and user experience.
\item Designed and implemented RESTful APIs and optimized SQL queries to improve system reliability and backend performance.
\item Deployed cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and high availability.
\item Collaborated within Agile teams through code reviews, sprint planning, and pair programming to deliver high-quality features.
\item Applied test-driven development and secure coding standards throughout SDLC reducing production issues and technical debt.
\item Led backend development for multiple applications while mentoring junior developers on best coding and deployment practices.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to developing enterprise-level web applications across both frontend and backend components using modern frameworks.
\item Participated in the design and implementation of management systems including requirements analysis and architecture planning.
\item Worked closely with cross functional teams to gather requirements, perform testing, and support deployment to production.
\item Gained hands-on experience in full stack development, software testing, and secure coding within Agile workflows and sprints.
\item Collaborated in project reviews to identify improvements in performance, scalability, and code maintainability for future releases.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with notes, videos, and interactive quizzes during the pandemic crisis.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL to support online education during the pandemic.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards for educators and students.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent user traffic.
\item Deployed the platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 active students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users integrating accessibility features and text-to-speech communication.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and Socket.io with accessibility-focused UI and responsive design.
\item Integrated AWS Polly and Azure Speech Services to enable text-to-speech and voice-to-text for inclusive communication.
\item Followed WCAG accessibility standards and tested with assistive technologies to ensure usability for diverse user groups.
\item Deployed on AWS App Runner with Docker containers for scalable, low-latency real-time communication and high availability.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}