% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Developer with proven expertise in building responsive web interfaces using HTML5, CSS3, JavaScript, React, and modern frameworks. Experienced in developing modular UI components, integrating RESTful APIs, optimizing performance, and implementing CI/CD pipelines. Skilled in deploying scalable applications on AWS and collaborating within Agile teams to deliver high-quality solutions aligned with modern web standards and business objectives.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Frontend Development:} HTML5, CSS3, JavaScript, React, Bootstrap, Responsive Design

\textbf{Backend Development:} Node.js, Python, Django, RESTful APIs, Authentication Flows

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQL Optimization

\textbf{Cloud \& DevOps:} AWS, Docker, CI/CD Pipelines, GitHub Actions, GitLab CI/CD

\textbf{Testing \& Performance:} Unit Testing, Performance Optimization, Caching, Lazy Loading

\textbf{Software Development Practices:} Agile, Scrum, Code Reviews, Technical Documentation

\textbf{Soft Skills:} Communication, Team Collaboration, Problem Solving, Adaptability, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed responsive full stack web applications using JavaScript, React, and Node.js to deliver user-friendly interfaces.
\item Implemented RESTful APIs with authentication flows and error handling to improve system reliability and data integration.
\item Optimized application performance through caching strategies, lazy loading, and bundle size analysis for faster load times.
\item Deployed cloud-based solutions using AWS and CI/CD pipelines ensuring consistent uptime and seamless deployment automation.
\item Collaborated in Agile teams through code reviews and sprint planning to maintain high-quality deliverables and best practices.
\item Mentored junior developers on modular UI components, scalable architecture, and secure coding standards throughout SDLC.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in building enterprise web applications with cross-browser compatible code using HTML5, CSS3, and JavaScript frameworks.
\item Contributed to frontend and backend integration by translating design mockups into high-quality, responsive user interfaces.
\item Worked closely with cross functional teams to gather requirements, perform testing, and ensure adherence to web standards.
\item Gained hands-on experience in implementing testing automation, Agile best practices, and technical documentation for APIs.
\item Collaborated in project reviews to identify improvements in performance, scalability, and maintainability of web components.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to access lessons, videos, and quizzes with real-time progress tracking dashboards.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL to support interactive online education and learning.
\item Integrated RESTful APIs for lesson uploads, quizzes, authentication flows, and real-time data updates with performance tracking.
\item Optimized database queries and implemented caching strategies to handle high concurrent usage from over 6,000 active students.
\item Deployed the platform on AWS with CDN caching, SSL encryption, and monitoring to ensure reliable, secure, and fast access.
\end{itemize}

\textbf{PROSPR " Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users with real-time communication and accessibility-focused UI design features.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and WebSockets with modular, reusable UI components for accessibility.
\item Integrated AWS Polly and Azure Speech Services to enable text-to-speech and voice-to-text for inclusive user communication.
\item Followed WCAG standards and tested with assistive technologies to ensure cross-browser and cross-device compatible interfaces.
\item Deployed using Docker on AWS with CI/CD automation for scalable, low-latency, and reliable communication across all devices.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}