% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Developer with 3+ years of experience building scalable web applications using JavaScript, React, and Node.js. Proven expertise in designing RESTful APIs, microservices, and responsive interfaces with strong proficiency in SQL databases and cloud platforms. Experienced in Agile workflows, CI/CD pipelines, and collaborating with cross-functional teams to deliver high-quality solutions. Skilled in containerization with Docker, automation testing, and implementing best practices for code quality and performance optimization.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, SQL, HTML5, CSS3

\textbf{Frontend Technologies:} React, Next.js, Angular, Vue.js, Bootstrap, Material UI

\textbf{Backend \& APIs:} Node.js, Express.js, REST API, GraphQL, Microservices

\textbf{Databases:} SQL Server, PostgreSQL, MySQL, MongoDB, Redis

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, CI/CD, GitHub Actions, Jenkins

\textbf{Development Practices:} Agile, Scrum, TDD, Code Reviews, Unit Testing

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js to enhance platform functionality and user experience.
\item Designed and implemented RESTful APIs and microservices, optimizing SQL queries to improve system performance and reliability.
\item Deployed cloud-based applications using AWS and Docker with CI/CD pipelines, ensuring consistent uptime and automated testing strategies.
\item Collaborated in Agile team environment through code reviews, sprint planning, and pair programming to maintain high code quality standards.
\item Conducted post-implementation reviews and shared knowledge to foster continuous learning and process improvement across the team.
\item Led backend development while mentoring junior developers on best practices for scalable, testable, and maintainable application systems.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level web applications with frontend UI tools and backend components across full software lifecycle.
\item Contributed to design and implementation of management systems, integrating applications with internal tools for feature delivery and support.
\item Worked with cross-functional teams to analyze organizational needs, gather requirements, and conduct thorough testing prior to release.
\item Gained hands-on experience in Agile processes, container platforms, and maintaining documentation for system development and revisions.
\item Participated in code reviews and project assessments to identify improvements in performance, scalability, and application responsiveness.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack LMS using React, Node.js, and relational database to support online education with responsive web application design.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards ensuring scalability and responsiveness.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent usage and performance.
\item Deployed platform on AWS with CDN caching and SSL encryption, maintaining reliable access for over 6,000 students with effective monitoring.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users and individuals with reading challenges, integrating accessibility features.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Node.js, and WebSockets with accessibility-focused responsive UI design for inclusive usability.
\item Integrated third-party cloud services to enable text-to-speech and voice-to-text communication, enhancing collaboration across user groups.
\item Followed accessibility standards and tested with assistive technologies to ensure application met organizational needs and best practices.
\item Deployed on cloud platform with Docker containers and automation testing for scalable, low-latency communication and continuous deployment.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}