% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Developer with strong proficiency in Python, FastAPI, Flask, and Django, coupled with hands-on experience in AWS services, cloud architecture, and serverless solutions. Skilled in building scalable applications using React, Node.js, and modern DevOps practices including Docker, Kubernetes, and CI/CD pipelines. Proven ability to deliver robust solutions leveraging AI integration, LLM APIs, and prompt engineering while maintaining security best practices and compliance standards.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, SQL, Bash, PowerShell, HTML, CSS

\textbf{Python Frameworks \& Libraries:} FastAPI, Flask, Django, pandas, Asyncio

\textbf{AWS \& Cloud Services:} AWS Lambda, AWS EC2, AWS S3, AWS RDS, CloudFormation, Serverless

\textbf{AI \& Machine Learning:} LLM API, ChatGPT API, Prompt Engineering, AI Integration, Machine Learning APIs

\textbf{DevOps \& Containerization:} Docker, Kubernetes, Git, GitHub Actions, GitLab CI/CD, Jenkins

\textbf{Database \& Architecture:} PostgreSQL, MongoDB, MySQL, Vector Databases, Microservices

\textbf{Security \& Compliance:} OAuth, JWT, API Security, Encryption, IAM, Responsible AI

\textbf{Soft Skills:} Communication, Team Collaboration, Adaptability, Problem Solving, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using Python, FastAPI, React, and Node.js to deliver high-performance enterprise solutions.
\item Implemented RESTful APIs, optimized database queries, and integrated AWS services including Lambda, S3, and RDS for cloud-native solutions.
\item Deployed containerized applications using Docker and Kubernetes with automated CI/CD pipelines ensuring consistent uptime and scalability.
\item Collaborated within Agile teams through code reviews, sprint planning, and technical documentation to ensure quality and compliance standards.
\item Applied secure coding practices, encryption, and OAuth authentication throughout SDLC reducing vulnerabilities and improving maintainability.
\item Led backend development initiatives integrating AI APIs and LLM services while mentoring junior developers on best coding practices.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level web applications using Python frameworks including Flask and Django across frontend and backend layers.
\item Contributed to design and implementation of cloud-based solutions leveraging AWS services and serverless architectures for scalability.
\item Worked closely with cross functional teams to gather requirements, perform integration testing, and support deployment using Git workflows.
\item Gained hands-on experience in containerization with Docker, API development, and secure coding within Agile and Scrum methodologies.
\item Collaborated in project reviews to identify performance improvements, optimize code maintainability, and implement security best practices.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS using Python, React, and AWS enabling 6K+ students to access notes, videos, and interactive quizzes securely.
\vspace{-1pt}
\begin{itemize}
\item Designed full-stack LMS using React, Node.js, Flask, and PostgreSQL to support online education with real-time progress tracking.
\item Integrated secure authentication, role-based access control, and optimized database queries for high concurrent usage and performance.
\item Deployed platform on AWS using Lambda, S3, and RDS with CDN caching and SSL encryption ensuring reliable access for 6,000+ students.
\item Implemented RESTful APIs and WebSocket communication for real-time updates, lesson uploads, quizzes, and performance dashboards.
\end{itemize}

\textbf{Automated Cryptocurrency Trading Bot} -- \emph{Personal Project}

\vspace{-1pt}

Created a Python trading bot using Binance API, FastAPI, and WebSocket for automated trade execution with risk control and monitoring.
\vspace{-1pt}
\begin{itemize}
\item Developed automated trading bot in Python using FastAPI, Binance API, and WebSocket for real-time data streaming and trade execution.
\item Implemented dynamic trading strategies, stop-loss mechanisms, and order execution algorithms using pandas and NumPy for market analysis.
\item Integrated secure API authentication, encryption, and compliance checks to ensure responsible AI and data security throughout operations.
\item Deployed using Docker on AWS EC2 with CloudWatch monitoring for 24/7 uptime, reliability, and detailed logging for performance optimization.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}