% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Motivated Frontend Developer with 2+ years of experience building user-facing features in React that drive engagement and conversions. Proven ability to implement A/B tests, analyze user behavior through data, and iterate rapidly on UI experiments. Experienced in collaborating with cross-functional teams using Agile methodologies while maintaining strong communication and ownership mindset. Passionate about leveraging technology to improve healthcare accessibility.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Frontend Development:} React, JavaScript, TypeScript, HTML5, CSS3, Tailwind CSS

\textbf{State Management \& Data Fetching:} Redux, React Query, React Hook Form, REST API, GraphQL

\textbf{Testing \& Performance:} Unit Testing, A/B Testing, Performance Optimization, Conversion Tracking

\textbf{Data \& Analytics:} SQL, BigQuery, Data Visualization, Chart.js, ETL Pipelines

\textbf{Development Practices:} Agile, Scrum, Git, CI/CD, Code Reviews, Technical Documentation

\textbf{Soft Skills:} Communication, Collaboration, Ownership, Adaptability, Growth Mindset, Curiosity

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed user-facing web applications using React and JavaScript to enhance e-commerce functionality and user engagement.
\item Implemented A/B testing experiments and analyzed user behavior data to optimize conversion funnels and drive key metrics.
\item Built and optimized RESTful APIs with SQL database queries improving system performance and reducing response times.
\item Collaborated within Agile teams through code reviews and sprint planning ensuring high-quality deliverables and knowledge sharing.
\item Deployed cloud-based applications using AWS and CI/CD pipelines maintaining consistent uptime and rapid iteration cycles.
\item Mentored team members on React best practices and modern frontend development patterns to improve code quality standards.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing frontend components for enterprise web applications using modern JavaScript frameworks and libraries.
\item Contributed to implementing user-facing features while gathering requirements from cross-functional teams and stakeholders.
\item Participated in Agile workflows including sprint planning, testing phases, and deployment support to ensure smooth releases.
\item Gained hands-on experience building responsive UI components and integrating with backend APIs for full-stack features.
\item Collaborated in project reviews to identify UI improvements, performance optimizations, and enhanced user experience patterns.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to engage with interactive lessons, quizzes, and real-time progress tracking.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed frontend using React with interactive dashboards for students and teachers to track learning progress.
\item Integrated real-time quiz modules and performance tracking features with role-based access control for different user types.
\item Implemented secure authentication flows and optimized database queries ensuring smooth performance during high traffic periods.
\item Deployed platform on AWS with CDN caching and SSL encryption providing reliable access for over 6,000 concurrent students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic }

\vspace{-1pt}

Developed an inclusive real-time chat application for low-vision users integrating accessibility features and assistive tech.
\vspace{-1pt}
\begin{itemize}
\item Built frontend interface using React and Socket.io with accessibility-focused UI design adhering to WCAG compliance standards.
\item Integrated text-to-speech and voice-to-text features using AWS Polly and Azure Speech Services for inclusive communication.
\item Conducted usability testing with assistive technologies to ensure seamless experience for users with reading challenges.
\item Deployed scalable application on AWS App Runner using Docker containers ensuring low-latency real-time messaging performance.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}