% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with expertise in Identity \& Access Management, Active Directory, and secure authentication systems. Proven ability to develop scalable IAM solutions using Python, JavaScript, and SQL while implementing role-based access control and security frameworks. Experienced in cloud infrastructure (AWS, GCP), automation, and DevOps practices with a strong foundation in vulnerability management, incident response, and compliance. Skilled in collaborating across teams to enhance security posture and streamline access provisioning workflows.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Identity \& Access Management:} IAM Policies, Active Directory, SSO, OAuth, JWT, Role-Based Access Control

\textbf{Programming \& Scripting:} Python, JavaScript, Bash, PowerShell, SQL, Shell Scripting

\textbf{Security \& Compliance:} OWASP, Vulnerability Management, Incident Response, Risk Assessments, Threat Intelligence, SIEM

\textbf{Systems \& Networking:} Windows Server, Linux Administration, Networking Principles, VPN, Cloud Networking

\textbf{Cloud \& Infrastructure:} AWS, GCP, Docker, Kubernetes, CI/CD Pipelines, Infrastructure as Code

\textbf{Database \& Automation:} PostgreSQL, MySQL, MongoDB, Automation, n8n, Jenkins

\textbf{Soft Skills:} Attention to Detail, Communication, Collaboration, Adaptability, Ownership, Problem Solving

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable IAM and authentication solutions using JavaScript, React, and Node.js to enhance secure access control workflows.
\item Implemented OAuth, JWT, and role-based access control systems with RESTful APIs ensuring secure authentication and authorization.
\item Deployed cloud-based IAM applications using AWS, Docker, and CI/CD pipelines maintaining consistent uptime and system availability.
\item Collaborated within Agile teams through code reviews and sprint planning to ensure high-quality security-focused deliverables.
\item Applied secure coding standards and test-driven development throughout SDLC improving maintainability and reducing vulnerabilities.
\item Automated access provisioning workflows with Python and PowerShell scripts reducing manual processing time and improving efficiency.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level IAM and security systems across both frontend and backend components.
\item Contributed to the design and implementation of access management systems with secure authentication and role-based controls.
\item Worked closely with cross functional teams to gather IAM requirements, perform security testing, and support deployment phases.
\item Gained hands-on experience in full stack IAM development, vulnerability assessments, and secure coding within Agile workflows.
\item Collaborated in project reviews to identify security improvements in performance, access control, and compliance requirements.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS with secure authentication, role-based access control, and encrypted data handling for 6K+ students.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full-stack LMS with secure authentication, IAM policies, and role-based access control using React and Node.js.
\item Implemented JWT authentication, user role management, and access provisioning modules for teachers, students, and administrators.
\item Integrated Active Directory concepts and optimized database queries with PostgreSQL for high concurrent user access and performance.
\item Deployed the platform on AWS with SSL encryption, secure API gateways, and monitoring ensuring reliable access for over 6K users.
\end{itemize}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Automated vulnerability scanning and patching workflows to strengthen enterprise security and reduce manual remediation effort.
\vspace{-1pt}
\begin{itemize}
\item Developed automated security workflows using Python and Jenkins for vulnerability scanning, access review, and patch deployment cycles.
\item Integrated Nessus API for real-time vulnerability reporting, risk prioritization, and security compliance tracking across systems.
\item Created dashboards and alert systems to track IAM anomalies, security compliance, and remediation progress in enterprise environments.
\item Reduced manual intervention by 60\% and accelerated patch cycles through full CI/CD automation improving overall security posture.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}