% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Versatile Full Stack Developer with hands-on experience building scalable web applications, data pipelines, and cloud-based solutions using JavaScript, React, Python, and Node.js. Proven ability to deliver user-centered digital products in Agile environments with strong skills in database management, API development, and deployment automation. Experienced collaborating with cross-functional teams to translate requirements into robust technical solutions while maintaining code quality and system reliability.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, SQL, HTML5, CSS3, PHP, Bash, PowerShell

\textbf{Frameworks \& Libraries:} React, Node.js, Django, Flask, Bootstrap, Redux

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQLite, Power BI, ETL Pipelines

\textbf{Cloud \& DevOps:} AWS, Docker, CI/CD, GitHub Actions, Azure, Git

\textbf{Software Development Practices:} Agile, Scrum, REST API, Testing, SDLC, Code Reviews

\textbf{Design \& UX:} UI/UX Design, Web Design, Accessibility Standards, Prototyping, Responsive Design

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Analytical Thinking, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js to enhance functionality and user experience.
\item Implemented RESTful APIs, optimized SQL queries, and integrated secure payment systems improving reliability and data integrity.
\item Deployed cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and operational efficiency.
\item Collaborated within Agile teams through code reviews, sprint planning, and pair programming to deliver high-quality software.
\item Applied test-driven development and secure coding throughout SDLC improving maintainability and reducing production defects.
\item Led backend development for multiple applications while mentoring junior developers on best practices and deployment strategies.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications across frontend and backend components using modern development frameworks.
\item Contributed to design and implementation of management systems supporting business process automation and workflow tracking.
\item Worked closely with cross-functional teams to gather requirements, perform testing, and support deployment and release phases.
\item Gained hands-on experience in full stack development, software testing, and secure coding practices within Agile workflows.
\item Collaborated in project reviews to identify improvements in performance, scalability, code quality, and system maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with notes, videos, quizzes, and real-time progress tracking dashboards.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL to support online education and collaborative learning.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards for instructors and students.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent user activity.
\item Deployed the platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 active learners.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users integrating accessibility features and speech-based communication services.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and Socket.io with accessibility-focused UI and assistive technology.
\item Integrated AWS Polly and Azure Speech Services enabling text-to-speech and voice-to-text communication for inclusive usability.
\item Followed WCAG accessibility standards and tested with screen readers and assistive tools to ensure user-centered design compliance.
\item Deployed on AWS App Runner with Docker containers ensuring scalable, low-latency communication for diverse accessibility needs.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}