% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Full Stack Developer with 2+ years of experience building scalable SaaS applications using modern web technologies including React, Node.js, PHP, and Laravel. Proven ability to deliver enterprise-grade solutions with strong foundations in object-oriented programming, RESTful architecture, and relational databases. Experienced in AWS cloud environments, Docker containerization, and CI/CD pipelines with a security-first mindset. Collaborative team player skilled in Agile workflows, code reviews, and mentoring peers while continuously learning emerging technologies.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, PHP, Python, SQL, HTML5, CSS3

\textbf{Frontend Development:} React, Redux, Bootstrap, Material UI, SASS, Responsive Design

\textbf{Backend Development:} Laravel, Node.js, Django, Flask, RESTful APIs, Microservices

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQL Optimization, Database Design

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, CI/CD Pipelines, GitHub Actions, Infrastructure as Code

\textbf{Development Practices:} Agile, TDD, Object-Oriented Programming, Code Reviews, Design Patterns, SDLC

\textbf{Security \& Integration:} OAuth, JWT, API Security, Third-Party Integration, OWASP, Encryption

\textbf{Soft Skills:} Collaboration, Communication, Mentorship, Problem Solving, Continuous Learning, Adaptability

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js, delivering high-quality customer-facing features.
\item Implemented RESTful APIs and optimized SQL queries on PostgreSQL to improve system performance and reliability for enterprise clients.
\item Deployed cloud-based applications using AWS, Docker, and CI/CD pipelines, ensuring consistent uptime and production stability.
\item Collaborated within Agile teams conducting code reviews, sprint planning, and pair programming to maintain high code quality standards.
\item Applied test-driven development and secure coding practices throughout SDLC, reducing production issues and improving maintainability.
\item Mentored junior developers on best practices for backend development, code quality, and deployment strategies in team collaboration.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level web applications across frontend and backend components using modern technology stacks.
\item Contributed to design and implementation of Proposal Management and Mailroom Tracking Systems for business process automation.
\item Collaborated with cross-functional teams to gather requirements, perform testing, and support deployment phases for production releases.
\item Gained hands-on experience in full stack development, software testing, and secure coding within Agile workflows and sprints.
\item Participated in project reviews to identify improvements in performance, scalability, and code maintainability across team deliverables.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with notes, videos, and interactive quizzes during the pandemic using React and MySQL.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack LMS using React, Node.js, and MySQL to support online education with responsive UI and scalable backend architecture.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards for teachers and administrators.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent user access and performance.
\item Deployed platform on AWS with CDN caching and SSL encryption, ensuring reliable access for over 6,000 students with consistent uptime.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed inclusive real-time chat application for low-vision users integrating accessibility features and third-party speech services.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Node.js, and WebSockets with accessibility-focused UI design following WCAG standards.
\item Integrated AWS and Azure Speech Services to enable text-to-speech and voice-to-text communication for users with reading challenges.
\item Tested application with assistive technologies to ensure inclusive usability and compliance with accessibility best practices.
\item Deployed on AWS using Docker containers for scalable, low-latency communication with secure third-party service integrations.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}