% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Full Stack Software Engineer with 2+ years of professional experience designing and deploying scalable web applications and data-driven solutions. Proficient in TypeScript, Python, SQL, and modern frameworks including React and Node.js. Proven ability to deliver client-facing implementations, gather stakeholder requirements, and build robust backend services and data pipelines. Strong communicator skilled in translating technical concepts for non-technical audiences and collaborating across teams to drive digital transformation initiatives.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} TypeScript, JavaScript, Python, SQL, HTML5, CSS3

\textbf{Frameworks \& Libraries:} React, Node.js, Django, Flask, Express.js, Bootstrap

\textbf{Database \& Data Engineering:} SQL, PostgreSQL, MySQL, MongoDB, ETL Pipelines, Data Warehousing

\textbf{Cloud \& DevOps:} AWS, GCP, Docker, Kubernetes, CI/CD, GitHub Actions

\textbf{Software Development Practices:} Agile, Scrum, Code Reviews, REST API, System Design, Testing

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Client Engagement, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, TypeScript, React, and Node.js to enhance business functionality.
\item Designed and optimized SQL-based data pipelines and RESTful APIs to improve system reliability and backend performance.
\item Deployed cloud-based solutions using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and high availability.
\item Collaborated with stakeholders to gather requirements, present technical solutions, and ensure successful adoption of tools.
\item Applied secure coding standards and test-driven development throughout SDLC improving maintainability and reducing issues.
\item Mentored junior developers on best practices for backend development, deployment workflows, and collaborative problem solving.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications across frontend and backend components using modern tech stacks.
\item Contributed to design and implementation of data-driven systems including Proposal Management and Mailroom Tracking.
\item Worked closely with cross functional teams to gather requirements, perform testing, and support deployment phases.
\item Gained hands-on experience in full stack development, database design, and secure coding within Agile workflows.
\item Participated in code reviews and project discussions to identify improvements in performance and scalability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with notes, videos, and interactive quizzes during the pandemic.
\vspace{-1pt}
\begin{itemize}
\item Designed full-stack LMS using React, Node.js, and MySQL to support online education with real-time progress dashboards.
\item Integrated lesson uploads, quizzes, and performance tracking with optimized SQL queries for high concurrent usage.
\item Implemented secure authentication, role-based access control, and scalable database architecture for user management.
\item Deployed on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 students and teachers.
\end{itemize}

\textbf{Custom Business Web Solutions} -- \emph{Personal Project}

\vspace{-1pt}

Built POS, e-commerce sites, landing pages, and inventory systems with secure, responsive design improving workflow efficiency.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed custom web solutions using React, Next.js, and Express.js tailored to client business needs.
\item Implemented secure authentication, inventory tracking, and payment processing with Stripe API integration.
\item Collaborated directly with clients to gather requirements and translate business goals into scalable applications.
\item Optimized UI performance, responsiveness, and SEO across all projects to enhance user engagement and accessibility.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}