% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Developer with hands-on expertise in backend and frontend technologies including JavaScript, React, Node.js, Python, Django, and PHP. Proven ability to design, develop, and deploy scalable cloud-native applications using Docker, Kubernetes, and AWS in microservices environments. Experienced in event-driven architectures, RESTful APIs, and CI/CD pipelines. Strong advocate for code quality through testing, code reviews, and Agile collaboration. Passionate about solving complex technical challenges and delivering impactful solutions.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, Python, PHP, SQL, HTML, CSS

\textbf{Frameworks \& Libraries:} React, Node.js, Django, Flask, FastAPI, Bootstrap

\textbf{Database \& Data Management:} MySQL, PostgreSQL, MongoDB, Redis, SQL

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, CI/CD, GitHub Actions, Terraform

\textbf{Software Development Practices:} Microservices, REST API, Agile, Scrum, Code Reviews, Testing

\textbf{Architecture \& Design:} Event-Driven Architecture, System Design, Scalability, Design Patterns, OOP

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Ownership, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using JavaScript, React, and Node.js with RESTful APIs for e-commerce platforms.
\item Implemented microservices architecture and optimized SQL queries improving system performance and reducing response latency.
\item Deployed cloud-native applications on AWS using Docker, Kubernetes, and CI/CD pipelines ensuring high availability and reliability.
\item Collaborated in Agile cross-functional teams through code reviews, sprint planning, and pair programming to deliver quality solutions.
\item Applied automated testing and secure coding standards throughout the SDLC reducing production issues and enhancing maintainability.
\item Mentored junior developers on backend development best practices, code quality, and deployment strategies within distributed teams.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications across frontend and backend components using modern development frameworks.
\item Contributed to the design and implementation of Proposal Management and Mailroom Tracking Systems in Agile environments.
\item Worked with cross-functional teams gathering requirements, performing integration testing, and supporting deployment phases.
\item Gained hands-on experience in full stack development, automated testing, and secure coding practices within software projects.
\item Collaborated in project reviews to identify performance improvements, scalability enhancements, and code maintainability optimizations.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with notes, videos, and quizzes deployed on AWS with real-time features.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack LMS using React, Node.js, and MySQL with RESTful APIs supporting online education for pandemic response.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards for teachers and students.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent usage and scalability.
\item Deployed platform on AWS with Docker containers, CDN caching, and SSL encryption ensuring reliable access for 6,000+ students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic }

\vspace{-1pt}

Developed inclusive real-time chat app for low-vision users integrating accessibility features and cloud-based deployment.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Node.js, and WebSockets with accessibility-focused UI design and responsive interface.
\item Integrated AWS Polly and Azure Speech Services enabling text-to-speech and voice-to-text communication for inclusive user experience.
\item Followed WCAG accessibility standards and tested with assistive technologies ensuring compliance and usability for diverse users.
\item Deployed on AWS with Docker containers and Kubernetes for scalable, low-latency communication and high availability in production.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}