% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Full Stack Developer with hands-on experience building scalable web applications using JavaScript, React, Node.js, Python, and Django. Proven ability to deliver impactful features across frontend and backend systems, with expertise in cloud deployment on AWS, CI/CD automation, and Agile workflows. Passionate about creating user-focused solutions and eager to contribute to experimentation and personalization initiatives in modern e-commerce and marketing platforms.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, PHP, SQL, HTML5, CSS3

\textbf{Frontend Development:} React, Redux, Bootstrap, Material UI, SASS, Responsive Design

\textbf{Backend Development:} Node.js, Express.js, Django, Flask, FastAPI, REST API

\textbf{Database \& Cloud:} PostgreSQL, MySQL, MongoDB, AWS, AWS Lambda, AWS S3

\textbf{DevOps \& Tools:} Docker, CI/CD, GitHub Actions, Git, Agile, Scrum

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Continuous Learning, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js to deliver enhanced e-commerce features.
\item Implemented RESTful APIs and optimized SQL queries to improve system performance and ensure reliable data processing workflows.
\item Deployed cloud-based applications on AWS using Docker and CI/CD pipelines to maintain consistent uptime and system availability.
\item Collaborated with Agile teams through code reviews, sprint planning, and pair programming to deliver high-quality solutions.
\item Applied test-driven development and secure coding practices across SDLC to reduce production issues and improve maintainability.
\item Led backend development for multiple Shopify applications while mentoring junior developers on best practices and deployments.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web and mobile applications across frontend and backend components using modern frameworks.
\item Contributed to the design and implementation of Proposal Management and Mailroom Tracking Systems with scalable architecture.
\item Worked closely with cross functional teams to gather requirements, perform testing, and support deployment and release phases.
\item Gained hands-on experience in full stack development, software testing, and secure coding within Agile development workflows.
\item Collaborated in project reviews to identify improvements in performance, scalability, and long-term code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL to support online education for thousands of students.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards for educators and learners.
\item Implemented secure authentication, role-based access, and optimized database queries for high concurrent user traffic.
\item Deployed platform on AWS with CDN caching and SSL encryption, ensuring reliable access for over 6,000 active students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users integrating text-to-speech and accessibility-focused UI design.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and Socket.io with accessibility-first interface and navigation.
\item Integrated AWS Polly and Azure Speech Services to enable seamless text-to-speech and voice-to-text communication features.
\item Followed WCAG accessibility standards and tested with assistive technologies to ensure inclusive and usable experience.
\item Deployed on AWS App Runner using Docker containers for scalable, low-latency communication and reliable uptime.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}