% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Developer with 3+ years building scalable web and mobile applications using JavaScript, React, and Node.js. Experienced in developing frontend and backend solutions, integrating REST APIs, and deploying cloud-based systems on AWS. Skilled in Agile Scrum environments, CI/CD automation, and database design using MySQL and PostgreSQL. Proven ability to collaborate with cross-functional teams, optimize application performance, and deliver high-quality, testable code aligned with business objectives.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, SQL, HTML5, CSS3

\textbf{Frontend Development:} React, Angular, Redux, Bootstrap, Material UI, Responsive Design

\textbf{Backend Development:} Node.js, Express.js, REST API, Django, Flask, Microservices

\textbf{Databases:} MySQL, PostgreSQL, MongoDB, SQLite, DynamoDB, Firebase

\textbf{Cloud \& DevOps:} AWS, Azure, Docker, CI/CD, GitHub Actions, Terraform

\textbf{Testing \& Debugging:} Unit Testing, Integration Testing, Postman, TDD, Automation Testing

\textbf{Development Practices:} Agile, Scrum, Code Reviews, System Design, Technical Documentation

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Ownership, Time Management

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js enhancing e-commerce functionality and user experience.
\item Built backend services and RESTful APIs with optimized SQL queries and secure payment integrations improving system reliability and performance.
\item Deployed and maintained cloud-based applications on AWS using Docker and CI/CD pipelines ensuring consistent uptime and availability.
\item Collaborated within Agile Scrum teams through sprint planning, code reviews, and pair programming delivering high-quality software solutions.
\item Applied test-driven development and debugging processes throughout SDLC improving code maintainability and reducing production issues.
\item Led backend development for multiple applications while mentoring junior developers on best practices for scalable and testable code.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web and mobile applications across frontend and backend components using modern frameworks and tools.
\item Contributed to design and implementation of Proposal Management and Mailroom Tracking Systems with responsive user interfaces.
\item Collaborated with cross-functional teams to gather requirements, perform integration testing, and support deployment phases.
\item Gained hands-on experience in full stack development, automated testing, and secure coding practices within Agile Scrum workflows.
\item Participated in project reviews identifying improvements in performance, scalability, and code maintainability across multiple applications.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes using modern web technologies.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL supporting online education with scalable architecture and responsive design.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards for teachers and students.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent usage and data integrity.
\item Deployed the platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 students and continuous uptime.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic }

\vspace{-1pt}

Developed an inclusive real-time chat app for low-vision users integrating accessibility features and cloud-based speech services.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and WebSocket technology with accessibility-focused UI design and responsive layout.
\item Integrated AWS and Azure Speech Services to enable text-to-speech and voice-to-text communication for users with reading challenges.
\item Followed WCAG accessibility standards and tested with assistive technologies ensuring inclusive usability and compliance with best practices.
\item Deployed on AWS with Docker containers for scalable, low-latency communication and continuous availability across multiple devices.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}