% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with expertise in full stack development, cloud infrastructure, and cybersecurity. Proven experience in digital forensics, incident response, and security automation using Python, JavaScript, and cloud platforms. Skilled in vulnerability assessment, threat intelligence, malware analysis, and phishing investigation. Adept at collaborating with cross-functional teams and law enforcement to support investigations while maintaining compliance with regulatory standards and security best practices.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming \& Scripting:} Python, JavaScript, SQL, Bash, PowerShell, PHP

\textbf{Digital Forensics \& Cybersecurity:} Digital Forensics, Incident Response, Malware Analysis, Phishing Investigation, Threat Intelligence, SIEM

\textbf{Security Tools \& Frameworks:} MITRE ATT\&CK, Threat Hunting, Vulnerability Management, Risk Assessments, OWASP, Sandbox Analysis

\textbf{Cloud \& Infrastructure:} AWS, Google Cloud Platform, Docker, Kubernetes, CI/CD, Infrastructure as Code

\textbf{Database \& Data Analysis:} PostgreSQL, MySQL, MongoDB, SQL Server, Pandas, ETL Pipelines

\textbf{Systems \& Networking:} Linux, Windows Server, Active Directory, VPN, Networking Principles, Security Best Practices

\textbf{Soft Skills:} Communication, Analytical Thinking, Collaboration, Adaptability, Problem Solving, Documentation

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed secure full stack web applications using JavaScript, React, and Node.js with focus on data protection and secure coding.
\item Implemented RESTful APIs with encryption, OAuth, and JWT authentication ensuring compliance with security standards and regulations.
\item Deployed cloud-based applications on AWS with monitoring, logging, and security controls ensuring high availability and incident response.
\item Collaborated with Agile teams conducting code reviews, security assessments, and sprint planning to deliver secure high-quality solutions.
\item Applied test-driven development and OWASP security principles throughout SDLC reducing vulnerabilities and improving system resilience.
\item Mentored junior developers on secure coding practices, threat mitigation strategies, and incident response procedures for production systems.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications with security controls and data protection measures across frontend and backend layers.
\item Contributed to the design and implementation of Proposal Management and Mailroom Tracking Systems with audit logging and access controls.
\item Collaborated with cross-functional teams to gather security requirements, perform testing, and support secure deployment phases.
\item Gained hands-on experience in full stack development, vulnerability testing, and secure coding within Agile workflows and sprints.
\item Participated in project reviews to identify security improvements, performance optimization, and code maintainability enhancements.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic }

\vspace{-1pt}

Automated vulnerability scanning and patching workflows to strengthen enterprise security posture and reduce manual remediation effort.
\vspace{-1pt}
\begin{itemize}
\item Developed automated security workflows using Python and Jenkins for continuous vulnerability scanning and patch deployment cycles.
\item Integrated Nessus API for real-time vulnerability reporting, risk prioritization, and compliance tracking across enterprise systems.
\item Created security dashboards and alert systems to track remediation progress, compliance metrics, and incident response activities.
\item Reduced manual intervention by 60\% and accelerated patch cycles through full CI/CD automation improving overall security posture.
\end{itemize}

\textbf{Automated Cryptocurrency Trading Bot} -- \emph{Personal Project}

\vspace{-1pt}

Created a Python trading bot using Binance API and WebSocket for automated trade execution with risk controls and live monitoring systems.
\vspace{-1pt}
\begin{itemize}
\item Developed a fully automated trading bot in Python using Binance API and WebSocket for real-time data streaming and market analysis.
\item Implemented dynamic trading strategies, stop-loss mechanisms, and secure order execution algorithms with logging and audit trails.
\item Integrated Pandas and NumPy for market analysis, backtesting, and pattern detection to improve trading accuracy and risk management.
\item Deployed using Docker on AWS EC2 for 24/7 uptime, reliability, and monitoring with detailed logging for incident analysis and review.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}