% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with 2+ years of experience developing scalable web applications using JavaScript, HTML, CSS, and SQL. Skilled in full stack development with Python, React, and Node.js, delivering production-ready tools and process automation solutions. Experienced in Agile methodologies, Jira, code reviews, and collaborative development. Proven ability to debug, test, and document code while maintaining high coding standards. Strong background in database design, cloud deployment, and working with cross-functional teams to improve operational efficiency.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming \& Markup:} JavaScript, Python, SQL, HTML5, CSS3, PHP, TypeScript

\textbf{Frameworks \& Libraries:} React, Node.js, Django, Bootstrap, jQuery, Redux

\textbf{Database \& Tools:} MySQL, PostgreSQL, MongoDB, MS Excel, MS Access, SQLite

\textbf{Cloud \& DevOps:} AWS, Docker, CI/CD, GitHub Actions, GitLab CI/CD

\textbf{Development Practices:} Agile, Scrum, Jira, Code Reviews, Testing, Debugging

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Stakeholder Management

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable web applications using JavaScript, HTML, CSS, and React to enhance functionality and user experience.
\item Implemented RESTful APIs and optimized SQL queries to improve system reliability, data integrity, and performance.
\item Deployed cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and availability.
\item Collaborated within Agile teams using Jira, participated in code reviews and sprint planning to deliver quality solutions.
\item Applied testing, debugging, and secure coding standards throughout SDLC improving maintainability and reducing issues.
\item Led backend development for multiple applications while mentoring junior developers on best practices and deployment.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications using JavaScript, HTML, CSS, and SQL for frontend and backend components.
\item Contributed to design, coding, and implementation of internal management systems with process improvement focus.
\item Worked with cross-functional teams to gather requirements, perform testing, and support deployment phases effectively.
\item Gained experience in full stack development, testing, debugging, and secure coding within Agile workflows and Jira.
\item Participated in code reviews to identify improvements in performance, scalability, and maintainability of solutions.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS using JavaScript, HTML, CSS, and SQL enabling 6K+ students to learn with interactive quizzes and dashboards.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full-stack LMS using React, Node.js, and MySQL to support online education during the pandemic.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards for instructors.
\item Implemented secure authentication, role-based access, and optimized SQL queries for high concurrent user traffic.
\item Deployed the platform on AWS with SSL encryption ensuring reliable access for over 6,000 students and educators.
\end{itemize}

\textbf{Custom Business Web Solutions} -- \emph{Personal Project}

\vspace{-1pt}

Built POS, e-commerce sites, and inventory systems using HTML, CSS, JavaScript, and SQL improving workflow and efficiency.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed multiple custom web solutions using JavaScript, React, HTML, CSS, and backend APIs for clients.
\item Implemented secure authentication, inventory tracking, and payment processing with integrated third-party services.
\item Collaborated with clients to gather requirements and translate business needs into scalable web applications.
\item Optimized UI performance, responsiveness, and database queries to enhance user engagement and operational efficiency.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}