% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Detail-oriented IT professional with a strong foundation in technical support, system administration, and troubleshooting across diverse computing environments. Experienced in managing user accounts, resolving hardware and software issues, and supporting cloud-based infrastructure using AWS and DevOps tools. Skilled in deploying IT equipment, maintaining documentation, and providing exceptional customer service to users with varying technical expertise. Proficient in Windows, Linux, Active Directory, and modern collaboration platforms.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Operating Systems \& Administration:} Windows OS, Linux, Ubuntu, Windows Server, Active Directory, PowerShell

\textbf{Hardware \& Mobile Support:} Hardware troubleshooting, Mobile device management, Networking principles, VPN, Deployment

\textbf{Cloud \& Infrastructure:} AWS, Docker, CI/CD, Cloud Monitoring, Backup Strategies, High Availability

\textbf{Database \& Productivity Tools:} SQL, MySQL, PostgreSQL, Microsoft Office, Excel, Microsoft 365, Microsoft Teams

\textbf{Security \& Compliance:} Incident Response, OWASP, IAM, Vulnerability management, Security best practices

\textbf{Development \& Scripting:} Python, Bash, PowerShell, JavaScript, Automation, Technical Documentation

\textbf{Soft Skills:} Communication, Problem solving, Collaboration, Adaptability, Time Management, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed full stack web applications using JavaScript, React, and Node.js to enhance functionality and user experience.
\item Troubleshot and resolved software issues, optimized SQL queries, and integrated secure systems to improve reliability.
\item Deployed cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and availability.
\item Collaborated with cross functional teams through Agile practices including sprint planning and code reviews for quality.
\item Applied secure coding standards and conducted testing throughout SDLC to improve maintainability and reduce production issues.
\item Mentored team members on best practices for deployment, troubleshooting, and technical documentation to ensure consistency.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web and mobile applications across both frontend and backend components.
\item Contributed to design, implementation, and testing of tracking systems supporting internal business operations.
\item Worked with cross functional teams to gather requirements, perform testing, and support deployment phases effectively.
\item Gained hands-on experience in troubleshooting, software testing, and secure coding within Agile development workflows.
\item Collaborated in project reviews to identify improvements in performance, scalability, and overall code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with notes, videos, and interactive quizzes during the pandemic.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed full-stack LMS using React, Node.js, and MySQL to support online education during the pandemic.
\item Integrated secure authentication, role-based access controls, and optimized database queries for high concurrent usage.
\item Deployed platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 active students.
\item Created technical documentation and support guides to assist instructors and administrators in using the platform effectively.
\end{itemize}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic }

\vspace{-1pt}

Automated vulnerability scanning and patching to strengthen enterprise security and reduce manual operational effort.
\vspace{-1pt}
\begin{itemize}
\item Developed automated workflows using Python and Jenkins for vulnerability scanning and patch deployment across systems.
\item Integrated Nessus API for real-time vulnerability reporting, risk prioritization, and compliance tracking dashboards.
\item Created alert systems to track security compliance and remediation progress reducing manual intervention by 60 percent.
\item Deployed solution with Docker and CI/CD automation accelerating patch cycles and improving overall security posture.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}