% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Web Developer with expertise in JavaScript, React, Node.js, and modern web technologies. Experienced in building scalable web applications, implementing RESTful APIs, and deploying cloud-based solutions using AWS and Docker. Strong background in teaching complex technical concepts through documentation and mentorship. Skilled in breaking down asynchronous programming patterns, DOM manipulation, and component-based architecture while emphasizing practical problem-solving approaches.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, PHP, SQL, HTML5, CSS3

\textbf{JavaScript Ecosystem:} React, Node.js, Redux, Express.js, ES6+, DOM Manipulation

\textbf{Frontend Technologies:} React, Bootstrap, Material UI, Responsive Design, SASS

\textbf{Backend \& APIs:} Node.js, Express.js, REST API, Django, Flask, FastAPI

\textbf{Database \& Cloud:} PostgreSQL, MySQL, MongoDB, AWS, Docker, CI/CD

\textbf{Development Practices:} Agile, Code Reviews, Testing, Debugging, Technical Documentation

\textbf{Soft Skills:} Communication, Adaptability, Mentorship, Problem Solving, Collaboration, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js enhancing functionality and user experience.
\item Built RESTful APIs with Express.js and optimized SQL queries improving system reliability, performance, and response times.
\item Deployed cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and reliable availability.
\item Collaborated within Agile teams through code reviews, sprint planning, and pair programming to deliver high-quality solutions.
\item Applied test-driven development practices and debugging techniques throughout SDLC reducing production issues significantly.
\item Mentored junior developers on JavaScript best practices, asynchronous programming patterns, and secure coding standards.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications across frontend and backend components using JavaScript and React frameworks.
\item Contributed to design and implementation of multiple systems applying object-oriented programming and design patterns effectively.
\item Worked with cross functional teams to gather requirements, perform testing, and support deployment phases within Agile workflows.
\item Gained hands-on experience in full stack development, debugging browser console errors, and implementing secure authentication.
\item Collaborated in project reviews to identify improvements in performance, scalability, and code maintainability across applications.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with interactive lessons, real-time quizzes, and performance tracking dashboards.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack LMS using React, Node.js, and MySQL supporting online education with interactive lesson modules and quizzes.
\item Integrated real-time progress dashboards for teachers using WebSocket and implemented role-based access control for secure usage.
\item Optimized database queries and implemented caching strategies to handle high concurrent usage and improve system performance.
\item Deployed platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 students and educators.
\end{itemize}

\textbf{PROSPR " Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed inclusive real-time chat app for low-vision users integrating text-to-speech, voice-to-text, and accessibility features.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Node.js, and Socket.io with accessibility-focused UI following WCAG standards.
\item Integrated AWS Polly and Azure Speech Services to enable seamless text-to-speech and voice-to-text communication features.
\item Implemented event handling and asynchronous programming patterns using async/await for smooth real-time message streaming.
\item Deployed on AWS App Runner using Docker containers for scalable, low-latency communication and consistent user experience.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}