% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Detail-oriented JavaScript Developer with hands-on experience building scalable full stack web applications using modern JavaScript frameworks and backend technologies. Proficient in React, Node.js, TypeScript, and REST API development with proven ability to deliver responsive, user-focused solutions. Experienced in cloud deployment, CI/CD automation, and Agile collaboration. Passionate about continuous learning and leveraging cutting-edge tools to create exceptional digital experiences.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, HTML5, CSS3, SQL

\textbf{Frameworks \& Libraries:} React, Next.js, Node.js, Express.js, Redux, Bootstrap

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, Firebase

\textbf{Cloud \& DevOps:} AWS, Docker, CI/CD, GitHub Actions, GitLab CI/CD

\textbf{Software Development Practices:} Agile, Scrum, REST API, Git, Code Reviews, Testing

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, TypeScript, React, and Node.js enhancing user experiences.
\item Built and maintained RESTful APIs with Express.js optimizing backend performance and ensuring seamless frontend integration.
\item Deployed cloud-based applications using AWS and Docker with CI/CD pipelines ensuring high availability and consistent uptime.
\item Collaborated within Agile teams through code reviews, sprint planning, and version control with Git to deliver quality code.
\item Implemented responsive UI components using React and modern CSS frameworks improving application accessibility and design.
\item Applied test-driven development and secure coding practices throughout SDLC reducing production issues and technical debt.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications using JavaScript frameworks across frontend and backend components.
\item Contributed to design and implementation of scalable systems collaborating with cross functional teams for deployment.
\item Gained hands-on experience in full stack development, API integration, and version control within Agile workflows.
\item Worked closely with developers to gather requirements, perform testing, and support continuous integration processes.
\item Participated in project reviews identifying improvements in performance, scalability, and code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS using React, Node.js, and MySQL enabling 6K+ students to access lessons, quizzes, and real-time tracking.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack LMS using React and Node.js with Express.js backend supporting concurrent users and real-time dashboards.
\item Integrated secure authentication with JWT, role-based access control, and optimized database queries for high performance.
\item Implemented interactive modules for lesson uploads, quizzes, and student progress tracking with REST API architecture.
\item Deployed platform on AWS with SSL encryption and CDN caching ensuring reliable access for over 6,000 students nationwide.
\end{itemize}

\textbf{Custom Business Web Solutions} -- \emph{Personal Project}

\vspace{-1pt}

Built responsive e-commerce sites, landing pages, and inventory systems using React, Next.js, and Express.js with secure design.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed custom web solutions using React, Next.js, and Express.js tailored to client business requirements.
\item Implemented secure authentication, payment processing with Stripe API, and inventory tracking for e-commerce functionality.
\item Collaborated with clients to gather requirements and translate business needs into scalable, user-friendly applications.
\item Optimized UI performance, responsiveness, and SEO across projects using modern JavaScript frameworks and best practices.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}