% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Developer with 3+ years of experience translating business requirements into scalable web applications across Agile environments. Proven expertise in JavaScript, Python, SQL, and cloud technologies with strong capabilities in data analysis, system integration, and stakeholder collaboration. Skilled in gathering and analyzing complex requirements, optimizing workflows, and delivering technical solutions aligned with business objectives.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, SQL, PHP, HTML5, CSS3, Bash, PowerShell

\textbf{Frameworks \& Libraries:} React, Django, Node.js, Flask, Bootstrap, Material UI

\textbf{Database \& Data Management:} SQL, PostgreSQL, MySQL, MongoDB, Data Analysis, BigQuery

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, GitHub Actions, CI/CD, Infrastructure as Code

\textbf{Project Management \& Collaboration Tools:} Jira, Confluence, Agile, Scrum, Microsoft Office Suite, Technical Documentation

\textbf{APIs \& System Integration:} REST API, GraphQL, API Gateway, OAuth, JWT, Microservices

\textbf{Software Development Practices:} Requirements Analysis, SDLC, Testing, Architecture Design, Data-Driven Decision Making

\textbf{Soft Skills:} Stakeholder Management, Cross-Functional Collaboration, Communication, Adaptability, Critical Thinking, Process Improvement

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Gathered and analyzed business requirements within Agile teams to develop scalable e-commerce web applications using JavaScript and React.
\item Designed and implemented RESTful APIs and GraphQL endpoints while optimizing SQL queries to improve system performance and reliability.
\item Collaborated with cross-functional stakeholders through sprint planning and code reviews to align technical solutions with business objectives.
\item Deployed cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and operational excellence.
\item Translated complex business needs into technical specifications and documentation supporting change management and process improvement.
\item Led backend development initiatives while mentoring junior developers on best practices in Agile methodologies and system integrations.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in gathering and analyzing business requirements for enterprise web and mobile applications across frontend and backend systems.
\item Contributed to the design and implementation of Proposal Management and Mailroom Tracking Systems aligned with stakeholder needs.
\item Worked closely with cross-functional teams to perform SQL-based data analysis, testing, and deployment phases within Agile workflows.
\item Gained hands-on experience in translating business requirements into technical solutions supporting process redesign initiatives.
\item Collaborated in project reviews using Jira and Confluence to identify improvements in performance, scalability, and data-driven decision making.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to access lessons, quizzes, and performance tracking with real-time dashboards.
\vspace{-1pt}
\begin{itemize}
\item Gathered and analyzed educational requirements to design a full-stack LMS using React, Node.js, and MySQL supporting online learning.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with data visualization dashboards for real-time insights.
\item Implemented secure authentication, role-based access, and optimized SQL queries for high concurrent usage and operational excellence.
\item Deployed the platform on AWS with CDN caching and SSL encryption ensuring reliable access and system integration for 6,000+ students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat application for low-vision users integrating accessibility features and API-based voice services.
\vspace{-1pt}
\begin{itemize}
\item Analyzed user requirements and built a real-time chat application using React, Node.js, and WebSocket with accessibility-focused design.
\item Integrated AWS Polly and Azure Speech Services APIs to enable text-to-speech and voice-to-text communication for diverse user needs.
\item Followed WCAG accessibility standards and tested with assistive technologies ensuring inclusive usability and stakeholder satisfaction.
\item Deployed on AWS App Runner with Docker containers for scalable, low-latency communication and operational excellence.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}