% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with expertise in Python, SQL, and full stack development, transitioning into data engineering. Hands-on experience building scalable cloud-based systems on AWS and GCP, implementing ETL pipelines, and working with databases including PostgreSQL, MySQL, and MongoDB. Proficient in object-oriented programming, containerization with Docker, and CI/CD automation. Strong foundation in data visualization, API development, and Agile methodologies with proven ability to deliver impactful solutions.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming \& Scripting:} Python, SQL, JavaScript, Bash, PowerShell, PHP

\textbf{Big Data \& Cloud Technologies:} AWS, GCP, MongoDB, Docker, PostgreSQL, MySQL

\textbf{Data Engineering \& Analytics:} ETL Pipelines, Data Warehousing, Power BI, BigQuery, pandas

\textbf{Frameworks \& Tools:} Django, Flask, FastAPI, React, Node.js, Jenkins

\textbf{Object-Oriented Programming \& Design:} OOP Principles, Design Patterns, Clean Architecture, MVC

\textbf{DevOps \& Infrastructure:} CI/CD, Kubernetes, GitHub Actions, GitLab CI/CD, Terraform

\textbf{Security \& Compliance:} Data Security Best Practices, Encryption, IAM, OWASP, OAuth, JWT

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using Python, JavaScript, and React, integrating RESTful APIs and optimizing SQL queries.
\item Deployed cloud-based applications on AWS with Docker and CI/CD pipelines, ensuring high availability and consistent system uptime.
\item Implemented ETL workflows and data processing pipelines to support analytics and reporting across e-commerce platforms.
\item Collaborated within Agile teams through code reviews and sprint planning, applying object-oriented programming principles throughout.
\item Applied test-driven development and secure coding standards across the SDLC, improving maintainability and reducing production issues.
\item Mentored junior developers on best practices for backend development, database design, and deployment strategies.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web and mobile applications using Python, SQL, and object-oriented programming principles.
\item Contributed to the design and implementation of data management systems including Proposal Management and Mailroom Tracking Systems.
\item Worked with cross functional teams to gather requirements, perform testing, and support deployment phases using Agile workflows.
\item Gained hands-on experience in database administration, secure coding, and software testing within full stack development projects.
\item Collaborated in project reviews to identify improvements in performance, scalability, and data processing efficiency.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with notes, videos, and interactive quizzes using Python and cloud services.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using Python, React, Node.js, and MySQL to support online education during the pandemic.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards using SQL and RESTful APIs.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent user loads.
\item Deployed the platform on AWS with Docker containerization and SSL encryption, ensuring reliable access for over 6,000 students.
\end{itemize}

\textbf{Automated Cryptocurrency Trading Bot} -- \emph{Personal Project}

\vspace{-1pt}

Created a Python trading bot using Binance API and WebSocket to automate trade execution with risk control and live monitoring.
\vspace{-1pt}
\begin{itemize}
\item Developed an automated trading bot in Python using object-oriented programming, Binance API, and WebSocket for real-time data.
\item Implemented dynamic trading strategies, stop-loss mechanisms, and order execution algorithms with pandas and NumPy for analysis.
\item Integrated data visualization dashboards to monitor trading performance, profitability, and risk metrics in real time.
\item Deployed using Docker on AWS EC2 for continuous uptime, reliability, and monitoring with detailed logging and alerting systems.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}