% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with experience in full stack development, cloud architecture, and data-driven solutions using Python, SQL, and modern frameworks. Proven ability to design and deploy scalable applications leveraging AWS, Docker, and CI/CD pipelines. Strong foundation in database management, API development, and automation with hands-on experience in machine learning integrations and ETL workflows. Eager to apply technical expertise in data science consulting roles.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, SQL, JavaScript, Bash, PowerShell

\textbf{Data \& Analytics:} pandas, ETL Pipelines, Data Warehousing, BigQuery, PostgreSQL, MySQL

\textbf{Cloud \& DevOps:} AWS, AWS Lambda, AWS S3, AWS EC2, Docker, GitLab

\textbf{Frameworks \& Tools:} Django, Flask, FastAPI, Node.js, React

\textbf{Machine Learning \& AI:} Machine Learning APIs, AI Integration, LLM API, Prompt Engineering

\textbf{Software Development:} Agile, CI/CD, REST API, Testing, Version Control

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Problem Solving, Analytical Thinking

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using Python, JavaScript, and React with integrated SQL databases and cloud deployments.
\item Built and optimized RESTful APIs, implemented secure authentication, and improved database query performance for high-traffic systems.
\item Deployed cloud-based solutions on AWS using Docker, Lambda, S3, and CI/CD pipelines ensuring consistent uptime and scalability.
\item Collaborated in Agile teams performing code reviews, sprint planning, and technical documentation for cross-functional delivery.
\item Applied secure coding standards, unit testing, and version control throughout SDLC reducing production bugs and technical debt.
\item Mentored team members on backend development, data pipeline design, automation workflows, and cloud infrastructure best practices.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise applications using Python, SQL, and frontend frameworks across multiple project lifecycles.
\item Contributed to design and implementation of data management systems with integrated tracking, reporting, and analytics features.
\item Worked closely with cross-functional teams to gather requirements, perform testing, and support deployment in Agile workflows.
\item Gained hands-on experience in full stack development, database design, cloud services, and secure coding within structured teams.
\item Participated in code reviews and project retrospectives to identify improvements in performance, scalability, and maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Automated Cryptocurrency Trading Bot} -- \emph{Personal Project}

\vspace{-1pt}

Built an automated Python trading bot using Binance API and real-time data streaming with integrated risk control mechanisms.
\vspace{-1pt}
\begin{itemize}
\item Developed Python-based trading bot leveraging Binance API and WebSocket for real-time market data streaming and trade execution.
\item Implemented machine learning-driven strategies, stop-loss algorithms, and automated order management for dynamic risk control.
\item Utilized pandas and NumPy for data analysis, backtesting, and performance optimization to improve trading decision accuracy.
\item Deployed bot on AWS EC2 with Docker ensuring 24/7 uptime, monitoring, detailed logging, and automated alert notifications.
\end{itemize}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Designed a scalable LMS serving 6K+ students with integrated content delivery, quizzes, and real-time progress tracking.
\vspace{-1pt}
\begin{itemize}
\item Built full stack LMS using Python, React, and SQL with modules for lesson uploads, quizzes, and real-time progress dashboards.
\item Implemented secure authentication, role-based access controls, and optimized SQL queries to handle high concurrent user traffic.
\item Deployed platform on AWS with S3 storage, CDN caching, SSL encryption, and automated backups for reliable student access.
\item Integrated analytics dashboards for educators to monitor student performance, engagement metrics, and course completion rates.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}