% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Frontend Developer with hands-on experience building responsive, accessible web applications using React, JavaScript, and TypeScript. Proven track record in developing WCAG-compliant interfaces, optimizing performance, and collaborating within Agile teams. Skilled in translating technical requirements into user-focused solutions while adhering to coding standards and best practices. Experienced with CI/CD pipelines, cloud deployment, and cross-functional collaboration to deliver high-quality enterprise applications.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Frontend Technologies:} JavaScript, TypeScript, React, Next.js, HTML5, CSS3

\textbf{UI Frameworks \& Styling:} Bootstrap, Material UI, Redux, React Query, Responsive Design

\textbf{Backend \& APIs:} Node.js, REST API, Express.js, GraphQL, WebSockets

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQL, Firebase

\textbf{Cloud \& DevOps:} Azure DevOps, Git, GitHub, CI/CD Pipelines, Docker, AWS

\textbf{Development Practices:} Agile, Scrum, Unit Testing, TDD, Code Reviews, Debugging

\textbf{Accessibility \& Standards:} WCAG 2.0, AODA, ARIA, Semantic HTML, Screen Reader Compatibility

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Time Management, Analytical Thinking

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed responsive full stack applications using JavaScript, React, and Node.js to enhance e-commerce functionality and user experience.
\item Implemented RESTful APIs, optimized database queries, and integrated secure payment systems improving reliability and performance.
\item Deployed cloud-based applications with AWS, Docker, and CI/CD pipelines ensuring consistent uptime and high availability.
\item Collaborated within Agile teams conducting code reviews, sprint planning, and pair programming to deliver quality solutions.
\item Applied test-driven development and secure coding standards throughout SDLC reducing production issues and enhancing maintainability.
\item Led backend development for Shopify applications while mentoring junior developers on best practices and deployment strategies.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web and mobile applications across frontend and backend components using modern frameworks.
\item Contributed to design and implementation of Proposal Management and Mailroom Tracking Systems with accessible UI components.
\item Collaborated with cross-functional teams to gather requirements, perform testing, and support deployment phases effectively.
\item Gained hands-on experience in full stack development, software testing, and secure coding practices within Agile workflows.
\item Participated in project reviews identifying improvements in performance, scalability, and code maintainability across applications.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive real-time chat app for low-vision users integrating accessibility features and assistive technologies.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Node.js, and Socket.io with accessibility-focused UI design and semantic HTML.
\item Integrated AWS Polly and Azure Speech Services enabling text-to-speech and voice-to-text for enhanced inclusive communication.
\item Followed WCAG 2.0 accessibility standards and tested with assistive technologies including screen readers ensuring full compliance.
\item Deployed on AWS App Runner with Docker containers for scalable, low-latency communication and consistent high availability.
\end{itemize}

\textbf{Custom Business Web Solutions} -- \emph{Personal Project}

\vspace{-1pt}

Built POS, e-commerce, and inventory systems with secure responsive design improving workflow efficiency for clients.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed custom web solutions using React, Next.js, and Express.js translating business needs into applications.
\item Implemented secure authentication, inventory tracking, and payment processing with Stripe API integration ensuring data security.
\item Collaborated with clients gathering requirements and delivering user-friendly interfaces aligned with business objectives.
\item Optimized UI performance, responsiveness, and SEO across projects enhancing user engagement and accessibility compliance.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}