% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Detail-oriented Junior Cybersecurity Analyst with hands-on experience in software development, cloud security, and system administration. Proficient in vulnerability management, incident response, and secure coding practices with strong knowledge of AWS, Docker, and CI/CD pipelines. Experienced in implementing security controls, authentication systems, and monitoring solutions. Skilled in Python scripting, networking fundamentals, and Agile collaboration with proven ability to investigate security issues, document findings, and support compliance initiatives.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cybersecurity \& Incident Response:} Vulnerability Management, Incident Response, Threat Intelligence, MITRE ATT\&CK, Phishing Investigation, Malware Analysis

\textbf{Security Tools \& Monitoring:} SIEM, OWASP, Risk Assessments, Vulnerability Management Tools, Threat Hunting, Digital Forensics

\textbf{Cloud Security \& Infrastructure:} AWS IAM, Encryption, VPN, Docker, Zero Trust Architecture, Cloud Monitoring

\textbf{Identity \& Access Management:} Active Directory, Microsoft 365, OAuth, JWT, SSO, IAM Policies

\textbf{Systems \& Networking:} Windows Server, Linux, PowerShell, Bash, Networking Principles, Hardware Troubleshooting

\textbf{Programming \& Scripting:} Python, SQL, PowerShell, Bash, REST API, Automation

\textbf{Compliance \& Documentation:} Technical Documentation, OWASP Standards, Security Best Practices, Compliance Evidence Collection

\textbf{Soft Skills:} Communication, Problem Solving, Attention to Detail, Team Collaboration, Adaptability, Confidentiality

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Implemented secure authentication systems, OAuth, JWT, and encryption protocols reducing security vulnerabilities across production applications.
\item Deployed cloud infrastructure on AWS using Docker and CI/CD pipelines ensuring secure configuration and consistent application uptime.
\item Applied secure coding standards and conducted code reviews identifying and remediating SQL injection and XSS vulnerabilities in production systems.
\item Monitored application logs and performance metrics using CloudWatch detecting anomalies and supporting incident response activities.
\item Collaborated with cross functional teams documenting security requirements and ensuring compliance with industry best practices.
\item Optimized SQL queries and database security controls improving data integrity and access management for enterprise applications.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in implementing security controls and access management features for enterprise web and mobile applications.
\item Supported vulnerability assessments and remediation efforts during software testing and deployment phases.
\item Documented security requirements, system configurations, and incident logs for compliance and audit preparation.
\item Collaborated with teams to gather requirements, perform testing, and ensure secure coding practices throughout SDLC.
\item Gained experience in secure application development, authentication mechanisms, and Agile security workflows.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic }

\vspace{-1pt}

Automated vulnerability scanning and patching workflows to strengthen enterprise security posture and reduce manual remediation efforts.
\vspace{-1pt}
\begin{itemize}
\item Developed automated vulnerability scanning workflows using Python and Jenkins integrating Nessus API for real-time threat detection.
\item Built security dashboards and alert systems tracking remediation progress and ensuring compliance with security policies.
\item Implemented risk prioritization logic categorizing vulnerabilities by severity and automating escalation to technical teams.
\item Reduced manual intervention by 60\% accelerating patch deployment cycles through full CI/CD automation and monitoring.
\end{itemize}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a secure and scalable LMS platform supporting 6K+ students with role-based access controls and encrypted data transmission.
\vspace{-1pt}
\begin{itemize}
\item Implemented secure authentication, role-based access controls, and session management protecting sensitive student and teacher data.
\item Deployed platform on AWS with SSL encryption, CDN caching, and IAM policies ensuring secure access for over 6,000 concurrent users.
\item Optimized database security controls and SQL queries preventing unauthorized access and ensuring data integrity.
\item Monitored system logs and performance metrics identifying security anomalies and supporting incident response activities.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}