% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with strong expertise in Python, JavaScript, and full stack web development. Proven ability to design scalable cloud-based systems using AWS, Docker, and CI/CD pipelines. Solid understanding of algorithms, data structures, and optimization with hands-on experience in RESTful APIs, PostgreSQL, and microservices architecture. Adept at collaborating in Agile environments to deliver high-quality, maintainable code and impactful solutions.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, TypeScript, SQL, HTML5, CSS3, Bash

\textbf{Frameworks \& Libraries:} React, Django, Flask, Node.js, Angular, Redux, Bootstrap

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, Redis, SQLite, ETL Pipelines

\textbf{Cloud \& DevOps:} AWS, Docker, Terraform, CI/CD, Jenkins, Kubernetes

\textbf{Software Development Practices:} Agile, Scrum, TDD, Code Reviews, SDLC, Continuous Integration

\textbf{Computer Science Fundamentals:} Data Structures, Algorithms, OOP, Distributed Systems, Optimization

\textbf{Systems \& Networking:} Unix/Linux, Nginx, RabbitMQ, Microservices, Cloud Monitoring

\textbf{Soft Skills:} Critical Thinking, Collaboration, Adaptability, Communication, Problem Solving, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js enhancing overall system performance.
\item Implemented and optimized RESTful APIs with secure authentication and PostgreSQL queries improving reliability and speed.
\item Deployed cloud-based applications on AWS with Docker and CI/CD pipelines ensuring high uptime and zero-downtime updates.
\item Collaborated within Agile teams through code reviews, sprint planning, and pair programming to maintain code quality.
\item Applied test-driven development and secure coding practices throughout SDLC reducing production issues significantly.
\item Mentored junior developers on backend best practices and contributed to microservices architecture design discussions.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications using Python, Django, and React across frontend and backend layers.
\item Contributed to system design and implementation of the Proposal Management and Mailroom Tracking Systems using SQL.
\item Worked with cross-functional teams to gather requirements, perform integration testing, and support deployments.
\item Gained practical experience in full stack development, secure coding, and automated testing within Agile workflows.
\item Participated in project reviews to identify performance improvements and enhance scalability of deployed systems.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to access lessons, videos, and quizzes with real-time progress tracking.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL to support concurrent online education access.
\item Integrated lesson uploads, quizzes, and teacher dashboards with real-time performance tracking for improved engagement.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrency.
\item Deployed platform on AWS with CDN caching, SSL encryption, and automated monitoring ensuring 99.9\% uptime.
\end{itemize}

\textbf{Automated Cryptocurrency Trading Bot} -- \emph{Personal Project}

\vspace{-1pt}

Automated Python trading bot using Binance API, WebSocket, and algorithmic strategies for real-time execution.
\vspace{-1pt}
\begin{itemize}
\item Developed automated trading bot in Python using Binance API, WebSocket, and real-time data streaming for execution.
\item Implemented dynamic trading algorithms with stop-loss mechanisms and risk management for improved trading accuracy.
\item Integrated Pandas and NumPy for market analysis, data preprocessing, and backtesting of optimization strategies.
\item Deployed using Docker on AWS EC2 with 24/7 monitoring, detailed logging, and automated alert mechanisms for uptime.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}