% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Backend Engineer with proven expertise in TypeScript, Node.js, and building scalable REST APIs and GraphQL services. Experienced in developing enterprise web applications, implementing secure authentication systems, and deploying cloud-based solutions using AWS and Docker. Proficient in SQL database optimization, version control with Git, and collaborating within Agile teams to deliver high-quality, maintainable code that scales across distributed systems and supports global business operations.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} TypeScript, JavaScript, Python, SQL, Bash, PowerShell

\textbf{Backend Development:} Node.js, Express.js, REST API, GraphQL, Django, Flask

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQL Queries, Database Optimization

\textbf{Cloud \& DevOps:} AWS, Docker, CI/CD Pipelines, GitHub Actions, Cloud Deployment

\textbf{Development Practices:} Agile, Scrum, Git, Code Reviews, Testing, Debugging

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable backend services and REST APIs using JavaScript, Node.js, and Express.js to support e-commerce applications.
\item Implemented and optimized SQL queries across PostgreSQL and MySQL databases to improve application performance and reliability.
\item Collaborated with cross functional teams including QAs and designers to deliver high-quality features within Agile sprint cycles.
\item Deployed and maintained cloud-based applications using AWS and Docker with automated CI/CD pipelines ensuring consistent uptime.
\item Conducted thorough code reviews and debugging sessions to maintain clean, maintainable code following best practices and standards.
\item Mentored junior developers on backend development workflows, version control with Git, and secure coding practices.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to backend development of enterprise web applications implementing business requirements into technical solutions.
\item Assisted in building and maintaining RESTful APIs and database integration for the Proposal Management System application.
\item Worked within Agile teams to perform requirements analysis, testing, and deployment support across project lifecycles.
\item Gained hands-on experience writing SQL queries, debugging backend issues, and implementing secure authentication mechanisms.
\item Participated in code reviews and sprint planning sessions to improve code quality, scalability, and system performance.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS with Node.js backend, MySQL database, and REST APIs supporting 6K+ students with secure authentication.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed backend services using Node.js and Express.js with MySQL database to support online education platform.
\item Implemented RESTful APIs for lesson management, quiz functionality, and real-time progress tracking with optimized SQL queries.
\item Integrated secure authentication with JWT tokens and role-based access control to protect user data and system integrity.
\item Deployed the application on AWS using Docker containers with SSL encryption ensuring reliable access for over 6,000 students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed backend for real-time chat application using Node.js, WebSockets, and cloud services with accessibility integrations.
\vspace{-1pt}
\begin{itemize}
\item Built backend services using Node.js and Socket.io to enable real-time communication with low-latency message delivery.
\item Integrated AWS cloud services and APIs to support text-to-speech and voice-to-text accessibility features for inclusive design.
\item Implemented secure authentication, database management, and API endpoints following best practices for scalability and performance.
\item Deployed application on AWS using Docker containers ensuring high availability and seamless scalability for concurrent users.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}