% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with expertise in full stack development using React, Python, and Node.js. Proven ability to design and deploy scalable web applications and microservices on cloud platforms including AWS and Google Cloud Platform. Skilled in building service-oriented architectures, REST APIs, and containerized solutions using Docker and Kubernetes. Experienced in Agile environments with strong collaboration and problem-solving abilities, delivering high-quality code and exceeding customer expectations.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, TypeScript, SQL, HTML5, CSS3, Bash

\textbf{Frameworks \& Libraries:} React, Redux, Django, Flask, Node.js, Bootstrap

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQLite, BigQuery, ETL Pipelines

\textbf{Cloud \& DevOps:} Google Cloud Platform, AWS, Docker, Kubernetes, CI/CD, GitHub Actions

\textbf{Development Practices:} Microservices, REST API, Agile, Scrum, Unit Testing, Code Reviews

\textbf{Computer Science Fundamentals:} Data Structures, Algorithms, Object-Oriented Programming, Design Patterns

\textbf{Systems \& Networking:} Cloud Networking, Unix/Linux, Security Best Practices, Performance Optimization

\textbf{Soft Skills:} Collaboration, Effective Communication, Adaptability, Problem Solving, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable web applications using React, JavaScript, and Node.js following service-oriented architecture patterns.
\item Built and maintained REST APIs with optimized database queries for PostgreSQL and MySQL to enhance system performance.
\item Deployed containerized applications on AWS and Google Cloud Platform using Docker and Kubernetes for high availability.
\item Collaborated with cross-functional teams in Agile environments to deliver high-quality features through code reviews and sprints.
\item Implemented unit testing and integration testing strategies to improve code reliability and reduce production defects.
\item Mentored junior developers on microservices architecture, cloud deployment, and best practices for maintainable code.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to enterprise web application development using React, Python, and SQL across frontend and backend components.
\item Assisted in designing scalable system architectures for management platforms with a focus on performance and reliability.
\item Collaborated with product stakeholders to gather requirements, implement features, and support deployment in Agile workflows.
\item Participated in unit testing, integration testing, and code reviews to ensure high-quality deliverables and maintainability.
\item Gained hands-on experience with cloud technologies, version control systems, and CI/CD pipelines for continuous deployment.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS platform using React, Node.js, and cloud services enabling 6K+ students to access online learning resources.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack LMS using React and Node.js with REST API architecture for lesson management and interactive quizzes.
\item Implemented real-time progress tracking dashboards and role-based access control for teachers and students using JWT authentication.
\item Optimized PostgreSQL database queries and implemented caching strategies to handle high concurrent user traffic efficiently.
\item Deployed on Google Cloud Platform with Docker containers and SSL encryption ensuring scalable and secure access for 6K+ users.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Built inclusive real-time chat app with accessibility features for low-vision users using React and microservices architecture.
\vspace{-1pt}
\begin{itemize}
\item Developed real-time messaging platform using React, Node.js, and WebSockets following microservices design patterns for scalability.
\item Integrated cloud-based speech services APIs to enable text-to-speech and voice-to-text communication for accessibility compliance.
\item Implemented WCAG accessibility standards and conducted testing with assistive technologies to ensure inclusive user experience.
\item Deployed on cloud platform using Docker and Kubernetes clusters for high-performance, low-latency communication at scale.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}