% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Detail-oriented Software Engineer with 1-2 years of experience in data analysis, reporting, and business intelligence. Proficient in SQL, Power BI, and Excel with a strong foundation in database management and data visualization. Skilled at extracting insights from complex datasets, building interactive dashboards, and supporting business decision-making through accurate reporting. Experienced in cloud technologies, automation, and collaborating with cross-functional teams in Agile environments to deliver data-driven solutions.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Data Analysis \& Reporting:} SQL, Power BI, Excel, Data Visualization, ETL Pipelines, BigQuery

\textbf{Database Management:} PostgreSQL, MySQL, MongoDB, SQL Server, Database Design

\textbf{Programming \& Scripting:} Python, JavaScript, Bash, PowerShell, pandas

\textbf{Cloud \& DevOps:} AWS, GCP, Docker, CI/CD, GitHub Actions

\textbf{Business Intelligence:} Dashboard Development, KPI Reporting, Trend Analysis, Data Modeling

\textbf{Soft Skills:} Communication, Teamwork, Problem Solving, Attention to Detail, Time Management, Adaptability

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable web applications using JavaScript and React while optimizing SQL queries to improve data retrieval efficiency.
\item Designed and maintained RESTful APIs and database schemas ensuring data accuracy and consistency across reporting systems.
\item Deployed cloud-based solutions using AWS and Docker with CI/CD pipelines to ensure consistent uptime and reliable performance.
\item Collaborated within Agile teams through sprint planning and code reviews to deliver high-quality solutions aligned with business needs.
\item Applied secure coding standards and testing throughout SDLC improving maintainability and reducing post-deployment issues.
\item Mentored junior developers on best practices for backend development, data modeling, and efficient query optimization techniques.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications with focus on database design, query optimization, and backend functionality.
\item Contributed to the Proposal Management System by implementing data extraction logic and generating automated business reports.
\item Worked with cross-functional teams to gather requirements, perform testing, and support deployment of data-driven applications.
\item Gained hands-on experience in SQL, data analysis, and reporting workflows within Agile software development environments.
\item Collaborated in project reviews to identify performance improvements, data consistency issues, and scalability enhancements.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with notes, videos, and quizzes while tracking performance through dashboards.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full-stack LMS using React, Node.js, and MySQL to support online education during the pandemic.
\item Integrated performance tracking modules with real-time dashboards enabling teachers to analyze student progress and engagement.
\item Implemented secure authentication, role-based access, and optimized SQL queries for high concurrent usage and data consistency.
\item Deployed the platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 students nationwide.
\end{itemize}

\textbf{Custom Business Web Solutions} -- \emph{Personal Project}

\vspace{-1pt}

Built POS, e-commerce sites, and inventory systems with secure responsive design improving business workflow efficiency.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed custom web solutions using React, Next.js, and Express.js tailored to client business requirements.
\item Implemented secure authentication, inventory tracking databases, and integrated payment processing with Stripe API functionality.
\item Collaborated with clients to gather requirements and translate business needs into scalable, data-driven web applications.
\item Optimized UI performance, responsiveness, and data visualization features across all projects to enhance user engagement metrics.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}