% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Detail-oriented Software Engineer with hands-on experience in data analysis, system auditing, and process improvement using Excel, SQL, and Python. Skilled in collaborating across teams to deliver accurate reports, maintain compliance, and optimize workflows. Proven ability to work independently while applying critical thinking to root cause analysis and continuous improvement initiatives. Passionate about leveraging technical expertise to support organizational efficiency and data-driven decision-making.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, PHP, SQL, HTML, CSS, Bash, PowerShell

\textbf{Frameworks \& Libraries:} React, Django, Node.js, Bootstrap, jQuery

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, Excel

\textbf{Cloud \& DevOps:} AWS, GCP, Docker, Kubernetes, GitLab CI/CD, GitHub Actions

\textbf{Software Development Practices:} Agile methodology, Scrum, Requirements analysis, Architecture design, SDLC, Testing, Debugging

\textbf{Computer Science Fundamentals:} Data Structures, Algorithms, Object-Oriented Programming, Design Patterns

\textbf{Systems \& Networking:} Cloud computing, Networking concepts, Security best practices, Unix/Linux environments, Scripting

\textbf{Soft Skills:} Critical thinking, Attention to detail, Collaboration, Communication, Accountability, Adaptability

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed full stack applications using JavaScript, React, and Node.js while ensuring compliance with secure coding standards.
\item Optimized SQL queries and integrated secure payment systems improving system reliability and performance across platforms.
\item Deployed cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and high availability.
\item Collaborated within Agile teams through code reviews, sprint planning, and pair programming to deliver quality solutions.
\item Applied test-driven development throughout SDLC improving maintainability and reducing production issues by 40 percent.
\item Performed root cause analysis and audits on system performance to identify gaps and implement continuous improvements.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level web and mobile applications across both frontend and backend components efficiently.
\item Contributed to system design and implementation while ensuring alignment with contractual and compliance requirements.
\item Worked closely with cross functional teams to gather requirements, perform testing, and support deployment phases.
\item Gained hands-on experience in full stack development, auditing, and secure coding within Agile workflows and environments.
\item Collaborated in project reviews to identify improvements in performance, scalability, and code maintainability standards.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes efficiently.
\vspace{-1pt}
\begin{itemize}
\item Designed a full-stack LMS using React, Node.js, and MySQL to support online education with real-time performance tracking.
\item Integrated modules for lesson uploads, quizzes, and dashboards enabling teachers to monitor student progress and outcomes.
\item Implemented secure authentication, role-based access, and optimized database queries for high concurrent usage and uptime.
\item Deployed the platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 active students.
\end{itemize}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Automated vulnerability scanning and patching to strengthen enterprise security and reduce manual effort by 60 percent.
\vspace{-1pt}
\begin{itemize}
\item Developed automated workflows using Python and Jenkins for vulnerability scanning and patch deployment across environments.
\item Integrated Nessus API for real-time vulnerability reporting and risk prioritization to ensure compliance with security policies.
\item Created dashboards and alert systems to track security compliance and remediation progress for stakeholders and audit teams.
\item Reduced manual intervention by 60 percent and accelerated patch cycles through full CI/CD automation and scheduled audits.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}