% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with hands-on Python scripting, automation, and system integration experience. Proven ability to build and deploy automation workflows, reduce manual processes, and scale production support solutions. Experienced in developing tools using Python, Django, and Flask alongside cloud platforms like AWS and GCP. Skilled in workflow automation, CI/CD pipelines, Docker, and monitoring systems. Passionate about automation-first approaches and AI-driven solutions.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, SQL, Bash, PowerShell, PHP

\textbf{Automation \& Workflow:} Workflow Automation, n8n, CI/CD Pipelines, Jenkins, GitHub Actions, Scripting

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, Infrastructure as Code, Terraform, Monitoring

\textbf{Frameworks \& Libraries:} Django, Flask, FastAPI, React, Node.js, Bootstrap

\textbf{Database \& Integration:} PostgreSQL, MySQL, MongoDB, REST API, GraphQL, ETL Pipelines

\textbf{AI \& Machine Learning:} AI Integration, ChatGPT API, Prompt Engineering, LLM API, Machine Learning APIs

\textbf{Systems \& Networking:} Cloud Computing, Security Best Practices, Unix/Linux, Logging, Load Balancing

\textbf{Soft Skills:} Problem Solving, Analytical Thinking, Communication, Collaboration, Adaptability, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using JavaScript, React, and Node.js improving e-commerce functionality and workflow efficiency.
\item Implemented RESTful APIs, optimized SQL queries, and integrated secure payment systems enhancing reliability and system performance.
\item Deployed and maintained cloud-based applications on AWS with Docker and CI/CD pipelines ensuring consistent uptime and availability.
\item Automated routine checks and monitoring tasks using Python scripts reducing manual intervention and improving operational efficiency.
\item Collaborated within Agile teams through code reviews, sprint planning, and pair programming to deliver high-quality solutions on schedule.
\item Led backend development for multiple applications while mentoring junior developers on automation best practices and deployment standards.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level web and mobile applications across frontend and backend components using modern frameworks.
\item Contributed to design and implementation of Proposal Management and Mailroom Tracking Systems improving operational workflows.
\item Worked closely with cross functional teams to gather requirements, perform testing, and support deployment phases within Agile sprints.
\item Gained hands-on experience in full stack development, software testing, and secure coding practices improving code quality standards.
\item Collaborated in project reviews identifying improvements in performance, scalability, and code maintainability across multiple projects.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic }

\vspace{-1pt}

Automated vulnerability scanning and patching workflows strengthening enterprise security and reducing manual effort by over 60 percent.
\vspace{-1pt}
\begin{itemize}
\item Developed automated workflows using Python and Jenkins for vulnerability scanning, patch deployment, and routine system health checks.
\item Integrated Nessus API for real-time vulnerability reporting, risk prioritization, and automated remediation tracking and alerts.
\item Created dashboards and alert systems to monitor security compliance, track remediation progress, and escalate critical issues automatically.
\item Reduced manual intervention by 60 percent and accelerated patch cycles through full CI/CD automation and continuous improvement practices.
\end{itemize}

\textbf{Automated Cryptocurrency Trading Bot} -- \emph{Personal Project}

\vspace{-1pt}

Created a Python trading bot using Binance API and WebSocket to automate trade execution with risk control and live system monitoring.
\vspace{-1pt}
\begin{itemize}
\item Developed fully automated trading bot in Python using Binance API and WebSocket for real-time data streaming and automated execution.
\item Implemented dynamic trading strategies, stop-loss mechanisms, and order execution algorithms optimizing trade accuracy and performance.
\item Integrated Pandas and NumPy for market analysis and backtesting improving trading accuracy and reducing risk exposure systematically.
\item Deployed using Docker on AWS EC2 for 24/7 uptime, reliability, and monitoring with detailed logging and automated alert notifications.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}