% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Junior Developer with 2+ years of hands-on experience in application development, system analysis, and production support. Proficient in Python, SQL, and relational databases with proven expertise in building scalable applications, optimizing database queries, and supporting large-scale data processing. Experienced in Agile environments, cross-functional collaboration, and delivering robust technical solutions within cloud-based infrastructures using Docker and CI/CD pipelines.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, SQL, Bash, PowerShell, JavaScript, PHP

\textbf{Databases \& Data Management:} PostgreSQL, MySQL, MongoDB, SQLite, SQL Server, Database Design

\textbf{Cloud \& DevOps:} Docker, Kubernetes, AWS, GCP, GitLab CI/CD, GitHub Actions

\textbf{Development Tools:} Git, Jira, Bitbucket, Jenkins, VS Code, Postman

\textbf{Frameworks \& Libraries:} Django, Flask, FastAPI, React, Node.js, Bootstrap

\textbf{Systems \& Networking:} Linux, Unix, Networking, Cloud Computing, Security Best Practices, Shell Scripting

\textbf{Software Development Practices:} Agile, Scrum, Unit Testing, TDD, Code Reviews, SDLC

\textbf{Soft Skills:} Problem Solving, Communication, Collaboration, Adaptability, Analytical Thinking, Documentation

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using Python, JavaScript, and React to enhance system reliability and performance.
\item Implemented RESTful APIs, optimized SQL queries, and integrated secure authentication systems improving database efficiency by 30\%.
\item Deployed and maintained cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring 99.9\% uptime and availability.
\item Collaborated with cross-functional teams through Agile sprints, code reviews, and pair programming to deliver high-quality solutions.
\item Applied test-driven development and secure coding standards throughout SDLC reducing production issues and enhancing maintainability.
\item Provided technical guidance to junior developers on best coding practices, deployment workflows, and troubleshooting methodologies.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications with backend components using Python, SQL, and relational database systems.
\item Contributed to the design and implementation of data management systems supporting daily operations and user acceptance testing.
\item Worked closely with cross-functional teams to gather requirements, perform unit testing, and support deployment phases successfully.
\item Gained hands-on experience in application support, debugging, and secure coding within Agile workflows and SDLC methodologies.
\item Collaborated in project reviews to identify improvements in performance, scalability, and system reliability across production systems.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full-stack LMS using Python, React, and PostgreSQL to support online education for over 6,000 students.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time progress dashboards for instructors.
\item Implemented secure authentication, role-based access, and optimized SQL queries for high concurrent usage and data integrity.
\item Deployed the platform on AWS with Docker containers and SSL encryption ensuring reliable access and 99.8\% uptime availability.
\end{itemize}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Automated vulnerability scanning and patching to strengthen enterprise security and reduce manual effort.
\vspace{-1pt}
\begin{itemize}
\item Developed automated workflows using Python and Jenkins for vulnerability scanning, patch deployment, and system compliance tracking.
\item Integrated third-party APIs for real-time vulnerability reporting, risk prioritization, and remediation progress monitoring.
\item Created dashboards and alert systems to track security compliance metrics and accelerate patch cycles across enterprise systems.
\item Reduced manual intervention by 60\% and accelerated remediation workflows through full CI/CD automation and scripting optimization.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}