% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Cloud Operations Engineer with 4+ years of hands-on experience in cloud infrastructure, automation, and DevOps practices across AWS, GCP, and Azure. Skilled in deploying scalable cloud solutions, implementing CI/CD pipelines, and leveraging infrastructure-as-code tools like Terraform and CloudFormation. Proven ability to monitor system performance, troubleshoot incidents, and collaborate with cross-functional teams in Agile environments to deliver reliable, secure cloud infrastructure aligned with business objectives.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Platforms \& Services:} AWS (EC2, S3, RDS, Lambda, CloudWatch), Google Cloud Platform (GCP), Microsoft Azure, Multi-Cloud Deployments

\textbf{Infrastructure as Code \& Automation:} Terraform, CloudFormation, Ansible, Docker, Kubernetes, CI/CD Pipelines

\textbf{Scripting \& Programming:} Python, Bash, PowerShell, Shell Scripting, JavaScript, SQL

\textbf{DevOps \& Version Control:} Jenkins, GitHub Actions, GitLab CI/CD, Git, Azure DevOps

\textbf{Monitoring \& Incident Response:} Cloud Monitoring, Cloud Logging, CloudWatch, System Monitoring, Troubleshooting, On-Call Support

\textbf{Security \& Networking:} IAM, VPC, Security Best Practices, Backup Strategies, Disaster Recovery, Encryption

\textbf{Databases \& Systems:} PostgreSQL, MySQL, MongoDB, Linux, Ubuntu, Windows Server Administration

\textbf{Soft Skills:} Team Collaboration, Problem Solving, Communication, Adaptability, Customer Service Mindset, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Deployed and maintained cloud-based applications on AWS using Docker, Kubernetes, and CI/CD pipelines ensuring consistent uptime.
\item Implemented infrastructure-as-code solutions with CloudFormation and Terraform automating resource provisioning and configuration.
\item Monitored cloud systems with CloudWatch and logging tools responding to incidents and troubleshooting infrastructure issues promptly.
\item Collaborated within Agile teams to automate repetitive tasks using Python, Bash, and PowerShell scripts improving operational efficiency.
\item Optimized SQL queries, configured secure IAM policies, and integrated backup strategies to ensure system reliability and security.
\item Participated in code reviews, sprint planning, and documentation to support DevOps workflows and maintain high-quality infrastructure.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in deploying cloud resources and maintaining infrastructure following established best practices and standard operating procedures.
\item Supported CI/CD pipeline operations and troubleshooting to ensure smooth build and deployment processes across development environments.
\item Gained hands-on experience with cloud platforms, scripting, and automation tools while working under guidance of senior engineers.
\item Collaborated with cross-functional teams to gather requirements, perform testing, and support cloud infrastructure deployment phases.
\item Documented activities, participated in project reviews, and proactively sought mentorship to build cloud engineering skills and expertise.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS on AWS supporting 6K+ students with secure authentication, performance tracking, and optimized cloud infrastructure.
\vspace{-1pt}
\begin{itemize}
\item Designed and deployed a full-stack LMS on AWS using EC2, S3, and RDS with SSL encryption ensuring secure, reliable access for users.
\item Implemented auto-scaling, load balancing, and CDN caching to optimize performance and handle high concurrent usage during peak periods.
\item Configured IAM policies, security groups, and VPC networking to enforce access controls and maintain compliance with security best practices.
\item Monitored system performance using CloudWatch and logs, troubleshooting infrastructure issues to maintain uptime and user satisfaction.
\end{itemize}

\textbf{PROSPR " Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an accessible real-time chat app integrating AWS and Azure cloud services with Docker deployment for scalable communication.
\vspace{-1pt}
\begin{itemize}
\item Deployed the application on AWS App Runner using Docker containers ensuring low-latency, scalable real-time communication infrastructure.
\item Integrated AWS Polly and Azure Speech Services APIs to enable cloud-based text-to-speech and voice-to-text accessibility features.
\item Configured cloud networking, security groups, and environment variables following cloud security and operational best practices.
\item Monitored application performance and logs, troubleshooting deployment issues to ensure reliable uptime and seamless user experience.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}