% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Detail-oriented QA Engineer with proven experience in manual and automated testing across web and mobile applications. Skilled in Python, Bash scripting, and working within Agile/Scrum environments to ensure high-quality software releases. Proficient in Linux and Windows administration, bug tracking, test suite execution, and technical documentation. Strong communicator experienced in collaborating with cross-functional and global teams to deliver reliable solutions meeting customer standards.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming \& Scripting:} Python, Bash, PowerShell, JavaScript, SQL

\textbf{Operating Systems \& Administration:} Linux (Ubuntu), Windows OS, Unix environments, System administration

\textbf{Testing \& Quality Assurance:} Test suite execution, Bug tracking, Automated testing, Integration testing, Unit testing

\textbf{Software Development \& Methodologies:} Agile methodology, Scrum, SDLC, CI/CD pipelines, Version control (Git)

\textbf{Tools \& Platforms:} Jira, Jenkins, Docker, GitHub Actions, Postman

\textbf{Database \& Cloud Technologies:} PostgreSQL, MySQL, AWS, Cloud computing

\textbf{Soft Skills:} Communication, Collaboration, Time management, Attention to detail, Adaptability, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable web applications using JavaScript and React ensuring functionality met customer standards and specifications.
\item Collaborated within Agile teams performing code reviews and sprint planning to deliver high-quality releases on schedule.
\item Implemented automated testing and CI/CD pipelines using Docker and AWS reducing production issues and deployment time.
\item Applied test-driven development and secure coding standards throughout SDLC improving maintainability and reliability.
\item Deployed and maintained cloud applications ensuring consistent uptime and optimized performance through monitoring and logging.
\item Worked with cross-functional teams to identify bugs, validate fixes, and ensure all releases passed quality control standards.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise applications performing manual testing and validation to ensure functionality met requirements.
\item Worked closely with developers to test bug fixes and document defects in tracking systems for resolution.
\item Contributed to software testing phases including integration and system testing within Agile workflows and sprint cycles.
\item Collaborated in project reviews identifying improvements in performance, scalability, and code quality standards.
\item Gained hands-on experience in full stack development, testing methodologies, and secure coding practices across projects.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full-stack LMS using React, Node.js, and MySQL supporting online education during the pandemic.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time progress dashboards for teachers.
\item Implemented secure authentication and role-based access with optimized database queries for high concurrent user volumes.
\item Deployed the platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 students.
\end{itemize}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Automated vulnerability scanning and patching to strengthen enterprise security and reduce manual effort.
\vspace{-1pt}
\begin{itemize}
\item Developed automated workflows using Python and Jenkins for vulnerability scanning and patch deployment across systems.
\item Integrated Nessus API for real-time vulnerability reporting and risk prioritization improving security compliance tracking.
\item Created dashboards and alert systems to track security compliance and remediation progress with detailed logging.
\item Reduced manual intervention by 60\% and accelerated patch cycles through full CI/CD automation and testing validation.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}