% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Detail-oriented Software Engineer with 2+ years of experience in full stack development, data visualization, and automation. Proficient in Python, SQL, and Power BI with a strong foundation in database design, ETL processes, and building scalable analytical solutions. Experienced in cloud infrastructure, agile collaboration, and delivering data-driven insights to stakeholders. Skilled in Excel modeling, technical documentation, and translating complex requirements into reliable systems.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming \& Query Languages:} Python, SQL, JavaScript, PHP, Bash, PowerShell

\textbf{Data \& Analytics Tools:} Power BI, Excel, BigQuery, ETL Pipelines, Data Visualization, Chart.js

\textbf{Database Management:} PostgreSQL, MySQL, MongoDB, Database Design, Database Administration

\textbf{Cloud \& DevOps:} AWS, Docker, CI/CD, GitHub Actions, Infrastructure as Code

\textbf{Development Practices:} Agile, Scrum, Requirements Analysis, Testing, Technical Documentation

\textbf{Soft Skills:} Analytical Thinking, Communication, Collaboration, Problem Solving, Adaptability, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable web applications with Python and JavaScript, optimizing SQL queries to improve data retrieval and reporting.
\item Built automated ETL pipelines and integrated Power BI dashboards to deliver actionable insights for key business stakeholders.
\item Designed and maintained relational databases ensuring data integrity, security, and high performance for concurrent operations.
\item Collaborated within Agile teams performing code reviews, testing, and sprint planning to deliver reliable production systems.
\item Deployed cloud-based solutions using AWS and Docker with CI/CD automation ensuring consistent uptime and rapid deployment cycles.
\item Mentored junior developers on database optimization, secure coding practices, and analytical tool integration best practices.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise systems with focus on database design, backend logic, and data-driven reporting components.
\item Contributed to building management tracking systems involving SQL database integration and performance measurement workflows.
\item Worked closely with cross functional teams to gather requirements, perform testing, and support deployment of analytical tools.
\item Gained hands-on experience in full stack development, data validation, and secure coding practices within Agile environments.
\item Collaborated in project reviews identifying improvements in data quality, system scalability, and maintainability standards.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS supporting 6K+ students with automated reporting, performance tracking, and data-driven analytics dashboards.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full-stack LMS using Python, SQL, and React to deliver real-time performance analytics and reporting.
\item Integrated automated modules for quiz scoring, progress tracking, and data visualization dashboards for educators and admins.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent user volumes.
\item Deployed the platform on AWS with CDN caching and SSL encryption ensuring reliable access and data security for 6,000+ users.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive real-time chat app with accessibility features, automated workflows, and cloud-based scalability.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time communication platform using Python, JavaScript, and SQL integrating accessibility-focused UI design standards.
\item Integrated AWS Polly and Azure Speech Services automating text-to-speech and voice-to-text features for inclusive communication.
\item Followed WCAG accessibility guidelines and performed rigorous testing to ensure compliance and usability for diverse user groups.
\item Deployed on AWS with Docker containers ensuring scalable, low-latency communication and automated monitoring for uptime reliability.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}