% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven DevOps Engineer with expertise in CI/CD pipeline design, cloud infrastructure automation, and scalable system deployment. Proficient in modern DevOps tools including Jenkins, Docker, Kubernetes, Terraform, and Ansible across AWS, GCP, and Azure platforms. Strong background in scripting with Python and Bash, infrastructure-as-code practices, and Agile collaboration. Proven ability to optimize workflows, enhance system reliability, and implement monitoring solutions that drive operational excellence.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{DevOps \& Cloud Platforms:} AWS, Google Cloud Platform, Azure, Docker, Kubernetes, Terraform

\textbf{CI/CD \& Automation:} Jenkins, GitHub Actions, GitLab CI/CD, Ansible, Infrastructure as Code

\textbf{Programming \& Scripting:} Python, Bash, PowerShell, JavaScript, Shell Scripting

\textbf{Monitoring \& Logging:} CloudWatch, Cloud Monitoring, Cloud Logging, System Performance Monitoring

\textbf{Database \& Storage:} PostgreSQL, MySQL, MongoDB, AWS S3, AWS RDS, SQL

\textbf{Version Control \& Collaboration:} Git, GitHub, GitLab, Bitbucket, Jira, Agile

\textbf{Systems \& Networking:} Linux, Ubuntu, Networking Principles, VPN, Load Balancing, Nginx

\textbf{Soft Skills:} Communication, Team Collaboration, Problem Solving, Adaptability, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Deployed and maintained cloud applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and availability.
\item Implemented automated CI/CD workflows with GitHub Actions and GitLab reducing deployment time and enhancing release reliability.
\item Optimized cloud infrastructure for scalability and performance using Docker containerization and orchestration best practices.
\item Collaborated across Agile teams through code reviews, sprint planning, and documentation to ensure high-quality deliverables.
\item Monitored system performance and resolved issues proactively using CloudWatch and logging tools to maintain operational stability.
\item Developed Python and Bash scripts for automation, infrastructure provisioning, and deployment process optimization across environments.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in deploying enterprise applications with Docker and cloud infrastructure across development and production environments.
\item Contributed to building CI/CD pipelines for automated testing and deployment improving software delivery workflows and efficiency.
\item Worked closely with cross-functional teams to gather requirements, perform integration testing, and support deployment phases.
\item Gained hands-on experience in infrastructure automation, scripting, and monitoring tools within Agile development workflows.
\item Collaborated in project reviews to identify improvements in system performance, scalability, and infrastructure maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic }

\vspace{-1pt}

Automated vulnerability scanning and patching workflows to strengthen security and reduce manual effort using CI/CD automation.
\vspace{-1pt}
\begin{itemize}
\item Developed automated CI/CD workflows using Python and Jenkins for vulnerability scanning, patch deployment, and compliance tracking.
\item Integrated Nessus API for real-time vulnerability reporting, risk prioritization, and automated security remediation processes.
\item Created monitoring dashboards and alert systems to track security compliance, remediation progress, and patch deployment status.
\item Reduced manual intervention by 60\% and accelerated patch cycles through full CI/CD automation and infrastructure-as-code practices.
\end{itemize}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with notes, videos, and quizzes using cloud infrastructure and automation.
\vspace{-1pt}
\begin{itemize}
\item Designed full-stack LMS using React, Node.js, and MySQL deployed on AWS with Docker containerization for scalable online education.
\item Implemented CI/CD pipelines for automated testing and deployment ensuring reliable updates and consistent platform availability.
\item Optimized database queries and integrated CDN caching with SSL encryption to support high concurrent usage and system performance.
\item Deployed platform infrastructure using AWS services including EC2, S3, and RDS with monitoring and logging for operational insights.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}