% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Developer with hands-on experience building scalable web applications using JavaScript, React, Node.js, and SQL. Proven ability to develop RESTful APIs, optimize database performance, and deploy cloud-based solutions on AWS. Experienced in Agile workflows, CI/CD pipelines, code reviews, and test-driven development. Strong problem-solving skills with a collaborative mindset, dedicated to continuous improvement and delivering high-quality software solutions.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, Python, SQL, HTML5, CSS3

\textbf{Frontend Technologies:} React, Redux, Bootstrap, Material UI, Responsive Design

\textbf{Backend Technologies:} Node.js, Express.js, REST API, Django, Flask

\textbf{Databases:} MySQL, PostgreSQL, MongoDB, SQLite

\textbf{Cloud \& DevOps:} AWS, CloudFormation, Docker, CI/CD, GitHub Actions

\textbf{Development Practices:} Agile, Scrum, Code Reviews, Unit Testing, Technical Documentation

\textbf{Soft Skills:} Communication, Team Collaboration, Problem Solving, Adaptability, Time Management, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js to enhance functionality and user experience.
\item Implemented RESTful APIs and optimized SQL queries improving system reliability, performance, and database query response times.
\item Deployed cloud-based applications on AWS using Docker and CI/CD pipelines ensuring consistent uptime and reliable availability.
\item Collaborated in Agile teams through code reviews, sprint planning, and pair programming to deliver high-quality software solutions.
\item Applied test-driven development and debugging techniques throughout SDLC reducing production issues and improving maintainability.
\item Mentored junior developers on best coding practices, deployment strategies, and architectural design ensuring knowledge transfer.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level web applications across frontend and backend components using modern development frameworks.
\item Contributed to the design and implementation of management systems supporting business operations and workflow automation.
\item Worked with cross functional teams to gather requirements, perform testing, and support deployment phases in Agile workflows.
\item Gained hands-on experience in full stack development, software testing, and secure coding practices within SDLC processes.
\item Collaborated in project reviews identifying improvements in performance, scalability, and code maintainability for better outcomes.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with notes, videos, and interactive quizzes during the pandemic period.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL to support online education for thousands of students.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards for educators and learners.
\item Implemented secure authentication, role-based access, and optimized SQL queries for high concurrent usage and data integrity.
\item Deployed on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 students with consistent uptime.
\end{itemize}

\textbf{PROSPR " Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive real-time chat app for low-vision users integrating accessibility features and assistive technologies.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and WebSockets with accessibility-focused UI design and responsiveness.
\item Integrated AWS cloud services to enable text-to-speech and voice-to-text communication improving user accessibility and inclusion.
\item Followed WCAG accessibility standards and tested with assistive technologies ensuring inclusive usability for diverse user groups.
\item Deployed on AWS with Docker containers for scalable, low-latency communication supporting concurrent users with high availability.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}