% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Web Developer with expertise in designing and deploying scalable web applications, cloud infrastructure, and automation solutions. Proficient in JavaScript, Python, React, Node.js, and cloud platforms including AWS and GCP. Experienced in full SDLC from requirements analysis to deployment with CI/CD automation. Strong technical documentation skills and proven ability to translate business requirements into robust technical solutions across diverse industries.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, PHP, SQL, HTML5, CSS3, Bash, PowerShell

\textbf{Frameworks \& Libraries:} React, Django, Node.js, Bootstrap, Express.js, Flask

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQLite, Firebase, SQL Server

\textbf{Cloud \& DevOps:} AWS, GCP, Docker, Kubernetes, CI/CD, Terraform

\textbf{Software Development Practices:} Agile, Scrum, Requirements Analysis, Architecture Design, SDLC, Technical Documentation

\textbf{Systems \& Networking:} Cloud Infrastructure, Networking, Security Best Practices, Linux, Automation

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Time Management, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js enhancing e-commerce and business functionality.
\item Designed and implemented RESTful APIs with secure payment integration improving system reliability and customer transaction processing.
\item Deployed cloud-based applications on AWS using Docker and automated CI/CD pipelines ensuring consistent uptime and rapid release cycles.
\item Collaborated with cross functional teams through Agile sprints, code reviews, and technical documentation to deliver high-quality solutions.
\item Applied secure coding standards and test-driven development throughout SDLC reducing production issues and improving maintainability.
\item Mentored junior developers on best practices for backend development, cloud deployment, and architectural design improving team productivity.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to enterprise web and mobile application development across frontend and backend components within Agile workflows.
\item Participated in design and implementation of business systems including Proposal Management and Mailroom Tracking applications.
\item Collaborated with cross functional teams to gather requirements, translate business needs, and support deployment and testing phases.
\item Gained hands-on experience in full stack development, software testing, and secure coding practices across multiple project lifecycles.
\item Supported project reviews to identify improvements in performance, scalability, code maintainability, and technical documentation quality.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes online.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed full stack LMS using React, Node.js, and MySQL supporting online education with interactive learning modules.
\item Integrated quizzes, lesson uploads, and real-time performance tracking dashboards enabling teachers to monitor student progress effectively.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent user traffic handling.
\item Deployed platform on AWS with CDN caching and SSL encryption ensuring reliable, secure access for over 6,000 students and educators.
\end{itemize}

\textbf{Custom Business Web Solutions} -- \emph{Personal Project}

\vspace{-1pt}

Built POS, e-commerce sites, landing pages, and inventory systems with secure responsive web design improving workflow efficiency.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed custom web solutions using React, Next.js, and Express.js translating business requirements into scalable systems.
\item Implemented secure authentication, inventory tracking, and payment processing with Stripe API integration enhancing transaction reliability.
\item Collaborated directly with clients to gather requirements, define technical specifications, and deliver tailored business automation solutions.
\item Optimized UI performance, responsiveness, and SEO across all projects improving user engagement and search engine visibility significantly.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}