% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with 2+ years of expertise building and deploying cloud infrastructure, DevOps pipelines, and scalable full stack systems. Proficient in Kubernetes, AWS, GCP, Terraform, Docker, and CI/CD automation with hands-on experience in infrastructure-as-code, secure deployments, and monitoring. Skilled in designing resilient cloud architectures, optimizing infrastructure for performance and reliability, and collaborating across engineering teams to deliver enterprise-grade solutions.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud \& Infrastructure:} AWS, GCP, Kubernetes, Docker, Terraform, Infrastructure as Code

\textbf{DevOps \& CI/CD:} GitHub Actions, GitLab CI/CD, Jenkins, CI/CD Pipelines, Automation

\textbf{Networking \& Security:} VPC, Load Balancers, IAM, VPN, SSL/TLS, Security Best Practices

\textbf{Observability \& Monitoring:} CloudWatch, Cloud Logging, Cloud Monitoring, Logging, Monitoring

\textbf{Programming \& Scripting:} Python, Bash, JavaScript, Node.js, Shell Scripting, PowerShell

\textbf{Databases \& Storage:} PostgreSQL, MySQL, MongoDB, S3, Cloud Storage, Redis

\textbf{Software Development Practices:} Agile, Scrum, Code Reviews, Testing, Documentation, System Design

\textbf{Soft Skills:} Collaboration, Communication, Adaptability, Ownership, Problem Solving

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Deployed and maintained scalable cloud infrastructure on AWS using Docker, Kubernetes, and CI/CD pipelines for consistent uptime.
\item Built and optimized infrastructure-as-code workflows using Terraform and CloudFormation for environment provisioning automation.
\item Implemented secure networking, load balancing, IAM policies, and monitoring with CloudWatch to ensure system reliability and security.
\item Developed RESTful APIs and backend services using Node.js and Python, integrating with cloud-native storage and database solutions.
\item Collaborated across Agile teams through code reviews, sprint planning, and pair programming to deliver high-quality infrastructure solutions.
\item Automated deployment pipelines using GitHub Actions and GitLab CI/CD, reducing deployment time and improving operational efficiency.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in deploying cloud-based enterprise applications on AWS and GCP, gaining hands-on experience with infrastructure provisioning.
\item Contributed to building CI/CD pipelines and automated testing frameworks to support continuous integration and deployment workflows.
\item Worked closely with cross-functional teams to gather infrastructure requirements, perform testing, and support production deployments.
\item Gained practical experience with containerization using Docker, cloud networking concepts, and secure coding within Agile environments.
\item Collaborated in project reviews to identify infrastructure improvements in performance, scalability, and operational maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS on AWS supporting 6K+ students with automated deployments, monitoring, and cloud infrastructure optimization.
\vspace{-1pt}
\begin{itemize}
\item Designed cloud infrastructure on AWS using EC2, S3, and RDS with auto-scaling and load balancing for high concurrent user traffic.
\item Deployed the full-stack application using Docker containers and CI/CD pipelines for automated releases and rollback capabilities.
\item Configured CloudWatch monitoring, logging, and alerting to track system health, performance metrics, and operational incidents.
\item Implemented secure networking with VPC, SSL/TLS encryption, IAM roles, and security best practices for data protection compliance.
\end{itemize}

\textbf{PROSPR " Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Deployed a real-time chat app on AWS using Docker, App Runner, and cloud infrastructure for scalable, low-latency communication.
\vspace{-1pt}
\begin{itemize}
\item Deployed containerized application using Docker on AWS App Runner with automated scaling and infrastructure-as-code provisioning.
\item Configured cloud networking, load balancers, and VPC settings to ensure secure, low-latency real-time communication for users.
\item Integrated AWS and Azure cloud services including Polly and Speech Services with secure IAM policies and API Gateway configurations.
\item Implemented monitoring and logging using CloudWatch and Cloud Logging to track application performance and troubleshoot production issues.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}