% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven cybersecurity professional with expertise in threat intelligence, vulnerability assessment, incident response, and cloud security. Holds a Postgraduate Certificate in Cybersecurity \& Threat Management (Honours) from Seneca College and an AWS Certified Solutions Architect credential. Background in software engineering provides a strong foundation in understanding application-layer threats and adversary techniques. Adept at researching emerging cyber threats across open and deep web sources, analyzing threat actor activity, and delivering timely, actionable intelligence to protect enterprise environments.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Offensive Security:} Penetration Testing, Ethical Hacking, Vulnerability Exploitation, Metasploit, Burp Suite, Nmap

\textbf{Defensive Security:} SIEM (Splunk, IBM QRadar), IDS/IPS, Threat Intelligence \& Analysis, Incident Response, Digital Forensics

\textbf{Vulnerability Management:} Nessus, OpenVAS, CVE Triage, Risk Prioritization, Patch Automation, Configuration Auditing

\textbf{Cloud \& Infrastructure:} AWS (Certified), Cloud Security Architecture, IAM, VPC, S3 Security, Linux/Unix Administration

\textbf{Programming \& Scripting:} Python, Bash, PowerShell, JavaScript (ReactJS), Django, Security Automation

\textbf{Compliance \& Frameworks:} NIST CSF, ISO 27001, CIS Controls, MITRE ATT\&CK, Incident Response Lifecycle (PICERL)

\textbf{Soft Skills:} Research \& Analysis, Communication, Collaboration, Critical Thinking, Adaptability, Attention to Detail

\vspace{8pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{SolarWinds Supply Chain Attack  Incident Analysis \& Threat Intelligence Report} -- \emph{Case Study  Cybersecurity \& Threat Management}

\vspace{-1pt}

Analyzed the SolarWinds SUNBURST supply chain attack, profiling threat actor TTPs and assessing impact on targeted organizations.
\vspace{-1pt}
\begin{itemize}
\item Reconstructed the full attack chain from the trojanized Orion update to lateral movement and data exfiltration across victims.
\item Mapped adversary tactics, techniques, and procedures (TTPs) to the MITRE ATT\&CK framework for structured threat actor profiling.
\item Assessed organizational impact scope across government agencies, Fortune 500 firms, and critical infrastructure sector providers.
\item Documented detection gaps, defensive recommendations, and vendor risk controls to strengthen supply chain security posture.
\end{itemize}

\textbf{Enterprise Vulnerability Assessment \& Patch Automation} -- \emph{Capstone  Cybersecurity \& Threat Management}

\vspace{-1pt}

Executed an end-to-end enterprise vulnerability assessment program spanning 50+ endpoints across segmented network zones.
\vspace{-1pt}
\begin{itemize}
\item Used Nessus and OpenVAS to identify and classify vulnerabilities by CVSS severity, producing a structured remediation roadmap.
\item Automated patch deployment with Python and Bash scripting, reducing manual effort and accelerating mean time to remediate (MTTR).
\item Applied CVSS risk scoring to prioritize critical CVE remediation, effectively reducing the organization's overall attack surface.
\item Generated a formal vulnerability assessment report per NIST SP 800-115 to meet compliance requirements and inform stakeholders.
\end{itemize}

\vspace{6pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Built three Shopify apps with secure SDLC practices to protect code integrity and prevent common web application vulnerabilities.
\item Built a Video Content Protection Service applying token-based auth and server-side controls to prevent unauthorized media access.
\item Configured PostgreSQL replication and hardened Nginx/Apache servers, reinforcing CIA Triad principles in production environments.
\item Built backend services in Django and ReactJS, gaining OWASP Top 10 exposure including SQLi, XSS, CSRF, and IDOR vulnerabilities.
\item Applied threat modeling during development cycles to identify application attack surfaces and reduce overall security exposure.
\item Monitored production systems for anomalies, developing skills in identifying behavioral patterns linked to potential security threats.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Supported development of a Proposal Management System and Mailroom Tracking System, gaining exposure to access control practices.
\item Participated in software testing and debugging, building skills in identifying logic flaws relevant to security code review.
\item Assisted with integration testing and documentation, developing analytical skills applicable to threat investigation and analysis.
\item Gained exposure to enterprise data workflows and access controls, building foundational information security awareness.
\item Collaborated with teams across SDLC stages, strengthening communication and analytical skills applicable to security operations.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}