% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with hands-on experience building full stack applications and cloud-based solutions using Python, JavaScript, React, and Node.js. Demonstrated expertise in AI integration including prompt engineering, LLM APIs, and machine learning solutions deployment on AWS and GCP. Proven ability to deliver scalable, secure applications through Agile methodologies while collaborating across cross-functional teams to drive innovation and technical excellence.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, SQL, Bash, PowerShell

\textbf{Frameworks \& Libraries:} React, Django, Flask, Node.js, Express.js, pandas

\textbf{Cloud \& DevOps:} AWS, GCP, Docker, Kubernetes, CI/CD, GitHub Actions

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, BigQuery, ETL Pipelines

\textbf{AI \& Machine Learning:} Prompt Engineering, LLM API, ChatGPT API, AI Integration, Machine Learning APIs

\textbf{Software Development Practices:} Agile, Scrum, Testing, System Design, Code Reviews

\textbf{Soft Skills:} Collaboration, Communication, Adaptability, Problem Solving, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using Python, JavaScript, React, and Node.js to deliver robust e-commerce functionality.
\item Implemented RESTful APIs and optimized SQL queries while integrating AI-driven features to enhance system reliability and user experience.
\item Deployed cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring high availability and consistent uptime across environments.
\item Collaborated within Agile teams through code reviews and sprint planning to deliver high-quality solutions aligned with business objectives.
\item Applied test-driven development and secure coding standards throughout SDLC improving maintainability and reducing production defects.
\item Led backend development initiatives while mentoring junior developers on deployment best practices and modern development workflows.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level applications across frontend and backend components using Python and JavaScript frameworks.
\item Contributed to requirements gathering, system design, and implementation of Proposal Management and Mailroom Tracking Systems.
\item Worked closely with cross-functional teams to perform testing, debugging, and support deployment phases in Agile environments.
\item Gained hands-on experience in full stack development, automation testing, and secure coding within collaborative team workflows.
\item Collaborated in project reviews to identify improvements in performance, scalability, and code maintainability across applications.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with notes, videos, and interactive quizzes during the pandemic using cloud infrastructure.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack LMS using React, Node.js, and MySQL to support online education with real-time performance tracking dashboards.
\item Integrated modules for lesson uploads, quizzes, and analytics with secure authentication and role-based access control mechanisms.
\item Optimized database queries and implemented caching strategies to handle high concurrent usage and improve application performance.
\item Deployed on AWS with CDN caching and SSL encryption ensuring reliable access and data security for over 6,000 active students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed inclusive real-time chat app for low-vision users integrating accessibility features and AI-powered speech services for communication.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Node.js, and Socket.io with accessibility-focused UI following WCAG standards.
\item Integrated AWS Polly and Azure Speech Services to enable text-to-speech and voice-to-text communication for inclusive usability.
\item Tested with assistive technologies and conducted user feedback sessions to ensure accessibility compliance and user satisfaction.
\item Deployed on AWS App Runner with Docker containers for scalable, low-latency communication and high availability across regions.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}