% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Backend Developer with 3+ years of experience building scalable web applications using PHP, Laravel, Python, and modern frameworks. Skilled in designing secure back-end systems, optimizing databases, and collaborating across distributed teams. Proven ability to translate complex requirements into efficient code, contribute to AI-related workflows, and deliver production-grade solutions in Agile environments. Strong communicator with expertise in cloud infrastructure, CI/CD automation, and full stack development.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} PHP, Python, JavaScript, SQL, HTML, CSS

\textbf{Frameworks \& Libraries:} Laravel, Django, Flask, React, Node.js, Bootstrap

\textbf{Database \& Data Management:} MySQL, PostgreSQL, MongoDB, SQLite, Database Design

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, CI/CD, GitHub Actions, Infrastructure as Code

\textbf{Software Development Practices:} Agile, Scrum, Version Control, Testing, Code Reviews, Documentation

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Self-Motivated, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable web applications using PHP, Laravel, JavaScript, and React to enhance business functionality and user experience.
\item Designed and implemented RESTful APIs, optimized MySQL and PostgreSQL queries, and integrated secure authentication systems.
\item Deployed cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring high availability and consistent performance.
\item Collaborated with distributed teams through code reviews, Agile ceremonies, and written documentation to ensure quality deliverables.
\item Applied best practices in testing, version control, and secure coding throughout SDLC improving maintainability and reliability.
\item Led back-end development efforts while mentoring junior developers on Laravel architecture, API design, and deployment strategies.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications using PHP, Python, and modern frameworks across front-end and back-end layers.
\item Contributed to designing and implementing scalable back-end systems for data-driven business applications.
\item Worked closely with cross functional teams to gather requirements, perform testing, and support deployment in Agile workflows.
\item Gained hands-on experience in full stack development, database optimization, secure coding, and troubleshooting production issues.
\item Participated in project reviews identifying improvements in performance, scalability, and adherence to software engineering standards.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to access lessons, videos, and interactive quizzes with real-time tracking dashboards.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL supporting online education for over 6,000 students.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards for instructors and learners.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent user activity.
\item Deployed the platform on AWS with CDN caching and SSL encryption ensuring reliable access and consistent system performance.
\end{itemize}

\textbf{Custom Business Web Solutions} -- \emph{Personal Project}

\vspace{-1pt}

Built POS systems, e-commerce platforms, and inventory management solutions with secure, responsive design improving client workflows.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed custom web applications using PHP, Laravel, React, and Next.js tailored to client business requirements.
\item Implemented secure authentication, inventory tracking, payment processing with Stripe API, and back-end data management systems.
\item Collaborated with clients to translate business needs into scalable, production-ready applications with clean code architecture.
\item Optimized UI performance, responsiveness, database queries, and SEO across all projects enhancing user engagement and efficiency.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}