% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with expertise in cloud infrastructure, DevOps automation, and full stack development. Skilled in AWS services including Lambda, S3, RDS, and API Gateway with hands-on experience building CI/CD pipelines, Infrastructure as Code, and event-driven microservices. Proficient in Python, JavaScript, and modern frameworks with a strong foundation in database management across MySQL, MongoDB, and DynamoDB. Proven ability to collaborate across technical teams, mentor developers, and deliver scalable cloud-native solutions.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, TypeScript, SQL, Bash, PowerShell

\textbf{Cloud \& AWS Services:} AWS Lambda, S3, RDS, API Gateway, ECS, CloudFormation, Step Functions

\textbf{Database Technologies:} MySQL, MongoDB, DynamoDB, PostgreSQL, Database Design

\textbf{DevOps \& Infrastructure:} Docker, Kubernetes, Terraform, CI/CD Pipelines, GitHub Actions, Jenkins

\textbf{Backend Frameworks:} FastAPI, Django, Flask, Node.js, Express.js, REST API

\textbf{Architecture \& Patterns:} Microservices, Event-Driven Architecture, Serverless, IaC, System Design

\textbf{Monitoring \& Observability:} CloudWatch, Cloud Monitoring, Logging, Performance Optimization

\textbf{Soft Skills:} Communication, Team Collaboration, Problem Solving, Mentorship, Adaptability, Technical Documentation

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Deployed and maintained cloud-native applications on AWS using Lambda, S3, RDS, and API Gateway ensuring consistent uptime.
\item Built and optimized CI/CD pipelines with GitHub Actions and Docker improving deployment speed and reducing manual intervention.
\item Implemented Infrastructure as Code using CloudFormation and Terraform for automated, repeatable cloud provisioning workflows.
\item Developed RESTful APIs and serverless microservices using Python, FastAPI, and Node.js enabling scalable backend solutions.
\item Integrated monitoring solutions with CloudWatch and logging frameworks improving observability and troubleshooting efficiency.
\item Mentored junior developers on containerization, cloud deployment best practices, and secure coding within Agile workflows.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in building full stack applications using Python, Django, and MySQL supporting enterprise-level systems and workflows.
\item Contributed to backend development for Proposal Management and Mailroom Tracking Systems with database design and optimization.
\item Collaborated with cross functional teams to gather requirements, perform integration testing, and support deployment processes.
\item Gained hands-on experience with AWS services including EC2, S3, and RDS for cloud infrastructure and application deployment.
\item Participated in Agile sprint planning, code reviews, and technical discussions to improve system performance and maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS on AWS enabling 6K+ students to access lessons, quizzes, and dashboards with real-time progress tracking.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed full stack LMS using React, Node.js, and MySQL deployed on AWS with CDN caching and SSL encryption.
\item Implemented role-based authentication, secure API endpoints, and optimized database queries for high concurrent user access.
\item Integrated CloudWatch monitoring and logging for system health, performance tracking, and automated alerting on critical events.
\item Deployed containerized services using Docker and set up automated CI/CD pipelines for continuous integration and deployment.
\end{itemize}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Automated vulnerability scanning and patch deployment reducing manual effort by 60% and strengthening enterprise security posture.
\vspace{-1pt}
\begin{itemize}
\item Developed automated workflows using Python and Jenkins for vulnerability scanning, patch deployment, and security compliance tracking.
\item Integrated Nessus API for real-time reporting and risk prioritization enabling proactive remediation of critical vulnerabilities.
\item Built monitoring dashboards and alert systems to track patching progress, compliance status, and remediation timelines across systems.
\item Implemented full CI/CD automation accelerating patch cycles and reducing manual intervention through infrastructure as code practices.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}