% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Software Engineer with expertise in cloud infrastructure, backend development, and DevOps automation. Proficient in Python, AWS services including Lambda, ECS, RDS, S3, and API Gateway, with hands-on experience building CI/CD pipelines and Infrastructure as Code using Terraform and Docker. Skilled in database management across MySQL, MongoDB, and DynamoDB, and experienced with monitoring tools and event-driven microservices architecture. Strong communicator and collaborator with a proven track record of mentoring developers.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming \& Scripting:} Python, JavaScript, SQL, Bash, PowerShell

\textbf{Cloud \& Infrastructure:} AWS (Lambda, ECS, RDS, S3, API Gateway), Docker, Kubernetes, Terraform, CloudFormation

\textbf{Databases:} MySQL, MongoDB, DynamoDB, PostgreSQL

\textbf{DevOps \& CI/CD:} GitHub Actions, GitLab CI/CD, Jenkins, Infrastructure as Code, Release Management

\textbf{Frameworks \& Tools:} FastAPI, Django, Flask, Node.js, React

\textbf{Architecture \& Design:} Microservices, Event-Driven Architecture, Serverless, Design Patterns, System Design

\textbf{Monitoring \& Observability:} CloudWatch, Cloud Monitoring, Logging, Performance Optimization

\textbf{Soft Skills:} Communication, Team Collaboration, Mentorship, Problem Solving, Continuous Learning, Adaptability

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Deployed and maintained cloud-based applications on AWS using Lambda, ECS, S3, and RDS with Docker containerization and CI/CD pipelines.
\item Built and optimized RESTful APIs and microservices using Python frameworks including FastAPI and Django for scalable backend systems.
\item Implemented Infrastructure as Code with Terraform and CloudFormation to automate resource provisioning and improve deployment efficiency.
\item Developed database solutions across MySQL, MongoDB, and DynamoDB optimizing queries and ensuring data integrity for high-traffic applications.
\item Collaborated with cross-functional teams using Agile methodologies, conducting code reviews and sprint planning to deliver quality solutions.
\item Monitored system performance using CloudWatch and logging tools, implementing observability improvements and troubleshooting production issues.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to backend development of enterprise applications using Python and Node.js with focus on API design and database integration.
\item Assisted in building CI/CD pipelines with GitHub Actions and GitLab CI/CD to automate testing, deployment, and release management processes.
\item Worked on containerizing services with Docker and deploying to cloud platforms ensuring scalability and consistent environment configurations.
\item Collaborated with platform teams to implement monitoring and logging solutions improving system observability and incident response capabilities.
\item Participated in Agile ceremonies including sprint planning and retrospectives while documenting platform processes and technical specifications.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS on AWS enabling 6K+ students with lessons, quizzes, and dashboards using cloud infrastructure and containerization.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack LMS using React and Node.js backend with MySQL database deployed on AWS using Lambda and RDS for serverless architecture.
\item Implemented event-driven architecture with AWS Step Functions and API Gateway to handle asynchronous processing of student assessments.
\item Deployed platform using Docker containers on AWS ECS with autoscaling and load balancing ensuring high availability for concurrent users.
\item Integrated CloudWatch monitoring and logging to track system performance, user activity, and error rates enabling proactive issue resolution.
\end{itemize}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Automated vulnerability scanning and patching using Python, Jenkins, and CI/CD pipelines to strengthen enterprise security posture.
\vspace{-1pt}
\begin{itemize}
\item Developed automated workflows in Python with Jenkins CI/CD pipelines for continuous vulnerability scanning and patch deployment across systems.
\item Integrated Nessus API for real-time security assessment and built custom scripts to prioritize vulnerabilities based on risk severity levels.
\item Created monitoring dashboards and alert systems to track patch compliance and security metrics improving incident response and remediation.
\item Reduced manual patching effort by 60\% through full automation of scanning, reporting, and deployment cycles using Infrastructure as Code principles.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}