% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with extensive experience in full stack development, cloud infrastructure, and DevOps automation. Proven expertise in designing, deploying, and managing containerized applications using Docker and Kubernetes across AWS and GCP environments. Skilled in building CI/CD pipelines with Jenkins and GitLab, implementing Infrastructure as Code with Terraform, and developing Python web applications using FastAPI, Flask, and Django. Strong background in Agile methodologies, microservices architecture, and cross-functional collaboration.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, SQL, Bash, PowerShell, HTML, CSS

\textbf{Frameworks \& Libraries:} FastAPI, Flask, Django, React, Node.js, Bootstrap

\textbf{Containerization \& Orchestration:} Docker, Kubernetes, Docker Compose, Microservices, Container Management

\textbf{Cloud Platforms \& Infrastructure:} AWS, Azure, GCP, AWS EC2, AWS Lambda, CloudFormation

\textbf{DevOps \& Automation:} CI/CD, Jenkins, GitLab CI/CD, GitHub Actions, Terraform, Ansible

\textbf{Monitoring \& Security:} Cloud Monitoring, Logging, OWASP, IAM, Security Best Practices

\textbf{Systems \& Networking:} Linux, Ubuntu, Networking Principles, Load Balancing, High Availability

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Continuous Learning, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using React, Node.js, and Python frameworks ensuring high performance and reliability.
\item Deployed and maintained containerized applications on AWS using Docker and orchestrated scaling with Kubernetes clusters.
\item Implemented automated CI/CD pipelines using Jenkins and GitLab CI/CD reducing deployment time and improving release efficiency.
\item Collaborated with cross-functional teams to optimize infrastructure, streamline workflows, and ensure high availability of production systems.
\item Applied Infrastructure as Code principles using Terraform and Ansible to automate cloud resource provisioning and configuration.
\item Integrated monitoring and logging solutions to track application health, performance metrics, and security compliance across environments.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications using Python, JavaScript, and SQL across frontend and backend components.
\item Contributed to container-based deployments and cloud infrastructure setup supporting scalable application delivery.
\item Worked closely with Agile teams to gather requirements, perform testing, and support deployment phases for production releases.
\item Gained hands-on experience with version control systems, CI/CD automation, and containerization technologies.
\item Collaborated in project reviews to identify performance improvements, scalability enhancements, and maintainability best practices.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built scalable LMS using Python, React, and MySQL deployed on AWS with Docker supporting 6K+ students during pandemic.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack LMS using React, Node.js, and MySQL with secure authentication and role-based access control.
\item Integrated lesson uploads, quizzes, and real-time progress dashboards optimized for high concurrent usage and performance.
\item Deployed platform on AWS using Docker containers with CDN caching and SSL encryption ensuring reliable student access.
\item Implemented automated CI/CD pipelines using GitHub Actions for continuous integration and deployment of feature updates.
\end{itemize}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Automated vulnerability scanning and patching using Python, Jenkins, and Nessus API reducing manual intervention by 60%.
\vspace{-1pt}
\begin{itemize}
\item Developed automated workflows using Python and Jenkins for continuous vulnerability scanning and patch deployment cycles.
\item Integrated Nessus API for real-time vulnerability reporting, risk prioritization, and security compliance tracking dashboards.
\item Created alerting systems and monitoring dashboards to track remediation progress and ensure enterprise security standards.
\item Reduced manual intervention by 60\% and accelerated patch cycles through full CI/CD automation and Infrastructure as Code.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}