% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with expertise in building scalable full stack web applications using JavaScript, React, Node.js, Python, and Django. Proven ability to develop user-centric solutions by leveraging technical proficiency, design thinking, and data-driven decision making. Experienced in collaborating with cross-functional teams, gathering requirements, and delivering high-quality products. Skilled in cloud technologies, CI/CD pipelines, and Agile methodologies with a strong focus on performance optimization and exceptional attention to detail.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, PHP, SQL, HTML5, CSS3

\textbf{Frameworks \& Libraries:} React, Redux, Next.js, Django, Node.js, Bootstrap

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQLite, Redis, DynamoDB

\textbf{Cloud \& DevOps:} AWS, GCP, Docker, Kubernetes, GitHub Actions, CI/CD

\textbf{Software Development Practices:} Agile, Scrum, Requirements Analysis, System Design, SDLC, A/B Testing

\textbf{Computer Science Fundamentals:} Data Structures, Algorithms, OOP, Design Patterns, REST API

\textbf{Systems \& Networking:} Cloud Computing, Security Best Practices, Unix/Linux, Networking

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Ownership, Attention to Detail, Curiosity

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web and Shopify applications using JavaScript, React, and Node.js to enhance e-commerce functionality.
\item Implemented RESTful APIs, optimized SQL queries, and integrated secure payment systems improving system reliability and performance.
\item Deployed and maintained cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and availability.
\item Collaborated within Agile teams through code reviews, sprint planning, and pair programming to ensure high-quality deliverables.
\item Applied test-driven development and secure coding standards throughout SDLC improving maintainability and reducing production issues.
\item Led backend development for multiple Shopify applications while mentoring junior developers on best coding and deployment practices.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level web and mobile applications across both frontend and backend components for diverse use cases.
\item Contributed to the design and implementation of the Proposal Management and Mailroom Tracking Systems with a focus on usability.
\item Worked closely with cross-functional teams to gather requirements, perform testing, and support deployment phases ensuring alignment.
\item Gained hands-on experience in full stack development, software testing, and secure coding within Agile workflows and sprint cycles.
\item Collaborated in project reviews to identify improvements in performance, scalability, and code maintainability based on user feedback.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes online.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL to support online education during the pandemic crisis.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time progress dashboards for teachers and students.
\item Implemented secure authentication, role-based access, and optimized database queries for high concurrent usage and responsiveness.
\item Deployed the platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 students and educators.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users and individuals with reading challenges integrating accessibility features.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and Socket.io with accessibility-focused UI design for inclusive usability.
\item Integrated AWS Polly and Azure Speech Services to enable text-to-speech and voice-to-text communication for diverse user needs.
\item Followed WCAG accessibility standards and tested with assistive technologies to ensure inclusive usability and exceptional user experience.
\item Deployed on AWS App Runner with Docker containers for scalable, low-latency communication ensuring high availability and performance.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}