% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with hands-on experience in software quality assurance, testing, and development across web and enterprise applications. Skilled in Python scripting, test automation, and debugging within fast-paced Agile environments. Proven ability to collaborate with cross-functional teams, validate hardware and software releases, and create detailed test plans and technical documentation. Adept at problem-solving and adapting to evolving technical requirements in broadcast, AV, and cloud-based systems.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming \& Scripting:} Python, JavaScript, SQL, Bash, PowerShell, HTML/CSS

\textbf{Testing \& Quality Assurance:} Test Automation, Manual Testing, Unit Testing, Integration Testing, Debugging, JIRA

\textbf{Frameworks \& Libraries:} React, Node.js, Django, Flask, Bootstrap

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQL Server, Database Design

\textbf{Cloud \& DevOps:} AWS, Docker, CI/CD Pipelines, GitHub Actions, GitLab CI/CD

\textbf{Systems \& Networking:} Linux, Windows, Networking Principles, Security Best Practices, Hardware Troubleshooting

\textbf{Development Practices:} Agile, Scrum, SDLC, Code Reviews, Technical Documentation, Version Control

\textbf{Soft Skills:} Problem Solving, Communication, Adaptability, Team Collaboration, Critical Thinking, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed and validated scalable web applications using JavaScript, React, and Node.js ensuring quality and reliability.
\item Implemented automated and manual testing protocols including unit, integration, and regression testing across software releases.
\item Collaborated with development teams to identify, track, and resolve deficiencies using JIRA within Agile sprint cycles.
\item Deployed and maintained cloud-based applications on AWS using Docker and CI/CD pipelines ensuring consistent system availability.
\item Created comprehensive technical documentation and test plans to support quality assurance and deployment processes.
\item Conducted code reviews and collaborated cross-functionally to ensure adherence to best practices and coding standards.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in validating enterprise web and mobile applications through systematic testing and defect tracking procedures.
\item Contributed to the design, testing, and deployment of Proposal Management and Mailroom Tracking Systems.
\item Worked closely with development and QA teams to gather requirements, execute test cases, and support release cycles.
\item Gained hands-on experience in software testing, debugging, and secure coding practices within Agile workflows.
\item Participated in sprint reviews and retrospectives to identify performance improvements and enhance code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Automated vulnerability scanning and patching to strengthen enterprise security and reduce manual effort.
\vspace{-1pt}
\begin{itemize}
\item Developed automated workflows using Python and Jenkins for vulnerability scanning and patch deployment validation.
\item Integrated Nessus API for real-time vulnerability reporting and risk prioritization to support proactive remediation.
\item Created comprehensive dashboards and alert systems to track security compliance and remediation progress effectively.
\item Reduced manual intervention by 60\% and accelerated patch cycles through full CI/CD automation and testing protocols.
\end{itemize}

\textbf{Automated Cryptocurrency Trading Bot} -- \emph{Personal Project}

\vspace{-1pt}

Created a Python trading bot using Binance API and WebSocket to automate trade execution with risk control and live monitoring.
\vspace{-1pt}
\begin{itemize}
\item Developed a fully automated trading bot in Python using Binance API and WebSocket for real-time data streaming and validation.
\item Implemented dynamic trading strategies, stop-loss mechanisms, and order execution algorithms with extensive unit testing.
\item Integrated Pandas and NumPy for market analysis and backtesting to improve trading accuracy and performance optimization.
\item Deployed using Docker on AWS EC2 for 24/7 uptime, reliability, and monitoring with detailed logging and error tracking.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}