% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with expertise in application security, DevSecOps, and full stack development. Proven experience implementing CI/CD automation, vulnerability scanning, and secure coding practices across cloud-based systems. Skilled in Python, JavaScript, and security tooling with hands-on knowledge of OWASP standards, API security, and incident response. Adept at collaborating with engineering teams to identify and remediate vulnerabilities while maintaining development velocity in fast-paced Agile environments.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Security \& DevSecOps:} OWASP Top 10, API Security, Vulnerability Management, CI/CD Pipelines, GitHub Actions, Incident Response

\textbf{Programming \& Scripting:} Python, JavaScript, Bash, PowerShell, SQL, PHP

\textbf{Cloud \& Infrastructure:} AWS, Docker, Kubernetes, Terraform, IAM, Infrastructure as Code

\textbf{Development Tools \& Practices:} Git, GitLab CI/CD, Jenkins, Agile, Code Reviews, Technical Documentation

\textbf{Frameworks \& Technologies:} React, Node.js, Django, Flask, REST API, PostgreSQL

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Time Management, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed secure full stack applications using JavaScript, React, and Node.js while implementing security best practices throughout SDLC.
\item Integrated secure authentication, IAM policies, and encrypted payment systems to protect user data and ensure regulatory compliance.
\item Deployed applications using AWS, Docker, and CI/CD pipelines with automated security scanning to maintain uptime and detect vulnerabilities.
\item Conducted thorough code reviews focused on security patterns and collaborated with cross-functional teams to remediate identified risks.
\item Applied secure coding standards and vulnerability assessments to reduce production issues and improve application security posture.
\item Mentored developers on security best practices, API protection techniques, and secure deployment workflows within Agile environments.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in building enterprise applications while learning secure coding practices and participating in security-focused code reviews.
\item Contributed to system design with attention to authentication, authorization, and data protection across frontend and backend components.
\item Collaborated with cross-functional teams to gather security requirements, perform testing, and support secure deployment phases.
\item Gained hands-on experience implementing security controls, testing methodologies, and vulnerability identification in Agile workflows.
\item Participated in project reviews to identify security improvements, performance optimization, and code maintainability enhancements.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Automated vulnerability scanning and patching workflows to strengthen enterprise security posture and reduce manual remediation effort.
\vspace{-1pt}
\begin{itemize}
\item Developed automated security workflows using Python and Jenkins to scan vulnerabilities and deploy patches across enterprise systems.
\item Integrated Nessus API for real-time vulnerability detection, risk prioritization, and compliance tracking with detailed reporting.
\item Built monitoring dashboards and alert systems to track remediation progress, security metrics, and compliance status in real time.
\item Reduced manual security intervention by 60\% and accelerated patch deployment cycles through comprehensive CI/CD automation pipelines.
\end{itemize}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS with secure authentication, role-based access control, and encrypted data transmission for 6K+ students.
\vspace{-1pt}
\begin{itemize}
\item Designed full-stack LMS using React, Node.js, and MySQL with secure authentication and role-based access control implementation.
\item Integrated encrypted data transmission, input validation, and SQL injection prevention to protect sensitive student information.
\item Implemented security controls including session management, HTTPS enforcement, and database query optimization for high concurrency.
\item Deployed on AWS with SSL encryption, CDN caching, and security monitoring to ensure reliable and secure access for over 6,000 users.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}