% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with expertise in Agile methodologies, full stack development, and cross-functional collaboration. Proven ability to translate business requirements into scalable technical solutions using React, Python, and cloud platforms. Experienced in backlog management, sprint planning, and delivering high-quality software across the full development lifecycle. Strong communicator skilled at partnering with stakeholders to align product features with business objectives and drive continuous improvement.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, PHP, SQL, HTML, CSS, Bash, PowerShell

\textbf{Frameworks \& Libraries:} React, Django, Node.js, Bootstrap, jQuery

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, Power BI, Data Warehousing, ETL Pipelines

\textbf{Cloud \& DevOps:} AWS, GCP, Docker, Kubernetes, Azure DevOps, CI/CD Pipelines

\textbf{Software Development Practices:} Agile, Scrum, Requirements Analysis, Backlog Management, SDLC, Testing

\textbf{Computer Science Fundamentals:} Data Structures, Algorithms, OOP, Design Patterns

\textbf{Systems \& Networking:} Cloud Computing, Security Best Practices, Unix/Linux, Automation, API Integration

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Ownership, Analytical Thinking, Problem Solving

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Collaborated with cross-functional teams using Agile and Scrum to deliver scalable web applications and e-commerce solutions.
\item Translated business requirements into actionable user stories and technical specifications for full stack development projects.
\item Developed and optimized RESTful APIs and integrated secure payment systems to enhance system reliability and performance.
\item Facilitated sprint planning, backlog grooming, and release activities ensuring timely delivery of high-quality software.
\item Deployed cloud-based applications using AWS, Docker, and CI/CD pipelines maintaining high availability and consistent uptime.
\item Led backend development initiatives while mentoring junior developers on Agile best practices and code quality standards.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Supported development of enterprise web and mobile applications working closely with product managers and engineering teams.
\item Contributed to requirements gathering, feature definition, and acceptance criteria for the Proposal Management System.
\item Collaborated in Agile workflows including sprint planning, testing, and deployment phases to ensure quality deliverables.
\item Participated in backlog refinement and release readiness activities to track progress against project milestones and KPIs.
\item Identified process gaps and contributed to continuous improvement initiatives improving performance and scalability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to access lessons, quizzes, and performance tracking with real-time dashboards.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed full stack LMS using React, Node.js, and MySQL translating user needs into technical requirements.
\item Integrated modules for lesson uploads, quizzes, and analytics dashboards enabling data-driven decision-making for educators.
\item Implemented secure authentication, role-based access, and optimized database queries to support high concurrent user activity.
\item Deployed on AWS with CDN caching and SSL encryption ensuring reliable access and high availability for 6,000+ students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed inclusive real-time chat app for low-vision users integrating accessibility features and cloud-based services.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Node.js, and Socket.io following Agile principles and accessibility standards.
\item Integrated AWS Polly and Azure Speech Services enabling text-to-speech and voice-to-text for enhanced user accessibility.
\item Collaborated with cross-functional team to define features, conduct testing, and ensure WCAG compliance throughout delivery.
\item Deployed on AWS App Runner using Docker containers ensuring scalable, low-latency communication and high availability.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}