% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Backend Python Engineer with 3+ years of experience designing and deploying scalable backend systems, RESTful APIs, and microservices architectures. Proficient in Python, system design, and distributed systems with hands-on expertise in relational databases, Docker, and cloud platforms. Proven ability to optimize performance, implement secure coding practices, and collaborate cross-functionally in Agile environments to deliver high-quality, maintainable solutions.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, SQL, JavaScript, Bash, PowerShell

\textbf{Backend Frameworks \& Tools:} Django, Flask, FastAPI, Node.js, RESTful APIs

\textbf{Database \& Data Management:} MySQL, PostgreSQL, MongoDB, SQLite, Database Design

\textbf{Cloud \& DevOps:} AWS, Docker, CI/CD Pipelines, GitHub Actions, GitLab CI/CD

\textbf{Architecture \& Design:} Microservices, System Design, OOP, Design Patterns, Distributed Systems

\textbf{Systems \& Networking:} Linux, Unix, Networking Principles, API Gateway, Load Balancing

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Ownership, Technical Documentation

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable backend services using Python and RESTful APIs, optimizing SQL queries for relational databases like MySQL.
\item Designed and implemented microservices architecture with Docker containers to ensure high availability and system reliability.
\item Collaborated with cross-functional teams in Agile sprints, conducting code reviews and technical design discussions.
\item Deployed and maintained cloud-based solutions on AWS leveraging CI/CD pipelines for continuous integration and deployment.
\item Applied secure coding practices throughout SDLC, implementing data protection standards and reducing production vulnerabilities.
\item Mentored junior engineers on backend development, system architecture, and best practices for maintainable code.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to backend development of enterprise applications, building APIs and working with relational databases.
\item Assisted in designing system architecture for Proposal Management and Mailroom Tracking Systems using Python and SQL.
\item Participated in sprint planning, estimations, and technical reviews to ensure timely delivery of high-quality features.
\item Worked closely with DevOps and frontend teams to integrate backend services and optimize application performance.
\item Gained hands-on experience with containerization tools like Docker and version control using Git-based repositories.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS with Python backend enabling 6K+ students to access lessons, quizzes, and real-time dashboards securely.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed backend services using Python and RESTful APIs with MySQL to support concurrent user sessions.
\item Implemented role-based access control, secure authentication, and optimized SQL queries for high-performance data retrieval.
\item Deployed platform on AWS with Docker containers, SSL encryption, and CDN caching ensuring reliable uptime and scalability.
\item Integrated real-time performance tracking dashboards enabling teachers to monitor student progress and engagement metrics.
\end{itemize}

\textbf{Automated Cryptocurrency Trading Bot} -- \emph{Personal Project}

\vspace{-1pt}

Created a Python trading bot using Binance API and WebSocket for real-time execution, backtesting, and 24/7 monitoring.
\vspace{-1pt}
\begin{itemize}
\item Developed automated backend in Python integrating Binance API and WebSocket for real-time market data streaming and execution.
\item Implemented dynamic trading algorithms, stop-loss mechanisms, and risk management using object-oriented programming principles.
\item Integrated Pandas and NumPy libraries for data analysis, backtesting strategies, and performance optimization.
\item Deployed on AWS EC2 using Docker for continuous uptime with structured logging and monitoring for system reliability.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}