% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with 2+ years of experience in full stack development, API testing, and automation. Proven ability to collaborate with cross-functional teams to deliver quality software solutions within Agile and Scrum frameworks. Strong background in manual and automated testing, defect management using Jira, and API validation with Postman. Experienced in CI/CD pipelines, DevOps practices, and backend data validation to ensure accuracy and reliability across development lifecycles.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, SQL, Bash, PowerShell

\textbf{Testing \& Quality Assurance:} Manual Testing, Automation Testing, Integration Testing, Regression Testing, API Testing, Postman

\textbf{Frameworks \& Tools:} React, Node.js, Django, Flask, Bootstrap, jQuery

\textbf{Database \& Data Validation:} PostgreSQL, MySQL, MongoDB, SQL Queries, Data Warehousing

\textbf{DevOps \& CI/CD:} Jenkins, GitHub Actions, GitLab CI/CD, Docker, AWS, GCP

\textbf{Project \& Collaboration Tools:} Jira, Agile, Scrum, Technical Documentation, Code Reviews

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Analytical Thinking, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js to enhance e-commerce functionality.
\item Implemented RESTful APIs, optimized SQL queries, and integrated secure payment systems improving reliability and performance.
\item Deployed and maintained cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and availability.
\item Collaborated within Agile teams through code reviews, sprint planning, and pair programming to ensure high-quality deliverables.
\item Applied test-driven development and secure coding standards throughout SDLC improving maintainability and reducing defects.
\item Led backend development for multiple applications while mentoring junior developers on best coding and deployment practices.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level web and mobile applications across both frontend and backend components.
\item Contributed to the design and implementation of the Proposal Management and Mailroom Tracking Systems ensuring data accuracy.
\item Worked closely with cross-functional teams to gather requirements, perform testing, and support deployment phases.
\item Gained hands-on experience in full stack development, software testing, and secure coding within Agile workflows.
\item Collaborated in project reviews to identify improvements in performance, scalability, and code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Automated vulnerability scanning and patching to strengthen enterprise security and reduce manual effort by 60 percent.
\vspace{-1pt}
\begin{itemize}
\item Developed automated workflows using Python and Jenkins for vulnerability scanning and patch deployment across systems.
\item Integrated Nessus API for real-time vulnerability reporting and risk prioritization improving security compliance tracking.
\item Created dashboards and alert systems to track security compliance and remediation progress for stakeholders and teams.
\item Reduced manual intervention by 60 percent and accelerated patch cycles through full CI/CD automation and DevOps practices.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users and individuals with reading challenges, integrating accessibility features.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and Socket.io with accessibility-focused UI design and standards.
\item Integrated AWS Polly and Azure Speech Services to enable text-to-speech and voice-to-text communication for accessibility.
\item Followed WCAG accessibility standards and tested with assistive technologies to ensure inclusive usability and compliance.
\item Deployed on AWS App Runner with Docker containers for scalable, low-latency communication and high availability.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}