% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Developer with expertise in Python, JavaScript, and React, specializing in rapid prototyping and AI-assisted development workflows. Proven ability to build scalable applications using FastAPI, Next.js, MongoDB, and modern cloud technologies. Strong debugging skills across the full stack with hands-on experience integrating REST APIs, authentication systems, and deploying containerized solutions. Adept at collaborating in Agile teams and delivering functional prototypes quickly while maintaining code quality.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, TypeScript, SQL, HTML5, CSS3

\textbf{Frameworks \& Libraries:} React, Next.js, FastAPI, Django, Flask, Node.js, Tailwind CSS, Bootstrap

\textbf{Database \& Data Management:} MongoDB, PostgreSQL, MySQL, Firebase, DynamoDB, Redis

\textbf{Cloud \& DevOps:} AWS, Docker, GitHub Actions, CI/CD, Serverless, Terraform

\textbf{APIs \& Integration:} REST API, GraphQL, Postman, OAuth, JWT, Webhooks

\textbf{AI \& Modern Tools:} AI Integration, Prompt Engineering, GitHub Copilot, ChatGPT API, LLM API

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Problem Solving, Ownership, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Built scalable full stack prototypes using React, Next.js, and Node.js with MongoDB integration to accelerate product validation.
\item Debugged complex full stack issues across frontend, backend, APIs, and Docker environments using Chrome DevTools and Postman.
\item Integrated REST APIs, OAuth authentication, and payment systems improving system reliability and reducing integration time.
\item Deployed cloud applications on AWS with Docker containers and CI/CD pipelines ensuring consistent uptime and rapid iteration.
\item Collaborated in Agile sprints through code reviews and pair programming delivering high-quality functional prototypes on schedule.
\item Leveraged AI coding assistants to accelerate development while validating code quality, security, and maintainability standards.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in rapid prototyping of enterprise web applications using Python, React, and MongoDB for proof-of-concept validation.
\item Contributed to full stack development of Proposal Management System integrating REST APIs and database schema design patterns.
\item Debugged frontend console errors, backend exceptions, and API integration issues to ensure functional prototype delivery.
\item Collaborated with cross functional teams in Agile workflows gathering requirements and iterating based on stakeholder feedback.
\item Gained hands-on experience with Docker, GitHub Actions, and automated testing improving deployment speed and code reliability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS supporting 6K+ students with interactive features enabling seamless online learning during the pandemic.
\vspace{-1pt}
\begin{itemize}
\item Developed full stack LMS using React, Node.js, and MySQL with REST APIs for lesson uploads, quizzes, and real-time dashboards.
\item Implemented secure authentication with JWT and role-based access control optimizing database queries for high concurrent usage.
\item Deployed on AWS with Docker containers, CDN caching, and SSL encryption ensuring reliable access for thousands of students.
\item Debugged performance bottlenecks across frontend, backend, and database layers improving load times and user experience.
\end{itemize}

\textbf{Custom Business Web Solutions} -- \emph{Personal Project}

\vspace{-1pt}

Built POS, e-commerce, and inventory systems with responsive design and secure integrations improving client workflow efficiency.
\vspace{-1pt}
\begin{itemize}
\item Designed multiple web prototypes using React, Next.js, and Express.js with MongoDB integration for rapid client demonstrations.
\item Integrated Stripe API for payment processing and implemented OAuth authentication ensuring secure and reliable transactions.
\item Collaborated with clients to gather requirements and translate business needs into functional prototypes within tight timelines.
\item Optimized UI performance and responsiveness using Tailwind CSS and Chrome DevTools improving user engagement and SEO rankings.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}