% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Web Developer with proven expertise in React, Python, and scalable API development. Experienced in building robust backend systems with Django, Flask, and FastAPI while ensuring seamless integration with modern frontend frameworks. Skilled in cloud deployment, CI/CD automation, and Agile collaboration to deliver high-performance web applications that meet business objectives and technical requirements.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, TypeScript, PHP, SQL, HTML5, CSS3

\textbf{Frontend Development:} React, Redux, Bootstrap, Material UI, SASS, React Query

\textbf{Backend \& APIs:} Django, Flask, FastAPI, Node.js, REST API, GraphQL

\textbf{Database \& Storage:} PostgreSQL, MySQL, MongoDB, SQLite, Firebase, DynamoDB

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, CI/CD, GitHub Actions, Terraform

\textbf{Development Practices:} Agile, Scrum, Unit Testing, Code Reviews, Design Patterns, OOP

\textbf{Soft Skills:} Communication, Team Collaboration, Problem Solving, Adaptability, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using React and Python to deliver robust backend APIs and responsive user interfaces.
\item Built and optimized RESTful APIs with secure authentication and integrated payment processing to improve system performance.
\item Deployed cloud-based applications on AWS using Docker and CI/CD pipelines ensuring high availability and seamless integration.
\item Collaborated with cross-functional teams through Agile sprints and code reviews to deliver high-quality technical solutions.
\item Applied test-driven development practices throughout the SDLC to enhance maintainability and reduce production defects.
\item Led backend development initiatives while mentoring team members on Python frameworks and deployment best practices.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to building enterprise web applications with both frontend and backend components using modern frameworks.
\item Assisted in designing and implementing scalable systems including Proposal Management and Mailroom Tracking applications.
\item Worked with Agile teams to gather requirements, perform integration testing, and support deployment activities.
\item Gained hands-on experience in full stack development, API design, and secure coding practices within collaborative workflows.
\item Participated in project reviews to identify performance improvements and enhance code quality across development cycles.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS using React and Python enabling 6K+ students to access lessons, quizzes, and real-time dashboards.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS with React frontend and Python backend to support online education during the pandemic.
\item Integrated modules for lesson uploads, interactive quizzes, and performance tracking with real-time dashboards for educators.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent usage.
\item Deployed the platform on AWS with SSL encryption and CDN caching ensuring reliable access for over 6,000 active students.
\end{itemize}

\textbf{PROSPR " Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app with React and Python backend integrating accessibility features for low-vision users.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Python, and WebSockets with accessibility-focused UI and WCAG compliance.
\item Integrated AWS Polly and Azure Speech Services APIs to enable text-to-speech and voice-to-text communication features.
\item Followed accessibility standards and tested with assistive technologies to ensure inclusive usability for all user groups.
\item Deployed on AWS with Docker containers for scalable, low-latency communication and seamless integration with frontend systems.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}