% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Frontend Developer with strong expertise in ReactJS, HTML5, CSS, and JavaScript. Proven experience building scalable web applications using React workflows including Redux and modern state management patterns. Skilled in consuming RESTful APIs, implementing responsive user interfaces, and collaborating across teams to deliver high-quality solutions. Adept at leveraging modern frontend frameworks and best practices to create seamless user experiences.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Frontend Technologies:} ReactJS, Redux, JavaScript, HTML5, CSS3, Bootstrap

\textbf{State Management \& APIs:} Redux, React Query, REST API, JSON, WebSockets

\textbf{Programming \& Scripting:} JavaScript, TypeScript, Python, PHP, SQL

\textbf{Database Management:} PostgreSQL, MySQL, MongoDB

\textbf{Development Practices:} Agile, Scrum, Testing, Code Reviews, Version Control

\textbf{Cloud \& DevOps:} AWS, Docker, CI/CD, GitHub Actions

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Curiosity, Knowledge Sharing

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript and React to enhance functionality and user experience.
\item Implemented RESTful APIs consuming JSON data from servers to improve system reliability and frontend-backend integration.
\item Applied Redux data patterns and state management workflows to maintain predictable application state across components.
\item Collaborated within Agile teams through code reviews and sprint planning to ensure high-quality frontend deliverables.
\item Built responsive user interfaces with HTML5, CSS, and modern React frameworks ensuring cross-browser compatibility.
\item Deployed cloud-based applications using AWS and CI/CD pipelines ensuring consistent uptime and performance optimization.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications focusing on frontend components using React and modern JavaScript.
\item Contributed to the design and implementation of user interfaces with emphasis on responsive design and accessibility.
\item Worked closely with cross functional teams to gather requirements and translate them into technical implementations.
\item Gained hands-on experience in full stack development, software testing, and collaborative workflows within Agile teams.
\item Collaborated in project reviews to identify improvements in frontend performance, scalability, and maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS using React and modern frontend frameworks enabling 6K+ students to access educational content online.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed full-stack LMS using React, HTML5, CSS, and REST APIs to support interactive online education.
\item Integrated modules for lesson uploads, quizzes, and real-time progress dashboards consuming JSON data from backend services.
\item Implemented secure authentication and role-based access control ensuring data protection and user privacy compliance.
\item Deployed the platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 active students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic }

\vspace{-1pt}

Developed an inclusive real-time chat app using React with accessibility features for low-vision users and reading challenges.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React and modern JavaScript with accessibility-focused UI design and responsive layout.
\item Integrated AWS Polly and Azure Speech Services APIs consuming JSON data to enable text-to-speech and voice-to-text features.
\item Followed WCAG accessibility standards and tested with assistive technologies to ensure inclusive and collaborative usability.
\item Deployed on AWS App Runner with Docker containers for scalable, low-latency communication and high availability performance.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}