% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Developer with strong expertise in React, TypeScript, and AI-powered application development. Experienced in building enterprise-grade systems with intelligent workflows, document generation, dynamic forms, and complex permissions logic. Skilled in integrating LLM APIs, prompt engineering, and AI-driven features for automated tasks. Proven ability to design scalable architectures using modern state management, cloud services, and REST/GraphQL APIs while delivering frictionless user experiences.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Frontend Development:} React, TypeScript, JavaScript, Redux, Next.js, HTML5, CSS3

\textbf{UI Frameworks \& Styling:} Material UI, Bootstrap, Tailwind CSS, Responsive Design, SASS

\textbf{Backend \& API:} Node.js, REST API, GraphQL, Django, Flask, FastAPI

\textbf{AI \& Automation:} LLM API, ChatGPT API, Prompt Engineering, AI Integration, Workflow Automation

\textbf{Database \& Cloud:} PostgreSQL, MySQL, MongoDB, AWS, GCP, AWS S3, AWS Lambda

\textbf{DevOps \& Tools:} Docker, Kubernetes, CI/CD, GitHub Actions, GitLab, Jenkins

\textbf{Development Practices:} Agile, Scrum, System Design, Code Reviews, Technical Documentation

\textbf{Soft Skills:} Communication, Team Collaboration, Problem Solving, Adaptability, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using React, JavaScript, and Node.js with advanced state management and component architecture.
\item Built modular UI components including dashboards, dynamic forms, and multi-step workflows for e-commerce and business automation platforms.
\item Integrated RESTful APIs and optimized database queries to support complex data structures and real-time user interactions.
\item Deployed cloud-based applications on AWS using Docker and CI/CD pipelines ensuring high availability and consistent system performance.
\item Collaborated in Agile teams through sprint planning, code reviews, and technical documentation to deliver enterprise-grade solutions.
\item Mentored developers on best practices in secure coding, testing strategies, and scalable architecture design throughout the SDLC.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to enterprise web and mobile applications supporting both frontend and backend development across multiple system modules.
\item Participated in designing Proposal Management and Mailroom Tracking Systems with workflow automation and permissions logic.
\item Worked with cross functional teams to gather requirements, implement features, and conduct testing for quality assurance.
\item Gained hands-on experience building data-driven interfaces, secure authentication flows, and role-based access controls.
\item Supported deployment phases and participated in project reviews focused on performance optimization and code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with notes, videos, quizzes, dashboards, and performance tracking capabilities.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack LMS using React, Node.js, and MySQL with modular components for lesson management and interactive assessments.
\item Implemented secure authentication, role-based permissions, and real-time dashboards for teachers to monitor student progress.
\item Integrated dynamic forms and conditional logic for quiz creation, performance tracking, and automated grading workflows.
\item Deployed on AWS with S3 for file storage, CDN caching, and SSL encryption supporting over 6,000 concurrent users reliably.
\end{itemize}

\textbf{PROSPR " Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed inclusive real-time chat application integrating AI-powered text-to-speech and voice-to-text for accessibility support.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Node.js, and WebSockets with accessibility-focused UI following WCAG standards.
\item Integrated AWS Polly and Azure Speech Services for AI-powered text-to-speech and voice-to-text communication features.
\item Designed modular components for chat interfaces, notifications, and user profiles with responsive layouts and assistive technology support.
\item Deployed on AWS App Runner with Docker containers ensuring scalable, low-latency communication and cloud-based data integration.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}