% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Frontend Developer with strong experience in ReactJS, JavaScript, and modern web technologies. Proven ability to build scalable, responsive applications using React workflows like Redux and Flux. Skilled in consuming RESTful APIs and collaborating in Agile environments to deliver high-quality, user-focused solutions. Passionate about learning new technologies and sharing knowledge with cross-functional teams to drive innovation and excellence.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Frontend Development:} ReactJS, Redux, JavaScript, HTML5, CSS3, Bootstrap

\textbf{Backend \& API Integration:} Node.js, REST API, JSON, Express.js, GraphQL

\textbf{Database Technologies:} PostgreSQL, MySQL, MongoDB, SQL

\textbf{Cloud \& DevOps:} AWS, Docker, CI/CD, GitHub Actions, Kubernetes

\textbf{Development Practices:} Agile, Scrum, Code Reviews, Testing, Version Control

\textbf{Soft Skills:} Collaboration, Communication, Adaptability, Problem Solving, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable web applications using JavaScript, React, and Redux workflows to enhance user experience and performance.
\item Built and consumed RESTful APIs with JSON data structures ensuring seamless frontend-backend communication and integration.
\item Collaborated with cross-functional teams using Agile methodologies and code reviews to deliver high-quality React components.
\item Deployed React applications on AWS using Docker and CI/CD pipelines ensuring consistent uptime and rapid feature deployment.
\item Optimized frontend performance and implemented responsive UI designs using HTML5, CSS3, and Bootstrap frameworks.
\item Mentored junior developers on React best practices, state management patterns, and modern JavaScript development techniques.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to frontend development of enterprise applications using React and JavaScript ensuring component reusability.
\item Assisted in API integration and consuming JSON data from backend services to render dynamic content in web applications.
\item Collaborated closely with team members in Agile sprints to gather requirements and deliver features on schedule.
\item Participated in code reviews and pair programming sessions to improve code quality and learn React development workflows.
\item Supported testing and debugging efforts across the full stack ensuring application reliability and user satisfaction.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS using React and Redux enabling 6K+ students to learn with notes, videos, and interactive quizzes.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed frontend using React and Redux for state management with HTML5 and CSS3 for responsive layouts.
\item Integrated RESTful APIs to fetch JSON data for lesson content, quizzes, and real-time progress tracking dashboards.
\item Implemented secure authentication and role-based access control ensuring data privacy and user-specific experiences.
\item Deployed on AWS with Docker containers and CI/CD automation ensuring scalable access for over 6,000 concurrent users.
\end{itemize}

\textbf{PROSPR " Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app using React and Node.js for low-vision users with accessibility-focused UI design.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat frontend using React with Redux for state management and WebSocket integration for live messaging.
\item Consumed JSON data from backend APIs and integrated text-to-speech features ensuring seamless accessibility support.
\item Followed WCAG standards and collaborated with UX designers to create an intuitive, inclusive user interface.
\item Deployed on AWS using Docker containers ensuring low-latency communication and high availability for users.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}