% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Frontend Developer with hands-on experience in ReactJS, JavaScript, and modern web development. Proven ability to build scalable, responsive web applications with seamless REST API integration and client-server architecture. Skilled in Redux workflows, HTML5, CSS3, and delivering high-quality user interfaces through collaborative Agile environments. Passionate about solving complex problems and continuously learning new technologies to drive impactful solutions.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Frontend Development:} React, Redux, JavaScript, HTML5, CSS3, Bootstrap

\textbf{Backend \& APIs:} Node.js, REST API, JSON, Python, Django, Flask

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQL

\textbf{Cloud \& DevOps:} AWS, Docker, CI/CD, GitHub Actions, GitLab CI/CD

\textbf{Development Practices:} Agile, Scrum, Git, Code Reviews, Testing, Debugging

\textbf{Soft Skills:} Collaboration, Communication, Problem Solving, Adaptability, Continuous Learning, Team Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable web applications using React and JavaScript to deliver responsive and user-friendly interfaces for clients.
\item Integrated RESTful APIs and JSON-based services ensuring seamless client-server communication and data exchange workflows.
\item Optimized code quality and performance through rigorous testing, debugging, and adherence to best development practices.
\item Collaborated closely with cross-functional teams in Agile sprints to deliver high-quality solutions on schedule and budget.
\item Deployed applications using Docker and CI/CD pipelines ensuring reliable uptime and consistent production environment stability.
\item Mentored junior developers on coding standards, API integration, and modern frontend workflows including Redux state management.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in building enterprise web applications with focus on frontend components using HTML5, CSS3, and JavaScript frameworks.
\item Contributed to API integration and testing efforts ensuring smooth client-server communication and data consistency checks.
\item Worked within Agile teams gathering requirements, performing code reviews, and supporting deployment phases effectively.
\item Gained hands-on experience with React development and modern frontend workflows while following industry best practices.
\item Collaborated on performance optimization initiatives improving application responsiveness and overall maintainability standards.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS with React and Node.js enabling 6K+ students to access lessons, quizzes, and real-time progress tracking.
\vspace{-1pt}
\begin{itemize}
\item Developed a full-stack LMS using React, HTML5, CSS3, and Node.js with seamless REST API integration for data management.
\item Implemented Redux workflows for state management ensuring consistent user experience across lesson uploads and quiz modules.
\item Integrated secure authentication and role-based access control maintaining data integrity and user privacy standards.
\item Deployed on AWS with CI/CD pipelines and optimized performance ensuring reliable access for over 6,000 concurrent students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Built an inclusive real-time chat app using React and Node.js with accessibility features for low-vision and reading-challenged users.
\vspace{-1pt}
\begin{itemize}
\item Developed a responsive chat application using React, JavaScript, HTML5, and CSS3 following WCAG accessibility standards.
\item Integrated REST APIs for text-to-speech and voice-to-text communication ensuring seamless user interaction and engagement.
\item Collaborated with cross-functional teams to gather requirements, conduct usability testing, and refine UI/UX design features.
\item Deployed on AWS using Docker containers ensuring scalable, low-latency communication for inclusive user experiences.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}