% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with strong expertise in React development and modern front-end technologies. Skilled in building scalable web applications using JavaScript, HTML5, CSS3, and React ecosystem tools including Redux and React Query. Experienced in consuming REST APIs, implementing state management patterns, and working within server-client architectures. Proven ability to deliver high-quality solutions through collaborative teamwork, code reviews, and Agile methodologies with a passion for exploring new technologies.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Frontend Technologies:} JavaScript, HTML5, CSS3, React, Redux, Bootstrap

\textbf{State Management \& Workflows:} Redux, React Query, Flux Pattern, Context API, Hooks

\textbf{Backend \& API Integration:} Node.js, REST API, JSON, Express.js, Server-Client Architecture

\textbf{Database \& Cloud:} PostgreSQL, MySQL, MongoDB, AWS, Docker

\textbf{Development Practices:} Agile, Scrum, Git, CI/CD, Code Reviews, Testing

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Ownership, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript and React with Redux state management to enhance user experience.
\item Implemented RESTful APIs consuming JSON data from server-client architectures ensuring seamless frontend-backend integration.
\item Optimized React component performance and implemented modern workflows including Redux pattern for predictable state management.
\item Collaborated with cross functional teams through Agile sprints, code reviews, and pair programming to deliver quality solutions.
\item Deployed cloud-based React applications using AWS, Docker, and CI/CD pipelines ensuring reliability and continuous deployment.
\item Mentored junior developers on React best practices, Redux workflows, and front-end development standards within team environment.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications using HTML5, CSS3, and JavaScript across frontend and backend components.
\item Contributed to implementation of frontend features consuming REST APIs and rendering JSON data within interactive user interfaces.
\item Worked closely with development teams to gather requirements, perform testing, and support deployment of web-based solutions.
\item Gained hands-on experience with React frameworks, state management patterns, and front-end development within Agile workflows.
\item Collaborated in project reviews to identify improvements in UI performance, code maintainability, and frontend scalability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS using React and Redux enabling 6K+ students to learn with notes, videos, and interactive quizzes.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed full-stack LMS using React with Redux state management and Node.js backend consuming REST APIs.
\item Integrated interactive modules for lesson uploads and quizzes with real-time progress dashboards consuming JSON data streams.
\item Implemented secure authentication, role-based access control, and optimized data fetching patterns for high concurrent usage.
\item Deployed platform on AWS with CDN caching and SSL encryption ensuring reliable performance for over 6,000 active students.
\end{itemize}

\textbf{PROSPR " Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed inclusive real-time chat app using React with server-client architecture for low-vision users and reading challenges.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Redux for state management, and WebSocket for bidirectional server-client communication.
\item Integrated AWS Polly and Azure Speech Services APIs consuming JSON responses for text-to-speech and voice-to-text features.
\item Followed WCAG accessibility standards and tested with assistive technologies ensuring inclusive and responsive user experience.
\item Deployed on AWS using Docker containers for scalable, low-latency real-time communication with continuous uptime monitoring.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}