% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with expertise in full stack development, DevOps automation, and CI/CD pipeline implementation. Skilled in Python, JavaScript, Bash, and PowerShell scripting with strong experience deploying applications on AWS and Docker. Proven ability to collaborate across development, QA, and operations teams to design scalable solutions, automate workflows, and maintain reliable release processes in Agile environments.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming \& Scripting:} Python, JavaScript, Bash, PowerShell, SQL, Shell Scripting

\textbf{DevOps \& CI/CD:} Jenkins, GitHub Actions, GitLab CI/CD, Docker, CI/CD Pipelines, Release Management

\textbf{Cloud \& Infrastructure:} AWS, AWS EC2, AWS S3, Terraform, Infrastructure as Code, Cloud Monitoring

\textbf{Operating Systems \& Tools:} Linux, Ubuntu, Windows OS, Git, GitHub, VMware

\textbf{Database \& Messaging:} MongoDB, PostgreSQL, MySQL, Redis, RabbitMQ

\textbf{Testing \& Automation:} Unit Testing, Integration Testing, Automation Testing, Postman, TDD

\textbf{Soft Skills:} Communication, Team Collaboration, Problem Solving, Adaptability, Ownership, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Deployed and maintained cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring high availability and uptime.
\item Implemented RESTful APIs and optimized database queries to improve system performance, scalability, and overall reliability.
\item Collaborated within Agile teams through code reviews and sprint planning to deliver high-quality production-ready features.
\item Applied test-driven development and secure coding practices across SDLC reducing production issues and improving maintainability.
\item Developed automated workflows using Jenkins and GitHub Actions streamlining release processes and deployment cycles.
\item Worked closely with development and QA teams to ensure complete coverage of features and consistent integration testing.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level applications contributing to both frontend and backend development components.
\item Contributed to design and implementation of Proposal Management and Mailroom Tracking Systems with full stack technologies.
\item Worked closely with cross functional teams to gather requirements, perform testing, and support deployment phases.
\item Gained hands-on experience in software testing, version control, and secure coding practices within Agile workflows.
\item Collaborated in project reviews to identify improvements in performance, scalability, and code quality.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Automated vulnerability scanning and patching workflows using Python and Jenkins to strengthen enterprise security posture.
\vspace{-1pt}
\begin{itemize}
\item Developed automated workflows using Python, Jenkins, and CI/CD pipelines for vulnerability scanning and patch deployment.
\item Integrated Nessus API for real-time vulnerability reporting and automated risk prioritization across enterprise systems.
\item Created dashboards and alert systems to track security compliance, remediation progress, and overall patch status.
\item Reduced manual intervention by 60\% and accelerated patch cycles through comprehensive CI/CD automation strategies.
\end{itemize}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS platform using React, Node.js, and MySQL enabling over 6,000 students to access online education.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed full stack LMS using React, Node.js, and MySQL supporting high concurrent usage and real-time data.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards for instructors.
\item Implemented secure authentication, role-based access control, and optimized database queries for improved performance.
\item Deployed platform on AWS with Docker, CDN caching, and SSL encryption ensuring reliable access for 6,000+ students.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}