% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with strong technical expertise in data analytics, cloud platforms, and reporting automation. Experienced in building dashboards using Power BI, analyzing complex datasets with Python and SQL, and deploying scalable solutions on AWS and GCP. Proven ability to collaborate cross-functionally, document technical processes, and deliver data-driven insights that support strategic decision-making in fast-paced environments.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming \& Scripting:} Python, SQL, JavaScript, Bash, PowerShell

\textbf{Data \& Analytics Tools:} Power BI, Excel, PostgreSQL, MySQL, MongoDB, BigQuery

\textbf{Cloud Platforms \& DevOps:} AWS, Google Cloud Platform, Microsoft Azure, Docker, CI/CD

\textbf{Development \& Frameworks:} React, Django, Node.js, REST API, GraphQL

\textbf{Data Management \& Processes:} ETL Pipelines, Data Warehousing, Database Design, Data Visualization

\textbf{Methodologies \& Practices:} Agile, Scrum, Requirements Analysis, Technical Documentation, Testing

\textbf{Soft Skills:} Communication, Collaboration, Analytical Thinking, Adaptability, Problem Solving, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js to support data-driven business operations.
\item Built and optimized SQL queries and RESTful APIs to improve data retrieval performance and ensure system reliability.
\item Deployed cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and scalability.
\item Collaborated with cross-functional teams through Agile sprints and code reviews to deliver high-quality technical solutions.
\item Documented reporting logic, data workflows, and technical processes to support transparency and knowledge transfer.
\item Led backend development initiatives while mentoring junior developers on best practices in coding and deployment.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to enterprise-level web applications focusing on data integration and backend component development.
\item Assisted in designing the Proposal Management System and Mailroom Tracking System with reporting capabilities.
\item Worked closely with cross-functional teams to gather requirements, perform testing, and support deployment phases.
\item Gained hands-on experience analyzing datasets, building technical reports, and supporting data accuracy initiatives.
\item Participated in project reviews to identify improvements in performance, scalability, and data integrity.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with notes, videos, quizzes, and real-time performance dashboards.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL to support data-driven online education.
\item Integrated performance tracking dashboards with visualizations enabling teachers to monitor student progress in real time.
\item Implemented secure authentication, role-based access, and optimized database queries for high concurrent usage.
\item Deployed the platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 students.
\end{itemize}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Automated vulnerability scanning and patching workflows to strengthen enterprise security and reduce manual effort.
\vspace{-1pt}
\begin{itemize}
\item Developed automated workflows using Python and Jenkins for vulnerability scanning and patch deployment across systems.
\item Integrated Nessus API for real-time vulnerability reporting and risk prioritization to support compliance initiatives.
\item Created dashboards and alert systems to track security compliance, remediation progress, and reporting accuracy.
\item Reduced manual intervention by 60\% and accelerated patch cycles through full CI/CD automation and documentation.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}