% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Web Developer with hands-on experience building scalable web applications using React, Node.js, and modern JavaScript frameworks. Skilled in Agile methodologies, RESTful API development, and cloud deployment using AWS and Docker. Proven ability to collaborate across teams throughout the SDLC, translating technical specifications into high-quality, tested applications. Experienced in frontend optimization, responsive design, version control, and implementing secure authentication systems with strong problem-solving and communication skills.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Frontend Development:} React, TypeScript, JavaScript, HTML5, CSS3, Bootstrap

\textbf{Backend \& APIs:} Node.js, RESTful APIs, Express.js, GraphQL, Next.js, API Security

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQL, Redis

\textbf{Cloud \& DevOps:} AWS, Azure, Docker, CI/CD, GitHub Actions, Kubernetes

\textbf{Development Practices:} Agile, Scrum, Kanban, Unit Testing, TDD, Version Control

\textbf{Architecture \& Design:} Microservices, MVC, Design Patterns, System Design, Scalability

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Ownership, Documentation

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Built scalable full stack applications with React, TypeScript, and Node.js, delivering responsive UI and optimized user experiences.
\item Developed and tested RESTful APIs ensuring secure data flow, input validation, and seamless integration with frontend components.
\item Deployed cloud applications on AWS using Docker containers and CI/CD pipelines, maintaining 99.8\% uptime and rapid iteration cycles.
\item Participated in Agile ceremonies including sprint planning, code reviews, and retrospectives to deliver features on tight deadlines.
\item Applied unit testing and debugging best practices throughout SDLC, reducing production bugs and improving application maintainability.
\item Mentored junior team members on modern development patterns, secure coding standards, and version control workflows using Git.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to full stack development for enterprise applications, implementing features across frontend and backend using Agile workflows.
\item Collaborated with cross-functional teams to gather requirements, perform functional testing, and support application deployment phases.
\item Assisted in building Proposal Management and Mailroom Tracking Systems with responsive design and optimized database queries.
\item Gained practical experience in structured development methodologies including code reviews, debugging, and technical documentation creation.
\item Supported troubleshooting efforts during testing and production, resolving technical issues to ensure smooth application operation.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Designed and deployed a full stack LMS using React and Node.js, serving 6,000+ students with secure authentication and real-time tracking.
\vspace{-1pt}
\begin{itemize}
\item Built responsive frontend with React and TypeScript, delivering interactive dashboards for students and teachers with optimized page load.
\item Developed RESTful APIs using Node.js and Express.js, handling lesson uploads, quiz submissions, and real-time progress tracking.
\item Integrated secure JWT-based authentication and role-based access control, ensuring data privacy and user-specific content delivery.
\item Deployed on AWS with CloudFront CDN and SSL encryption, supporting 6,000+ concurrent users with minimal latency and high availability.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Created accessible real-time chat app using React, Node.js, and Socket.io with voice-to-text and text-to-speech for inclusive communication.
\vspace{-1pt}
\begin{itemize}
\item Developed real-time messaging with React frontend and Node.js backend, integrating WebSockets for low-latency message delivery.
\item Integrated Azure Speech Services and AWS Polly APIs, enabling text-to-speech and voice-to-text features for low-vision users.
\item Implemented WCAG-compliant UI with responsive design, high-contrast themes, and keyboard navigation for assistive technology compatibility.
\item Deployed using Docker containers on AWS App Runner with autoscaling, ensuring reliable performance during peak usage periods.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}