% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Developer with proven expertise in designing and delivering scalable web applications using React, JavaScript, TypeScript, and Python. Skilled in building RESTful APIs, microservices, and database-driven solutions with PostgreSQL, MySQL, and MongoDB. Experienced in cloud deployment with AWS and GCP, CI/CD automation using Docker and GitHub Actions, and collaborating within Agile teams to deliver high-quality, maintainable code aligned with modern development best practices.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, SQL, HTML5, CSS3

\textbf{Frontend Development:} React, Redux, Angular, Bootstrap, Material UI, SASS

\textbf{Backend Development:} Flask, FastAPI, Django, Node.js, REST API, Microservices

\textbf{Database Management:} PostgreSQL, MySQL, MongoDB, SQLite, Firebase

\textbf{Cloud \& DevOps:} AWS, Azure, GCP, Docker, Kubernetes, CI/CD

\textbf{Version Control \& Tools:} Git, GitHub, GitLab, Jenkins, GitHub Actions, Jira

\textbf{Security \& Authentication:} OAuth, JWT, API Security, OWASP, Encryption

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Problem Solving, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using React, JavaScript, TypeScript, and Node.js to enhance platform functionality.
\item Designed and integrated RESTful APIs and microservices optimizing backend performance and ensuring seamless system communication.
\item Managed PostgreSQL and MySQL databases with optimized queries and indexing improving data retrieval speed and reliability.
\item Deployed cloud-based applications on AWS using Docker containers and CI/CD pipelines ensuring consistent uptime and availability.
\item Collaborated within Agile teams through code reviews, sprint planning, and testing to deliver high-quality maintainable solutions.
\item Applied secure coding standards, unit testing, and debugging throughout SDLC reducing production issues and enhancing performance.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing full stack web applications using React and Python contributing to both frontend and backend components.
\item Participated in designing and implementing REST APIs and database-driven features for enterprise management systems.
\item Worked closely with cross functional teams in Agile workflows to gather requirements, perform testing, and support deployment.
\item Gained hands-on experience with Git version control, CI/CD practices, and containerization tools for streamlined development.
\item Collaborated in code reviews and project assessments to identify improvements in scalability, performance, and code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS using React, Node.js, and MySQL enabling 6K+ students to access lessons, quizzes, and performance tracking.
\vspace{-1pt}
\begin{itemize}
\item Developed full stack LMS using React, Node.js, and MySQL with responsive UI and role-based access for teachers and students.
\item Designed RESTful APIs for lesson uploads, quiz management, and real-time progress dashboards with optimized database queries.
\item Implemented secure authentication using JWT and OAuth ensuring data privacy and controlled access across user roles.
\item Deployed on AWS with Docker, CDN caching, and SSL encryption supporting reliable access for over 6,000 concurrent users.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive real-time chat application integrating text-to-speech and voice-to-text for low-vision and reading-challenged users.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Node.js, and WebSockets with accessibility-focused UI following WCAG standards.
\item Integrated AWS and Azure speech services enabling text-to-speech and voice-to-text communication for inclusive user experience.
\item Conducted extensive testing with assistive technologies ensuring compliance with accessibility best practices and usability standards.
\item Deployed scalable solution on AWS using Docker containers ensuring low-latency communication and high availability for all users.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}