% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with 5+ years of experience specializing in frontend and full stack development using JavaScript, TypeScript, React, and Node.js. Proven expertise in building scalable web applications, implementing CI/CD pipelines, and deploying cloud-based solutions on AWS and Azure. Strong background in Agile methodologies, API development, and secure coding practices with hands-on experience in Docker, MongoDB, and modern testing frameworks.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, PHP, SQL, HTML5, CSS3

\textbf{Frontend Frameworks \& Libraries:} React, Vue.js, Redux, Bootstrap, Material UI, SASS

\textbf{Backend \& API Development:} Node.js, Express.js, REST API, GraphQL, MongoDB, PostgreSQL

\textbf{Cloud \& DevOps:} Azure DevOps, AWS, Docker, CI/CD, GitHub Actions, Kubernetes

\textbf{Testing \& Quality Assurance:} Postman, Unit Testing, Integration Testing, TDD, Automation Testing

\textbf{Architecture \& Design:} Microservices, Design Patterns, System Design, Scalability, Performance Optimization

\textbf{Agile \& Collaboration:} Agile, Scrum, Jira, Code Reviews, Technical Documentation

\textbf{Soft Skills:} Communication, Team Collaboration, Problem Solving, Adaptability, Continuous Learning, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable web applications using JavaScript, TypeScript, React, and Node.js to enhance e-commerce functionality and user experience.
\item Designed and implemented RESTful APIs with Express.js and optimized MongoDB and SQL queries improving system performance by 40\%.
\item Deployed cloud-based applications using AWS, Docker, and Azure DevOps CI/CD pipelines ensuring 99.9\% uptime and consistent availability.
\item Collaborated within Agile teams conducting code reviews, sprint planning, and pair programming to deliver high-quality software solutions.
\item Applied test-driven development using Postman and unit testing frameworks throughout SDLC reducing production defects significantly.
\item Led backend development for multiple applications while mentoring junior developers on coding standards, security, and DevOps practices.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications using JavaScript, React, and Node.js across frontend and backend components.
\item Contributed to design and implementation of Proposal Management and Mailroom Tracking Systems with secure database integration.
\item Worked closely with cross-functional teams to gather requirements, perform testing, and support deployment in Agile workflows.
\item Gained hands-on experience in full stack development, API testing with Postman, and secure coding within CI/CD environments.
\item Collaborated in project reviews to identify improvements in performance, scalability, and code maintainability across applications.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS using React, Node.js, and MongoDB enabling 6K+ students to learn with interactive quizzes and real-time tracking.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed full stack LMS using React, Node.js, Express.js, and MongoDB supporting online education during the pandemic.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time progress dashboards using RESTful APIs.
\item Implemented secure authentication with JWT, role-based access control, and optimized database queries for high concurrent usage.
\item Deployed platform on AWS with Docker containers, CDN caching, and SSL encryption ensuring reliable access for over 6,000 students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed inclusive chat app using React, Node.js, and WebSockets for low-vision users integrating text-to-speech accessibility.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Node.js, and WebSockets with accessibility-focused UI design and responsive layout.
\item Integrated Azure Speech Services and AWS Polly to enable text-to-speech and voice-to-text communication for inclusive usability.
\item Followed WCAG accessibility standards and tested with assistive technologies ensuring compliance and enhanced user experience.
\item Deployed on AWS using Docker containers and CI/CD pipelines for scalable, low-latency communication and continuous delivery.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}