% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with expertise in threat intelligence, malware analysis, and cybersecurity automation. Proficient in Python scripting, MITRE ATT\&CK framework, and leveraging tools such as BigQuery for data-driven threat hunting and incident response. Experienced in developing secure, scalable applications and implementing security best practices across cloud environments. Skilled in collaborating with cross-functional teams to deliver actionable intelligence and enhance detection capabilities.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming \& Scripting:} Python, JavaScript, Bash, PowerShell, SQL

\textbf{Threat Intelligence \& Security:} MITRE ATT\&CK, Malware Analysis, Threat Hunting, SIEM, Incident Response, Digital Forensics

\textbf{Data Analysis \& Platforms:} BigQuery, pandas, SQL Server, PostgreSQL, MySQL

\textbf{Cloud \& Infrastructure:} AWS, GCP, Docker, Kubernetes, CI/CD Pipelines

\textbf{Security Tools \& Practices:} Vulnerability Management, Risk Assessments, OWASP, Encryption, OAuth, IAM

\textbf{Systems \& Networking:} Linux, Windows Server, Networking Principles, VPN, Active Directory

\textbf{Soft Skills:} Analytical Thinking, Communication, Collaboration, Adaptability, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using Python, JavaScript, and React to enhance system functionality and security.
\item Implemented secure RESTful APIs, optimized SQL queries, and integrated authentication systems improving reliability and performance.
\item Deployed and maintained cloud-based solutions using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and availability.
\item Collaborated within Agile teams through code reviews, sprint planning, and technical documentation to ensure high-quality deliverables.
\item Applied secure coding standards, vulnerability management, and testing throughout SDLC reducing production issues significantly.
\item Led backend development initiatives while mentoring junior developers on security best practices and deployment methodologies.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications focusing on secure coding and threat mitigation across frontend and backend.
\item Contributed to design and implementation of tracking systems integrating security controls and vulnerability assessments.
\item Worked closely with cross-functional teams to gather requirements, perform security testing, and support deployment phases.
\item Gained hands-on experience in full stack development, incident response workflows, and secure coding within Agile environments.
\item Collaborated in project reviews to identify improvements in performance, scalability, security posture, and code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic }

\vspace{-1pt}

Automated vulnerability scanning and patching workflows to strengthen enterprise security posture and reduce manual intervention.
\vspace{-1pt}
\begin{itemize}
\item Developed automated workflows using Python and Jenkins for vulnerability scanning, risk prioritization, and patch deployment.
\item Integrated Nessus API for real-time vulnerability reporting, threat analysis, and security compliance tracking across systems.
\item Created dashboards and alert systems to track remediation progress, security metrics, and compliance with security frameworks.
\item Reduced manual intervention by 60\% and accelerated patch cycles through full CI/CD automation improving overall security posture.
\end{itemize}

\textbf{Automated Cryptocurrency Trading Bot} -- \emph{Personal Project}

\vspace{-1pt}

Created a Python trading bot using Binance API and WebSocket to automate execution with risk control and real-time monitoring.
\vspace{-1pt}
\begin{itemize}
\item Developed a fully automated trading bot in Python using Binance API and WebSocket for real-time data streaming and analysis.
\item Implemented dynamic trading strategies, stop-loss mechanisms, and order execution algorithms for risk management and control.
\item Integrated Pandas and NumPy for market analysis, backtesting, and data-driven decision making to improve trading accuracy.
\item Deployed using Docker on AWS EC2 for 24/7 uptime, reliability, and monitoring with detailed logging and alerting capabilities.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}