% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Developer with expertise in Python, FastAPI, Vue.js, and Azure cloud technologies, specializing in scalable AI-driven web applications and microservices architecture. Proven experience designing and deploying enterprise solutions using React, Django, and modern JavaScript frameworks, with hands-on proficiency in Docker, Kubernetes, and CI/CD automation. Adept at translating complex technical solutions into business value while collaborating across cross-functional teams in Agile environments.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, TypeScript, SQL, HTML5, CSS3, PHP, Bash

\textbf{Frameworks \& Libraries:} FastAPI, Vue.js, React, Django, Flask, Node.js, Redux, Bootstrap

\textbf{Database \& Data Management:} Azure SQL, PostgreSQL, MySQL, MongoDB, Redis, DynamoDB

\textbf{Cloud \& DevOps:} Microsoft Azure, AKS, Docker, Kubernetes, CI/CD, GitHub Actions

\textbf{AI \& Machine Learning:} AI Integration, LLM API, ChatGPT API, Prompt Engineering, RAG Pipelines, ML APIs

\textbf{Development Practices:} Agile, Scrum, Microservices, REST API, Unit Testing, TDD

\textbf{Security \& Architecture:} OAuth, JWT, API Security, Clean Architecture, Scalability, Performance Optimization

\textbf{Soft Skills:} Leadership, Mentorship, Communication, Problem Solving, Team Collaboration, Adaptability

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using JavaScript, React, and Node.js delivering enterprise-grade e-commerce solutions.
\item Architected and implemented RESTful APIs with optimized database queries ensuring high performance and system reliability.
\item Deployed cloud-based solutions using AWS, Docker, and CI/CD pipelines maintaining consistent uptime and availability standards.
\item Collaborated in Agile teams through code reviews, sprint planning, and pair programming to deliver high-quality software.
\item Applied test-driven development and secure coding practices throughout SDLC reducing production issues and technical debt.
\item Led backend development for multiple applications while mentoring junior developers on best practices and deployment strategies.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web and mobile applications across frontend and backend components in Agile workflows.
\item Contributed to design and implementation of Proposal Management and Mailroom Tracking Systems with full stack technologies.
\item Worked closely with cross-functional teams to gather requirements, perform testing, and support deployment phases.
\item Gained hands-on experience in full stack development, software testing, and secure coding practices within team environments.
\item Collaborated in project reviews to identify performance improvements, scalability enhancements, and code maintainability strategies.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL supporting online education for thousands of students.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time progress dashboards for educators.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent user traffic.
\item Deployed the platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 active students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users and individuals with reading challenges, integrating accessibility features.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and Socket.io with accessibility-focused UI adhering to WCAG standards.
\item Integrated Azure Speech Services and AWS Polly to enable text-to-speech and voice-to-text communication for inclusive usability.
\item Followed WCAG accessibility guidelines and tested with assistive technologies ensuring compliance and user-centric design.
\item Deployed on AWS App Runner with Docker containers delivering scalable, low-latency communication for diverse user needs.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}