% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with 5+ years of experience designing and delivering scalable, enterprise-level solutions across cloud platforms and distributed systems. Proven expertise in full stack development with React, Node.js, Python, and Django, alongside strong DevOps capabilities using AWS, Docker, Kubernetes, and CI/CD pipelines. Skilled in microservices architecture, RESTful and GraphQL APIs, and Infrastructure as Code with Terraform and CloudFormation. Experienced collaborating with cross functional teams in Agile environments to deliver secure, high-performance applications. Passionate about technical leadership, mentorship, and driving architectural best practices.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, TypeScript, PHP, SQL, Bash

\textbf{Frontend Technologies:} React, Redux, Bootstrap, Material UI, HTML5, CSS3

\textbf{Backend \& APIs:} Node.js, Django, Flask, FastAPI, REST API, GraphQL

\textbf{Cloud Platforms \& Infrastructure:} AWS, GCP, Azure, Terraform, CloudFormation, Serverless

\textbf{DevOps \& Orchestration:} Docker, Kubernetes, CI/CD, Jenkins, GitHub Actions, Infrastructure as Code

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, DynamoDB, Redis, ETL Pipelines

\textbf{Architecture \& Integration:} Microservices, Event-Driven Architecture, API Gateway, Clean Architecture, Design Patterns

\textbf{Security \& Compliance:} OAuth, JWT, IAM, Encryption, OWASP, Zero Trust Architecture

\textbf{Soft Skills:} Technical Leadership, Communication, Collaboration, Mentorship, Adaptability, Problem Solving

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using React, Node.js, and RESTful APIs to deliver robust e-commerce solutions.
\item Designed and implemented microservices architecture with secure authentication and optimized database queries for performance.
\item Deployed cloud-based solutions on AWS using Docker, Kubernetes, and CI/CD pipelines ensuring high availability and reliability.
\item Collaborated with cross functional Agile teams through code reviews, sprint planning, and technical documentation practices.
\item Applied Infrastructure as Code principles and DevOps best practices to automate deployment and monitoring workflows.
\item Mentored junior developers on software architecture, secure coding standards, and deployment strategies across SDLC phases.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level web applications across frontend and backend components using modern frameworks.
\item Contributed to architecture design and implementation of Proposal Management and Mailroom Tracking Systems for clients.
\item Collaborated with stakeholders and delivery teams to gather requirements, perform integration testing, and support rollouts.
\item Gained hands-on experience in full stack development, secure coding, and Agile workflows within enterprise environments.
\item Participated in architecture reviews to identify performance improvements, scalability enhancements, and maintainability standards.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes.
\vspace{-1pt}
\begin{itemize}
\item Designed end-to-end solution architecture using React, Node.js, and MySQL to support scalable online education delivery.
\item Integrated real-time dashboards, role-based access, and performance tracking with secure authentication and data encryption.
\item Optimized database queries and implemented caching strategies to handle high concurrent usage with minimal latency.
\item Deployed on AWS with CloudFormation, CDN caching, and SSL encryption ensuring reliable access for over 6,000 students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users and individuals with reading challenges, integrating accessibility features.
\vspace{-1pt}
\begin{itemize}
\item Architected real-time communication solution using React, Node.js, and Socket.io with WCAG compliant UI design principles.
\item Integrated AWS Polly and Azure Speech Services APIs to enable text-to-speech and voice-to-text accessibility features.
\item Designed event-driven architecture for low-latency messaging and tested with assistive technologies for inclusive usability.
\item Deployed using Docker containers on AWS App Runner with autoscaling and monitoring for scalable, reliable communication.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}