% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Software Engineer with hands-on experience building scalable full stack systems using TypeScript, Node.js, and cloud infrastructure. Skilled in architecting distributed services, integrating APIs, and deploying production-grade solutions on AWS with Docker and CI/CD pipelines. Proficient in implementing event-driven architectures, optimizing system performance, and ensuring high reliability in cloud environments. Experienced collaborating in Agile teams and delivering end-to-end product-facing systems.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} TypeScript, JavaScript, Python, SQL, HTML, CSS, Bash, PowerShell

\textbf{Frameworks \& Libraries:} Node.js, React, Express.js, Django, Flask, Bootstrap

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, Redis, DynamoDB, SQLite

\textbf{Cloud \& DevOps:} AWS, EKS, Docker, Kubernetes, CI/CD, Terraform, CloudWatch

\textbf{APIs \& Architecture:} REST API, GraphQL, Microservices, Event-Driven Architecture, Serverless

\textbf{AI \& Integration:} LLM API, ChatGPT API, Prompt Engineering, AI Integration, Workflow Automation

\textbf{Monitoring \& Observability:} CloudWatch, Logging, Monitoring, Performance Optimization, Load Testing

\textbf{Soft Skills:} Ownership, Collaboration, Adaptability, Communication, Problem Solving, Team Leadership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Built production-grade full stack applications using JavaScript, React, and Node.js to deliver scalable e-commerce solutions.
\item Designed RESTful APIs and optimized backend services in Node.js with PostgreSQL and MySQL improving reliability and latency.
\item Deployed distributed services on AWS using Docker, Kubernetes, and CI/CD pipelines ensuring high availability and uptime.
\item Integrated secure payment systems and implemented OAuth, JWT, and API security protocols reducing vulnerabilities by 40\%.
\item Collaborated in Agile teams through sprint planning, code reviews, and pair programming to ship high-quality features quickly.
\item Mentored junior engineers on architecture design, best coding practices, and deployment workflows in cloud environments.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to full stack development of enterprise applications building frontend interfaces and backend APIs using Node.js.
\item Participated in the design and implementation of real-time Proposal Management and Mailroom Tracking Systems using React.
\item Worked with cross-functional teams to gather requirements, conduct integration testing, and support production deployments.
\item Applied Agile methodologies and secure coding standards throughout SDLC improving code maintainability and system performance.
\item Collaborated in sprint reviews to identify scalability improvements and optimize database queries for better application speed.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS supporting 6K+ students with real-time progress tracking, quizzes, and video lessons on AWS infrastructure.
\vspace{-1pt}
\begin{itemize}
\item Architected and developed a full stack LMS using React, Node.js, and MySQL with modules for lessons, quizzes, and dashboards.
\item Implemented secure authentication, role-based access control, and optimized SQL queries for high concurrent user traffic.
\item Deployed on AWS with CloudFront CDN, SSL encryption, and autoscaling ensuring reliable access for over 6,000 active students.
\item Integrated real-time progress tracking for teachers with APIs and WebSocket connections to monitor student performance instantly.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic }

\vspace{-1pt}

Developed an inclusive real-time chat app with text-to-speech and voice-to-text features for low-vision users and accessibility.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and Socket.io with WCAG-compliant UI for accessibility-focused design.
\item Integrated AWS Polly and Azure Speech Services to enable bidirectional text-to-speech and voice-to-text communication features.
\item Tested with assistive technologies and screen readers to ensure inclusive usability for users with visual and reading challenges.
\item Deployed on AWS App Runner with Docker containers for scalable, low-latency real-time messaging and high system reliability.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}