% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Full Stack Software Engineer with proven expertise in building secure, scalable web applications using Python, Django, React, and JavaScript. Demonstrated experience implementing RESTful APIs, cloud infrastructure on AWS and GCP, and automated CI/CD pipelines. Strong foundation in web security principles including OWASP, authentication systems, and secure coding practices. Adept at collaborating in distributed Agile teams and contributing to open development workflows while maintaining high code quality standards.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, TypeScript, SQL, HTML5, CSS3, Bash, PowerShell

\textbf{Frameworks \& Libraries:} React, Django, Flask, Node.js, Bootstrap, Redux

\textbf{Database \& Cloud Infrastructure:} MySQL, PostgreSQL, MongoDB, Google Cloud Platform, AWS, Docker

\textbf{DevOps \& Security:} CI/CD, Kubernetes, GitHub Actions, GitLab CI/CD, OWASP, OAuth, JWT

\textbf{Security \& Monitoring:} Web Security, Incident Response, Threat Intelligence, Vulnerability Management, SIEM, Cloud Monitoring

\textbf{Development Practices:} Agile, Scrum, Code Reviews, Test-Driven Development, System Design, Technical Documentation

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Problem Solving, Ownership, Mentorship

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed secure full stack web applications using JavaScript, React, Django, and Node.js to enhance platform functionality and user experience.
\item Implemented RESTful APIs with authentication systems using OAuth and JWT while optimizing MySQL queries to improve system reliability.
\item Deployed cloud-based applications using AWS, Docker, and CI/CD pipelines with monitoring systems ensuring consistent platform availability.
\item Collaborated within distributed Agile teams through code reviews, sprint planning, and pair programming to deliver high-quality features.
\item Applied secure coding standards and test-driven development throughout SDLC reducing production issues and improving code maintainability.
\item Led backend development initiatives while mentoring junior developers on security best practices, deployment workflows, and coding standards.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level web applications across frontend and backend components using modern development frameworks.
\item Contributed to design and implementation of management systems while ensuring adherence to security principles and coding standards.
\item Worked closely with cross functional teams to gather requirements, perform testing, and support deployment phases in Agile environment.
\item Gained hands-on experience in full stack development, software testing, and secure coding practices within collaborative team workflows.
\item Collaborated in project reviews to identify improvements in performance, scalability, security compliance, and overall code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Automated vulnerability scanning and patching workflows to strengthen enterprise security posture and reduce manual remediation effort.
\vspace{-1pt}
\begin{itemize}
\item Developed automated security workflows using Python and Jenkins for continuous vulnerability scanning and patch deployment cycles.
\item Integrated Nessus API for real-time vulnerability reporting, risk prioritization, and compliance tracking across enterprise infrastructure.
\item Created monitoring dashboards and alert systems to track security compliance metrics and accelerate incident response and remediation.
\item Reduced manual security intervention by 60\% and accelerated patch cycles through full CI/CD automation and orchestration frameworks.
\end{itemize}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to access educational content with secure authentication and real-time progress tracking.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack LMS using React, Node.js, and MySQL with secure authentication and role-based access control for multiple user types.
\item Integrated modules for lesson uploads, interactive quizzes, and performance tracking with real-time dashboards for instructors and students.
\item Implemented web security best practices including input validation, SQL injection prevention, and encrypted data transmission protocols.
\item Deployed platform on AWS with CDN caching, SSL encryption, and monitoring systems ensuring reliable access for over 6,000 concurrent users.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}