% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with hands-on experience in cloud infrastructure, DevOps automation, and production systems. Skilled in AWS services including EC2, RDS, S3, and IAM, alongside Kubernetes, Docker, and CI/CD pipeline orchestration. Proven ability to build scalable infrastructure using Terraform and automation tools while collaborating cross-functionally to deliver reliable, high-performance platforms. Strong foundation in monitoring, system design, and cloud-native architectures.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud \& Infrastructure:} AWS (EC2, RDS, S3, IAM, Lambda), Kubernetes, Docker, Terraform, CloudFormation, Infrastructure as Code

\textbf{DevOps \& Automation:} CI/CD Pipelines, GitHub Actions, GitLab CI/CD, Jenkins, Continuous Integration, Release Management

\textbf{Monitoring \& Observability:} CloudWatch, Cloud Monitoring, Logging, Autoscaling, Load Balancing, High Availability

\textbf{Programming \& Scripting:} Python, Bash, JavaScript, PowerShell, Shell Scripting, Automation

\textbf{Databases \& Networking:} PostgreSQL, MySQL, MongoDB, VPC, Cloud Networking, API Gateway

\textbf{Development Practices:} Agile, Scrum, System Design, Code Reviews, Technical Documentation, Performance Optimization

\textbf{Soft Skills:} Collaboration, Communication, Problem Solving, Adaptability, Ownership, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Deployed and maintained cloud-based applications using AWS services, Docker containers, and CI/CD pipelines ensuring 99.9\% uptime.
\item Automated infrastructure provisioning and configuration management improving deployment consistency and reducing manual effort by 40\%.
\item Implemented monitoring, logging, and alerting systems using CloudWatch to proactively identify and resolve production incidents.
\item Optimized containerized application performance and resource utilization across Kubernetes clusters for cost efficiency and scalability.
\item Collaborated with development and QA teams through Agile sprints to support reliable feature delivery and infrastructure improvements.
\item Led backend infrastructure enhancements while mentoring team members on DevOps best practices and cloud-native architecture design.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in deploying enterprise applications using cloud infrastructure and automated testing frameworks within Agile workflows.
\item Contributed to CI/CD pipeline configuration and deployment automation for multiple internal systems and client-facing applications.
\item Worked closely with cross-functional teams to gather infrastructure requirements, perform load testing, and support production releases.
\item Gained hands-on experience in cloud services, containerization, scripting, and infrastructure monitoring to ensure system reliability.
\item Participated in project reviews to identify opportunities for performance tuning, scalability improvements, and operational efficiency.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS on AWS supporting 6K+ students with optimized infrastructure, secure authentication, and CDN caching for reliability.
\vspace{-1pt}
\begin{itemize}
\item Architected and deployed a highly available LMS on AWS using EC2, RDS, and S3 with auto-scaling and load balancing configurations.
\item Implemented secure IAM policies, SSL encryption, and role-based access control to protect user data and ensure compliance standards.
\item Optimized database queries and integrated CDN caching to reduce latency and support high concurrent user loads during peak usage.
\item Automated infrastructure provisioning using Infrastructure as Code practices and monitored system health using CloudWatch dashboards.
\end{itemize}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Automated vulnerability scanning and patching workflows using Python, Jenkins, and Nessus API to strengthen enterprise security posture.
\vspace{-1pt}
\begin{itemize}
\item Developed automated CI/CD workflows using Jenkins and Python scripts for vulnerability scanning, reporting, and patch deployment cycles.
\item Integrated Nessus API for real-time vulnerability detection, risk prioritization, and compliance tracking across enterprise infrastructure.
\item Created monitoring dashboards and alert systems to track security remediation progress and ensure timely response to critical vulnerabilities.
\item Reduced manual intervention by 60\% and accelerated patch deployment through full automation and orchestration of security operations.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}