% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with 2+ years of experience in DevOps, cloud infrastructure, and full stack development. Proven expertise in AWS, Terraform, Docker, and CI/CD automation using Jenkins and GitHub Actions. Skilled in building scalable, cloud-native applications and supporting real-time systems in Linux environments. Strong foundation in infrastructure as code, containerization, and automated workflows with a passion for reliability engineering and system optimization.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud \& Infrastructure:} AWS (EC2, S3, RDS, Lambda), Terraform, CloudFormation, Docker, Kubernetes

\textbf{DevOps \& Automation:} Jenkins, GitHub Actions, GitLab CI/CD, Ansible, Infrastructure as Code, CI/CD Pipelines

\textbf{Monitoring \& Observability:} CloudWatch, Logging, Cloud Monitoring, Performance Optimization, Autoscaling

\textbf{Programming \& Scripting:} Python, Bash, PowerShell, JavaScript, Node.js

\textbf{Systems \& Architecture:} Linux, Serverless, Event-Driven Architecture, Microservices, System Design

\textbf{Development Practices:} Agile, Scrum, SDLC, Code Reviews, Technical Documentation

\textbf{Soft Skills:} Problem Solving, Team Collaboration, Communication, Adaptability, Continuous Learning, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Deployed and maintained cloud-based applications on AWS using Docker, Terraform, and CI/CD pipelines ensuring high availability.
\item Automated infrastructure provisioning and configuration management reducing deployment time and improving system reliability.
\item Developed scalable full stack applications using JavaScript, React, and Node.js optimized for performance under high traffic.
\item Implemented RESTful APIs and optimized database queries enhancing application responsiveness and real-time data processing.
\item Collaborated within Agile teams through code reviews, sprint planning, and cross-functional communication ensuring quality delivery.
\item Applied Infrastructure as Code principles and secure coding standards throughout SDLC reducing production incidents and downtime.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications with frontend and backend components deployed on cloud infrastructure platforms.
\item Contributed to system design and implementation while gaining hands-on experience with CI/CD automation and containerized deployments.
\item Worked with cross-functional teams to gather requirements, perform testing, and support deployment phases in Agile environments.
\item Supported monitoring and logging implementation to track application health and performance across development and production systems.
\item Collaborated in project reviews identifying optimization opportunities for performance, scalability, and maintainability improvements.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic }

\vspace{-1pt}

Automated vulnerability scanning and patching workflows reducing manual effort and accelerating remediation cycles for enterprise security.
\vspace{-1pt}
\begin{itemize}
\item Developed automated workflows using Python and Jenkins for vulnerability scanning, patch deployment, and compliance tracking.
\item Integrated Nessus API for real-time vulnerability reporting, risk prioritization, and automated alert generation for security teams.
\item Created monitoring dashboards for tracking security compliance, patch status, and remediation progress across enterprise infrastructure.
\item Reduced manual intervention by 60\% and accelerated patch cycles through full CI/CD automation and infrastructure orchestration.
\end{itemize}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to access educational content with real-time performance tracking and secure authentication.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL optimized for high concurrent usage and real-time updates.
\item Implemented secure authentication, role-based access control, and optimized database queries for reliable performance under load.
\item Deployed the platform on AWS with CDN caching, SSL encryption, and autoscaling ensuring uptime for over 6,000 concurrent users.
\item Integrated real-time dashboards for performance tracking enabling teachers to monitor student progress and engagement metrics instantly.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}