% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with hands-on experience in cloud infrastructure, automation, and platform reliability. Proven expertise building scalable systems using Docker, Kubernetes, AWS, and CI/CD pipelines. Strong foundation in scripting with Python, Bash, and PowerShell to eliminate toil and improve operational efficiency. Experienced collaborating across teams in Agile environments to deliver resilient, secure, and maintainable solutions that support business growth and system scalability.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming \& Scripting:} Python, Bash, PowerShell, JavaScript, SQL

\textbf{Cloud \& Infrastructure:} AWS, Microsoft Azure, GCP, Terraform, Infrastructure as Code

\textbf{Containerization \& Orchestration:} Docker, Kubernetes, Autoscaling, Cloud Networking

\textbf{CI/CD \& Automation:} GitHub Actions, GitLab CI/CD, Jenkins, Release Management, Continuous Deployment

\textbf{Monitoring \& Observability:} Logging, Monitoring, CloudWatch, Cloud Monitoring

\textbf{Security \& Compliance:} IAM, Encryption, API Security, OWASP, Incident Response

\textbf{Systems \& Networking:} Linux, Ubuntu, Networking principles, Load Balancing, VPN

\textbf{Soft Skills:} Collaboration, Communication, Problem Solving, Adaptability, Ownership, Mentorship

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Deployed and maintained cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and reliability.
\item Automated infrastructure provisioning and configuration management reducing manual toil and accelerating deployment cycles.
\item Implemented monitoring, logging, and alerting solutions to improve observability and support proactive incident response.
\item Collaborated across Agile teams through code reviews, sprint planning, and technical documentation to deliver resilient systems.
\item Optimized cloud resource usage and applied security best practices including IAM, encryption, and secure API design.
\item Led backend development efforts and mentored junior developers on automation, scalability, and cloud-native best practices.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing scalable web applications with focus on performance, reliability, and security across deployment phases.
\item Contributed to system design, testing, and deployment automation within Agile workflows and cross-functional collaboration.
\item Worked with cloud infrastructure and CI/CD pipelines to support continuous integration and deployment of enterprise systems.
\item Gained hands-on experience in scripting, configuration management, and infrastructure automation to reduce operational overhead.
\item Participated in code reviews and technical retrospectives to identify improvements in system scalability and maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes.
\vspace{-1pt}
\begin{itemize}
\item Designed and deployed a full-stack LMS using React, Node.js, and MySQL with cloud infrastructure on AWS for scalability.
\item Implemented secure authentication, role-based access, and optimized database queries to support high concurrent user loads.
\item Deployed platform with CDN caching, SSL encryption, and autoscaling to ensure reliable access for over 6,000 students.
\item Integrated real-time dashboards for performance tracking and built automated monitoring to ensure system uptime and health.
\end{itemize}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Automated vulnerability scanning and patching to strengthen enterprise security and reduce manual effort.
\vspace{-1pt}
\begin{itemize}
\item Developed automated workflows using Python and Jenkins for vulnerability scanning, patch deployment, and compliance tracking.
\item Integrated Nessus API for real-time vulnerability reporting, risk prioritization, and automated remediation workflows.
\item Created dashboards and alert systems to track security posture, remediation progress, and improve operational visibility.
\item Reduced manual intervention by 60\% and accelerated patch cycles through full CI/CD automation and orchestration.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}