% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Developer with expertise in Python, JavaScript, and modern web technologies. Skilled in building scalable applications using React, Django, and Node.js with strong experience in Docker, Kubernetes, and CI/CD pipelines. Proven ability to develop RESTful APIs, automate workflows, and deploy cloud-based solutions on AWS and GCP. Collaborative team player with hands-on experience in Agile environments, GitHub version control, and DevOps practices.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, PHP, SQL, HTML, CSS, Bash, PowerShell

\textbf{Frameworks \& Libraries:} React, Django, Flask, Node.js, Bootstrap, jQuery

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQLite, DynamoDB

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, GitHub Actions, CI/CD, Terraform

\textbf{Software Development Practices:} Agile, Scrum, SDLC, Testing, Debugging, Code Reviews

\textbf{Computer Science Fundamentals:} Data Structures, Algorithms, OOP, Design Patterns

\textbf{Systems \& Networking:} REST API, GraphQL, Automation, Unix/Linux, Security

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Problem Solving, Ownership, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed full stack web applications using JavaScript, React, and Node.js with RESTful APIs deployed via Docker and CI/CD pipelines.
\item Integrated secure payment systems and optimized SQL queries improving reliability and performance across e-commerce platforms.
\item Deployed cloud-based applications on AWS using Docker containers and GitHub Actions ensuring consistent uptime and availability.
\item Collaborated in Agile teams through code reviews, sprint planning, and pair programming to deliver high-quality solutions.
\item Applied test-driven development and secure coding practices throughout SDLC reducing production issues and improving maintainability.
\item Led backend development for Shopify applications mentoring junior developers on coding standards and deployment best practices.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications using Python and JavaScript across frontend and backend components.
\item Contributed to design and implementation of management systems working with APIs and database integrations.
\item Collaborated with cross-functional teams to gather requirements, perform testing, and support deployment phases.
\item Gained hands-on experience in full stack development, software testing, and secure coding within Agile workflows.
\item Participated in project reviews identifying improvements in performance, scalability, and code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic }

\vspace{-1pt}

Automated vulnerability scanning and patching to strengthen enterprise security and reduce manual effort using Python workflows.
\vspace{-1pt}
\begin{itemize}
\item Developed automated workflows using Python and Jenkins for vulnerability scanning and patch deployment in CI/CD pipelines.
\item Integrated Nessus API for real-time vulnerability reporting and risk prioritization with automated alert systems.
\item Created dashboards to track security compliance and remediation progress using Python-based data visualization tools.
\item Reduced manual intervention by 60\% and accelerated patch cycles through full automation and Docker containerization.
\end{itemize}

\textbf{Automated Cryptocurrency Trading Bot} -- \emph{Personal Project}

\vspace{-1pt}

Created a Python trading bot using Binance API and WebSocket to automate trade execution with real-time monitoring and logging.
\vspace{-1pt}
\begin{itemize}
\item Developed a fully automated trading bot in Python using Binance API and WebSocket for real-time data streaming and execution.
\item Implemented dynamic trading strategies, stop-loss mechanisms, and order execution algorithms with robust error handling.
\item Integrated Pandas and NumPy for market analysis and backtesting to improve trading accuracy and risk management.
\item Deployed using Docker on AWS EC2 for 24/7 uptime, reliability, and monitoring with detailed logging and alerting.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}