% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with hands-on experience in threat hunting, incident response, and security operations. Proficient in Python, PowerShell, Bash scripting, and SIEM platforms with demonstrated expertise in vulnerability management, malware analysis, and MITRE ATT\&CK framework. Proven track record in developing automated security workflows, digital forensics, and proactive threat detection within complex environments. Adept at collaboration and continuous learning.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Security Operations \& Threat Intelligence:} SIEM Platforms, Threat Hunting, Incident Response, Digital Forensics, MITRE ATT\&CK, Malware Analysis

\textbf{Scripting \& Automation:} Python, PowerShell, Bash, Shell Scripting, Automation, API Integration

\textbf{Vulnerability \& Risk Management:} Vulnerability Management Tools, Risk Assessments, Phishing Investigation, Sandbox Analysis, Compliance

\textbf{Systems \& Networking:} Active Directory, Networking Principles, Linux Administration, Windows Server, VPN, IAM

\textbf{Cloud \& DevOps:} AWS, Docker, CI/CD Pipelines, GitHub Actions, Infrastructure as Code, Monitoring

\textbf{Development \& Database:} SQL, PostgreSQL, MySQL, REST API, Node.js, React

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Problem Solving, Analytical Thinking, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed automated security workflows using Python and PowerShell to enhance threat detection and incident response capabilities.
\item Integrated SIEM platforms with RESTful APIs and optimized queries to identify anomalies and improve real-time monitoring coverage.
\item Deployed cloud-based security solutions using AWS, Docker, and CI/CD pipelines ensuring continuous uptime and secure configurations.
\item Collaborated within Agile teams through security reviews, sprint planning, and cross-functional alignment to ensure compliance.
\item Applied secure coding standards, vulnerability assessments, and proactive threat modeling throughout SDLC to reduce risk exposure.
\item Led backend security automation initiatives while mentoring team members on security best practices and detection strategies.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing security-focused applications incorporating authentication, authorization, and access control mechanisms.
\item Contributed to incident response processes by analyzing logs, performing malware investigations, and documenting findings.
\item Worked closely with security teams to gather requirements, perform testing, and support secure deployment phases.
\item Gained hands-on experience in threat hunting, security monitoring, and secure coding within Agile security operations workflows.
\item Collaborated in security reviews to identify improvements in detection coverage, response time, and system resilience.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic }

\vspace{-1pt}

Automated vulnerability scanning and patching to strengthen enterprise security and reduce manual effort.
\vspace{-1pt}
\begin{itemize}
\item Developed automated workflows using Python and Jenkins for vulnerability scanning and patch deployment reducing manual intervention.
\item Integrated Nessus API for real-time vulnerability reporting aligned with MITRE ATT\&CK framework and risk prioritization strategies.
\item Created security dashboards and alert systems to track compliance, remediation progress, and emerging threat patterns effectively.
\item Reduced manual intervention by 60\% and accelerated patch cycles through full CI/CD automation enhancing security posture.
\end{itemize}

\textbf{Automated Cryptocurrency Trading Bot} -- \emph{Personal Project}

\vspace{-1pt}

Created a Python trading bot using Binance API and WebSocket to automate trade execution with risk control and live monitoring.
\vspace{-1pt}
\begin{itemize}
\item Developed a fully automated bot in Python using API integration and WebSocket for real-time data streaming and event monitoring.
\item Implemented dynamic strategies, risk controls, and execution algorithms incorporating anomaly detection and threat modeling principles.
\item Integrated Pandas and NumPy for data analysis and pattern recognition to improve accuracy and reduce false positives in execution.
\item Deployed using Docker on AWS EC2 for continuous uptime, reliability, and comprehensive logging aligned with security best practices.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}