% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Full Stack Software Developer with proven expertise in JavaScript, React, Node.js, and Python, specializing in building scalable web applications and cloud-based solutions. Experienced in developing with PostgreSQL, Docker, Kubernetes, and CI/CD pipelines while working within Agile teams. Strong foundation in frontend technologies, RESTful APIs, and modern frameworks with growing proficiency in backend systems. Passionate about leveraging AI tools and emerging technologies to drive innovation and deliver high-quality solutions.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, PHP, SQL, HTML5, CSS3, Bash

\textbf{Frontend Frameworks \& Libraries:} React, Redux, Angular, Vue.js, Bootstrap, Material UI, SASS

\textbf{Backend Technologies:} Node.js, Django, Flask, FastAPI, Express.js, Laravel

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, Redis, DynamoDB, Firebase

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, GitHub Actions, CI/CD, Terraform

\textbf{APIs \& Architecture:} REST API, GraphQL, Microservices, Event-Driven Architecture, MVC

\textbf{Development Practices:} Agile, Scrum, Code Reviews, TDD, System Design, Technical Documentation

\textbf{Soft Skills:} Communication, Team Collaboration, Adaptability, Problem Solving, Continuous Learning, Resourcefulness

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, Redux, and Node.js to deliver robust e-commerce solutions.
\item Implemented RESTful APIs and GraphQL endpoints with optimized PostgreSQL queries improving system reliability and performance.
\item Deployed cloud-based applications using AWS, Docker, Kubernetes, and CI/CD pipelines ensuring high availability and scalability.
\item Collaborated within Agile teams conducting peer code reviews, sprint planning, and design discussions to maintain quality standards.
\item Applied automated testing strategies and secure coding practices throughout SDLC reducing production issues and technical debt.
\item Led backend development initiatives while mentoring junior developers on best practices in system design and deployment processes.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications using modern JavaScript frameworks across frontend and backend components.
\item Contributed to design and implementation of tracking systems incorporating database design and API integration patterns.
\item Worked with cross functional teams to gather requirements, perform integration testing, and support deployment cycles.
\item Gained hands-on experience in full stack development, automated testing, and version control within Agile workflows.
\item Participated in code reviews and project retrospectives to identify improvements in performance, scalability, and maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Redux, Node.js, and PostgreSQL to support online education delivery.
\item Integrated real-time progress dashboards, quiz modules, and lesson tracking with role-based access control for teachers.
\item Implemented secure authentication, optimized database queries, and caching strategies for high concurrent user activity.
\item Deployed the platform on AWS with Docker containers, CDN caching, and SSL encryption ensuring reliable student access.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users and individuals with reading challenges, integrating accessibility features.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and WebSockets with accessibility-focused responsive UI design.
\item Integrated AWS Polly and Azure Speech Services enabling text-to-speech and voice-to-text communication for accessibility.
\item Followed WCAG standards and conducted testing with assistive technologies ensuring inclusive usability across user groups.
\item Deployed on AWS using Docker and Kubernetes for scalable, low-latency communication with automated CI/CD pipelines.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}