% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Developer with expertise in JavaScript, React, and Node.js, specializing in building scalable full stack web applications and cloud-based solutions. Proven track record deploying serverless architectures on AWS using Lambda, DynamoDB, and CI/CD pipelines. Experienced in developing intuitive user interfaces, optimizing backend systems, and collaborating within Agile teams to deliver high-value products. Detail-oriented problem solver with strong focus on maintainability, performance optimization, and customer-centric product development.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, SQL, HTML5, CSS3

\textbf{Frontend Development:} React, Redux, React Query, Bootstrap, Material UI, Responsive Design

\textbf{Backend \& API Development:} Node.js, Express.js, REST API, GraphQL, WebSockets, Serverless

\textbf{Database Technologies:} DynamoDB, PostgreSQL, MySQL, MongoDB, SQLite, Firebase

\textbf{AWS \& Cloud Infrastructure:} AWS Lambda, DynamoDB, AWS S3, CloudFormation, Serverless, AWS EC2

\textbf{DevOps \& Deployment:} Docker, CI/CD, GitHub Actions, Git, Kubernetes, Infrastructure as Code

\textbf{Software Engineering Practices:} Agile, Scrum, System Design, Performance Optimization, Unit Testing, Code Reviews

\textbf{Soft Skills:} Problem Solving, Communication, Team Collaboration, Adaptability, Time Management, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js to deliver intuitive user experiences.
\item Implemented RESTful APIs and optimized database queries to improve backend system performance and reliability across platforms.
\item Deployed cloud-based applications using AWS services, Docker, and CI/CD pipelines ensuring 99.9\% uptime and seamless deployments.
\item Collaborated within Agile teams through sprint planning, code reviews, and pair programming to maximize product value delivery.
\item Applied best practices in maintainability, testing, and secure coding throughout SDLC to reduce technical debt and defects.
\item Mentored junior developers on coding standards, architecture design, and deployment strategies to elevate team capabilities.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications across frontend and backend components using modern JavaScript frameworks.
\item Contributed to design, implementation, and testing of Proposal Management and Mailroom Tracking Systems for operational efficiency.
\item Worked closely with cross functional teams to gather requirements, prioritize tasks, and support timely product deployments.
\item Gained hands-on experience in full stack development, unit testing, and secure coding practices within Agile workflows.
\item Participated in project reviews to identify performance improvements, scalability enhancements, and code maintainability optimizations.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to access lessons, videos, and quizzes with real-time progress tracking dashboards.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack LMS using React, Node.js, and MySQL to support scalable online education with concurrent user access.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards for teachers and administrators.
\item Implemented secure authentication, role-based access control, and optimized database queries for high performance under load.
\item Deployed on AWS with CDN caching and SSL encryption ensuring reliable, secure access for over 6,000 active students daily.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive real-time chat app for low-vision users integrating text-to-speech and voice-to-text communication features.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Node.js, and WebSockets with accessibility-focused UI design and navigation.
\item Integrated AWS services for text-to-speech and voice-to-text communication enabling inclusive user experiences for all abilities.
\item Followed WCAG accessibility standards and tested with assistive technologies to ensure compliance and inclusive usability.
\item Deployed on AWS using Docker containers for scalable, low-latency communication with automated monitoring and error logging.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}