% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Developer with proven expertise in JavaScript, React, Node.js, and AWS cloud-native solutions. Experienced in building scalable web applications, serverless APIs, and CI/CD pipelines with strong focus on performance, security, and reliability. Skilled in modern frameworks including Next.js, along with backend technologies and DevOps practices. Collaborative team player with hands-on experience in Agile workflows, cross-functional collaboration, and delivering seamless digital experiences.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, PHP, SQL, HTML5, CSS3

\textbf{Frontend Frameworks \& Libraries:} React, Next.js, Angular, Vue.js, Redux, Bootstrap, Tailwind CSS

\textbf{Backend \& APIs:} Node.js, Express.js, Django, Flask, REST API, GraphQL, Serverless

\textbf{Database Management:} PostgreSQL, MySQL, MongoDB, DynamoDB, SQLite, Redis

\textbf{Cloud \& AWS Services:} AWS Lambda, API Gateway, S3, DynamoDB, Cognito, CloudWatch, CloudFormation

\textbf{DevOps \& CI/CD:} Docker, Kubernetes, GitHub Actions, Jenkins, CI/CD Pipelines, Infrastructure as Code

\textbf{Security \& Best Practices:} OAuth, JWT, API Security, OWASP, IAM, Encryption

\textbf{Software Development Practices:} Agile, Scrum, Code Reviews, TDD, Performance Optimization, System Design

\textbf{Soft Skills:} Communication, Collaboration, Ownership, Adaptability, Problem Solving, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Built scalable full-stack applications using JavaScript, React, and Node.js with AWS cloud services for high-traffic e-commerce.
\item Designed RESTful APIs and serverless functions with AWS Lambda and API Gateway to improve system performance and reliability.
\item Deployed cloud-native solutions using AWS S3, DynamoDB, and CI/CD pipelines ensuring consistent uptime and fast delivery cycles.
\item Optimized front-end performance, security, and accessibility across web applications following industry best practices.
\item Collaborated cross-functionally with product, design, and DevOps teams through Agile sprints and peer code reviews.
\item Applied test-driven development and secure coding standards throughout SDLC reducing production issues and enhancing code quality.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to full-stack development of enterprise applications using modern JavaScript frameworks and backend technologies.
\item Assisted in designing scalable APIs and database schemas for Proposal Management and Mailroom Tracking Systems.
\item Worked closely with cross-functional teams to gather requirements, perform testing, and support deployment workflows.
\item Gained hands-on experience with cloud infrastructure, DevOps practices, and Agile development methodologies.
\item Participated in code reviews and project retrospectives to identify improvements in performance, scalability, and maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes.
\vspace{-1pt}
\begin{itemize}
\item Developed full-stack LMS using React, Node.js, and AWS cloud services with real-time dashboards for teachers and students.
\item Integrated secure authentication, role-based access control, and optimized SQL queries for high concurrent user sessions.
\item Deployed platform on AWS with S3 storage, CloudWatch monitoring, and SSL encryption ensuring reliable access for 6,000+ users.
\item Implemented RESTful APIs for lesson uploads, quizzes, and performance tracking with seamless front-end integration.
\end{itemize}

\textbf{Custom Business Web Solutions} -- \emph{Personal Project}

\vspace{-1pt}

Built POS, e-commerce sites, landing pages, and inventory systems with secure, responsive web design, improving workflow efficiency.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed custom web solutions using React, Next.js, and Node.js with serverless backend architecture on AWS.
\item Implemented secure authentication, payment processing with Stripe API, and inventory tracking for multiple client projects.
\item Collaborated with clients to gather requirements and translate business needs into scalable, high-performance applications.
\item Optimized UI responsiveness, performance, and SEO across all projects enhancing user engagement and conversion rates.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}