% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Full Stack Software Engineer with 1-3 years of professional experience building scalable web applications using JavaScript, TypeScript, Python, and modern frameworks. Skilled in backend development with Node.js, Django, and Flask, frontend design with React, and cloud deployment on AWS and GCP. Experienced in RESTful API design, database optimization, CI/CD pipelines, and Agile collaboration. Passionate about writing clean, maintainable code and continuously learning new technologies to deliver high-quality solutions.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, TypeScript, PHP, Ruby, SQL

\textbf{Frontend Technologies:} React, HTML5, CSS3, Bootstrap, Redux, Material UI

\textbf{Backend Frameworks:} Node.js, Django, Flask, FastAPI, Express.js

\textbf{Databases \& APIs:} PostgreSQL, MySQL, MongoDB, REST API, GraphQL

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, CI/CD, GitHub Actions, Terraform

\textbf{Testing \& Best Practices:} Unit Testing, Integration Testing, Code Reviews, TDD, Security

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Problem Solving, Ownership, Learning Agility

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js to enhance platform functionality and user experience.
\item Implemented RESTful APIs, optimized SQL queries, and integrated secure payment systems improving reliability and system performance.
\item Deployed and maintained cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and availability.
\item Collaborated within Agile teams through code reviews, sprint planning, and pair programming to deliver high-quality features on schedule.
\item Applied test-driven development and secure coding standards throughout SDLC reducing production issues and improving maintainability.
\item Supported backend development while mentoring junior developers on coding best practices, testing principles, and deployment workflows.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level web applications across frontend and backend components within Agile development workflows.
\item Contributed to the design and implementation of internal management systems ensuring alignment with business requirements and UX goals.
\item Worked closely with cross functional teams to gather requirements, perform testing, and support deployment phases for production releases.
\item Gained hands-on experience in full stack development, debugging, troubleshooting, and secure coding practices within team environments.
\item Collaborated in project retrospectives to identify improvements in performance, scalability, code quality, and maintainability standards.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes and assessments.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full-stack LMS using React, Node.js, and MySQL to support online education with high concurrent user access.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time progress dashboards for instructors and admins.
\item Implemented secure authentication, role-based access control, and optimized database queries for performance under heavy traffic loads.
\item Deployed the platform on AWS with CDN caching and SSL encryption, ensuring reliable uptime and access for over 6,000 active students.
\end{itemize}

\textbf{PROSPR " Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users and individuals with reading challenges, integrating accessibility features.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and Socket.io with accessibility-focused UI design and keyboard navigation.
\item Integrated AWS Polly and Azure Speech Services to enable text-to-speech and voice-to-text communication for users with diverse needs.
\item Followed WCAG accessibility standards and tested with assistive technologies to ensure inclusive usability for low-vision individuals.
\item Deployed on AWS App Runner with Docker containers for scalable, low-latency communication and continuous integration and deployment.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}