% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with 2+ years of experience building scalable web applications and backend services using JavaScript, TypeScript, React, and Node.js. Proven expertise in designing REST APIs, cloud-native architecture, and microservices with AWS, Docker, and Kubernetes. Skilled in Agile development, CI/CD pipelines, and delivering high-performance production systems. Passionate about distributed systems and engineering excellence.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, SQL, HTML5, CSS3

\textbf{Frameworks \& Libraries:} React, Node.js, Express.js, Redux, Bootstrap, Django

\textbf{Backend \& APIs:} REST API, Microservices, GraphQL, WebSockets, Event-Driven Architecture

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, CI/CD, GitHub Actions, CloudFormation

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, Redis, DynamoDB

\textbf{Software Development Practices:} Agile, Scrum, System Design, Code Reviews, TDD, Performance Optimization

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Ownership, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using JavaScript, TypeScript, React, and Node.js to deliver high-performance features.
\item Designed and implemented REST APIs handling thousands of requests per second with optimized SQL queries and backend services.
\item Deployed cloud-native applications using AWS, Docker, Kubernetes, and CI/CD pipelines ensuring 99.9\% uptime and availability.
\item Collaborated in Agile teams through sprint planning, code reviews, and technical estimation to deliver production releases.
\item Applied TDD, secure coding standards, and engineering best practices throughout SDLC reducing production issues by 30\%.
\item Mentored junior developers on microservices architecture, Git workflows, and backend development best practices.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to building enterprise web applications using JavaScript and backend frameworks within Agile workflows.
\item Assisted in designing and implementing distributed systems including Proposal Management and Mailroom Tracking Systems.
\item Collaborated with cross-functional teams to gather requirements, perform integration testing, and support deployment cycles.
\item Gained hands-on experience in full stack development, API design, and secure coding in production environments.
\item Participated in sprint reviews and technical discussions to identify scalability improvements and performance optimizations.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS using TypeScript, React, Node.js, and AWS supporting 6K+ students with real-time progress tracking.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack LMS using React, Node.js, TypeScript, and MySQL to support concurrent access by thousands of students.
\item Developed REST APIs for lesson uploads, quizzes, and performance tracking with real-time dashboards for instructors.
\item Implemented secure authentication, role-based access control, and optimized database queries for high-traffic environments.
\item Deployed on AWS using Docker, CloudFront CDN, and SSL encryption ensuring 99.9\% uptime and low-latency performance.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed inclusive chat application using TypeScript, Node.js, and WebSockets with accessibility features for low-vision users.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat platform using React, Node.js, TypeScript, and Socket.io with accessibility-focused UI design.
\item Integrated AWS Polly and Azure Speech Services for text-to-speech and voice-to-text communication features.
\item Followed WCAG standards and tested with assistive technologies to ensure inclusive usability for all users.
\item Deployed on AWS using Docker containers and autoscaling for low-latency, high-availability communication infrastructure.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}