% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Full Stack Developer with expertise in building scalable web applications using React, Node.js, and Django. Experienced in developing frontend and backend systems, working with relational and NoSQL databases including PostgreSQL, MySQL, and MongoDB. Proven ability to deploy cloud-based solutions on AWS and GCP using Docker and CI/CD pipelines. Strong communicator with a track record of collaborating effectively in remote, distributed team environments and delivering end-to-end features across the stack.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, Python, TypeScript, PHP, SQL, HTML5, CSS3

\textbf{Frontend Technologies:} React, Redux, Angular, Vue.js, Bootstrap, Material UI

\textbf{Backend Technologies:} Node.js, Django, Flask, FastAPI, Express.js, REST API

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQLite, DynamoDB, Redis

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, CI/CD, GitHub Actions, Terraform

\textbf{Development Practices:} Agile, Scrum, TDD, Code Reviews, System Design, Documentation

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Problem Solving, Time Management, Remote Work

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using React, Node.js, and Django to deliver end-to-end feature development.
\item Built and maintained RESTful APIs and optimized database queries for PostgreSQL, MySQL, and MongoDB to enhance performance.
\item Deployed cloud-based applications on AWS using Docker, CI/CD pipelines, and infrastructure automation for high availability.
\item Collaborated with distributed teams in Agile environments through code reviews, sprint planning, and remote communication.
\item Implemented secure authentication, role-based access control, and API security practices following industry standards.
\item Mentored developers on best practices for frontend and backend development, testing, and deployment in remote workflows.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to frontend and backend development of enterprise web applications using React, Node.js, and relational databases.
\item Assisted in building features for Proposal Management and Mailroom Tracking Systems with cross-functional collaboration.
\item Participated in Agile ceremonies including requirement gathering, sprint planning, and testing to support project delivery.
\item Gained hands-on experience working with NoSQL and relational databases to support scalable application architecture.
\item Collaborated remotely with team members to review code, identify improvements, and ensure maintainability across projects.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes.
\vspace{-1pt}
\begin{itemize}
\item Developed full stack LMS using React, Node.js, and MySQL with role-based access and secure authentication for educators.
\item Integrated real-time dashboards, quiz modules, and performance tracking to support interactive online learning experiences.
\item Optimized database queries and implemented caching strategies to handle high concurrent usage across multiple user roles.
\item Deployed platform on AWS with CDN, SSL encryption, and automated backups ensuring reliability for over 6,000 active users.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users and individuals with reading challenges, integrating accessibility features.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Node.js, and WebSockets with accessibility-focused UI following WCAG standards.
\item Integrated AWS Polly and Azure Speech Services to enable text-to-speech and voice-to-text communication for inclusivity.
\item Collaborated with distributed team members remotely to gather requirements, test features, and ensure usability standards.
\item Deployed on AWS using Docker containers for scalable, low-latency communication with continuous monitoring and logging.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}