% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with proven expertise in Python, cloud infrastructure, and data engineering. Experienced in designing scalable solutions using AWS, Docker, Kubernetes, and CI/CD pipelines. Strong background in database management with PostgreSQL, MySQL, and ETL workflows. Adept at collaborating with cross-functional teams in Agile environments to deliver high-quality technical solutions that meet complex business requirements and drive operational excellence.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, SQL, JavaScript, Bash, Shell Scripting, PowerShell

\textbf{Database \& Data Management:} PostgreSQL, MySQL, SQL Server, MongoDB, ETL Pipelines, Data Warehousing

\textbf{Cloud \& Infrastructure:} AWS, GCP, Docker, Kubernetes, Terraform, CloudFormation

\textbf{DevOps \& CI/CD:} Jenkins, Bitbucket, GitHub Actions, GitLab CI/CD, Continuous Deployment

\textbf{Development Frameworks:} Django, Flask, FastAPI, Node.js, React, Bootstrap

\textbf{Computer Science \& Design:} Object-Oriented Programming, Design Patterns, Microservices, System Design

\textbf{Systems \& Tools:} Linux, Unix environments, Power BI, Nginx, Apache, Monitoring

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Problem Solving, Ownership, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using Python, JavaScript, and React with PostgreSQL and MySQL database integration.
\item Implemented RESTful APIs and optimized SQL queries to improve system performance, reliability, and data processing efficiency.
\item Deployed cloud-based solutions on AWS using Docker, Kubernetes, and CI/CD pipelines ensuring high availability and uptime.
\item Collaborated with cross-functional teams in Agile environments through code reviews, sprint planning, and technical documentation.
\item Applied object-oriented design patterns and secure coding practices throughout SDLC to enhance maintainability and quality.
\item Led backend development initiatives while mentoring developers on DevOps best practices and continuous deployment strategies.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level applications with Python and JavaScript across frontend and backend components.
\item Contributed to ETL process design and implementation for data management systems improving operational data workflows.
\item Worked closely with stakeholders to gather requirements, perform integration testing, and support deployment activities.
\item Gained hands-on experience in Linux environments, shell scripting, and database administration within Agile workflows.
\item Collaborated in technical reviews to identify improvements in performance, scalability, and code quality standards.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS using Python backend enabling 6K+ students to access educational content with interactive features.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed full stack LMS using Python, React, and MySQL supporting real-time performance tracking dashboards.
\item Integrated secure authentication, role-based access control, and optimized database queries for high concurrent user loads.
\item Implemented ETL workflows for lesson uploads, quiz management, and analytics enabling data-driven educational insights.
\item Deployed on AWS with Docker containers, load balancing, and SSL encryption ensuring reliable access for 6,000+ students.
\end{itemize}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Automated vulnerability scanning and patching using Python workflows to strengthen enterprise security posture.
\vspace{-1pt}
\begin{itemize}
\item Developed automated Python scripts with Jenkins integration for vulnerability scanning and patch deployment workflows.
\item Integrated third-party APIs for real-time vulnerability reporting, risk prioritization, and compliance tracking dashboards.
\item Created monitoring solutions and alert systems to track security metrics and remediation progress across environments.
\item Reduced manual intervention by 60\% and accelerated patch cycles through full DevOps CI/CD pipeline automation.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}