% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Web Developer with 3+ years of experience building scalable web applications using React, JavaScript, and TypeScript. Expertise in developing high-performance frontend solutions with modern frameworks, state management libraries, and RESTful API integration. Proven ability to deliver responsive, user-focused web experiences while collaborating with cross-functional teams in Agile environments. Skilled in full-cycle software development, code reviews, and implementing best practices to ensure scalability, security, and maintainability.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Frontend Technologies:} React, TypeScript, JavaScript, HTML5, CSS3, Next.js

\textbf{State Management \& UI Libraries:} Redux, React Query, Material UI, Bootstrap, Tailwind CSS

\textbf{Backend \& API Development:} Node.js, RESTful APIs, GraphQL, Django, Flask, FastAPI

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQL

\textbf{Cloud \& DevOps:} AWS, Docker, CI/CD, GitHub Actions, GitLab CI/CD

\textbf{Testing \& Development Practices:} Unit Testing, TDD, Agile, Scrum, Code Reviews, Pair Programming

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Continuous Learning, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using React, JavaScript, TypeScript, and Node.js to enhance user experience and functionality.
\item Designed and implemented RESTful APIs with optimized state management patterns improving system reliability and frontend performance.
\item Collaborated within Agile teams through code reviews, pair programming, and sprint planning to deliver high-quality responsive web solutions.
\item Deployed and maintained cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and rapid delivery cycles.
\item Applied test-driven development practices and participated in technical design discussions throughout the full software development lifecycle.
\item Mentored junior developers on frontend best practices, component architecture, and deployment strategies to elevate team code quality.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to developing enterprise web applications across frontend and backend components using React and modern JavaScript frameworks.
\item Participated in technical design discussions and collaborated with product managers and designers to define and implement new features.
\item Worked closely with cross-functional teams to gather requirements, perform testing, and troubleshoot complex technical issues during deployment.
\item Gained hands-on experience in full stack development, API integration, and secure coding practices within Agile workflows and Scrum ceremonies.
\item Assisted in implementing responsive UI components with HTML5, CSS3, and component libraries ensuring scalability and accessibility standards.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with notes, videos, and interactive quizzes using React and modern web technologies.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, TypeScript, Node.js, and MySQL to support online education with real-time features.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with state management using Redux for seamless user experience.
\item Implemented secure authentication, role-based access control, and optimized API design for high concurrent usage and data integrity.
\item Deployed the platform on AWS with CDN caching, SSL encryption, and Docker containers ensuring reliable access for over 6,000 students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive real-time chat app for low-vision users integrating accessibility features and modern frontend technologies.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, TypeScript, Node.js, and WebSockets with accessibility-focused responsive UI design.
\item Integrated AWS Polly and Azure Speech Services APIs to enable text-to-speech and voice-to-text communication for inclusive usability.
\item Followed WCAG accessibility standards and participated in testing cycles with assistive technologies to ensure optimal user experience.
\item Deployed on AWS using Docker containers and CI/CD pipelines for scalable, low-latency communication and continuous deployment cycles.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}