% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Software Engineer with hands-on experience designing and building scalable full stack applications using JavaScript, Python, React, Node.js, and cloud platforms. Skilled in Agile methodologies, data structures, algorithms, and object-oriented programming with proven ability to deliver high-quality code through test-driven development and CI/CD pipelines. Experienced collaborating with cross-functional teams to gather requirements, troubleshoot issues, and implement secure solutions using AWS, Docker, and version control systems like Git.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, SQL, HTML5, CSS3, Bash

\textbf{Frameworks \& Libraries:} React, Node.js, Django, Flask, Bootstrap, jQuery

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQLite, Database Design

\textbf{Cloud \& DevOps:} AWS, Docker, CI/CD, GitHub Actions, Terraform

\textbf{Software Development Practices:} Agile, Scrum, Git, Code Reviews, Testing, Technical Documentation

\textbf{Computer Science Fundamentals:} Data Structures, Algorithms, Object-Oriented Programming, Design Patterns

\textbf{Soft Skills:} Problem Solving, Communication, Team Collaboration, Adaptability, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js following Agile methodologies and coding standards.
\item Implemented RESTful APIs, optimized SQL queries, and integrated secure payment systems improving system reliability and performance.
\item Deployed and maintained cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and availability.
\item Collaborated with cross-functional teams through code reviews, sprint planning, and troubleshooting to deliver high-quality features.
\item Applied test-driven development and secure coding practices throughout the full software development lifecycle reducing production issues.
\item Led backend development initiatives while mentoring team members on coding standards, version control, and deployment best practices.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level web applications across both frontend and backend components using object-oriented programming.
\item Contributed to design and implementation of management systems, participating in requirements gathering, coding, and testing phases.
\item Worked closely with team members to troubleshoot and resolve software defects ensuring high-quality deliverables and code maintainability.
\item Gained hands-on experience in full stack development, version control with Git, and secure coding within Agile and Scrum workflows.
\item Collaborated in project reviews and technical discussions to identify improvements in performance, scalability, and coding standards.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes using AWS.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL applying data structures and object-oriented programming principles.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards leveraging efficient algorithms.
\item Implemented secure authentication, role-based access, and optimized database queries using SQL for high concurrent usage and performance.
\item Deployed the platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 students with minimal downtime.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic }

\vspace{-1pt}

Developed an inclusive chat app for low-vision users integrating accessibility features and cloud services for scalable communication.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and Socket.io applying object-oriented design patterns and clean code principles.
\item Integrated AWS Polly and Azure Speech Services to enable text-to-speech and voice-to-text communication for accessibility compliance.
\item Followed WCAG accessibility standards and tested with assistive technologies ensuring inclusive usability across diverse user groups.
\item Deployed on AWS App Runner with Docker containers for scalable, low-latency communication using infrastructure as code and version control.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}