% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with hands-on experience in full stack development, system design, and cloud deployment. Proficient in Python, JavaScript, React, Node.js, and SQL with a strong foundation in Agile methodologies and SDLC. Experienced in developing scalable web applications, implementing secure APIs, and deploying solutions on AWS and GCP. Skilled in requirements gathering, system testing, technical documentation, and collaborating with cross-functional teams to deliver high-quality software solutions.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, PHP, SQL, HTML, CSS

\textbf{Frameworks \& Libraries:} React, Django, Node.js, Bootstrap, Flask

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQLite, SQL Server

\textbf{Cloud \& DevOps:} AWS, Docker, CI/CD, GitHub Actions, Terraform

\textbf{Software Development:} Agile, Scrum, SDLC, Testing, Documentation

\textbf{Systems \& Security:} Linux, Networking, OWASP, API Security, Encryption

\textbf{Soft Skills:} Analytical, Team Player, Organized, Communication, Adaptability, Judgment

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js to enhance business functionality and user experience.
\item Implemented RESTful APIs, optimized SQL queries, and integrated secure systems to improve application reliability and performance.
\item Deployed and maintained cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and availability.
\item Collaborated within Agile teams through code reviews, sprint planning, and pair programming to ensure high-quality deliverables.
\item Applied test-driven development and secure coding standards throughout SDLC improving maintainability and reducing production issues.
\item Consulted with stakeholders to gather requirements, design solutions, and provide ongoing support ensuring alignment with business needs.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level web applications across both frontend and backend components using modern frameworks.
\item Contributed to design and implementation of management systems by documenting requirements and developing technical solutions.
\item Worked closely with cross-functional teams to gather requirements, perform testing, and support deployment phases successfully.
\item Gained hands-on experience in full stack development, software testing, and secure coding within Agile workflows and environments.
\item Collaborated in project reviews to identify improvements in performance, scalability, and code maintainability through detailed analysis.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with notes, videos, and interactive quizzes, deployed on cloud infrastructure.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL to support online education with interactive features.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time progress dashboards for instructors and users.
\item Implemented secure authentication, role-based access, and optimized database queries for high concurrent usage and data integrity.
\item Deployed the platform on AWS with CDN caching and SSL encryption, ensuring reliable access for over 6,000 students and educators.
\end{itemize}

\textbf{PROSPR " Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users integrating accessibility features, speech services, and real-time communication.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and WebSockets with accessibility-focused UI design and inclusive features.
\item Integrated AWS Polly and Azure Speech Services to enable text-to-speech and voice-to-text communication for diverse user needs.
\item Followed WCAG accessibility standards and tested with assistive technologies to ensure inclusive usability and compliance throughout.
\item Deployed on AWS with Docker containers for scalable, low-latency communication ensuring high availability and consistent performance.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}