% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Software Engineer with proven expertise in designing and implementing front-end applications using React, JavaScript, and TypeScript. Skilled in building RESTful APIs, user interfaces, and full-stack solutions with Node.js and modern frameworks. Experienced in Agile methodologies, cloud platforms including Azure, and translating technical specifications into tested, production-ready code. Strong background in SDLC, responsive design, cross-browser compatibility, and collaborating with diverse stakeholders to deliver scalable, accessible web applications.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming \& Front-End:} JavaScript, TypeScript, HTML5, CSS3, React, Next.js, Redux, SASS, Responsive Design

\textbf{Backend \& API Development:} Node.js, Express.js, RESTful APIs, GraphQL, WebSockets, Jamstack Architecture

\textbf{Database \& Cloud Platforms:} PostgreSQL, MySQL, MongoDB, Azure, AWS, Firebase, Cloud Deployment

\textbf{DevOps \& Testing:} Docker, Kubernetes, CI/CD Pipelines, GitHub Actions, Unit Testing, Debugging, Version Control

\textbf{Development Methodologies:} Agile, Scrum, Kanban, TDD, SDLC, Code Reviews, Technical Documentation

\textbf{Security \& Authentication:} OAuth, JWT, SSO, Azure AD B2C, API Security, HTTPS, Encryption

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Stakeholder Engagement, Team Leadership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full-stack web applications using JavaScript, React, Node.js, and TypeScript to enhance functionality.
\item Implemented RESTful APIs, optimized database queries, and integrated secure authentication improving system performance.
\item Deployed cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring high availability and consistent uptime.
\item Collaborated with cross-functional teams in Agile sprints through code reviews and task boards to meet project deadlines.
\item Applied structured methodologies and design patterns throughout SDLC reducing technical debt and production issues.
\item Resolved technical problems in deployment and operation phases while mentoring developers on best coding practices.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level web applications across frontend and backend components using modern frameworks.
\item Contributed to design specifications, testing, and deployment of Proposal Management and Mailroom Tracking Systems.
\item Worked with stakeholders to elicit requirements, document workflows, and translate business needs into technical solutions.
\item Gained hands-on experience in Agile development, debugging, and maintaining applications within structured methodologies.
\item Collaborated in project reviews identifying performance improvements, scalability enhancements, and code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS using React, Node.js, and MySQL enabling 6,000+ students to access lessons, quizzes, and performance tracking.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full-stack LMS using React, Node.js, and MySQL to support online education during the pandemic.
\item Integrated modules for lesson uploads, quizzes, and real-time progress dashboards with role-based access for teachers.
\item Implemented secure authentication, optimized database queries, and ensured cross-browser compatibility for high usage.
\item Deployed the platform on AWS with CDN caching, SSL encryption, and load balancing ensuring reliable student access.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive real-time chat app using React, Node.js, and Socket.io with accessibility features for low-vision users.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and Socket.io with responsive, accessibility-focused UI design.
\item Integrated Azure Speech Services and AWS Polly to enable text-to-speech and voice-to-text communication features.
\item Followed WCAG accessibility standards and tested with assistive technologies to ensure inclusive, barrier-free usability.
\item Deployed on AWS using Docker containers for scalable, low-latency communication with monitoring and logging enabled.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}