% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Software Developer with expertise in React, Node.js, SQL, and REST API development. Skilled in Entity Framework, TypeScript, JavaScript, and modern frameworks including Next.js. Proven experience deploying scalable cloud-based solutions using AWS, Docker, and CI/CD pipelines. Strong knowledge of WCAG accessibility standards and Agile/Scrum methodologies. Committed to building inclusive, high-performance applications with clean architecture and robust testing practices.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, SQL, Python, HTML5, CSS3

\textbf{Frameworks \& Libraries:} React, Next.js, Node.js, Express.js, Bootstrap, Redux

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, Entity Framework, SQL Server

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, CI/CD, GitHub Actions, Jenkins

\textbf{Software Development Practices:} Agile, Scrum, REST API, WCAG, TDD, Code Reviews

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Analytical Thinking, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using JavaScript, TypeScript, React, and Node.js to enhance system functionality.
\item Designed and implemented RESTful APIs with Entity Framework and optimized SQL queries improving performance and reliability.
\item Deployed cloud-based solutions using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and seamless deployments.
\item Collaborated within Agile teams conducting code reviews, sprint planning, and pair programming to deliver high-quality code.
\item Applied WCAG accessibility standards and secure coding practices throughout SDLC reducing production issues significantly.
\item Led backend development efforts mentoring junior developers on API design, database management, and deployment best practices.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications using both frontend and backend technologies within Agile workflows.
\item Contributed to design and implementation of database-driven systems including relational database schema and query optimization.
\item Worked closely with cross functional teams gathering requirements, performing testing, and supporting deployment activities.
\item Gained hands-on experience with REST APIs, SQL databases, and secure coding standards ensuring application reliability.
\item Participated in project reviews identifying performance improvements, scalability enhancements, and code maintainability strategies.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{PROSPR " Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive real-time chat application integrating accessibility features for low-vision users following WCAG standards.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and WebSockets with accessibility-focused UI adhering to WCAG guidelines.
\item Integrated AWS Polly and Azure Speech Services enabling text-to-speech and voice-to-text communication for inclusive usability.
\item Designed responsive frontend interfaces with TypeScript and tested extensively with assistive technologies for compliance.
\item Deployed on AWS using Docker containers with CI/CD automation ensuring scalable, low-latency, and reliable communication.
\end{itemize}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS using React, Node.js, and SQL supporting over 6,000 students with interactive learning features.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack LMS using React, Node.js, and MySQL with secure authentication and role-based access control mechanisms.
\item Developed REST APIs for lesson uploads, quizzes, and real-time performance tracking dashboards improving educational outcomes.
\item Optimized SQL database queries and implemented caching strategies to handle high concurrent usage with minimal latency.
\item Deployed on AWS with CDN integration, SSL encryption, and automated CI/CD pipelines ensuring reliable access for 6K+ students.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}