% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with 3+ years of experience building scalable backend systems, RESTful APIs, and full stack web applications. Proven expertise in Python, JavaScript, React, and cloud platforms including AWS and GCP. Skilled in designing microservices architectures, implementing CI/CD pipelines with Docker and Kubernetes, and optimizing database performance. Strong background in Agile collaboration and delivering high-quality code through TDD and code reviews. Passionate about leveraging AI-driven automation to enhance workflows.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, SQL, HTML5, CSS3, Bash

\textbf{Backend Frameworks \& Tools:} Django, Flask, FastAPI, Node.js, GraphQL, REST API

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, Redis, SQL Optimization

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, Jenkins, CI/CD, Terraform

\textbf{Frontend Technologies:} React, Redux, Bootstrap, Material UI, SASS

\textbf{Development Practices:} Agile, Scrum, TDD, Code Reviews, System Design, API Security

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Ownership, Mentorship

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable backend APIs using Python and Node.js, optimizing SQL queries to enhance system performance and reliability.
\item Built full stack web applications with React and integrated RESTful APIs and secure payment systems to improve e-commerce functionality.
\item Deployed cloud-based applications on AWS using Docker, Kubernetes, and CI/CD pipelines ensuring consistent uptime and scalability.
\item Collaborated with cross-functional Agile teams through code reviews and sprint planning to deliver high-quality, maintainable code.
\item Applied TDD and secure coding standards throughout SDLC, reducing production issues and improving application maintainability.
\item Led backend development for multiple applications while mentoring junior developers on best practices in coding and deployment.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level web applications across backend and frontend components using modern frameworks and tools.
\item Contributed to design and implementation of Proposal Management and Mailroom Tracking Systems with scalable architectures.
\item Worked closely with cross-functional teams to gather requirements, perform integration testing, and support deployment phases.
\item Gained hands-on experience in full stack development, API design, and secure coding practices within Agile workflows.
\item Collaborated in project reviews to identify improvements in performance, scalability, and code maintainability across all systems.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with notes, videos, and interactive quizzes during the pandemic using React and Node.js.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL to support online education for over 6,000 students.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time progress dashboards for teachers and admins.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent usage and performance.
\item Deployed the platform on AWS with CDN caching and SSL encryption, ensuring reliable access and scalability for thousands of users.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive real-time chat app for low-vision users integrating text-to-speech and voice-to-text accessibility features.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and Socket.io with accessibility-focused UI design and WCAG compliance.
\item Integrated AWS Polly and Azure Speech Services to enable seamless text-to-speech and voice-to-text communication for all users.
\item Followed WCAG accessibility standards and tested with assistive technologies to ensure inclusive and usable design for diverse needs.
\item Deployed on AWS App Runner with Docker containers for scalable, low-latency communication and high availability across all regions.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}