% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Software Engineer with proven experience building scalable full stack web applications and distributed systems. Skilled in JavaScript, TypeScript, React, Node.js, and Python with hands-on expertise in cloud infrastructure using AWS and GCP. Experienced in developing RESTful and GraphQL APIs, implementing CI/CD pipelines, and ensuring high availability in production environments. Strong collaborator with a track record of working in Agile teams, mentoring developers, and delivering reliable solutions for e-commerce and real-time platforms.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, PHP, SQL, HTML5, CSS3

\textbf{Frontend \& UI Frameworks:} React, Redux, Bootstrap, Material UI, Next.js, Angular

\textbf{Backend \& APIs:} Node.js, Express.js, Django, Flask, REST API, GraphQL

\textbf{Databases \& Caching:} PostgreSQL, MySQL, MongoDB, Redis, DynamoDB, Firebase

\textbf{Cloud \& DevOps:} AWS, GCP, Docker, Kubernetes, CI/CD, GitHub Actions

\textbf{Architecture \& Design:} Microservices, Event-Driven Architecture, System Design, Scalability, MVC

\textbf{Soft Skills:} Ownership, Collaboration, Continuous Learning, Adaptability, Mentorship

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js supporting high-traffic e-commerce platforms.
\item Built and optimized RESTful APIs and integrated secure payment systems improving transaction reliability and user experience.
\item Deployed cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring high availability and consistent uptime.
\item Collaborated in Agile teams through code reviews, sprint planning, and pair programming to deliver high-quality software releases.
\item Applied test-driven development and secure coding standards throughout the SDLC reducing production issues and technical debt.
\item Mentored junior developers on backend development best practices, deployment strategies, and distributed systems architecture.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web and mobile applications working across both frontend and backend system components.
\item Contributed to the design and implementation of scalable systems including Proposal Management and Mailroom Tracking Systems.
\item Worked closely with cross functional teams to gather requirements, perform testing, and support production deployments.
\item Gained hands-on experience in full stack development, automated testing, and secure coding within Agile workflows.
\item Collaborated in project reviews identifying improvements in performance, scalability, and long-term code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes online.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL supporting thousands of concurrent online learners.
\item Integrated lesson uploads, interactive quizzes, and real-time performance tracking dashboards for teachers and students.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent usage.
\item Deployed the platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 active students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive real-time chat app for low-vision users integrating text-to-speech and voice-to-text accessibility features.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and WebSockets with accessibility-focused responsive UI design.
\item Integrated AWS Polly and Azure Speech Services enabling seamless text-to-speech and voice-to-text communication features.
\item Followed WCAG accessibility standards and tested with assistive technologies ensuring inclusive usability for all users.
\item Deployed on AWS App Runner with Docker containers for scalable, low-latency real-time messaging and high availability.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}