% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with hands-on experience building scalable full stack web applications and distributed systems using Python, JavaScript, Node.js, and React. Proven expertise in designing RESTful APIs, deploying cloud-based solutions on AWS with services like DynamoDB, RDS, and Lambda, and following Agile methodologies throughout the SDLC. Strong foundation in computer science fundamentals including data structures, algorithms, and system design with a commitment to clean architecture and continuous learning.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, TypeScript, SQL, HTML5, CSS3, Bash

\textbf{Frameworks \& Libraries:} React, Node.js, Django, Flask, FastAPI, Bootstrap

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, DynamoDB, Redis

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, CI/CD, GitHub Actions, CloudFormation

\textbf{AWS Services:} Lambda, EC2, S3, RDS, DynamoDB, CloudWatch

\textbf{API Development:} REST API, GraphQL, WebSockets, Microservices, API Gateway

\textbf{Software Development Practices:} Agile, Scrum, SDLC, Code Reviews, Unit Testing, TDD

\textbf{Computer Science Fundamentals:} Data Structures, Algorithms, OOP, Design Patterns, Distributed Systems

\textbf{Soft Skills:} Problem Solving, Communication, Team Collaboration, Adaptability, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using JavaScript, React, and Node.js implementing REST APIs for e-commerce platforms.
\item Built reusable service modules from requirements, integrating secure payment systems improving reliability and system performance.
\item Deployed cloud-based solutions on AWS leveraging services like RDS, S3, and Lambda ensuring high availability and uptime.
\item Debugged and troubleshot production issues applying problem-solving strategies to maintain optimal application performance.
\item Collaborated within Agile teams through sprint planning, code reviews, and continuous integration improving delivery timelines.
\item Applied SDLC best practices including test-driven development and secure coding standards reducing production defects significantly.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to enterprise web and mobile applications across frontend and backend components within Agile development workflows.
\item Assisted in designing and implementing distributed systems including Proposal Management and Mailroom Tracking Systems.
\item Worked with cross functional teams gathering requirements, performing integration testing, and supporting deployment phases.
\item Gained hands-on experience developing REST APIs and asynchronous services ensuring scalability and performance optimization.
\item Collaborated in code reviews identifying improvements in performance, maintainability, and adherence to coding standards.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with interactive lessons, quizzes, and performance tracking during the pandemic.
\vspace{-1pt}
\begin{itemize}
\item Developed full stack LMS using React, Node.js, and MySQL implementing REST APIs for lesson uploads and real-time progress tracking.
\item Integrated role-based authentication and optimized database queries supporting high concurrent usage and low-latency interactions.
\item Deployed platform on AWS with EC2, S3, and CloudFront implementing SSL encryption ensuring reliable access for 6,000+ students.
\item Applied SDLC best practices including unit testing, code reviews, and continuous delivery ensuring maintainable and scalable code.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic }

\vspace{-1pt}

Developed inclusive real-time chat app for low-vision users integrating accessibility features and assistive technology support.
\vspace{-1pt}
\begin{itemize}
\item Built asynchronous real-time chat application using React, Node.js, and WebSockets following clean architecture and WCAG standards.
\item Integrated AWS Polly enabling text-to-speech and voice-to-text communication improving accessibility for users with reading challenges.
\item Deployed on AWS App Runner using Docker containers ensuring scalable, low-latency communication and high availability for end users.
\item Collaborated in Agile team conducting code reviews, sprint planning, and testing with assistive technologies ensuring inclusive design.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}