% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with expertise in Python, Django, Flask, and cloud-based SaaS architecture. Proven experience building scalable backend systems, RESTful APIs, and enterprise management solutions using PostgreSQL and modern DevOps practices. Strong foundation in Linux environments, CI/CD automation, and distributed team collaboration. Committed to code quality, automated testing, and delivering secure, high-performance web services at scale.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, PHP, SQL, HTML, CSS, Bash

\textbf{Frameworks \& Libraries:} Django, Flask, FastAPI, React, Node.js, Bootstrap

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQLite, Redis, ORMs

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, CI/CD, GitHub Actions, Terraform

\textbf{Software Development Practices:} Agile, Scrum, TDD, Code Reviews, SDLC, Release Management

\textbf{Systems \& Networking:} Linux, Ubuntu, Cloud Computing, API Security, Monitoring, Logging

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Ownership, Self-Motivation, Accountability

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable web applications and public-facing APIs using Python, Django, and Flask to enhance backend functionality.
\item Implemented RESTful APIs with PostgreSQL optimization and secure authentication improving reliability and performance.
\item Deployed cloud-based SaaS applications using AWS, Docker, and CI/CD pipelines ensuring uptime and operational stability.
\item Collaborated in distributed Agile teams through code reviews, sprint planning, and automated testing for quality delivery.
\item Applied TDD principles and secure coding standards across development lifecycle reducing production issues and bugs.
\item Led backend system architecture and mentored junior engineers on best practices for deployment and code maintainability.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise management systems focusing on backend components and database integration using Python.
\item Contributed to system design, implementation, and automated testing for management and tracking applications.
\item Worked with cross-functional teams to gather requirements, perform integration testing, and support deployment cycles.
\item Gained experience in backend development, database optimization, and secure coding within Agile development workflows.
\item Collaborated in project reviews identifying improvements in performance, scalability, and maintainability of codebases.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built scalable LMS with Python backend enabling 6K+ students to access lessons, quizzes, and progress tracking dashboards.
\vspace{-1pt}
\begin{itemize}
\item Designed full-stack LMS using Python, Flask, React, and PostgreSQL to support large-scale online education platform.
\item Integrated lesson management, quiz modules, and real-time performance tracking with role-based access controls.
\item Implemented secure authentication using OAuth, optimized PostgreSQL queries, and ensured high concurrency support.
\item Deployed on AWS with Docker, SSL encryption, and CDN caching ensuring reliable access for over 6,000 active users.
\end{itemize}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic }

\vspace{-1pt}

Automated vulnerability scanning and patch deployment using Python and Jenkins reducing manual effort by 60 percent.
\vspace{-1pt}
\begin{itemize}
\item Developed automated workflows using Python and Jenkins for vulnerability scanning and orchestrated patch deployment.
\item Integrated Nessus API for real-time vulnerability reporting with automated risk prioritization and alerting systems.
\item Created monitoring dashboards and alert systems to track security compliance and remediation progress across estate.
\item Reduced manual intervention by 60 percent and accelerated patch cycles through full CI/CD automation and orchestration.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}