% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Full Stack Software Engineer with 2+ years of professional experience building scalable web applications using Python, JavaScript, and React. Proven track record deploying cloud-native solutions on AWS and GCP with Docker, Kubernetes, and CI/CD automation. Experienced in developing end-to-end features from design through production, integrating APIs, and optimizing distributed systems. Strong background in Agile development, DevOps practices, and cross-functional collaboration with a demonstrated ability to rapidly learn new technologies and deliver innovative solutions.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, SQL, HTML5, CSS3, Bash

\textbf{Frameworks \& Libraries:} React, Django, Flask, Node.js, Bootstrap, Redux

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQLite, Firebase

\textbf{Cloud \& DevOps:} AWS, GCP, Azure, Docker, Kubernetes, CI/CD

\textbf{Development Practices:} Agile, Scrum, REST API, Microservices, TDD, DevOps

\textbf{Systems \& Networking:} Distributed Systems, Cloud Architecture, Linux, Security

\textbf{Soft Skills:} Ownership, Collaboration, Adaptability, Communication, Problem Solving

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js delivering end-to-end features from design to production.
\item Built and maintained RESTful APIs with optimized SQL queries and cloud-native architectures improving system reliability and performance.
\item Deployed applications on AWS using Docker, Kubernetes, and CI/CD pipelines ensuring consistent uptime and high availability in production.
\item Collaborated within Agile teams through code reviews, sprint planning, and pair programming to deliver high-quality software consistently.
\item Applied test-driven development and secure coding standards throughout SDLC reducing production issues and improving code maintainability.
\item Led backend development for multiple applications while mentoring junior developers on best practices, DevOps workflows, and deployment strategies.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level web applications across frontend and backend components using modern frameworks and cloud technologies.
\item Contributed to design and implementation of Proposal Management and Mailroom Tracking Systems with scalable distributed architectures.
\item Worked closely with cross-functional teams gathering requirements, performing testing, and supporting deployment phases in Agile workflows.
\item Gained hands-on experience in full stack development, containerization, software testing, and secure coding within DevOps environments.
\item Collaborated in project reviews identifying improvements in performance, scalability, code maintainability, and cloud infrastructure optimization.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes using cloud technologies.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL supporting online education with real-time progress dashboards.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with optimized database queries for high concurrent usage scenarios.
\item Implemented secure authentication with role-based access control and encrypted data transmission ensuring privacy and compliance standards.
\item Deployed the platform on AWS with CDN caching, SSL encryption, and autoscaling ensuring reliable access for over 6,000 active students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users integrating accessibility features, cloud AI services, and real-time communication protocols.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and Socket.io with accessibility-focused UI design following WCAG standards.
\item Integrated AWS Polly and Azure Speech Services enabling text-to-speech and voice-to-text communication for inclusive user experiences.
\item Tested with assistive technologies and validated accessibility compliance ensuring usability for individuals with reading and vision challenges.
\item Deployed on AWS App Runner with Docker containers for scalable, low-latency communication and high availability in production environments.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}