% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Full Stack Software Engineer with proven expertise in building scalable cloud-based applications using React, Node.js, and AWS. Experienced in designing microservices architectures, RESTful APIs, and serverless infrastructure across distributed systems. Strong background in CI/CD pipelines, DevOps practices, and production system operations. Skilled in implementing secure authentication, database optimization, and observability solutions. Collaborative team player with agile development experience and a commitment to writing high-quality, tested code that delivers reliable user experiences.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, SQL, HTML5, CSS3

\textbf{Frontend Technologies:} React, Redux, Material UI, Bootstrap, HTML, CSS

\textbf{Backend \& APIs:} Node.js, Express.js, REST API, GraphQL, Microservices

\textbf{Database Systems:} MySQL, PostgreSQL, MongoDB, DynamoDB, SQLite

\textbf{Cloud \& Infrastructure:} AWS Lambda, AWS S3, AWS EC2, API Gateway, CloudWatch, Serverless

\textbf{DevOps \& CI/CD:} Docker, Jenkins, GitHub Actions, Kubernetes, Terraform

\textbf{Testing \& Quality:} Jest, Unit Testing, Integration Testing, Postman, TDD

\textbf{Soft Skills:} Communication, Team Collaboration, Adaptability, Problem Solving, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using React, Node.js, and JavaScript to deliver customer-facing features and intuitive UX.
\item Built and maintained RESTful APIs, optimized MySQL queries, and integrated secure authentication to ensure system reliability.
\item Deployed cloud-based applications on AWS using Docker, S3, EC2, and CI/CD pipelines ensuring high availability and performance.
\item Collaborated in Agile teams through sprint planning, code reviews, and pair programming to deliver high-quality, tested code.
\item Applied test-driven development and security best practices throughout SDLC reducing production issues and improving stability.
\item Provided on-call support, troubleshooting, and mentored junior developers on deployment practices and architectural patterns.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing distributed web applications across frontend and backend components using JavaScript and cloud services.
\item Contributed to API design and implementation for Proposal Management and Mailroom Tracking Systems with database integration.
\item Collaborated with cross functional teams including design to gather requirements, perform testing, and support deployments.
\item Gained hands-on experience writing unit and integration tests within Agile workflows to ensure code quality and reliability.
\item Participated in project reviews to identify improvements in performance, scalability, and adherence to architectural standards.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL supporting high concurrent usage and real-time features.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with dashboards providing observability for educators.
\item Implemented secure authentication with JWT, role-based access control, and optimized database queries for system performance.
\item Deployed the platform on AWS with S3 storage, CloudWatch monitoring, and CDN caching ensuring reliability for 6,000+ users.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users and individuals with reading challenges, integrating accessibility features.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and WebSockets with accessibility-focused UI collaborating with design.
\item Integrated AWS Polly and cloud APIs to enable text-to-speech and voice-to-text communication for inclusive user experience.
\item Followed WCAG standards and tested with assistive technologies ensuring compliance and intuitive functionality for all users.
\item Deployed on AWS with Docker containers and serverless infrastructure for scalable, low-latency, high-availability communication.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}