% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with hands-on expertise in developing scalable full stack applications using React, Node.js, and TypeScript. Proven ability to design RESTful APIs, optimize database performance with PostgreSQL and MongoDB, and implement robust solutions throughout the software development lifecycle. Experienced in collaborating with cross-functional teams in Agile environments to deliver high-quality software products that align with business goals and technical requirements.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, SQL, HTML5, CSS3, PHP

\textbf{Frontend Development:} React, Redux, React Query, Bootstrap, Material UI, SASS

\textbf{Backend Development:} Node.js, Express.js, RESTful APIs, Django, Flask, FastAPI

\textbf{Database Management:} PostgreSQL, SQL Server, MongoDB, Redis, MySQL, SQLite

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, CI/CD, GitHub Actions, GitLab CI/CD

\textbf{Testing \& Quality Assurance:} Unit Testing, Integration Testing, TDD, Debugging, Postman, Code Reviews

\textbf{Software Development Practices:} Agile, Scrum, Design Patterns, System Design, Scalability, Performance Optimization

\textbf{Soft Skills:} Problem Solving, Communication, Team Collaboration, Analytical Thinking, Adaptability, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using React, Node.js, and TypeScript adhering to best practices and coding standards.
\item Designed and implemented RESTful APIs and optimized SQL queries to improve system reliability, performance, and data integrity.
\item Collaborated with cross-functional teams to analyze user requirements and translate them into efficient software specifications.
\item Deployed cloud-based applications using AWS and Docker with CI/CD pipelines ensuring high availability and consistent uptime.
\item Conducted comprehensive unit and integration testing throughout SDLC improving maintainability and reducing production issues.
\item Participated in code reviews and sprint planning within Agile teams to deliver high-quality, scalable software solutions.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to development of enterprise applications throughout the software development lifecycle using best practices.
\item Designed and implemented components for Proposal Management and Mailroom Tracking Systems with frontend and backend integration.
\item Collaborated with quality assurance engineers to execute testing, identify bugs, and ensure delivery of high-quality products.
\item Worked within Agile teams to gather requirements, perform code reviews, and support deployment phases for multiple projects.
\item Gained hands-on experience with relational databases, optimizing queries, and ensuring data integrity and security.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS using React and Node.js enabling 6K+ students to learn with interactive quizzes and performance tracking.
\vspace{-1pt}
\begin{itemize}
\item Developed full stack LMS using React, Node.js, and relational databases to support online education with high concurrent usage.
\item Designed and implemented RESTful APIs for lesson uploads, quizzes, and real-time progress dashboards for teachers and students.
\item Optimized database performance and scalability with efficient queries and indexing to handle high-volume traffic reliably.
\item Deployed on AWS with SSL encryption and CDN caching ensuring data security, integrity, and reliable access for 6K+ students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed inclusive real-time chat app using React and Node.js with accessibility features for low-vision and reading challenges.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Node.js, and WebSockets with accessibility-focused UI following best practices.
\item Integrated RESTful APIs and external services to enable text-to-speech and voice-to-text communication with robust architecture.
\item Collaborated with cross-functional teams to analyze requirements and ensure WCAG standards for inclusive usability and testing.
\item Deployed on AWS using Docker containers ensuring scalable, high-performance, and low-latency communication for all users.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}