% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Frontend Engineer with 2+ years of experience building scalable, accessible web applications using React, JavaScript, and modern frontend technologies. Proven ability to design and deliver intuitive user interfaces, optimize performance, and implement responsive designs that enhance user experience. Skilled in cross-browser compatibility, RESTful API integration, and collaborating with cross-functional teams in Agile environments to ship high-quality products that solve real business problems.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, HTML5, CSS3, SQL

\textbf{Frontend Frameworks \& Libraries:} React, Redux, React Query, Bootstrap, Material UI, Next.js

\textbf{Backend \& APIs:} Node.js, Express.js, REST API, Django, Flask, GraphQL

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, Firebase, Redis

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, CI/CD, GitHub Actions, Terraform

\textbf{Testing \& Quality Assurance:} Unit Testing, Integration Testing, TDD, Postman, Automation Testing

\textbf{Web Standards \& Best Practices:} Responsive Design, WCAG Accessibility, Cross-browser Compatibility, Performance Optimization, SEO

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Problem Solving, Ownership, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js to enhance e-commerce user experiences.
\item Implemented RESTful APIs and integrated secure payment systems improving system reliability and transaction performance.
\item Deployed and maintained cloud applications on AWS using Docker and CI/CD pipelines ensuring high availability and uptime.
\item Collaborated within Agile teams through code reviews, sprint planning, and pair programming to deliver quality features.
\item Applied test-driven development and secure coding standards throughout SDLC reducing production issues and improving code quality.
\item Led backend development for multiple web applications while mentoring junior developers on coding and deployment best practices.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web and mobile applications across frontend and backend components using modern frameworks.
\item Contributed to design and implementation of Proposal Management and Mailroom Tracking Systems improving workflow efficiency.
\item Worked closely with cross-functional teams to gather requirements, perform testing, and support deployment phases successfully.
\item Gained hands-on experience in full stack development, software testing, and secure coding practices within Agile workflows.
\item Collaborated in project reviews to identify improvements in performance, scalability, and overall code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with notes, videos, and interactive quizzes during the pandemic.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL to support online education during the pandemic.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time progress dashboards for educators.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent user access.
\item Deployed the platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 active students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users integrating accessibility features and real-time communication.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and Socket.io with accessibility-focused UI design and features.
\item Integrated AWS Polly and Azure Speech Services to enable text-to-speech and voice-to-text communication for inclusivity.
\item Followed WCAG accessibility standards and tested with assistive technologies to ensure usability for all user groups.
\item Deployed on AWS App Runner with Docker containers for scalable, low-latency communication and consistent performance.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}