% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Developer with expertise in full stack web development using JavaScript, React, Node.js, Python, and PHP. Proven ability to build scalable applications, implement secure APIs, and optimize database performance. Experienced in cloud deployment with AWS and GCP, CI/CD pipelines, and Agile methodologies. Adept at translating business requirements into technical solutions, ensuring code quality through testing and reviews, and collaborating across teams to deliver high-impact software.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, PHP, SQL, HTML, CSS

\textbf{Frameworks \& Libraries:} React, Django, Node.js, Bootstrap, jQuery, Express.js

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQLite, Database Design

\textbf{Cloud \& DevOps:} AWS, GCP, Docker, Kubernetes, GitLab CI/CD, GitHub Actions

\textbf{Software Development Practices:} Agile, Scrum, SDLC, Testing, Debugging, Code Reviews

\textbf{Computer Science Fundamentals:} Data Structures, Algorithms, OOP, Design Patterns, MVC

\textbf{Systems \& Networking:} Cloud Computing, Security Best Practices, Unix/Linux, Scripting

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Ownership, Documentation

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js to enhance e-commerce functionality.
\item Implemented RESTful APIs, optimized SQL queries, and integrated secure payment systems to improve system reliability.
\item Deployed and maintained cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime.
\item Collaborated within Agile teams through code reviews, sprint planning, and pair programming to deliver high-quality code.
\item Applied test-driven development and secure coding standards throughout SDLC improving maintainability and reducing issues.
\item Led backend development for Shopify applications while mentoring junior developers on best coding and deployment practices.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web and mobile applications across both frontend and backend components using modern tools.
\item Contributed to the design and implementation of the Proposal Management and Mailroom Tracking Systems for internal use.
\item Worked closely with cross functional teams to gather requirements, perform testing, and support deployment phases efficiently.
\item Gained hands-on experience in full stack development, software testing, and secure coding within Agile workflows and sprints.
\item Collaborated in project reviews to identify improvements in performance, scalability, and code maintainability across systems.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes online.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL to support online education during the pandemic.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time progress dashboards for teachers.
\item Implemented secure authentication, role-based access, and optimized database queries for high concurrent usage and speed.
\item Deployed the platform on AWS with CDN caching and SSL encryption, ensuring reliable access for over 6,000 active students.
\end{itemize}

\textbf{Custom Business Web Solutions} -- \emph{Personal Project}

\vspace{-1pt}

Built POS, e-commerce sites, landing pages, and inventory systems with secure, responsive web design improving client workflow.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed multiple custom web solutions using React, Next.js, and Express.js for diverse business requirements.
\item Implemented secure authentication, inventory tracking, and payment processing with Stripe API integration for transactions.
\item Collaborated with clients to gather requirements and translate business needs into scalable, maintainable web applications.
\item Optimized UI performance, responsiveness, and SEO across all client projects to enhance user engagement and satisfaction.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}