% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Software Engineer with hands-on experience building scalable backend systems, RESTful APIs, and cloud-based applications using Python, Django, Flask, and PostgreSQL. Proficient in developing full stack web applications with strong expertise in cloud platforms including AWS and GCP, containerization with Docker and Kubernetes, and CI/CD automation. Experienced in Agile development, code reviews, and test-driven development within distributed teams, delivering secure and high-performance solutions aligned with business objectives.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, PHP, SQL, HTML, CSS, Bash

\textbf{Frameworks \& Libraries:} Django, Flask, FastAPI, React, Node.js, Bootstrap

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, ORMs, Query Optimization

\textbf{Cloud \& DevOps:} AWS, GCP, Docker, Kubernetes, GitLab CI/CD, GitHub Actions

\textbf{Software Development Practices:} Agile, Scrum, TDD, Code Reviews, Release Management, Automated Testing

\textbf{Systems \& Networking:} Ubuntu, Linux, Cloud Computing, Security Best Practices, API Development

\textbf{Soft Skills:} Communication, Collaboration, Accountability, Adaptability, Ownership, Self-Motivation

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable backend APIs and full stack web applications using Python, Django, Flask, JavaScript, and React to enhance system functionality.
\item Designed and optimized RESTful APIs with secure authentication, PostgreSQL query optimization, and integrated payment systems for reliability.
\item Deployed and maintained cloud-based applications on AWS and GCP using Docker, Kubernetes, and automated CI/CD pipelines for consistent uptime.
\item Collaborated within distributed Agile teams through code reviews, sprint planning, and automated testing to deliver high-quality software.
\item Applied test-driven development, architectural reviews, and secure coding throughout SDLC improving maintainability and reducing bugs.
\item Led backend development for multiple applications while mentoring junior developers on best practices, code quality, and deployment workflows.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level web applications across backend and frontend using Python, JavaScript, and PostgreSQL databases.
\item Contributed to design, implementation, and release management for Proposal Management and Mailroom Tracking Systems in Agile environments.
\item Worked closely with cross-functional teams to gather requirements, perform integration testing, and support deployment cycles and releases.
\item Gained hands-on experience in full stack development, automated testing, secure coding, and version control within distributed Agile workflows.
\item Collaborated in code reviews and project retrospectives to identify improvements in performance, scalability, and overall code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS using Python, Django, React, and PostgreSQL enabling 6K+ students to learn with interactive quizzes and dashboards.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using Django, React, and PostgreSQL to support online education with real-time progress tracking.
\item Integrated modules for lesson uploads, quizzes, and performance monitoring with role-based access control and secure authentication mechanisms.
\item Optimized PostgreSQL database queries and implemented caching strategies to handle high concurrent usage and improve response times significantly.
\item Deployed the platform on AWS with Docker, SSL encryption, and load balancing ensuring reliable access for over 6,000 students and educators.
\end{itemize}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic }

\vspace{-1pt}

Automated vulnerability scanning and patching using Python, Jenkins, and CI/CD pipelines to strengthen enterprise security and reduce manual effort.
\vspace{-1pt}
\begin{itemize}
\item Developed automated workflows using Python, Flask, and Jenkins for vulnerability scanning, risk prioritization, and patch deployment cycles.
\item Integrated Nessus API for real-time vulnerability reporting and implemented monitoring dashboards to track security compliance and remediation.
\item Created alert systems and automated scripts to accelerate patch cycles through full CI/CD automation reducing manual intervention by 60 percent.
\item Deployed the solution using Docker and Kubernetes on cloud infrastructure ensuring scalability, high availability, and consistent security coverage.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}