% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with expertise in building scalable backend systems using Python, JavaScript, Node.js, and RESTful API design. Experienced in developing financial and enterprise applications with strong SQL database management, cloud deployment on AWS, and containerization using Docker and Kubernetes. Proven ability to deliver high-quality solutions through Agile collaboration, CI/CD automation, and rigorous testing practices while taking ownership from inception to production deployment.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, TypeScript, SQL, Bash, PHP

\textbf{Backend Frameworks \& APIs:} Node.js, Express.js, Django, Flask, FastAPI, RESTful API

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, Redis, Database Design

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, CI/CD, GitHub Actions, Jenkins

\textbf{Software Development Practices:} Microservices, Unit Testing, Agile, Scrum, TDD, Code Reviews

\textbf{Systems \& Architecture:} Distributed Systems, Event-Driven Architecture, Design Patterns, Scalability

\textbf{Soft Skills:} Ownership, Problem Solving, Collaboration, Communication, Adaptability, Mentorship

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable backend systems and RESTful APIs using JavaScript, Node.js, and Python improving system reliability and performance.
\item Optimized SQL queries across PostgreSQL and MySQL databases to support high-volume transactional applications and data integrity.
\item Deployed microservices-based applications using AWS, Docker, and Kubernetes with CI/CD pipelines ensuring high availability and uptime.
\item Collaborated within Agile teams through code reviews, sprint planning, and Git branching to deliver high-quality, maintainable code.
\item Implemented unit and functional testing with TDD practices throughout SDLC reducing production issues and improving code quality.
\item Mentored junior developers on backend architecture, API design, secure coding standards, and best practices for scalable systems.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level backend services and APIs for financial and operational tracking systems using Python and SQL.
\item Contributed to the design and implementation of scalable solutions for Proposal Management and Mailroom Tracking Systems.
\item Worked closely with cross functional teams to gather requirements, perform testing, and support production deployment phases.
\item Gained hands-on experience in backend development, database optimization, debugging, and secure coding within Agile workflows.
\item Collaborated in project reviews to identify improvements in performance, scalability, code maintainability, and system reliability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Automated Cryptocurrency Trading Bot} -- \emph{Personal Project}

\vspace{-1pt}

Created a Python trading bot using Binance API and WebSocket to automate trade execution with risk control and live monitoring.
\vspace{-1pt}
\begin{itemize}
\item Developed a fully automated trading bot in Python using Binance API and WebSocket for real-time data streaming and order execution.
\item Implemented dynamic trading strategies, stop-loss mechanisms, and risk management algorithms with comprehensive logging for audit.
\item Integrated Pandas and NumPy for market analysis and backtesting to improve trading accuracy and optimize strategy performance.
\item Deployed using Docker on AWS EC2 for 24/7 uptime, reliability, and monitoring with detailed logging and alerting for rapid issue resolution.
\end{itemize}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full-stack LMS using React, Node.js, and MySQL to support online education during the pandemic for 6,000 users.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time progress dashboards for teachers and students.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent usage and scalability.
\item Deployed the platform on AWS with CDN caching, SSL encryption, and load balancing ensuring reliable access and high availability.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}