% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with proven experience building scalable backend services and public-facing APIs using Python, JavaScript, and modern frameworks. Proficient in designing high-performance data models with PostgreSQL, MySQL, and MongoDB while leveraging cloud infrastructure on AWS and GCP. Experienced in Agile collaboration, CI/CD automation, and deploying production systems with Docker and Kubernetes. Passionate about clean code, automated testing, and delivering reliable solutions at scale.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, PHP, SQL, HTML5, CSS3, Bash, PowerShell

\textbf{Frameworks \& Libraries:} Django, Flask, FastAPI, React, Node.js, Express.js, Bootstrap

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQLite, Redis, DynamoDB

\textbf{Cloud \& DevOps:} AWS, GCP, Docker, Kubernetes, GitLab CI/CD, GitHub Actions

\textbf{API \& Web Services:} REST API, GraphQL, WebSockets, Microservices, OAuth, JWT

\textbf{Software Development Practices:} Agile, Scrum, TDD, Unit Testing, Code Reviews, SDLC

\textbf{Systems \& Networking:} Linux, Ubuntu, Nginx, Load Balancing, VPC, Security

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Accountability, Ownership, Curiosity

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable backend services and RESTful APIs using Python and JavaScript to power web and e-commerce applications.
\item Designed and optimized relational database schemas with PostgreSQL and MySQL ensuring efficient query performance at scale.
\item Deployed cloud-based applications on AWS using Docker containers and automated CI/CD pipelines for continuous delivery.
\item Collaborated in Agile teams conducting code reviews, sprint planning, and pair programming to maintain code quality standards.
\item Applied automated testing practices and secure coding principles throughout development lifecycle improving reliability.
\item Led backend architecture design while mentoring team members on best practices in API development and deployment strategies.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in building enterprise web applications focusing on backend API development and database integration components.
\item Contributed to design and implementation of systems including Proposal Management and Mailroom Tracking applications.
\item Collaborated with cross functional teams gathering requirements, performing testing, and supporting production deployments.
\item Gained hands-on experience with full stack development, automated testing, and secure coding within Agile environments.
\item Participated in project reviews identifying opportunities for performance improvements, scalability, and code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed full stack LMS using React, Node.js, and MySQL supporting online education for pandemic learning.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards for instructor visibility.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent usage scenarios.
\item Deployed platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 active students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users and individuals with reading challenges, integrating accessibility features.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Node.js, and Socket.io with accessibility-focused UI following WCAG standards.
\item Integrated AWS Polly and Azure Speech Services to enable text-to-speech and voice-to-text communication capabilities.
\item Tested application with assistive technologies ensuring inclusive usability for users with visual and reading disabilities.
\item Deployed on AWS App Runner with Docker containers for scalable, low-latency communication supporting concurrent users.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}