% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with proven expertise in backend development, cloud infrastructure, and scalable system design. Skilled in Python, Django, SQL databases, and building robust RESTful APIs with strong emphasis on correctness and performance. Experienced in CI/CD automation, Docker, Kubernetes, and AWS deployments across Agile environments. Demonstrated ability to collaborate cross-functionally, maintain production systems, and deliver secure financial-grade solutions with mentorship and technical leadership.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, SQL, PHP, Bash, HTML, CSS, PowerShell

\textbf{Backend Frameworks \& Tools:} Django, Flask, FastAPI, Node.js, Express.js, REST API

\textbf{Database \& Transactions:} PostgreSQL, MySQL, MongoDB, SQLite, Redis, DynamoDB

\textbf{Cloud \& Infrastructure:} AWS, Docker, Kubernetes, Terraform, CI/CD, GitHub Actions

\textbf{Software Engineering Practices:} Agile, Scrum, TDD, System Design, Scalability, Code Reviews

\textbf{Computer Science Fundamentals:} Data Structures, Algorithms, OOP, Design Patterns, Clean Architecture

\textbf{Security \& Reliability:} OAuth, JWT, API Security, Encryption, IAM, High Availability

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Ownership, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable backend services and RESTful APIs using Python, Django, and Node.js to support high-transaction web applications.
\item Optimized SQL queries and database transactions in PostgreSQL and MySQL to improve system reliability and query performance.
\item Deployed and maintained cloud infrastructure on AWS using Docker, Kubernetes, and automated CI/CD pipelines for consistent uptime.
\item Collaborated with cross-functional teams in Agile sprints through code reviews, pair programming, and technical planning sessions.
\item Applied test-driven development and secure coding standards across SDLC reducing production issues and improving maintainability.
\item Led backend development for multiple projects while mentoring junior developers on architecture design and deployment practices.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications across backend and frontend components using modern frameworks and libraries.
\item Contributed to design and implementation of Proposal Management and Mailroom Tracking Systems with scalable architecture patterns.
\item Worked closely with cross-functional teams to gather requirements, perform integration testing, and support production deployments.
\item Gained hands-on experience in backend development, relational databases, secure coding, and Agile workflows during training period.
\item Collaborated in project reviews to identify improvements in performance, scalability, code quality, and system maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS using Python and React enabling 6K+ students to learn with notes, videos, quizzes, and real-time tracking.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed full-stack LMS with React frontend and Python backend using Flask to support online education at scale.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards using SQL database queries.
\item Implemented secure authentication, role-based access control, and optimized database transactions for high concurrent user loads.
\item Deployed platform on AWS with Docker containers, CDN caching, and SSL encryption ensuring reliable access for 6,000+ students.
\end{itemize}

\textbf{Automated Cryptocurrency Trading Bot} -- \emph{Personal Project}

\vspace{-1pt}

Created a Python trading bot using Binance API and WebSocket for automated trade execution with risk control and live monitoring.
\vspace{-1pt}
\begin{itemize}
\item Developed automated trading bot in Python using Binance API and WebSocket for real-time data streaming and order execution logic.
\item Implemented dynamic trading strategies, stop-loss mechanisms, and algorithmic order execution with configurable risk management.
\item Integrated Pandas and NumPy libraries for market analysis, backtesting, and data transformation to improve trading accuracy.
\item Deployed using Docker on AWS EC2 for 24/7 uptime, reliability, and monitoring with detailed logging and alerting mechanisms.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}