% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Web Developer with 3+ years of experience building scalable web applications using JavaScript, TypeScript, React, Django, and Node.js. Proficient in designing optimized data models, implementing RESTful APIs, and deploying cloud-native solutions on AWS and GCP with Docker and Kubernetes. Experienced in Agile methodologies, CI/CD pipelines, technical documentation, and cross-functional collaboration to deliver high-quality software solutions that drive business value.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, TypeScript, SQL, HTML5, CSS3

\textbf{Frameworks \& Libraries:} React, Django, Django Rest Framework, React Query, Node.js, Bootstrap

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, Database Design, SQL Optimization

\textbf{Cloud \& DevOps:} AWS, Google Cloud Platform, Docker, Kubernetes, CI/CD, GitHub Actions

\textbf{Software Development Practices:} Agile, Scrum, SDLC, Code Reviews, Technical Documentation, System Design

\textbf{Security \& IAM:} SSO, OAuth, JWT, IAM, RBAC, API Security

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Ownership, Teamwork

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js with Django backends to enhance functionality.
\item Designed optimized data models and implemented RESTful APIs with secure authentication using OAuth and JWT for robust integrations.
\item Wrote optimized SQL queries to analyze datasets and improve database performance for high-concurrency environments.
\item Deployed cloud-based applications on AWS and GCP using Docker, Kubernetes, and CI/CD pipelines ensuring 99.9\% uptime.
\item Collaborated within Agile teams through code reviews, sprint planning, and technical documentation to deliver quality solutions.
\item Led backend API development while mentoring junior developers on design patterns, testing standards, and deployment best practices.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications using full stack technologies across frontend and backend components.
\item Contributed to designing and implementing scalable systems including Proposal Management and Mailroom Tracking platforms.
\item Worked closely with cross-functional teams to gather requirements, conduct testing, and support deployment phases.
\item Gained hands-on experience in Agile workflows, software testing, technical documentation, and secure coding practices.
\item Collaborated in project reviews to identify performance improvements, scalability enhancements, and code maintainability optimizations.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with notes, videos, quizzes, and real-time progress dashboards for teachers.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack LMS using React, Node.js, and PostgreSQL with optimized data models supporting high concurrent user access.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards leveraging RESTful APIs.
\item Implemented secure authentication with role-based access control and optimized SQL queries for performance under heavy load.
\item Deployed on AWS with Docker containers, CDN caching, and SSL encryption ensuring reliable access for over 6,000 students daily.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed inclusive real-time chat app for low-vision users integrating text-to-speech and voice-to-text accessibility features.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Node.js, and WebSockets with accessibility-focused UI following WCAG standards.
\item Integrated AWS Polly and Azure Speech Services APIs to enable seamless text-to-speech and voice-to-text communication features.
\item Collaborated with cross-functional team to conduct user testing with assistive technologies ensuring inclusive usability.
\item Deployed on AWS with Docker and Kubernetes for scalable, low-latency communication supporting diverse accessibility requirements.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}