% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Frontend Software Engineer with 3+ years of experience building dynamic, user-focused web applications using React, JavaScript, and modern UI frameworks. Proven ability to deliver high-quality features in fast-paced, Agile environments while collaborating closely with cross-functional teams. Experienced in developing accessible, responsive interfaces, optimizing performance, and mentoring peers to improve code quality and team outcomes. Passionate about solving complex problems and shipping scalable solutions.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, HTML5, CSS3, SQL

\textbf{Frontend Frameworks \& Libraries:} React, Redux, Vue.js, Next.js, Bootstrap, Material UI

\textbf{Frontend Tooling \& Styling:} SASS, Tailwind CSS, React Query, ES6, Jest, React Testing Library

\textbf{Backend \& Database:} Node.js, Express.js, Django, PostgreSQL, MongoDB, REST API

\textbf{Cloud \& DevOps:} AWS, Docker, CI/CD, GitHub Actions, Jenkins, Kubernetes

\textbf{Development Practices:} Agile, Scrum, Unit Testing, Code Reviews, TDD, Git

\textbf{Soft Skills:} Communication, Collaboration, Mentorship, Adaptability, Problem Solving, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Built dynamic, responsive UIs using React and modern JavaScript, improving user engagement and application performance.
\item Collaborated with design and backend teams to integrate RESTful APIs and deliver cohesive, high-quality features.
\item Implemented comprehensive unit tests with Jest and React Testing Library, increasing code coverage and reliability.
\item Optimized frontend performance through component refactoring, lazy loading, and efficient state management with Redux.
\item Mentored junior developers on best practices, code structure, and testing methodologies, elevating team output.
\item Worked within Agile sprints, participating in sprint planning, code reviews, and retrospectives to ensure timely delivery.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing frontend components for enterprise web and mobile apps using HTML, CSS, and JavaScript frameworks.
\item Contributed to UI design and implementation, ensuring responsiveness and accessibility across multiple devices.
\item Collaborated with cross-functional teams to gather requirements, troubleshoot UI issues, and support deployment phases.
\item Gained hands-on experience with testing frameworks and secure coding practices in Agile development workflows.
\item Participated in project reviews to identify UI performance improvements and enhance code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS with React, Node.js, and MySQL, enabling 6K+ students to access lessons, quizzes, and performance tracking.
\vspace{-1pt}
\begin{itemize}
\item Developed the frontend using React, implementing reusable components, state management, and responsive UI for seamless user experience.
\item Integrated lesson uploads, quizzes, and real-time progress dashboards, enhancing interactivity for students and teachers.
\item Implemented secure authentication and role-based access control to protect user data and ensure proper permissions.
\item Optimized frontend performance with lazy loading and CDN caching, supporting reliable access for over 6,000 concurrent users.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Built an inclusive real-time chat app using React and Socket.io, integrating accessibility features for low-vision users.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed the frontend with React, focusing on accessibility-first UI adhering to WCAG standards.
\item Integrated AWS Polly and Azure Speech Services for text-to-speech and voice-to-text, improving usability for users with disabilities.
\item Collaborated with team members to test UI with assistive technologies, ensuring inclusive and intuitive user interactions.
\item Deployed the app on AWS App Runner with Docker, delivering scalable, low-latency communication for real-time chat.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}