% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Developer with 2+ years of experience building scalable cloud-based applications and REST APIs using JavaScript, React, Node.js, and AWS. Proficient in microservices architecture, CI/CD pipelines, and agile methodologies with a strong focus on performance, security, and reliability. Experienced in collaborating with cross-functional teams to deliver high-quality solutions that meet business needs while applying modern cloud design patterns and best practices.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, SQL, HTML5, CSS3

\textbf{Frameworks \& Libraries:} React, Node.js, Redux, Bootstrap, Django, Flask

\textbf{Cloud \& DevOps:} AWS (Lambda, EC2, S3, RDS), Docker, Kubernetes, CI/CD Pipelines, GitHub Actions

\textbf{Database \& APIs:} PostgreSQL, MySQL, MongoDB, REST API, GraphQL, Microservices

\textbf{Development Practices:} Agile, Scrum, TDD, Code Reviews, System Design, Performance Optimization

\textbf{Security \& Networking:} OAuth, JWT, HTTPS, Load Balancing, Cloud Security, API Security

\textbf{Soft Skills:} Communication, Team Collaboration, Adaptability, Problem Solving, Ownership, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed full stack applications using JavaScript, React, and Node.js implementing REST APIs and microservices architecture.
\item Deployed cloud-based services on AWS using Docker and CI/CD pipelines ensuring high availability and reliability for end users.
\item Optimized SQL queries and database performance across PostgreSQL and MySQL environments reducing latency and improving throughput.
\item Collaborated in agile teams through sprint planning, code reviews, and pair programming delivering quality software on schedule.
\item Applied security best practices including OAuth, JWT, and HTTPS to build secure modern cloud services meeting compliance standards.
\item Supported production services through on-call rotations troubleshooting incidents and implementing monitoring with logging systems.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to enterprise web application development implementing features across frontend and backend using modern frameworks.
\item Assisted in REST API development and integration within service-oriented architecture supporting distributed system components.
\item Participated in agile workflows collaborating with product owners and designers to gather requirements and deliver solutions.
\item Performed testing and debugging throughout short release cycles ensuring code quality and adherence to development standards.
\item Gained experience in CI/CD deployment pipelines and cloud infrastructure supporting scalable application delivery processes.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS supporting 6K+ students with real-time dashboards, quizzes, and secure authentication using cloud services.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack LMS with React and Node.js implementing REST APIs and microservices for lesson delivery and tracking modules.
\item Integrated secure authentication with role-based access control and optimized database queries for high concurrent user throughput.
\item Deployed on AWS leveraging S3, CloudFront CDN, and SSL encryption ensuring reliable performance and security for thousands of users.
\item Implemented real-time dashboards and caching strategies to support performance optimization and scalability under heavy traffic loads.
\end{itemize}

\textbf{PROSPR " Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed inclusive real-time chat with AWS Polly and Azure Speech Services following WCAG standards for accessible communication.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Node.js, and WebSockets implementing cloud services for text-to-speech capabilities.
\item Integrated AWS Polly and Azure APIs to enable voice communication features aligned with modern accessibility best practices.
\item Followed WCAG security and accessibility standards testing with assistive technologies for inclusive user experience delivery.
\item Deployed using Docker on AWS App Runner with load balancing and autoscaling ensuring low-latency scalable communication service.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}