% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with 2+ years of experience building scalable backend services and full stack applications using Python, FastAPI, Django, React, and Node.js. Proven expertise in cloud infrastructure with AWS, Docker, Kubernetes, and CI/CD pipelines. Skilled in developing AI-powered systems, REST APIs, microservices, and real-time communication platforms. Strong foundation in distributed systems, database optimization, and secure coding practices with hands-on experience deploying production systems on cloud environments.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, TypeScript, SQL, HTML5, CSS3, Bash, PowerShell

\textbf{Backend Frameworks \& Tools:} FastAPI, Django, Flask, Node.js, Express.js, REST API, WebSockets, GraphQL

\textbf{Frontend Frameworks \& Libraries:} React, Next.js, Redux, Bootstrap, Material UI, jQuery

\textbf{Databases \& Vector Systems:} PostgreSQL, MySQL, MongoDB, Redis, DynamoDB, Firebase

\textbf{Cloud \& Infrastructure:} AWS ECS, AWS Lambda, AWS EC2, AWS S3, AWS IAM, VPC, Docker, Kubernetes

\textbf{AI \& Machine Learning:} LLM API, ChatGPT API, Prompt Engineering, AI Integration, Machine Learning APIs

\textbf{DevOps \& CI/CD:} GitHub Actions, Jenkins, Docker Compose, CI/CD Pipelines, Infrastructure as Code

\textbf{Software Development Practices:} Microservices, Agile, Scrum, System Design, Design Patterns, TDD

\textbf{Monitoring \& Security:} Logging, Monitoring, CloudWatch, OAuth, JWT, API Security, Encryption

\textbf{Soft Skills:} Communication, Problem Solving, Collaboration, Ownership, Adaptability, Documentation

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using Python, Django, FastAPI, React, and Node.js to enhance system functionality.
\item Built and deployed RESTful APIs with optimized SQL queries and integrated secure authentication systems using JWT and OAuth.
\item Deployed cloud-based services on AWS using Docker, Kubernetes, and CI/CD pipelines ensuring high availability and uptime.
\item Collaborated in Agile teams through sprint planning, code reviews, and technical design sessions to deliver quality solutions.
\item Applied test-driven development and secure coding practices across distributed microservices improving system reliability.
\item Led backend development initiatives and mentored team members on best practices for scalable architecture and deployment.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications across frontend and backend using Python, JavaScript, and SQL databases.
\item Contributed to design and implementation of management systems with focus on performance optimization and scalability.
\item Collaborated with cross functional teams to gather requirements, perform integration testing, and support deployment cycles.
\item Gained hands-on experience in full stack development, API design, and secure coding standards within Agile methodologies.
\item Participated in project reviews to identify improvements in system architecture, code maintainability, and performance tuning.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive real-time chat application for low-vision users integrating accessibility features and cloud deployment.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat platform using React, Node.js, and WebSockets with accessibility-focused UI following WCAG standards.
\item Integrated AWS Polly and Azure Speech Services APIs to enable text-to-speech and voice-to-text communication workflows.
\item Deployed containerized application on AWS using Docker with load balancing for scalable low-latency communication.
\item Implemented secure authentication, session management, and optimized backend performance for concurrent user connections.
\end{itemize}

\textbf{Automated Cryptocurrency Trading Bot} -- \emph{Personal Project}

\vspace{-1pt}

Created a Python trading bot using Binance API and WebSocket to automate execution with risk control and live monitoring.
\vspace{-1pt}
\begin{itemize}
\item Developed automated trading bot in Python using Binance API and WebSocket for real-time data streaming and order execution.
\item Implemented dynamic trading strategies, stop-loss mechanisms, and algorithms using Pandas and NumPy for market analysis.
\item Deployed on AWS EC2 with Docker for 24/7 uptime, reliability, and comprehensive logging for performance monitoring.
\item Integrated asynchronous processing and error handling to ensure robust execution in distributed cloud environments.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}