% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with expertise in building scalable full-stack applications using React, Python, and Django. Proven experience developing high-performance systems with AWS, Kubernetes, and PostgreSQL while implementing RESTful APIs and event-driven architectures. Skilled in delivering robust solutions through Agile methodologies, CI/CD pipelines, and collaborative development. Strong focus on system reliability, performance optimization, and technical excellence in fast-paced environments.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, TypeScript, SQL, HTML5, CSS3, PHP, Bash

\textbf{Frameworks \& Libraries:} React, Redux, Django, Flask, Node.js, Bootstrap, Material UI

\textbf{Database \& Data Management:} PostgreSQL, DynamoDB, MySQL, MongoDB, Redis, ETL Pipelines

\textbf{Cloud \& DevOps:} AWS, Kubernetes, Docker, CI/CD, GitHub Actions, Infrastructure as Code

\textbf{Architecture \& Design:} Microservices, Event-Driven Architecture, REST API, System Design, Scalability

\textbf{Development Practices:} Agile, Scrum, Unit Testing, Code Reviews, Performance Optimization, TDD

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Problem Solving, Ownership, Attention to Detail

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full-stack web applications using React, JavaScript, and Node.js to enhance product functionality and user experience.
\item Designed and implemented high-performance RESTful APIs with optimized database queries for improved system reliability and throughput.
\item Deployed and maintained cloud-based applications on AWS using Docker, Kubernetes, and CI/CD pipelines ensuring high availability.
\item Collaborated within Agile teams through code reviews, sprint planning, and pair programming to deliver quality features on schedule.
\item Applied test-driven development and performance optimization techniques throughout SDLC reducing production issues and improving speed.
\item Led backend development initiatives while mentoring junior developers on architectural best practices and deployment strategies.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to enterprise web application development across frontend and backend components using modern tech stacks and frameworks.
\item Participated in design and implementation of management systems focusing on scalability, performance, and data integrity requirements.
\item Collaborated with cross-functional teams to gather requirements, execute testing cycles, and support production deployment activities.
\item Gained hands-on experience in full-stack development, API integration, and secure coding practices within Agile team environments.
\item Engaged in project reviews to identify opportunities for performance improvements, code maintainability, and system scalability enhancements.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to access educational content with lessons, quizzes, and real-time progress tracking.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed full-stack LMS using React, Node.js, and MySQL supporting concurrent access for over 6,000 active students.
\item Integrated modules for content uploads, interactive quizzes, and performance dashboards with real-time analytics for instructors.
\item Implemented secure authentication, role-based access control, and optimized queries for high-concurrency scenarios and low latency.
\item Deployed on AWS with CDN caching, SSL encryption, and load balancing ensuring reliable performance and consistent uptime at scale.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed inclusive real-time chat application for low-vision users integrating accessibility features and assistive technologies.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Node.js, and WebSockets with accessibility-focused UI following WCAG compliance standards.
\item Integrated AWS Polly and Azure Speech Services APIs to enable seamless text-to-speech and voice-to-text communication experiences.
\item Conducted extensive testing with assistive technologies to ensure inclusive usability for users with diverse accessibility requirements.
\item Deployed on AWS using Docker containers and autoscaling infrastructure for low-latency, scalable real-time messaging at high volume.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}