% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Developer with proven expertise in full stack development using JavaScript, Python, React, Node.js, and Django. Experienced in building scalable mobile and web applications with REST API integration, cloud deployment on AWS and GCP, and backend optimization. Skilled in collaborating with cross-functional teams using Agile methodologies to deliver high-quality solutions. Passionate about solving complex challenges through clean code and continuous learning.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, TypeScript, PHP, SQL, HTML5, CSS3

\textbf{Backend \& API Development:} Node.js, Django, Flask, FastAPI, Express.js, REST API

\textbf{Frontend Frameworks:} React, Redux, Bootstrap, Material UI, Next.js, Angular

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQLite, Firebase, DynamoDB

\textbf{Cloud \& DevOps:} AWS, Google Cloud Platform, Docker, CI/CD, GitHub Actions, Kubernetes

\textbf{Software Development Practices:} Agile, Scrum, Unit Testing, Design Patterns, Clean Architecture, Code Reviews

\textbf{Machine Learning \& AI:} Machine Learning APIs, AI Integration, Data Science Tools, LLM API, Automation

\textbf{Soft Skills:} Problem Solving, Communication, Collaboration, Continuous Learning, Adaptability, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js to enhance functionality and user experience.
\item Implemented RESTful APIs and integrated third-party services, optimizing performance and ensuring secure, reliable system operations.
\item Deployed cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring high availability and consistent uptime across platforms.
\item Collaborated with cross-functional teams through Agile sprints, code reviews, and pair programming to deliver high-quality solutions.
\item Applied clean code principles and design patterns throughout the software development lifecycle improving maintainability and reducing bugs.
\item Led backend development initiatives and mentored team members on best practices in coding, testing, and deployment automation.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web and mobile applications across frontend and backend components using modern frameworks and tools.
\item Contributed to the design and implementation of business solutions including Proposal Management and Mailroom Tracking Systems.
\item Worked closely with cross-functional teams to gather requirements, perform testing, and support deployment phases effectively.
\item Gained hands-on experience in full stack development, API integration, and secure coding practices within Agile workflows.
\item Participated in project reviews to identify improvements in performance, scalability, and overall code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with notes, videos, and interactive quizzes during the pandemic.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL to support online education during the pandemic.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time progress dashboards for teachers.
\item Implemented secure authentication, role-based access, and optimized database queries for high concurrent usage and scalability.
\item Deployed the platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 students worldwide.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users and individuals with reading challenges, integrating accessibility features.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and Socket.io with accessibility-focused UI design and features.
\item Integrated AWS Polly and Azure Speech Services to enable text-to-speech and voice-to-text communication for diverse users.
\item Followed WCAG accessibility standards and tested with assistive technologies to ensure inclusive usability and compliance.
\item Deployed on AWS App Runner with Docker containers for scalable, low-latency communication and high availability across regions.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}