% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with 4+ years of experience building scalable backend systems and full stack applications. Proficient in Python, JavaScript, and cloud technologies including AWS and GCP. Experienced in API development, database design with PostgreSQL and MySQL, and containerization using Docker and Kubernetes. Strong foundation in algorithms, data structures, and object-oriented programming with proven ability to deliver secure, maintainable enterprise software solutions in Agile environments.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, SQL, PHP, Bash, HTML5, CSS3

\textbf{Backend \& API Development:} Django, Flask, FastAPI, Node.js, REST API, GraphQL

\textbf{Database Technologies:} PostgreSQL, MySQL, MongoDB, Redis, SQLite, DynamoDB

\textbf{Cloud \& DevOps:} AWS, GCP, Docker, Kubernetes, CI/CD, Terraform

\textbf{Development Practices:} Agile, Scrum, TDD, Microservices, System Design, API Security

\textbf{Computer Science Fundamentals:} Algorithms, Data Structures, OOP, Design Patterns

\textbf{Soft Skills:} Problem Solving, Communication, Team Collaboration, Adaptability, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable backend systems and RESTful APIs using Python, Django, and Node.js to support enterprise applications.
\item Optimized PostgreSQL and MySQL database schemas and queries to enhance performance and support high concurrent user loads.
\item Deployed and maintained cloud applications using AWS, Docker, and CI/CD pipelines ensuring 99.9\% uptime and reliability.
\item Implemented secure authentication systems including OAuth and JWT following industry security best practices and protocols.
\item Collaborated with cross-functional teams using Agile methodologies to deliver maintainable code through reviews and sprints.
\item Built containerized microservices with Docker and Kubernetes enabling scalable deployment in multi-tenant SaaS environments.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to backend development of enterprise applications using Python and JavaScript within Agile development workflows.
\item Assisted in designing and implementing scalable data schemas and API integrations for internal management systems.
\item Worked with cross-functional teams to gather requirements, conduct testing, and ensure secure code deployment practices.
\item Gained hands-on experience in full stack development, test-driven development, and cloud technologies including AWS and GCP.
\item Participated in code reviews to improve maintainability, scalability, and adherence to object-oriented programming principles.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS using Python, React, and MySQL enabling 6K+ students to access lessons, quizzes, and progress tracking.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed backend APIs using Python and Node.js with PostgreSQL database to support online education platform.
\item Implemented secure authentication, role-based access control, and RESTful APIs following industry security best practices.
\item Optimized database queries and indexing strategies to handle high concurrent usage with consistent performance and reliability.
\item Deployed on AWS using Docker containers with CI/CD pipelines, SSL encryption, and CDN caching for over 6,000 active users.
\end{itemize}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Automated vulnerability scanning and patch deployment using Python and Jenkins to strengthen enterprise security posture.
\vspace{-1pt}
\begin{itemize}
\item Developed automated workflows using Python, Jenkins, and CI/CD pipelines for vulnerability scanning and patch deployment cycles.
\item Integrated Nessus API for real-time vulnerability reporting, risk prioritization, and security compliance tracking dashboards.
\item Implemented secure authentication and API integrations following enterprise security protocols and OWASP best practices.
\item Reduced manual intervention by 60\% and accelerated patch cycles through containerized deployment using Docker and Kubernetes.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}