% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Software Developer with 2+ years of experience building scalable AI-driven applications using Python, Django, and Flask. Proven expertise in deploying machine learning systems on AWS and Kubernetes with strong knowledge of SQL, PostgreSQL, and MongoDB. Skilled in developing RESTful APIs, implementing CI/CD pipelines, and collaborating cross-functionally in Agile environments. Passionate about mentoring junior developers and applying test-driven development to deliver high-quality solutions.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, SQL, Bash, HTML, CSS

\textbf{AI \& Machine Learning:} Machine Learning APIs, LLM API, ChatGPT API, Prompt Engineering, AI Integration

\textbf{Frameworks \& Libraries:} Django, Flask, FastAPI, React, Node.js

\textbf{Database Management:} PostgreSQL, MySQL, MongoDB, Redis, SQL Server

\textbf{Cloud \& DevOps:} AWS, GCP, Docker, Kubernetes, Jenkins, GitHub Actions

\textbf{Testing \& Quality Assurance:} Unit Testing, Integration Testing, TDD, Automation Testing, Postman

\textbf{Software Development Practices:} Agile, Scrum, REST API, Microservices, System Design, Code Reviews

\textbf{Soft Skills:} Problem Solving, Communication, Collaboration, Adaptability, Mentorship, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using Python, JavaScript, and React integrating AI APIs and machine learning models.
\item Architected and implemented RESTful APIs optimizing PostgreSQL queries to improve system reliability and application performance.
\item Deployed cloud-based applications on AWS using Docker, Kubernetes, and CI/CD pipelines ensuring high availability and uptime.
\item Collaborated within Agile teams through code reviews, sprint planning, and pair programming delivering production-grade solutions.
\item Applied test-driven development and automated testing frameworks improving code maintainability and reducing production defects.
\item Mentored junior developers on Python best practices, DevOps workflows, and secure coding standards to elevate team capabilities.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications across frontend and backend using Python, JavaScript, and SQL databases.
\item Contributed to system architecture design implementing scalable APIs and software components for high-performance applications.
\item Worked closely with cross-functional teams including data scientists and product managers to integrate ML models and features.
\item Gained hands-on experience in full stack development, automated testing, and debugging complex issues in distributed systems.
\item Participated in Agile workflows performing code reviews and sprint retrospectives to improve performance and scalability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS with Python, React, and PostgreSQL enabling 6K+ students to learn with interactive quizzes and dashboards.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack LMS using React, Node.js, and PostgreSQL supporting real-time dashboards and role-based authentication.
\item Integrated secure user authentication, performance tracking modules, and optimized SQL queries for high concurrent usage.
\item Implemented automated testing and CI/CD pipelines using GitHub Actions ensuring code quality and rapid deployment cycles.
\item Deployed platform on AWS with Docker containers, CDN caching, and SSL encryption ensuring reliable access for 6K+ students.
\end{itemize}

\textbf{Automated Cryptocurrency Trading Bot} -- \emph{Personal Project}

\vspace{-1pt}

Created Python trading bot using Binance API and WebSocket to automate trade execution with risk control and live monitoring.
\vspace{-1pt}
\begin{itemize}
\item Developed automated trading bot in Python using Binance API and WebSocket for real-time data streaming and order execution.
\item Implemented dynamic trading strategies, stop-loss mechanisms, and algorithms leveraging Pandas and NumPy for market analysis.
\item Applied unit and integration testing frameworks ensuring reliability and accuracy of trading logic under various market scenarios.
\item Deployed using Docker on AWS EC2 with Kubernetes for 24/7 uptime, monitoring, and detailed logging of all trading activities.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}