% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Full Stack Software Engineer with expertise in TypeScript, React, Next.js, Python, and building user-facing web applications. Proven track record developing scalable internal tools, enhancing system reliability through RESTful APIs, and collaborating with cross-functional teams in Agile environments. Strong technical communicator experienced in mentoring junior engineers, architectural documentation, and delivering fast, snappy web experiences relied upon by thousands of users across diverse stakeholder groups.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} TypeScript, JavaScript, Python, SQL, HTML5, CSS3, Bash, PowerShell

\textbf{Frameworks \& Libraries:} React, Next.js, Node.js, Django, Bootstrap, Redux

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQLite, Redis

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, CI/CD, GitHub Actions, Terraform

\textbf{Software Development Practices:} Agile, Scrum, System Design, Testing, Code Reviews, Pair Programming

\textbf{Computer Science Fundamentals:} Data Structures, Algorithms, OOP, Design Patterns, Clean Architecture

\textbf{Systems \& Networking:} Cloud Computing, Networking, Security Best Practices, Unix/Linux, Scripting

\textbf{Soft Skills:} Communication, Collaboration, Mentorship, Adaptability, Documentation, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed fast and snappy full stack web applications using JavaScript, React, and Node.js serving thousands of users daily.
\item Built and maintained RESTful APIs and optimized SQL queries collaborating with stakeholders across product and engineering teams.
\item Deployed resilient cloud applications using AWS, Docker, and CI/CD pipelines ensuring mission-critical uptime and reliability.
\item Collaborated in Agile teams through code reviews, sprint planning, and pair programming to deliver high-quality features rapidly.
\item Mentored junior engineers on TypeScript, secure coding standards, and architectural design improving team engineering velocity.
\item Produced comprehensive technical documentation to communicate implementations and facilitate knowledge sharing across teams.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to developing enterprise web applications across frontend and backend components using modern JavaScript frameworks.
\item Collaborated with cross-functional teams to gather requirements, perform testing, and support deployment of internal tools.
\item Worked closely with senior engineers through direct pairing sessions to learn best practices in system design and scalability.
\item Gained hands-on experience in Agile workflows, full stack development, and writing maintainable code for mission-critical systems.
\item Participated in architectural discussions and documentation reviews to identify improvements in performance and code quality.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with notes, videos, and quizzes through a fast and snappy web interface.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack LMS using React, Node.js, and MySQL supporting thousands of concurrent users with real-time dashboards.
\item Integrated secure authentication, role-based access control, and optimized database queries for mission-critical uptime.
\item Deployed on AWS with CDN caching and SSL encryption ensuring reliable, high-performance access for over 6,000 active users.
\item Collaborated with educators to gather requirements and translate complex needs into easy-to-understand user experiences.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Built inclusive real-time chat app with accessibility features for low-vision users using TypeScript, React, and Node.js.
\vspace{-1pt}
\begin{itemize}
\item Developed real-time chat application using React, Node.js, and WebSockets with accessibility-focused UI following WCAG standards.
\item Integrated AWS Polly and Azure Speech Services enabling text-to-speech and voice-to-text for inclusive user experiences.
\item Collaborated with team members through pair programming and code reviews to deliver delightful, snappy web application.
\item Deployed on AWS with Docker containers for resilient, scalable, and low-latency communication across diverse user groups.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}