% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Software Engineer with expertise in building secure, scalable distributed systems and cloud infrastructure. Proficient in Python, JavaScript, and modern DevOps practices including Docker, Kubernetes, and CI/CD pipelines. Experienced in developing full stack applications with strong security implementation, API design, and cloud deployment on AWS and GCP. Proven track record in Agile environments, delivering resilient systems while collaborating across teams to ensure quality and performance.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, SQL, Bash, PowerShell, PHP

\textbf{Distributed Systems \& Infrastructure:} Docker, Kubernetes, Microservices, API Gateway, Load Balancing, High Availability

\textbf{Cloud \& DevOps:} AWS, GCP, CI/CD, GitLab, GitHub Actions, Infrastructure as Code

\textbf{Security \& Cryptography:} OAuth, JWT, TLS, Encryption, IAM, Zero Trust Architecture

\textbf{Frameworks \& Tools:} React, Node.js, Django, Flask, PostgreSQL, MongoDB

\textbf{Systems Administration:} Linux, Unix environments, Shell Scripting, Networking, Cloud Networking, VPN

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Critical Thinking, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed secure, scalable full stack applications using JavaScript, React, and Node.js with integrated authentication and encryption.
\item Built and optimized RESTful APIs with secure payment systems, implementing IAM policies and TLS to protect sensitive transactions.
\item Deployed cloud-based applications on AWS using Docker, Kubernetes, and CI/CD pipelines ensuring high availability and reliability.
\item Collaborated in Agile teams through code reviews, sprint planning, and technical design sessions to deliver secure, quality software.
\item Applied secure coding standards, test-driven development, and OWASP principles throughout SDLC to reduce vulnerabilities significantly.
\item Led backend development initiatives while mentoring junior engineers on distributed systems design and secure deployment practices.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to enterprise web applications by developing secure frontend and backend components with focus on system reliability.
\item Assisted in designing and implementing scalable systems including Proposal Management and Mailroom Tracking with role-based access.
\item Collaborated with cross functional teams to gather requirements, perform integration testing, and support secure deployment phases.
\item Gained hands-on experience in full stack development, API security, and distributed systems within Agile and Scrum workflows.
\item Participated in project reviews to identify improvements in performance, security best practices, and overall code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a secure, scalable LMS using distributed architecture, enabling 6K+ students to access lessons, quizzes, and dashboards.
\vspace{-1pt}
\begin{itemize}
\item Designed a distributed full stack LMS with React, Node.js, and MySQL to handle concurrent usage by thousands of students securely.
\item Integrated secure authentication, role-based access control, and encrypted data transmission using JWT and HTTPS for user privacy.
\item Optimized database queries and implemented caching strategies to support high-performance access under heavy concurrent load.
\item Deployed on AWS with CDN, SSL encryption, and monitoring tools ensuring reliable, scalable infrastructure for 6,000+ active users.
\end{itemize}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Automated vulnerability scanning and patching workflows to strengthen enterprise security posture and reduce manual intervention.
\vspace{-1pt}
\begin{itemize}
\item Developed automated security workflows using Python and Jenkins for vulnerability scanning, patch deployment, and risk prioritization.
\item Integrated Nessus API for real-time vulnerability reporting and tracking, improving security compliance and remediation efficiency.
\item Built dashboards and alert systems for monitoring security compliance, incident response, and patch management across infrastructure.
\item Reduced manual intervention by 60\% and accelerated patch cycles using full CI/CD automation and distributed deployment strategies.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}