% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Developer with 5+ years of experience building scalable web applications using JavaScript, PHP, HTML, CSS, and database technologies. Proven expertise in developing e-commerce solutions, integrating APIs, and implementing secure software systems. Skilled in Angular.js, React, and full-stack development with strong focus on client requirements, technical documentation, and delivering solutions under tight deadlines in fast-paced consulting environments.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, PHP, Python, SQL, HTML5, CSS3

\textbf{Frameworks \& Libraries:} Angular.js, React, Node.js, Django, Bootstrap, jQuery

\textbf{Database \& Data Management:} MySQL, PostgreSQL, MongoDB, Database Design, SQL Optimization

\textbf{Cloud \& DevOps:} AWS, Docker, CI/CD Pipelines, GitHub Actions, Infrastructure as Code

\textbf{Software Development Practices:} Agile, Scrum, Testing, Code Reviews, Technical Documentation

\textbf{Security \& Web Technologies:} HTTPS, OAuth, API Security, Data Encryption, OWASP Standards

\textbf{Soft Skills:} Communication, Team Collaboration, Client Focus, Adaptability, Initiative, Judgement

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable e-commerce and web applications using JavaScript, PHP, React, and Angular.js to enhance business functionality.
\item Integrated RESTful APIs, optimized database queries, and implemented secure payment systems improving reliability and performance.
\item Deployed cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and application availability.
\item Collaborated with cross-functional teams through Agile sprints, code reviews, and documentation to meet tight project deadlines.
\item Applied secure coding standards, wrote detailed technical documentation, and maintained software throughout the full SDLC.
\item Communicated technical solutions effectively with clients, gathered requirements, and delivered user-focused software under pressure.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications using JavaScript, HTML, CSS, and database software for frontend and backend.
\item Contributed to design and implementation of business management systems with focus on user requirements and specifications.
\item Worked with cross-functional teams to gather requirements, perform integration testing, and support deployment activities.
\item Gained hands-on experience in full-stack development, software testing, and secure coding within fast-paced Agile workflows.
\item Collaborated in project reviews identifying improvements in performance, code quality, and technical documentation standards.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to access notes, videos, and quizzes with secure authentication and performance tracking.
\vspace{-1pt}
\begin{itemize}
\item Designed full-stack LMS using JavaScript, React, Node.js, and MySQL supporting online education with role-based access control.
\item Integrated lesson uploads, interactive quizzes, and real-time dashboards for teachers to track student performance and progress.
\item Implemented secure authentication, database optimization, and data security procedures ensuring safe access for concurrent users.
\item Deployed on AWS with CDN caching and SSL encryption providing reliable access for over 6,000 students with high availability.
\end{itemize}

\textbf{Custom Business Web Solutions} -- \emph{Personal Project}

\vspace{-1pt}

Built e-commerce sites, POS systems, and inventory management solutions with secure payment integration and responsive design.
\vspace{-1pt}
\begin{itemize}
\item Designed custom web solutions using JavaScript, React, PHP, HTML, and CSS translating business requirements into applications.
\item Implemented secure authentication, inventory tracking, and payment processing with API integration meeting client specifications.
\item Collaborated with clients gathering requirements, providing technical documentation, and delivering user-focused scalable systems.
\item Optimized UI performance, responsiveness, and database queries enhancing user engagement and operational workflow efficiency.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}