% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with proven experience in full stack development using Python, TypeScript, React, and Node.js. Skilled in designing scalable cloud-based applications on AWS, implementing CI/CD pipelines, and building RESTful APIs with PostgreSQL and MongoDB. Strong background in automated testing, Infrastructure as Code with Terraform, and secure coding practices. Collaborative team player with expertise in Agile methodologies, problem-solving, and delivering high-quality software solutions in fast-paced environments.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, TypeScript, JavaScript, SQL, Bash

\textbf{Frontend Development:} React, Redux, HTML5, CSS3, Bootstrap, Material UI

\textbf{Backend \& APIs:} Node.js, Django, Flask, FastAPI, REST API, GraphQL

\textbf{Databases:} PostgreSQL, MongoDB, MySQL, SQLite, Redis

\textbf{Cloud \& DevOps:} AWS (EC2, S3, RDS, Lambda, CloudWatch), Terraform, Docker, Kubernetes, CI/CD

\textbf{Testing \& Quality Assurance:} Unit Testing, Integration Testing, TDD, Postman, Automation Testing

\textbf{Version Control \& Collaboration:} Git, GitHub, GitHub Actions, Jenkins, Code Reviews

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Continuous Learning, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using JavaScript, React, and Node.js to enhance functionality and user experience.
\item Implemented RESTful APIs with optimized SQL queries and secure authentication improving system reliability and performance.
\item Deployed and maintained cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring high availability and uptime.
\item Collaborated within Agile teams through code reviews and sprint planning delivering high-quality software in iterative cycles.
\item Applied test-driven development and automated testing practices throughout SDLC reducing production issues and technical debt.
\item Mentored junior developers on coding best practices, secure development, and deployment strategies fostering team growth and efficiency.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level web applications across frontend and backend components using modern frameworks and tools.
\item Contributed to the design and implementation of management systems with focus on usability, scalability, and maintainability.
\item Worked closely with cross-functional teams to gather requirements, perform testing, and support deployment ensuring project success.
\item Gained hands-on experience in full stack development, automated testing, and secure coding within Agile collaborative environments.
\item Participated in project reviews identifying improvements in performance, code quality, and system architecture for future iterations.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to access notes, videos, and quizzes with real-time performance tracking dashboards.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL supporting online education for thousands of students.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards for educators and administrators.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent user traffic.
\item Deployed the platform on AWS with CDN caching and SSL encryption ensuring reliable, secure access for over 6,000 active users.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive real-time chat app for low-vision users integrating text-to-speech and voice-to-text communication features.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and WebSockets with accessibility-focused UI design and responsive layout.
\item Integrated AWS Polly and Azure Speech Services enabling text-to-speech and voice-to-text communication for inclusive user experience.
\item Followed WCAG accessibility standards and tested with assistive technologies ensuring usability for individuals with visual impairments.
\item Deployed on AWS using Docker containers for scalable, low-latency communication with automated CI/CD pipelines for consistent delivery.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}