% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Developer with progressive experience building scalable web applications using JavaScript, React, and Node.js. Proven ability to design and deliver enterprise-grade software solutions following secure coding standards and industry best practices. Skilled in collaborating with cross-functional teams within Agile environments to analyze requirements, architect solutions, and maintain high code quality through testing and mentorship. Strong problem-solving abilities combined with effective communication skills.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, SQL, HTML5, CSS3

\textbf{Frontend Development:} React, Redux, SASS, Bootstrap, Material UI, Responsive Design

\textbf{Backend Development:} Node.js, Express.js, RESTful APIs, GraphQL, Microservices

\textbf{Database \& Cloud:} PostgreSQL, MySQL, MongoDB, AWS, Docker, CI/CD Pipelines

\textbf{Development Practices:} Agile, Scrum, Unit Testing, Code Reviews, Secure Coding, TDD

\textbf{Soft Skills:} Communication, Collaboration, Mentorship, Problem Solving, Time Management, Adaptability

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js following secure coding and industry best practices.
\item Designed and implemented RESTful APIs with optimized SQL queries to improve system performance and reliability across enterprise platforms.
\item Deployed cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring high availability and consistent system uptime.
\item Collaborated with cross-functional teams including business analysts and architects through Agile sprints and code reviews.
\item Maintained high software quality standards by applying unit testing and test-driven development throughout the software lifecycle.
\item Provided technical leadership and mentorship to junior developers through coaching on coding standards and deployment best practices.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications utilizing JavaScript frameworks across both frontend and backend components.
\item Contributed to design and implementation of management systems while collaborating with delivery leads and business analysts.
\item Worked closely with cross-functional teams to gather requirements, plan development efforts, and compile effort estimates.
\item Gained hands-on experience in full stack development applying secure coding standards within Agile workflows and sprint planning.
\item Participated in code reviews and testing phases to identify improvements in performance, scalability, and maintainability standards.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to access educational content with interactive quizzes and real-time progress tracking.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed full stack LMS using React, Node.js, and MySQL to support online education with interactive features.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards following best practices.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent user loads.
\item Deployed platform on AWS with SSL encryption and CDN caching ensuring reliable access for over 6,000 concurrent students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed inclusive real-time chat application with accessibility features for low-vision users and individuals with reading challenges.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Node.js, and WebSockets with accessibility-focused UI design and semantic HTML.
\item Integrated AWS and Azure speech services to enable text-to-speech and voice-to-text communication for enhanced accessibility.
\item Followed WCAG accessibility standards and tested with assistive technologies ensuring inclusive usability across user groups.
\item Deployed on AWS using Docker containers for scalable, low-latency communication with high availability and performance.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}