% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with 2+ years of experience developing scalable web applications using modern frontend technologies including Angular, React, JavaScript, and TypeScript. Proven expertise in building responsive user interfaces with Material UI and Bootstrap, implementing state management solutions, and integrating RESTful APIs. Experienced in Agile development, CI/CD pipelines, and cloud platforms including AWS and GCP. Strong background in writing clean, maintainable code with unit testing frameworks and collaborating across cross-functional teams to deliver high-quality solutions.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, HTML5, CSS3, SQL

\textbf{Frontend Frameworks \& Libraries:} Angular, React, Bootstrap, Material UI, RxJS, Redux

\textbf{Backend \& API Development:} Node.js, RESTful APIs, Express.js, Django, Microservices

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQLite, Firebase

\textbf{Cloud \& DevOps:} AWS, Google Cloud Platform, Azure, Docker, CI/CD Pipelines, GitHub Actions

\textbf{Testing \& Quality Assurance:} Unit Testing, Jasmine, Integration Testing, TDD, Postman

\textbf{Development Practices:} Agile, Scrum, Code Reviews, Design Patterns, Version Control, Git

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Mentorship, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, TypeScript, and Node.js enhancing functionality and user experience.
\item Implemented RESTful APIs with optimized database queries and integrated secure payment systems improving reliability and performance metrics.
\item Deployed and maintained cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring 99.9\% uptime and consistent availability.
\item Collaborated within Agile teams through code reviews, sprint planning, and cross-functional communication to deliver high-quality solutions.
\item Applied unit testing, TDD practices, and secure coding standards throughout SDLC improving maintainability and reducing production issues.
\item Led backend development for multiple applications while mentoring junior developers on best coding practices and deployment methodologies.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level web applications across frontend and backend components using modern JavaScript frameworks.
\item Contributed to design and implementation of Proposal Management and Mailroom Tracking Systems following Agile development methodologies.
\item Worked closely with cross-functional teams including designers and product managers to gather requirements and support deployment phases.
\item Gained hands-on experience in full stack development, unit testing, integration testing, and secure coding within Agile workflows.
\item Collaborated in code reviews and project retrospectives to identify improvements in performance, scalability, and code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with interactive modules, notes, videos, and real-time progress tracking features.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL supporting online education with responsive UI design components.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards for teachers and role-based access control.
\item Implemented secure authentication, optimized database queries, and state management to support high concurrent usage and scalability.
\item Deployed the platform on AWS with CDN caching and SSL encryption ensuring reliable, high-performance access for over 6,000 active users.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive real-time chat app for low-vision users integrating accessibility features and text-to-speech functionality.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and WebSockets with accessibility-focused responsive UI design and Material components.
\item Integrated AWS and Azure cloud services to enable text-to-speech and voice-to-text communication for inclusive user accessibility standards.
\item Followed WCAG accessibility guidelines and tested with assistive technologies ensuring compliance and inclusive usability for diverse user groups.
\item Deployed on AWS with Docker containers for scalable, low-latency communication supporting real-time messaging and high-performance delivery.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}