% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Backend Software Engineer with 1+ years of experience building scalable microservices and RESTful APIs using Python, JavaScript, and Node.js. Proven ability to design event-driven architectures and deploy cloud-based solutions on AWS and GCP with Docker and CI/CD pipelines. Experienced in optimizing SQL databases, implementing secure authentication systems, and collaborating with cross-functional teams to deliver high-impact features that drive user engagement and business growth.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, PHP, SQL, Bash

\textbf{Backend Frameworks \& Tools:} Node.js, Django, Flask, FastAPI, Express.js

\textbf{Databases \& Data Systems:} PostgreSQL, MySQL, MongoDB, Redis, SQLite

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, CI/CD, GitHub Actions, Terraform

\textbf{Architecture \& Design:} Microservices, REST API, Event-Driven Architecture, System Design, Scalability

\textbf{Development Practices:} Agile, Scrum, TDD, Code Reviews, Testing, Debugging

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Ownership, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable backend services and RESTful APIs using JavaScript, Node.js, and Python to support high-traffic e-commerce platforms.
\item Designed event-driven microservices and optimized SQL queries in PostgreSQL and MySQL to improve system performance and reliability.
\item Deployed cloud-based applications on AWS using Docker, Kubernetes, and CI/CD pipelines ensuring 99.9\% uptime and consistent availability.
\item Collaborated with Product, Marketing, and cross-functional teams through Agile sprints to deliver data-driven features that improved user engagement.
\item Implemented automated testing frameworks and secure coding standards reducing production issues by 40\% and accelerating release cycles.
\item Mentored junior developers on backend architecture, API design, and deployment best practices while conducting thorough code reviews.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to backend development of enterprise systems including Proposal Management and Mailroom Tracking using Python and SQL databases.
\item Collaborated with cross-functional teams to gather requirements, design scalable APIs, and support deployment phases in Agile workflows.
\item Assisted in building automation scripts and background job processing to improve system efficiency and reduce manual operational overhead.
\item Participated in testing, debugging, and performance optimization efforts ensuring high-quality service delivery and system stability.
\item Gained hands-on experience with microservice architecture, database design, and secure authentication mechanisms in production environments.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to access lessons, quizzes, and performance tracking with real-time dashboards for educators.
\vspace{-1pt}
\begin{itemize}
\item Designed backend services using Node.js and Express.js with RESTful APIs to handle user authentication, lesson delivery, and quiz management.
\item Implemented MySQL database schema optimized for high concurrency with indexing and query optimization for real-time performance tracking.
\item Integrated background job processing for automated quiz scoring and notification delivery using event-driven architecture patterns.
\item Deployed on AWS with EC2, S3, and CloudFront CDN ensuring secure SSL encryption and reliable access for over 6,000 concurrent users.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive real-time chat application with accessibility features for low-vision users and individuals with reading challenges.
\vspace{-1pt}
\begin{itemize}
\item Built backend services with Node.js and Socket.io enabling real-time messaging, user presence tracking, and event-driven notifications.
\item Integrated AWS Polly and Azure Speech Services APIs for text-to-speech and voice-to-text processing with low-latency response times.
\item Designed RESTful APIs for user authentication, session management, and message persistence using MongoDB for scalable data storage.
\item Deployed microservices on AWS App Runner with Docker containerization ensuring high availability and seamless scalability under load.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}