% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with 2+ years of experience building scalable full stack web applications using JavaScript, React, and Node.js. Proven ability to develop microservices, RESTful APIs, and cloud-based solutions on AWS with Docker and Kubernetes. Strong foundation in Agile methodologies, CI/CD pipelines, and performance optimization. Eager to leverage technical expertise and entrepreneurial mindset to deliver high-impact features for rapidly growing platforms.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, SQL, HTML5, CSS3, PHP, Bash

\textbf{Frontend Technologies:} React, Redux, Bootstrap, Material UI, Next.js, Responsive Design

\textbf{Backend \& APIs:} Node.js, Express.js, Django, REST API, GraphQL, Microservices

\textbf{Databases:} PostgreSQL, MySQL, MongoDB, SQLite, Redis, DynamoDB

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, Terraform, CI/CD, GitHub Actions

\textbf{Development Practices:} Agile, Scrum, TDD, Code Reviews, System Design, Performance Optimization

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Ownership, Problem Solving

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js enhancing e-commerce functionality and user experience.
\item Implemented RESTful APIs, optimized SQL queries, and integrated secure payment processing to improve system reliability and performance.
\item Deployed and maintained cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and high availability.
\item Collaborated within Agile teams through code reviews, sprint planning, and pair programming to deliver high-quality software solutions.
\item Applied test-driven development and secure coding standards throughout SDLC reducing production issues and improving maintainability.
\item Led backend development for multiple applications while mentoring junior developers on best practices, coding standards, and deployment.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level web and mobile applications across both frontend and backend components using modern frameworks.
\item Contributed to the design and implementation of Proposal Management and Mailroom Tracking Systems improving operational efficiency.
\item Worked closely with cross-functional teams to gather requirements, perform testing, and support deployment phases in Agile environment.
\item Gained hands-on experience in full stack development, software testing, and secure coding within structured Agile workflows and sprints.
\item Collaborated in project reviews to identify improvements in performance, scalability, and code maintainability across multiple projects.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes efficiently.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL to support online education during the pandemic effectively.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time progress dashboards for teachers and students.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent user traffic and performance.
\item Deployed the platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 students with minimal downtime.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users and individuals with reading challenges integrating accessibility features.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and Socket.io with accessibility-focused UI design and intuitive navigation.
\item Integrated AWS Polly and Azure Speech Services to enable text-to-speech and voice-to-text communication for enhanced user accessibility.
\item Followed WCAG accessibility standards and tested with assistive technologies to ensure inclusive usability and compliance with best practices.
\item Deployed on AWS App Runner with Docker containers for scalable, low-latency communication ensuring high performance and reliability.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}