% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Full Stack Software Engineer with 3+ years of experience building scalable web applications using React, Django, Node.js, and cloud technologies. Proficient in backend API development with Django Rest Framework, frontend integration with TypeScript and React Query, and deploying containerized systems on Kubernetes and GCP. Strong background in database design, CI/CD pipelines, and Agile methodologies with expertise in technical communication and stakeholder collaboration.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, TypeScript, SQL, HTML5, CSS3, Bash

\textbf{Frameworks \& Libraries:} Django Rest Framework, React, React Query, Node.js, Bootstrap, Redux

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, Database Design, SQL Optimization, Data Modeling

\textbf{Cloud \& DevOps:} Google Cloud Platform, AWS, Docker, Kubernetes, Helm, CI/CD, GitHub Actions

\textbf{Software Development Practices:} Agile, Scrum, SDLC, TDD, Code Reviews, Technical Documentation

\textbf{Security \& IAM:} SSO, MFA, RBAC, OAuth, JWT, IAM Policies, API Security

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Analytical Thinking, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using React, TypeScript, and Django Rest Framework to deliver robust user experiences.
\item Designed and implemented RESTful APIs with optimized SQL queries and database models improving system performance by 30 percent.
\item Deployed containerized applications using Docker and Kubernetes on GCP with CI/CD pipelines ensuring consistent high availability.
\item Collaborated in Agile teams conducting code reviews, writing technical documentation, and leading design demos for stakeholders.
\item Applied test-driven development and IAM best practices including RBAC and SSO to enhance security and maintain compliance standards.
\item Mentored junior developers on backend architecture, API design, and cloud deployment practices driving team technical growth.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to full stack development of enterprise web applications using React and backend frameworks across multiple projects.
\item Designed database schemas and implemented denormalization techniques to optimize query performance and data retrieval efficiency.
\item Collaborated with cross functional teams to gather requirements, sequence implementation tasks, and provide accurate complexity estimates.
\item Participated in Agile ceremonies including sprint planning and retrospectives to improve delivery timelines and product quality.
\item Supported deployment and monitoring activities using CI/CD tools and cloud telemetry ensuring reliable production environments.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS using React, Node.js, and MySQL enabling 6K+ students to access lessons, quizzes, and performance tracking.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack architecture with React frontend and Node.js backend implementing RESTful APIs and optimized database models.
\item Integrated real-time progress dashboards, role-based access control, and secure authentication using JWT and OAuth standards.
\item Optimized SQL queries and implemented caching strategies to handle high concurrent usage and ensure sub-second response times.
\item Deployed on AWS with Docker containers, CDN distribution, and SSL encryption achieving 99.9 percent uptime for 6000 plus users.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive real-time chat app using React, Node.js, and Socket.io with integrated accessibility features for diverse users.
\vspace{-1pt}
\begin{itemize}
\item Built real-time messaging system using React, Node.js, and Socket.io following WCAG accessibility standards for inclusive design.
\item Integrated AWS Polly and Azure Speech Services APIs enabling text-to-speech and voice-to-text communication for low-vision users.
\item Conducted extensive testing with assistive technologies to validate usability and ensure compliance with accessibility guidelines.
\item Deployed containerized application on AWS with Docker and autoscaling for reliable, low-latency communication across user base.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}