% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with 2+ years building scalable full stack applications using Python, JavaScript, and React. Proven experience in DevOps automation, CI/CD pipeline design, and containerized deployments with Docker and Kubernetes across AWS and GCP. Adept at developing microservices, implementing automated testing suites, and collaborating with cross-functional teams to deliver high-quality solutions that enhance reliability and performance.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, Bash, PowerShell, SQL, HTML5, CSS3

\textbf{Frameworks \& Libraries:} React, Next.js, Django, Flask, FastAPI, Node.js

\textbf{DevOps \& Infrastructure:} Docker, Kubernetes, CI/CD, Jenkins, GitHub Actions, Terraform

\textbf{Cloud Platforms:} AWS, Google Cloud Platform, AWS Lambda, AWS EC2, AWS S3, CloudFormation

\textbf{Testing \& Automation:} Unit Testing, Integration Testing, Automation Testing, TDD, Postman

\textbf{Database Management:} PostgreSQL, MySQL, MongoDB, Redis, SQLite

\textbf{Development Practices:} Agile, Scrum, Microservices, REST API, Code Reviews, SDLC

\textbf{Soft Skills:} Communication, Team Collaboration, Adaptability, Problem Solving, Ownership, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using Python, JavaScript, and React to enhance e-commerce functionality and system reliability.
\item Built and maintained CI/CD pipelines with GitHub Actions and Docker improving deployment automation and reducing release cycles.
\item Deployed and managed containerized applications on AWS using Docker and Kubernetes ensuring high availability and consistent uptime.
\item Implemented automated testing suites including unit and integration tests to improve code quality and reduce production issues.
\item Optimized RESTful APIs and database queries to enhance performance, scalability, and system responsiveness under high traffic.
\item Collaborated with cross-functional Agile teams through code reviews and sprint planning to deliver high-quality software solutions.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications using modern frameworks across frontend and backend components.
\item Contributed to design and implementation of Proposal Management and Mailroom Tracking Systems with integrated automation features.
\item Worked with cross-functional teams to gather requirements, perform testing, and support deployment phases within Agile workflows.
\item Gained hands-on experience in full stack development, automated testing, and secure coding practices throughout the SDLC.
\item Collaborated in project reviews identifying improvements in performance, scalability, and maintainability of production systems.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Automated vulnerability scanning and patching workflows to strengthen enterprise security and reduce manual remediation effort.
\vspace{-1pt}
\begin{itemize}
\item Developed automated CI/CD workflows using Python, Jenkins, and Bash for vulnerability scanning and patch deployment automation.
\item Integrated Nessus API for real-time vulnerability reporting, risk prioritization, and compliance tracking across environments.
\item Built monitoring dashboards and alert systems to track security compliance, remediation progress, and system health metrics.
\item Reduced manual intervention by 60\% and accelerated patch cycles through full automation and continuous integration practices.
\end{itemize}

\textbf{Automated Cryptocurrency Trading Bot} -- \emph{Personal Project}

\vspace{-1pt}

Created a Python trading bot using Binance API and WebSocket for automated trade execution with risk control and live monitoring.
\vspace{-1pt}
\begin{itemize}
\item Developed a fully automated trading bot in Python using Binance API and WebSocket for real-time data streaming and execution.
\item Implemented dynamic trading strategies, stop-loss mechanisms, and order execution algorithms with comprehensive error handling.
\item Integrated Pandas and NumPy for market analysis and backtesting to improve trading accuracy and strategy optimization.
\item Deployed using Docker on AWS EC2 with automated logging and monitoring ensuring 24/7 uptime and system reliability.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}