% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with hands-on experience building scalable web applications, RESTful APIs, and cloud-native solutions using TypeScript, JavaScript, Node.js, and React. Proven ability to deliver production-ready features in Agile environments while collaborating across cross-functional teams. Skilled in AWS, Docker, Kubernetes, and CI/CD pipelines with a strong foundation in microservices architecture and system design. Passionate about performance optimization, engineering excellence, and continuous learning.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, SQL, HTML5, CSS3

\textbf{Backend Development:} Node.js, REST API, Microservices, Express.js, Django, GraphQL

\textbf{Frontend Technologies:} React, Redux, Bootstrap, Material UI, jQuery

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, Redis, DynamoDB

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, CI/CD, GitHub Actions, Jenkins

\textbf{Software Development Practices:} Agile, Scrum, System Design, Code Reviews, TDD, SDLC

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Continuous Learning, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable web applications using JavaScript, TypeScript, React, and Node.js to deliver high-performance user experiences.
\item Designed and built RESTful APIs handling thousands of requests per second ensuring reliability, scalability, and maintainability.
\item Deployed cloud-based solutions on AWS using Docker, Kubernetes, and automated CI/CD pipelines for consistent production uptime.
\item Collaborated within Agile teams through code reviews, sprint planning, and technical discussions to deliver quality features.
\item Applied TDD and secure coding practices throughout SDLC reducing bugs and improving overall code quality and performance.
\item Mentored junior developers on backend development, distributed systems, and deployment best practices while driving excellence.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications across frontend and backend components using modern frameworks and libraries.
\item Contributed to system design and implementation of management platforms improving operational workflows and user experience.
\item Worked closely with cross-functional teams gathering requirements, performing testing, and supporting deployment phases.
\item Gained hands-on experience in full stack development, software testing, and secure coding practices within Agile workflows.
\item Participated in project reviews identifying performance improvements, scalability enhancements, and code maintainability optimizations.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS platform enabling 6K+ students to access lessons, quizzes, and real-time progress tracking during pandemic.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed full stack LMS using React, Node.js, and MySQL supporting high concurrent usage for online education.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards for educators and students.
\item Implemented secure authentication, role-based access control, and optimized database queries for efficient data retrieval.
\item Deployed platform on AWS with CDN caching, SSL encryption, and autoscaling ensuring reliable access for thousands of users.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed inclusive real-time chat application for low-vision users integrating accessibility features and speech services.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Node.js, and Socket.io with accessibility-focused UI adhering to WCAG standards.
\item Integrated AWS Polly and Azure Speech Services enabling seamless text-to-speech and voice-to-text communication features.
\item Tested with assistive technologies ensuring inclusive usability and compliance with accessibility guidelines for diverse users.
\item Deployed on AWS App Runner with Docker containers for scalable, low-latency, and reliable real-time communication delivery.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}