% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with hands-on experience building full stack web applications using Python, JavaScript, React, and Node.js. Proven ability to deliver scalable solutions with cloud technologies including AWS, Docker, and Kubernetes while collaborating in Agile teams. Passionate about leveraging technology to solve real-world problems and eager to contribute to innovative product development that creates meaningful impact for users.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, TypeScript, SQL, HTML5, CSS3

\textbf{Frameworks \& Libraries:} React, Redux, Node.js, Django, Flask, FastAPI

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, Redis, Firebase

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, CI/CD, GitHub Actions, Terraform

\textbf{Software Development Practices:} Agile, Scrum, REST API, Testing, Code Reviews

\textbf{Computer Science Fundamentals:} Data Structures, Algorithms, OOP, Design Patterns, System Design

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Problem Solving, Ownership, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Built production-ready full stack applications using JavaScript, React, and Node.js to deliver scalable e-commerce solutions.
\item Designed and implemented RESTful APIs with optimized database queries, improving system performance and user experience.
\item Deployed cloud applications using AWS, Docker, and CI/CD pipelines ensuring 99.9\% uptime and rapid feature delivery.
\item Collaborated cross-functionally in Agile teams through code reviews, sprint planning, and pair programming sessions.
\item Applied engineering excellence with test-driven development and secure coding standards throughout the development lifecycle.
\item Mentored and upleveled junior developers by sharing best practices in coding, testing, and deployment workflows.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to enterprise applications spanning frontend and backend technologies, shipping production code regularly.
\item Owned project components from requirements gathering through deployment for Proposal Management and Mailroom Systems.
\item Worked cross-functionally with diverse teams to deliver high-quality solutions aligned with business requirements.
\item Gained hands-on experience building scalable software using full stack technologies within Agile development workflows.
\item Drove continuous improvement by identifying performance optimizations and maintainability enhancements during code reviews.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack LMS using React, Node.js, and MySQL supporting real-time progress tracking for educators and students.
\item Integrated lesson uploads, interactive quizzes, and analytics dashboards enabling data-driven insights for improved learning.
\item Implemented secure authentication with role-based access control and optimized queries for high concurrent user loads.
\item Deployed on AWS infrastructure with CDN caching and SSL encryption, reliably serving over 6,000 active students daily.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users and individuals with reading challenges, integrating accessibility features.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Node.js, and Socket.io with accessibility-first UI design and interactions.
\item Integrated AWS Polly and Azure Speech Services enabling seamless text-to-speech and voice-to-text communication features.
\item Followed WCAG accessibility standards and validated usability with assistive technologies ensuring inclusive user experience.
\item Deployed using Docker containers on AWS App Runner for scalable, low-latency communication supporting diverse user needs.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}