% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with proven expertise in backend development, data engineering, and API design using Python, SQL, and cloud technologies. Experienced in building scalable data pipelines, ETL workflows, and automation tools across AWS and GCP environments. Strong collaborator skilled in Agile methodologies, CI/CD practices, and delivering tested, documented solutions that drive data-driven insights and operational efficiency across cross-functional teams.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, SQL, Bash, PHP, HTML, CSS, PowerShell

\textbf{Data Engineering \& Analytics:} ETL Pipelines, Pandas, NumPy, Data Visualization, PostgreSQL, MySQL, MongoDB

\textbf{Backend \& API Development:} REST API, Django, Flask, FastAPI, Node.js, Microservices

\textbf{Cloud \& DevOps:} AWS, GCP, Docker, Kubernetes, CI/CD, GitHub Actions, GitLab CI/CD

\textbf{Development Tools \& Practices:} Git, Jira, Agile, Scrum, Unit Testing, Technical Documentation

\textbf{Soft Skills:} Collaboration, Communication, Problem Solving, Adaptability, Ownership, Critical Thinking

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack applications using Python, JavaScript, and React to enhance business functionality and user experience.
\item Designed and implemented RESTful APIs, optimized SQL queries, and built secure backend services improving system reliability by 30\%.
\item Built and maintained ETL pipelines and data processing workflows using Pandas and NumPy for analytics and reporting automation.
\item Deployed cloud-based applications on AWS using Docker, Kubernetes, and CI/CD pipelines ensuring consistent uptime and scalability.
\item Collaborated with cross-functional teams through Agile workflows, code reviews, and sprint planning to deliver high-quality software.
\item Applied test-driven development and standards-compliant practices throughout SDLC reducing production issues and improving maintainability.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level applications across frontend and backend components using modern software engineering practices.
\item Contributed to design and implementation of data management systems including backend API services and database integration.
\item Worked closely with cross-functional teams to gather requirements, perform testing, and support deployment phases using Git workflows.
\item Gained hands-on experience in full stack development, containerization, and secure coding within Agile and Scrum environments.
\item Collaborated in project reviews to identify improvements in performance, scalability, and code maintainability across multiple projects.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with notes, videos, and quizzes using full stack technologies and cloud infrastructure.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL to support online education with real-time performance tracking.
\item Built backend REST APIs for lesson uploads, quizzes, and student progress dashboards with optimized SQL queries for high concurrency.
\item Implemented secure authentication, role-based access control, and data validation ensuring OWASP compliance and API security standards.
\item Deployed on AWS with Docker, CDN caching, and SSL encryption ensuring reliable access and performance for over 6,000 concurrent users.
\end{itemize}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Automated vulnerability scanning and patching workflows to strengthen enterprise security and reduce manual remediation effort by 60%.
\vspace{-1pt}
\begin{itemize}
\item Developed automated workflows using Python, Jenkins, and CI/CD pipelines for vulnerability scanning and patch deployment across systems.
\item Integrated Nessus API for real-time vulnerability reporting, risk prioritization, and automated remediation tracking and alert generation.
\item Created data visualization dashboards using Python libraries to track security compliance metrics and remediation progress in real time.
\item Reduced manual intervention by 60\% and accelerated patch cycles through full automation and documented deployment processes for operations.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}