% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Full Stack Software Engineer with 2+ years of experience building scalable web applications and cloud infrastructure. Expertise in JavaScript, TypeScript, React, and Node.js with proven ability to deliver end-to-end features across frontend and backend systems. Strong background in AWS services, CI/CD pipelines, and Agile methodologies. Passionate about solving complex problems, collaborating cross-functionally, and driving continuous improvement in fast-paced environments.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, SQL, HTML5, CSS3

\textbf{Frontend Technologies:} React, Redux, Material UI, Bootstrap, Tailwind CSS, Responsive Design

\textbf{Backend \& APIs:} Node.js, Express.js, REST API, GraphQL, Serverless, Microservices

\textbf{Database \& Storage:} PostgreSQL, MySQL, MongoDB, DynamoDB, Redis, AWS S3

\textbf{Cloud \& DevOps:} AWS (Lambda, ECS, RDS, S3), Docker, Terraform, GitHub Actions, CI/CD

\textbf{Development Practices:} Agile, Scrum, TDD, Code Reviews, System Design, Performance Optimization

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Ownership, Problem Solving, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed full stack web applications using JavaScript, TypeScript, React, and Node.js to deliver scalable e-commerce solutions.
\item Built and optimized RESTful APIs with PostgreSQL and integrated secure payment systems to enhance reliability and performance.
\item Deployed cloud-based applications on AWS using Docker, Lambda, and CI/CD pipelines ensuring high availability and uptime.
\item Collaborated with cross-functional teams through Agile sprints, code reviews, and pair programming to ship quality features.
\item Applied test-driven development and security best practices throughout SDLC reducing production issues and technical debt.
\item Led backend architecture for multiple applications while mentoring team members on coding standards and deployment practices.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in building enterprise web and mobile applications across frontend and backend using React and Node.js frameworks.
\item Contributed to design and implementation of Proposal Management and Mailroom Tracking Systems with database integration.
\item Worked with cross-functional teams to gather requirements, perform testing, and support deployment in Agile environments.
\item Gained hands-on experience in full stack development, automated testing, and secure coding practices within production systems.
\item Participated in project reviews to identify performance improvements, scalability enhancements, and code maintainability optimizations.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack LMS using React, Node.js, and PostgreSQL to support online education with real-time dashboards for educators.
\item Integrated lesson uploads, quizzes, and performance tracking modules with secure authentication and role-based access control.
\item Optimized database queries and implemented caching strategies to handle high concurrent usage across thousands of active users.
\item Deployed platform on AWS with Lambda, S3, and CloudFront CDN ensuring reliable access, SSL encryption, and 99.9\% uptime.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users and individuals with reading challenges, integrating accessibility features.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Node.js, and WebSockets with accessibility-focused UI following WCAG standards.
\item Integrated AWS Polly and speech services to enable text-to-speech and voice-to-text communication for inclusive user experience.
\item Tested application with assistive technologies to ensure usability for users with visual impairments and reading challenges.
\item Deployed on AWS using Docker containers and ECS for scalable, low-latency communication with monitoring and logging setup.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}