% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Developer with 3+ years of experience building scalable, cloud-based microservices and full stack applications using JavaScript, React, Node.js, and AWS. Proven expertise in event-driven architecture, CI/CD pipelines, RESTful APIs, and production system operations. Adept at collaborating within Agile teams to deliver high-quality, testable code that powers business-critical platforms with high availability and low latency for seamless user experiences.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, SQL, HTML5, CSS3

\textbf{Backend \& API Development:} Node.js, Express.js, REST API, GraphQL, Microservices, Event-Driven Architecture

\textbf{Cloud \& Serverless:} AWS Lambda, AWS S3, AWS RDS, AWS EC2, DynamoDB, Serverless

\textbf{Database Technologies:} PostgreSQL, MySQL, MongoDB, DynamoDB, Redis

\textbf{DevOps \& CI/CD:} Docker, Jenkins, GitHub Actions, CI/CD, Infrastructure as Code, CloudWatch

\textbf{Frontend Technologies:} React, Redux, Bootstrap, Material UI, Responsive Design

\textbf{Testing \& Quality Assurance:} Unit Testing, Integration Testing, TDD, Postman, Automation Testing

\textbf{Security \& Authentication:} OAuth, JWT, SSO, IAM, API Security, Encryption

\textbf{Agile \& Collaboration:} Scrum, Agile, Jira, Code Reviews, Technical Documentation

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Problem Solving, Ownership, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable microservices and full stack applications using JavaScript, React, and Node.js on AWS for high availability systems.
\item Built and optimized RESTful APIs with event-driven architecture improving system reliability and supporting seamless user experiences.
\item Deployed cloud-based applications using Docker, AWS Lambda, and CI/CD pipelines ensuring consistent uptime and operational excellence.
\item Collaborated in Agile Scrum teams through code reviews and sprint planning delivering high-quality testable code on schedule.
\item Applied continuous delivery practices and secure coding standards across SDLC reducing production issues and improving maintainability.
\item Led backend development for distributed systems while mentoring developers on best practices for microservices and cloud deployments.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications using full stack technologies across frontend and backend components.
\item Contributed to design and implementation of scalable systems for Proposal Management and Mailroom Tracking applications.
\item Worked closely with cross functional teams to gather requirements perform testing and support deployment in Agile workflows.
\item Gained hands-on experience in monitoring production systems and ensuring operational aspects were considered in engineering work.
\item Collaborated in project reviews to identify improvements in performance scalability and code quality for business-critical systems.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes using AWS.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React and Node.js with event-driven updates for real-time progress tracking dashboards.
\item Implemented secure authentication with JWT and role-based access control ensuring high-quality testable code throughout development.
\item Optimized MySQL queries and integrated caching to support high concurrent usage with low latency for thousands of active students.
\item Deployed on AWS using S3 for content delivery CloudWatch for monitoring and CI/CD pipelines for continuous delivery automation.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive real-time chat app for low-vision users integrating text-to-speech and voice-to-text with AWS cloud services.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React Node.js and WebSockets with event-driven architecture for seamless messaging experiences.
\item Integrated AWS Lambda and S3 for serverless processing and storage ensuring scalable highly available infrastructure on AWS cloud.
\item Followed Agile development and accessibility standards delivering testable performant code through CI/CD pipelines with Docker containers.
\item Deployed on AWS with CloudWatch monitoring and optimized API Gateway for low latency operations supporting geographically diverse users.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}