% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Full Stack Software Engineer with 2+ years of experience building scalable SaaS platforms and enterprise applications using React, TypeScript, Python, and cloud infrastructure. Proven track record in designing secure, high-performance systems including real-time collaboration tools, authentication frameworks, and platform-level integrations. Experienced in delivering intuitive user experiences for thousands of concurrent users while maintaining rigorous security and reliability standards. Strong background in Agile development, CI/CD automation, and cross-functional collaboration.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Frontend Development:} React, TypeScript, JavaScript, HTML5, CSS3, Tailwind CSS

\textbf{Backend Development:} Python, Node.js, Django, Flask, FastAPI, RESTful APIs

\textbf{Database \& Infrastructure:} PostgreSQL, MySQL, MongoDB, Redis, AWS, Docker

\textbf{DevOps \& Automation:} CI/CD, GitHub Actions, Kubernetes, AWS Lambda, Terraform

\textbf{Security \& Authentication:} OAuth, JWT, SSO, IAM, TLS/HTTPS, OWASP

\textbf{Development Practices:} Agile, Scrum, TDD, Code Reviews, System Design, Documentation

\textbf{Soft Skills:} Ownership, Communication, Collaboration, Adaptability, Problem Solving

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed full stack applications using React, TypeScript, and Node.js to deliver scalable SaaS solutions for e-commerce clients.
\item Built secure authentication systems and RESTful APIs with role-based permissions enabling multi-tenant enterprise workflows.
\item Deployed cloud infrastructure on AWS using Docker, Lambda, and CI/CD pipelines ensuring 99.9\% uptime and rapid feature delivery.
\item Collaborated with product and design teams through Agile sprints to ship user-facing features balancing simplicity and functionality.
\item Implemented feature flagging and notification systems supporting gradual rollouts and improved customer engagement metrics.
\item Mentored junior engineers on coding standards, security best practices, and platform architecture accelerating team productivity.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Built frontend and backend components for enterprise web applications supporting workflow automation and document management systems.
\item Contributed to secure authentication, permissions frameworks, and data integrations across multiple internal product lines.
\item Collaborated with cross-functional teams to gather requirements, conduct testing, and deploy features in Agile environments.
\item Gained expertise in full stack development, system reliability, and secure coding practices within fast-paced engineering teams.
\item Participated in code reviews and design discussions to optimize performance, maintainability, and scalability of platform features.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack platform using React, Node.js, and PostgreSQL supporting concurrent access for thousands of active learners.
\item Implemented secure authentication, role-based permissions, and admin controls enabling teachers to manage classrooms efficiently.
\item Integrated real-time dashboards and notification systems tracking student progress and quiz performance across multiple courses.
\item Deployed on AWS with CDN caching, SSL encryption, and automated backups ensuring high availability and data privacy compliance.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users integrating accessibility features and real-time communication.
\vspace{-1pt}
\begin{itemize}
\item Built real-time collaboration platform using React, Node.js, and WebSockets with accessibility-focused UI and WCAG compliance.
\item Integrated AWS Polly and Azure Speech Services enabling text-to-speech and voice-to-text for inclusive user experiences.
\item Implemented secure authentication, feature flagging, and notification infrastructure supporting multi-user collaboration workflows.
\item Deployed on AWS with Docker containers and autoscaling ensuring low-latency communication for distributed user base.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}