% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Full Stack Software Developer with proven experience designing and deploying scalable web applications using JavaScript, React, Node.js, and cloud platforms. Skilled in Agile methodologies, CI/CD pipelines, and cross-functional collaboration. Proficient in both frontend and backend development with a strong foundation in object-oriented programming, REST APIs, and database management including NoSQL solutions like MongoDB. Committed to continuous learning, DevOps culture, and delivering high-quality, secure software that exceeds client expectations.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, SQL, HTML5, CSS3

\textbf{Frameworks \& Libraries:} React, Redux, Node.js, Express.js, Django, Bootstrap

\textbf{Database \& Data Management:} MongoDB, PostgreSQL, MySQL, SQL Server, Firebase

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, CI/CD, GitHub Actions, Terraform

\textbf{Software Development Practices:} Agile, Scrum, Kanban, Unit Testing, Code Reviews, TDD

\textbf{Computer Science Fundamentals:} OOP, Design Patterns, Data Structures, Algorithms, MVC, REST API

\textbf{Systems \& Networking:} Cloud Computing, Networking, Security Best Practices, Linux, Bash

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Continuous Learning, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js to enhance functionality and user experience.
\item Implemented RESTful APIs, optimized SQL and NoSQL queries, and integrated secure payment systems improving reliability and performance.
\item Deployed and maintained cloud applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and availability.
\item Collaborated within Agile teams through code reviews, sprint planning, and pair programming to deliver high-quality software on schedule.
\item Applied object-oriented programming principles and secure coding standards throughout SDLC reducing production issues significantly.
\item Led backend development initiatives while mentoring junior developers on best practices, coding standards, and deployment strategies.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web and mobile applications across frontend and backend components using modern technology stacks.
\item Contributed to design and implementation of management systems working closely with stakeholders to define technical requirements.
\item Worked with cross-functional teams to gather requirements, perform integration testing, and support deployment phases successfully.
\item Gained hands-on experience in full stack development, automated testing, and secure coding practices within Agile workflows.
\item Collaborated in project reviews to identify improvements in performance, scalability, and maintainability aligning with DevOps culture.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes effectively.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL to support online education during the pandemic effectively.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards for teachers and administrators.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent usage and performance.
\item Deployed the platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 students and instructors.
\end{itemize}

\textbf{PROSPR " Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users and individuals with reading challenges integrating accessibility features.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and WebSockets with accessibility-focused UI design and intuitive navigation.
\item Integrated AWS and Azure cloud services to enable text-to-speech and voice-to-text communication for enhanced user accessibility.
\item Followed WCAG accessibility standards and tested with assistive technologies to ensure inclusive usability for diverse user groups.
\item Deployed on AWS using Docker containers for scalable, low-latency communication ensuring high performance and reliable uptime.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}