% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Full Stack Software Engineer with 2+ years of experience delivering scalable web applications using Python, JavaScript, and React. Proven expertise in cloud platforms (AWS, GCP), CI/CD pipelines, Docker, and Kubernetes with hands-on experience deploying production systems. Strong background in building end-to-end solutions from design through deployment, collaborating in Agile teams, and rapidly adapting to new technologies including AI integrations and real-time distributed systems.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, TypeScript, SQL, HTML5, CSS3, Bash, PowerShell

\textbf{Frameworks \& Libraries:} React, Redux, Node.js, Django, Flask, FastAPI, Bootstrap, Material UI

\textbf{Cloud Platforms \& Infrastructure:} AWS, Google Cloud Platform, Azure, Docker, Kubernetes, Lambda, EC2, S3

\textbf{DevOps \& CI/CD:} Jenkins, GitHub Actions, GitLab CI/CD, Terraform, CloudFormation, Ansible

\textbf{Database \& APIs:} PostgreSQL, MySQL, MongoDB, DynamoDB, REST API, GraphQL, WebSockets

\textbf{AI \& Machine Learning:} LLM API, ChatGPT API, Prompt Engineering, AI Integration, ML APIs, Automation

\textbf{Architecture \& Practices:} Microservices, Event-Driven Architecture, System Design, Agile, Scrum, TDD

\textbf{Soft Skills:} Ownership, Problem Solving, Collaboration, Adaptability, Communication, Learning Agility

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js improving e-commerce functionality and user experience.
\item Implemented RESTful APIs, optimized SQL queries, and integrated secure payment systems enhancing system reliability and performance.
\item Deployed cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and high availability.
\item Collaborated in Agile teams through code reviews, sprint planning, and pair programming delivering high-quality software consistently.
\item Applied test-driven development and secure coding standards throughout SDLC reducing production issues and improving maintainability.
\item Led backend development for multiple applications mentoring junior developers on best practices for coding and deployment workflows.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level web and mobile applications across frontend and backend components using modern frameworks.
\item Contributed to design and implementation of Proposal Management and Mailroom Tracking Systems improving operational workflows.
\item Worked with cross functional teams to gather requirements, perform testing, and support deployment phases ensuring project success.
\item Gained hands-on experience in full stack development, software testing, and secure coding within Agile workflows and sprints.
\item Collaborated in project reviews to identify improvements in performance, scalability, and code maintainability across deliverables.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes successfully.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed full-stack LMS using React, Node.js, and MySQL to support online education during the pandemic effectively.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time progress dashboards for teachers and students.
\item Implemented secure authentication, role-based access, and optimized database queries for high concurrent usage and reliability.
\item Deployed the platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 students consistently.
\end{itemize}

\textbf{PROSPR " Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users and individuals with reading challenges integrating accessibility features.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Node.js, and Socket.io with accessibility-focused UI design for inclusive usability.
\item Integrated AWS Polly and Azure Speech Services to enable text-to-speech and voice-to-text communication for accessibility compliance.
\item Followed WCAG accessibility standards and tested with assistive technologies ensuring inclusive usability for diverse user groups.
\item Deployed on AWS App Runner with Docker containers for scalable, low-latency communication ensuring high performance and uptime.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}