% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with proven expertise in Python, JavaScript, and full stack development across cloud platforms. Experienced in building scalable systems, implementing CI/CD pipelines with GitHub Actions, and collaborating with cross-functional teams in Agile environments. Strong foundation in data structures, algorithms, and multithread programming with proficiency in Git, Docker, and Linux. Skilled in debugging complex systems and delivering high-quality software solutions that drive innovation.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, SQL, Bash, HTML5, CSS3

\textbf{Frameworks \& Libraries:} React, Django, Flask, Node.js, Bootstrap

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, Database Design

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, CI/CD, GitHub Actions, Git

\textbf{Software Development Practices:} Agile, Scrum, SDLC, Testing, Code Reviews, Debugging

\textbf{Computer Science Fundamentals:} Data Structures, Algorithms, OOP, Design Patterns, Multithread Programming

\textbf{Systems \& Networking:} Linux, Unix Environments, Networking, System Design, Scalability

\textbf{Soft Skills:} Collaboration, Communication, Problem Solving, Adaptability, Analytical Thinking, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js enhancing system performance and reliability.
\item Implemented RESTful APIs and optimized SQL database queries to improve data retrieval efficiency and application responsiveness.
\item Deployed cloud-based solutions using AWS, Docker, and CI/CD pipelines with GitHub Actions ensuring consistent uptime and delivery.
\item Collaborated with cross-functional Agile teams through code reviews, sprint planning, and pair programming to deliver quality software.
\item Applied test-driven development and secure coding practices throughout SDLC reducing production issues and improving maintainability.
\item Led backend development initiatives while mentoring junior engineers on coding standards, debugging techniques, and deployment best practices.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications across frontend and backend components using modern development frameworks.
\item Contributed to design and implementation of Proposal Management and Mailroom Tracking Systems in collaborative team environments.
\item Worked with cross-functional teams to gather requirements, perform testing, and support deployment phases ensuring project success.
\item Gained hands-on experience in full stack development, debugging, and secure coding practices within Agile workflows and sprints.
\item Participated in project reviews identifying improvements in performance, scalability, and code quality to enhance system architecture.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed full stack LMS using React, Node.js, and MySQL supporting online education for thousands of concurrent users.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards for instructors and administrators.
\item Implemented secure authentication, role-based access control, and optimized database queries for high-performance concurrent usage.
\item Deployed platform on AWS with CDN caching and SSL encryption ensuring reliable access and data security for over 6,000 students.
\end{itemize}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic }

\vspace{-1pt}

Automated vulnerability scanning and patching to strengthen enterprise security and reduce manual effort.
\vspace{-1pt}
\begin{itemize}
\item Developed automated workflows using Python and Jenkins for vulnerability scanning and patch deployment across enterprise systems.
\item Integrated Nessus API for real-time vulnerability reporting and risk prioritization improving security compliance and response time.
\item Created dashboards and alert systems to track security compliance metrics and remediation progress for stakeholder visibility.
\item Reduced manual intervention by 60\% and accelerated patch cycles through full CI/CD automation improving operational efficiency.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}