% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Backend Developer with hands-on expertise in Python, Django, and REST API development. Proven track record designing scalable systems, optimizing MySQL and MongoDB databases, and deploying production-ready solutions on AWS. Experienced in backend architecture, performance tuning, query optimization, and end-to-end feature ownership. Adept at collaborating with cross-functional teams while maintaining clean code practices, thorough documentation, and disciplined development workflows.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, PHP, SQL, Bash, PowerShell

\textbf{Backend Frameworks \& APIs:} Django, Django REST Framework, Flask, FastAPI, Node.js, RESTful APIs

\textbf{Database \& Optimization:} MySQL, MongoDB, PostgreSQL, Query Optimization, Schema Design, Indexing

\textbf{Cloud \& DevOps:} AWS, Docker, CI/CD Pipelines, GitHub Actions, GitLab CI/CD, Kubernetes

\textbf{Development Practices:} Agile, Unit Testing, Integration Testing, Code Reviews, TDD, Documentation

\textbf{Architecture \& Design:} Microservices, Clean Architecture, System Design, Design Patterns, Scalability

\textbf{Soft Skills:} Ownership, Clear Communication, Collaboration, Problem Solving, Adaptability, Mentorship

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable backend systems using Python, Django, and Node.js with optimized MySQL queries and efficient database schema design.
\item Built secure RESTful APIs and integrated payment processing systems to improve reliability and enhance system performance.
\item Deployed production-ready applications on AWS using Docker and CI/CD pipelines ensuring consistent uptime and availability.
\item Collaborated in Agile teams through code reviews, sprint planning, and pair programming to deliver high-quality backend features.
\item Applied unit testing, integration testing, and clean architecture principles to improve maintainability and reduce production issues.
\item Mentored junior developers on backend best practices, debugging techniques, and disciplined coding standards.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to backend development of enterprise web applications using Python and database optimization techniques.
\item Designed and implemented backend components for Proposal Management and Mailroom Tracking Systems with modular architecture.
\item Collaborated with cross-functional teams to gather requirements, perform integration testing, and support deployment phases.
\item Gained hands-on experience in backend development, SQL optimization, and secure coding practices within Agile workflows.
\item Participated in project reviews identifying performance improvements, scalability enhancements, and code maintainability strategies.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built scalable LMS backend using Python and MySQL enabling 6K+ students to access lessons, quizzes, and performance tracking.
\vspace{-1pt}
\begin{itemize}
\item Designed backend architecture using Python, Node.js, and MySQL with optimized queries and indexing for high concurrent usage.
\item Developed REST APIs for lesson uploads, quizzes, and real-time progress tracking with role-based access control and authentication.
\item Implemented database migrations, query optimization, and schema design to ensure scalability and fast response times.
\item Deployed platform on AWS with Docker containers, SSL encryption, and CDN caching ensuring reliable access for 6,000+ students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed backend for inclusive real-time chat app with accessibility features integrating AWS services and WebSocket communication.
\vspace{-1pt}
\begin{itemize}
\item Built real-time backend using Node.js and Socket.io handling WebSocket connections and message routing for low-latency communication.
\item Integrated AWS Polly and Azure Speech Services APIs enabling text-to-speech and voice-to-text functionality through REST endpoints.
\item Designed modular backend architecture with proper authentication, logging, and error handling following clean architecture principles.
\item Deployed on AWS App Runner using Docker containers ensuring scalability, high availability, and consistent backend performance.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}