% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with hands-on experience in full stack web development, cloud infrastructure, and collaborative Agile environments. Proficient in JavaScript, Python, React, Node.js, and AWS, with proven ability to build scalable applications, optimize performance, and deliver reliable systems. Experienced in code reviews, CI/CD pipelines, and end-to-end project ownership. Adept at learning new technologies quickly and working cross-functionally to solve complex technical challenges.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, Python, PHP, SQL, HTML, CSS

\textbf{Frameworks \& Libraries:} React, Node.js, Django, Bootstrap, Express.js, jQuery

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQLite, SQL Server

\textbf{Cloud \& DevOps:} AWS, GCP, Docker, CI/CD, GitHub Actions, GitLab CI/CD

\textbf{Software Development Practices:} Agile, Scrum, Code Reviews, SDLC, Testing, Debugging

\textbf{Computer Science Fundamentals:} Data Structures, Algorithms, OOP, Design Patterns, System Design

\textbf{Systems \& Networking:} Cloud Computing, Security Best Practices, Unix/Linux, Bash Scripting

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Ownership, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js to enhance e-commerce functionality.
\item Implemented RESTful APIs, optimized SQL queries, and integrated secure payment systems improving reliability and performance.
\item Deployed cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and system availability.
\item Collaborated within Agile teams through code reviews, sprint planning, and pair programming to deliver high-quality software.
\item Applied test-driven development and secure coding standards throughout SDLC reducing production issues and improving code quality.
\item Led backend development for multiple applications while mentoring junior developers on best practices and deployment workflows.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web and mobile applications across both frontend and backend components within Agile teams.
\item Contributed to design and implementation of Proposal Management and Mailroom Tracking Systems using modern tech stacks.
\item Worked closely with cross-functional teams to gather requirements, perform testing, and support deployment phases effectively.
\item Gained hands-on experience in full stack development, software testing, and secure coding within collaborative workflows.
\item Collaborated in project reviews to identify improvements in performance, scalability, and code maintainability standards.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built scalable LMS enabling 6K+ students to learn with notes, videos, and interactive quizzes during the pandemic response.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack LMS using React, Node.js, and MySQL to support online education during pandemic with scalable architecture.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time progress dashboards for educators.
\item Implemented secure authentication, role-based access, and optimized database queries for high concurrent usage and performance.
\item Deployed platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 students continuously.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed inclusive real-time chat app for low-vision users integrating accessibility features and speech technologies.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Node.js, and Socket.io with accessibility-focused UI following WCAG standards.
\item Integrated AWS Polly and Azure Speech Services enabling text-to-speech and voice-to-text communication for inclusive access.
\item Followed WCAG accessibility standards and tested with assistive technologies ensuring inclusive usability across user groups.
\item Deployed on AWS App Runner with Docker containers for scalable, low-latency communication and high system availability.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}