% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Entry-level Software Engineer with hands-on experience developing full stack web applications using JavaScript, React, Node.js, and Python. Skilled in building scalable cloud-based solutions on AWS and GCP with CI/CD automation. Experienced in collaborating within Agile teams, conducting code reviews, and contributing across the full software development lifecycle from design through deployment and monitoring. Passionate about writing maintainable code and eager to grow through mentorship.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, Python, SQL, HTML5, CSS3, Bash

\textbf{Frameworks \& Libraries:} React, Node.js, Django, Express.js, Bootstrap, Redux

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQLite, Firebase

\textbf{Cloud \& DevOps:} AWS, Docker, CI/CD, GitHub Actions, Kubernetes, Terraform

\textbf{Development Practices:} Agile, Scrum, Unit Testing, Code Reviews, TDD, Documentation

\textbf{Computer Science Fundamentals:} Data Structures, Algorithms, OOP, Design Patterns, System Design

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Problem Solving, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js to enhance e-commerce functionality.
\item Implemented RESTful APIs, optimized SQL queries, and integrated secure payment systems improving system reliability.
\item Deployed and maintained cloud applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and availability.
\item Collaborated within Agile teams through code reviews, sprint planning, and retrospectives to deliver high-quality features.
\item Applied test-driven development and secure coding standards throughout SDLC reducing production issues and improving code quality.
\item Mentored junior developers on best practices for coding, testing, and deployment supporting team growth and knowledge sharing.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web and mobile applications across both frontend and backend components with guidance.
\item Contributed to design and implementation of Proposal Management and Mailroom Tracking Systems improving operational workflows.
\item Worked closely with cross functional teams to gather requirements, perform testing, and support deployment phases effectively.
\item Gained hands-on experience in full stack development, software testing, and secure coding within Agile workflows and sprints.
\item Collaborated in project reviews to identify improvements in performance, scalability, and code maintainability across projects.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes online.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL to support online education during the pandemic.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time progress dashboards for educators.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent usage patterns.
\item Deployed the platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 active students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users and individuals with reading challenges integrating accessibility features.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and Socket.io with accessibility-focused UI design and interactions.
\item Integrated AWS Polly and Azure Speech Services to enable text-to-speech and voice-to-text communication for accessibility.
\item Followed WCAG accessibility standards and tested with assistive technologies to ensure inclusive usability for diverse users.
\item Deployed on AWS App Runner with Docker containers for scalable, low-latency communication and monitoring across environments.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}