% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Full Stack Developer with 2+ years of experience building scalable web applications using React, Node.js, and cloud technologies. Proven ability to design and deploy customer-facing solutions within Agile teams, with hands-on expertise in CI/CD pipelines, RESTful APIs, and DevOps practices. Experienced in collaborating with cross-functional teams to deliver high-quality software, mentoring developers, and implementing test-driven development methodologies to enhance system reliability and performance.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, SQL, HTML5, CSS3

\textbf{Frontend Technologies:} React, Next.js, Redux, Bootstrap, Material UI, Responsive Design

\textbf{Backend \& Server-Side:} Node.js, Express.js, NestJS, Django, Flask, REST API

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, Redis, Firebase

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, CI/CD, GitHub Actions, Infrastructure as Code

\textbf{Testing \& Quality:} Unit Testing, Integration Testing, TDD, Postman, Automation Testing

\textbf{Development Practices:} Agile, Scrum, Pair Programming, Code Reviews, System Design

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Ownership, Mentorship

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack e-commerce applications using React, Node.js, and RESTful APIs to enhance customer experience.
\item Implemented CI/CD pipelines with GitHub Actions and deployed applications on AWS, ensuring high availability and uptime.
\item Optimized SQL database queries and integrated secure payment systems improving system reliability and performance metrics.
\item Collaborated within Agile teams through sprint planning, code reviews, and pair programming to deliver high-quality solutions.
\item Applied test-driven development and secure coding practices throughout SDLC, reducing production issues by 40 percent.
\item Mentored junior developers on best practices for architecture design, deployment workflows, and DevOps methodologies.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications using frontend and backend technologies within cross-functional teams.
\item Contributed to the design and implementation of Proposal Management and Mailroom Tracking Systems using Agile workflows.
\item Worked with product owners and designers to gather requirements, perform testing, and support deployment activities.
\item Gained hands-on experience in full stack development, unit and integration testing, and continuous delivery practices.
\item Participated in code reviews and project retrospectives to identify improvements in scalability and maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS platform enabling 6K+ students to access lessons, quizzes, and real-time progress tracking during pandemic.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL to support interactive online education features.
\item Integrated lesson uploads, quizzes, and performance tracking with real-time dashboards for teachers and administrators.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent user loads.
\item Deployed the platform on AWS with CDN caching and SSL encryption, ensuring reliable access for over 6,000 active students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive real-time chat app for low-vision users integrating text-to-speech and voice-to-text features.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and Socket.io with accessibility-focused UI following WCAG standards.
\item Integrated AWS Polly and Azure Speech Services to enable seamless text-to-speech and voice-to-text communication capabilities.
\item Tested with assistive technologies to ensure inclusive usability and compliance with accessibility best practices and guidelines.
\item Deployed on AWS App Runner with Docker containers for scalable, low-latency communication and reliable uptime for end users.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}