% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Frontend-focused Software Engineer with 5+ years of experience building scalable, enterprise-grade platforms and user-facing features using React, TypeScript, and modern JavaScript. Proven track record designing secure systems including authentication, permissions, and real-time collaboration tools for high-traffic applications. Strong full stack capabilities with cloud infrastructure expertise across AWS and GCP, coupled with deep understanding of accessibility standards and enterprise SaaS patterns.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Frontend Technologies:} React, TypeScript, JavaScript, Redux, HTML5, CSS3

\textbf{Backend \& APIs:} Node.js, REST API, GraphQL, WebSockets, Python, Django

\textbf{Cloud \& Infrastructure:} AWS, Docker, Kubernetes, CI/CD, Terraform, GCP

\textbf{Security \& Enterprise Patterns:} OAuth, JWT, RBAC, IAM, Feature Flags, SSO

\textbf{Database \& Data:} PostgreSQL, MongoDB, MySQL, Firebase, DynamoDB

\textbf{Development Practices:} Agile, Scrum, TDD, Code Reviews, System Design

\textbf{Soft Skills:} Ownership, Cross-functional Collaboration, Communication, Adaptability, Problem Solving, Decisiveness

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable frontend applications using React and TypeScript with secure authentication and permission systems to enhance user experiences.
\item Built RESTful and GraphQL APIs with Node.js optimizing performance for high-traffic enterprise platforms serving thousands of concurrent users.
\item Implemented feature flagging infrastructure and notification systems enabling controlled rollouts and real-time user engagement across products.
\item Deployed cloud-based applications on AWS using Docker and CI/CD pipelines ensuring high availability and zero-downtime releases for critical services.
\item Collaborated cross-functionally with product and design teams through Agile sprints delivering intuitive enterprise-grade features with measurable impact.
\item Led frontend architecture decisions for collaborative tools applying accessibility standards and security best practices throughout the development lifecycle.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Built full stack web applications across frontend and backend components using React and modern JavaScript frameworks for enterprise clients.
\item Contributed to designing and implementing secure document management and tracking systems with role-based access control and audit logging.
\item Worked closely with cross-functional teams gathering requirements and performing integration testing to ensure robust product delivery.
\item Gained hands-on experience in software development lifecycle including testing secure coding and deployment within Agile methodologies.
\item Participated in code reviews and project retrospectives to improve system performance scalability and overall code quality.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS with React and Node.js enabling 6K+ students to access lessons, quizzes, and performance dashboards securely.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed full stack LMS using React TypeScript and Node.js with secure authentication and role-based permissions for students and teachers.
\item Integrated real-time dashboards for performance tracking quiz modules and lesson uploads with WebSocket-based notifications for instant updates.
\item Implemented optimized database queries and caching strategies in PostgreSQL to handle high concurrent usage across thousands of active users.
\item Deployed platform on AWS with CDN caching SSL encryption and autoscaling ensuring reliable access and low-latency performance for 6K+ students.
\end{itemize}

\textbf{PROSPR " Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed inclusive real-time chat app with React and Node.js integrating text-to-speech and accessibility features for low-vision users.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React TypeScript and Socket.io with accessibility-first UI design following WCAG standards for inclusive usability.
\item Integrated AWS Polly and Azure Speech Services enabling text-to-speech and voice-to-text communication for users with reading challenges.
\item Tested application with assistive technologies ensuring seamless navigation and usability for low-vision users and individuals with disabilities.
\item Deployed on AWS App Runner with Docker containers implementing autoscaling and monitoring for scalable low-latency real-time communication.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}