% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven System Administrator with extensive experience in cloud infrastructure, automation, and enterprise systems. Proven expertise in deploying and maintaining secure network environments, optimizing Linux and Windows server infrastructures, and implementing disaster recovery solutions. Skilled in infrastructure automation, vulnerability management, and collaborating with cross-functional teams to enhance system availability and performance while adhering to industry best practices and security standards.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Operating Systems \& Virtualization:} Linux system administration, Windows Server administration, Docker, Kubernetes, Active Directory

\textbf{Cloud \& Infrastructure:} AWS, GCP, Infrastructure as Code, Terraform, Ansible, High Availability

\textbf{Networking \& Security:} VPN, Networking principles, API Security, OWASP, OAuth, IAM

\textbf{Automation \& Monitoring:} CI/CD, GitHub Actions, Jenkins, Cloud Monitoring, Logging, Bash scripting

\textbf{Security \& Compliance:} Vulnerability management, Incident Response, Disaster Recovery, Backup Strategies, Encryption

\textbf{Database \& System Tools:} PostgreSQL, MySQL, MongoDB, SQL Server, PowerShell, Git

\textbf{Soft Skills:} Problem solving, Communication, Team collaboration, Adaptability, Time management, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Deployed and maintained cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and availability.
\item Optimized database queries across PostgreSQL and MySQL environments to improve system reliability and performance.
\item Implemented secure authentication mechanisms and access controls adhering to OWASP best practices and encryption standards.
\item Monitored production systems and performed proactive troubleshooting to maintain high availability and minimize downtime.
\item Collaborated with cross-functional teams through Agile workflows to deliver scalable infrastructure and automation improvements.
\item Applied infrastructure as code principles and automated deployment workflows to enhance productivity and system consistency.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in deploying enterprise-level applications and supported infrastructure setup across cloud and on-premises environments.
\item Contributed to system testing, configuration management, and performance monitoring throughout deployment phases.
\item Worked closely with cross-functional teams to gather requirements and implement secure coding and system integration practices.
\item Gained hands-on experience in troubleshooting, system maintenance, and backup strategies within Agile workflows.
\item Collaborated in project reviews to identify improvements in scalability, security compliance, and operational efficiency.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Enterprise Vulnerability Assessment and Patching Automation} -- \emph{Group Capstone Project, Seneca Polytechnic }

\vspace{-1pt}

Automated vulnerability scanning and patching to strengthen enterprise security and reduce manual effort across systems.
\vspace{-1pt}
\begin{itemize}
\item Developed automated workflows using Python and Jenkins for vulnerability scanning, patch deployment, and compliance reporting.
\item Integrated Nessus API for real-time vulnerability reporting, risk prioritization, and remediation tracking across infrastructure.
\item Created monitoring dashboards and alert systems to track security compliance, patch status, and remediation progress metrics.
\item Reduced manual intervention by 60\% and accelerated patch cycles through full CI/CD automation and infrastructure orchestration.
\end{itemize}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes.
\vspace{-1pt}
\begin{itemize}
\item Designed and deployed a full-stack LMS using React, Node.js, and MySQL to support high-volume online education infrastructure.
\item Implemented secure authentication, role-based access controls, and optimized database queries for high concurrent user loads.
\item Deployed the platform on AWS with CDN caching, load balancing, and SSL encryption ensuring reliable access for 6,000+ students.
\item Configured monitoring and logging systems to track performance metrics, uptime, and user activity across cloud infrastructure.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}