% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Full Stack Developer with 4+ years of experience building scalable web applications using TypeScript, JavaScript, React, and Node.js. Proven expertise in designing RESTful APIs, implementing secure authentication, and deploying cloud-based solutions on AWS and GCP with Docker and Kubernetes. Strong background in full SDLC practices including CI/CD pipelines, code reviews, and Agile methodologies. Skilled at collaborating with cross-functional teams to deliver high-quality software solutions with attention to detail and reliability.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} TypeScript, JavaScript, Python, SQL, HTML5, CSS3

\textbf{Frontend Development:} React, Redux, Next.js, Bootstrap, Material UI, Responsive Web Design

\textbf{Backend Development:} Node.js, Express.js, REST API, GraphQL, Django, Flask

\textbf{Database Technologies:} PostgreSQL, MySQL, MongoDB, Redis, Database Design

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, CI/CD, GitHub Actions, Infrastructure as Code

\textbf{Software Development Practices:} Agile, Scrum, Design Patterns, Unit Testing, Code Reviews, Git

\textbf{Security \& Performance:} OAuth, JWT, API Security, Performance Optimization, Monitoring, Logging

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Attention to Detail, Continuous Learning

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, TypeScript, React, and Node.js with modern design patterns.
\item Implemented and maintained RESTful APIs with secure authentication and optimized database queries for high-performance systems.
\item Deployed cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring reliability and consistent uptime.
\item Participated in Agile development processes including sprint planning, code reviews, and daily standups for quality deliverables.
\item Applied test-driven development practices and secure coding standards throughout the SDLC to reduce production defects.
\item Collaborated with cross-functional teams to design full solutions addressing complex business requirements effectively.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications with both frontend and backend components using modern technologies.
\item Contributed to design and implementation of Proposal Management and Mailroom Tracking Systems with secure architectures.
\item Worked closely with cross-functional teams gathering requirements, performing testing, and supporting deployment phases.
\item Gained hands-on experience in full stack development, troubleshooting complex issues, and secure coding within Agile workflows.
\item Participated in team design discussions and project reviews identifying improvements in performance and maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed full stack LMS using React, Node.js, and MySQL supporting online education with modern TypeScript patterns.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards for instructors and students.
\item Implemented secure authentication with JWT, role-based access control, and optimized database queries for high concurrent usage.
\item Deployed platform on AWS with Docker containers, CDN caching, and SSL encryption ensuring reliable access for 6,000+ students.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users and individuals with reading challenges integrating accessibility features.
\vspace{-1pt}
\begin{itemize}
\item Built real-time chat application using React, Node.js, and WebSockets with accessibility-focused UI following web standards.
\item Integrated AWS Polly and Azure Speech Services enabling text-to-speech and voice-to-text communication for inclusive usability.
\item Followed WCAG accessibility standards and tested with assistive technologies to ensure effective communication for all users.
\item Deployed on AWS with Docker containers for scalable, low-latency communication with monitoring and performance profiling.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}