% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Web Developer with hands-on experience in JavaScript, HTML, CSS, and modern web technologies including React and Node.js. Proven ability to build responsive, customer-focused web applications and collaborate effectively within Agile and Scrum teams. Skilled in Git version control, problem-solving, and delivering scalable solutions that enhance user experience and drive business outcomes. Passionate about code quality, performance optimization, and working directly with customers to deliver successful implementations.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, HTML5, CSS3, Python, PHP, SQL

\textbf{Frameworks \& Libraries:} React, Node.js, Bootstrap, jQuery, Django

\textbf{Database \& Data Management:} MySQL, PostgreSQL, MongoDB, SQLite

\textbf{Cloud \& DevOps:} AWS, Docker, Git, GitHub, CI/CD, GitHub Actions

\textbf{Software Development Practices:} Agile, Scrum, Testing, Code Reviews, SDLC

\textbf{Soft Skills:} Problem Solving, Communication, Collaboration, Adaptability, Customer Focus

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable web applications using JavaScript, React, and Node.js to enhance functionality and user experience.
\item Collaborated within Agile Scrum teams through code reviews, sprint planning, and pair programming to deliver high-quality solutions.
\item Managed version control with Git and GitHub, ensuring code quality, performance, and secure deployment across all projects.
\item Implemented RESTful APIs, optimized SQL queries, and integrated secure systems to improve reliability and customer satisfaction.
\item Worked directly with stakeholders to gather requirements, troubleshoot issues, and ensure successful project implementations.
\item Applied best practices in HTML, CSS, JavaScript, and testing throughout the development lifecycle to meet security standards.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing web applications using HTML, CSS, and JavaScript across frontend and backend components.
\item Worked closely with cross-functional teams to gather requirements, perform testing, and support deployment phases.
\item Contributed to the design and implementation of enterprise systems with a focus on code quality and performance.
\item Gained hands-on experience in Agile workflows, version control with Git, and collaborative problem-solving within Scrum teams.
\item Collaborated in project reviews to identify improvements in scalability, maintainability, and customer-focused solutions.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with notes, videos, and interactive quizzes using modern web technologies.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full-stack LMS using React, Node.js, HTML, CSS, and MySQL to support online education effectively.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards for teachers and students.
\item Implemented secure authentication, role-based access, and optimized queries for high concurrent usage and fast page loads.
\item Deployed the platform on AWS with CDN caching and SSL encryption, ensuring reliable access for over 6,000 active students.
\end{itemize}

\textbf{Custom Business Web Solutions} -- \emph{Personal Project}

\vspace{-1pt}

Built POS, e-commerce sites, landing pages, and inventory systems with secure, responsive web design for diverse clients.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed custom web solutions using HTML, CSS, JavaScript, React, and Node.js tailored to client requirements.
\item Implemented secure authentication, inventory tracking, and payment processing with API integration for seamless transactions.
\item Collaborated directly with clients to gather requirements and translate business needs into scalable, customer-focused applications.
\item Optimized UI performance, responsiveness, and code quality across all projects to enhance user engagement and satisfaction.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}