% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Full Stack Web Developer with proven experience designing and deploying scalable web applications using HTML, CSS, JavaScript, React, and Node.js. Skilled in developing secure, maintainable code following Agile methodologies and best practices throughout the software development life cycle. Proficient in version control with Git, REST API development, automated testing, and collaboration with cross-functional teams to deliver high-quality solutions that meet business objectives.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, TypeScript, Python, PHP, SQL, HTML5, CSS3

\textbf{Frameworks \& Libraries:} React.js, Angular, Node.js, Express.js, Redux, Bootstrap

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQLite, Firebase

\textbf{Cloud \& DevOps:} AWS, Docker, CI/CD, GitHub Actions, Version Control

\textbf{Software Development Practices:} Agile, Scrum, Unit Testing, REST API, SDLC, Code Reviews

\textbf{Computer Science Fundamentals:} Data Structures, Algorithms, OOP, Design Patterns

\textbf{Systems \& Networking:} Security Best Practices, Unix/Linux, Cloud Computing

\textbf{Soft Skills:} Communication, Collaboration, Adaptability, Problem Solving, Continuous Learning, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable web applications using JavaScript, React, and Node.js ensuring high performance and responsive user experiences.
\item Wrote secure, maintainable code adhering to best practices and standards throughout the entire software development life cycle.
\item Implemented RESTful APIs and optimized database queries to improve system reliability, efficiency, and overall performance.
\item Deployed cloud-based applications using AWS, Docker, and CI/CD pipelines to maintain high availability and consistent uptime.
\item Collaborated effectively with Agile teams through code reviews, sprint planning, and pair programming to achieve shared goals.
\item Discovered and resolved programming bugs working closely with Testers to ensure timely resolution and continuous improvement.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications across frontend and backend components using modern development frameworks.
\item Contributed to design and implementation of systems following Agile Scrum methodology and version control with Git and SVN.
\item Worked closely with cross-functional teams to gather requirements, conduct testing, and support deployment of applications.
\item Gained hands-on experience in full stack development, automated testing, and secure coding practices within Agile workflows.
\item Collaborated in project reviews identifying improvements in performance, scalability, and code quality for continuous learning.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS using HTML, CSS, React, and Node.js enabling 6K+ students to access educational content and quizzes.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full-stack LMS using React, Node.js, and MySQL to support online education and remote learning.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time dashboards for educators and students.
\item Implemented secure authentication and role-based access control with optimized database queries for high concurrent usage.
\item Deployed the platform on AWS with automated testing, CDN caching, and SSL encryption ensuring reliable access for 6K+ users.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app using React and Node.js with accessibility features for low-vision users and reading challenges.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using HTML, CSS, React, Node.js, and WebSockets with accessibility-focused UI design.
\item Integrated AWS Polly and Azure Speech Services enabling text-to-speech and voice-to-text communication for accessibility.
\item Followed WCAG accessibility standards and tested with assistive technologies ensuring inclusive usability for all users.
\item Deployed on AWS with Docker containers and automated system tests for scalable, low-latency real-time communication.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}