% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Web Developer with 2+ years of experience building scalable full-stack applications using JavaScript, React, Node.js, and Python. Skilled in writing, modifying, and testing website-related code while maintaining optimal server performance. Proven ability to communicate technical problems and solutions, assist in requirements analysis, and conduct security and quality controls. Experienced in e-commerce platforms, API integration, and cloud deployment using AWS and Docker.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, Python, PHP, SQL, HTML5, CSS3

\textbf{Frameworks \& Libraries:} React, Node.js, Django, Bootstrap, jQuery

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQLite

\textbf{Cloud \& DevOps:} AWS, Docker, GitHub Actions, CI/CD

\textbf{Software Development Practices:} Testing, Security Controls, Code Reviews, Documentation, Requirements Analysis

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable web applications using JavaScript, React, and Node.js, writing and testing code to enhance functionality.
\item Maintained existing programs by modifying code, optimizing SQL queries, and integrating secure systems for improved reliability.
\item Determined hardware and software requirements while deploying cloud applications using AWS and Docker for optimal performance.
\item Communicated technical problems and solutions to cross-functional teams through code reviews and sprint planning sessions.
\item Conducted security and quality control tests throughout SDLC, ensuring compliance with secure coding standards and best practices.
\item Prepared technical documentation and reports on system status, operation, and maintenance to support deployment and uptime goals.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications, writing and testing code for frontend and backend components.
\item Contributed to the design and implementation of management systems by collecting and documenting user requirements.
\item Worked closely with teams to perform security controls, quality testing, and support deployment phases of software projects.
\item Gained hands-on experience modifying existing programs and conducting tests within Agile workflows and SDLC processes.
\item Collaborated in project reviews to identify improvements in performance, maintainability, and compliance with technical standards.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed full-stack LMS using React, Node.js, and MySQL to support online education during the pandemic.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time progress dashboards for teachers.
\item Implemented secure authentication, role-based access, and optimized database queries for high concurrent user access.
\item Deployed platform on AWS with SSL encryption and CDN caching, ensuring reliable access for over 6,000 students daily.
\end{itemize}

\textbf{Custom Business Web Solutions} -- \emph{Personal Project}

\vspace{-1pt}

Built POS, e-commerce sites, landing pages, and inventory systems with secure, responsive web design improving workflow.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed custom web solutions using React, Next.js, and Express.js for various business requirements.
\item Implemented secure authentication, inventory tracking, and payment processing with Stripe API integration for clients.
\item Collaborated with clients to gather and document requirements, translating business needs into scalable applications.
\item Optimized UI performance, responsiveness, and SEO across all client projects to enhance user engagement and conversion.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}