% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Full Stack Web Developer with 3+ years of experience building scalable, database-driven web applications using modern PHP, JavaScript, React, Node.js, and SQL. Proven track record deploying production systems on AWS and GCP with Docker, CI/CD pipelines, and cloud infrastructure. Skilled in developing accessible, secure, and maintainable solutions following OWASP and WCAG standards. Experienced in Agile workflows, code reviews, API development, and cross-functional collaboration to deliver high-quality features.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} PHP, JavaScript, Python, SQL, HTML5, CSS3, Bash, PowerShell

\textbf{Frameworks \& Libraries:} React, Node.js, Laravel, Django, Bootstrap, Redux

\textbf{Database \& Data Management:} MySQL, PostgreSQL, MongoDB, SQLite, Redis

\textbf{Cloud \& DevOps:} AWS, Google Cloud Platform, Docker, Kubernetes, CI/CD, GitHub Actions

\textbf{Software Development Practices:} Agile, Scrum, Unit Testing, Integration Testing, Code Reviews, SDLC

\textbf{Security \& Accessibility:} OWASP, WCAG, OAuth, JWT, API Security, Encryption

\textbf{Soft Skills:} Communication, Collaboration, Problem Solving, Adaptability, Continuous Learning, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js improving e-commerce functionality and user experience.
\item Implemented RESTful APIs, optimized SQL queries, and integrated secure payment systems to enhance system reliability and performance.
\item Deployed and maintained cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and availability.
\item Collaborated within Agile teams through code reviews, sprint planning, and pair programming to ensure high-quality deliverables.
\item Applied test-driven development and secure coding standards throughout SDLC improving maintainability and reducing production issues.
\item Led backend development for multiple web applications while mentoring junior developers on best coding and deployment practices.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web and mobile applications across both frontend and backend components using modern frameworks.
\item Contributed to design and implementation of Proposal Management and Mailroom Tracking Systems with database-driven architectures.
\item Worked closely with cross-functional teams to gather requirements, perform testing, and support deployment phases effectively.
\item Gained hands-on experience in full stack development, software testing, and secure coding within Agile workflows and sprints.
\item Collaborated in project reviews to identify improvements in performance, scalability, and code maintainability for production systems.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS during the pandemic enabling 6K+ students to learn with notes, videos, and interactive quizzes using React and Node.js.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL to support online education during the pandemic effectively.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time progress dashboards for teachers and students.
\item Implemented secure authentication, role-based access, and optimized database queries for high concurrent usage and system reliability.
\item Deployed the platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 students and educators.
\end{itemize}

\textbf{PROSPR  Real-Time Chat Application for Accessibility} -- \emph{Group Capstone Project, Seneca Polytechnic}

\vspace{-1pt}

Developed an inclusive chat app for low-vision users integrating accessibility features and following WCAG standards with React and Node.js.
\vspace{-1pt}
\begin{itemize}
\item Built a real-time chat application using React, Node.js, and Socket.io with accessibility-focused UI design for inclusive communication.
\item Integrated AWS Polly and Azure Speech Services to enable text-to-speech and voice-to-text communication for low-vision users effectively.
\item Followed WCAG accessibility standards and tested with assistive technologies to ensure inclusive usability and compliance with best practices.
\item Deployed on AWS App Runner with Docker containers for scalable, low-latency communication and reliable performance across devices.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}