% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Detail-oriented Web Developer with hands-on experience in designing, developing, and maintaining dynamic web applications using JavaScript, React, PHP, and MySQL. Skilled in full stack development, integrating databases, optimizing performance, and implementing secure coding practices. Proficient in working with AWS, Git, and modern web technologies including Bootstrap, jQuery, and SASS. Strong understanding of Agile and Scrum methodologies with a proven ability to deliver under tight deadlines in fast-paced environments.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, PHP, Python, SQL, HTML5, CSS3, Bash

\textbf{Frameworks \& Libraries:} React, Node.js, Bootstrap, jQuery, SASS, Django

\textbf{Database \& Data Management:} MySQL, PostgreSQL, MongoDB, SQLite, Database Design

\textbf{Cloud \& DevOps:} AWS, Docker, Git, GitHub, CI/CD, Cloud Deployment

\textbf{Web Development Tools:} WordPress, Postman, Figma, API Integration, JSON, XML

\textbf{Software Development Practices:} Agile, Scrum, Testing, Debugging, Code Reviews, Documentation

\textbf{Soft Skills:} Communication, Team Collaboration, Adaptability, Accountability, Problem Solving, Initiative

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js to enhance functionality and user experience.
\item Designed and integrated RESTful APIs with optimized SQL queries and secure payment systems to improve system performance.
\item Deployed and maintained cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and reliability.
\item Collaborated within Agile teams through code reviews, sprint planning, and pair programming to deliver high-quality solutions.
\item Applied test-driven development and secure coding standards throughout SDLC to improve maintainability and reduce production issues.
\item Led backend development for multiple web applications while mentoring junior developers on best coding and deployment practices.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level web applications across both frontend and backend components using modern technologies.
\item Contributed to the design and implementation of management systems ensuring scalable and maintainable architecture.
\item Worked closely with cross functional teams to gather requirements, perform testing, and support deployment phases effectively.
\item Gained hands-on experience in full stack development, software testing, and secure coding within Agile workflows and sprints.
\item Collaborated in project reviews to identify improvements in performance, scalability, and code maintainability across projects.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with notes, videos, and interactive quizzes using modern web technologies.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL to support online education and interactive learning.
\item Integrated modules for lesson uploads, quizzes, and performance tracking with real-time progress dashboards for instructors.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent user access.
\item Deployed the platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 active students.
\end{itemize}

\textbf{Custom Business Web Solutions} -- \emph{Personal Project}

\vspace{-1pt}

Built e-commerce sites, landing pages, and inventory systems with secure, responsive web design improving workflow efficiency.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed multiple custom web solutions using React, JavaScript, PHP, and MySQL for diverse business requirements.
\item Implemented secure authentication, inventory tracking, and payment processing with API integration for seamless transactions.
\item Collaborated with clients to gather requirements and translate business needs into scalable, user-friendly web applications.
\item Optimized UI performance, responsiveness, and SEO across all client projects to enhance user engagement and search visibility.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}