% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Web Developer with 2+ years of experience building full stack applications using JavaScript, React, and Node.js. Skilled in designing and integrating website-related code, developing scalable architectures, and optimizing database performance with SQL and MySQL. Experienced in Agile methodologies, cloud deployment on AWS, and creating user-focused solutions for e-commerce and web applications. Proven ability to collaborate with cross-functional teams and deliver high-quality, maintainable code.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, Python, HTML5, CSS3, SQL, PHP

\textbf{Frameworks \& Libraries:} React.js, Node.js, jQuery, Bootstrap, Angular.js, Django

\textbf{Database \& Data Management:} MySQL, PostgreSQL, MongoDB, Database Design, SQL Queries

\textbf{Cloud \& DevOps:} AWS, Docker, Git, GitHub, CI/CD Pipelines

\textbf{Development Tools \& Practices:} VS Code, Jira, Agile, Object-Oriented Programming, Software Quality Assurance

\textbf{Web Technologies:} REST API, JSON, Web Service Design, E-commerce Development, Responsive Design

\textbf{Soft Skills:} Communication, Team Collaboration, Client Focus, Problem Solving, Attention to Detail, Adaptability

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js to enhance e-commerce functionality and user experience.
\item Designed and integrated website-related code, RESTful APIs, and optimized SQL queries to improve system reliability and performance.
\item Deployed and maintained cloud-based applications on AWS with Docker and CI/CD pipelines ensuring consistent uptime and availability.
\item Collaborated with cross-functional teams using Agile and Scrum methodologies to deliver high-quality, client-focused solutions on schedule.
\item Applied test-driven development and secure coding standards throughout SDLC improving maintainability and reducing production issues.
\item Consulted with clients to gather website requirements, provided ongoing support, and documented software operation and maintenance procedures.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level web applications across frontend and backend components using HTML, CSS, and JavaScript frameworks.
\item Contributed to design, integration, and testing of website architecture for Proposal Management and Mailroom Tracking Systems.
\item Worked closely with cross-functional teams to gather requirements, perform testing, and support deployment phases under tight deadlines.
\item Gained hands-on experience in full stack development, software quality assurance, and secure coding within Agile workflows and sprints.
\item Collaborated in code reviews to identify improvements in performance, scalability, and maintainability of web applications and databases.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with notes, videos, and interactive quizzes using full stack web technologies.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed a full stack LMS using React, Node.js, and MySQL to support online education with interactive content modules.
\item Integrated lesson uploads, quizzes, and performance tracking with real-time dashboards enabling teachers to monitor student progress.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent user performance.
\item Deployed the platform on AWS with CDN caching and SSL encryption, ensuring reliable access for over 6,000 students during pandemic.
\end{itemize}

\textbf{Custom Business Web Solutions} -- \emph{Personal Project}

\vspace{-1pt}

Built POS, e-commerce sites, landing pages, and inventory systems with secure, responsive design improving workflow efficiency.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed custom web solutions using React, JavaScript, and Node.js to meet diverse client business and operational needs.
\item Implemented secure authentication, inventory tracking, and payment processing with Stripe API integration for e-commerce applications.
\item Consulted with clients to gather website requirements and translated business needs into scalable, user-focused web applications.
\item Optimized UI performance, responsiveness, and SEO across all client projects to enhance user engagement and search engine visibility.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}