% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Detail-oriented Web Developer with expertise in Python, JavaScript, and SQL, specializing in full stack development and AI integration. Proven ability to evaluate code logic, solve complex algorithmic problems, and improve software quality through systematic testing and debugging. Experienced in building scalable web applications, REST APIs, and data-driven solutions with strong foundations in data structures, algorithms, and performance optimization.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, SQL, HTML5, CSS3, PHP

\textbf{Frameworks \& Libraries:} React, Django, Flask, Node.js, Bootstrap

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQLite

\textbf{Cloud \& DevOps:} AWS, Docker, GitHub Actions, CI/CD

\textbf{Software Development Practices:} Agile, Scrum, Testing, Debugging, Code Reviews

\textbf{Computer Science Fundamentals:} Data Structures, Algorithms, OOP, Design Patterns

\textbf{Soft Skills:} Problem Solving, Communication, Adaptability, Collaboration, Analytical Thinking

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed scalable full stack web applications using JavaScript, React, and Node.js to enhance functionality and user experience.
\item Implemented RESTful APIs, optimized SQL queries, and integrated secure systems to improve reliability and performance metrics.
\item Deployed cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and seamless delivery.
\item Collaborated within Agile teams through code reviews, sprint planning, and pair programming to deliver high-quality solutions.
\item Applied test-driven development and debugging workflows throughout SDLC improving maintainability and reducing production issues.
\item Led backend development for multiple applications while mentoring junior developers on best coding and deployment practices.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise web applications across frontend and backend components using Python and JavaScript frameworks.
\item Contributed to design and implementation of management systems focusing on data structures and efficient algorithm application.
\item Worked with cross-functional teams to gather requirements, perform testing, and evaluate code quality during deployment phases.
\item Gained hands-on experience in full stack development, debugging workflows, and secure coding practices within Agile environments.
\item Collaborated in project reviews to identify improvements in performance, scalability, and overall code correctness evaluation.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS with Python and JavaScript enabling 6K+ students to access lessons, quizzes, and performance tracking.
\vspace{-1pt}
\begin{itemize}
\item Designed full-stack LMS using React, Node.js, and MySQL to support online education with real-time performance dashboards.
\item Integrated modules for lesson uploads, quizzes, and tracking with secure authentication and role-based access implementation.
\item Optimized database queries and debugging workflows for high concurrent usage ensuring correctness and reliable performance.
\item Deployed platform on AWS with SSL encryption and CDN caching ensuring scalable access for over 6,000 active student users.
\end{itemize}

\textbf{Automated Cryptocurrency Trading Bot} -- \emph{Personal Project}

\vspace{-1pt}

Created Python trading bot using Binance API and WebSocket to automate execution with algorithm-based risk control logic.
\vspace{-1pt}
\begin{itemize}
\item Developed fully automated trading bot in Python using Binance API and WebSocket for real-time data streaming and execution.
\item Implemented dynamic trading algorithms, stop-loss mechanisms, and order execution logic solving complex performance challenges.
\item Integrated Pandas and NumPy for market analysis, backtesting, and debugging to improve trading accuracy and data handling.
\item Deployed using Docker on AWS EC2 for continuous uptime, reliability, and monitoring with detailed logging for evaluation.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}