% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Software Engineer with expertise in Python, JavaScript, and full stack web development. Proven ability to build scalable web applications, evaluate code quality, and solve complex algorithmic problems. Experienced in debugging workflows, data structures, and AI integration with strong attention to detail. Skilled in code reviews, technical documentation, and collaborating across teams to deliver high-quality solutions in Agile environments.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} Python, JavaScript, HTML, CSS, SQL, PHP

\textbf{Frameworks \& Libraries:} React, Django, Flask, Node.js, Bootstrap, jQuery

\textbf{Database \& Data Management:} PostgreSQL, MySQL, MongoDB, SQLite, Firebase

\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, GitHub Actions, CI/CD

\textbf{Software Development Practices:} Agile, Scrum, Testing, Debugging, Code Reviews, TDD

\textbf{Computer Science Fundamentals:} Algorithms, Data Structures, OOP, Design Patterns

\textbf{Soft Skills:} Problem Solving, Communication, Adaptability, Collaboration, Attention to Detail

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed full stack web applications using JavaScript, React, and Node.js with focus on performance and scalability.
\item Implemented RESTful APIs and optimized SQL queries to improve system reliability and response times.
\item Deployed cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring consistent uptime and availability.
\item Collaborated within Agile teams through code reviews and sprint planning to ensure high-quality deliverables.
\item Applied secure coding standards and debugging workflows throughout SDLC reducing production issues significantly.
\item Mentored junior developers on best coding practices, testing methodologies, and deployment strategies.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing enterprise-level web applications across both frontend and backend components.
\item Contributed to design and implementation of Proposal Management and Mailroom Tracking Systems.
\item Worked closely with teams to gather requirements, perform testing, and support deployment phases.
\item Gained hands-on experience in full stack development, debugging, and secure coding within Agile workflows.
\item Collaborated in project reviews to identify improvements in performance, scalability, and code maintainability.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS using Python and JavaScript enabling 6K+ students to access lessons, quizzes, and performance tracking.
\vspace{-1pt}
\begin{itemize}
\item Designed full-stack LMS using React, Node.js, and MySQL to support online education with interactive features.
\item Integrated modules for lesson uploads, quizzes, and real-time dashboards with role-based access control.
\item Implemented secure authentication and optimized database queries for high concurrent usage and performance.
\item Deployed platform on AWS with CDN caching and SSL encryption ensuring reliable access for over 6,000 students.
\end{itemize}

\textbf{Automated Cryptocurrency Trading Bot} -- \emph{Personal Project}

\vspace{-1pt}

Created a Python trading bot using Binance API with real-time data streaming, risk control, and automated trade execution.
\vspace{-1pt}
\begin{itemize}
\item Developed automated trading bot in Python using Binance API and WebSocket for real-time market data streaming.
\item Implemented dynamic trading strategies, stop-loss mechanisms, and order execution algorithms with risk management.
\item Integrated Pandas and NumPy for market analysis and backtesting to improve trading accuracy and performance.
\item Deployed using Docker on AWS EC2 for continuous uptime, reliability, and monitoring with detailed logging.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}