% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Web Developer with hands-on experience designing, building, and deploying scalable web applications using JavaScript, React, Node.js, PHP, and cloud technologies. Proficient in website related code integration, technical documentation, and collaborating with clients to identify requirements and deliver tailored solutions. Adept at optimizing system performance, ensuring security best practices, and managing full SDLC from planning through deployment on AWS and GCP environments.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, PHP, Python, HTML5, CSS3, SQL

\textbf{Web Development \& Design:} React, Bootstrap, Web design, UI/UX, Graphic design, Responsive design

\textbf{Backend \& Databases:} Node.js, Django, PostgreSQL, MySQL, MongoDB, Database design

\textbf{Cloud \& DevOps:} AWS, Docker, CI/CD pipelines, GitHub Actions, Terraform

\textbf{Development Practices:} Agile methodology, Testing and debugging, Code reviews, Technical documentation

\textbf{Security \& Compliance:} OAuth, HTTPS, OWASP, API security, Encryption, Security best practices

\textbf{Soft Skills:} Client focus, Team collaboration, Excellent communication, Dependability, Initiative, Adaptability

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed and integrated website related code using JavaScript, React, and Node.js to enhance user experience and functionality.
\item Consulted with clients to document website requirements, identify business needs, and deliver tailored web solutions on schedule.
\item Designed RESTful APIs, optimized database queries, and configured hardware and software for optimal server performance and security.
\item Deployed cloud-based web applications using AWS, Docker, and CI/CD automation ensuring consistent uptime and scalability.
\item Executed software application tests and documented results to ensure products meet business requirements and quality standards.
\item Collaborated in Agile teams through code reviews, sprint planning, and technical documentation improving project delivery quality.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in designing and integrating website related code for enterprise-level web applications across frontend and backend layers.
\item Contributed to developing Proposal Management and Mailroom Tracking Systems by writing, modifying, and testing application code.
\item Worked with cross functional teams to gather client requirements and document technical specifications for system implementation.
\item Executed information and telecommunication systems tests and documented outcomes to ensure compliance with business requirements.
\item Supported deployment phases by optimizing content using graphics, database, and animation software for improved user engagement.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to access lessons, videos, and quizzes with secure authentication and real-time tracking.
\vspace{-1pt}
\begin{itemize}
\item Designed and integrated website related code using React, Node.js, and MySQL to support online education and user engagement.
\item Integrated lesson uploads, interactive quizzes, and performance dashboards enabling teachers to monitor student progress in real time.
\item Implemented secure authentication, role-based access control, and optimized database queries for high concurrent usage and reliability.
\item Deployed the platform on AWS with CDN caching, SSL encryption, and load balancing ensuring accessibility for over 6,000 students.
\end{itemize}

\textbf{Custom Business Web Solutions} -- \emph{Personal Project}

\vspace{-1pt}

Built POS systems, e-commerce sites, landing pages, and inventory management tools with secure, responsive design for multiple clients.
\vspace{-1pt}
\begin{itemize}
\item Consulted with clients to develop and document website requirements translating business needs into scalable web applications.
\item Designed and integrated website related code using React, Next.js, and Express.js with secure authentication and payment processing.
\item Created optimized content for websites using graphics, database integration, and animation software enhancing user experience and SEO.
\item Executed software application tests and documented technical requirements ensuring products met client specifications and quality standards.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}