% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Full Stack Web Developer with 3+ years of experience building and optimizing scalable web applications using JavaScript, React, PHP, and Python. Proven track record in WordPress development, third-party API integration, and performance optimization. Skilled in AWS cloud services, RESTful API design, and CI/CD automation. Experienced in refactoring legacy systems while implementing modern solutions to improve maintainability and load handling. Collaborative team player with strong problem-solving abilities.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Programming Languages:} JavaScript, PHP, Python, SQL, HTML5, CSS3, TypeScript, Bash

\textbf{Frameworks \& Libraries:} React, Redux, Node.js, Express.js, Django, Bootstrap, jQuery

\textbf{Database \& Data Management:} MySQL, PostgreSQL, MongoDB, DynamoDB, SQLite, Redis

\textbf{Cloud \& DevOps:} AWS, AWS S3, CloudFront, Lambda, Docker, CI/CD, GitHub Actions

\textbf{Development Practices:} Agile, Scrum, REST API, Git, Code Reviews, Performance Optimization

\textbf{Web Technologies:} WordPress, SEO, Responsive Design, API Integration, Version Control

\textbf{Soft Skills:} Problem Solving, Communication, Collaboration, Adaptability, Technical Documentation, Ownership

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed full stack web applications using JavaScript, React, and Node.js, improving e-commerce platform functionality and user experience.
\item Optimized SQL queries and integrated third-party APIs with secure authentication to enhance system reliability and performance.
\item Deployed cloud-based applications using AWS, Docker, and CI/CD pipelines ensuring 99.9\% uptime and seamless continuous deployment.
\item Refactored legacy code and replaced inefficient plugins with custom solutions reducing page load times and improving maintainability.
\item Collaborated within Agile teams through code reviews and sprint planning to deliver high-quality features on tight deadlines.
\item Mentored junior developers on WordPress best practices, API integration, and deployment strategies improving overall team productivity.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Contributed to full stack development of enterprise web applications using modern JavaScript frameworks and backend technologies.
\item Integrated RESTful APIs and third-party services to support proposal management and tracking system functionality.
\item Collaborated with cross functional teams to gather requirements, perform testing, and support deployment ensuring project success.
\item Applied performance optimization techniques and debugging tools to identify bottlenecks and improve application load handling.
\item Participated in Agile workflows including sprint planning and retrospectives to continuously improve development processes and code quality.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Built a scalable LMS enabling 6K+ students to learn with notes, videos, and interactive quizzes using React and Node.js.
\vspace{-1pt}
\begin{itemize}
\item Designed full stack LMS using React, Node.js, and MySQL with secure authentication and role-based access for teachers and students.
\item Integrated lesson uploads, quizzes, and real-time performance tracking dashboards optimizing user engagement and learning outcomes.
\item Optimized database queries and implemented caching strategies to handle high concurrent usage with minimal latency.
\item Deployed on AWS with CloudFront CDN, SSL encryption, and load balancing ensuring reliable access for over 6,000 active students.
\end{itemize}

\textbf{Custom Business Web Solutions} -- \emph{Personal Project}

\vspace{-1pt}

Built POS systems, e-commerce sites, and inventory management solutions with secure, responsive design improving client workflows.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed custom web applications using React, Next.js, and Express.js tailored to unique client business requirements.
\item Implemented secure authentication, inventory tracking, and payment processing with Stripe API integration ensuring transaction security.
\item Collaborated closely with clients to translate business needs into scalable technical solutions with iterative feedback cycles.
\item Optimized UI performance, responsiveness, and SEO across all projects to enhance user engagement and improve search rankings.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}