% Compile with XeLaTeX or LuaLaTeX
\documentclass[10pt,letterpaper]{article}

\usepackage{fontspec}
\usepackage[letterpaper, top=0.5in, bottom=0.5in, left=0.3in, right=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\usepackage[none]{hyphenat}
\sloppy
\emergencystretch=3em

% Set main font - Roboto Condensed Light for thinner letters
\IfFontExistsTF{Roboto Condensed}{
  \setmainfont{Roboto Condensed}[
    UprightFont=*-Light, 
    BoldFont=*-Regular
  ]
}{
  \setmainfont{TeX Gyre Heros} % bundled with TeX Live; safe on latexonline
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=15pt,topsep=2pt,itemsep=0pt,parsep=0pt,before=\vspace{-2pt},after=\vspace{2pt}}

\renewcommand{\baselinestretch}{0.95}

\begin{document}

\begin{center}
{\LARGE\textbf{Kusal Thiwanka}}\\[3pt]
\href{mailto:mhkusalthiwanka@gmail.com}{mhkusalthiwanka@gmail.com}\hspace{2em}%
(647) 677{-}2260\hspace{2em}%
Toronto, ON\hspace{2em}
linkedin.com/in/kusal-thiwanka
\end{center}

\vspace{6pt}

\textbf{PROFESSIONAL SUMMARY}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

Results-driven Front-End Developer with expertise in responsive website design, WordPress development, and modern JavaScript frameworks including React and Node.js. Proficient in HTML5, CSS3, and SASS with a strong focus on mobile-first design principles and SEO best practices. Experienced in optimizing website performance, implementing user-friendly interfaces, and collaborating across teams to deliver high-quality web solutions that meet business objectives and user needs.

\vspace{8pt}

\textbf{TECHNICAL SKILLS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Web Design \& Development:} HTML5, CSS3, SASS, JavaScript, React, Responsive Design, Mobile-First Design

\textbf{Frontend Frameworks \& Tools:} Bootstrap, jQuery, UI/UX Design, Web Design, Graphic Design

\textbf{Backend \& Database:} Node.js, PHP, MySQL, PostgreSQL, MongoDB

\textbf{Cloud \& DevOps:} AWS, Docker, CI/CD, GitHub Actions, GitLab

\textbf{SEO \& Performance:} SEO Best Practices, Performance Optimization, Website Maintenance, Debugging

\textbf{Software Development Practices:} Agile, Scrum, Testing, Code Reviews, Version Control

\textbf{Soft Skills:} Attention to Detail, Team Collaboration, Adaptability, Problem Solving, Time Management, Communication

\vspace{8pt}

\textbf{WORK EXPERIENCE}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Software Engineer -- KILATECH (Pvt) Ltd}, \textbf{Sri Lanka} \hfill Apr 2020 -- Dec 2022

\vspace{-1pt}

\begin{itemize}
\item Developed responsive web applications using JavaScript, React, and Node.js ensuring mobile-first design and cross-device compatibility.
\item Optimized website performance through efficient SQL queries, caching strategies, and frontend optimization techniques.
\item Collaborated with cross-functional teams to implement user-friendly interfaces meeting accessibility and usability standards.
\item Maintained and troubleshooted production websites using AWS and CI/CD pipelines ensuring consistent uptime and rapid issue resolution.
\item Conducted code reviews and followed Agile methodologies to deliver high-quality, maintainable code within project deadlines.
\item Applied SEO best practices and performance optimization techniques improving site visibility and user engagement across platforms.
\end{itemize}

\textbf{Software Engineer Trainee -- FMI (Pvt) Ltd, Sri Lanka} \hfill Apr 2019 -- Dec 2019

\vspace{-1pt}

\begin{itemize}
\item Assisted in developing responsive web applications with focus on frontend interfaces using HTML5, CSS3, and JavaScript frameworks.
\item Collaborated with design teams to implement user-friendly interfaces ensuring consistency across multiple devices and browsers.
\item Participated in website maintenance activities including troubleshooting issues, updating content, and optimizing performance.
\item Worked within Agile teams to prioritize tasks, meet conflicting deadlines, and deliver projects in fast-paced environments.
\item Gained hands-on experience in responsive design principles, SEO optimization, and website best practices across projects.
\end{itemize}

\vspace{6pt}

\textbf{RELATED PROJECTS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud-Based Learning Management System} -- \emph{Personal Project}

\vspace{-1pt}

Designed and built a fully responsive learning platform using React and Node.js enabling 6,000+ students to access educational content.
\vspace{-1pt}
\begin{itemize}
\item Developed a responsive full-stack web application using React, Node.js, and MySQL optimized for mobile and desktop devices.
\item Implemented user-friendly interfaces with intuitive navigation, interactive dashboards, and real-time progress tracking features.
\item Optimized website performance through database query optimization, caching, and frontend code optimization techniques.
\item Deployed on AWS with SSL encryption and CDN integration ensuring fast load times and secure access across all devices.
\end{itemize}

\textbf{Custom Business Web Solutions} -- \emph{Personal Project}

\vspace{-1pt}

Built multiple responsive business websites including e-commerce platforms and landing pages with SEO optimization and modern design.
\vspace{-1pt}
\begin{itemize}
\item Designed and developed responsive websites using React, Next.js, and CSS3 ensuring mobile-first design and cross-browser compatibility.
\item Collaborated with clients to understand requirements and translate business needs into user-friendly web interfaces and features.
\item Implemented SEO best practices including meta tags, semantic HTML, and performance optimization to improve search engine rankings.
\item Optimized website performance through code minification, image compression, and lazy loading resulting in faster load times.
\end{itemize}

\vspace{6pt}

\textbf{EDUCATION \& CERTIFICATIONS}\\[-8pt]
\noindent\rule{\textwidth}{1pt}

\vspace{-2pt}

\textbf{Cloud Architecture \& Administration Postgraduate Certificate (Hons)} \hfill Jan 2024 -- Aug 2024

Seneca College, Toronto, Canada

\textbf{Cybersecurity \& Threat Management Postgraduate Certificate (Hons)} \hfill Jan 2023 -- Aug 2023

Seneca College, Toronto, Canada

\textbf{Information Technology Bachelor of Science (Hons)} \hfill Jan 2016 -- Mar 2020

University of Colombo, Colombo, Sri Lanka

\textbf{AWS Certified Solutions Architect - Associate (Certification)} \hfill Aug 2024

\end{document}